### 2020-10-14 latex/2020-09-30_brownbag_slides/slides.tex
Initial commit of latex slides and paper

\documentclass[aspectratio=43]{beamer}
% Metropolis Theme ---------------------------------
\usetheme{metropolis} % Use metropolis theme

% Title --------------------------------------------
\title{Differnces-in-Differences with Spatial Spillover}
\date{\today}
\author{Kyle Butts}
% \institue{}

\input{preamble.tex}

% ---------------------------------------------------
\begin{document}
\maketitle

\begin{frame}{Spatial Spillovers}
    Effects of treatments at states, counties, etc. can spill over boundaries.

    \begin{itemize}
        \item e.g. large employer opening/closing in a county have positive or negative employment effects on nearby counties
    \end{itemize}

    Differences-in-differences that compare outcomes among treated units with ``control'' units are biased from the spillover of effects.
\end{frame}

\begin{frame}{Research Question}
    What are the sources of bias when researchers do not account for sptial spillover of treatment effects?

    \begin{itemize}
        \item In what contexts are these biases particularly large?

        \item Do current simple adjustments work?
    \end{itemize}
\end{frame}

\begin{frame}{Preview of Results}
    There are two sources of bias:
        \begin{itemize}
            \item[1.] Treatment effects spillover onto control units
            \item[2.] Treatment effects spillover onto also treated units
        \end{itemize}

    Solutions:
        \begin{itemize}
            \item Fixing bias 1 is relatively easy and works better when you have relatively few treated units

            \item Bias 2 worsens as treatment locations bunch more (spatial correlation of treatment increases)

            \item However, spatial correlation of treatment decreases bias 1
        \end{itemize}
\end{frame}

% Just TE
\imageframe{../../figures/figure-map_te.png}

% TE + Spill Control
\imageframe{../../figures/figure-map_te_spill_control.png}

% TE + Spill Control + Spill Treat
\imageframe{../../figures/figure-map_te_spill_all.png}

\begin{frame}{Potential Outcomes Framework}
    For exposition, I will label units as counties. Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{This form adapts the framework of Vazquez-Bare (2020) for the diff-in-diff setting.}

    \begin{itemize}
        \item Let $Y_{it}(D_i, h_i(\vec{D}))$ be the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.

        \item $\vec{D} \in \{0,1\}^N$ is the vector of all units treatments.

        \item The function $h_i(\vec{D})$ maps the entire treatment vector into a scalar that completely determines the spillover.

        \item In the world with no treatment, $\vec{0}$, we say $h_i(\vec{0}) = 0$.
    \end{itemize}
\end{frame}

\begin{frame}{Examples of $h_i(\vec{D})$}

    Examples of $h_i(\vec{D})$:

    \begin{itemize}
        \item \textbf{Treatment within $x$ miles:}

        $h_i(\vec{D})$ = 1 if there is a treated unit within $x$-miles of unit $i$ and = 0 otherwise

        \item \textbf{Average treatment among k-nearest neighbors:}

        $h_i(\vec{D}) = \sum_{j = 1}^k D_{n(i,j)} / k$ where $n(i,j)$ represents the j-th closest neighbor to unit $i$.

    \end{itemize}
\end{frame}

\begin{frame}{Estimand of Interest}
    Estimand of Interest: \[ 
        \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
    \]

    This is the direct effect in the absense of spillovers.
\end{frame}

\begin{frame}{Parallel Trends}
    \begin{itemize}
        \item I assume a modified version of the parallel trends assumption: \[
            \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 1, \vec{D} = 0 \right] 
        \] \[
            \quad =
            \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 0, \vec{D} = 0 \right],
        \]

        \item In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
    \end{itemize}
\end{frame}

\begin{frame}{What does Diff-in-Diff identify?}
    \begin{itemize}
        \item With that, I decompose the diff-in-diff estimate as follows:

        \begin{align*}
            &\mathbb{E}_i \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right] \\
            &\quad = 
            \textcolor{green}{\mathbb{E}_i \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
            &\quad\quad + 
            \textcolor{red}{\mathbb{E}_i \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
            &\quad\quad - 
            \textcolor{purple}{\mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\
            &\quad \equiv \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
        \end{align*}

    \end{itemize}
\end{frame}

\begin{frame}{Signing the Bias}
    \[ 
        \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}    
    \]

    \begin{table}
        \caption{Bias from Spillovers}
        \begin{tabular}{|l|cc|}
            \hline
            & + Spillover & - Spillover \\ \hline
            onto Treated & + Bias & - Bias \\
            onto Control & - Bias & + Bias \\
            \hline
        \end{tabular}
    \end{table}
\end{frame}

\begin{frame}{Example of Bias Simulation}
    \textbf{Treated Spillover:}

    $\mathbb{E}_i \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right] = -0.5$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.

    \textbf{Control Spillover:}

    $\mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right] = 1$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.

    \begin{itemize}
        \item Then, the bias term is \begin{align*}
            -0.5 * \text{\% of treated within 40 miles of a treated county} \\
            -1 * \text{\% of control within 40 miles of a treated county}
        \end{align*}
    \end{itemize}
\end{frame}

\begin{frame}{Monte Carlo Simulations}
    \begin{itemize}
        \item Simulated the following Data Generating Process \begin{align*}
            y_{it} &= -2 + \mu_t + \mu_i + \tau_{\text{direct}} D_{it} + \tau_{\text{spillover, control}} (1-D_{it}) \text{Near}_{it} \\ 
            &\quad + \tau_{\text{spillover, treated}} D_{it} \text{Near}_{it} + \varepsilon_{it}
        \end{align*}

        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly or through a spatial process.

        \item $\text{Near}_{it}$ is an indicator for having your county centroid be within 40 miles of a treated unit.

        \item $\tau_{\text{direct}} = 2$, $\tau_{\text{spillover, control}} = 1$ and $\tau_{\text{spillover, treat}} = -0.5$.
    \end{itemize}
\end{frame}

\begin{frame}{Source of Bias 1: Control Units}
    Simulation 1:

    \begin{itemize}
        \item The first simulation changes the probability of treatment, $D_{it}$.

        \item Assume, for now, there is only spillover on the control.

        \item Estimate the following equation: \[ 
            y_{it} = \alpha + \mu_t + \mu_i + \tau D_{it} + \epsilon_{it}    
        \]

        \item The bias of our estimate is \textit{Bias} $= \hat{\tau} - 2$
    \end{itemize}

\end{frame}

\imageframe{../../figures/figure-bias_from_prob_treat.png}

\begin{frame}{Solution: Removing ``contaminated'' controls}
    A common solution to the problem of spillover is to restimate without neighboring control units and see what happens to the bias.

    This simulation assumes the correct ``contaminated'' control units, i.e. only control units with $h_i(\vec{D}) \neq 0$, which is not possible for researchers.
\end{frame}

\imageframe{../../figures/figure-bias_fix.png}

\begin{frame}{Source of Bias 2: Treated Units}
    Simulation 2:

    \begin{itemize}
        \item I now add in the bias from spillover of treated units on to other treated units.

        \item This source of bias only occurs when treated units are located next to eachother, so the magnitude of bias depends on spatial autocorrelation of $D_{it}$.

        \item Using a method from geosciences, I generate correlated ``fields'' across the US.

        \item Then, for the counties in the top 10\% of values (hot spots in the field), I increase the probability of treatment.

        \item The unconditional probability remains fixed at 10\%.
    \end{itemize}
\end{frame}

\imageframe{../../figures/figure-krig.png}

\imageframe{../../figures/figure-spcorr_high_map_te_spill_all.png}

\imageframe{../../figures/figure-spcorr_low_map_te_spill_all}

\imageframe{../../figures/figure-bias_from_spatial_autocorr.png}

\imageframe{../../figures/figure-bias_fix_spatial_autocorr.png}

\begin{frame}{Spillovers as estimand of interest}
    Until now, we assumed our estimand of interest is $\textcolor{green}{\tau_{\text{direct}}}$.

    However, the two other spillover effects are of interest as well:
    \begin{itemize}
        \item $\textcolor{purple}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?

        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on others treatment? (This is what you should consider if you are a policy maker)
    \end{itemize}

    To estimate the spillover effects, we have to parameterize $h_i(\vec{D})$ function and the potential outcomes function $Y_i(D_i, h_i(\vec{D}))$.
\end{frame}

\begin{frame}{Next Steps}
    \begin{itemize}
        \item Monte Carlo: estimating spillovers and the problem of misspecification

        \item Application: replicate paper(s) with a consideration of spillovers (any ideas?)
    \end{itemize}
\end{frame}

\end{document}

### 2020-10-14 latex/paper/paper.tex
Initial commit of latex slides and paper

\documentclass[11pt]{article}

\title{Differences-in-Differences with Spatial Spillover}
% \subtitle{Subtitle}
\date{\today}
\author{Kyle Butts}
% \institue{}

\input{../preamble.tex}

\usepackage[
    citestyle= authoryear,
    style= authoryear, 
    natbib= true, 
    backend= biber
]{biblatex}
\addbibresource{references.bib}

\usepackage{rotating}

\begin{document}

% Title Page ---------------------------------------
\maketitle
\begin{abstract}
    Empirical work often uses treatment variables defined by geographic boundaries. When researchers ignore the common problem that the effects of treatment cross over borders, differences-in-differences produces biased estimates for the average treatment effect. In this paper, I identify two sources of bias. First, the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment. Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. I use Monte Carlo simulations to show when the biases are particularly large. Further, I show that common solution used in the literature of removing `contaminated' control units only prevents one source of bias. Lastly, I propose improved estimation strategies that can remove both sources of bias.  
\end{abstract}

\newpage

% --------------------------------------------------
\section{Introduction}
% --------------------------------------------------
Empirical work in economic often considers treatment assigned by geographic boundaries such as cities, counties, and states. The effects of treatment does not typically stay within these boundaries whether it be from people crossing borders or from general equilibrium mechanisms affecting neighboring areas. 
In causal inference, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that treatment effects do not depend on the treatment status of any other unit \citep{Rubin_1980}. This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units treatment assignment affects a unit's outcome.\footnote{Close can refer to many different things, e.g. geographic distance, node distance in graph theory, or social relationships in schools or cities.}

Despite the problem of spatial spillovers being common across many settings, Table 1 of \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously. In a survey of 8 top Economics and Finance Journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only 8 include spillovers to prevent bias in the estimation of treatment effects.

In the presence of these spatial spillovers, I identify two sources of bias that result when estimating treatment effects by differences-in-differences. First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend. When estimating by differences-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes. Therefore the spillover is subtracted from the estimated treatment effect and the sign of the bias is the opposite sign of the spillover. For example, if a factory opening in a given county benefits both that county and neighboring counties, the treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be in the counterfactual.

Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units. Therefore the spillover is added to the treated units' change in outcomes. Therefore the bias of treatment effect is the same sign as the sign of the spillover. For example a factory opening in two neighboring counties might cause the benefit of each individual factory to decrease. The estimated treatment effect will be negatively biased because there is a negative spillover onto also treated units.

The magnitude of the bias depends on two factors: the size of the spillover and the number of units affected by spillovers. If a researcher expects that spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large. My paper provides an explicit form for this bias and therefore researchers can give bounds for the bias under assumptions about the upper bound of the spillover effect and on number of units affected. In the paper, I use Monte Carlo simulations in order to quantify the magnitude of bias in various spillover settings.

In \citet{Berg_Streitz_2019}, they find that 6 of the 8 papers that include spillovers directly in their estimation strategy simply drop the control units they suspect to be affected by spillovers. Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers on to control units. Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where there is a high proportion of control units neighboring treated units.

% @TODO: Urban Application

% --------------------------------------------------
\subsection{Literature Review}
% --------------------------------------------------

There are two different models of SUTVA violations in the literature. Within-group spillovers are when units are in distinct groups and outcomes depend on the treatment status of your group only. For example, SUTVA is violated if a person's likelihood of getting sick depends on the vaccine rate of his community. In this case, the community is the group within which spillovers can occur. Between-group spillovers is this case where groups are overlapping which allows for more general forms of spillover. For example, a counties' economic outcomes depend on the economic outcomes of nearby counties (even across state borders).

One set of literature discusses `partial intereference' where spillovers are assumed to only occur within a group and not across groups.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with contrl units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.

The potential outcome framework used in my paper extends the model in \citet{Vazquez-Bare_2019} which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$ (this is referred to as an exposure mapping). Adding an exposure mapping to the potential outcomes framework allows to explicitly model SUTVA violations. In \citet{Vazquez-Bare_2019}, he models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector. Using this framework, he shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect. My paper considers the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by differences-in-differences.

\citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''. Then, the authors describe how the ATE estimated by diff-in-diff averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h_i(\vec{D})$. This paper does not include spillovers in the estimation of ATE because researchers often wish to understand the effects seperately.

The paper closest to mine is \citet{Delgado_Florax_2015} where they consider spillover only on to control units and identify a bias that can come from estimating a diff-in-diff model without explicitly controlling for spillovers. Using Monte-Carlo simulations, they find that there is an omitted variable bias problem by not including a measure of spillovers. My paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.

A similar paper, \citet{Clarke_2017}, finds an explicit form for bias when estimating a diff-in-diff model with spillover onto control units. However, they model a specific kind of spillover that only allows spillovers onto control units and assumes spillovers are non-additive. Lastly, \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} find results for a specific potential outcome function where $h_i(\vec{D})$ is the proportion of treated contiguous counties. They allow this spillover to enter the potential outcome additively and the coefficient is allowed to differ by own treatment status.

In my framework, if I assume the particular functional forms for potential outcomes of \citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}, I arrive at the same bias equation as theirs.

%%%%
The paper is structured as follows. ...

% --------------------------------------------------
\section{Potential Outcomes Framework}
% --------------------------------------------------

In this paper, I am assuming there is a time $t_0$ where treatment turns on for all treated units and remains on afterwards. The potential outcome framework used here extends \citet{Vazquez-Bare_2019} model which defines potential outcomes for unit $i$ at time $t$ as a function of own treatment-status $D_i$ and of a function of the vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$. This function $h_i(\vec{D})$ is referred to as an `exposure mapping' and in this paper will be assumed to be a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The function $h_i(\vec{D})$ measures the exposure to spatial spillover and no exposure to spatial spillovers is when $h_i(\vec{D}) = 0$.

To help better understand an exposure mapping, I will give three examples of $h_i(\vec{D})$. Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$. First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $x$-miles of a treated unit (also commonly used is counties that share borders). In this case \[
    h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < x ] 
\] Second, $h_i(\vec{D})$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
    h_i(\vec{D}) = 1/k \sum_{j \in k(i)} D_j,
\]
where $k(i)$ is the index of unit $i$'s k-nearest neighbors. Last, is the spatial decay function which depends on  the decay parameter $\alpha$. In this case, spillover intensity is the sum of across all treated observations' decay term, i.e. \[ 
    h_i(\vec{D}) = \sum_{j \neq i} D_j \exp^{-\alpha d_i(j)}
\] 
The exposure mapping is part of the parameterization of spillovers, but the functional form of the potential outcome still would need to be specified.

% --------------------------------------------------
\subsection{Spatial Spillovers}
% --------------------------------------------------

With a new definition of potential outcomes, let me formalize what is meant by ``spatial spillovers'. I will define `spillover onto control units' as: \[
    Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0).
\] 
Then, we will take the average spillover onto control units which averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
    \tau_{\text{spillover, control}} = \mathbb{E}_i \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
\]
These spillover effects depend on the average of exposure mapping. For example, assuming the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$, then an individual control unit's spillover effect is $\beta_{\text{spillover, control}} \ h_i(\vec{D})$. The average spillover onto control unit would therefore be $\tau_{\text{spillover, control}} = \beta_{\text{spillover, control}} * \mathbb{E}_{i} \left[ h_i(\vec{D})\right]$, i.e. the average over all control units exposure mapping.

Similarly, we define the spillover onto also treated units as: \[ 
    \tau_{\text{spillover, treated}} = \mathbb{E}_i \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
\]

It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using differences-in-differences. For the paper, I assume that the term `Average Treatment Effect' is trying to measure what I will call the `direct effect of treatment': \[
    \tau_{\text{direct}} = \mathbb{E}_i \left[ Y_{i}(1, 0) - Y_{i}(0, 0) \ \vert \ D_i = 1 \right],
\] 
which measures the effect of being treated in the absence of exposure to spillovers. This differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
    \mathbb{E}_i \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(0, h_i(\vec{D})) \ \vert \ D_i = 1 \right],
\] 
where the expectation is over individuals and their exposures. I prefer the former because it allows for seperation between the direct effect of treatment and the spillover effects themselves.\footnote{The spillover effects themselves might be of interest to the researcher, so clearly seperating them is beneficial in estimation. Later they can be combined to estimate the `net effects' that \citet{Sävje_Aronow_Hudgens_2019} estimate.}

% --------------------------------------------------
\subsection{Bias in Differences-in-Difference Estimation}
% --------------------------------------------------

In this section, I identify the two sources of bias in differences-in-differences estimation. For exposition, I will refer to two periods, $t = 0$ and $t = 1$, but this can be replaced by averages across $Y$ in the pre-period and the post-period respectively. First, I present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.

\begin{assumption}[Parallel Counterfactual Trends]\label{parallel}
    \[ 
        \mathbb{E}\left[ Y_{i1}(0, 0) - Y_{i0}(0, 0) \ \vert \ D_i = 1 \right] = 
        \mathbb{E}\left[ Y_{i1}(0, 0) - Y_{i0}(0, 0) \ \vert \ D_i = 0 \right]
    \]
\end{assumption}

This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status. This generalizes to the typical Parallel Counterfactual Trends because typically SUTVA assumes that every unit has zero exposure.

When researchers run the canonical differences-in-differences regression \[ 
    y_{it}  = \alpha + \tau D_{it} + \epsilon_{it},
\]
$\hat{\tau}$ will be a biased estimate for $\tau_{\text{direct}}$.
Given that Assumption \ref{parallel} holds, the estimate can be decomposed as the direct effect and the two sources of spillover bias.

\begin{theorem}
    \label{thm:bias}
    If Assumption \ref{parallel} holds, 
    \begin{align*}
        \mathbb{E}[\hat{\tau}] &= \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right] \\ 
        &= \tau_{\text{direct}} + \tau_{\text{spillover, treated}} - \tau_{\text{spillover, control}}
    \end{align*}
\end{theorem}

The intuition behind the biases are as follows. First, the change in outcomes among treated units combines the direct effect and the spillover from nearby treated units. Therefore the first difference adds the average spillover onto the treated units. Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover onto control units. Since $\tau{hat}$ is found by subtracting this second difference, we subtract the average spillover onto the control.

% --------------------------------------------------
\subsection{Example Parameterization of Bias}
% --------------------------------------------------

% --------------------------------------------------
\section{Monte Carlo Simulations}
% --------------------------------------------------

I now turn to a series of Monte Carlo Simulations to highlight the importance for controlling for spillovers in simulations.

% --------------------------------------------------
\newpage \printbibliography
% --------------------------------------------------

% --------------------------------------------------
\newpage \appendix 
\renewcommand{\thetable}{\Alph{section}.\arabic{table}}
% --------------------------------------------------

% --------------------------------------------------
\section{Proofs}
% --------------------------------------------------

\textbf{Proof of Theorem \ref{thm:bias}}
\begin{align*}
    \mathbb{E}_i\left[ \hat{\tau} \right] &= \mathbb{E}_i\left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E}_i\left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right] \\
    &= 
    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i\left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
    &= 
    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i\left[ Y_{i1}(0, h_i(\vec{D})) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
    &= 
    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\ 
    &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\ 
    &= 
    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1 \right] \\
    &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\  
    &= \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
    &= \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
    &= \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
    &= 
    \mathbb{E}_i \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E}_i \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
    &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
    &= \tau_{\text{direct}} + \tau_{\text{spillover, treated}} - \tau_{\text{spillover, control}}
\end{align*}

\end{document}

### 2020-10-15 latex/paper/paper.tex
Added Jim Flynn's Comments

@@
 
-\title{Differences-in-Differences with Spatial Spillover}
+\title{\color{teal} Differences-in-Differences with Spatial Spillover}
 % \subtitle{Subtitle}
-\date{\today}
-\author{Kyle Butts}
-% \institue{}
+\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
+\date{\footnotesize\today}
 
@@
 % Title Page ---------------------------------------
+
+\begin{titlepage}
+
     \maketitle
+
     \begin{abstract}
@@
 Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-I use Monte Carlo simulations to show when the biases are particularly large.
-Further, I show that common solution used in the literature of removing `contaminated' control units only prevents one source of bias.
+I use Monte Carlo simulations to demonstrate when the biases are particularly large.
+Further, I show that a common solution used in the literature of removing `contaminated' control units only prevents one source of bias.
 Lastly, I propose improved estimation strategies that can remove both sources of bias.
     \end{abstract}
+\end{titlepage}
 
@@
 % --------------------------------------------------
-Empirical work in economic often considers treatment assigned by geographic boundaries such as cities, counties, and states.
-The effects of treatment does not typically stay within these boundaries whether it be from people crossing borders or from general equilibrium mechanisms affecting neighboring areas.
-In causal inference, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that treatment effects do not depend on the treatment status of any other unit \citep{Rubin_1980}.
-This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units treatment assignment affects a unit's outcome.\footnote{Close can refer to many different things, e.g.
+Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states.
+The effect of these treatments do not typically stay within these boundaries whether it be from people crossing borders or from general equilibrium mechanisms affecting neighboring areas.
+In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that treatment effects do not depend on the treatment status of any other unit \citep{Rubin_1980}.
+This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
 geographic distance, node distance in graph theory, or social relationships in schools or cities.}
 
-Despite the problem of spatial spillovers being common across many settings, Table 1 of \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
-In a survey of 8 top Economics and Finance Journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only 8 include spillovers to prevent bias in the estimation of treatment effects.
+Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
+In a survey of eight top Economics and Finance Journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers to prevent bias in the estimation of treatment effects.
 
-In the presence of these spatial spillovers, I identify two sources of bias that result when estimating treatment effects by differences-in-differences.
+In the presence of these spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard differences-in-differences methodologies.
 First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
 When estimating by differences-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes.
-Therefore the spillover is subtracted from the estimated treatment effect and the sign of the bias is the opposite sign of the spillover.
-For example, if a factory opening in a given county benefits both that county and neighboring counties, the treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be in the counterfactual.
+In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
+For example, if a factory opening in a given county benefits both that county and neighboring counties, the treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
 
@@
 The magnitude of the bias depends on two factors: the size of the spillover and the number of units affected by spillovers.
-If a researcher expects that spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large.
-My paper provides an explicit form for this bias and therefore researchers can give bounds for the bias under assumptions about the upper bound of the spillover effect and on number of units affected.
-In the paper, I use Monte Carlo simulations in order to quantify the magnitude of bias in various spillover settings.
+If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large.
+This paper provides an explicit form for this bias and enables researchers to give bounds for it under assumptions about the size of the spillover effect and on number of units affected.
+I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.
 
-In \citet{Berg_Streitz_2019}, they find that 6 of the 8 papers that include spillovers directly in their estimation strategy simply drop the control units they suspect to be affected by spillovers.
+\citet{Berg_Streitz_2019} find that six of the eight papers that include spillovers directly in their estimation strategy simply drop the control units they suspect to be affected by spillovers.
 Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers on to control units.
 Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where there is a high proportion of control units neighboring treated units.
+
+@TODO: Paragraph on practical guidance on including spillover measures
 
@@
 In this case, the community is the group within which spillovers can occur.
-Between-group spillovers is this case where groups are overlapping which allows for more general forms of spillover.
+Between-group spillovers occur when groups are overlapping which allows for more general forms of spillover.
 For example, a counties' economic outcomes depend on the economic outcomes of nearby counties (even across state borders).
+@TODO: Add citations for papers that find this.
 
-One set of literature discusses `partial intereference' where spillovers are assumed to only occur within a group and not across groups.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with contrl units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.
+One set of literature discusses `partial intereference' where spillovers are assumed to only occur within a group and not across groups.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with control units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.
 
-The potential outcome framework used in my paper extends the model in \citet{Vazquez-Bare_2019} which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$ (this is referred to as an exposure mapping).
+\citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector.
+He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$ (this is referred to as an exposure mapping).
 Adding an exposure mapping to the potential outcomes framework allows to explicitly model SUTVA violations.
-In \citet{Vazquez-Bare_2019}, he models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector.
 Using this framework, he shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.
-My paper considers the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by differences-in-differences.
+My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by differences-in-differences.
 
@@
 Then, the authors describe how the ATE estimated by diff-in-diff averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h_i(\vec{D})$.
-This paper does not include spillovers in the estimation of ATE because researchers often wish to understand the effects seperately.
+This paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
 
@@
 Using Monte-Carlo simulations, they find that there is an omitted variable bias problem by not including a measure of spillovers.
-My paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.
+This paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.
 
-A similar paper, \citet{Clarke_2017}, finds an explicit form for bias when estimating a diff-in-diff model with spillover onto control units.
-However, they model a specific kind of spillover that only allows spillovers onto control units and assumes spillovers are non-additive.
+Similarly, \citet{Clarke_2017} finds an explicit form for bias when estimating a diff-in-diff model with spillover onto control units.
+However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units.
 Lastly, \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} find results for a specific potential outcome function where $h_i(\vec{D})$ is the proportion of treated contiguous counties.
@@
 
-In this paper, I am assuming there is a time $t_0$ where treatment turns on for all treated units and remains on afterwards.
-The potential outcome framework used here extends \citet{Vazquez-Bare_2019} model which defines potential outcomes for unit $i$ at time $t$ as a function of own treatment-status $D_i$ and of a function of the vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$.
-This function $h_i(\vec{D})$ is referred to as an `exposure mapping' and in this paper will be assumed to be a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The function $h_i(\vec{D})$ measures the exposure to spatial spillover and no exposure to spatial spillovers is when $h_i(\vec{D}) = 0$.
+Assume there is a time $t_0$ where treatment turns on for all treated units and remains on afterwards.
+As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and of a function of the vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$.
+This function $h_i(\vec{D})$ is referred to as an `exposure mapping' and is a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The function $h_i(\vec{D})$ measures the exposure to spatial spillover and no exposure to spatial spillovers is when $h_i(\vec{D}) = 0$.
 
-To help better understand an exposure mapping, I will give three examples of $h_i(\vec{D})$.
+To help better understand an exposure mapping, I give three examples of $h_i(\vec{D})$.
 Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
-First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $x$-miles of a treated unit (also commonly used is counties that share borders).
+First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $x$-miles of unit $i$ (also commonly used is counties that share borders).
 In this case \[
     h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < x ] 
-\] Second, $h_i(\vec{D})$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
+\] 
+Second, $h_i(\vec{D})$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
     h_i(\vec{D}) = 1/k \sum_{j \in k(i)} D_j,
@@
 Last, is the spatial decay function which depends on  the decay parameter $\alpha$.
-In this case, spillover intensity is the sum of across all treated observations' decay term, i.e.
+In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
 \[
@@
 \] 
-The exposure mapping is part of the parameterization of spillovers, but the functional form of the potential outcome still would need to be specified.
+The exposure mapping is part of the parameterization of spillovers, but the functional form of the potential outcome still needs to be specified.
 
@@
 
-With a new definition of potential outcomes, let me formalize what is meant by ``spatial spillovers'. I will define `spillover onto control units' as: \[
+With a new definition of potential outcomes, I now formalize what is meant by ``spatial spillovers'. I define `spillover onto control units' as: \[
     Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0).
 \] 
-Then, we will take the average spillover onto control units which averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
+Then, the average spillover onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
     \tau_{\text{spillover, control}} = \mathbb{E}_i \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
 \]
-These spillover effects depend on the average of exposure mapping.
+To emphasize, the average spillover effect depends on the average of exposure mapping.
 For example, assuming the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$, then an individual control unit's spillover effect is $\beta_{\text{spillover, control}} \ h_i(\vec{D})$.
@@
 It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using differences-in-differences.
-For the paper, I assume that the term `Average Treatment Effect' is trying to measure what I will call the `direct effect of treatment': \[
+I assume that the term `Average Treatment Effect' is trying to measure what I will call the `direct effect of treatment': \[
     \tau_{\text{direct}} = \mathbb{E}_i \left[ Y_{i}(1, 0) - Y_{i}(0, 0) \ \vert \ D_i = 1 \right],
@@
 where the expectation is over individuals and their exposures.
-I prefer the former because it allows for seperation between the direct effect of treatment and the spillover effects themselves.\footnote{The spillover effects themselves might be of interest to the researcher, so clearly seperating them is beneficial in estimation.
+I prefer the former because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.\footnote{The spillover effects themselves might be of interest to the researcher, so clearly seperating them is beneficial in estimation.
 Later they can be combined to estimate the `net effects' that \citet{Sävje_Aronow_Hudgens_2019} estimate.}
@@
 Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover onto control units.
-Since $\tau{hat}$ is found by subtracting this second difference, we subtract the average spillover onto the control.
+Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover onto the control.
 

### 2020-10-15 sim-bias_as_treat_increase.R
Added option to export slides format or paper format for Monte Carlo Simulations

@@ -28,6 +28,7 @@ source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd4
 
 # Export
 export <- TRUE
+slides <- FALSE
 
 
 ## Load Spatial Data -----------------------------------------------------------
@@ -169,25 +170,39 @@ bias <- sim_results %>%
 	) %>%
 	ungroup()
 
-(bias_plot <- ggplot(bias, aes(x= treat_prob, y= bias)) +
+bias_plot <- ggplot(bias, aes(x= treat_prob, y= bias)) +
 	geom_point(color = "#B48EAD") + geom_line(color = "#B48EAD") +
 	geom_ribbon(aes(ymin = bias_lower, ymax = bias_upper), fill = "#B48EAD", color = "white", alpha = 0.2) + 
 	xlim(0, 0.5) +
 	ylim(NA, 0) +
 	labs(
 		x = "Treatment Probability", 
-		y = "Bias of Tau hat", 
-		title = "As more units are treated, the bias increases", 
-		subtitle = "Monte Carlo simulations with 100 trials per simulation"
-		# caption = "spillovers: contiguous, tau = 2, tau_spill,control = 1, tau_spill,treat = 0.5"
+		y = "Bias of Tau hat"
 	) +
- 	theme_kyle(slides = TRUE, title_pos = "left", has_subtitle = TRUE) +
 	# Put Legend on Bottom
 	guides(fill = guide_legend(title.position = "top", nrow = 1)) 
-)
 
-if(export) ggsave("figures/figure-bias_from_prob_treat.png", plot= bias_plot, 
+
+if(slides) {
+	bias_plot <- bias_plot + 
+		labs(	
+			title = "As more units are treated, the bias increases", 
+			subtitle = "Monte Carlo simulations with 100 trials per simulation"
+		) + 
+		theme_kyle(slides = TRUE, title_pos = "left", has_subtitle = TRUE)
+}
+if(!slides) {
+	bias_plot <- bias_plot +
+		theme_kyle()
+}
+
+bias_plot
+
+if(export & slides) ggsave("figures/figure-bias_from_prob_treat_slides.png", plot= bias_plot, 
 	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+
+if(export & !slides) ggsave("figures/figure-bias_from_prob_treat.png", plot= bias_plot, 
+						   dpi= 300, width= 2400/300, height= 1800/300, bg= "transparent")
 
 
[…]

### 2020-10-15 sim-bias_from_spatial_autocorr.R

@@ -28,6 +28,9 @@ source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd4
 # Export
 export <- TRUE
 
+# Produce figures for slides?
+slides <- TRUE
+
 ## Load Spatial Data -----------------------------------------------------------
 # From data-prepare_counties.R
 load(file= "data/counties_and_mat.RData")
@@ -166,8 +169,6 @@ bias <- sim_results %>%
  	labs(
  		x= "Spatial Autocorrelation Measure", 
  		y= "Bias of Tau hat", 
- 		title= "Bias as spatial correlation changes", 
- 		subtitle= "Monte Carlo simulations with 100 trials for each simulation",
  		color= "Spillover on to Treated Units"
 	) +
  	theme_kyle(slides = TRUE, title_pos = "left", has_subtitle = TRUE) + 
@@ -175,8 +176,31 @@ bias <- sim_results %>%
 )
 
 
-if(export) ggsave("figures/figure-bias_from_spatial_autocorr.png", plot= bias_plot, 
-	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+
+if(slides) {
+	bias_plot <- bias_plot + 
+		labs(	
+			title= "Bias as spatial correlation changes", 
+			subtitle= "Monte Carlo simulations with 100 trials for each simulation"
+		) + 
+		theme_kyle(slides = TRUE, title_pos = "left", has_subtitle = TRUE) + 
+		theme(plot.title = ggplot2::element_text(size = 14))
+}
+if(!slides) {
+	bias_plot <- bias_plot +
+		theme_kyle()
+}
+
+bias_plot
+
+
+
+if(export & slides) ggsave("figures/figure-bias_from_spatial_autocorr_slides.png", plot= bias_plot, 
+						   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+
+if(export & !slides) ggsave("figures/figure-bias_from_spatial_autocorr.png", plot= bias_plot, 
+							dpi= 300, width= 2400/300, height= 1800/300, bg= "transparent")
+
 
 
 ## With and Without removing Control units
@@ -211,21 +235,42 @@ bias_by_method <- sim_results %>%
 		labs(
 			x = "Spatial Autocorrelation Measure", 
 			y = "Bias of Tau hat", 
-			title = "Dropping control units no longer effectively removes all bias", 
[…]

### 2020-10-15 figure-gen_map_examples_with_bias.R
Finished adjusting figures to be slide and non-slide versions

@@ -24,6 +24,10 @@ source("helper-sim_function.R")
 # Load theme_kyle()
 source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/ef6834e879f98be630bec9fd48c7e0bd945689be/theme_kyle.R")
 
+# Is for slides or paper?
+slides <- FALSE
+
+
 ## Load Parameters -------------------------------------------------------------
 te <- 2
 te_spill <- 1
@@ -313,27 +317,37 @@ usethis::ui_done("Finished exporting high_zp maps")
 
 
 ## Kriging Example -------------------------------------------------------------
-(
-	plot_krig <- ggplot() +
-		geom_sf(data= counties_treat_high_zp, aes(fill= sim), color= "grey60", size= 0.2) + 
-		geom_sf(data= counties_treat_high_zp %>% filter(zone == TRUE), fill = NA, color = "black") +
-		geom_sf(data= us, fill = NA, color= "grey30", size= 0.2) + 
-		# Remove Coordinates, leaving just the map
-		coord_sf(datum = NA) +
+plot_krig <- ggplot() +
+	geom_sf(data= counties_treat_high_zp, aes(fill= sim), color= "grey60", size= 0.2) + 
+	geom_sf(data= counties_treat_high_zp %>% filter(zone == TRUE), fill = NA, color = "black") +
+	geom_sf(data= us, fill = NA, color= "grey30", size= 0.2) + 
+	# Remove Coordinates, leaving just the map
+	coord_sf(datum = NA) +
+	labs(
+		fill= ""
+	) +
+	# Put Legend on Bottom
+	guides(fill = guide_legend(title.position = "top", nrow = 1)) +
+	# Fill Scale, colors from R color Brewer
+	scale_fill_distiller(palette = "Spectral")
+
+if(slides) {
+	plot_krig <- plot_krig + 
 		labs(
-			# title= "Direct Effect + Spillover on Control and Treated", 
 			title = "Kriging Example",
-			subtitle= glue::glue("Spatial Autocorrelation Measure = {high_zone_plus}"),
-			fill= ""
-		) +
+			subtitle= glue::glue("Spatial Autocorrelation Measure = {high_zone_plus}")
+		) + 
 		theme_kyle(slides = TRUE) + 
-		# Put Legend on Bottom
[…]

### 2020-10-15 sim-bias_as_treat_increase.R

@@ -232,15 +232,17 @@ bias_by_method <- sim_results %>%
 	ungroup()
 
 bias_fix_plot <- ggplot(bias_by_method, aes(x = treat_prob, y = bias)) +
- 	geom_point(aes(color = method)) + geom_line(aes(color = method)) +
+	geom_line(aes(color = method)) +
+ 	geom_point(aes(color = method, shape = method), size = 2) + 
  	geom_ribbon(aes(ymin = bias_lower, ymax = bias_upper, fill = method), color = "white", alpha = 0.2) + 
  	xlim(0, 0.5) + 
  	labs(
  		x = "Treatment Probability", 
  		y = "Bias of Tau hat",
- 		color = "Estimation Strategy", fill = "Estimation Strategy"
+ 		color = "Estimation Strategy", fill = "Estimation Strategy", shape = "Estimation Strategy"
  		# caption = "spillovers: contiguous, tau = 2, tau_spill,control = 1, tau_spill,treat = 0.5"
  	) +
+	scale_shape_manual(values = c(16, 18)) + 
 	scale_fill_manual(values = c("#5E81AC", "#B48EAD")) +
 	scale_color_manual(values = c("#5E81AC", "#B48EAD")) +
 	# Put Legend on Bottom

### 2020-10-15 sim-bias_from_spatial_autocorr.R

@@ -228,15 +228,17 @@ bias_by_method <- sim_results %>%
 	)
 
 (bias_fix_plot <- ggplot(bias_by_method, aes(x = zone_plus, y = bias)) +
-		geom_point(aes(color = method)) + geom_line(aes(color = method)) +
+		geom_line(aes(color = method)) +
+		geom_point(aes(color = method, shape = method), size = 2) + 
 		geom_ribbon(aes(ymin = bias_lower, ymax = bias_upper, fill = method), color = "white", alpha = 0.2) + 
 		xlim(0, 2.0) + 
 		ylim(NA, 0) +
 		labs(
 			x = "Spatial Autocorrelation Measure", 
 			y = "Bias of Tau hat", 
-			color = "Estimation Strategy", fill = "Estimation Strategy"
+			color = "Estimation Strategy", fill = "Estimation Strategy", shape = "Estimation Strategy"
 		) +
+		scale_shape_manual(values = c(16, 18)) + 
 		scale_fill_manual(values = c("#5E81AC", "#B48EAD")) +
 		scale_color_manual(values = c("#5E81AC", "#B48EAD")) +
 		# Put Legend on Bottom

### 2020-10-15 latex/paper/paper.tex
Wrote initial draft of Monte Carlo Simulation #1

@@
 
-% Title Page ---------------------------------------
-
+% --------------------------------------------------
 \begin{titlepage}
-
     \maketitle
@@
 \end{titlepage}
+% --------------------------------------------------
 
@@
 % --------------------------------------------------
+
 Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states.
@@
 Then, the average spillover onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
-    \tau_{\text{spillover, control}} = \mathbb{E}_i \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
+    \tau_{\text{spill,control}} = \mathbb{E}_i \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
 \]
 To emphasize, the average spillover effect depends on the average of exposure mapping.
-For example, assuming the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$, then an individual control unit's spillover effect is $\beta_{\text{spillover, control}} \ h_i(\vec{D})$.
-The average spillover onto control unit would therefore be $\tau_{\text{spillover, control}} = \beta_{\text{spillover, control}} * \mathbb{E}_{i} \left[ h_i(\vec{D})\right]$, i.e.
+For example, assuming the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$, then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h_i(\vec{D})$.
+The average spillover onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E}_{i} \left[ h_i(\vec{D})\right]$, i.e.
 the average over all control units exposure mapping.
@@
 Similarly, we define the spillover onto also treated units as: \[ 
-    \tau_{\text{spillover, treated}} = \mathbb{E}_i \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
+    \tau_{\text{spill,treated}} = \mathbb{E}_i \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
 \]
@@
         \mathbb{E}[\hat{\tau}] &= \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right] \\ 
-        &= \tau_{\text{direct}} + \tau_{\text{spillover, treated}} - \tau_{\text{spillover, control}}
+        &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
     \end{align*}
@@
 
+To exemplify the above bias, I will model a particular form of spillovers by parameterizing the exposure mapping and the potential outcomes equation.
+For the exposure mapping, I will assume that spillovers occur for any county that is within 40 miles of a treated county, i.e.
+\begin{align}
+    \label{eq:example_exposure}
+    \text{Near}_{it} \equiv h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < 40 ].
+\end{align}
+This specification is a simple one in that the spillover is not additive in the number of nearby treated units and does not decay over distance.
+The potential outcome is assumed to be additive in both treatment and in the exposure mapping, but the coefficient on $\text{Near}_{it}$ is allowed to differ between treated and non-treated unitts:
+\begin{align}
+    \label{eq:example_po}
+    \begin{split}
+        y_{it} &= \alpha + \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill,control}} (1-D_{it}) \text{Near}_{it} \\
+        &\quad + \beta_{\text{spill,treated}} D_{it} \text{Near}_{it} + \varepsilon_{it},
+    \end{split}
+\end{align}
+where $\mu_t$ and $\mu_i$ are unit and time fixed effects respectively.
+In this case, the spillover on an individual control unit is given by $\tau_{\text{spill,control}}$ and on an treated unit is $\tau_{\text{spill,treated}}$.
+
+If a researcher estimates 
+\begin{align}
+    \label{eq:twfe}    
+    y_{it} = \alpha + \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it},    
+\end{align}
+then the bias will be $\tau_{\text{spill,treated}} - \tau_{\text{spill,control}}$ where the two bias terms are \[ 
+    \tau_{\text{spill,control}} = \beta_{\text{spill,control}} \frac{\sum_{i: D_{it} = 0} \text{Near}_{it}}{N_C}
+\] and \[ 
+    \tau_{\text{spill,treated}} = \beta_{\text{spill,treated}} \frac{\sum_{i: D_{it} = 1} \text{Near}_{it}}{N_T},
+\]
+where $N_C$ and $N_T$ are the number of control and treated units respectively.
+Simply put, the bias will be the proportion of treated units that receive spillover effects time the size of the effect on treated units minus the proportion of control units that receive spillover effects time the size of the effect on control units.
+
 % --------------------------------------------------
@@
 
+% --------------------------------------------------
+\subsection{Simulation 1}
+% --------------------------------------------------
+
+\begin{figure}[t]
+    \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
+    \label{fig:bias_as_treat_prob}
+    {\centering
+        \resizebox{\columnwidth}{!}{
+            \includegraphics{../../figures/figure-bias_fix.png}
+        } 
+    }
+    {\footnotesize
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp1}.
+Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
+The line with diamond markers estimates with all control units.
+The line with circle markers removes control units with $\text{Near}_{it} = 1$.
+    }
+\end{figure}
+
 I now turn to a series of Monte Carlo Simulations to highlight the importance for controlling for spillovers in simulations.
+The data generating process used is defined by the exposure mapping given in Equation \ref{eq:example_exposure} and the data generating process given in Equation \ref{eq:example_po}.
+A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on in period $t = 10$.
+The intercepet is $\alpha = -2$, the fixed effects are $\mu_t \sim N(t * 0.2, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$, and the error term is $\epsilon \sim N(0, 2^2)$.
+Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spillover, control}} = 1$ and $\beta_{\text{spillover, treat}} = 0$.
+
+For the first simulation, I restrict spillovers only to occur among control units, i.e.
+$\tau_{\text{spillover, treat}} = 0$ and estimate the typical two-way fixed effects model.
+This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
+I assign treatment among U.S.
+counties randomly with various probabilities between 3 percent and 50 percent.
+The DGP is therefore
+\begin{equation}
+    \label{dgp1} 
+    y_{it} = -2 + \mu_t + \mu_i + 2 D_{it} - (1-D_{it}) \text{Near}_{it} + \varepsilon_{it}   
+\end{equation}
+
+The size of the bias from estimating Equation \ref{eq:twfe} at different treatment probabilities are presented in Figure \ref{fig:bias_as_treat_prob} as the line with diamond markers.
+As displayed in the figure, even for a low treatment probability of three percent, the bias is quite large with a 95 percent empirical confidence interval between -0.28 and -0.75.
+As treatment frequency increases, the bias increases as well but at a slower rate due to fewer additional control units receiving spillover units.
+
+A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers.
+I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers.
+The line stays centered constantly around zero as all control units that no longer followed their counterfactual trend were removed.
+This however requires complete knowledge of which units are affected.
+The bias would fall between the two lines as fewer problematic control units are removed.
+
+There is a trade-off between the bias and the variance of the estimator when using this methodolgy.
+As the treatment probability increases, the number of control units removed increases as well.
+This naturally yields are more variable estimator as seen in the wider 95 percent empirical confidence intervals.
+
+% --------------------------------------------------
+\subsection{Simulation 2}
+% --------------------------------------------------
+
+For the following simulation, I will add in spillovers onto treated units with $\beta_{\text{spillover, treat}} = -0.5$.
+The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
+In empirical applications, it is often the case that treatment assignment is concentrated in specific areas which yields higher proportion of treated units receiving spillover effects.
+
+In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
+
+\begin{figure}[t]
+    \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
+    \label{fig:kriging}
+    {\centering
+        \resizebox{\columnwidth}{!}{
+            \includegraphics{../../figures/figure-bias_fix.png}
+        } 
+    }
+    {\footnotesize
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp1}.
+Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
+The line with diamond markers estimates with all control units.
+The line with circle markers removes control units with $\text{Near}_{it} = 1$.
+    }
+\end{figure}
+
+\begin{figure}[t]
+    \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
+    \label{fig:bias_as_treat_prob}
+    {\centering
+        \resizebox{\columnwidth}{!}{
+            \includegraphics{../../figures/figure-bias_fix.png}
+        } 
+    }
+    {\footnotesize
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp1}.
+Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
+The line with diamond markers estimates with all control units.
+The line with circle markers removes control units with $\text{Near}_{it} = 1$.
+    }
+\end{figure}
 
@@
     &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
-    &= \tau_{\text{direct}} + \tau_{\text{spillover, treated}} - \tau_{\text{spillover, control}}
+    &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
 \end{align*}

### 2020-10-17 latex/paper/paper.tex
Finished Draft of paper with Second Monte Carlo Simulation

@@
 
-\title{\color{teal} Differences-in-Differences with Spatial Spillover}
+\title{\color{dark-maroon} Differences-in-Differences with Spatial Spillover}
 % \subtitle{Subtitle}
@@
 
-\usepackage{rotating}
+\usepackage{subcaption}
 
@@
     }
+
     {\footnotesize
@@
 The line with diamond markers estimates with all control units.
-The line with circle markers removes control units with $\text{Near}_{it} = 1$.
+The line with circle markers removes control units that share a border with a treated county.
     }
@@
 I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers.
-The line stays centered constantly around zero as all control units that no longer followed their counterfactual trend were removed.
-This however requires complete knowledge of which units are affected.
-The bias would fall between the two lines as fewer problematic control units are removed.
+Even though, I remove contiguous controls which is not hte correct measure of $h_i(\vec{D}$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
+As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.
 
@@
 
-For the following simulation, I will add in spillovers onto treated units with $\beta_{\text{spillover, treat}} = -0.5$.
+For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spillover, treat}} = -0.5$. The DGP is as follows 
+\begin{equation}
+    \label{dgp2} 
+    y_{it} = -2 + \mu_t + \mu_i + 2 D_{it} - (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
+\end{equation} 
 The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
@@
 
-In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
-
 \begin{figure}[t]
-    \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
+    \caption{Example of Kriging Field}
     \label{fig:kriging}
@@
         \resizebox{\columnwidth}{!}{
-            \includegraphics{../../figures/figure-bias_fix.png}
+            \includegraphics{../../figures/figure-krig.png}
         } 
@@
     {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp1}.
-Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
-The line with diamond markers estimates with all control units.
-The line with circle markers removes control units with $\text{Near}_{it} = 1$.
+        \textit{Notes:} This figure plots an example of a kriging simulation using the `gstat' package in R using an exponential variogram.
+The outlined counties are in the top ten percent of values for this simulation.
     }
@@
 
+In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
+Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
+One such field is depicted in Figure \ref{fig:kriging}.
+For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
+Then I assign treatment with a probability that differs based on Zone.
+The unconditional probability is equal to 5 percent in all simulations.
+To do this, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment:
+\begin{equation}
+    \label{eq:cond_prob}
+    P(D_i \ \vert \ \text{Zone}_i) = (.1 + \text{Zone Plus} * \text{Zone}_i) \frac{.05}{.1 * .9 + (.1 + \text{Zone Plus}) * .1}
+\end{equation}
+The second term normalizes probabilities so the unconditional probability stays at 5 percent.
+In our simulations, Zone Plus ranges from 0 which is the case where p = 10 percent for all counties to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.166 + 0.35 * \text{Zone}_i$
+
 \begin{figure}[t]
-    \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
-    \label{fig:bias_as_treat_prob}
+    \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
+    \label{fig:bias_spatial_autocorr}
     {\centering
         \resizebox{\columnwidth}{!}{
-            \includegraphics{../../figures/figure-bias_fix.png}
+            \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
         } 
@@
     {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp1}.
-Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp2}.
+Treatment probability is assigned according to the method described by the text and Equation \ref{eq:cond_prob}.
+Each point corresponds to the average bias for the given Zone Plus and the band is the 95 percent empirical confidence interval over 1000 simulations.
 The line with diamond markers estimates with all control units.
-The line with circle markers removes control units with $\text{Near}_{it} = 1$.
+The line with circle markers removes control units that share a border with a treated county.
     }
 \end{figure}
+
+The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
+The line with diamond markers is run on the full sample.
+As the level of spatial autocorrelation increases, the bias actually decreases.
+The reason for this is that as treatment becomes more concentrated in the `Zones', the number of control units receiving spillovers decreases while the number of treated units receiving spillovers increases.
+In this particular DGP, the effect of fewer control units on the bias is larger than the bias from more treated units.
+
+The line with circle markers in Figure \ref{fig:bias_spatial_autocorr} repeats the exercise of dropping control units that share a border with treated units.
+In the case where spillovers occur on treated units, all bias is not removed when dropping control units.
+That is because we only remove $\tau_{\text{spill,control}}$ but $\tau_{\text{spill,treated}}$ remains.
+To remove the second source of bias, it is necessary to acount directly for spillovers in the estimation strategy.
+I turn to this next.
 

### 2020-10-17 figure-gen_map_examples_with_bias.R

@@ -17,6 +17,7 @@ library("exactextractr")
 library("fixest")
 library("doParallel")  
 library("RColorBrewer")
+library("patchwork")
 
 # sim_data(i)
 source("helper-sim_function.R")
@@ -331,6 +332,48 @@ plot_krig <- ggplot() +
 	# Fill Scale, colors from R color Brewer
 	scale_fill_distiller(palette = "Spectral")
 
+plot_krig_highzp <- ggplot() +
+	geom_sf(data= counties_treat_high_zp, aes(fill= as.factor(treat)), color= "grey60", size= 0.2) + 
+	geom_sf(data= counties_treat_high_zp %>% filter(zone == TRUE), fill = NA, color = "black", size = 0.4) +
+	geom_sf(data= us, fill = NA, color= "grey30", size= 0.2) + 
+	# Remove Coordinates, leaving just the map
+	coord_sf(datum = NA) +
+	labs(
+		title = "Zone Plus = 1.4",
+		fill= "Treated Unit"
+	) +
+	theme_kyle() +
+	theme(legend.position = "bottom") +
+	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A")) + 
+	# Put Legend on Bottom
+	guides(fill = guide_legend(title.position = "top", nrow = 1))
+
+counties_treat_high_zp <- counties_treat_high_zp %>% mutate(
+	# `zone` has increased probability of treatment
+	prob_low = 0.1 + low_zone_plus * zone,
+	prob_low = prob_low * treat_prob/mean(prob_low),
+	
+	# Generate Treatment Variable
+	treat_low = (runif(n()) <= prob_low),
+	treat_low = as.numeric(treat_low)
+) 
+
+plot_krig_lowzp <- ggplot() +
+	geom_sf(data= counties_treat_high_zp, aes(fill= as.factor(treat_low)), color= "grey60", size= 0.2) + 
+	geom_sf(data= counties_treat_high_zp %>% filter(zone == TRUE), fill = NA, color = "black", size = 0.4) +
+	geom_sf(data= us, fill = NA, color= "grey30", size= 0.2) + 
+	# Remove Coordinates, leaving just the map
+	coord_sf(datum = NA) +
+	labs(
+		title = "Zone Plus = 0.4",
+		fill= "Treated Unit"
+	) +
+	theme_kyle() +
[…]

### 2020-10-17 sim-bias_from_spatial_autocorr.R

@@ -234,7 +234,6 @@ bias_by_method <- sim_results %>%
 		xlim(0, 2.0) + 
 		ylim(NA, 0) +
 		labs(
-			x = "Spatial Autocorrelation Measure", 
 			y = "Bias of Tau hat", 
 			color = "Estimation Strategy", fill = "Estimation Strategy", shape = "Estimation Strategy"
 		) +
@@ -249,7 +248,8 @@ if(slides) {
 	bias_fix_plot <- bias_fix_plot + 
 		labs(	
 			title = "Dropping control units no longer effectively removes all bias", 
-			subtitle = "Monte Carlo simulations with 100 trials per simulation"
+			subtitle = "Monte Carlo simulations with 100 trials per simulation",
+			x = "Spatial Autocorrelation Measure"
 		) + 
 		theme_kyle(slides = TRUE, title_pos = "left", has_subtitle = TRUE) + 
 		theme(
@@ -260,6 +260,9 @@ if(slides) {
 }
 if(!slides) {
 	bias_fix_plot <- bias_fix_plot +
+		labs(
+			x = "Zone Plus"
+		) +
 		theme_kyle() +
 		theme(
 			plot.title = ggplot2::element_text(size = 14),

### 2020-11-19 figure-gen_map_examples_with_bias.R
Updated Figures with "Treated counties outlined"

@@ -78,7 +78,7 @@ plot_te <- ggplot() +
 	coord_sf(datum = NA) +
 	labs(
 		title= "Direct Effect of Treatment",
-		subtitle= glue::glue("Pr(treatment) = {treat_prob_percent}; Bias = 0"),
+		subtitle= glue::glue("Pr(treatment) = {treat_prob_percent}; Bias = 0 \n Treated units outlined in black"),
 		fill= "Effect Size"
 	) + 
 	theme_kyle(slides = TRUE) + 
@@ -86,7 +86,8 @@ plot_te <- ggplot() +
 	guides(fill = guide_legend(title.position = "top", nrow = 1)) +
 	theme(legend.position = "bottom") +
 	# Fill Scale, colors from R color Brewer
-	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A"))
+	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A")) + 
+	theme(title = element_text(lineheight = 1.2))
 
 )
 
@@ -99,7 +100,7 @@ plot_te_spill_control <- ggplot(counties_treat) +
 	coord_sf(datum = NA) +
 	labs(
 		title= "Direct Effect + Spillover on Control", 
-		subtitle= glue::glue("Pr(treatment) = {treat_prob_percent}; Bias = -{bias_control}"),
+		subtitle= glue::glue("Pr(treatment) = {treat_prob_percent}; Bias = -{bias_control} \n Treated units outlined in black"),
 		fill= "Effect Size"
 	) + 
 	theme_kyle(slides = TRUE) + 
@@ -107,7 +108,8 @@ plot_te_spill_control <- ggplot(counties_treat) +
 	guides(fill = guide_legend(title.position = "top", nrow = 1)) +
 	theme(legend.position = "bottom") +
 	# Fill Scale, colors from R color Brewer
-	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A"))
+	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A")) + 
+	theme(title = element_text(lineheight = 1.2))
 )
 
 (
@@ -119,7 +121,7 @@ plot_te_spill_all <- ggplot(counties_treat) +
[…]

### 2020-11-19 latex/slides/Spillover_slides.tex
Renamed slides to Spillover_slides

--- 2020-10-14 latex/2020-09-30_brownbag_slides/slides.tex
@@
 
-\imageframe{../../figures/figure-bias_from_prob_treat.png}
+\imageframe{../../figures/figure-bias_from_prob_treat_slides.png}
 
@@
 
-\imageframe{../../figures/figure-bias_fix.png}
+\imageframe{../../figures/figure-bias_fix_slides.png}
 
@@
 
-\imageframe{../../figures/figure-krig.png}
+\imageframe{../../figures/figure-krig_slides.png}
 
@@
 
-\imageframe{../../figures/figure-bias_from_spatial_autocorr.png}
+\imageframe{../../figures/figure-bias_from_spatial_autocorr_slides.png}
 
-\imageframe{../../figures/figure-bias_fix_spatial_autocorr.png}
+\imageframe{../../figures/figure-bias_fix_spatial_autocorr_slides.png}
 

### 2020-11-22 latex/paper/paper.tex
Edits and added Bounding the Bias subsection

@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \begin{titlepage}
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Introduction}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 
-% @TODO: Urban Application
-
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \subsection{Literature Review}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \section{Potential Outcomes Framework}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-Assume there is a time $t_0$ where treatment turns on for all treated units and remains on afterwards.
-As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and of a function of the vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$.
-This function $h_i(\vec{D})$ is referred to as an `exposure mapping' and is a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The function $h_i(\vec{D})$ measures the exposure to spatial spillover and no exposure to spatial spillovers is when $h_i(\vec{D}) = 0$.
+Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards.
+As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$, denoted $Y_{i,t}(D_i, h_i(\vec{D})$), are a function of own treatment-status $D_i$ and,  departing from the canonical framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$.
+The function $h_i(\vec{D})$ is referred to as an `exposure mapping' and is a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The `exposure mapping' measures the intensity at which unit $i$ is affected by spatial spillovers.
+When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = 0$.
+The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment and can be summarized by $h_i(\vec{D})$.
 
@@
 \] 
+This exposure mapping is useful when it is assumed that spillovers do not decay over distance and the number of neighboring units treated do not impact the intensity of spillovers.
+For example, this mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
+In this case the distance $\bar{d}$ would be the distance people would likely travel to a nearby library.
+Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to the level of spillovers.
+
 Second, $h_i(\vec{D})$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \subsection{Spatial Spillovers}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
     \begin{align*}
-        \mathbb{E}[\hat{\tau}] &= \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right] \\ 
+        \mathbb{E}[\hat{\tau}] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right]}_{\text{Difference-in-Differences}} \\
+        &= 
+        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
+        &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
         &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
@@
 
-% --------------------------------------------------
-\subsection{Example Parameterization of Bias}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
+\subsection{Bounding the Bias}
+% ------------------------------------------------------------------------------
+
+The previous section finds an explicit form of the bias when estimating Equation \ref{eq:twfe}.
+The explicit form of bias can be used by researchers to provide bounds on the bias in a manner simmilar to \citet{Rambachan_Roth_2020}.
+To provide bounds on the bias, researchers must identify the set $\Delta = [\underline{\Delta}, \overline{\Delta}]$ such that it contains the bias \[
+    \tau_{\text{spill,treated}} - \tau_{\text{spill, control}} \in \Delta
+\]
+
+Choosing this set requires considerations of the economic context.
+It is guided by choices of parameterization of the exposure mapping and potential outcomes.
+To exemplify this bias, I will show a simple example that allows for a maximum bias bound.
+
+% ------------------------------------------------------------------------------
+\subsubsection{Example Parameterization of Bias}
+% ------------------------------------------------------------------------------
 
@@
     \begin{split}
-        y_{it} &= \alpha + \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill,control}} (1-D_{it}) \text{Near}_{it} \\
+        y_{it} &= \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill,control}} (1-D_{it}) \text{Near}_{it} \\
         &\quad + \beta_{\text{spill,treated}} D_{it} \text{Near}_{it} + \varepsilon_{it},
@@
 where $N_C$ and $N_T$ are the number of control and treated units respectively.
-Simply put, the bias will be the proportion of treated units that receive spillover effects time the size of the effect on treated units minus the proportion of control units that receive spillover effects time the size of the effect on control units.
+Simply put, the bias will be the product of the proportion of treated units that receive spillover effects and the size of the effect on treated units minus the proportion of control units that receive spillover effects time the size of the effect on control units.
 
-% --------------------------------------------------
+Then researchers wanting to create the bias set $\Delta$, will assume minimum and maximum values of $\beta_{\text{spill,control}}$, $\beta_{\text{spill, treated}}$, and a maximum proportion of exposed treated and control units.
+With these assumptions, the set $\Delta$ can be approximated and the partially identified set is given by $[\hat{\tau} + \underline{\Delta}, \hat{\tau} + \overline{\Delta}]$.
+Inference on this set can be done in the manner described in \citet{Rambachan_Roth_2020}.
+
+% ------------------------------------------------------------------------------
+\subsection{Improving Estimation}
+% ------------------------------------------------------------------------------
+
+The previous section shows how to estimate the magnitude of potential bias in the estimation of Equation \ref{eq:twfe}.
+However, parameterization of the potential outcomes and exposure mapping allows for unbiased estimates of $\tau_{\text{direct}}$ by controlling for the exposure mapping directly.
+This is recommended for two reasons.
+
+First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatmnet if the potential outcomes are correctly specified.
+In the case where potential outcomes are `somewhat' incorrectly specified, this can remove some of the bias in estimation.
+Simulations below highlight that since spillovers are likely to decay over distance, controlling for immediate neighbors removes a large portion of the average spillover effects.
+
+Second, the spillover effects are highly relevant for policy makers.
+If treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will understate the true effect of treatment.
+First, it will not include the neighboring units' benefit in the calculation.
+Second, since the treatment effect will subtract the neighboring units' benefit, the neighboring units' beneift will be \emph{double undercounted}.
+Similarly, the net benefits for a treated location depend on the direct effect and the spillover effect onto treated units.
+Therefore whether the benefits depend on the number of treated units nearby.
+
+% ------------------------------------------------------------------------------
 \section{Monte Carlo Simulations}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \subsection{Simulation 1}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
@@
 The intercepet is $\alpha = -2$, the fixed effects are $\mu_t \sim N(t * 0.2, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$, and the error term is $\epsilon \sim N(0, 2^2)$.
-Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spillover, control}} = 1$ and $\beta_{\text{spillover, treat}} = 0$.
+Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
 
 For the first simulation, I restrict spillovers only to occur among control units, i.e.
-$\tau_{\text{spillover, treat}} = 0$ and estimate the typical two-way fixed effects model.
+$\tau_{\text{spill, treat}} = 0$ and estimate the typical two-way fixed effects model.
 This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
@@
 
-% --------------------------------------------------
+% -----------------------------------------------------------------------------
 \subsection{Simulation 2}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spillover, treat}} = -0.5$. The DGP is as follows 
+For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
 \begin{equation}
@@
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \newpage \printbibliography
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 \newpage \appendix 
 \renewcommand{\thetable}{\Alph{section}.\arabic{table}}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
 

### 2020-11-28 latex/paper/paper.tex
Initial Draft of TVA Replication

@@
 
-\input{../preamble.tex}
+\input{preamble.tex}
 
-\usepackage[
-    citestyle= authoryear,
-    style= authoryear, 
-    natbib= true, 
-    backend= biber
-]{biblatex}
 \addbibresource{references.bib}
-
-\usepackage{subcaption}
 
@@
 
+These biases are explicit functions of potential outcomes and can be used inuitively by researchers to sign the bias.
 The magnitude of the bias depends on two factors: the size of the spillover and the number of units affected by spillovers.
@@
 
-\citet{Berg_Streitz_2019} find that six of the eight papers that include spillovers directly in their estimation strategy simply drop the control units they suspect to be affected by spillovers.
-Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers on to control units.
-Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where there is a high proportion of control units neighboring treated units.
+Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
+In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers in their empirical specification to prevent bias in the estimation of treatment effects.
 
@@
 % ------------------------------------------------------------------------------
-\subsection{Literature Review}
+\subsection{Contribution}
 % ------------------------------------------------------------------------------
@@
 
+Similarly, \citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model.
+However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units.
+Lastly, \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} find results for a specific potential outcome function where $h_i(\vec{D})$ is the proportion of treated contiguous counties.
+They allow this spillover to enter the potential outcome additively and the coefficient is allowed to differ by own treatment status.
+In my framework, if I assume the particular functional forms for potential outcomes of \citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}, I arrive at the same bias equation as theirs.
+
+The rest of the paper is structured as follows.
+Section 2 presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
+Section 3 presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature.
+Section 4 presents an application for evaluating the Tennessee Valley Authority program.
+
 % ------------------------------------------------------------------------------
@@
 For example, this mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
-In this case the distance $\bar{d}$ would be the distance people would likely travel to a nearby library.
+In this case the distance $\bar{d}$ would be the maximum distance people would likely travel to a nearby library.
 Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to the level of spillovers.
@@
 It is guided by choices of parameterization of the exposure mapping and potential outcomes.
-To exemplify this bias, I will show a simple example that allows for a maximum bias bound.
+To exemplify this bias, I will show a simple example that allows a researcher to bound the bias.
 
@@
 \end{align}
-This specification is a simple one in that the spillover is not additive in the number of nearby treated units and does not decay over distance.
+This specification is a simple one in that the spillover is not additive in the number of nearby treated counties and does not decay over distance before reaching $\bar{d}$.
 The potential outcome is assumed to be additive in both treatment and in the exposure mapping, but the coefficient on $\text{Near}_{it}$ is allowed to differ between treated and non-treated unitts:
@@
 
+In the example of library construction, a researcher would assume that people would not drive further than 40 miles to access the library.
+Further, a researcher can argue that treatment effect does not depend on whether other counties also have access to libraries.
+Therefore, only $\beta_{\text{spill,control}}$ needs to be bounded for the the bias to be bounded.
+
 % ------------------------------------------------------------------------------
@@
 
-Second, the spillover effects are highly relevant for policy makers.
+Second, the spillover effects themselves are potentially relevant for policy makers.
 If treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will understate the true effect of treatment.
@@
 
+There are a few practical considerations researchers should make when parametrizing the spillovers.
+
+In a set of Monte Carlo simulations, I check the sensitivity of estimates to misspecification of spillovers.
+
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\subsection{Simulation 1}
+\subsection{Simulation 1: Spillover on Controls Only}
 % ------------------------------------------------------------------------------
@@
     {\centering
-        \resizebox{\columnwidth}{!}{
+        \resizebox{\textwidth}{!}{
             \includegraphics{../../figures/figure-bias_fix.png}
@@
 I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers.
-Even though, I remove contiguous controls which is not hte correct measure of $h_i(\vec{D}$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
+Even though, I remove contiguous controls which is not hte correct measure of $h_i(\vec{D})$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
 As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.
@@
     {\centering
-        \resizebox{\columnwidth}{!}{
+        \resizebox{\textwidth}{!}{
             \includegraphics{../../figures/figure-krig.png}
@@
     {\centering
-        \resizebox{\columnwidth}{!}{
+        \resizebox{\textwidth}{!}{
             \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
@@
 To remove the second source of bias, it is necessary to acount directly for spillovers in the estimation strategy.
-I turn to this next.
 
 % ------------------------------------------------------------------------------
-\newpage \printbibliography
+\section{Application in Urban Economics}
+% ------------------------------------------------------------------------------
+
+To illustrate the importance of accounting for spatial spillovers in the estimation of treatment effects, I revisit the analysis of the Tennessee Valley Authority (TVA) in \citet{Kline_Moretti_2014}.
+The TVA program was a large-scale federal investment started in 1934 that focused on modernizing the Tennessee valley economy.
+The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy.
+By the end of WWII, the TVA became the largest single power supplier in the country.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.} With over \$20 Billion (in 2000 dollars) spent and hundreds of dollars transferred per person in the Authority, the impacts are very likely to cross far past the authority's borders.
+
+I will focus on three outcome variables in the analysis.
+The first two are (the log of) agricultural and manufacturing employment and the last is (the log of) median household income.
+Since the TVA focused on manufacturing employment, the authors predict that employment will grow in manufacturing and shrink in agricultural.
+Since manufacturing jobs pay more on average, the median household income will therefore grow.
+
+There are two primary forces causing spillover in this context.
+First, the large-scale investment in dams and electricity transmission lines brought cheap power to the region.
+It became cheaper for nearby locations to get connected to low-cost power and therefore likely lead to transition to manufacturing and away from farming in nearby counties.
+Second, \citet{Duranton_Puga_2003} highlight the agglomeration of input sourcing.
+When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties.
+These both suggest that spillovers will occur close to the spillover region and that the exposure will decay over distance.
+
+The analysis in \citet{Kline_Moretti_2014} begins by comparing long-differences in county-level outcomes from 1940 to 2000 between treated counties in the Authority and control counties outside.
+The primary difference-in-differences specification is
+\begin{equation}\label{eq:tva}
+    y_{c, t} = \mu_c + \alpha \text{Post}_t + \tau \text{TVA}_c \times \text{Post}_t + X_{c, 1940} \beta + X_{c, 1940} \times \text{Post}_t \gamma + \epsilon_{c,t},
+\end{equation}
+where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a series of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[
+    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
+\] Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
+
+\citet{Kline_Moretti_2014} estimate Equation \ref{eq:tva} to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
+However, their point estimates compare, in part, changes in outcomes between TVA counties with neighboring counties that likely were impacted by the large-scale electrification program.
+As described above and estimated below, the program likely induced positive manufacturing and negative agricultural employment effects in nearby counties.
+Therefore, the authors likely underestimate the impact on employment by comparing counties inside the Authroity to counties on the other side of the border.
+The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this and appear to do so in the empirical analysis below.
+
+The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is a weighted difference-in-differences.
+The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted.
+Hence, their method magnifies the bias compared to a standard difference-in-differences estimator.
+However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results.
+
+I extend their analysis to include spatial spillovers in the difference-in-differences specification.
+To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority.
+Specifically, I use the following intervals $\text{Dist} = \{(0, 100], (100, 250], (250, 500]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
+The extended specification is given as follows:
+\begin{equation}\label{eq:tva_spillover}
+    y_{i, 2000} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, 2000} - \varepsilon_{i, 1940})
+\end{equation} 
+The coefficients $\delta_d$ measure the spillover effect at different distances from the Authority.
+
+\begin{landscape}
+\thispagestyle{lscaped}
+
+\begin{table}[ht]
+    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
+    \label{tab:tva}
+    \renewcommand{\arraystretch}{1}
+
+    \begin{adjustbox}{width = 1.3\textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} lc@{\extracolsep{20pt}}cc@{\extracolsep{4pt}}ccc @{}}
+                % Head
+                \toprule
+
+                & \multicolumn{1}{c}{\textbf{Kline \& Moretti (2011)}} &
+                \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
+                \cmidrule{2-2} \cmidrule{3-3} \cmidrule{4-7} 
+                & & & & TVA between & TVA between & TVA between \\ 
+                & TVA & TVA & TVA & 0-100 mi. & 100-250 mi. & 250-500 mi. \\ 
+                \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\
+
+                % Body
+                \midrule
+
+                \input{../../tables/tva_replication.tex}
+
+                \bottomrule
+            \end{tabular}
+
+            % Notes 
+            \begin{tablenotes}\footnotesize
+                \item \textit{Notes.} Each row corresponds to an outcome variable.
+Each cell is the point estimate and the standard error for the variable described in the column title.
+All standard errors are clustered at the state-level.
+The column labeled \citet{Kline_Moretti_2014} replicates the Oaxaca-Blinder estimator found in column (3) of Table III.
+The column labeled `Diff-in-Diff' estimates Equation \ref{eq:tva} by OLS.
+The final four columns labeled `Diff-in-Diff with Spillovers' are estimates from Equation \ref{eq:tva_spillover}.
+
+                \item $^{*} p< 0.1$; $^{**} p < 0.05$; $^{***} p < 0.01$.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
+\end{landscape}
+
+The results of the analysis are presented in Table \ref{tab:tva}.
+The first column lists which dependent variable (measured in logs) was used in the row.
+The following columns contain point estimates for $\tau$ and $\delta_s$ in different specifications and can be interpreted as decadel growth rates in outcomes.
+The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for Equation \ref{eq:tva}.
+The two columns are very close in magnitude to each other.
+They find a decline in agricultural employment of about $5.7\%$ per decade, an increase in manufacturing employment of about $7\%$ per decade, and an increase in median family income of about $2.6\%$ per decade.
+
+Turning to the last four columns that estimate Equation \ref{eq:tva_spillover}, the columns contain point estimates for $\tau$ and $\delta_d$.
+For agricultural employment, our point estimates show there was a decline in agriculture employment in control units near to the authority.
+This is likely due to the fact that electrification of the region provided benefits beyond the border of the authority.\footnote{As noted in footnote 9 of \citet{Kline_Moretti_2014}, the spillover could theoretically be of either sign.
+It could be positive if farmers chose to locate in the authority to receive the benefits instead of just over the border.} Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
+The new point estimate indicates a decline of agricultural employment of about $9.6\%$ per decade compared to $5.7\%$.
+
+Similarly, manufacturing employment grew in nearby counties likely due to agglomeration economies and the improved regional transportation system.
+However, the size of the spillovers are smaller than in the agricultural employment regression, so the bias is smaller in this instance.
+The new point estimate is an increase of manufacturing employment of $8.54\%$ per decade compared to an original estimate of $7\%$.
+Median family income similarly increased in nearby counties and therefore the estimate was negatively biased.
+The point estimate is an increase of family income of $3.5\%$ per decade compared to $2.58\%$.
+These results show that including spillovers in the estimation of direct treatment effects is important and can lead to \emph{significant} differences in treatment effect estimates.
+
+% ------------------------------------------------------------------------------
+\newpage \printbibliography%
 % ------------------------------------------------------------------------------
@@
 \renewcommand{\thetable}{\Alph{section}.\arabic{table}}
+\renewcommand{\thefigure}{\Alph{section}.\arabic{figure}}
 % ------------------------------------------------------------------------------

### 2020-11-28 latex/slides/Spillover_slides.tex
Initial Draft of TVA Replication

@@
-\documentclass[aspectratio=43]{beamer}
-% Metropolis Theme ---------------------------------
+\documentclass[aspectratio=169]{beamer}
+% Metropolis Theme ------------------------------------------------------------------------------
 \usetheme{metropolis} % Use metropolis theme
 
-% Title --------------------------------------------
+% Title ------------------------------------------------------------------------------
 \title{Differnces-in-Differences with Spatial Spillover}
@@
 
-% ---------------------------------------------------
+\usepackage{adjustbox}
+\usepackage{tabularx}
+\usepackage{booktabs}
+\usepackage{threeparttable}
+
+% ------------------------------------------------------------------------------
 \begin{document}
+
+% ------------------------------------------------------------------------------
 \maketitle
+% ------------------------------------------------------------------------------
 
@@
 \imageframe{../../figures/figure-map_te_spill_all.png}
+
+% ------------------------------------------------------------------------------
+\section{Theory}
+% ------------------------------------------------------------------------------
 
@@
 
+% ------------------------------------------------------------------------------
+\section{Simulations}
+% ------------------------------------------------------------------------------
+
 \begin{frame}{Monte Carlo Simulations}
@@
 
-\begin{frame}{Next Steps}
-    \begin{itemize}
-        \item Monte Carlo: estimating spillovers and the problem of misspecification
+% ------------------------------------------------------------------------------
+\section{Application: Tennessee Valley Authority}
+% ------------------------------------------------------------------------------
 
-        \item Application: replicate paper(s) with a consideration of spillovers (any ideas?)
-    \end{itemize}
+\begin{frame}{Tennessee Valley Authority}
+
+\end{frame}
+
+\begin{frame}
+\begin{table}[ht]
+    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
+    \label{tab:tva}
+    \renewcommand{\arraystretch}{1}
+
+    \begin{adjustbox}{width = 1\textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} lc@{\extracolsep{20pt}}c@{\extracolsep{4pt}}ccc @{}}
+                % Head
+                \toprule
+
+                & \multicolumn{1}{c}{\textbf{Kline \& Moretti (2011)}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
+                \cmidrule{2-2} \cmidrule{3-6} 
+                & & & TVA between & TVA between & TVA between \\ 
+                \textit{Dependent Var.} & TVA & TVA & 0-100 mi. & 100-250 mi. & 250-500 mi. \\
+
+                % Body
+                \midrule
+
+                \input{../../tables/tva_replication_slides.tex}
+
+                \bottomrule
+            \end{tabular}
+
+            % Notes 
+            \begin{tablenotes}\footnotesize
+
+                \item $^{*} p< 0.1$; $^{**} p < 0.05$; $^{***} p < 0.01$.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
 \end{frame}

### 2020-11-28 tva-analysis-helpers.R

@@ -1,0 +1,93 @@
+
+# Winsorize helper function ----------------------------------------------------
+
+# https://gist.github.com/maifeng/3e5a1f0dd65bf0fd9c2b8f4ac8f5fab3
+winsorize_x = function(x, cut = 0.01){
+	cut_point_top <- quantile(x, 1 - cut, na.rm = T)
+	cut_point_bottom <- quantile(x, cut, na.rm = T)
+	i = which(x >= cut_point_top) 
+	x[i] = cut_point_top
+	j = which(x <= cut_point_bottom) 
+	x[j] = cut_point_bottom
+	return(x)
+}
+
+
+# Format Regression tex cell ---------------------------------------------------
+# Regression Star helper function
+reg_format <- function(pt, se) {
+	pt_str <- paste0("$", sprintf("%0.4f", pt))
+	
+	t_stat <- abs(pt/se)
+	
+	if(t_stat > 2.576) {
+		pt_str <- paste0(pt_str, "^{***}$")
+	}else if(t_stat > 1.960) {
+		pt_str <- paste0(pt_str, "^{**}$")
+	}else if(t_stat > 1.645) {
+		pt_str <- paste0(pt_str, "^{*}$")
+	}else {
+		pt_str <- paste0(pt_str, "$")
+	}
+	
+	return(pt_str)
+}
+
+
+
+# Oaxaca-Blinder Regression ----------------------------------------------------
+
+#' @description This function returns the Oaxaca-Blinder Estimand for the Average Treatment Effect on the Treated, following Patrick Kline - Oaxaca-Blinder as a Reweighting Estimator (2011)
+#'
+#' @param data dataframe to estimate with
+#' @param formula Formula for linear regression specification. Either formula or string object. Do not include the treatment variable in this
+#' @param treat string for treatment variable, must be 1 = treat, 0 = control
+#' @param cluster optional - string for cluster variable. Variable "indicating which observations belong to the same cluster". Passed along to `clubSandwich::vcovCR()`
+oaxaca_estimate <- function(data, formula, treat, cluster = NA) {
+	
+	## Regression using Control units ------------------------------------------
+	
+	# Prepare formula
+	if(is.character(formula)) formula <- as.formula(formula)
+	Y_var <- all.vars(formula[[2]])
[…]

### 2020-11-28 tva-analysis-replicate.R

@@ -1,0 +1,269 @@
+## -----------------------------------------------------------------------------
+## tva-analysis-replicate.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## Replicate Table 3 of Klein and Moretti (2014) 
+## -----------------------------------------------------------------------------
+
+library(tidyverse)
+library(haven)
+library(sf)
+library(Rcpp)
+library(RcppArmadillo)
+
+
+setwd("~/Documents/Projects/Spatial Spillover/")
+
+# Load theme_kyle()
+source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
+
+# Helper functions
+source("tva-analysis-helpers.R")
+source("helper-conley.R")
+
+# Export
+export <- FALSE
+keep_slides <- TRUE
+
+## Load Data -------------------------------------------------------------------
+
+df <- read_dta("data/tva/build.dta") %>% 
+	mutate(
+		fips = sprintf("%05d", fipstat * 1000 + fipcnty)
+	)
+ 
+counties <- sf::read_sf("data/counties.geojson")
+
+# Create TVA shape
+tva_fips <- scan("data/tva/tvacounties.txt", character())
+
+tva <- counties %>% 
+	filter(fips %in% tva_fips) %>% 
+	summarize()
+	
+dist_mat <- st_distance(counties %>% st_point_on_surface(), tva) 
+counties$dist_to_tva <- as.vector(units::drop_units(units::set_units(dist_mat, "mi")))
+
+
+# sanity check
+ggplot() +
+	geom_sf(data = counties, aes(fill = dist_to_tva)) + 
+	geom_sf(data = tva, color = "red", fill = NA) + 
+	coord_sf(datum = NULL) + 
+	scale_fill_distiller()
+
+
+# lat-long of county centroids
+temp <- counties %>% st_transform(4326) %>% st_point_on_surface() %>% st_coordinates()
+counties$long <- temp[,1]
+counties$lat  <- temp[,2]
+
+# Create spillover variable donuts
+df_reg <- df %>% 
[…]

### 2020-11-28 helper-conley.R
Initial attempt at Conley Standard Errors in C++

@@ -1,0 +1,107 @@
+## -----------------------------------------------------------------------------
+## helper-conley.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## This creates R functions for Conley (1999) Spatial-HAC standard errors. 
+## For panel or cross-sectional data. For cross-sectional just don't include time and id vectors 
+## 
+## -----------------------------------------------------------------------------
+
+library(Rcpp)
+library(RcppArmadillo)
+
+# setwd("")
+Rcpp::sourceCpp("helper-conley.cpp")
+
+
+#' Conley Spatial-HAC Variance-Covariance Matrix
+#' 
+#' Formula from: Conley (1999) and Robust Inference with Multi-way Clustering
+#' Original code from: https://github.com/darinchristensen/conley-se
+#' 
+#' @param X - nxk matrix of covariates (don't include lat and long if not in regression; if using fixed effects, they should not be included and X should be centered. See the `demeaned` option in `fixest::feols` if you want centered Xs)
+#' @param e - vector of residuals
+#' @param coords - nx2 matrix of lat and long (order doesn't matter)
+#' @param dist_cutoff - Cutoff distance in km for spatial correlation
+#' @param lag_cutoff - Cutoff time in units of your time variable for serial correlation
+#' @param cores - multicore support with parallel::mclapply
+#' @param verbose - if TRUE, prints out a lot of details
+#' @param id - nx1 vector of id variable
+#' @param time - nx1 vector of time variable (can be in any units)
+#'
+#' @note could be speed up if you put the lapply within C++ code. I calculate the N^2 distances for each time period
+conley_ses <- function(X, e, coords, dist_cutoff, lag_cutoff, cores = 1, verbose = FALSE, id = NULL, time = NULL) {
+	
+	# Load multicore
+	if(cores > 1) library(parallel)
+	
+	n <- nrow(X)
+	k <- ncol(X)
+	
+	panel <- !(is.null(id) | is.null(time))
+	if(!panel) print("No Panel dimension provided. Using just Spatial adjustment")
+	
+	# Spatial Correlation ------------------------------------------------------
+	
+	if(panel) {
[…]

### 2020-11-28 helper-conley.cpp

@@ -1,0 +1,148 @@
+// https://github.com/darinchristensen/conley-se
+
+#include <iostream>
+#include <math.h>
+#include <RcppArmadillo.h>
+// [[Rcpp::depends(RcppArmadillo)]]
+
+// Enable C++11 via this plugin (Rcpp 0.10.3 or later)
+// [[Rcpp::plugins(cpp11)]]
+
+using namespace Rcpp;
+using namespace arma;
+
+
+// Helper functions ------------------------------------------------------------
+
+// Degrees to Radians ----------------------------------------------------------
+double to_radians_cpp(double degrees){
+	return(degrees * 3.141593 / 180);
+}
+
+// Haversine Distance ----------------------------------------------------------
+double haversine_cpp(double lat1, double long1,
+                     double lat2, double long2,
+                     std::string unit="km"){
+	int radius = 6378;
+	double delta_phi = to_radians_cpp(lat2 - lat1);
+	double delta_lambda = to_radians_cpp(long2 - long1);
+	double phi1 = to_radians_cpp(lat1);
+	double phi2 = to_radians_cpp(lat2);
+	double term1 = pow(sin(delta_phi / 2), 2);
+	double term2 = cos(phi1) * cos(phi2) * pow(sin(delta_lambda/2), 2);
+	double the_terms = term1 + term2;
+	double delta_sigma = 2 * atan2(sqrt(the_terms), sqrt(1-the_terms));
+	double distance = radius * delta_sigma;
+	
+	/* if it is anything *but* km it is miles */
+	if(unit != "km"){
+		return(distance*0.621371);
+	}
+	
+	return(distance);
+}
+
+// Distance Formula used by Solomon Hsiang -------------------------------------
+double sh_cpp(double lat1, double long1,
+              double lat2, double long2) {
+	double distance = pow(pow(111 * (lat1 - lat2), 2) + pow(cos(lat1 * 3.1415927 / 180) * 111 * (long1 - long2), 2), .5);
+	return(distance);
+}
+
+
+
+// Cross-sectional spatial clustering ------------------------------------------
+
+//' Cross-sectional XeeX matrix 
+//' Lg because it doesn't store distance matrices
+//' 
+//' @param M - nx2 matrix of lat-long points 
[…]

### 2020-11-28 latex/paper/paper.tex
Edits to paper draft

@@
 % ------------------------------------------------------------------------------
-\subsection{Improving Estimation}
+\subsection{Improving Estimation by Parameterizing Spillovers}
 % ------------------------------------------------------------------------------
@@
 
-There are a few practical considerations researchers should make when parametrizing the spillovers.
+There are a few practical considerations researchers should make when parametrizing the spillovers. % @TODO: Expand upon considerations in the introduction
 
@@
 % ------------------------------------------------------------------------------
-\subsection{Simulation 1: Spillover on Controls Only}
+\subsection{Spillover on Controls Only}
 % ------------------------------------------------------------------------------
@@
 I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers.
-Even though, I remove contiguous controls which is not hte correct measure of $h_i(\vec{D})$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
+Even though, I remove contiguous controls which is not the correct measure of $h_i(\vec{D})$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
 As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.
@@
 % -----------------------------------------------------------------------------
-\subsection{Simulation 2}
+\subsection{Spillovers onto Control and Treated Units}
 % ------------------------------------------------------------------------------
@@
 
+In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
+Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
+One such field is depicted in Figure \ref{fig:kriging}.
+For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
+Then I assign treatment with a probability that differs based on Zone.
+The unconditional probability is equal to 5 percent in all simulations.
+To do this, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment:
+\begin{equation}
+    \label{eq:cond_prob}
+    P(D_i \ \vert \ \text{Zone}_i) = (.1 + \text{Zone Plus} * \text{Zone}_i) \times \frac{.05}{.1 * .9 + (.1 + \text{Zone Plus}) * .1}
+\end{equation}
+The second term normalizes probabilities so the unconditional probability stays at five percent.
+In our simulations, Zone Plus ranges from 0 which is the case where p = five percent for all counties to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.0166 + 0.35 * \text{Zone}_i$
+
 The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
@@
 % ------------------------------------------------------------------------------
+\subsection{Misspecification of Spillovers}
+% ------------------------------------------------------------------------------
+
+% @ TODO
+
+% ------------------------------------------------------------------------------
 \section{Application in Urban Economics}
@@
 
-I will focus on three outcome variables in the analysis.
+\citet{Kline_Moretti_2014} focus on a set of outcome variables, but I will focus on three in the analysis.
 The first two are (the log of) agricultural and manufacturing employment and the last is (the log of) median household income.
@@
 First, the large-scale investment in dams and electricity transmission lines brought cheap power to the region.
-It became cheaper for nearby locations to get connected to low-cost power and therefore likely lead to transition to manufacturing and away from farming in nearby counties.
+It became cheaper for nearby locations to get connected to low-cost power and therefore this likely caused a transition to manufacturing and away from farming in nearby counties.
 Second, \citet{Duranton_Puga_2003} highlight the agglomeration of input sourcing.
@@
 \end{equation}
-where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a series of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[
+where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a set of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[
     y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
@@
 Hence, their method magnifies the bias compared to a standard difference-in-differences estimator.
-However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results.
+However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform.
 
@@
 To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority.
+I do this for two reasons.
 Specifically, I use the following intervals $\text{Dist} = \{(0, 100], (100, 250], (250, 500]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
-The extended specification is given as follows:
+As discussed above, I suspect the spillover to decrease as counties move further away, hence I allow the effect to be seperately identified in bins.
+However, I
+
+The specification with spillovers is given as follows:  
 \begin{equation}\label{eq:tva_spillover}

### 2020-11-28 figure-gen_map_examples_with_bias.R

@@ -23,7 +23,7 @@ library("patchwork")
 source("helper-sim_function.R")
 
 # Load theme_kyle()
-source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/ef6834e879f98be630bec9fd48c7e0bd945689be/theme_kyle.R")
+source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
 
 # Is for slides or paper?
 slides <- FALSE

### 2020-11-28 tva-analysis-replicate.R
Updated spillovers for TVA with appropriate distances

@@ -32,7 +32,8 @@ df <- read_dta("data/tva/build.dta") %>%
 		fips = sprintf("%05d", fipstat * 1000 + fipcnty)
 	)
  
-counties <- sf::read_sf("data/counties.geojson")
+counties <- sf::read_sf("data/counties.geojson") %>% 
+	mutate(state = as.numeric(fips) %% 1000)
 
 # Create TVA shape
 tva_fips <- scan("data/tva/tvacounties.txt", character())
@@ -44,13 +45,21 @@ tva <- counties %>%
 dist_mat <- st_distance(counties %>% st_point_on_surface(), tva) 
 counties$dist_to_tva <- as.vector(units::drop_units(units::set_units(dist_mat, "mi")))
 
-
+counties <- counties %>% mutate(
+		spill = case_when(
+			0 < dist_to_tva & dist_to_tva <= 50 ~ "0 to 50 miles",
+			50 < dist_to_tva & dist_to_tva <= 100 ~ "50 to 100 miles",
+			100 < dist_to_tva & dist_to_tva <= 150 ~ "100 to 150 miles"
+		)
+	)
 # sanity check
 ggplot() +
-	geom_sf(data = counties, aes(fill = dist_to_tva)) + 
-	geom_sf(data = tva, color = "red", fill = NA) + 
-	coord_sf(datum = NULL) + 
-	scale_fill_distiller()
+	geom_sf(data = counties, aes(fill = spill), color = "grey40") + 
+	# Outline of TVA
+	geom_sf(data = tva, color = "Black", fill = NA) + 
+	coord_sf(datum = NA) + 
+	theme_kyle() +
+	scale_fill_manual(values = c("red", "yellow", "orange"), na.translate = FALSE)
 
 
 # lat-long of county centroids
@@ -63,10 +72,10 @@ df_reg <- df %>%
 	left_join(., counties %>% st_drop_geometry(), by = "fips") %>% 
 	mutate(
 		tva_0_100 = !tva & dist_to_tva >= 0 & dist_to_tva < 100,
-		tva_100_250 = !tva & dist_to_tva >= 100 & dist_to_tva < 250,
-		tva_250_500 = !tva & dist_to_tva >= 250 & dist_to_tva < 500,
+		tva_0_50 = !tva & dist_to_tva >= 0 & dist_to_tva < 50,
[…]

### 2020-11-28 latex/paper/paper.tex
Updated paper with improved spillover TVA analysis

@@
 
-There are two primary forces causing spillover in this context.
-First, the large-scale investment in dams and electricity transmission lines brought cheap power to the region.
-It became cheaper for nearby locations to get connected to low-cost power and therefore this likely caused a transition to manufacturing and away from farming in nearby counties.
-Second, \citet{Duranton_Puga_2003} highlight the agglomeration of input sourcing.
-When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties.
-These both suggest that spillovers will occur close to the spillover region and that the exposure will decay over distance.
+In \citet{Kline_Moretti_2014}, they discuss the nature of spillovers that can occur.
+For agriculture employment, \citet{Kline_Moretti_2014} claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
+Hence they predict a negative spillover.
+For manufacturing, the sign is ambiguous.
+There could be positive spillovers if electrification brought cheap power to the neighboring areas.
+Also, agglomeration effects increase manufacturing employment in nearby counties.\footnote{\citet{Duranton_Puga_2003} give theoretical motivations for different sources of agglomeration.
+In this context, agglomerations due to `sourcing' is most likely.
+When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate nearby.
 
@@
 However, their point estimates compare, in part, changes in outcomes between TVA counties with neighboring counties that likely were impacted by the large-scale electrification program.
-As described above and estimated below, the program likely induced positive manufacturing and negative agricultural employment effects in nearby counties.
-Therefore, the authors likely underestimate the impact on employment by comparing counties inside the Authroity to counties on the other side of the border.
+As described above and estimated below, the program likely induced manufacturing and agricultural employment effects in nearby counties.
+By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
 The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this and appear to do so in the empirical analysis below.
@@
 I do this for two reasons.
-Specifically, I use the following intervals $\text{Dist} = \{(0, 100], (100, 250], (250, 500]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
-As discussed above, I suspect the spillover to decrease as counties move further away, hence I allow the effect to be seperately identified in bins.
-However, I
+Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
+As discussed above, I suspect the spillover effects to change with distance to the authority, hence I allow the effect to be seperately identified in bins.
+I keep the number of bins small to improve precision of spillover estimates.
 
@@
 \end{equation} 
-The coefficients $\delta_d$ measure the spillover effect at different distances from the Authority.
+The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority.
+If specification \ref{eq:tva_spillover} is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for the `local' effect.
+As shown above, minor misspecification will remove some but not all of the bias from standard difference-in-differences estimates.
 
-\begin{landscape}
-\thispagestyle{lscaped}
-
-\begin{table}[ht]
+% \begin{landscape}
+% \thispagestyle{lscaped}
+\begin{table}[!tb]
     \caption{Effects of Tennessee Valley Authority on Decadel Growth}
@@
 
-    \begin{adjustbox}{width = 1.3\textwidth, center}
+    \begin{adjustbox}{width = 1.2\textwidth, center}
         \begin{threeparttable}
@@
                 & & & & TVA between & TVA between & TVA between \\ 
-                & TVA & TVA & TVA & 0-100 mi. & 100-250 mi. & 250-500 mi. \\ 
+                & TVA & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\ 
                 \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\
@@
 
-                \input{../../tables/tva_replication.tex}
+                \input{../../tables/tva_replication_slides.tex}
 
@@
 \end{table}
-
-\end{landscape}
+%\end{landscape}
 
@@
 
-Turning to the last four columns that estimate Equation \ref{eq:tva_spillover}, the columns contain point estimates for $\tau$ and $\delta_d$.
-For agricultural employment, our point estimates show there was a decline in agriculture employment in control units near to the authority.
-This is likely due to the fact that electrification of the region provided benefits beyond the border of the authority.\footnote{As noted in footnote 9 of \citet{Kline_Moretti_2014}, the spillover could theoretically be of either sign.
-It could be positive if farmers chose to locate in the authority to receive the benefits instead of just over the border.} Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
-The new point estimate indicates a decline of agricultural employment of about $9.6\%$ per decade compared to $5.7\%$.
+Turning to the last four columns that estimate Equation \ref{eq:tva_spillover}, column (3) contains a point estimate for $\tau$ and and columns (4)-(6) contain point estimates of the spillover effects $\delta_d$.
+For agricultural employment, our point estimates show there was a decline in agriculture employment in control units near the Authority.
+This is likely due to the fact that higher paying manufacturing jobs within the Authority drew migrants from nearby counties.
+Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
+The new point estimate indicates a decline of agricultural employment of about $7.6\%$ per decade compared to $5.8\%$.
 
-Similarly, manufacturing employment grew in nearby counties likely due to agglomeration economies and the improved regional transportation system.
-However, the size of the spillovers are smaller than in the agricultural employment regression, so the bias is smaller in this instance.
-The new point estimate is an increase of manufacturing employment of $8.54\%$ per decade compared to an original estimate of $7\%$.
-Median family income similarly increased in nearby counties and therefore the estimate was negatively biased.
-The point estimate is an increase of family income of $3.5\%$ per decade compared to $2.58\%$.
-These results show that including spillovers in the estimation of direct treatment effects is important and can lead to \emph{significant} differences in treatment effect estimates.
+For manufacturing, our point estimates for spillovers in column (4)-(6) are statistically significant, but suggest that neighboring counties had a potentially negative spillover effect.
+Since there is little spillovers present, the new point estimate in column (3) of $-5.18\%$ is close to the original estimate.
+Similarly, there is not a significant spillover on median family income.
+The point estimate therefore stays the same.
+These results show that including spillovers in the estimation of direct treatment effects is potentially important and in the case of agricultural employment can lead to \emph{significant} differences in treatment effect estimates.
 

### 2020-11-28 latex/paper/Spillover.tex
Fixed rebase problems (removed data in rebase)

--- 2020-11-28 latex/paper/paper.tex
@@
 
-\title{\color{dark-maroon} Differences-in-Differences with Spatial Spillover}
+\title{\color{navyblue} Differences-in-Differences with Spatial Spillover}
 % \subtitle{Subtitle}
@@
         Empirical work often uses treatment variables defined by geographic boundaries.
-When researchers ignore the common problem that the effects of treatment cross over borders, differences-in-differences produces biased estimates for the average treatment effect.
-In this paper, I identify two sources of bias.
+When researchers ignore the common problem that the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect.
+In this paper, I decompose this bias in two parts.
 First, the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment.
@@
 I use Monte Carlo simulations to demonstrate when the biases are particularly large.
-Further, I show that a common solution used in the literature of removing `contaminated' control units only prevents one source of bias.
+Further, I show that a common solution used in the literature of removing `contaminated' control units only prevents the first source of bias.
 Lastly, I propose improved estimation strategies that can remove both sources of bias.
+I highlight the importance of considering spillovers by revisiting analysis of the Tennessee Valley Authority.
     \end{abstract}
 \end{titlepage}
-% --------------------------------------------------
-
-\newpage
+% ------------------------------------------------------------------------------
 
@@
 Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states.
-The effect of these treatments do not typically stay within these boundaries whether it be from people crossing borders or from general equilibrium mechanisms affecting neighboring areas.
-In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that treatment effects do not depend on the treatment status of any other unit \citep{Rubin_1980}.
+The effect of these treatments do not typically stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects affecting neighboring areas.
+In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that a unit's potential outcome does not depend on the treatment status of any other unit \citep{Rubin_1980}.
 This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
-geographic distance, node distance in graph theory, or social relationships in schools or cities.}
+geographic distance, node distance in a graph, or social relationships in schools or cities.}
 
-Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
-In a survey of eight top Economics and Finance Journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers to prevent bias in the estimation of treatment effects.
+This paper first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}.
+In the presence of spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard difference-in-differences methodologies.
 
-In the presence of these spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard differences-in-differences methodologies.
 First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
-When estimating by differences-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes.
+When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes.
 In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
 For example, if a factory opening in a given county benefits both that county and neighboring counties, the treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
+Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had preferences over both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units.
+Difference-in-differences estimation would result in double undercounting.}
 
 Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-Therefore the spillover is added to the treated units' change in outcomes.
+The spillover is added to the treated units' change in outcomes.
 Therefore the bias of treatment effect is the same sign as the sign of the spillover.
-For example a factory opening in two neighboring counties might cause the benefit of each individual factory to decrease.
-The estimated treatment effect will be negatively biased because there is a negative spillover onto also treated units.
+For example a factory opening in two neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces.
+The estimated treatment effect will be positively biased because there is a positive spillover onto also treated units.
 
@@
 
-@TODO: Paragraph on practical guidance on including spillover measures
+Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers.
+Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers on to control units.
+Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.
+
+Removing both kinds of bias requires a researcher to take a stance and parameterize a functional form for the spillover function.
+The particular functional form depends on the context of the application however there are a few practical considerations.
+First, the researcher should argue whether spillovers on control units and on treated units exist.
+Second, they should argue what the maximum distance these spillovers can occur.
+Last, they should consider if spillovers are additive in the number of nearby units that are treated.
 
@@
 There are two different models of SUTVA violations in the literature.
-Within-group spillovers are when units are in distinct groups and outcomes depend on the treatment status of your group only.
-For example, SUTVA is violated if a person's likelihood of getting sick depends on the vaccine rate of his community.
-In this case, the community is the group within which spillovers can occur.
-Between-group spillovers occur when groups are overlapping which allows for more general forms of spillover.
+Within-group spillovers are when units are in distinct groups and outcomes depend on the treatment status within your group only.
+For example, SUTVA is violated if a student's standardized test score depends on the proportion of students enrolled in a tutoring program at that school.
+In this case, each school constitutes a group and it is assumed treatment effect is not affected by other schools' tutoring enrollment.
+Estimation in this case is done in a `partial intereference' framework.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with control units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.
+
+The more general form is sometimes called between-group spillovers which occur when groups are overlapping.
 For example, a counties' economic outcomes depend on the economic outcomes of nearby counties (even across state borders).
-@TODO: Add citations for papers that find this.
-
-One set of literature discusses `partial intereference' where spillovers are assumed to only occur within a group and not across groups.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with control units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.
+Estimation in this framework is more difficult and requires the researcher to either identify control units that are free from spillovers or to parameterize how control units are affected by treatment.
 
 \citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector.
-He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$ (this is referred to as an exposure mapping).
-Adding an exposure mapping to the potential outcomes framework allows to explicitly model SUTVA violations.
-Using this framework, he shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.
-My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by differences-in-differences.
+He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$.
+The function $h_i(\vec{D})$ is referred to as an exposure mapping and adding an exposure mapping to the potential outcomes framework allows to explicitly model SUTVA violations.
+Using this framework, \citet{Vazquez-Bare_2019} shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.
+My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by difference-in-differences.
 
 \citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''.
-Then, the authors describe how the ATE estimated by diff-in-diff averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h_i(\vec{D})$.
-This paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
+Then, the authors describe how the ATE estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h_i(\vec{D})$.
+My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
 
-The paper closest to mine is \citet{Delgado_Florax_2015} where they consider spillover only on to control units and identify a bias that can come from estimating a diff-in-diff model without explicitly controlling for spillovers.
+\citet{Delgado_Florax_2015} consider spillover only on to control units and identify a bias that can come from estimating a difference-in-differences model without explicitly controlling for spillovers.
 Using Monte-Carlo simulations, they find that there is an omitted variable bias problem by not including a measure of spillovers.
-This paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.
-
-Similarly, \citet{Clarke_2017} finds an explicit form for bias when estimating a diff-in-diff model with spillover onto control units.
-However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units.
-Lastly, \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} find results for a specific potential outcome function where $h_i(\vec{D})$ is the proportion of treated contiguous counties.
-They allow this spillover to enter the potential outcome additively and the coefficient is allowed to differ by own treatment status.
-
-In my framework, if I assume the particular functional forms for potential outcomes of \citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}, I arrive at the same bias equation as theirs.
-
-%%%%
-The paper is structured as follows. ...
+My paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.
 
@@
 In my framework, if I assume the particular functional forms for potential outcomes of \citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}, I arrive at the same bias equation as theirs.
+
+Lastly, I contribute to a literature in urban economics on local place-based policies.
+Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' effects of the policy are offset in parts by indirect effects.
+I contribute to estimating aggregate effects of place-based policies by showing that typical estimation strategies can underestimate the local effect by ignoring spillovers.
+To do so, I revise the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
+The Tennessee Valley Authority was a large push to bring electrification to the Tennessee Valley with the goal of improving the manufacturing sector there.
+The scale of the program was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies.
+I show that estimation by difference-in-differences fails to account for these spillovers and underestimates the local effect.
 
@@
 
-To help better understand an exposure mapping, I give three examples of $h_i(\vec{D})$.
+To help better understand the exposure mapping function, I give three examples of $h_i(\vec{D})$ that are commonly used in the literature.
+First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$ (similarly a dummy for counties that share borders is commonly used).
 Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
-First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $x$-miles of unit $i$ (also commonly used is counties that share borders).
 In this case \[
-    h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < x ] 
+    h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
 \] 
@@
 where $k(i)$ is the index of unit $i$'s k-nearest neighbors.
-Last, is the spatial decay function which depends on  the decay parameter $\alpha$.
+This exposure mapping is no longer binary, so intensity of spillovers depend on the number of units treated.
+In the context of large store openings and agglomeration economies, this would imply that as the number of nearby counties receiving new factories increase, the effect on own-county outcomes increase as well \citep{Basker_2005}.
+
+Last, is the spatial decay function where exposure decreases with distance.
+This depends on the decay parameter $\alpha$ that is decided by the researcher.
 In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
 \[
-    h_i(\vec{D}) = \sum_{j \neq i} D_j \exp^{-\alpha d_i(j)}
+    h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
 \] 
-The exposure mapping is part of the parameterization of spillovers, but the functional form of the potential outcome still needs to be specified.
+This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units.
+This creates problems with inference because it implies potential correlation between all units' error terms.
+For this reason, this function often is summed over only the $k$-nearest neighbors.} In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
+This allows for the technology spillovers to decay over distance to an exponential degree.
+
+The last thing a researcher must do is specify the functional form of the potential outcomes.
+Typically, the spillover function enters into the regression linearly and ocasionally the coefficient is allowed to differ by treatment status.
 
@@
 
-With a new definition of potential outcomes, I now formalize what is meant by ``spatial spillovers'. I define `spillover onto control units' as: \[
+With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
     Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0).
 \] 
+The spillover measures the difference in non-treated potential outcomes between being exposed and not being exposed at level $h_i(\vec{D})$.
 Then, the average spillover onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
-    \tau_{\text{spill,control}} = \mathbb{E}_i \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
+    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
 \]
-To emphasize, the average spillover effect depends on the average of exposure mapping.
-For example, assuming the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$, then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h_i(\vec{D})$.
+
+To emphasize, the average spillover onto conrol units averages over each control unit's exposure mapping.
+For example, assume the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$ and that the coefficient $\beta_{\text{spill,control}}$ measures the effect of $h_i(\vec{D})$ on outcome $Y$ among control units.
+Then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h_i(\vec{D})$.
 The average spillover onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E}_{i} \left[ h_i(\vec{D})\right]$, i.e.
@@
 
-Similarly, we define the spillover onto also treated units as: \[ 
-    \tau_{\text{spill,treated}} = \mathbb{E}_i \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
+Similarly, we define the average spillover onto also treated units as: \[ 
+    \tau_{\text{spill,treated}} \equiv \mathbb{E} \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
 \]
 
-It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using differences-in-differences.
-I assume that the term `Average Treatment Effect' is trying to measure what I will call the `direct effect of treatment': \[
-    \tau_{\text{direct}} = \mathbb{E}_i \left[ Y_{i}(1, 0) - Y_{i}(0, 0) \ \vert \ D_i = 1 \right],
+It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences.
+I assume that what the `Average Treatment Effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
+    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{i}(1, 0) - Y_{i}(0, 0) \ \vert \ D_i = 1 \right],
 \] 
 which measures the effect of being treated in the absence of exposure to spillovers. This differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
-    \mathbb{E}_i \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(0, h_i(\vec{D})) \ \vert \ D_i = 1 \right],
+    \mathbb{E} \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(0, h_i(\vec{D})) \ \vert \ D_i = 1 \right],
 \] 
@@
 
-% --------------------------------------------------
-\subsection{Bias in Differences-in-Difference Estimation}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
+\subsection{Bias in Difference-in-Differences Estimation}
+% ------------------------------------------------------------------------------
 
-In this section, I identify the two sources of bias in differences-in-differences estimation.
-For exposition, I will refer to two periods, $t = 0$ and $t = 1$, but this can be replaced by averages across $Y$ in the pre-period and the post-period respectively.
-First, I present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.
+In this section, I identify the two sources of bias in difference-in-differences estimation.
+For exposition, I will refer to one pre- and post-period, $t = 0$ and $t = 1$, but this can be replaced by averages across $Y$ in the pre-period and the post-period respectively.
+To estimate the `direct effect of treatment', researchers estimate the canonical two-way fixed effects model,
+\begin{equation}\label{eq:twfe}    
+    y_{it} = \tau D_{it} + \mu_i + \mu_t + \epsilon_{it}.
+\end{equation}
+
+The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$.
+To show this, I first present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.
 
@@
 \end{assumption}
+This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status.
+This generalizes to the classic parallel counterfactual trends when SUTVA is satisfied because then every unit has zero exposure.
 
-This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status.
-This generalizes to the typical Parallel Counterfactual Trends because typically SUTVA assumes that every unit has zero exposure.
+When researchers run the canonical difference-in-differences regression, 
+the estimate $\hat{\tau}$ will be a biased estimate for $\tau_{\text{direct}}$.
+Given that Assumption \ref{parallel} holds, the estimate can be decomposed as the direct effect and the two sources of spillover bias.
+The proof is given in Appendix \ref{sec:proofs}.
 
-When researchers run the canonical differences-in-differences regression \[ 
-    y_{it}  = \alpha + \tau D_{it} + \epsilon_{it},
-\]
-$\hat{\tau}$ will be a biased estimate for $\tau_{\text{direct}}$.
-Given that Assumption \ref{parallel} holds, the estimate can be decomposed as the direct effect and the two sources of spillover bias.
-
-\begin{theorem}
-    \label{thm:bias}
-    If Assumption \ref{parallel} holds, 
+\begin{theorem}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
+    If Assumption \ref{parallel} holds, the expectation of the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} is
     \begin{align*}
@@
 First, the change in outcomes among treated units combines the direct effect and the spillover from nearby treated units.
-Therefore the first difference adds the average spillover onto the treated units.
+Therefore the first difference adds the average spillover onto the treated units, $\tau_{\text{spill,treated}}$.
 Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover onto control units.
-Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover onto the control.
+Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover onto the control, $\tau_{\text{spill,control}}$.
 
@@
 
-To exemplify the above bias, I will model a particular form of spillovers by parameterizing the exposure mapping and the potential outcomes equation.
-For the exposure mapping, I will assume that spillovers occur for any county that is within 40 miles of a treated county, i.e.
+As an example of Theorem \ref{thm:bias}, I will consider the example of the effect of new libraries on school outcomes.
+Following the motivation above, I assume that spillovers occur for any county that is within $\bar{d}$ miles of a treated county, i.e.
 \begin{align}
     \label{eq:example_exposure}
-    \text{Near}_{it} \equiv h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < 40 ].
+    h_i(\vec{D}) \equiv \text{Near}_{it} = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ].
 \end{align}
@@
 
-If a researcher estimates 
-\begin{align}
-    \label{eq:twfe}    
-    y_{it} = \alpha + \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it},    
-\end{align}
-then the bias will be $\tau_{\text{spill,treated}} - \tau_{\text{spill,control}}$ where the two bias terms are \[ 
+If a researcher estimates Equation \ref{eq:twfe}, then the bias will be $\tau_{\text{spill,treated}} - \tau_{\text{spill,control}}$ where the two bias terms are \[ 
     \tau_{\text{spill,control}} = \beta_{\text{spill,control}} \frac{\sum_{i: D_{it} = 0} \text{Near}_{it}}{N_C}
@@
 
-\begin{figure}[t]
+\begin{figure}[t!]
     \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
@@
 As the treatment probability increases, the number of control units removed increases as well.
-This naturally yields are more variable estimator as seen in the wider 95 percent empirical confidence intervals.
+This naturally yields a more variable estimator as seen in the wider 95 percent empirical confidence intervals.
 
@@
 
-\begin{figure}[t]
+\begin{figure}[htb!]
     \caption{Example of Kriging Field}
@@
 
-In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
-Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
-One such field is depicted in Figure \ref{fig:kriging}.
-For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
-Then I assign treatment with a probability that differs based on Zone.
-The unconditional probability is equal to 5 percent in all simulations.
-To do this, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment:
-\begin{equation}
-    \label{eq:cond_prob}
-    P(D_i \ \vert \ \text{Zone}_i) = (.1 + \text{Zone Plus} * \text{Zone}_i) \frac{.05}{.1 * .9 + (.1 + \text{Zone Plus}) * .1}
-\end{equation}
-The second term normalizes probabilities so the unconditional probability stays at 5 percent.
-In our simulations, Zone Plus ranges from 0 which is the case where p = 10 percent for all counties to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.166 + 0.35 * \text{Zone}_i$
-
-\begin{figure}[t]
+\begin{figure}[htb!]
     \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
@@
 
-% --------------------------------------------------
-\section{Proofs}
-% --------------------------------------------------
+% ------------------------------------------------------------------------------
+\section{Proofs}\label{sec:proofs}
+% ------------------------------------------------------------------------------
 
@@
 \begin{align*}
-    \mathbb{E}_i\left[ \hat{\tau} \right] &= \mathbb{E}_i\left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E}_i\left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right] \\
+    \mathbb{E}\left[ \hat{\tau} \right] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\
     &= 
-    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i\left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
+    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
     &= 
-    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i\left[ Y_{i1}(0, h_i(\vec{D})) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
+    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h_i(\vec{D})) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
     &= 
-    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\ 
-    &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\ 
+    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\ 
+    &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\ 
     &= 
-    \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1 \right] \\
-    &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\  
-    &= \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= \mathbb{E}_i\left[ Y_{i1}(1, h_i(\vec{D})) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
+    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1 \right] \\
+    &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\  
+    &= \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
+    &= \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
+    &= \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
     &= 
-    \mathbb{E}_i \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E}_i \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
-    &\quad - \mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
+    \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
+    &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
     &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}

### 2020-11-28 latex/paper/Spillover.tex
Added logistic regression for subsample

@@
 where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a set of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[
-    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
+    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, pre} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
 \] Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
@@
 The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted.
-Hence, their method magnifies the bias compared to a standard difference-in-differences estimator.
 However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform.
@@
 
-    \begin{adjustbox}{width = 1.2\textwidth, center}
+    \begin{adjustbox}{width = 1.15\textwidth, center}
         \begin{threeparttable}
@@
 
-The results of the analysis are presented in Table \ref{tab:tva}.
-The first column lists which dependent variable (measured in logs) was used in the row.
-The following columns contain point estimates for $\tau$ and $\delta_s$ in different specifications and can be interpreted as decadel growth rates in outcomes.
-The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for Equation \ref{eq:tva}.
-The two columns are very close in magnitude to each other.
-They find a decline in agricultural employment of about $5.7\%$ per decade, an increase in manufacturing employment of about $7\%$ per decade, and an increase in median family income of about $2.6\%$ per decade.
-
 Turning to the last four columns that estimate Equation \ref{eq:tva_spillover}, column (3) contains a point estimate for $\tau$ and and columns (4)-(6) contain point estimates of the spillover effects $\delta_d$.
 For agricultural employment, our point estimates show there was a decline in agriculture employment in control units near the Authority.
+For control units between 0 and 50 miles, column (4) indicates a decline in agricultural employment of $3.1\%$.
+Between 50 and 100 miles the point estimate is $-1.1\%$ and between 100 and 150 miles, the point estimate is $-2.5\%$.
 This is likely due to the fact that higher paying manufacturing jobs within the Authority drew migrants from nearby counties.
 Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
-The new point estimate indicates a decline of agricultural employment of about $7.6\%$ per decade compared to $5.8\%$.
+The new point estimate indicates a decline of agricultural employment of about $6.8\%$ per decade compared to $5.1\%$ in the standard difference-in-difference specification.
 
-For manufacturing, our point estimates for spillovers in column (4)-(6) are statistically significant, but suggest that neighboring counties had a potentially negative spillover effect.
-Since there is little spillovers present, the new point estimate in column (3) of $-5.18\%$ is close to the original estimate.
+For manufacturing, our point estimates for spillovers in column (4)-(6) are not statistically significant, but the signs on all three spillover estimates suggest that neighboring counties had a potentially negative spillover effect.
+Since there is little to no spillovers present, the new point estimate in column (3) of $4.6\%$ is not too far from the standard difference-in-differences estimate of $5.6\%$.
 Similarly, there is not a significant spillover on median family income.
-The point estimate therefore stays the same.
+The point estimate therefore stays the same between the standard and spillover-adjusted difference-in-differences estimate of about $1.9\%$.
+
 These results show that including spillovers in the estimation of direct treatment effects is potentially important and in the case of agricultural employment can lead to \emph{significant} differences in treatment effect estimates.
+Analysis of place-based policies that do not account for the fact that treatment effects can spillover beyond the borders of treated areas can potentially be biased.
+The above results suggest this can over or underestimate the size of the effects depending on the sign of the spillovers.
 

### 2020-11-28 tva-analysis-replicate.R

@@ -33,7 +33,8 @@ df <- read_dta("data/tva/build.dta") %>%
 	)
  
 counties <- sf::read_sf("data/counties.geojson") %>% 
-	mutate(state = as.numeric(fips) %% 1000)
+	mutate(state = as.numeric(fips) %% 1000) %>% 
+	rmapshaper::ms_simplify(keep = 0.05)
 
 # Create TVA shape
 tva_fips <- scan("data/tva/tvacounties.txt", character())
@@ -45,22 +46,11 @@ tva <- counties %>%
 dist_mat <- st_distance(counties %>% st_point_on_surface(), tva) 
 counties$dist_to_tva <- as.vector(units::drop_units(units::set_units(dist_mat, "mi")))
 
-counties <- counties %>% mutate(
-		spill = case_when(
-			0 < dist_to_tva & dist_to_tva <= 50 ~ "0 to 50 miles",
-			50 < dist_to_tva & dist_to_tva <= 100 ~ "50 to 100 miles",
-			100 < dist_to_tva & dist_to_tva <= 150 ~ "100 to 150 miles"
-		)
-	)
-# sanity check
-ggplot() +
-	geom_sf(data = counties, aes(fill = spill), color = "grey40") + 
-	# Outline of TVA
-	geom_sf(data = tva, color = "Black", fill = NA) + 
-	coord_sf(datum = NA) + 
-	theme_kyle() +
-	scale_fill_manual(values = c("red", "yellow", "orange"), na.translate = FALSE)
 
+controls <- c("lnelevmax", "lnelevrang", "lnarea", "lnpop20", "lnpop20sq", "lnpop30", "lnpop30sq", "popdifsq", "agrshr20", "agrshr20sq", "agrshr30", "agrshr30sq", "manufshr20", "manufshr30", "lnwage20", "lnwage30", "lntwage30", "lnemp20", "lnemp30", "urbshare20", "urbshare30", "lnfaval20", "lnfaval30", "lnmedhsval30", "lnmedrnt30", "white20", "white20sq", "white30", "white30sq", "pctil20", "pctil30", "urate30", "fbshr20", "fbshr30", "PRADIO30", "nowage20dum", "nowage30dum", "notwage30dum")
+
+
+## Create Spillover Variables --------------------------------------------------
 
 # lat-long of county centroids
 temp <- counties %>% st_transform(4326) %>% st_point_on_surface() %>% st_coordinates()
@@ -79,7 +69,15 @@ df_reg <- df %>%
 	)
 
 
[…]

### 2020-11-28 latex/paper/Spillover.tex
Add figure of effective sample and spill vars

@@
 
-This paper first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}.
+This paper identifies problems in estimation of treatment effets in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers.
+
+To do this, I first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}.
 In the presence of spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard difference-in-differences methodologies.
@@
 
+In order to more likely satisfy the paralell trends assumption, the run a logistic regression to predict being in the TVA based on their set of control variables $X_{c, pre}$ and keep only observations in the top 75\% of predicted probability.
+The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
+
+\begin{figure}[tbh!]
+    \caption{TVA Effective Sample and Spillover Variables}
+    \label{fig:tva_sample}
+
+    {\centering
+        \resizebox{\textwidth}{!}{
+            \includegraphics{../../figures/figure-tva-sample.pdf}
+        } 
+    }
+
+    {\footnotesize \textit{Notes:} The above figure plots all the counties used in the estimation.
+Counties that fall within the distance intervals $\{(0, 50], (50, 100], (100, 150]\}$ measured in miles are colored by their respective bin.}
+\end{figure}
+
 I extend their analysis to include spatial spillovers in the difference-in-differences specification.
@@
 Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
-As discussed above, I suspect the spillover effects to change with distance to the authority, hence I allow the effect to be seperately identified in bins.
+Figure \ref{fig:tva_sample} displays the three spillover variables by filling in each distance bin in a different color.
+As discussed above, I suspect the spillover effects to change with distance to the Authority, hence I allow the effect to be seperately identified in bins.
 I keep the number of bins small to improve precision of spillover estimates.
@@
 The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority.
-If specification \ref{eq:tva_spillover} is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for the `local' effect.
+If specification \ref{eq:tva_spillover} is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect.
 As shown above, minor misspecification will remove some but not all of the bias from standard difference-in-differences estimates.
+
+The results of the analysis are presented in Table \ref{tab:tva}.
+The first column lists which dependent variable (measured in logs) was used in the row.
+The following columns contain point estimates for $\tau$ and $\delta_s$ in different specifications and can be interpreted as decadel growth rates in outcomes.
+The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for Equation \ref{eq:tva}.
+The two columns are very close in magnitude to each other.
+They find a decline in agricultural employment of about $5.6\%$ per decade, an increase in manufacturing employment of about $6.1\%$ per decade, and an increase in median family income of about $2.2\%$ per decade.
 

### 2020-11-28 tva-analysis-replicate.R

@@ -79,7 +79,57 @@ df_reg <- df_reg %>%
 		keep = phat > quantile(phat, probs = c(0.25), na.rm = TRUE)
 	)
 
-# Regression -------------------------------------------------------------------
+
+## Figure of counties and spillover variable -----------------------------------
+
+fips_in_sample <- df_reg %>%
+	drop_na(!!c(controls, y)) %>% 
+	filter(keep == TRUE) %>% 
+	pull(fips)
+
+rings <- counties %>% 
+	filter(fips %in% fips_in_sample) %>%
+	mutate(
+		spill = case_when(
+			0 < dist_to_tva & dist_to_tva <= 50 ~ "0 to 50 miles",
+			50 < dist_to_tva & dist_to_tva <= 100 ~ "50 to 100 miles",
+			100 < dist_to_tva & dist_to_tva <= 150 ~ "100 to 150 miles"
+		)
+	) %>% 
+	filter(!is.na(spill)) %>% 
+	group_by(spill) %>% 
+	summarize()
+
+rings$spill <- factor(rings$spill, levels = c("0 to 50 miles", "50 to 100 miles", "100 to 150 miles"))
+
+
+nord_palette <- c("#295080", "#BF616A", "#A3BE8C", "#D08770")
+grey_palette <- c("grey30", "grey50", "grey70")
+
+(spillover_map <- ggplot() +
+		geom_sf(
+			data = counties %>% filter(fips %in% fips_in_sample), 
+			fill = NA, color = "grey40", size = 0.5
+		) + 
+		geom_sf(data = rings, aes(fill = spill), color = NA) + 
+		# Outline of TVA
+		geom_sf(data = tva, color = "Black", fill = NA, size = 1.1) + 
+		coord_sf(datum = NA) + 
+		theme_kyle(base_size = 14) +
+		theme(
+			legend.position = c(0.1, 0.15), 
+			legend.background = element_rect(colour = "grey40")
+		) +
+		labs(fill = "Spillover Bin") +
+		scale_fill_manual(values = nord_palette, na.translate = FALSE)) 
+		# scale_fill_manual(values = grey_palette, na.translate = FALSE)) 
+
+
+if(export) ggsave("figures/figure-tva-sample.pdf", spillover_map, 
+	   dpi= 300, width= 2400/300, height= 1350/300, bg= "white")
+
+
+## Regression -------------------------------------------------------------------
 
[…]

### 2020-11-28 latex/paper/Spillover.tex
Heuristics for signing bias and small edits

@@
 
+Readers that are judging estimates in the presence of spillovers can use the following heuristics to size the bias.
+If they suspect spillovers onto control units, the bias is the opposite sign of the spillover.
+If they suspect spillovers onto treated units, the bias is in the same sign of the spillover.
+The overall bias is the sum of the two.
+
 % ------------------------------------------------------------------------------
@@
 
-\begin{figure}[t!]
+\begin{figure}[tb!]
     \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
@@
 
-\begin{figure}[htb!]
+\begin{figure}[tbh!]
     \caption{Example of Kriging Field}
@@
 
-\begin{figure}[htb!]
+\begin{figure}[tbh!]
     \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
@@
 However, their point estimates compare, in part, changes in outcomes between TVA counties with neighboring counties that likely were impacted by the large-scale electrification program.
+Their identification strategy depends \emph{explicitly} a parallel counterfactual trends assumption after controlling for covariates and \emph{implicitly} on no violations of the SUTVA assumption.
+
 As described above and estimated below, the program likely induced manufacturing and agricultural employment effects in nearby counties.
@@
 The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted.
-However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform.
+However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.
 
@@
 
-\begin{figure}[tbh!]
+\begin{figure}[tb!]
     \caption{TVA Effective Sample and Spillover Variables}

### 2020-12-03 latex/slides/Spillover_slides.tex
Added TVA section to slides and small edits

@@
-\documentclass[aspectratio=169]{beamer}
+\documentclass[aspectratio=43]{beamer}
 % Metropolis Theme ------------------------------------------------------------------------------
@@
 \input{preamble.tex}
+
+\addbibresource{references.bib}
 
@@
     For exposition, I will label units as counties.
-Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{This form adapts the framework of Vazquez-Bare (2020) for the diff-in-diff setting.}
+Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{This form adapts the framework of \citet{Vazquez-Bare_2019} for the diff-in-diff setting.}
 
@@
 \begin{frame}{Parallel Trends}
-    \begin{itemize}
-        \item I assume a modified version of the parallel trends assumption: \[
+    I assume a modified version of the parallel trends assumption: 
+    \[
         \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 1, \vec{D} = 0 \right] 
@@
 
+    \begin{itemize}
         \item In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
@@
 \begin{frame}{What does Diff-in-Diff identify?}
-    \begin{itemize}
-        \item With that, I decompose the diff-in-diff estimate as follows:
+    With the parallel trends assumption and random assignment of $D_i$, I decompose the diff-in-diff estimate as follows:
 
@@
 
-    \end{itemize}
 \end{frame}
@@
 
-\begin{frame}{Example of Bias Simulation}
+\begin{frame}{Example of Bias}
     \textbf{Treated Spillover:}
@@
 \begin{frame}{Tennessee Valley Authority}
+    \citet{Kline_Moretti_2014} look at the long-run impacts of the Tennessee Valley Authority (TVA).
 
+    \begin{itemize}
+        \item The TVA was a large-scale federal investment started in 1934 that focused on improving manufacturing economy.
+
+        \item The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy
+
+        \item Hundreds of dollars spent anually per person
+    \end{itemize}
 \end{frame}
+
+\begin{frame}{Identification}
+    \citet{Kline_Moretti_2014} run the county-level difference-in-differences  specification: 
+    \begin{equation}\label{eq:tva_spillover}
+        y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \beta + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940})
+    \end{equation}
+
+    \begin{itemize}
+        \item $y$ are outcomes for agricultural employment, manufacturing employment, and median family income.
+        \item $\text{TVA}_c$ is the treatment variable
+        \item $X_{c, 1940}$ allow for different long-term trends based on covariates in 1940. 
+    \end{itemize}
+
+    They trim the sample using a logit regression to predict treatment using $X_{c,1940}$ and keep control units in the top 75\% of predicted probability.
+\end{frame}
+
+\begin{frame}{Spillovers in the TVA Context}
+    In our context, there is reason to believe spillovers can occur to nearby counties
+
+    \begin{itemize}
+        \item Agricultural employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley
+
+        \item Manufacturing jobs that would have been created in the control units in the absence of treatment might move to the Tennessee Valley
+
+        \item Since manufacutring jobs pay higher than agricultural jobs, the above two spillover effects can cause changes in median family income
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Specification including spillovers}
+    \begin{equation}
+        \Delta y_c = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + \Delta \varepsilon_c
+    \end{equation}
+
+    \begin{itemize}
+        \item $\text{Between}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
+        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] \right\} \]
+    \end{itemize}
+\end{frame}
+
+\imageframe{../../figures/figure-tva-sample_slides.pdf}
 
@@
     \label{tab:tva}
-    \renewcommand{\arraystretch}{1}
+    \renewcommand{\arraystretch}{1.2}
 
@@
 
-                & \multicolumn{1}{c}{\textbf{Kline \& Moretti (2011)}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
+                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
                 \cmidrule{2-2} \cmidrule{3-6} 
                 & & & TVA between & TVA between & TVA between \\ 
-                \textit{Dependent Var.} & TVA & TVA & 0-100 mi. & 100-250 mi. & 250-500 mi. \\
+                \textit{Dependent Var.} & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\
 

### 2020-12-03 figure-gen_map_examples_with_bias.R

@@ -26,7 +26,9 @@ source("helper-sim_function.R")
 source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
 
 # Is for slides or paper?
-slides <- FALSE
+slides <- TRUE
+# h_w_ratio <- 9/16
+h_w_ratio <- 3/4
 
 
 ## Load Parameters -------------------------------------------------------------
@@ -135,11 +137,11 @@ plot_te_spill_all <- ggplot(counties_treat) +
 
 # Export Maps for Beamer Slides
 ggsave("figures/figure-map_te.png", plot_te, 
-	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+	   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 ggsave("figures/figure-map_te_spill_control.png", plot_te_spill_control, 
-	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+	   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 ggsave("figures/figure-map_te_spill_all.png", plot_te_spill_all, 
-	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+	   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 
 usethis::ui_done("Finished exporting no sp_corr maps")
 
@@ -228,9 +230,9 @@ plot_te_spill_all_low_zp <- ggplot() +
 )
 
 
-ggsave("figures/figure-spcorr_low_map_te.png", plot_te_low_zp, dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
-ggsave("figures/figure-spcorr_low_map_te_spill_control.png", plot_te_spill_control_low_zp, dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
-ggsave("figures/figure-spcorr_low_map_te_spill_all.png", plot_te_spill_all_low_zp, dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+ggsave("figures/figure-spcorr_low_map_te.png", plot_te_low_zp, dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
[…]

### 2020-12-03 tva-analysis-replicate.R

@@ -83,7 +83,7 @@ df_reg <- df_reg %>%
 ## Figure of counties and spillover variable -----------------------------------
 
 fips_in_sample <- df_reg %>%
-	drop_na(!!c(controls, y)) %>% 
+	drop_na(!!c(controls)) %>% 
 	filter(keep == TRUE) %>% 
 	pull(fips)
 
@@ -115,18 +115,25 @@ grey_palette <- c("grey30", "grey50", "grey70")
 		# Outline of TVA
 		geom_sf(data = tva, color = "Black", fill = NA, size = 1.1) + 
 		coord_sf(datum = NA) + 
-		theme_kyle(base_size = 14) +
+		theme_kyle(base_size = 14, slides = slides) +
 		theme(
 			legend.position = c(0.1, 0.15), 
 			legend.background = element_rect(colour = "grey40")
 		) +
-		labs(fill = "Spillover Bin") +
+		labs(fill = "Spillover Bin") + {
+			if(slides) labs(title = "Effective Sample and Spillover Variables")
+		} +
 		scale_fill_manual(values = nord_palette, na.translate = FALSE)) 
 		# scale_fill_manual(values = grey_palette, na.translate = FALSE)) 
 
 
-if(export) ggsave("figures/figure-tva-sample.pdf", spillover_map, 
+if(export & !slides) ggsave("figures/figure-tva-sample.pdf", spillover_map, 
 	   dpi= 300, width= 2400/300, height= 1350/300, bg= "white")
+
+if(export & slides) ggsave("figures/figure-tva-sample_slides.pdf", spillover_map, 
+						   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
+
+
 
 
 ## Regression -------------------------------------------------------------------
@@ -227,8 +234,8 @@ for(y in dep_names) {
 	se_str <- str_pad(paste0("$(", sprintf("%0.4f", se), ")$"), 15, "both")
 	row    <- paste0(row, pt_str, "& ")
 	row_se <- paste0(row_se, se_str, "& ")
-	row_slides    <- paste0(row_slides, pt_str, "& ")
-	row_slides_se <- paste0(row_slides_se, se_str, "& ")
+	# row_slides    <- paste0(row_slides, pt_str, "& ")
+	# row_slides_se <- paste0(row_slides_se, se_str, "& ")
 	
 	# Diff-in-Diff Controls TVA
 	pt     <- coef(reg_controls)[["tva"]]

### 2020-12-03 latex/slides/Spillover_slides.tex
Added slides for bias-adjustment and inference

@@
 \begin{frame}{Spatial Spillovers}
+
+    Researchers use difference-in-differences to estimate the average treatment effect on the treated: 
+    \[
+        \mathbb{E} \{ Y_{i1}(1) - Y_{i1}(0) \ \vert \ D_{i} = 1 \}
+    \]
+
     Effects of treatments at states, counties, etc. can spill over boundaries.
@@
     \end{itemize}
+\end{frame}
 
-    Differences-in-differences that compare outcomes among treated units with ``control'' units are biased from the spillover of effects.
+\begin{frame}{Spatial Spillovers}
+    The difference-in-differences estimate is: 
+    \[ 
+        \hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - 
+        \hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]     
+    \]
+
+    Two problems in presence of spillover effects: 
+    \begin{itemize}
+        \item Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment
+
+        \item Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
+    \end{itemize}
+
 \end{frame}
@@
 
+\begin{frame}{Partial Identification}
+    Now, I turn to formalizing the above example following the literature on partial identification for treatment effects: \begin{citecolor}
+        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
+    \end{citecolor}
+
+    In this framework, researchers need to specify bounds on spillovers in the context of their research question.
+\end{frame}
+
+\begin{frame}{Partially-identified Set}
+    Following \citet{Rambachan_Roth_2020} and \citet{Manski_Pepper_2018}, researchers can provide bounds to the maximum spillovers.
+
+    Let $\Delta$ denote the interval of potential biases: 
+    \begin{align*}
+        \Delta &\equiv [\underline{\Delta}, \overline{\Delta}] \\
+        &= \left[ \min \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}, \ \max \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \right] 
+    \end{align*}
+
+    The partially identified set is formed by \[ 
+        \left[\hat{\tau} - \underline{\Delta} , \ \hat{\tau} + \overline{\Delta} \right]    
+    \]
+
+\end{frame}
+
+\begin{frame}{Bias-adjusted Inference}
+
+    Inference can be done following \citet{Rambachan_Roth_2020} by creating a Fixed-Length Confidence Interval: 
+    \[ 
+        \left[
+            \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}
+        \right]
+    \]
+
+    These standard errors should account for the spatial structure of outcomes following \citet{Conley_1999}.
+\end{frame}
+
 % ------------------------------------------------------------------------------
@@
 
-        \item Assume, for now, there is only spillover on the control.
+        \item Assume, for now, there is only spillover on the control, i.e. $\tau_{\text{spillover,treat}} = 0$.
 
@@
 \end{frame}
+
+% @kylebutts @TODO: show parametrization fixes biases.
 

### 2020-12-04 latex/slides/Spillover_slides.tex
Econometrics Brownbag Slides

@@
 \begin{frame}{Spatial Spillovers}
-
-    Researchers use difference-in-differences to estimate the average treatment effect on the treated: 
+    Researchers aim to estimate the average treatment effect on the treated: 
     \[
-        \mathbb{E} \{ Y_{i1}(1) - Y_{i1}(0) \ \vert \ D_{i} = 1 \}
+        \tau \equiv \mathbb{E} \left[ Y_{i1}(1) - Y_{i1}(0) \ \vert \ D_{i} = 1 \right]
     \]
 
-    Effects of treatments at states, counties, etc. can spill over boundaries.
+    \vspace{5mm}
+    Spillover effects are when effect of treatment extend over boundaries such as states, counties, etc.
 
@@
 
-\begin{frame}{Spatial Spillovers}
-    The difference-in-differences estimate is: 
+\begin{frame}{Bias from Spatial Spillovers}
+    The canonical difference-in-differences estimate is: 
     \[ 
-        \hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - 
-        \hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]     
+        \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
+        \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Counterfactual Trend}}
     \]
@@
     \begin{itemize}
-        \item Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment
+        \item \textbf{Spillover onto Control Units:}
 
-        \item Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
+        Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment
+
+        \item \textbf{Spillover onto other Treated Units:}
+
+        Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
     \end{itemize}
@@
 
-\begin{frame}{Research Question}
-    What are the sources of bias when researchers do not account for sptial spillover of treatment effects?
+% Just TE
+\imageframe{../../figures/figure-map_te.png}
+
+% TE + Spill Control
+\imageframe{../../figures/figure-map_te_spill_control.png}
+
+% TE + Spill Control + Spill Treat
+\imageframe{../../figures/figure-map_te_spill_all.png}
+
+\begin{frame}{Outline}
 
     \begin{itemize}
-        \item In what contexts are these biases particularly large?
+        \item[1--] Using a potential outcomes framework, I derive the bias in the presence of spillovers
 
-        \item Do current simple adjustments work?
+        \item[2--] Using Monte Carlo simulations, show when biases are large and analyze effectiveness of current adjustments done by applied researchers
+
+        \item[3--] Revisit \citet{Kline_Moretti_2014} analysis of the Tennessee Valley Authority
     \end{itemize} 
@@
 \end{frame}
-
-% Just TE
-\imageframe{../../figures/figure-map_te.png}
-
-% TE + Spill Control
-\imageframe{../../figures/figure-map_te_spill_control.png}
-
-% TE + Spill Control + Spill Treat
-\imageframe{../../figures/figure-map_te_spill_all.png}
 
@@
 
-        $h_i(\vec{D})$ = 1 if there is a treated unit within $x$-miles of unit $i$ and = 0 otherwise
+        $h_i(\vec{D})$ equals 1 if there is a treated unit within $x$-miles of unit $i$ and equals 0 otherwise
 
-        \item \textbf{Average treatment among k-nearest neighbors:}
+        \item \textbf{Average treatment among $k$-nearest neighbors:}
 
@@
 
-    \begin{itemize}
-        \item In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
-    \end{itemize}
+    \vspace{5mm}
+    In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
+
 \end{frame}
@@
     \begin{align*}
-        &\mathbb{E}_i \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E}_i \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right] \\
+        &\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right] \\
         &\quad = 
-        \textcolor{green}{\mathbb{E}_i \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
+        \textcolor{green}{\mathbb{E} \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
         &\quad\quad + 
-        \textcolor{red}{\mathbb{E}_i \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
+        \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
         &\quad\quad - 
-        \textcolor{purple}{\mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\
+        \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\
         &\quad \equiv \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
@@
 
-    $\mathbb{E}_i \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right] = -0.5$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+    $Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) = -0.5$ if county $i$ shares a border with a treated county and $0$ otherwise.
 
@@
 
-    $\mathbb{E}_i \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right] = 1$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 1$ if county $i$ shares a border with a treated county and $0$ otherwise.
 
-    \begin{itemize}
-        \item Then, the bias term is \begin{align*}
-            -0.5 * \text{\% of treated within 40 miles of a treated county} \\
-            -1 * \text{\% of control within 40 miles of a treated county}
+    Then, the bias term is 
+    \begin{align*}
+        &-0.5 * \text{\% of treated counties sharing a border with a treated county} \\
+        &-1 * \text{\% of treated counties sharing a border with a treated county}
     \end{align*}
-    \end{itemize}
 \end{frame}
@@
 \begin{frame}{Partial Identification}
-    Now, I turn to formalizing the above example following the literature on partial identification for treatment effects: \begin{citecolor}
+    Researchers can us the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.
+
+    To formalize this, I follow the literature on partial identification for treatment effects:
+
+    \begin{citecolor}
         [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
     \end{citecolor}
-
-    In this framework, researchers need to specify bounds on spillovers in the context of their research question.
 \end{frame}
@@
 
+% ------------------------------------------------------------------------------
+% \section{Estimation with Spillovers}
+% ------------------------------------------------------------------------------
+
 \begin{frame}{Spillovers as estimand of interest}
@@
 % @kylebutts @TODO: show parametrization fixes biases.
+
+% \begin{frame}{Including Spillovers in Regression}
+%    How well does the modified specification do with misspecified spillovers?
+% \end{frame}
 
@@
 
-    They trim the sample using a logit regression to predict treatment using $X_{c,1940}$ and keep control units in the top 75\% of predicted probability.
+    They trim the sample using a logit regression to predict treatment using $X_{c,1940}$ and then keep control units in the top 75\% of predicted probability.
 \end{frame}
@@
 
-                \input{../../tables/tva_replication_slides.tex}
+                Agricultural employment     & $-0.0514^{***}$& $-0.0678^{***}$& $-0.0310^{**}$ &    $-0.0112$   & $-0.0252^{***}$\\
+                &   $(0.0087)$   &   $(0.0102)$   &   $(0.0123)$   &   $(0.0094)$   &   $(0.0084)$
 
+                \onslide<2->{
+                \\
+                Manufacturing employment    & $0.0560^{***}$ &  $0.0461^{**}$ &    $-0.0104$   &    $-0.0128$   &  $-0.0248^{*}$ \\
+                &   $(0.0187)$   &   $(0.0210)$   &   $(0.0205)$   &   $(0.0257)$   &   $(0.0147)$ 
+                }
+                \onslide<3->{
+                \\
+                Median family income        & $0.0191^{***}$ &  $0.0196^{**}$ &    $0.0056$    &    $-0.0062$   &    $-0.0011$   \\
+                &   $(0.0067)$   &   $(0.0077)$   &   $(0.0079)$   &   $(0.0060)$   &   $(0.0032)$ 
+                }
+                \\
+
+                % \input{../../tables/tva_replication_slides.tex}
                 \bottomrule
@@
 
+\section{Conclusion}
+
+\begin{frame}{To-do:}
+    \begin{itemize}
+        \item Include Monte-Carlo simulations on misspecification of spillovers
+
+        \item Extend bias to settings with differential timing of treatment
+    \end{itemize}
+\end{frame}
+
+\begin{frame}
+    \begin{center}
+        \Large \textbf{Thank you!}
+    \end{center}
+\end{frame}
+
 \end{document}

### 2020-12-04 figure-gen_map_examples_with_bias.R
Updated example figures for Slides

@@ -61,7 +61,7 @@ treat_prob_percent <- paste0(round(treat_prob * 100, 1), "%")
 
 counties_treat <- sim_data(
 		treat_prob = treat_prob, treat_spillover_distance = 30, treat_effect = te, 
-		treat_effect_spill = te_spill, treat_effect_spill_treat = te_spill_treat, spill_type = "within", 
+		treat_effect_spill = te_spill, treat_effect_spill_treat = te_spill_treat, spill_type = "contig", 
 		spatial_autocorr = FALSE, zone_plus = 0, drop_geometry = FALSE
 	) %>% 
 	filter(year == 2019) %>% select(-centroid) %>% st_as_sf()
@@ -71,7 +71,6 @@ bias_treat <- round(te_spill_treat * sum(counties_treat$spill_within_treat) / su
 
 
 # Treatment Effect Maps
-(
 plot_te <- ggplot() +
 	geom_sf(data= counties_treat, aes(fill= factor(te)), color= "grey60", size= 0.2) + 
 	geom_sf(data= counties_treat %>% filter(treat == 1), fill = NA, color = "black") +
@@ -85,15 +84,13 @@ plot_te <- ggplot() +
 	) + 
 	theme_kyle(slides = TRUE) + 
 	# Put Legend on Bottom
-	guides(fill = guide_legend(title.position = "top", nrow = 1)) +
-	theme(legend.position = "bottom") +
+	guides(fill = guide_legend(title.position = "top", nrow = 4)) +
+	# theme(legend.position = "bottom") +
 	# Fill Scale, colors from R color Brewer
 	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A")) + 
 	theme(title = element_text(lineheight = 1.2))
 
-)
 
-(
 plot_te_spill_control <- ggplot(counties_treat) +
 	geom_sf(data= counties_treat, aes(fill= factor(te_spill + te)), color = "grey60", size = 0.1) + 
 	geom_sf(data= counties_treat %>% filter(treat == 1), fill = NA, color = "black") +
@@ -107,14 +104,12 @@ plot_te_spill_control <- ggplot(counties_treat) +
 	) + 
 	theme_kyle(slides = TRUE) + 
 	# Put Legend on Bottom
-	guides(fill = guide_legend(title.position = "top", nrow = 1)) +
[…]

### 2020-12-14 figure-gen_map_examples_with_bias.R
Made figures Cleaner

@@ -68,10 +68,12 @@ counties_treat <- sim_data(
 
 bias_control <- round(te_spill * sum(counties_treat$spill_within) / sum(counties_treat$treat == 0), 2)
 bias_treat <- round(te_spill_treat * sum(counties_treat$spill_within_treat) / sum(counties_treat$treat == 1), 2)
-
+estimate <- te
+estimate_control <- te - bias_control
+estimate_both <- te + bias_treat - bias_control
 
 # Treatment Effect Maps
-plot_te <- ggplot() +
+(plot_te <- ggplot() +
 	geom_sf(data= counties_treat, aes(fill= factor(te)), color= "grey60", size= 0.2) + 
 	geom_sf(data= counties_treat %>% filter(treat == 1), fill = NA, color = "black") +
 	geom_sf(data= us, fill = NA, color= "grey30", size= 0.2) + 
@@ -79,7 +81,7 @@ plot_te <- ggplot() +
 	coord_sf(datum = NA) +
 	labs(
 		title= "Direct Effect of Treatment",
-		subtitle= glue::glue("Pr(treatment) = {treat_prob_percent}; Bias = 0 \n Treated units outlined in black"),
+		subtitle= glue::glue("Treatment Effect Estimate: {estimate} \n Treated units outlined in black"),
 		fill= "Effect Size"
 	) + 
 	theme_kyle(slides = TRUE) + 
@@ -88,7 +90,7 @@ plot_te <- ggplot() +
 	# theme(legend.position = "bottom") +
 	# Fill Scale, colors from R color Brewer
 	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A")) + 
-	theme(title = element_text(lineheight = 1.2))
+	theme(title = element_text(lineheight = 1.2)))
 
 
 plot_te_spill_control <- ggplot(counties_treat) +
@@ -99,7 +101,7 @@ plot_te_spill_control <- ggplot(counties_treat) +
 	coord_sf(datum = NA) +
 	labs(
 		title= "Direct Effect + Spillover on Control", 
-		subtitle= glue::glue("Pr(treatment) = {treat_prob_percent}; Bias = -{bias_control} \n Treated units outlined in black"),
[…]

### 2020-12-14 helper-sim_function.R

@@ -145,21 +145,13 @@ sim_data <- function(
 	df <- counties_treat %>% 
 			expand_grid(year = 2000:2019) %>%
 			mutate(
-				treat_ind= case_when(
-					year >= 2010 ~ 1 * treat,
-					year <= 2009 ~ 0
-				),
-				spill_ind= case_when(
-					year >= 2010 ~ 1 * spill,
-					year <= 2009 ~ 0
-				),
-				spill_ind_treat= case_when(
-					year >= 2010 ~ 1 * spill_treat,
-					year <= 2009 ~ 0
-				),
-				te= treat_effect * treat_ind,
-				te_spill= treat_effect_spill * spill_ind,
-				te_spill_treat= treat_effect_spill_treat * spill_ind_treat
+				post = if_else(year >= 2010, 1, 0),
+				treat_ind = treat * post,
+				spill_ind = spill * post, 
+				spill_ind_treat = spill_treat * post, 
+				te = treat_effect * treat_ind,
+				te_spill = treat_effect_spill * spill_ind,
+				te_spill_treat = treat_effect_spill_treat * spill_ind_treat
 			) %>%
 			# Year FE
 			group_by(year) %>%

### 2020-12-14 latex/paper/Spillover.tex
Updated introduction and contribution

@@
 Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states.
-The effect of these treatments do not typically stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects affecting neighboring areas.
+Potentially, the effect of these treatments do not stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects affecting neighboring areas.
 In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that a unit's potential outcome does not depend on the treatment status of any other unit \citep{Rubin_1980}.
-This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
-geographic distance, node distance in a graph, or social relationships in schools or cities.}
+This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units' treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
+geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.}
 
-This paper identifies problems in estimation of treatment effets in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers.
+This paper identifies problems in estimation of treatment effects in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers.
+To do this, I first introduces a potential outcome framework that explicitly models spatial spillovers following \citet{Vazquez-Bare_2019}.
+Typically researchers are interested in the `direct' effect on the treated units (sometimes called the partial equilibrium effect or the `local' effect).
+In the presence of spatial spillovers, difference-in-differences estimates identify the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
 
-To do this, I first introduces a potential outcome framework that explicitly models this violation of SUTVA following \citet{Vazquez-Bare_2019}.
-In the presence of spatial spillovers, I identify two sources of bias that result when estimating treatment effects by standard difference-in-differences methodologies.
-
+The intuition for these two sources is as follows.
 First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
@@
 In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
-For example, if a factory opening in a given county benefits both that county and neighboring counties, the treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
-Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had preferences over both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units.
+For example, consider a factory opening in a county.
+Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain \citep{Duranton_Puga_2003}.
+The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
+Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had a welfare function that included both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units.
 Difference-in-differences estimation would result in double undercounting.}
@@
 Therefore the bias of treatment effect is the same sign as the sign of the spillover.
-For example a factory opening in two neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces.
-The estimated treatment effect will be positively biased because there is a positive spillover onto also treated units.
+Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces.
+The estimated treatment effect will count the `direct` effect of the factory opening as well as the benefit of the agglomeration economies.
+Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.
 
-These biases are explicit functions of potential outcomes and can be used inuitively by researchers to sign the bias.
-The magnitude of the bias depends on two factors: the size of the spillover and the number of units affected by spillovers.
+These biases are explicit functions of potential outcomes and can be used by researchers to sign or bound the bias using insight from their economic context.
+The magnitude of the bias depends on two factors: the size of the spillovers and the number of units affected by spillovers.
 If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large.
-This paper provides an explicit form for this bias and enables researchers to give bounds for it under assumptions about the size of the spillover effect and on number of units affected.
+This result of this paper enables researchers to give bounds for it under assumptions about the size of the spillover effect and on number of units affected.
 I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.
@@
 In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers in their empirical specification to prevent bias in the estimation of treatment effects.
+The other papers usually will first estimate the direct effect without controlling for spillovers and then later on seperately estimate the spillover effects.
+This paper shows that not controlling for spillovers produces biased estimates of the direct effect.
 
 Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers.
-Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers on to control units.
+Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers onto control units.
+In the presence of spillover onto other treated units, the estimates will still be biased for the direct effect.
 Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.
 
-Removing both kinds of bias requires a researcher to take a stance and parameterize a functional form for the spillover function.
-The particular functional form depends on the context of the application however there are a few practical considerations.
+Removing both sources of bias requires a researcher to take a stance and parameterize a functional form for the spillover function.
+The particular functional form depends on the context of the application.
+However, there are a few practical considerations.
 First, the researcher should argue whether spillovers on control units and on treated units exist.
@@
 Last, they should consider if spillovers are additive in the number of nearby units that are treated.
+
+% @TODO: Discuss effectiveness under misspecification of spillovers.
 
@@
 
-There are two different models of SUTVA violations in the literature.
-Within-group spillovers are when units are in distinct groups and outcomes depend on the treatment status within your group only.
-For example, SUTVA is violated if a student's standardized test score depends on the proportion of students enrolled in a tutoring program at that school.
-In this case, each school constitutes a group and it is assumed treatment effect is not affected by other schools' tutoring enrollment.
-Estimation in this case is done in a `partial intereference' framework.\footnote{\citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} This setting compares ``control'' units in a partially treated group with control units in completely untreated groups to estimate spillover effects.\footnote{\citet{Angelucci_DiMaro_2016} provides a summary for estimation of within-group treatment effects.} However, the setting in my paper does not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups.
-
-The more general form is sometimes called between-group spillovers which occur when groups are overlapping.
-For example, a counties' economic outcomes depend on the economic outcomes of nearby counties (even across state borders).
-Estimation in this framework is more difficult and requires the researcher to either identify control units that are free from spillovers or to parameterize how control units are affected by treatment.
+The literature considering spillovers primarily has focused on ``within-group'' spillovers where units are in distinct groups and outcomes depend on the treatment status within the observation's group only.\footnote{For example, researchers consider peer effects within schools.
+In this case, each school constitutes a group and it is assumed that outcomes do not depend on other schools' treatment status, i.e.
+SUTVA is satisfied between-groups.
+Estimation of spillover effects in this case is done in a `partial intereference' framework that compares ``control'' units in a partially treated group with control units in completely untreated groups.
+\citet{Angelucci_DiMaro_2016} provides a summary for estimation of spillover effects in within-group settings.
+Examples in the literature include: \citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.}
+However, spatial settings such as counties do not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups (a county is connected to all other counties by some chain of neighbors).
+My paper considers a more general form of interference.
+Identification in this framework requires the researcher to either identify control units that are free from spillovers (far-away from treatment) or to parameterize how control units are affected by treatment.
 
 \citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector.
-He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h_i(\vec{D})$.
-The function $h_i(\vec{D})$ is referred to as an exposure mapping and adding an exposure mapping to the potential outcomes framework allows to explicitly model SUTVA violations.
+He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h(\vec{D}, i)$.
+The function $h(\vec{D}, i)$ is referred to as an exposure mapping and adding this to the potential outcomes framework allows me to explicitly model SUTVA violations.
 Using this framework, \citet{Vazquez-Bare_2019} shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.
+
 My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by difference-in-differences.
@@
 \citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''.
-Then, the authors describe how the ATE estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h_i(\vec{D})$.
-My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
+That is, a treated unit's treatment effect is defined as the direct effect and the general equilibrium spillover effects.
+Then, the authors describe how the ATE estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h(\vec{D}, i)$.
+My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.\footnote{These estimates can be combined afterwards to estimate their definition of average treatment effect.
+The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.}
 
-\citet{Delgado_Florax_2015} consider spillover only on to control units and identify a bias that can come from estimating a difference-in-differences model without explicitly controlling for spillovers.
-Using Monte-Carlo simulations, they find that there is an omitted variable bias problem by not including a measure of spillovers.
-My paper derives an explicit form for this bias in terms of potential outcomes and also includes the presence of spillovers on to also treated units.
+There are a few papers that discuss estimation of treatment effects with spatial spillovers using the difference-in-differences framework.
+\citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model.
+However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units.
+\citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} identifies biases in estimation of the direct effect for a specific potential outcome function where $h(\vec{D}, i)$ is the proportion of treated contiguous counties.
+Finally, \citet{Delgado_Florax_2015} consider the case where the exposure mapping is defined by a spatial weights matrix $W\vec{D}$ that enters linearly into the potential outcomes.
+This does not allow for the coefficient to change for control and treated units.\footnote{Although, one could change the weighting matrix to make ad-hoc assumption of the signs and relative magnitudes of spillovers onto treated and control units, but this allows for less data-driven estimation.}
 
-Similarly, \citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model.
-However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units.
-Lastly, \citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} find results for a specific potential outcome function where $h_i(\vec{D})$ is the proportion of treated contiguous counties.
-They allow this spillover to enter the potential outcome additively and the coefficient is allowed to differ by own treatment status.
-In my framework, if I assume the particular functional forms for potential outcomes of \citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}, I arrive at the same bias equation as theirs.
+My paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers.
+For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly.
 
 Lastly, I contribute to a literature in urban economics on local place-based policies.
-Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' effects of the policy are offset in parts by indirect effects.
+Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects.
 I contribute to estimating aggregate effects of place-based policies by showing that typical estimation strategies can underestimate the local effect by ignoring spillovers.
-To do so, I revise the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
+As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
 The Tennessee Valley Authority was a large push to bring electrification to the Tennessee Valley with the goal of improving the manufacturing sector there.
 The scale of the program was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies.
-I show that estimation by difference-in-differences fails to account for these spillovers and underestimates the local effect.
+I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.
 
 The rest of the paper is structured as follows.
-Section 2 presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
-Section 3 presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature.
-Section 4 presents an application for evaluating the Tennessee Valley Authority program.
+Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
+Section \ref{sec:monte_carlo} presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature.
+Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
 
@@
 \section{Potential Outcomes Framework}
+\label{sec:po_framework}
 % ------------------------------------------------------------------------------
@@
 Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards.
-As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$, denoted $Y_{i,t}(D_i, h_i(\vec{D})$), are a function of own treatment-status $D_i$ and,  departing from the canonical framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$.
-The function $h_i(\vec{D})$ is referred to as an `exposure mapping' and is a non-negative scalar.\footnote{The derivation of bias does not require this assumption.} The `exposure mapping' measures the intensity at which unit $i$ is affected by spatial spillovers.
-When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = 0$.
-The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment and can be summarized by $h_i(\vec{D})$.
+As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$, denoted $Y_{i,t}(D_i, h(\vec{D}, i)$), are a function of own treatment-status $D_i$ and,  departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function.
+The `exposure mapping' measures the intensity at which unit $i$ is affected by spatial spillovers.
+When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = 0$.
+The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment which are summarized by $h(\vec{D}, i)$.
 
-To help better understand the exposure mapping function, I give three examples of $h_i(\vec{D})$ that are commonly used in the literature.
-First, $h_i(\vec{D})$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$ (similarly a dummy for counties that share borders is commonly used).
-Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
+To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature.
+First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
 In this case \[
-    h_i(\vec{D}) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
+    h(\vec{D}, i) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
 \] 
-This exposure mapping is useful when it is assumed that spillovers do not decay over distance and the number of neighboring units treated do not impact the intensity of spillovers.
-For example, this mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
-In this case the distance $\bar{d}$ would be the maximum distance people would likely travel to a nearby library.
-Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to the level of spillovers.
+This exposure mapping is useful when it is assumed that spillovers do not decay over distance until $\bar{d}$ and the number of neighboring units treated do not impact the intensity of spillovers.
+For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
+In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library.
+Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to spillovers in this context.
 
-Second, $h_i(\vec{D})$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
-    h_i(\vec{D}) = 1/k \sum_{j \in k(i)} D_j,
+Second, $h(\vec{D}, i)$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
+    h(\vec{D}, i) = 1/k \sum_{j \in K(i)} D_j,
 \]
-where $k(i)$ is the index of unit $i$'s k-nearest neighbors.
-This exposure mapping is no longer binary, so intensity of spillovers depend on the number of units treated.
-In the context of large store openings and agglomeration economies, this would imply that as the number of nearby counties receiving new factories increase, the effect on own-county outcomes increase as well \citep{Basker_2005}.
+where $K(i)$ is the index of unit $i$'s k-nearest neighbors.
+This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of units treated.
+In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies.
+As more nearby counties receive new factories, the agglomeration forces increase \citep{Basker_2005}.
 
-Last, is the spatial decay function where exposure decreases with distance.
-This depends on the decay parameter $\alpha$ that is decided by the researcher.
-In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
-\[
-    h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
+Last, is the spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \[ 
+    h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
 \] 
@@
 This creates problems with inference because it implies potential correlation between all units' error terms.
-For this reason, this function often is summed over only the $k$-nearest neighbors.} In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
-This allows for the technology spillovers to decay over distance to an exponential degree.
+For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be decided by the researcher or estimated using non-linear least squares.
+In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
 
 The last thing a researcher must do is specify the functional form of the potential outcomes.
-Typically, the spillover function enters into the regression linearly and ocasionally the coefficient is allowed to differ by treatment status.
+Typically, the spillover function enters into the regression linearly and potentially the coefficient is allowed to differ by treatment status.
 
@@
 With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
-    Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0).
+    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0).
 \] 
-The spillover measures the difference in non-treated potential outcomes between being exposed and not being exposed at level $h_i(\vec{D})$.
-Then, the average spillover onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h_i(\vec{D})$: \[
-    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{i}(0, h_i(\vec{D})) - Y_{i}(0, 0) \ \vert \ D_i = 0 \right].
+The spillover measures the difference in non-treated potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
+Then, the average spillover effect onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
+    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0) \ \vert \ D_i = 0 \right].
 \]
 
-To emphasize, the average spillover onto conrol units averages over each control unit's exposure mapping.
-For example, assume the potential outcomes is additively linear in $D_i$ and $h_i(\vec{D})$ and that the coefficient $\beta_{\text{spill,control}}$ measures the effect of $h_i(\vec{D})$ on outcome $Y$ among control units.
-Then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h_i(\vec{D})$.
-The average spillover onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E}_{i} \left[ h_i(\vec{D})\right]$, i.e.
+To emphasize, the average spillover effect onto conrol units averages over each control unit's exposure mapping.
+For example, assume the potential outcomes is additively linear in $D_i$ and $h(\vec{D}, i)$ and that the coefficient $\beta_{\text{spill,control}}$ measures the effect of $h(\vec{D}, i)$ on outcome $Y$ among control units.
+Then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h(\vec{D}, i)$.
+The average spillover effect onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E} \left[ h(\vec{D}, i)\right]$, i.e.
 the average over all control units exposure mapping.
 
-Similarly, we define the average spillover onto also treated units as: \[ 
-    \tau_{\text{spill,treated}} \equiv \mathbb{E} \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(1, 0) \ \vert \ D_i = 1 \right].
+Similarly, we define the average spillover effect onto also treated units as: \[ 
+    \tau_{\text{spill,treated}} \equiv \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0) \ \vert \ D_i = 1 \right].
 \]
@@
 I assume that what the `Average Treatment Effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
-    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{i}(1, 0) - Y_{i}(0, 0) \ \vert \ D_i = 1 \right],
+    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, 0) - Y_{it}(0, 0) \ \vert \ D_i = 1 \right],
 \] 
-which measures the effect of being treated in the absence of exposure to spillovers. This differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
-    \mathbb{E} \left[ Y_{i}(1, h_i(\vec{D})) - Y_{i}(0, h_i(\vec{D})) \ \vert \ D_i = 1 \right],
+which measures the effect of being treated in the absence of exposure to spillovers. This effect does not include the general equilibrium effects of multiple treated areas near one-another.
+
+My definition of the direct effect of treatment differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
+    \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(0, h(\vec{D}, i)) \ \vert \ D_i = 1 \right],
 \] 
 where the expectation is over individuals and their exposures.
-I prefer the former because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.\footnote{The spillover effects themselves might be of interest to the researcher, so clearly seperating them is beneficial in estimation.
-Later they can be combined to estimate the `net effects' that \citet{Sävje_Aronow_Hudgens_2019} estimate.}
+I prefer the former because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.
+For example, a county deciding whether to implement a policy will want to consider the treatment effect plus the spillover at their current level of exposure.
+The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at different levels.\footnote{Estimation of the direct effect and spillover effect can be combined to estimate the ATE as defined by \citet{Sävje_Aronow_Hudgens_2019}.}
 
@@
 
-The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$.
+The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$ in the presence of spillovers.
 To show this, I first present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.
@@
 
-When researchers run the canonical difference-in-differences regression, 
-the estimate $\hat{\tau}$ will be a biased estimate for $\tau_{\text{direct}}$.
-Given that Assumption \ref{parallel} holds, the estimate can be decomposed as the direct effect and the two sources of spillover bias.
+Given that Assumption \ref{parallel} holds, the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} can be decomposed as the direct effect and the two sources of spillover bias.
 The proof is given in Appendix \ref{sec:proofs}.
@@
         &= 
-        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
-        &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
+        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
+        &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
         &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
@@
 First, the change in outcomes among treated units combines the direct effect and the spillover from nearby treated units.
-Therefore the first difference adds the average spillover onto the treated units, $\tau_{\text{spill,treated}}$.
-Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover onto control units.
-Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover onto the control, $\tau_{\text{spill,control}}$.
+Therefore the first difference adds the average spillover effect onto the treated units, $\tau_{\text{spill,treated}}$.
+Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units.
+Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover effect onto the control, $\tau_{\text{spill,control}}$.
 
-Readers that are judging estimates in the presence of spillovers can use the following heuristics to size the bias.
+Readers that are judging estimates in the presence of spillovers can use the following heuristics to sign the bias.
 If they suspect spillovers onto control units, the bias is the opposite sign of the spillover.
@@
 It is guided by choices of parameterization of the exposure mapping and potential outcomes.
-To exemplify this bias, I will show a simple example that allows a researcher to bound the bias.
-
-% ------------------------------------------------------------------------------
-\subsubsection{Example Parameterization of Bias}
-% ------------------------------------------------------------------------------
-
-As an example of Theorem \ref{thm:bias}, I will consider the example of the effect of new libraries on school outcomes.
+To exemplify this bias, I will illustrate how a researcher would bound the bias in a simple example.
+I will consider the example of the effect of new libraries on school outcomes.
 Following the motivation above, I assume that spillovers occur for any county that is within $\bar{d}$ miles of a treated county, i.e.
@@
     \label{eq:example_exposure}
-    h_i(\vec{D}) \equiv \text{Near}_{it} = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ].
+    h(\vec{D}, i) \equiv \text{Near}_{it} = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ].
 \end{align}
 This specification is a simple one in that the spillover is not additive in the number of nearby treated counties and does not decay over distance before reaching $\bar{d}$.
-The potential outcome is assumed to be additive in both treatment and in the exposure mapping, but the coefficient on $\text{Near}_{it}$ is allowed to differ between treated and non-treated unitts:
+Since treated counties have access to their own library, I will assume that no spillovers exist.
+The potential outcome is assumed to be additive in both treatment and in the exposure mapping:
 \begin{align}
@@
     \begin{split}
-        y_{it} &= \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill,control}} (1-D_{it}) \text{Near}_{it} \\
-        &\quad + \beta_{\text{spill,treated}} D_{it} \text{Near}_{it} + \varepsilon_{it},
+        y_{it} &= \beta_{\text{direct}} D_{it} + \beta_{\text{spill,control}} (1-D_{it}) \text{Near}_{it} + \mu_t + \mu_i + \varepsilon_{it},
     \end{split}
 \end{align}
-where $\mu_t$ and $\mu_i$ are unit and time fixed effects respectively.
-In this case, the spillover on an individual control unit is given by $\tau_{\text{spill,control}}$ and on an treated unit is $\tau_{\text{spill,treated}}$.
+where $\mu_t$ and $\mu_i$ are unit and time fixed effects respectively. In this case, the spillover on an individual control unit is given by $\tau_{\text{spill,control}}$.
 
-If a researcher estimates Equation \ref{eq:twfe}, then the bias will be $\tau_{\text{spill,treated}} - \tau_{\text{spill,control}}$ where the two bias terms are \[ 
-    \tau_{\text{spill,control}} = \beta_{\text{spill,control}} \frac{\sum_{i: D_{it} = 0} \text{Near}_{it}}{N_C}
-\] and \[ 
-    \tau_{\text{spill,treated}} = \beta_{\text{spill,treated}} \frac{\sum_{i: D_{it} = 1} \text{Near}_{it}}{N_T},
+If a researcher estimates Equation \ref{eq:twfe}, then the bias will be \[ 
+    - \tau_{\text{spill,control}} = - \beta_{\text{spill,control}} \frac{\sum_{i: D_{it} = 0} \text{Near}_{it}}{N_C},
 \] 
-where $N_C$ and $N_T$ are the number of control and treated units respectively.
-Simply put, the bias will be the product of the proportion of treated units that receive spillover effects and the size of the effect on treated units minus the proportion of control units that receive spillover effects time the size of the effect on control units.
+where $N_C$ are the number of control units respectively.
+Simply put, the bias will be negative one times the proportion of control units that receive spillover effects time the size of the effect on control units.
+Then the bound can be created by conservatively set by bounding $\beta_{\text{spill,control}}$ and the proportion of control units that receive spillovers.
 
-Then researchers wanting to create the bias set $\Delta$, will assume minimum and maximum values of $\beta_{\text{spill,control}}$, $\beta_{\text{spill, treated}}$, and a maximum proportion of exposed treated and control units.
-With these assumptions, the set $\Delta$ can be approximated and the partially identified set is given by $[\hat{\tau} + \underline{\Delta}, \hat{\tau} + \overline{\Delta}]$.
-Inference on this set can be done in the manner described in \citet{Rambachan_Roth_2020}.
-
-In the example of library construction, a researcher would assume that people would not drive further than 40 miles to access the library.
-Further, a researcher can argue that treatment effect does not depend on whether other counties also have access to libraries.
-Therefore, only $\beta_{\text{spill,control}}$ needs to be bounded for the the bias to be bounded.
+With a chosen $\Delta$, the partially identified set is given by $[\hat{\tau} + \underline{\Delta}, \hat{\tau} + \overline{\Delta}]$.
+Inference on this set can be done using Fixed-Length Confidence Intervals as in \citet{Rambachan_Roth_2020}.
+The confidence interval can be formed using critical values from the Z-distribution and  standard normal critical values since we are assuming a specific spatial relationship between outcomes, spatially adjusted standard errors following \citet{Conley_1999}: \[
+    \left[ \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}\right].  
+\]
 
@@
 Second, the spillover effects themselves are potentially relevant for policy makers.
-If treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will understate the true effect of treatment.
+If treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will double-understate the true effect of treatment.
 First, it will not include the neighboring units' benefit in the calculation.
@@
 Similarly, the net benefits for a treated location depend on the direct effect and the spillover effect onto treated units.
-Therefore whether the benefits depend on the number of treated units nearby.
+Therefore the size of benefits created by the treatment depend on the number of treated units nearby.
 
-There are a few practical considerations researchers should make when parametrizing the spillovers. % @TODO: Expand upon considerations in the introduction
+There are a few practical considerations researchers should make when parametrizing the spillovers. 
+% @TODO: Expand upon considerations in the introduction
 
@@
 \section{Monte Carlo Simulations}
+\label{sec:monte_carlo}
 % ------------------------------------------------------------------------------
@@
 \begin{figure}[tb!]
-    \caption{Bias of $\hat{\tau}$ with and without Control Units with Spillovers}
+    \caption{Bias of $\hat{\tau}$ with Spillovers Effects \emph{only} on Control Units}
     \label{fig:bias_as_treat_prob}
     {\centering
-        \resizebox{\textwidth}{!}{
-            \includegraphics{../../figures/figure-bias_fix.png}
+        \includegraphics[width=\textwidth]{../../figures/figure-bias_fix.png}
     } 
-    }
-
     {\footnotesize
@@
 The data generating process used is defined by the exposure mapping given in Equation \ref{eq:example_exposure} and the data generating process given in Equation \ref{eq:example_po}.
-A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on in period $t = 10$.
+A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
 The intercepet is $\alpha = -2$, the fixed effects are $\mu_t \sim N(t * 0.2, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$, and the error term is $\epsilon \sim N(0, 2^2)$.
@@
 For the first simulation, I restrict spillovers only to occur among control units, i.e.
-$\tau_{\text{spill, treat}} = 0$ and estimate the typical two-way fixed effects model.
+$\beta_{\text{spill, treat}} = 0$ and estimate the typical two-way fixed effects model.
 This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
@@
 As treatment frequency increases, the bias increases as well but at a slower rate due to fewer additional control units receiving spillover units.
+This is in part due to the assumption that spillovers are not additive in the number of nearby units treated.
 
@@
 I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers.
-Even though, I remove contiguous controls which is not the correct measure of $h_i(\vec{D})$, it approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
+Even though I remove contiguous control counties which is not the correct measure of $h(\vec{D}, i)$, contiguous counties approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
 As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.
@@
 % ------------------------------------------------------------------------------
-\subsection{Misspecification of Spillovers}
+% \subsection{Misspecification of Spillovers}
 % ------------------------------------------------------------------------------
 
-% @ TODO
+% @TODO
 
@@
 \section{Application in Urban Economics}
+\label{sec:tva}
 % ------------------------------------------------------------------------------
@@
 To illustrate the importance of accounting for spatial spillovers in the estimation of treatment effects, I revisit the analysis of the Tennessee Valley Authority (TVA) in \citet{Kline_Moretti_2014}.
-The TVA program was a large-scale federal investment started in 1934 that focused on modernizing the Tennessee valley economy.
+The TVA program was a large-scale federal investment started in 1934 that focused on modernizing the Tennessee Valley economy.
 The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy.
@@
 In \citet{Kline_Moretti_2014}, they discuss the nature of spillovers that can occur.
-For agriculture employment, \citet{Kline_Moretti_2014} claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
+For agriculture employment, the authors claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
 Hence they predict a negative spillover.
@@
 In this context, agglomerations due to `sourcing' is most likely.
-When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate nearby.
+When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.
 
@@
 \begin{equation}\label{eq:tva}
-    y_{c, t} = \mu_c + \alpha \text{Post}_t + \tau \text{TVA}_c \times \text{Post}_t + X_{c, 1940} \beta + X_{c, 1940} \times \text{Post}_t \gamma + \epsilon_{c,t},
+    y_{c, t} = \mu_c + \mu_t + \tau \text{TVA}_c \times \text{Post}_t + X_{c, 1940} \times \text{Post}_t \gamma + \epsilon_{c,t},
 \end{equation}
-where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a set of outcome variables.\footnote{The text writes the equivalent first-differences regression: \[
-    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, pre} (\gamma - \beta) + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
-\] Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
+where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a set of outcome variables.\footnote{Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.
+The text writes the equivalent first-differences regression: \[
+    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \gamma + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
+\]} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
 
 \citet{Kline_Moretti_2014} estimate Equation \ref{eq:tva} to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
-However, their point estimates compare, in part, changes in outcomes between TVA counties with neighboring counties that likely were impacted by the large-scale electrification program.
-Their identification strategy depends \emph{explicitly} a parallel counterfactual trends assumption after controlling for covariates and \emph{implicitly} on no violations of the SUTVA assumption.
+However, their point estimates compare, in part, changes in outcomes in TVA counties with changes in outcomes for neighboring counties that likely were impacted by the large-scale program.
+Their identification strategy depends \emph{explicitly} on a parallel counterfactual trends assumption after controlling for covariates and \emph{implicitly} on the SUTVA assumption.
 
 As described above and estimated below, the program likely induced manufacturing and agricultural employment effects in nearby counties.
-By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
+By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect and median family income is theoretically ambiguous.
 The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this and appear to do so in the empirical analysis below.
@@
 
-                \input{../../tables/tva_replication_slides.tex}
+                \input{../../tables/tva_replication.tex}
 
@@
 % ------------------------------------------------------------------------------
-\section{Proofs}\label{sec:proofs}
+\section{Proofs}
+\label{sec:proofs}
 % ------------------------------------------------------------------------------
@@
     &= 
-    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
+    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
     &= 
-    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h_i(\vec{D})) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
+    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h(\vec{D}, i)) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
     &= 
-    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\ 
-    &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\ 
+    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\ 
+    &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\ 
     &= 
-    \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1 \right] \\
-    &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\  
-    &= \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= \mathbb{E}\left[ Y_{i1}(1, h_i(\vec{D})) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
+    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1 \right] \\
+    &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\  
+    &= \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
+    &= \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
+    &= \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
     &= 
-    \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
-    &\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
+    \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
+    &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
     &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}

### 2021-01-27 data-prepare_counties.R
Use county center of population instead of centroids

@@ -25,32 +25,34 @@ library("doParallel")
 data("fips_codes", package= "tigris")
 
 # Load Counties Shapefile at low resolution
-counties <- tigris::counties() %>%
-	# From {sp} to {sf}
-	st_as_sf() %>%
-	# ms_simplify maintains borders touching
-	rmapshaper::ms_simplify() %>%
+counties <- sf::read_sf("data/2010_county.json") %>% 
 	st_make_valid() %>% 
-	select(state_code= STATEFP, county_code= COUNTYFP) %>%
+	select(state_code= STATEFP10, county_code= COUNTYFP10) %>%
 	# Merge with fips_codes to get state and county names
 	left_join(., fips_codes, by= c("state_code", "county_code")) %>%
 	# Remove non-continental states
 	filter(!state_name %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) %>%
 	# Project to a prettier US project EPSG:2163
 	st_transform(st_crs(2163)) %>%
-	# State + County Code make unique identifier
-	mutate(state_county = paste(state_code, county_code, sep= "-"))
+	mutate(state_county = paste(state_code, county_code, sep="-")) %>% 
+	arrange(state_code, county_code)
 
+
+# Load Counties Center of Popula"tion from NHGIS
+counties_centpop <- sf::read_sf("data/2010_county_centpop/US_county_cenpop_2010.shp") %>%
+	filter(!STNAME %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) %>%
+	select(state_code= STATEFP, county_code= COUNTYFP) %>%
+	arrange(state_code, county_code) %>% 
+	# Project to a prettier US project EPSG:2163
+	st_transform(st_crs(2163))
 
 ## Create Distance Matrix ------------------------------------------------------
 
-# st_point_on_surface is the best approximation to centroid that falls within the polygon (removes the centroids that aren't in the polygon)
-counties <- counties %>% mutate(centroid= st_point_on_surface(.$geometry))
 
-ggplot(counties$centroid) + geom_sf(size= 0.2)
+counties$centpop <- st_geometry(counties_centpop)
 
 # st_crs(counties) will show you that units are in meters
-dist <- st_distance(st_geometry(counties$centroid))
[…]

### 2021-01-27 data-prepare_counties.R
Fixed counties with center of pop

@@ -24,16 +24,17 @@ library("doParallel")
 # Load FIPS codes
 data("fips_codes", package= "tigris")
 
+# Run once
+# sf::read_sf("data/2010_county/US_county_2010.shp") %>% rmapshaper::ms_simplify(keep = 0.02) %>% st_transform(st_crs(2163)) %>% sf::write_sf(., "data/2010_county.geojson")
+
 # Load Counties Shapefile at low resolution
-counties <- sf::read_sf("data/2010_county.json") %>% 
-	st_make_valid() %>% 
+counties <- sf::read_sf("data/2010_county.geojson") %>% 
+	sf::st_make_valid() %>% st_buffer(0) %>%
 	select(state_code= STATEFP10, county_code= COUNTYFP10) %>%
 	# Merge with fips_codes to get state and county names
 	left_join(., fips_codes, by= c("state_code", "county_code")) %>%
 	# Remove non-continental states
 	filter(!state_name %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) %>%
-	# Project to a prettier US project EPSG:2163
-	st_transform(st_crs(2163)) %>%
 	mutate(state_county = paste(state_code, county_code, sep="-")) %>% 
 	arrange(state_code, county_code)
 
@@ -49,10 +50,8 @@ counties_centpop <- sf::read_sf("data/2010_county_centpop/US_county_cenpop_2010.
 ## Create Distance Matrix ------------------------------------------------------
 
 
-counties$centpop <- st_geometry(counties_centpop)
-
 # st_crs(counties) will show you that units are in meters
-dist <- st_distance(st_geometry(counties$centpop))
+dist <- st_distance(st_geometry(counties_centpop))
 
 dist_mi <- dist %>%
 	units::set_units(., "mi") %>% 

### 2021-01-28 data-prepare_counties.R
Small fixes to be consistent with paper

@@ -49,6 +49,7 @@ counties_centpop <- sf::read_sf("data/2010_county_centpop/US_county_cenpop_2010.
 
 ## Create Distance Matrix ------------------------------------------------------
 
+counties$centroid <- counties_centpop$geometry
 
 # st_crs(counties) will show you that units are in meters
 dist <- st_distance(st_geometry(counties_centpop))

### 2021-01-28 helper-sim_function.R

@@ -86,7 +86,7 @@ sim_data <- function(
 				zone = sim > quantile(sim, 1-treat_prob),
 				
 				# `zone` has increased probability of treatment
-				prob = 0.1 + zone_plus * zone,
+				prob = 0.05 + zone_plus * zone,
 				prob = prob * treat_prob/mean(prob),
 				
 				# Generate Treatment Variable

### 2021-01-28 latex/slides/Spillover_slides.tex
Add Literature Review to Slides
For Research Methods 1 presentation

@@
 % Title ------------------------------------------------------------------------------
-\title{Differnces-in-Differences with Spatial Spillover}
+\title{Difference-in-Differences with Spatial Spillover}
 \date{\today}
@@
     \begin{itemize}
-        \item e.g. large employer opening/closing in a county have positive or negative employment effects on nearby counties
+        \item e.g. large employer opening/closing in a county have positive employment effects on nearby counties
     \end{itemize}
@@
 
+        \vspace{2.5mm}
         \item \textbf{Spillover onto other Treated Units:}
@@
     \begin{itemize}
-        \item[1--] Using a potential outcomes framework, I derive the bias in the presence of spillovers
+        \item[1--] Using a potential outcomes framework, I decompose the difference-in-differences estimator in to three parts:
+        \begin{itemize}
+            \item Direct Effect of Treatment
+            \item Spillover onto Treated Units
+            \item Spillover onto Control Units
+        \end{itemize}
 
-        \item[2--] Using Monte Carlo simulations, show when biases are large and analyze effectiveness of current adjustments done by applied researchers
+        \item[2--] Using Monte Carlo simulations:
+        \begin{itemize}
+            \item Show when biases are relatively large
+            \item Analyze effectiveness of current adjustments done by applied researchers 
+        \end{itemize}
 
@@
 
-\begin{frame}{Preview of Results}
-    There are two sources of bias:
-        \begin{itemize}
-            \item[1.] Treatment effects spillover onto control units
-            \item[2.] Treatment effects spillover onto also treated units
-        \end{itemize}
+% @TODO: Literature Review
+\begin{frame}{Contribution}
 
-    Solutions:
-        \begin{itemize}
-            \item Fixing bias 1 is relatively easy and works better when you have relatively few treated units
+    \underline{Difference-in-Differences Estimation with Spillovers}
 
-            \item Bias 2 worsens as treatment locations bunch more (spatial correlation of treatment increases)
+    \begin{citecolor}
+        [\citet{Clarke_2017}, \citet{Berg_Streitz_2019}, and \citet{Verbitsky-Savitz_Raudenbush_2012}]
+    \end{citecolor}
 
-            \item However, spatial correlation of treatment decreases bias 1
-        \end{itemize}
+    % \begin{itemize}
+    %     \item My derivation generalizes the above papers by being in the form of potential outcomes.
+    % \end{itemize}
+
+    \underline{Potential Outcome Framework for Spillovers}
+
+    \begin{citecolor}
+        [\citet{Vazquez-Bare_2019}, \citet{Angelucci_DiMaro_2016}, \citet{Angrist_2014}]        
+    \end{citecolor}
+
+    \underline{Place-based Policies}
+
+    \begin{citecolor}
+        [\citet{Kline_Moretti_2014b} and \citet{Kline_Moretti_2014}]
+    \end{citecolor}
+
+    % \begin{itemize}
+    %     \item I highlight the need to control for spillovers to properly estimate local effects of policies.
+    % \end{itemize}
 \end{frame}
@@
 
+        \vspace{2.5mm}
         \item \textbf{Average treatment among $k$-nearest neighbors:}
@@
 
-\begin{frame}{Signing the Bias}
+\begin{frame}{Biased Estimate for $\tau_{\text{direct}}$}
     \[ 
-        \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}    
+        \mathbb{E}[\hat{\tau}_{\text{diff-in-diff}}] - \textcolor{green}{\tau_{\text{direct}}} = \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
     \]
@@
 
-    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 1$ if county $i$ shares a border with a treated county and $0$ otherwise.
+    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) = 1$ if county $i$ shares a border with a treated county and $0$ otherwise.
 
@@
 \begin{frame}{Partial Identification}
-    Researchers can us the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.
+    Researchers can use the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.
 
-    To formalize this, I follow the literature on partial identification for treatment effects:
-
+    To formalize this, I follow the literature on partial identification for treatment effects
     \begin{citecolor}

### 2021-01-28 helper-sim_function_misspecification.R
Write Initial Misspecification of Spillovers Program

@@ -1,0 +1,191 @@
+## -----------------------------------------------------------------------------
+## helper-sim_function_misspecification.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## This file is going to create a function that will be used for monte carlo simulations. There will be many options to the function that can be used to test things. 
+## -----------------------------------------------------------------------------
+
+## Sim Function ----------------------------------------------------------------
+
+#' Returns a dataframe generated with the given parameters to be used for diff-in-diff estimation
+#'
+#' @param treat_prob This is the unconditional probability of treatment
+#' @param treat_spillover_distance The maximum distance in miles away a treated county can be to be considered treated 
+#' @param treat_effect The true simulated treatment effect
+#' @param treat_effect_spill The true simulated spillover effect.
+#' @param treat_effect_spill_treat The true simulated spillover effect onto treated units.
+#' @param spill_type Either "within", "contig", or "decay". Represents how spillover indicator is created
+#' @param spatial_autocorr Should there be spatial autocorrelation of treament
+#' @param zone_plus Value >= 0 and tells you how much to favor counties with values in the top 10% of the generated field
+#' @param remove_spill Should control units with spillover effects be removed
+#' 
+#' @return a tibble of estimates of treatment effect under different scenarios. This will be used with dplyr::add_row
+#'
+sim_data_misspecification <- function(
+	treat_prob = 0.05,
+	treat_spillover_distance = 40,
+	treat_spillover_distance_large = 80,
+	treat_effect = 2,
+	treat_effect_spill = 1,
+	treat_effect_spill_treat = 0.5,
+	spill_type = "contig",
+	spatial_autocorr = FALSE,
+	zone_plus = 0.4,
+	drop_geometry = TRUE
+){
+	## Create Treatment and Spillover Variables --------------------------------
+	
+	# Logical matrix, =1 if within the maxmium distance for spillover
[…]

### 2021-01-28 sim-misspecification_of_spillover.R

@@ -1,0 +1,176 @@
+## -----------------------------------------------------------------------------
+## sim-misspecification_of_spillover.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## This file estimates spillover functions using misspecified spillover variables and compares the biases found.
+## -----------------------------------------------------------------------------
+
+library("tidyverse")
+library("glue")
+library("sf")
+library("stars")
+library("units")
+library("gstat")
+library("exactextractr")
+library("fixest")
+library("doParallel")
+library("gt")
+library("magrittr")
+
+# Macbook
+setwd("~/Documents/Projects/Spatial Spillover/")
+# Research Computing
+# setwd("/projects/kybu6659/spatial_spillover/")
+
+# Load theme_kyle()
+source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/15196997e5aad41696b03c49be3bfaaca132fdf2/theme_kyle.R")
+
+# Export
+export <- TRUE
+slides <- FALSE
+
+# extract_body()
+extract_body <- function(gt) {
+	if(inherits(gt, "gt_tbl")) gt <- as.character(gt::as_latex(gt))
+	stringr::str_match(gt, "(?s)\\\\midrule\\n(.*)\\\\bottomrule")[[2]]
+}
+
+
+
+# sim_data_misspecification()
+source("helper-sim_function_misspecification.R")
+ 
+
+## Load Spatial Data -----------------------------------------------------------
+# From data_prepare_counties.R
+load(file= "data/counties_and_mat.RData")
+
+
+
+# Helper function estimate
+estimate_treatment_effect <- function(data, formula, treat_var){
+	feols(formula, data= data) %>%
+		coefficients() %>% .[[treat_var]]
+}
+
+
+
+## Experimentation
+
+sim <- sim_data_misspecification(drop_geometry=FALSE) %>% 
+	st_as_sf()
+
+# Check treatment effects with optional center of population dots
+ggplot(data = sim %>% filter(year == 2019)) + 
+	geom_sf(mapping = aes(fill = te_spill_decay_additive, color = as.factor(treat))) + 
+	# geom_sf(mapping = aes(geometry = centroid), color="white", size= 0.25) +
[…]

### 2021-01-28 latex/paper/Spillover.tex
Edit introduction
Add Hannah's revisions

@@
 Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states.
-Potentially, the effect of these treatments do not stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects affecting neighboring areas.
-In the causal inference literature, the Stable Unit Treatment Value Assumption (SUTVA) is often assumed which says that a unit's potential outcome does not depend on the treatment status of any other unit \citep{Rubin_1980}.
-This article considers a common violation of SUTVA in a process I label `spatial spillovers' where `close' units' treatment assignment affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
-geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.}
+Potentially, the effect of these treatments do not stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects influencing neighboring areas.
+Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
+In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run difference-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} In this paper, I show that failing to account for spatial spillovers can lead to poorly identified estimates of treatment effects.
 
-This paper identifies problems in estimation of treatment effects in the presence of spillovers and provides practical advice on using specifications that are robust to spillovers.
-To do this, I first introduces a potential outcome framework that explicitly models spatial spillovers following \citet{Vazquez-Bare_2019}.
-Typically researchers are interested in the `direct' effect on the treated units (sometimes called the partial equilibrium effect or the `local' effect).
-In the presence of spatial spillovers, difference-in-differences estimates identify the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
+In the causal inference literature, researchers assume that a unit's potential outcome does not depend on the treatment status of any other unit -- what \citet{Rubin_1980} calls the Stable Unit Treatment Value Assumption (SUTVA).
+This article considers a common violation of SUTVA in a process I label `spatial spillovers' where the treatment assignment of `close' units' affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
+geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} Typically researchers are interested in the `direct effect' on the treated units.\footnote{This is sometimes called the `partial equilibrium' effect or the `local effect'.} In the presence of spatial spillovers, I show using a potential outcomes framework that the difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
 
-The intuition for these two sources is as follows.
+The intuition for the two bias terms resulting from spillovers is as follows.
 First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
-When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated change in outcomes.
+When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes.
 In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
@@
 Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had a welfare function that included both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units.
-Difference-in-differences estimation would result in double undercounting.}
+Difference-in-differences estimation would therefore result in double undercounting.}
 
 Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-The spillover is added to the treated units' change in outcomes.
+The spillover onto other treated units is averaged into the treated units' change in outcomes.
 Therefore the bias of treatment effect is the same sign as the sign of the spillover.
@@
 
-These biases are explicit functions of potential outcomes and can be used by researchers to sign or bound the bias using insight from their economic context.
+These biases can be written as functions of the potential outcomes in my framework and can be used by researchers to sign or bound the bias using insight from their economic context.
 The magnitude of the bias depends on two factors: the size of the spillovers and the number of units affected by spillovers.
 If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large.
-This result of this paper enables researchers to give bounds for it under assumptions about the size of the spillover effect and on number of units affected.
+Th results of this paper enable researchers to estimate bounds for it by making assumptions about the average size of the spillover effect and the number of units affected.
 I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.
 
-Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
-In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run differencse-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} Of those 21, only eight include spillovers in their empirical specification to prevent bias in the estimation of treatment effects.
-The other papers usually will first estimate the direct effect without controlling for spillovers and then later on seperately estimate the spillover effects.
+In the survey by \citet{Berg_Streitz_2019}, only eight of the 21 papers that discuss spillovers control for this potential source of bias in their primary empirical specification to prevent bias in the estimation of treatment effects.
+The other thirteen papers usually first estimate the direct effect without controlling for spillovers and then seperately estimate the spillover effects.
 This paper shows that not controlling for spillovers produces biased estimates of the direct effect.
@@
 Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers.
-Since this is a common strategy by researchers, I use Monte Carlo simulations to show that this method is effective in the case where there is \textit{only} spillovers onto control units.
-In the presence of spillover onto other treated units, the estimates will still be biased for the direct effect.
+Since this is a common strategy used by researchers, I use Monte Carlo simulations to show that this method is effective in the case where spillovers \textit{only} occur onto control units.
+In the presence of spillover onto also treated units, the estimates for the direct effect will still be biased.
 Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.
 
-Removing both sources of bias requires a researcher to take a stance and parameterize a functional form for the spillover function.
+Removing both sources of bias requires a researcher to take a stance and parameterize a functional form for the spillovers.
 The particular functional form depends on the context of the application.
@@
 
-% @TODO: Discuss effectiveness under misspecification of spillovers.
+In section \ref{sec:monte_carlo}, I use Monte-Carlo simulations to emphasize when misspecificied spillovers still remove most of the bias and when they fail to do so.
+
+% @TODO: Discuss effectiveness under misspecification of spillovers (correct distance and additive/non-additive).
 
@@
 \citet{Angelucci_DiMaro_2016} provides a summary for estimation of spillover effects in within-group settings.
-Examples in the literature include: \citet{Halloran_Struchiner_1995} considers community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.}
-However, spatial settings such as counties do not feature distinct groups which allow for the researcher to seperate areas into distinct non-overlapping groups (a county is connected to all other counties by some chain of neighbors).
+Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} However, spatial settings such as counties do not feature distinct groups which allow for the researcher to separate areas into distinct non-overlapping groups (a county is connected to all other counties by some chain of neighbors).
 My paper considers a more general form of interference.
@@
 \citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''.
-That is, a treated unit's treatment effect is defined as the direct effect and the general equilibrium spillover effects.
-Then, the authors describe how the ATE estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h(\vec{D}, i)$.
+That is, a treated unit's treatment effect is defined as the direct effect \textit{and} the general equilibrium spillover effects.
+Then, the authors describe how the average treatment effect (ATE) estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h(\vec{D}, i)$.
 My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.\footnote{These estimates can be combined afterwards to estimate their definition of average treatment effect.
@@
 For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly.
+My paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
 
@@
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
+Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_Sant’Anna_2020}.
 

### 2021-01-28 latex/paper/Spillover.tex
Revise Theory Section
Improved writing with many small edits

@@
 Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards.
-As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$, denoted $Y_{i,t}(D_i, h(\vec{D}, i)$), are a function of own treatment-status $D_i$ and,  departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+This framework can be extended in section \ref{sec:event_study}.
+As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+The potential outcomes are denoted $Y_{i,t}(D_i, h(\vec{D}, i)$).
 The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function.
-The `exposure mapping' measures the intensity at which unit $i$ is affected by spatial spillovers.
+The exposure mapping measures the intensity at which unit $i$ is affected by spatial spillovers.
 When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = 0$.
-The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment which are summarized by $h(\vec{D}, i)$.
+The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment as summarized by $h(\vec{D}, i)$.
+To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature.
 
-To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature.
 First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
-In this case \[
+In this case \begin{equation}\label{eq:h_within}
     h(\vec{D}, i) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
-\] 
+\end{equation}
 This exposure mapping is useful when it is assumed that spillovers do not decay over distance until $\bar{d}$ and the number of neighboring units treated do not impact the intensity of spillovers.
@@
 In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library.
-Access to a neighboring town library likely does not depend on whether you can access 1 or more nearby libraries, so the binary value is a good approximation to spillovers in this context.
+Access to a neighboring town library is binary in nature, so it does not matter whether you can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
 
-Second, $h(\vec{D}, i)$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \[
+Second, $h(\vec{D}, i)$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \begin{equation}\label{eq:h_within}
     h(\vec{D}, i) = 1/k \sum_{j \in K(i)} D_j,
-\]
+\end{equation}
 where $K(i)$ is the index of unit $i$'s k-nearest neighbors.
@@
 In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies.
-As more nearby counties receive new factories, the agglomeration forces increase \citep{Basker_2005}.
+As more nearby counties receive new stores, the agglomeration forces increase \citep{Basker_2005}.
 
-Last, is the spatial decay function where exposure decreases with distance. In this case, spillover intensity is the sum across all treated observations' decay term, i.e. \[ 
+Last, is the spatial decay function where exposure decreases with distance.
+In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
+\begin{equation}\label{eq:h_decay}
     h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
-\] 
+\end{equation} 
 This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units.
 This creates problems with inference because it implies potential correlation between all units' error terms.
-For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be decided by the researcher or estimated using non-linear least squares.
+For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using non-linear least squares.
 In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
 
-The last thing a researcher must do is specify the functional form of the potential outcomes.
+After chosing an exposure mapping that makes sense in the economic context, a researcher must also specify the functional form of the potential outcomes.
 Typically, the spillover function enters into the regression linearly and potentially the coefficient is allowed to differ by treatment status.
@@
 It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences.
-I assume that what the `Average Treatment Effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
+I assume that what the `average treatment effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
     \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, 0) - Y_{it}(0, 0) \ \vert \ D_i = 1 \right],
@@
 
-My definition of the direct effect of treatment differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the Average Treatment Effect as \[ 
+My definition of the direct effect of treatment differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the average treatment effect as \[ 
     \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(0, h(\vec{D}, i)) \ \vert \ D_i = 1 \right],
@@
 
-In this section, I identify the two sources of bias in difference-in-differences estimation.
+In this section, I identify the two sources of bias in difference-in-differences estimation of the direct effect of treatment.
 For exposition, I will refer to one pre- and post-period, $t = 0$ and $t = 1$, but this can be replaced by averages across $Y$ in the pre-period and the post-period respectively.
@@
 
-\begin{assumption}[Parallel Counterfactual Trends]\label{parallel}
+\begin{assumption}[Parallel Counterfactual Trends]\label{eq:parallel}
     \[ 
@@
 
-Given that Assumption \ref{parallel} holds, the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} can be decomposed as the direct effect and the two sources of spillover bias.
+Given that Assumption (\ref{eq:parallel}) holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias.
 The proof is given in Appendix \ref{sec:proofs}.
@@
 \begin{theorem}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
-    If Assumption \ref{parallel} holds, the expectation of the estimate $\hat{\tau}$ from Equation \ref{eq:twfe} is
+    If Assumption (\ref{eq:parallel}) holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
     \begin{align*}
@@
 
-The previous section finds an explicit form of the bias when estimating Equation \ref{eq:twfe}.
+The previous section finds an explicit form of the bias when estimating (\ref{eq:twfe}).
 The explicit form of bias can be used by researchers to provide bounds on the bias in a manner simmilar to \citet{Rambachan_Roth_2020}.
@@
 This specification is a simple one in that the spillover is not additive in the number of nearby treated counties and does not decay over distance before reaching $\bar{d}$.
-Since treated counties have access to their own library, I will assume that no spillovers exist.
+Since treated counties have access to their own library, I will assume that no spillovers on to treated units exist.
 The potential outcome is assumed to be additive in both treatment and in the exposure mapping:
@@
 
-If a researcher estimates Equation \ref{eq:twfe}, then the bias will be \[ 
+If a researcher estimates (\ref{eq:twfe}), then the bias will be \[ 
     - \tau_{\text{spill,control}} = - \beta_{\text{spill,control}} \frac{\sum_{i: D_{it} = 0} \text{Near}_{it}}{N_C},
@@
 Simply put, the bias will be negative one times the proportion of control units that receive spillover effects time the size of the effect on control units.
-Then the bound can be created by conservatively set by bounding $\beta_{\text{spill,control}}$ and the proportion of control units that receive spillovers.
+Then the bound can be created by bounding $\beta_{\text{spill,control}}$ and the proportion of control units that receive spillovers.
 
@@
 Inference on this set can be done using Fixed-Length Confidence Intervals as in \citet{Rambachan_Roth_2020}.
-The confidence interval can be formed using critical values from the Z-distribution and  standard normal critical values since we are assuming a specific spatial relationship between outcomes, spatially adjusted standard errors following \citet{Conley_1999}: \[
+The confidence interval can be formed using standard normal critical values and spatially adjusted standard errors following \citet{Conley_1999} since we are assuming a specific spatial relationship between outcomes: \[
     \left[ \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}\right].  
@@
 
-The previous section shows how to estimate the magnitude of potential bias in the estimation of Equation \ref{eq:twfe}.
+The previous section shows how to estimate the magnitude of potential bias in the estimation of (\ref{eq:twfe}).
 However, parameterization of the potential outcomes and exposure mapping allows for unbiased estimates of $\tau_{\text{direct}}$ by controlling for the exposure mapping directly.
@@
 First, it will not include the neighboring units' benefit in the calculation.
-Second, since the treatment effect will subtract the neighboring units' benefit, the neighboring units' beneift will be \emph{double undercounted}.
-Similarly, the net benefits for a treated location depend on the direct effect and the spillover effect onto treated units.
-Therefore the size of benefits created by the treatment depend on the number of treated units nearby.
+Second, since the treatment effect will subtract the neighboring units' benefit, the neighboring units' benefit will be \emph{double undercounted}.
+Similarly, a policy maker trying to determine the net benefits for a treated location must consider the direct effect and the spillover effect onto treated units.
+This is because the size of benefits created by the treatment depend on the number of treated units nearby.
 
-There are a few practical considerations researchers should make when parametrizing the spillovers. 
-% @TODO: Expand upon considerations in the introduction
+There are a few practical considerations researchers should make when parametrizing the spillovers and the answers to the questions will depend ultimately on the economic context being studied.
+First, researchers should consider whether control units and/or treated units experience effects from the treatment status of other units.
+For example, in the context of library construction, treated units likely do not experience spillovers while close control units do.
+In the context of factory openings, both control and treated units likely experience spillovers.
 
-In a set of Monte Carlo simulations, I check the sensitivity of estimates to misspecification of spillovers.
+Second, a researcher must decide how far the spillovers can reasonably be experience and whether the effect decays over distance.
+Things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
+There are two commonly used techniques to model treatment effect decay.\footnote{If the spillovers is due to crossing borders into the treated area, then a reasonable decision about whether the effect decays is the frequency in which people use the good.
+For example, libraries whose benefit is only experienced from frequent usage would suggest that the effect decays over distance.
+On the other hand, abortion clinics opening are used infrequently and therefore the effect likely doesn't decay over distance within a certain cutoff.} First, as seen above is to use an exponential decay function with regards to distance.
+The other option is to use a set of `cocentric donut' indicators which are easy to interpret.
+An example of this is shown in the empirical application in Section \ref{sec:tva}.
+
+Last, it is important for estimation to know if the spillovers are additive or non-additive in nature.
+If the number of nearby treated units matter, then the exposure mapping should sum over nearby treated units in some way.
+For example, in the context of library construction, the number of neighbors with libraries does not change the size of the spillover for it is access to \textit{any} library that matters.
+In the context of factory openings, though, agglomeration economies imply that the spillovers are additive in nature.
 

### 2021-01-28 latex/paper/Spillover.tex
Edited Monte Carlo Simulations
Improved readability

@@
 
+I now turn to a series of Monte Carlo Simulations to highlight the importance for controlling for spillovers in simulations.
+I use the set of counties in the contiguous United States and the data generating process used is defined by the exposure mapping given in (\ref{eq:example_exposure}) with cutoff distance $\bar{d} = 40$ miles and the data generating process given in (\ref{eq:example_po}).
+A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
+The intercepet is $\alpha = -2$, the fixed effects are generated by $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$, and the error term is $\varepsilon \sim N(0, 2^2)$.
+Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
+
+For the first simulation, I restrict spillovers only to occur among control units, i.e.
+$\beta_{\text{spill, treat}} = 0$, and estimate the two-way fixed effects model, (\ref{eq:twfe}).
+This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
+I assign treatment among counties randomly with various unconditional probabilities between 3 percent and 50 percent.
+The DGP is therefore
+\begin{equation}
+    \label{eq:dgp1} 
+    y_{it} = \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill, control}} (1-D_{it}) \text{Near}_{it} + \varepsilon_{it}   
+\end{equation}
+
 \begin{figure}[tb!]
@@
     {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp1}.
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp1}.
 Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
@@
 
-I now turn to a series of Monte Carlo Simulations to highlight the importance for controlling for spillovers in simulations.
-The data generating process used is defined by the exposure mapping given in Equation \ref{eq:example_exposure} and the data generating process given in Equation \ref{eq:example_po}.
-A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
-The intercepet is $\alpha = -2$, the fixed effects are $\mu_t \sim N(t * 0.2, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$, and the error term is $\epsilon \sim N(0, 2^2)$.
-Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
-
-For the first simulation, I restrict spillovers only to occur among control units, i.e.
-$\beta_{\text{spill, treat}} = 0$ and estimate the typical two-way fixed effects model.
-This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
-I assign treatment among U.S.
-counties randomly with various probabilities between 3 percent and 50 percent.
-The DGP is therefore
-\begin{equation}
-    \label{dgp1} 
-    y_{it} = -2 + \mu_t + \mu_i + 2 D_{it} - (1-D_{it}) \text{Near}_{it} + \varepsilon_{it}   
-\end{equation}
-
-The size of the bias from estimating Equation \ref{eq:twfe} at different treatment probabilities are presented in Figure \ref{fig:bias_as_treat_prob} as the line with diamond markers.
+The size of the bias from estimating the two-fixed effects model, (\ref{eq:twfe}), at different treatment probabilities are presented in Figure \ref{fig:bias_as_treat_prob} as the line with diamond markers.
+Each point represents a set of 10,000 simulation and displays the mean bias as well as a 95 percent empirical confidence interval.
 As displayed in the figure, even for a low treatment probability of three percent, the bias is quite large with a 95 percent empirical confidence interval between -0.28 and -0.75.
 As treatment frequency increases, the bias increases as well but at a slower rate due to fewer additional control units receiving spillover units.
-This is in part due to the assumption that spillovers are not additive in the number of nearby units treated.
+The slow increase in bias is in part due to the assumption that spillovers are not additive in the number of nearby units treated.
 
 A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers.
-I do this in Figure \ref{fig:bias_as_treat_prob} and the results are shown by the line with circle markers.
-Even though I remove contiguous control counties which is not the correct measure of $h(\vec{D}, i)$, contiguous counties approximates it well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
-As the portion of control units receiving spillovers that are kept in the sapmle increases, the bias would fall between the two lines.
+To do this, I remove contiguous control counties which is a close, but misspecificied, measure of $h(\vec{D}, i)$.
+The results are shown in Figure \ref{fig:bias_as_treat_prob} by the line with circle markers.
+Even though the exposure mapping is misspecified, contiguous counties approximates the true exposure mapping well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
+However, if the distance cutoff $\bar{d}$ were larger, more control units would remain in the sample that experience non-zero exposures.
+In this case, the bias would fall between the two lines.
 
@@
 As the treatment probability increases, the number of control units removed increases as well.
-This naturally yields a more variable estimator as seen in the wider 95 percent empirical confidence intervals.
+This naturally yields a more variable estimator as seen in the wider 95 percent empirical confidence intervals in Figure \ref{fig:bias_as_treat_prob}.
+This trade-off can be avoided altogether by parameterizing the spillovers and including them in estimation directly.
 
@@
 For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
-\begin{equation}
-    \label{dgp2} 
-    y_{it} = -2 + \mu_t + \mu_i + 2 D_{it} - (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
+\begin{equation}\label{eq:dgp2} 
+    y_{it} = \mu_t + \mu_i + 2 D_{it} + (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
 \end{equation} 
@@
     \label{fig:kriging}
-    {\centering
-        \resizebox{\textwidth}{!}{
+    \begin{center}
+        \resizebox{0.8\textwidth}{!}{
             \includegraphics{../../figures/figure-krig.png}
         } 
-    }
+    \end{center}
+
     {\footnotesize
@@
     }
+
     {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating Equation \ref{eq:twfe} for data generated as described in the text and Equation \ref{dgp2}.
-Treatment probability is assigned according to the method described by the text and Equation \ref{eq:cond_prob}.
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp2}.
+Treatment probability is assigned according to the method described by the text and (\ref{eq:cond_prob}).
 Each point corresponds to the average bias for the given Zone Plus and the band is the 95 percent empirical confidence interval over 1000 simulations.
@@
 For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
-Then I assign treatment with a probability that differs based on Zone.
-The unconditional probability is equal to 5 percent in all simulations.
-To do this, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment:
+Then I assign treatment with a probability that differs based on $\text{Zone}_i$.
+To avoid changes in bias due to a difference in the number of treated units, the unconditional probability is equal to 5 percent in all simulations.
+
+To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
 \begin{equation}
     \label{eq:cond_prob}
-    P(D_i \ \vert \ \text{Zone}_i) = (.1 + \text{Zone Plus} * \text{Zone}_i) \times \frac{.05}{.1 * .9 + (.1 + \text{Zone Plus}) * .1}
+    P(D_i \ \vert \ \text{Zone}_i) = (.05 + \text{Zone Plus} * \text{Zone}_i) \times \underbrace{\frac{.05}{.05 * .9 + (.05 + \text{Zone Plus}) * .1}}_{\text{Normalize } P(D_i) = 0.05}
 \end{equation}
 The second term normalizes probabilities so the unconditional probability stays at five percent.
-In our simulations, Zone Plus ranges from 0 which is the case where p = five percent for all counties to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.0166 + 0.35 * \text{Zone}_i$
+In our simulations, Zone Plus ranges from 0 which is the case where $P(D_i \vert \text{Zone}_i) = P(D_i) = 0.05$ to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.01 + 0.41 * \text{Zone}_i$.
 
@@
 The line with diamond markers is run on the full sample.
-As the level of spatial autocorrelation increases, the bias actually decreases.
+As the level of spatial autocorrelation increases, the bias surprisingly decreases.
 The reason for this is that as treatment becomes more concentrated in the `Zones', the number of control units receiving spillovers decreases while the number of treated units receiving spillovers increases.

### 2021-01-28 latex/paper/Spillover.tex
Revise TVA

@@
 % ------------------------------------------------------------------------------
-\section{Application in Urban Economics}
+\section{Application in Place-Based Policy Analysis}
 \label{sec:tva}
@@
 
-\citet{Kline_Moretti_2014} estimate Equation \ref{eq:tva} to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
+\citet{Kline_Moretti_2014} estimate (\ref{eq:tva}) to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
 However, their point estimates compare, in part, changes in outcomes in TVA counties with changes in outcomes for neighboring counties that likely were impacted by the large-scale program.
@@
 The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority.
-If specification \ref{eq:tva_spillover} is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect.
+If specification (\ref{eq:tva_spillover}) is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect.
 As shown above, minor misspecification will remove some but not all of the bias from standard difference-in-differences estimates.
@@
 The following columns contain point estimates for $\tau$ and $\delta_s$ in different specifications and can be interpreted as decadel growth rates in outcomes.
-The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for Equation \ref{eq:tva}.
+The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for (\ref{eq:tva}).
 The two columns are very close in magnitude to each other.
@@
 
-                & \multicolumn{1}{c}{\textbf{Kline \& Moretti (2011)}} &
+                & \multicolumn{1}{c}{\textbf{\citet{Kline_Moretti_2014}}} &
                 \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
@@
 The column labeled \citet{Kline_Moretti_2014} replicates the Oaxaca-Blinder estimator found in column (3) of Table III.
-The column labeled `Diff-in-Diff' estimates Equation \ref{eq:tva} by OLS.
-The final four columns labeled `Diff-in-Diff with Spillovers' are estimates from Equation \ref{eq:tva_spillover}.
+The column labeled `Diff-in-Diff' estimates (\ref{eq:tva}) by OLS.
+The final four columns labeled `Diff-in-Diff with Spillovers' are estimates from (\ref{eq:tva_spillover}).
 
@@
 
-Turning to the last four columns that estimate Equation \ref{eq:tva_spillover}, column (3) contains a point estimate for $\tau$ and and columns (4)-(6) contain point estimates of the spillover effects $\delta_d$.
+Turning to the last four columns that estimate (\ref{eq:tva_spillover}), column (3) contains a point estimate for $\tau$ and and columns (4)-(6) contain point estimates of the spillover effects $\delta_d$.
 For agricultural employment, our point estimates show there was a decline in agriculture employment in control units near the Authority.

### 2021-01-31 helper-sim_function_misspecification.R
Add MSPE for Spillovers

@@ -40,9 +40,9 @@ sim_data_misspecification <- function(
 	within_large <- (dist_mi > 0 & dist_mi <= treat_spillover_distance_large)
 	within_100 <- (dist_mi > 0 & dist_mi <= 100)
 	
-	within_0_10 = (dist_mi > 0 & dist_mi <= 10)
-	within_10_20 = (dist_mi > 10 & dist_mi <= 20)
-	within_20_40 = (dist_mi > 20 & dist_mi <= 40)
+	within_0_20 = (dist_mi > 0 & dist_mi <= 20)
+	within_20_30 = (dist_mi > 20 & dist_mi <= 30)
+	within_30_40 = (dist_mi > 30 & dist_mi <= 40)
 	within_40_60 = (dist_mi > 40 & dist_mi <= 60)
 	within_60_80 = (dist_mi > 60 & dist_mi <= 80)
 	within_80_100 = (dist_mi > 60 & dist_mi <= 80)
@@ -50,7 +50,7 @@ sim_data_misspecification <- function(
 	
 	# Spatial Decay
 	# Following https://fmwww.bc.edu/repec/bocode/s/spgen.pdf
-	spatial_decay <- exp(-.01 * dist_mi) 
+	spatial_decay <- exp(-.02 * dist_mi) 
 	
 	# Cutoff by element-wise multiplication & no self-spillover
 	spatial_decay <- spatial_decay * within_large
@@ -104,12 +104,12 @@ sim_data_misspecification <- function(
 			spill_decay_additive_treat = (treat == 1) * spatial_decay %*% treat,
 			spill_decay_additive_treat = as.numeric(spill_decay_additive_treat),
 			# Spillover Rings
-			spill_0_10 = (treat == 0) * within_0_10 %*% treat,
-			spill_0_10 = as.numeric(spill_0_10 > 0),
-			spill_10_20 = (treat == 0) * within_10_20 %*% treat,
-			spill_10_20 = as.numeric(spill_10_20 > 0),
-			spill_20_40 = (treat == 0) * within_20_40 %*% treat,
-			spill_20_40 = as.numeric(spill_20_40 > 0),
+			spill_0_20 = (treat == 0) * within_0_20 %*% treat,
+			spill_0_20 = as.numeric(spill_0_20 > 0),
+			spill_20_30 = (treat == 0) * within_20_30 %*% treat,
[…]

### 2021-01-31 sim-misspecification_of_spillover.R

@@ -47,24 +47,72 @@ load(file= "data/counties_and_mat.RData")
 
 
 
-# Helper function estimate
-estimate_treatment_effect <- function(data, formula, treat_var){
-	feols(formula, data= data) %>%
-		coefficients() %>% .[[treat_var]]
+## Experimentation
+
+df <- sim_data_misspecification(drop_geometry=FALSE) %>% 
+	st_as_sf()
+
+# Check treatment effects with optional center of population dots
+ggplot(data = df %>% filter(year == 2019)) + 
+	geom_sf(mapping = aes(fill = te_spill_decay, color = as.factor(treat))) + 
+	# geom_sf(mapping = aes(geometry = centroid), color="white", size= 0.25) +
+	scale_color_manual(values = c("black", "red"))
+
+
+
+## Exerimentation
+
+for(i in 1:10) {
+	
+df <- sim_data_misspecification(drop_geometry=FALSE) %>% 
+	st_as_sf()
+	
+y <- "spill_decay"
+x <- "spill_within_large"
+
+# Donuts 80
+formula <- as.formula(glue("y_{y} ~ treat_ind + post:spill_0_20 + spill_20_30:post + spill_30_40:post ", 
+						   "+ spill_40_60:post + spill_60_80:post | state_county + year"))
+
+reg <- feols(formula, data= df %>% st_drop_geometry()) 
+
+coef <- reg %>% coefficients()
+b_0_20 <- coef[2]
+b_20_30 <- coef[3]
+b_30_40 <- coef[4]
+b_40_60 <- coef[5]
+b_60_80 <- coef[6]
+
+var <- as.character(glue("te_{y}"))
+
+# Within 80
+formula <- as.formula(glue("y_{y} ~ treat_ind + ({x}:post) | state_county + year"))
+
+reg <- feols(formula, data= df %>% st_drop_geometry()) 
+coef <- reg %>% coefficients()
+b <- coef[2]
+
+var <- as.character(glue("te_{y}"))
+
+df <- df %>%
+	mutate(
+		te_spill_hat_within_large = b * !!rlang::sym(x),
+		te_spill_hat_donut = b_0_20 * spill_0_20 + b_20_30 * spill_20_30 + b_30_40 * spill_30_40 + b_40_60 * spill_40_60 + b_60_80 * spill_60_80
+	)
+
+temp1 <- df %>% filter(year == 2019 & treat == 0) %>% pull(te_spill_decay)
[…]

### 2021-02-12 figure-gen_map_examples_with_bias.R
Update Figures for slides

@@ -27,8 +27,8 @@ source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_them
 
 # Is for slides or paper?
 slides <- TRUE
-# h_w_ratio <- 9/16
-h_w_ratio <- 3/4
+h_w_ratio <- 9/16
+# h_w_ratio <- 3/4
 
 
 ## Load Parameters -------------------------------------------------------------
@@ -158,53 +158,6 @@ counties_treat_low_zp <- sim_data(
 	spatial_autocorr = TRUE, zone_plus = low_zone_plus, drop_geometry = FALSE
 ) %>% 
 	filter(year == 2019) %>% select(-centroid) %>% st_as_sf()
-	
-
-bias_control <- round(te_spill * sum(counties_treat_low_zp$spill_within) / sum(counties_treat_low_zp$treat_ind == 0), 2)
-bias_treat <- round(te_spill_treat * sum(counties_treat_low_zp$spill_within_treat) / sum(counties_treat_low_zp$treat_ind == 1), 2)
-
-
-# Treatment Effect Maps, spcorr_low_zp
-(
-plot_te_low_zp <- ggplot() +
-	geom_sf(data= counties_treat_low_zp, aes(fill= as.factor(te)), color= "grey60", size= 0.2) + 
-	geom_sf(data= counties_treat_low_zp %>% filter(treat_ind == 1), fill = NA, color = "black") +
-	geom_sf(data= us, fill = NA, color= "grey30", size= 0.2) + 
-	# Remove Coordinates, leaving just the map
-	coord_sf(datum = NA) +
-	labs(
-		title= "Small Spatial Autocorrelation",
-		subtitle= glue::glue("Treatment Effect Estimate: {estimate} \n Spatial Autocorrelation Measure = {low_zone_plus}"),
-		fill= "Effect Size"
-	) + 
-	theme_kyle(slides = TRUE) + 
-	# Put Legend on Bottom
-	guides(fill = guide_legend(title.position = "top", nrow = 4)) +
-	# theme(legend.position = "bottom") +
-	# Fill Scale, colors from R color Brewer
-	scale_fill_manual(values= c("0" = "#ffffff", "1" = "#FBB4B9", "1.5" = "#F768A1", "2" = "#C51B8A")) 
-)
-
-
-(
-plot_te_spill_control_low_zp <- ggplot() +
[…]

### 2021-02-12 helper-sim_function_misspecification.R

@@ -93,6 +93,11 @@ sim_data_misspecification <- function(
 			spill_within_additive = as.numeric(spill_within_additive),
 			spill_within_additive_treat = (treat == 1) * within %*% treat,
 			spill_within_additive_treat = as.numeric(spill_within_additive_treat),
+			# Within Large Additive
+			spill_within_large_additive = (treat == 0) * within_large %*% treat,
+			spill_within_large_additive = as.numeric(spill_within_large_additive),
+			spill_within_large_additive_treat = (treat == 1) * within_large %*% treat,
+			spill_within_large_additive_treat = as.numeric(spill_within_large_additive_treat),
 			# Decay (Closest) w/ Cutoff Length 
 			spill_decay = (treat == 0) * apply(spatial_decay * kronecker(matrix(1,n(),1), t(treat)), 1, max),
 			spill_decay = as.numeric(spill_decay),
@@ -122,6 +127,13 @@ sim_data_misspecification <- function(
 			spill_40_60 = as.numeric(spill_40_60 == 1 & (spill_30_40 == 0) & (spill_20_30 == 0) & (spill_0_20 == 0)),
 			spill_60_80 = as.numeric(spill_60_80 == 1 & (spill_40_60 == 0) & (spill_30_40 == 0) & (spill_20_30 == 0) & (spill_0_20 == 0)),
 			spill_80_100 = as.numeric(spill_80_100 == 1 & (spill_60_80 == 0) & (spill_40_60 == 0) & (spill_30_40 == 0) & (spill_20_30 == 0) & (spill_0_20 == 0)),
+			# Spillover Rings Additive
+			spill_0_20_additive = (treat == 0) * within_0_20 %*% treat,
+			spill_20_30_additive = (treat == 0) * within_20_30 %*% treat,
+			spill_30_40_additive = (treat == 0) * within_30_40 %*% treat,
+			spill_40_60_additive = (treat == 0) * within_40_60 %*% treat,
+			spill_60_80_additive = (treat == 0) * within_60_80 %*% treat,
+			spill_80_100_additive = (treat == 0) * within_80_100 %*% treat
 		)
 	
 	## Spillover Variables Have Same Average Effect ----------------------------
@@ -132,6 +144,7 @@ sim_data_misspecification <- function(
 			spill_within = 1/4 * treat_effect_spill * spill_within / mean(spill_within),
 			spill_within_large = 1/4 * treat_effect_spill * spill_within_large / mean(spill_within_large),
[…]

### 2021-02-12 sim-bias_as_treat_increase.R

@@ -29,6 +29,9 @@ source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd4
 # Export
 export <- TRUE
 slides <- FALSE
+h_w_ratio <- 9/16
+# h_w_ratio <- 3/4
+
 
 
 ## Load Spatial Data -----------------------------------------------------------
@@ -199,10 +202,10 @@ if(!slides) {
 bias_plot
 
 if(export & slides) ggsave("figures/figure-bias_from_prob_treat_slides.png", plot= bias_plot, 
-	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+	   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 
 if(export & !slides) ggsave("figures/figure-bias_from_prob_treat.png", plot= bias_plot, 
-						   dpi= 300, width= 2400/300, height= 1800/300, bg= "transparent")
+						   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "transparent")
 
 
 ## Plot Bias with and without removing spillover -------------------------------
@@ -277,7 +280,8 @@ bias_fix_plot
 
 
 if(export & slides) ggsave("figures/figure-bias_fix_slides.png", plot= bias_fix_plot, 
-	   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+	   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
+
 
 if(export & !slides) ggsave("figures/figure-bias_fix.png", plot= bias_fix_plot, 
-		dpi= 300, width= 2400/300, height= 1800/300, bg= "transparent")
+		dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "transparent")

### 2021-02-12 sim-bias_from_spatial_autocorr.R

@@ -27,9 +27,10 @@ source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd4
 
 # Export
 export <- TRUE
-
-# Produce figures for slides?
 slides <- TRUE
+h_w_ratio <- 9/16
+# h_w_ratio <- 3/4
+
 
 ## Load Spatial Data -----------------------------------------------------------
 # From data-prepare_counties.R
@@ -196,10 +197,10 @@ bias_plot
 
 
 if(export & slides) ggsave("figures/figure-bias_from_spatial_autocorr_slides.png", plot= bias_plot, 
-						   dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+						   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 
 if(export & !slides) ggsave("figures/figure-bias_from_spatial_autocorr.png", plot= bias_plot, 
-							dpi= 300, width= 2400/300, height= 1800/300, bg= "transparent")
+							dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "transparent")
 
 
 
@@ -275,7 +276,7 @@ bias_fix_plot
 
 
 if(export & slides)  ggsave("figures/figure-bias_fix_spatial_autocorr_slides.png", plot= bias_fix_plot, 
-							dpi= 300, width= 2400/300, height= 1800/300, bg= "#ECECEC")
+							dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 
 if(export & !slides)  ggsave("figures/figure-bias_fix_spatial_autocorr.png", plot= bias_fix_plot, 
-							 dpi= 300, width= 2400/300, height= 1800/300, bg= "transparent")
+							 dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "transparent")

### 2021-02-12 sim-misspecification_of_spillover.R

@@ -136,13 +136,14 @@ estimate_treatment_effect <- function(df, formula, treat_var){
 }
 
 
-n_trials <- 250
+n_trials <- 100
 doParallel::registerDoParallel(10)
 
 dgp_types <- c(
 	"Within 40mi." = "spill_within", 
 	"Within 80mi." = "spill_within_large", 
-	"Within (Additive)" = "spill_within_additive", 
+	"Within 40mi. (Additive)" = "spill_within_additive", 
+	"Within 80mi. (Additive)" = "spill_within_large_additive", 
 	"Decay" = "spill_decay", 
 	"Decay (Additive)" = "spill_decay_additive"
 )
@@ -152,11 +153,13 @@ estimation_types <- c(
 	"Within 40mi." = "spill_within", 
 	"Within 80mi." = "spill_within_large", 
 	"Within 100mi." = "spill_within_100",
-	"Within (Additive)" = "spill_within_additive", 
+	"Within 40mi. (Additive)" = "spill_within_additive", 
+	"Within 80mi. (Additive)" = "spill_within_large_additive", 
 	"Decay" = "spill_decay", 
 	"Decay (Additive)" = "spill_decay_additive",
 	"Donuts (0-20, 20-30, 30-40)" = "donuts_small",
-	"Donuts (0-20, 20-30, 30-40, 40-60, 60-80)" = "donuts"
+	"Donuts (0-20, 20-30, 30-40, 40-60, 60-80)" = "donuts",
+	"Donuts (0-20, 20-30, 30-40, 40-60, 60-80) (Additive)" = "donuts_additive"
 )
 
 results <- foreach(i = 1:n_trials, .combine = 'rbind') %dopar% {
@@ -172,6 +175,9 @@ results <- foreach(i = 1:n_trials, .combine = 'rbind') %dopar% {
 			} else if(x == "donuts") {
 				formula <- as.formula(glue("y_{y} ~ treat_ind + spill_0_20:post + spill_20_30:post + spill_30_40:post ", 
 										   "+ spill_40_60:post + spill_60_80:post | state_county + year"))
+			} else if(x == "donuts_additive") {
+				formula <- as.formula(glue("y_{y} ~ treat_ind + spill_0_20_additive:post + spill_20_30_additive:post + spill_30_40_additive:post ", 
+										   "+ spill_40_60_additive:post + spill_60_80_additive:post | state_county + year"))
[…]

### 2021-02-12 latex/paper/Spillover.tex
Add section on misspecification of spillovers

@@
 The reason for this is that as treatment becomes more concentrated in the `Zones', the number of control units receiving spillovers decreases while the number of treated units receiving spillovers increases.
-In this particular DGP, the effect of fewer control units on the bias is larger than the bias from more treated units.
+In this particular data-generating process, the effect of fewer control units on the bias is larger than the bias from more treated units.
 
@@
 % ------------------------------------------------------------------------------
-% \subsection{Misspecification of Spillovers}
+\subsection{Misspecification of Spillovers}
 % ------------------------------------------------------------------------------
 
-% @TODO
+Now we turn to simulations where we include potentially incorrectly specified exposure mappings and see their performance in a set of different data generating processes.
+In the general form, I generate data with the same fixed effects and error term as before, but for many different exposure mappings $h(\vec{D}, i)$
+\begin{equation}\label{eq:dgp_general}
+    y_{it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it}   
+\end{equation}
+
+In order to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are qualitatively the same.
+For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
+The goal of this exercise is to see which specifications perform well under broad classes of spillovers.
+
+The set of spillover specifications include `Within $x$mi.' which equals 1 if the counties' center of population is within $x$ miles to a treated county's center of population, and `Within $x$mi.
+(Additive)' is the number of treated county's within $x$ miles of the control county.
+`Decay' is given by $\max_j D_j e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$ and `Decay (Additive)' is given by Equation (\ref{eq:h_decay}) with $\alpha = 0.02$.
+
+The last set of spillover specifications is commonly used in the literature as a semi-parametric estimator and are referred to as `Donuts` or `Rings'.
+These consist of a set of indicators for falling within distance bins from the nearest treated unit (e.g.
+indicators for being between 0-20, 20-40, and 40-60 miles to closest treated unit).
+This approach is worth discussing in more detail because it will turn out to be the most consistent approach.
+These donuts are able to trace out all of the non-additive spillovers so long as the distance bins are numerous enough.
+For example, the donuts indicators add up to all the `Within xmi.' specifications if there are enough rings.
+The donuts can also trace out the decaying spillovers with the coefficients on each indicator decreasing in an exponential way.
+Donuts that go further than the maximum spillover distance will be estimated near zero, so adding too many rings is not a large concern.
+The last specification is an additive version of `Donuts' which is the number of treated units within each distance bin.
+
+\begin{table}[!tb]
+    \caption{Bias from Misspecification of Spillovers}
+    \label{tab:misspecification}
+
+    \begin{adjustbox}{width = 1.1\textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} l rrrrrr @{}}
+                % Head
+                \toprule
+                & \multicolumn{6}{c}{Data-Generating Process} \\
+                \cmidrule{2-7}
+
+                & \multicolumn{1}{c}{\textbf{Within 40mi}} & \multicolumn{1}{c}{\textbf{Within 80mi}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay}} & \multicolumn{1}{c}{\textbf{Decay}} \\
+                Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
+
+                % Body
+                \midrule
+
+                \input{../../tables/misspecification.tex}
+
+                \bottomrule
+            \end{tabular}
+
+            % Notes 
+            \begin{tablenotes}\footnotesize
+                \item \textit{Notes.} Each cell corresponds to the mean bias from 1000 simulations of the data generating process specified by the column header and under the specification given by Equation (\ref{eq:dgp_general}) by the row label.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
+The results of the simulations are produced in Table \ref{tab:misspecification}.
+For each entry in the table, the column label corresponds to the true exposure mapping used in the data-generating process and the row label corresponds to the exposure mapping, $\tilde{h}(\vec{D}, i)$, used in estimation.
+The corresponding cell gives the mean bias from estimating Equation (\ref{eq:dgp_general}) with the $\tilde{h}(\vec{D}, i)$.
+
+The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed effect estimate and in particular, correctly specifying the data-generating process removes almost all the bias.
+The second result is that both the `Donuts' and the `Within' specification do the best amongst all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers.
+This is due to the fact that indicator variables will correctly identify the average spillovers onto control units if they cover all the affected control units.
+If researchers are primarily interested in identifying the direct effect, then either `Donuts' or `Within' specifications with a large cutoff distance are preferred as they remove almost all bias in all settings.
+
+However, we will now turn to seeing how these misspecifications are able to capture the spillovers themselves, and we will see that `Donuts' are superior to `Within' indicators in their ability to trace out spillovers, so they should be the default used by researchers unless there is theoretical motivation to use any specific parametrization for exposure mapping.
+For the next table, for each control county, I will predict their spillover value from the point estimates on $\tilde{h}(\vec{D}, i)$.
+Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (to make numbers comparable across data-generating processes), \[
+    1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}.
+\] This will produce a percentage of spillovers that are explained by the specification, so numbers closer to 1 represent better modelling of the spillovers.
+
+\begin{table}[!tb]
+    \caption{Percent of Spillovers Predicted by Specification}
+    \label{tab:misspecification_mspe}
+
+    \begin{adjustbox}{width = 1.1\textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} l rrrrrr @{}}
+                % Head
+                \toprule
+                & \multicolumn{6}{c}{Data-Generating Process} \\
+                \cmidrule{2-7}
+
+                & \multicolumn{1}{c}{\textbf{Within 40mi}} & \multicolumn{1}{c}{\textbf{Within 80mi}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay}} & \multicolumn{1}{c}{\textbf{Decay}} \\
+                Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
+
+                % Body
+                \midrule
+
+                \input{../../tables/misspecification_mspe_percent.tex}
+
+                \bottomrule
+            \end{tabular}
+
+            % Notes 
+            \begin{tablenotes}\footnotesize
+                \item \textit{Notes.} Each cell corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects from 1000 simulations of the data generating process specified by the column header and under the specification given by Equation (\ref{eq:dgp_general}) by the row label.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
+Results are presented in Table \ref{tab:misspecification_mspe}.
+For each specification, correctly specifying the spillovers produces the best estimates for spillovers as expected.
+Among misspecified exposure mapping, `Donuts' that are large enough to caputre all the spillovers perform better than all other specifications in all non-additive data-generating processes.
+When the spillovers are additive, the predicted spillovers from the non-additive donut specifications do not as accurately measure these spillovers as they did before.
+
+For additive data-generating processes, `Within (Additive)' and `Decay (Additive)' don't do a great job at predicting spillovers for the other data-generating process.
+On the other hand, the additive version of donuts sucessfully predicts spillovers in both additive data-generating processes.
+Therefore, the most important aspect of correctly estimating spillovers is to consider whether they are additive in the number of treated units or not.
+Researchers should use a version of donuts either way.
 

### 2021-02-12 latex/paper/Spillover.tex
Add event study and Conclusion

@@
 % ------------------------------------------------------------------------------
+\section{Event Study with Spillovers}
+\label{sec:event_study}
+% ------------------------------------------------------------------------------
+
+The intuition from how spillovers cause biases in estimates of the direct effect of treatment extend into the setting where there is staggered adoption in treatment.
+Two-way fixed effects estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates and therefore the bias terms will be identically weighted of the bias terms from the $2 \times 2$ estimates, assuming the parallel counterfactual trends assumption (\ref{eq:parallel}).\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Callaway_Sant’Anna_2020}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_D’Haultfoeuille_2019}.
+I won't recharacterize the weights in this article and guide interested readers to the source articles themselves.}
+
+Now, I will propose an estimation strategy that follows \citet{Callaway_Sant’Anna_2020} (C\&S) while incorporating spillovers directly into estimation.
+However, I won't cover all the technical details and point the reader to the main text for these details.
+To begin, C\&S define a `cohort' $g$ as the set of units that recevie treatment starting in period $g$.
+Let $G_g$ be an idicator equal to one for all units where treatment starts at period $g$ and $C$ an indicator equal to one if the unit never receives treatment.
+Each cohort will serve as the treated group for a set of $2\times 2$ difference-in-differences.
+For each period $t$ they define the `group-time average treatment effect', $ATT(g,t) = \mathbb{E}\left[ Y_t(g) - Y_t(0) \ \vert \ G_g = 1 \right]$, where $G_g$ is an indicator for starting treatment in year $g$.
+The potential outcome is indexed by $g$ to allow for treatment effects to differ depending on the initial treatment year.
+
+Therefore in the context of spillovers, our equivalent term is the `group-time average direct effect' which will be defined as $$ 
+    ATT_{\text{direct}}(g,t) = \mathbb{E}\left[ Y_t(g, 0) - Y_t(0, 0) \ \vert \ G_g = 1 \right],
+$$ where the second term in potential outcomes represents an exposure mapping of $h(\vec{D}, i) = 0$.
+Similar to above, we modify the parallel trends assumptions given by CS to hold in the absence of exposure.
+
+\begin{assumption}[Parallel Counterfactual Trends on a ``Never-Treated'' Group]\label{eq:parallel_es_never}
+    $$
+        \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 \right] = \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ C = 1 \right] 
+    $$ 
+\end{assumption}
+
+\begin{assumption}[Parallel Counterfactual Trends on ``Not-Yet-Treated'' Groups]\label{eq:parallel_es_notyet}
+    $$ 
+        \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 \right] = \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ D_s = 0, G_g = 0 \right]
+    $$ 
+\end{assumption}
+
+% ------------------------------------------------------------------------------
+\subsection{Estimating Direct Effects}
+% ------------------------------------------------------------------------------
+
+The group-time average direct effect is the building block of analysis in the framework proposed by C\&S.
+Estimation of the group-time average direct treatment effect, $ATT_{\text{direct}}(g,t)$ depends on which parallel trends assumption a researcher use.
+If a researcher is using Assumption \ref{eq:parallel_es_never}, then estimation will be done using a supsample containing only control units and units in group $g$.
+The difference-in-difference estimate uses period $t$ outcomes as the post-period and some period $g - \delta$ as the pre-period where $\delta$ is the number of periods before initial treatment.
+In the context of spillovers, the canoncial difference-in-differences estimation will have to be adjusted using a parameterized exposure mapping to prevent the bias detailed in the $2 \times 2$ setting.
+As shown in Section \ref{sec:monte_carlo}, this can be done using a set of donut indicators that is wide enough to capture all of the spillovers.
+
+If a researcher is using Assumption \ref{eq:parallel_es_notyet}, then estimation will be done with a subsample containing treated units from group $g$ and all units that are in groups $g' > t$.
+Again, estimation of the group-time direct effect will have to include controls for spillovers.
+
+Then, as detailed in C\&S, these ATT can be aggregated using different weights depending on the pararmeter of interest (see Table 1 of \citet{Callaway_Sant’Anna_2020}).
+These aggregations take the form of
+\begin{equation*}
+    \theta = \sum_{g} \sum_{t} w(g,t) ATT_{\text{direct}}(g,t)    
+\end{equation*} 
+These weights include the option to make event study estimates, or group-level average treatment effects (across time).
+Estimation and different aggregation of the direct effects can be done using the `did' package produced by CS where the measure of spillovers are included as covariates.
+
+% ------------------------------------------------------------------------------
+\subsection{Estimating Spillover Effects}
+% ------------------------------------------------------------------------------
+
+Estimation of the spillover effects is potentially much more difficult as estimation of continuous variables in the presence of staggered treatment is still a work in progress and past the scope of this article.
+However, for indicator variables, estimation can be done in much the same way as the direct effect.
+
+Since a set of donut indicators captures non-additive spillovers generally, I will focus on estimation of these donut indicators.
+For a given ring indicator, you would define groups by the period that a unit's ring indicator turns on.
+However, treated units can always move to more inner rings as treatment turns on over time, so control units should only enter estimation for the most inner indicator they enter.
+
+Then, estimation can be done assuming that all control units are on the same counterfactual trends in the absence of spillovers.
+For a given ring, the `treated' units consist of units that have that ring be the most inner spillovers they experience and the `control' units consist of all control units whose spillover status remains constant between the pre-period, $g - \delta$ and $t$.
+As above, estimation of the group-time average spillover effect should include the other spillover indicators to avoid biases from other spillover effects.
+
+Therefore, for each spillover donut, estimation and aggregation can be done in much the same way as for the direct effect.
+However, estimation and aggregation can not be done using the `did' program as subsamples have to be constructed more specifically for each group-time average spillover effect.
+
+% ------------------------------------------------------------------------------
+\section{Conclusion}
+\label{sec:conclusion}
+% ------------------------------------------------------------------------------
+
+This paper has considered the common environment where treatment is assigned via administrative boundary while the effects of treatment spread across these borders.
+In this context, difference-in-differences estimation will identify a combination of the direct effect of treatment and two additional terms resulting from spillovers.
+I have proposed a potential outcomes framework that is used to express each of these spillover terms as a function of potential outcomes and the exposure mapping.
+
+Further, I show that parameterizing these spillovers can remove most of the biases even in the presence of some misspecification.
+In particular, I find that specifications with a set of `Donuts' are the best at capturing the spatial structure of spillovers.
+When estimating spillover effects themselves, I find that it is important to correctly identify is spillovers are additive or non-additive in the number of nearby treated units.
+
+Then, I show that these approaches can change estimates significantly in the context of estimating the effects of place-based policies.
+Since place-based policies change the nature of agglomeration in the local and surrounding area --that is cause spillovers--local effects of these policies can be misestimated without controlling for spillovers.
+
+Finally, I show how researchers can include spillovers in settings with variation in treatment timing following \citet{Callaway_Sant’Anna_2020}.
+
+% ------------------------------------------------------------------------------
 \newpage \printbibliography%

### 2021-02-12 latex/paper/Spillover.tex
Rework Introduction

@@
 
-\title{\color{navyblue} Differences-in-Differences with Spatial Spillover}
+\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillover}
 % \subtitle{Subtitle}
@@
 Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-I use Monte Carlo simulations to demonstrate when the biases are particularly large.
-Further, I show that a common solution used in the literature of removing `contaminated' control units only prevents the first source of bias.
-Lastly, I propose improved estimation strategies that can remove both sources of bias.
-I highlight the importance of considering spillovers by revisiting analysis of the Tennessee Valley Authority.
+I propose estimation strategies that can remove both sources of bias as well as semi-parametrically estimate the spillovers themselves.
+Lastly, I extend this estimation strategy in an event-study framework following \citet{Callaway_Sant’Anna_2020}.
+Then, I turn to an empirical application revisiting an analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
+I highlight the importance of considering general equilibrium spillovers in the analysis of place-based policies when estimating the direct effect on targeted areas.
     \end{abstract}
@@
 
-Empirical work in economics often considers treatment assigned by geographic boundaries such as cities, counties, and states.
-Potentially, the effect of these treatments do not stay within these boundaries whether it be from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects influencing neighboring areas.
-Despite the problem of spatial spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis takes the problem seriously.
-In a survey of eight top economics and finance journals in 2017, they find that only 21 articles out of 108 that run difference-in-differences estimation discuss spillovers.\footnote{The articles surveyed are American Economic Review, Econometrica, the Journal of Political Economy, the Quarterly Journal of Economics, the Review of Economic Studies, the Journal of Finance, the Journal of Financial Economics, and the Review of Financial Studies.} In this paper, I show that failing to account for spatial spillovers can lead to poorly identified estimates of treatment effects.
-
-In the causal inference literature, researchers assume that a unit's potential outcome does not depend on the treatment status of any other unit -- what \citet{Rubin_1980} calls the Stable Unit Treatment Value Assumption (SUTVA).
-This article considers a common violation of SUTVA in a process I label `spatial spillovers' where the treatment assignment of `close' units' affects outcomes of nearby units.\footnote{Close can refer to many different things, e.g.
-geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} Typically researchers are interested in the `direct effect' on the treated units.\footnote{This is sometimes called the `partial equilibrium' effect or the `local effect'.} In the presence of spatial spillovers, I show using a potential outcomes framework that the difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
+Empirical work in economics often considers treatment assigned to groups of units, but the effect of these treatments potentially do not stay within these groups and spillover onto ‘close’ units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+geographic
+distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, treatment is often assigned to geographic boundaries and spillovers occur from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects influencing neighboring areas.
+Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.\footnote{The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect.
+In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The central result of my paper is that in the presence of spillovers, the difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
 
@@
 In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
-For example, consider a factory opening in a county.
-Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain \citep{Duranton_Puga_2003}.
+For example, consider trying to estimate employment effects of a factory opening in a county.
+Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain which would potentially increase employment \citep{Duranton_Puga_2003}.
 The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
@@
 Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces.
-The estimated treatment effect will count the `direct` effect of the factory opening as well as the benefit of the agglomeration economies.
+The estimated treatment effect will count the `direct' effect of the factory opening as well as the benefit of the agglomeration economies.
 Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.
 
-These biases can be written as functions of the potential outcomes in my framework and can be used by researchers to sign or bound the bias using insight from their economic context.
-The magnitude of the bias depends on two factors: the size of the spillovers and the number of units affected by spillovers.
-If spillovers are quite large in magnitude or spread far over distance, then the bias will generally be large.
-Th results of this paper enable researchers to estimate bounds for it by making assumptions about the average size of the spillover effect and the number of units affected.
-I use Monte Carlo simulations to quantify the magnitude of bias in various spillover settings.
+I then propose an estimation strategy that will remove both sources of bias with very minimal assumptions on the structure of spillovers.
+To remove \textit{all bias} from the direct effect estimate, a research needs to just include an indicator for being close to a treated unit interacted with treatment status, so long as the indicator captures all units affected by spillovers.
+An indicator removes all bias because in my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units.
+The interacted indicator will estimate this average and remove both bias terms from the treatment effect estimate.
+Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
+The only assumption required is the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed.
+However, including too many units will increase the variance in the estimates for average spillover effects.}
 
-In the survey by \citet{Berg_Streitz_2019}, only eight of the 21 papers that discuss spillovers control for this potential source of bias in their primary empirical specification to prevent bias in the estimation of treatment effects.
-The other thirteen papers usually first estimate the direct effect without controlling for spillovers and then seperately estimate the spillover effects.
-This paper shows that not controlling for spillovers produces biased estimates of the direct effect.
+Since spillovers themselves are often important causal effects themselves, I next turn to how to estimate spillovers directly.
+I show with evidence from Monte Carlo simulations, that commonly used semi-parametric estimation strategies capture spillovers well (in a mean square prediction error sense).
+This involves creating a set of distance bins from treated units (e.g.
+being 0-20 miles, 20-40 miles, 40-60 miles from treated unit).
+The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not.
+For non-additive spillovers, I recommend a set of mutually-exclusive indicators for the closest treated unit being in each distance bin.
+For additive spillovers, I recommend using the number of treated units within each spillover bin.
 
-Of the eight papers that include spillovers directly in their estimation strategy, six simply drop the control units they suspect to be affected by spillovers.
-Since this is a common strategy used by researchers, I use Monte Carlo simulations to show that this method is effective in the case where spillovers \textit{only} occur onto control units.
-In the presence of spillover onto also treated units, the estimates for the direct effect will still be biased.
-Dropping control unit observations, however, makes estimates less precise, so parameterizing the spillover function may be a better strategy especially in the case where a high proportion of control units would need to be removed.
+As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
+The Tennessee Valley Authority was a large scale New Deal program that created many new dams for flood-protection and navigation.
+The construction of large-scale dams lowered the cost of power for industrial firms giving the region an industrial boost \citep{Kitchens_2014}.
+The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citet{Severnini_2014}.
+I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.
 
-Removing both sources of bias requires a researcher to take a stance and parameterize a functional form for the spillovers.
-The particular functional form depends on the context of the application.
-However, there are a few practical considerations.
-First, the researcher should argue whether spillovers on control units and on treated units exist.
-Second, they should argue what the maximum distance these spillovers can occur.
-Last, they should consider if spillovers are additive in the number of nearby units that are treated.
+I turn to an empirical application in the literature in urban economics on local place-based policies in section \ref{sec:tva}.
+Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects in non-treated locations.
+I contribute by showing that because of these general equilibrium effects, estimation of local effects are often underestimated by not controlling for the spillover effects in estimation.
 
-In section \ref{sec:monte_carlo}, I use Monte-Carlo simulations to emphasize when misspecificied spillovers still remove most of the bias and when they fail to do so.
+Last, in section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_Sant’Anna_2020}.
+I first show how to adjust their methods to control for spatial spillovers in estimation of treatment effects.
+Second, I show how an extension of their method allows for estimation of spillover effects.
+My paper is the first paper to study estimation of treatment effects in an event-study framework.
 
-% @TODO: Discuss effectiveness under misspecification of spillovers (correct distance and additive/non-additive).
+There is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
+Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares untis in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects.
+This allows standard difference-in-differences estimation of both the direct effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).
 
-% ------------------------------------------------------------------------------
-\subsection{Contribution}
-% ------------------------------------------------------------------------------
+More recently, a new strand of literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster by using a potential outcomes framework.
+\citet{Vazquez-Bare_2019} presents a potential outcomes model that explicitly accounts for ``within-group'' spillovers in experiments which allows for seperate estimation of direct effect and spillover effects by a simple differences-in-means.
+I extend this work by focusing on difference-in-differences estimation in non-experimental settings.
+\citet{Sävje_Aronow_Hudgens_2019} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
+My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.These estimates can be combined afterwards to estimate their definition of average treatment effect.
+The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.
 
-The literature considering spillovers primarily has focused on ``within-group'' spillovers where units are in distinct groups and outcomes depend on the treatment status within the observation's group only.\footnote{For example, researchers consider peer effects within schools.
-In this case, each school constitutes a group and it is assumed that outcomes do not depend on other schools' treatment status, i.e.
-SUTVA is satisfied between-groups.
-Estimation of spillover effects in this case is done in a `partial intereference' framework that compares ``control'' units in a partially treated group with control units in completely untreated groups.
-\citet{Angelucci_DiMaro_2016} provides a summary for estimation of spillover effects in within-group settings.
-Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} However, spatial settings such as counties do not feature distinct groups which allow for the researcher to separate areas into distinct non-overlapping groups (a county is connected to all other counties by some chain of neighbors).
-My paper considers a more general form of interference.
-Identification in this framework requires the researcher to either identify control units that are free from spillovers (far-away from treatment) or to parameterize how control units are affected by treatment.
-
-\citet{Vazquez-Bare_2019} models within-group spillovers such that their exposure mapping is only a function of unit $i$'s group's treatment vector.
-He develops a potential outcomes framework which assumes that potential outcomes are a function of both own treatment-status $D_i$ and a function of the vector of treatment assignments $h(\vec{D}, i)$.
-The function $h(\vec{D}, i)$ is referred to as an exposure mapping and adding this to the potential outcomes framework allows me to explicitly model SUTVA violations.
-Using this framework, \citet{Vazquez-Bare_2019} shows that a difference in means comparison between treated and control units is a biased estimated for the treatment effect.
-
-My paper uses this potential outcome framework in the case where treatment spillover is not limited to within-group spillovers and considers estimation of treatment effects by difference-in-differences.
-
-\citet{Sävje_Aronow_Hudgens_2019} consider a similar potential outcome framework as \citet{Vazquez-Bare_2019}, but they instead include spillovers as a part of their definition of ``treatment effect''.
-That is, a treated unit's treatment effect is defined as the direct effect \textit{and} the general equilibrium spillover effects.
-Then, the authors describe how the average treatment effect (ATE) estimated by difference-in-differences averages over both individual heterogeneity and, central to their contribution, over heterogeneity in the exposure mapping, $h(\vec{D}, i)$.
-My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.\footnote{These estimates can be combined afterwards to estimate their definition of average treatment effect.
-The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.}
-
-There are a few papers that discuss estimation of treatment effects with spatial spillovers using the difference-in-differences framework.
-\citet{Clarke_2017} finds an explicit form for bias when estimating a difference-in-differences model.
-However, their model only allows spillovers onto control units and assumes spillovers are constant regardless on the number of nearby treated units.
-\citet{Berg_Streitz_2019} and \citet{Verbitsky-Savitz_Raudenbush_2012} identifies biases in estimation of the direct effect for a specific potential outcome function where $h(\vec{D}, i)$ is the proportion of treated contiguous counties.
-Finally, \citet{Delgado_Florax_2015} consider the case where the exposure mapping is defined by a spatial weights matrix $W\vec{D}$ that enters linearly into the potential outcomes.
-This does not allow for the coefficient to change for control and treated units.\footnote{Although, one could change the weighting matrix to make ad-hoc assumption of the signs and relative magnitudes of spillovers onto treated and control units, but this allows for less data-driven estimation.}
-
-My paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers.
+I also contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
+I contribute to this literature in two ways.
+First, my paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers.
 For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly.
-My paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
-
-Lastly, I contribute to a literature in urban economics on local place-based policies.
-Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects.
-I contribute to estimating aggregate effects of place-based policies by showing that typical estimation strategies can underestimate the local effect by ignoring spillovers.
-As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
-The Tennessee Valley Authority was a large push to bring electrification to the Tennessee Valley with the goal of improving the manufacturing sector there.
-The scale of the program was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies.
-I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.
+Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
 
@@
 Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards.
-This framework can be extended in section \ref{sec:event_study}.
-As in \citet{Vazquez-Bare_2019}, potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+This framework is extended to staggered treatment adoption in section \ref{sec:event_study}.
+Potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
 The potential outcomes are denoted $Y_{i,t}(D_i, h(\vec{D}, i)$).
@@
 The exposure mapping measures the intensity at which unit $i$ is affected by spatial spillovers.
-When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = 0$.
+When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$.
 The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment as summarized by $h(\vec{D}, i)$.
@@
 
+\begin{example}
     First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
@@
 Access to a neighboring town library is binary in nature, so it does not matter whether you can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
+\end{example}
 
-Second, $h(\vec{D}, i)$ can be a function that equals the proportion of the k-nearest neighbors that are treated, i.e. \begin{equation}\label{eq:h_within}
-    h(\vec{D}, i) = 1/k \sum_{j \in K(i)} D_j,
+\begin{example}
+    Second, $h(\vec{D}, i)$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
+        h(\vec{D}, i) = \sum_{j} D_j * 1[ d(i,j) < \bar{d} ].
     \end{equation}
-where $K(i)$ is the index of unit $i$'s k-nearest neighbors.
-This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of units treated.
+    This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of nearby units treated.
 In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies.
 As more nearby counties receive new stores, the agglomeration forces increase \citep{Basker_2005}.
+\end{example}
 
+\begin{example}
     Last, is the spatial decay function where exposure decreases with distance.
@@
 In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
+\end{example}
 
@@
 With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
-    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0).
+    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, \vec{0}).
 \] 
 The spillover measures the difference in non-treated potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
-Then, the average spillover effect onto control units averages over potential heterogeneity in spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
-    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, 0) \ \vert \ D_i = 0 \right].
+Then, the average spillover effect onto control units averages over potential heterogeneity in the effect size of spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
+    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, \vec{0}) \ \vert \ D_i = 0 \right].
 \]
@@
 I assume that what the `average treatment effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
-    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, 0) - Y_{it}(0, 0) \ \vert \ D_i = 1 \right],
+    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, \vec{0}) - Y_{it}(0, \vec{0}) \ \vert \ D_i = 1 \right],
 \] 
@@
 In this section, I identify the two sources of bias in difference-in-differences estimation of the direct effect of treatment.
-For exposition, I will refer to one pre- and post-period, $t = 0$ and $t = 1$, but this can be replaced by averages across $Y$ in the pre-period and the post-period respectively.
 To estimate the `direct effect of treatment', researchers estimate the canonical two-way fixed effects model,
@@
     \[ 
-        \mathbb{E}\left[ Y_{i1}(0, 0) - Y_{i0}(0, 0) \ \vert \ D_i = 1 \right] = 
-        \mathbb{E}\left[ Y_{i1}(0, 0) - Y_{i0}(0, 0) \ \vert \ D_i = 0 \right]
+        \mathbb{E}\left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1 \right] = 
+        \mathbb{E}\left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0 \right]
     \]
@@
 
-Given that Assumption (\ref{eq:parallel}) holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias.
+Given that Assumption \ref{eq:parallel} holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias.
 The proof is given in Appendix \ref{sec:proofs}.
 
-\begin{theorem}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
-    If Assumption (\ref{eq:parallel}) holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
+\begin{proposition}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
+    If Assumption \ref{eq:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
     \begin{align*}
@@
     \end{align*}
-\end{theorem}
+\end{proposition}
 
@@
 
-First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatmnet if the potential outcomes are correctly specified.
+First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatment if the potential outcomes are correctly specified.
 In the case where potential outcomes are `somewhat' incorrectly specified, this can remove some of the bias in estimation.
-Simulations below highlight that since spillovers are likely to decay over distance, controlling for immediate neighbors removes a large portion of the average spillover effects.
+Simulations below highlight that since spillovers are likely to decay over distance, controlling for immediate neighbors removes a large portion of the average spillover effects even under misspecification.
 
@@
 On the other hand, abortion clinics opening are used infrequently and therefore the effect likely doesn't decay over distance within a certain cutoff.} First, as seen above is to use an exponential decay function with regards to distance.
-The other option is to use a set of `cocentric donut' indicators which are easy to interpret.
+The other option is to use a set of `concentric donut' indicators which are easy to interpret.
 An example of this is shown in the empirical application in Section \ref{sec:tva}.
@@
 A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
-The intercepet is $\alpha = -2$, the fixed effects are generated by $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$, and the error term is $\varepsilon \sim N(0, 2^2)$.
+The unit and time fixed effects are generated by $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively, and the error term is $\varepsilon \sim N(0, 2^2)$.
 Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
@@
 I assign treatment among counties randomly with various unconditional probabilities between 3 percent and 50 percent.
-The DGP is therefore
+The data-generating process is therefore
 \begin{equation}
@@
 To avoid changes in bias due to a difference in the number of treated units, the unconditional probability is equal to 5 percent in all simulations.
-
+To increase the spatial autocorrelation of treatment, I increase the probability of treatment for units with $\text{Zone}_i = 1$ and hence lower the probability for units with $\text{Zone}_i = 0$.
+\footnote{
     To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
@@
 In our simulations, Zone Plus ranges from 0 which is the case where $P(D_i \vert \text{Zone}_i) = P(D_i) = 0.05$ to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.01 + 0.41 * \text{Zone}_i$.
+}
 
@@
 The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority.
-If specification (\ref{eq:tva_spillover}) is correctly specified, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect.
-As shown above, minor misspecification will remove some but not all of the bias from standard difference-in-differences estimates.
+From the above simulations, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect so long as spillovers don't occur past 150 miles from the TVA.
 

### 2021-02-14 latex/paper/Spillover.tex
Rework simulation section

@@
 Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
-Section \ref{sec:monte_carlo} presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature.
+Section \ref{sec:estimation} presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature.
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
 Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_Sant’Anna_2020}.
+% @TODO Fix this
 
@@
 For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using non-linear least squares.
-In the literature on R\&D investment, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
+In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
 \end{example}
@@
 
-\begin{proposition}[Bias from Difference-in-Differences Estimation]\label{thm:bias}\ \\    
+\begin{proposition}[Decomposition of Difference-in-Differences Estimate]\label{thm:bias}\ \\    
     If Assumption \ref{eq:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
@@
 % ------------------------------------------------------------------------------
-\subsection{Improving Estimation by Parameterizing Spillovers}
+\section{Estimation of Treatment Effects with Spillovers}
+\label{sec:estimation}
 % ------------------------------------------------------------------------------
 
-The previous section shows how to estimate the magnitude of potential bias in the estimation of (\ref{eq:twfe}).
-However, parameterization of the potential outcomes and exposure mapping allows for unbiased estimates of $\tau_{\text{direct}}$ by controlling for the exposure mapping directly.
+In this section, I analyze methods that have been used by researchers for estimation of the direct and spillover effects.
+I provide practical guidance on when the methods are effective and in particular propose a method that is most robust.
+
+% ------------------------------------------------------------------------------
+\subsection{Removing Bias by Dropping Control Units}
+% ------------------------------------------------------------------------------
+
+A common approach in the literature is to drop control units neighboring treated units to avoid the problems of spillovers in identification.
+The above proposition would suggest that this can be effective in removing (at least part of) the average spillover effect on control units.
+However, since researchers do not know how far the spillovers spread there is difficulty in this method.
+On the one hand, removal of too few units will keep some control units that are experiencing spillover effects which would leave the treatment effect biased.
+On the other hand, removing too many units will leave few observations and therefore make the estimate have high variance.
+There is therefore a bias-variance trade off inherit to this method that can be readily improved by the method proposed in Section \ref{sec:parameterize}.
+
+The second problem with this approach is that removal of control problems will not remove spillovers onto also treated units.
+Therefore if treated units are affected by the treatment status of nearby units, then the average spillover effect on treated untis which would remain as a source of bias.
+Appendix \ref{sec:monte_carlo} contains a set of Monte Carlo simulations that highlight the problems more rigorously.
+
+% ------------------------------------------------------------------------------
+\subsection{Parameterization of Spillovers}
+\label{sec:parameterize}
+% ------------------------------------------------------------------------------
+
+While some researchers try to remove untis that are most likely to experience spillover effects in order to estimate the direct effects, another common approach is to directly parameterize the spillovers themselves.
+Parameterization of the potential outcomes allows for unbiased estimates of $\tau_{\text{direct}}$ by controlling for the exposure mapping directly.
 This is recommended for two reasons.
@@
 First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatment if the potential outcomes are correctly specified.
-In the case where potential outcomes are `somewhat' incorrectly specified, this can remove some of the bias in estimation.
-Simulations below highlight that since spillovers are likely to decay over distance, controlling for immediate neighbors removes a large portion of the average spillover effects even under misspecification.
+However, the functional form of spillovers is not observed by the researcher.
+I show in simulations below that information on the exact functional form is not required for unbiased estimates of the treatment effect.
+Therefore, estimation can occur without dropping units which will improve efficiency.
 
 Second, the spillover effects themselves are potentially relevant for policy makers.
-If treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will double-understate the true effect of treatment.
+For example, if treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will double-understate the true effect of treatment.
 First, it will not include the neighboring units' benefit in the calculation.
@@
 
-Second, a researcher must decide how far the spillovers can reasonably be experience and whether the effect decays over distance.
+Second, a researcher must decide how far the spillovers extend and whether the effect decays over distance.
 Things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
@@
 On the other hand, abortion clinics opening are used infrequently and therefore the effect likely doesn't decay over distance within a certain cutoff.} First, as seen above is to use an exponential decay function with regards to distance.
-The other option is to use a set of `concentric donut' indicators which are easy to interpret.
+The parameter $\alpha$ in Equation (\ref{eq:h_decay}) determines the rate of decline over distance.
+
+The other option is to use a set of `concentric rings' which are a semi-parametric way to estimate spillovers.
+If the spillovers do decay over distance, then the coefficients on the indicators should decrease as they move out.
+On the other hand, they are robust in estimating spillovers that do not decay, whereas exponential decay is not.
+In the simulations below, we will see that the rings are very flexible across forms of spillovers.
 An example of this is shown in the empirical application in Section \ref{sec:tva}.
@@
 In the context of factory openings, though, agglomeration economies imply that the spillovers are additive in nature.
+The simulations below show that in order to accurately estimate spillovers requires correctly using a additive or non-additive version of the concentric rings.
 
-% ------------------------------------------------------------------------------
-\section{Monte Carlo Simulations}
-\label{sec:monte_carlo}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\subsection{Spillover on Controls Only}
-% ------------------------------------------------------------------------------
-
-I now turn to a series of Monte Carlo Simulations to highlight the importance for controlling for spillovers in simulations.
-I use the set of counties in the contiguous United States and the data generating process used is defined by the exposure mapping given in (\ref{eq:example_exposure}) with cutoff distance $\bar{d} = 40$ miles and the data generating process given in (\ref{eq:example_po}).
-A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
-The unit and time fixed effects are generated by $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively, and the error term is $\varepsilon \sim N(0, 2^2)$.
-Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
-
-For the first simulation, I restrict spillovers only to occur among control units, i.e.
-$\beta_{\text{spill, treat}} = 0$, and estimate the two-way fixed effects model, (\ref{eq:twfe}).
-This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
-I assign treatment among counties randomly with various unconditional probabilities between 3 percent and 50 percent.
-The data-generating process is therefore
-\begin{equation}
-    \label{eq:dgp1} 
-    y_{it} = \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill, control}} (1-D_{it}) \text{Near}_{it} + \varepsilon_{it}   
-\end{equation}
-
-\begin{figure}[tb!]
-    \caption{Bias of $\hat{\tau}$ with Spillovers Effects \emph{only} on Control Units}
-    \label{fig:bias_as_treat_prob}
-    {\centering
-        \includegraphics[width=\textwidth]{../../figures/figure-bias_fix.png}
-    } 
-    {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp1}.
-Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
-The line with diamond markers estimates with all control units.
-The line with circle markers removes control units that share a border with a treated county.
-    }
-\end{figure}
-
-The size of the bias from estimating the two-fixed effects model, (\ref{eq:twfe}), at different treatment probabilities are presented in Figure \ref{fig:bias_as_treat_prob} as the line with diamond markers.
-Each point represents a set of 10,000 simulation and displays the mean bias as well as a 95 percent empirical confidence interval.
-As displayed in the figure, even for a low treatment probability of three percent, the bias is quite large with a 95 percent empirical confidence interval between -0.28 and -0.75.
-As treatment frequency increases, the bias increases as well but at a slower rate due to fewer additional control units receiving spillover units.
-The slow increase in bias is in part due to the assumption that spillovers are not additive in the number of nearby units treated.
-
-A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers.
-To do this, I remove contiguous control counties which is a close, but misspecificied, measure of $h(\vec{D}, i)$.
-The results are shown in Figure \ref{fig:bias_as_treat_prob} by the line with circle markers.
-Even though the exposure mapping is misspecified, contiguous counties approximates the true exposure mapping well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
-However, if the distance cutoff $\bar{d}$ were larger, more control units would remain in the sample that experience non-zero exposures.
-In this case, the bias would fall between the two lines.
-
-There is a trade-off between the bias and the variance of the estimator when using this methodolgy.
-As the treatment probability increases, the number of control units removed increases as well.
-This naturally yields a more variable estimator as seen in the wider 95 percent empirical confidence intervals in Figure \ref{fig:bias_as_treat_prob}.
-This trade-off can be avoided altogether by parameterizing the spillovers and including them in estimation directly.
-
-% -----------------------------------------------------------------------------
-\subsection{Spillovers onto Control and Treated Units}
-% ------------------------------------------------------------------------------
-
-For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
-\begin{equation}\label{eq:dgp2} 
-    y_{it} = \mu_t + \mu_i + 2 D_{it} + (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
-\end{equation} 
-The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
-In empirical applications, it is often the case that treatment assignment is concentrated in specific areas which yields higher proportion of treated units receiving spillover effects.
-
-\begin{figure}[tbh!]
-    \caption{Example of Kriging Field}
-    \label{fig:kriging}
-    \begin{center}
-        \resizebox{0.8\textwidth}{!}{
-            \includegraphics{../../figures/figure-krig.png}
-        } 
-    \end{center}
-
-    {\footnotesize
-        \textit{Notes:} This figure plots an example of a kriging simulation using the `gstat' package in R using an exponential variogram.
-The outlined counties are in the top ten percent of values for this simulation.
-    }
-\end{figure}
-
-\begin{figure}[tbh!]
-    \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
-    \label{fig:bias_spatial_autocorr}
-    {\centering
-        \resizebox{\textwidth}{!}{
-            \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
-        } 
-    }
-
-    {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp2}.
-Treatment probability is assigned according to the method described by the text and (\ref{eq:cond_prob}).
-Each point corresponds to the average bias for the given Zone Plus and the band is the 95 percent empirical confidence interval over 1000 simulations.
-The line with diamond markers estimates with all control units.
-The line with circle markers removes control units that share a border with a treated county.
-    }
-\end{figure}
-
-In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
-Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
-One such field is depicted in Figure \ref{fig:kriging}.
-For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
-Then I assign treatment with a probability that differs based on $\text{Zone}_i$.
-To avoid changes in bias due to a difference in the number of treated units, the unconditional probability is equal to 5 percent in all simulations.
-To increase the spatial autocorrelation of treatment, I increase the probability of treatment for units with $\text{Zone}_i = 1$ and hence lower the probability for units with $\text{Zone}_i = 0$.
-\footnote{
-    To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
-    \begin{equation}
-        \label{eq:cond_prob}
-        P(D_i \ \vert \ \text{Zone}_i) = (.05 + \text{Zone Plus} * \text{Zone}_i) \times \underbrace{\frac{.05}{.05 * .9 + (.05 + \text{Zone Plus}) * .1}}_{\text{Normalize } P(D_i) = 0.05}
-    \end{equation}
-    The second term normalizes probabilities so the unconditional probability stays at five percent.
-In our simulations, Zone Plus ranges from 0 which is the case where $P(D_i \vert \text{Zone}_i) = P(D_i) = 0.05$ to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.01 + 0.41 * \text{Zone}_i$.
-}
-
-The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
-The line with diamond markers is run on the full sample.
-As the level of spatial autocorrelation increases, the bias surprisingly decreases.
-The reason for this is that as treatment becomes more concentrated in the `Zones', the number of control units receiving spillovers decreases while the number of treated units receiving spillovers increases.
-In this particular data-generating process, the effect of fewer control units on the bias is larger than the bias from more treated units.
-
-The line with circle markers in Figure \ref{fig:bias_spatial_autocorr} repeats the exercise of dropping control units that share a border with treated units.
-In the case where spillovers occur on treated units, all bias is not removed when dropping control units.
-That is because we only remove $\tau_{\text{spill,control}}$ but $\tau_{\text{spill,treated}}$ remains.
-To remove the second source of bias, it is necessary to acount directly for spillovers in the estimation strategy.
-
-% ------------------------------------------------------------------------------
-\subsection{Misspecification of Spillovers}
-% ------------------------------------------------------------------------------
-
-Now we turn to simulations where we include potentially incorrectly specified exposure mappings and see their performance in a set of different data generating processes.
+To highlight the importance of these considerations, we turn to simulations where we include potentially incorrectly specified exposure mappings and see their performance in a set of different data generating processes.
 In the general form, I generate data with the same fixed effects and error term as before, but for many different exposure mappings $h(\vec{D}, i)$
@@
 In the context of spillovers, the canoncial difference-in-differences estimation will have to be adjusted using a parameterized exposure mapping to prevent the bias detailed in the $2 \times 2$ setting.
-As shown in Section \ref{sec:monte_carlo}, this can be done using a set of donut indicators that is wide enough to capture all of the spillovers.
+As shown in Section \ref{sec:estimation}, this can be done using a set of donut indicators that is wide enough to capture all of the spillovers.
 
@@
 
+% ------------------------------------------------------------------------------
+\section{Details on Monte Carlo Simulations}
+\label{sec:monte_carlo}
+% ------------------------------------------------------------------------------
+
+I use the set of counties in the contiguous United States and the data generating process used is defined by the exposure mapping given in (\ref{eq:example_exposure}) with cutoff distance $\bar{d} = 40$ miles and the data generating process given in (\ref{eq:example_po}).
+A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
+The unit and time fixed effects are generated by $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively, and the error term is $\varepsilon \sim N(0, 2^2)$.
+Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
+
+This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
+I assign treatment among counties randomly with various unconditional probabilities between 3 percent and 50 percent.
+The data-generating process is therefore
+\begin{equation}
+    \label{eq:dgp1} 
+    y_{it} = \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill, control}} (1-D_{it}) \text{Near}_{it} + \varepsilon_{it}   
+\end{equation}
+
+\begin{figure}[tb!]
+    \caption{Bias of $\hat{\tau}$ with Spillovers Effects \emph{only} on Control Units}
+    \label{fig:bias_as_treat_prob}
+    {\centering
+        \includegraphics[width=\textwidth]{../../figures/figure-bias_fix.png}
+    } 
+    {\footnotesize
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp1}.
+Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
+The line with diamond markers estimates with all control units.
+The line with circle markers removes control units that share a border with a treated county.
+    }
+\end{figure}
+
+The size of the bias from estimating the two-fixed effects model, (\ref{eq:twfe}), at different treatment probabilities are presented in Figure \ref{fig:bias_as_treat_prob} as the line with diamond markers.
+Each point represents a set of 10,000 simulation and displays the mean bias as well as a 95 percent empirical confidence interval.
+As displayed in the figure, even for a low treatment probability of three percent, the bias is quite large with a 95 percent empirical confidence interval between -0.28 and -0.75.
+As treatment frequency increases, the bias increases as well but at a slower rate due to fewer additional control units receiving spillover units.
+The slow increase in bias is in part due to the assumption that spillovers are not additive in the number of nearby units treated.
+
+A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers.
+To do this, I remove contiguous control counties which is a close, but misspecificied, measure of $h(\vec{D}, i)$.
+The results are shown in Figure \ref{fig:bias_as_treat_prob} by the line with circle markers.
+Even though the exposure mapping is misspecified, contiguous counties approximates the true exposure mapping well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
+However, if the distance cutoff $\bar{d}$ were larger, more control units would remain in the sample that experience non-zero exposures.
+In this case, the bias would fall between the two lines.
+
+There is a trade-off between the bias and the variance of the estimator when using this methodolgy.
+As the treatment probability increases, the number of control units removed increases as well.
+This naturally yields a more variable estimator as seen in the wider 95 percent empirical confidence intervals in Figure \ref{fig:bias_as_treat_prob}.
+This trade-off can be avoided altogether by parameterizing the spillovers and including them in estimation directly.
+
+For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
+\begin{equation}\label{eq:dgp2} 
+    y_{it} = \mu_t + \mu_i + 2 D_{it} + (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
+\end{equation} 
+The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
+In empirical applications, it is often the case that treatment assignment is concentrated in specific areas which yields higher proportion of treated units receiving spillover effects.
+
+\begin{figure}[tbh!]
+    \caption{Example of Kriging Field}
+    \label{fig:kriging}
+    \begin{center}
+        \resizebox{0.8\textwidth}{!}{
+            \includegraphics{../../figures/figure-krig.png}
+        } 
+    \end{center}
+
+    {\footnotesize
+        \textit{Notes:} This figure plots an example of a kriging simulation using the `gstat' package in R using an exponential variogram.
+The outlined counties are in the top ten percent of values for this simulation.
+    }
+\end{figure}
+
+\begin{figure}[tbh!]
+    \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
+    \label{fig:bias_spatial_autocorr}
+    {\centering
+        \resizebox{\textwidth}{!}{
+            \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
+        } 
+    }
+
+    {\footnotesize
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp2}.
+Treatment probability is assigned according to the method described by the text and (\ref{eq:cond_prob}).
+Each point corresponds to the average bias for the given Zone Plus and the band is the 95 percent empirical confidence interval over 1000 simulations.
+The line with diamond markers estimates with all control units.
+The line with circle markers removes control units that share a border with a treated county.
+    }
+\end{figure}
+
+In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
+Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
+One such field is depicted in Figure \ref{fig:kriging}.
+For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
+Then I assign treatment with a probability that differs based on $\text{Zone}_i$.
+To avoid changes in bias due to a difference in the number of treated units, the unconditional probability is equal to 5 percent in all simulations.
+To increase the spatial autocorrelation of treatment, I increase the probability of treatment for units with $\text{Zone}_i = 1$ and hence lower the probability for units with $\text{Zone}_i = 0$.
+\footnote{
+    To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
+    \begin{equation}
+        \label{eq:cond_prob}
+        P(D_i \ \vert \ \text{Zone}_i) = (.05 + \text{Zone Plus} * \text{Zone}_i) \times \underbrace{\frac{.05}{.05 * .9 + (.05 + \text{Zone Plus}) * .1}}_{\text{Normalize } P(D_i) = 0.05}
+    \end{equation}
+    The second term normalizes probabilities so the unconditional probability stays at five percent.
+In our simulations, Zone Plus ranges from 0 which is the case where $P(D_i \vert \text{Zone}_i) = P(D_i) = 0.05$ to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.01 + 0.41 * \text{Zone}_i$.
+}
+
+The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
+The line with diamond markers is run on the full sample.
+As the level of spatial autocorrelation increases, the bias surprisingly decreases.
+The reason for this is that as treatment becomes more concentrated in the `Zones', the number of control units receiving spillovers decreases while the number of treated units receiving spillovers increases.
+In this particular data-generating process, the effect of fewer control units on the bias is larger than the bias from more treated units.
+
+The line with circle markers in Figure \ref{fig:bias_spatial_autocorr} repeats the exercise of dropping control units that share a border with treated units.
+In the case where spillovers occur on treated units, all bias is not removed when dropping control units.
+That is because we only remove $\tau_{\text{spill,control}}$ but $\tau_{\text{spill,treated}}$ remains.
+To remove the second source of bias, it is necessary to acount directly for spillovers in the estimation strategy.
+
 \end{document}

### 2021-02-22 figure-example_exposure_mappings.R
Create figures of spillover functions

@@ -1,0 +1,156 @@
+## -----------------------------------------------------------------------------
+## figure-example_exposure_mappings.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## Create examples of each exposure mapping
+## -----------------------------------------------------------------------------
+
+library("tidyverse")
+library("glue")
+library("sf")
+library("stars")
+library("units")
+library("gstat")
+library("exactextractr")
+library("fixest")
+library("doParallel")
+library("gt")
+library("magrittr")
+
+# Macbook
+setwd("~/Documents/Projects/Spatial Spillover/")
+# Research Computing
+# setwd("/projects/kybu6659/spatial_spillover/")
+
+# Load theme_kyle()
+source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/15196997e5aad41696b03c49be3bfaaca132fdf2/theme_kyle.R")
+
+# Export Options
+slides <- TRUE
+h_w_ratio <- 9/16
+# h_w_ratio <- 3/4
+
+
+
+# sim_data_misspecification()
+source("helper-sim_function_misspecification.R")
+
+
+## Load Spatial Data -----------------------------------------------------------
+# From data_prepare_counties.R
+load(file= "data/counties_and_mat.RData")
+
+us <- counties %>% summarize()
+
+
+set.seed(20210215)
+
+df <- sim_data_misspecification(drop_geometry = FALSE, normalize = TRUE) %>% 
+	st_as_sf()
+
+
+
+
+
+## Treatment Effect ------------------------------------------------------------
+
+types <- c(
+	"Within 40mi." = "spill_within", 
+	"Within 80mi." = "spill_within_large", 
+	"Within 40mi. (Additive)" = "spill_within_additive", 
+	"Within 80mi. (Additive)" = "spill_within_large_additive", 
+	"Decay" = "spill_decay", 
+	"Decay (Additive)" = "spill_decay_additive"
+)
+
+
+
+for(type in types){
+	title <- names(types)[types == type]
+	cli::cli_rule(glue("{title}: {type}"))
+
+	temp <- df %>% 
+		filter(year == 2019) %>% 
[…]

### 2021-02-22 helper-sim_function_misspecification.R

@@ -18,6 +18,7 @@
 #' @param spatial_autocorr Should there be spatial autocorrelation of treament
 #' @param zone_plus Value >= 0 and tells you how much to favor counties with values in the top 10% of the generated field
 #' @param remove_spill Should control units with spillover effects be removed
+#' @param normalize Should the treatment effects be normalized across specifications
 #' 
 #' @return a tibble of estimates of treatment effect under different scenarios. This will be used with dplyr::add_row
 #'
@@ -31,7 +32,8 @@ sim_data_misspecification <- function(
 	spill_type = "contig",
 	spatial_autocorr = FALSE,
 	zone_plus = 0.4,
-	drop_geometry = TRUE
+	drop_geometry = TRUE,
+	normalize = TRUE
 ){
 	## Create Treatment and Spillover Variables --------------------------------
 	
@@ -138,6 +140,8 @@ sim_data_misspecification <- function(
 	
 	## Spillover Variables Have Same Average Effect ----------------------------
 	
+	if(normalize) {
+		
 	counties_treat <- counties_treat %>% 
 		mutate(
 			spill_contig = 1/4 * treat_effect_spill * spill_contig / mean(spill_contig),
@@ -148,6 +152,7 @@ sim_data_misspecification <- function(
 			spill_decay = 1/4 * treat_effect_spill * spill_decay / mean(spill_decay),
 			spill_decay_additive = 1/4 * treat_effect_spill * spill_decay_additive / mean(spill_decay_additive)
 		)
+	}
 	
 	
 	## Create Panel Data -------------------------------------------------------

### 2021-02-22 sim-bias_as_treat_increase.R
Update bias simulation to include spillover onto treated units

@@ -63,7 +63,8 @@ treatment_effect_simulation <- function(
 	spill_type = "contig",
 	spatial_autocorr = FALSE,
 	zone_plus = 0.4,
-	drop_geometry = TRUE
+	drop_geometry = TRUE,
+	spill_on_treat = FALSE
 ) {
 	# Display what the function is doing
 	usethis::ui_todo("Running simulation with parameters: (n_trials= {n_trials}, treat_prob= {treat_prob}).")
@@ -84,23 +85,40 @@ treatment_effect_simulation <- function(
 			drop_geometry = drop_geometry
 		)
 		
-		te_hat <- feols(y_spill ~ treat_ind | state_county + year, data= df) %>%
-			coefficients() %>% .[["treat_ind"]]
-		
-		te_hat_drop_control <- feols(y_spill ~ treat_ind | state_county + year, 
-										   data= df %>% filter(spill_ind != 1)) %>% 
-			coefficients() %>% .[["treat_ind"]]
-		
-		te_hat_control_spill <- feols(y_spill ~ treat_ind + spill_ind | state_county + year, 
-									  data= df) %>%
-			coefficients() %>% .[["treat_ind"]]
-		
-		te_hat_all_spill <- feols(y_spill ~ treat_ind + spill_ind + spill_ind_treat | state_county + year, 
-								  data= df) %>%
-			coefficients() %>% .[["treat_ind"]]
+		if(spill_on_treat) {
+			te_hat <- feols(y_spill_treat ~ treat_ind | state_county + year, data= df) %>%
+				coefficients() %>% .[["treat_ind"]]
+			
+			te_hat_drop_control <- feols(y_spill_treat ~ treat_ind | state_county + year, 
+										 data= df %>% filter(spill_ind != 1)) %>% 
+				coefficients() %>% .[["treat_ind"]]
+			
+			# te_hat_control_spill <- feols(y_spill_treat ~ treat_ind + spill_ind | state_county + year, 
+			# 							  data= df) %>%
+			# 	coefficients() %>% .[["treat_ind"]]
+			# 
+			# te_hat_all_spill <- feols(y_spill_treat ~ treat_ind + spill_ind + spill_ind_treat | state_county + year, 
+			# 						  data= df) %>%
[…]

### 2021-02-22 sim-misspecification_of_spillover.R
Change from Donuts to Rings

@@ -70,7 +70,7 @@ df <- sim_data_misspecification(drop_geometry=FALSE) %>%
 y <- "spill_decay"
 x <- "spill_within_large"
 
-# Donuts 80
+# Rings 80
 formula <- as.formula(glue("y_{y} ~ treat_ind + post:spill_0_20 + spill_20_30:post + spill_30_40:post ", 
 						   "+ spill_40_60:post + spill_60_80:post | state_county + year"))
 
@@ -142,9 +142,9 @@ doParallel::registerDoParallel(10)
 dgp_types <- c(
 	"Within 40mi." = "spill_within", 
 	"Within 80mi." = "spill_within_large", 
+	"Decay" = "spill_decay", 
 	"Within 40mi. (Additive)" = "spill_within_additive", 
 	"Within 80mi. (Additive)" = "spill_within_large_additive", 
-	"Decay" = "spill_decay", 
 	"Decay (Additive)" = "spill_decay_additive"
 )
 
@@ -152,14 +152,13 @@ estimation_types <- c(
 	"TWFE (No Spillovers)" = "twfe",
 	"Within 40mi." = "spill_within", 
 	"Within 80mi." = "spill_within_large", 
-	"Within 100mi." = "spill_within_100",
 	"Within 40mi. (Additive)" = "spill_within_additive", 
 	"Within 80mi. (Additive)" = "spill_within_large_additive", 
 	"Decay" = "spill_decay", 
 	"Decay (Additive)" = "spill_decay_additive",
-	"Donuts (0-20, 20-30, 30-40)" = "donuts_small",
-	"Donuts (0-20, 20-30, 30-40, 40-60, 60-80)" = "donuts",
-	"Donuts (0-20, 20-30, 30-40, 40-60, 60-80) (Additive)" = "donuts_additive"
+	"Rings (0-20, 20-30, 30-40)" = "donuts_small",
+	"Rings (0-20, 20-30, 30-40, 40-60, 60-80)" = "donuts",
+	"Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive)" = "donuts_additive"
 )
 
 results <- foreach(i = 1:n_trials, .combine = 'rbind') %dopar% {
@@ -241,9 +240,9 @@ doParallel::registerDoParallel(10)
 dgp_types <- c(
 	"Within 40mi." = "spill_within", 
 	"Within 80mi." = "spill_within_large", 
[…]

### 2021-02-22 latex/slides/Spillover_slides.tex
Update Slides for LEPHD Brown Bag

@@
-\documentclass[aspectratio=43]{beamer}
+\documentclass[aspectratio=169]{beamer}
 % Metropolis Theme ------------------------------------------------------------------------------
@@
 % Title ------------------------------------------------------------------------------
-\title{Difference-in-Differences with Spatial Spillover}
+\title{Difference-in-Differences with Spatial Spillovers}
 \date{\today}
@@
 \usepackage{threeparttable}
+\usepackage{dcolumn}
+
+% Table Highlighting
+\usepackage[beamer,customcolors]{hf-tikz}
+\usetikzlibrary{calc}
+\usetikzlibrary{fit,shapes.misc}
+
+% To set the hypothesis highlighting boxes red.
+\tikzset{hl/.style={
+    set fill color=red!80!black!40,
+    set border color=red!80!black,
+  },
+}
+\newcommand\marktopleft[1]{%
+    \tikz[overlay,remember picture] 
+        \node (marker-#1-a) at (0,1.5ex) {};%
+}
+\newcommand\markbottomright[1]{%
+    \tikz[overlay,remember picture] 
+        \node (marker-#1-b) at (0,0) {};%
+    \tikz[red, ultra thick, overlay, remember picture, inner sep=4pt]
+        \node[draw, rectangle, fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
+}
 
@@
 \begin{frame}{Spatial Spillovers}
-    Researchers aim to estimate the average treatment effect on the treated: 
+    Researchers aim to estimate the \textbf{average treatment effect on the treated}: 
     \[
@@
 
+    Estimation is complicated by \textbf{Spillover Effects}
+
     \vspace{5mm}
-    Spillover effects are when effect of treatment extend over boundaries such as states, counties, etc.
+    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries such as states, counties, etc.
 
     \begin{itemize}
-        \item e.g. large employer opening/closing in a county have positive employment effects on nearby counties
+        \item e.g. large employer opening/closing in a \textbf{treated} county have positive employment effects on \textit{nearby counties}
     \end{itemize}
@@
 \begin{frame}{Bias from Spatial Spillovers}
+
+    \onslide<1->{
         The canonical difference-in-differences estimate is: 
+        \only<1>{
             \[ 
@@
             \]
+        }
+        \only<2>{
+            \[ 
+                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
+                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{purple} Spillover on Control}}}
+            \]
+        }
+        \only<3>{
+            \[ 
+                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{red} Spillover on Treated}}} -
+                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{purple} Spillover on Control}}}
+            \]
+        }
+    }
 
     Two problems in presence of spillover effects:
+
     \begin{itemize}
-        \item \textbf{Spillover onto Control Units:}
+        \onslide<2->{
+            \item {\bf \color{purple} Spillover onto Control Units:}
 
             Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment
+        }
 
+        \onslide<3->{
             \vspace{2.5mm}
-        \item \textbf{Spillover onto other Treated Units:}
+            \item {\bf \color{red} Spillover onto other Treated Units:}
 
             Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
+        }
     \end{itemize}
@@
 
-% Just TE
-\imageframe{../../figures/figure-map_te.png}
-
-% TE + Spill Control
-\imageframe{../../figures/figure-map_te_spill_control.png}
-
-% TE + Spill Control + Spill Treat
-\imageframe{../../figures/figure-map_te_spill_all.png}
+% Grey out overlays
+\setbeamercovered{transparent}
 
@@
     \begin{itemize}
-        \item[1--] Using a potential outcomes framework, I decompose the difference-in-differences estimator in to three parts:
+        \item[1--] Using a potential outcomes framework, I decompose the difference-in-differences estimator into three parts:
         \begin{itemize}
-            \item Direct Effect of Treatment
-            \item Spillover onto Treated Units
-            \item Spillover onto Control Units
+            \item Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units
         \end{itemize}
 
-        \item[2--] Using Monte Carlo simulations:
+        \pause
+        \item[2--] Analyze effectiveness of common ad-hoc adjustments done by researchers
         \begin{itemize}
-            \item Show when biases are relatively large
-            \item Analyze effectiveness of current adjustments done by applied researchers 
+            \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers
+            \item `Rings' are able to estimate spillover effects while still removing all bias
         \end{itemize}
 
-        \item[3--] Revisit \citet{Kline_Moretti_2014} analysis of the Tennessee Valley Authority
+        \pause
+        \item[3--] Apply framework to Urban Economics
+        \begin{itemize}
+            \item Revisit \citet{Kline_Moretti_2014a} analysis of the Tennessee Valley Authority
+
+            \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}
+        \end{itemize}
     \end{itemize} 
@@
 
-% @TODO: Literature Review
 \begin{frame}{Contribution}
+
+    {\footnotesize
 
@@
 
-    % \begin{itemize}
-    %     \item My derivation generalizes the above papers by being in the form of potential outcomes.
-    % \end{itemize}
+    \begin{itemize}
+        \item I generalize the work by deriving the bias in terms of potential outcomes and show how to estimate treatment effects by removing spillover effects
+    \end{itemize}
 
+    \pause
     \underline{Potential Outcome Framework for Spillovers}
@@
     \begin{citecolor}
-        [\citet{Vazquez-Bare_2019}, \citet{Angelucci_DiMaro_2016}, \citet{Angrist_2014}]        
+        [\citet{Miguel_Kremer_2004}, \citet{Vazquez-Bare_2019}, \citet{Angelucci_DiMaro_2016}, \citet{Angrist_2014}]        
     \end{citecolor}
 
+    \begin{itemize}
+        \item These papers consider spillovers in network clusters. I focus on spatial setting
+    \end{itemize}
+
+    \pause
     \underline{Place-based Policies}
@@
     \begin{citecolor}
-        [\citet{Kline_Moretti_2014b} and \citet{Kline_Moretti_2014}]
+        [\citet{Kline_Moretti_2014b}, \citet{Kline_Moretti_2014a}, \citet{Busso_Gregory_Kline_2013}, and \citet{Neumark_Kolko_2010}]
     \end{citecolor}
 
-    % \begin{itemize}
-    %     \item I highlight the need to control for spillovers to properly estimate local effects of policies.
-    % \end{itemize}
+    \begin{itemize}
+        \item I highlight the need to control for general equilibrium effects to properly estimate local effects of policies
+    \end{itemize}
+    }
 \end{frame}
@@
     For exposition, I will label units as counties.
-Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{This form adapts the framework of \citet{Vazquez-Bare_2019} for the diff-in-diff setting.}
+Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{I extend this into an event study framework in the paper, but the intuition is the same as in the $2 \times 2$ setting.}
 
     \begin{itemize}
-        \item Let $Y_{it}(D_i, h_i(\vec{D}))$ be the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.
+        \item $Y_{it}(D_i, \textcolor{blue}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.
 
@@
 
-        \item The function $h_i(\vec{D})$ maps the entire treatment vector into a scalar that completely determines the spillover.
+        \pause
+        \item The function $\textcolor{blue}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping' which can be a scalar or a vector.
 
-        \item In the world with no treatment, $\vec{0}$, we say $h_i(\vec{0}) = 0$.
+        \pause
+        \item No exposure is when $\textcolor{blue}{h(\vec{D}, i)} = \vec{0}$.
     \end{itemize}
 \end{frame}
+
+% Grey out
+% \setbeamercovered{transparent}
 
@@
 
-        $h_i(\vec{D})$ equals 1 if there is a treated unit within $x$-miles of unit $i$ and equals 0 otherwise
+        $\textcolor{blue}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.
 
-        \vspace{2.5mm}
-        \item \textbf{Average treatment among $k$-nearest neighbors:}
+        \begin{itemize}
+            \item e.g. library access where $x$ is the maximum distance people will travel
 
-        $h_i(\vec{D}) = \sum_{j = 1}^k D_{n(i,j)} / k$ where $n(i,j)$ represents the j-th closest neighbor to unit $i$.
+            \item Spillovers are non-additive
+        \end{itemize}
 
@@
 \end{frame}
+
+\imageframe{../../figures/figure-spill_within.png}
+
+\begin{frame}{Examples of $h_i(\vec{D})$}
+
+    Examples of $h_i(\vec{D})$:
+
+    \begin{itemize}
+        \item \textbf{Treatment within $x$ miles:}
+
+        $\textcolor{blue}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.
+
+        \begin{itemize}
+            \item e.g. library access where $x$ is the maximum distance people will travel
+
+            \item Spillovers are non-additive
+        \end{itemize}
+
+        \vspace{2.5mm}
+        \item \textbf{Number of Treated within $x$ miles:}
+
+        $\textcolor{blue}{h(\vec{D}, i)} = \sum_{j = 1}^k 1(d(i, j) \leq x)$.
+
+        \begin{itemize}
+            \item e.g. large factories opening
+
+            \item Agglomeration economies suggest spillovers are additive
+        \end{itemize}
+
+    \end{itemize}
+\end{frame}
+
+\imageframe{../../figures/figure-spill_within_additive.png}
 
@@
 
-    This is the direct effect in the absense of spillovers.
+    \vspace{10mm}
+    This is the direct effect in the absense of exposure to spillovers.
 \end{frame}
@@
 \begin{frame}{Parallel Trends}
-    I assume a modified version of the parallel trends assumption: 
-    \[
-        \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 1, \vec{D} = 0 \right] 
-    \] \[
-        \quad =
-        \mathbb{E}\left[ Y_{i,1}(0, 0) - Y_{i,0}(0, 0) \mid D_i = 0, \vec{D} = 0 \right],
-    \]
+    I assume a modified version of the parallel counterfactual trends assumption: 
+    \begin{align*}
+        &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] \\
+        = \ &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big],
+    \end{align*}
 
     \vspace{5mm}
-    In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
+    In the \textit{complete absence of treatment }(not just the absence of individual $i$'s treatment):
+
+    Changes in outcomes does not depend on treatment status
 
@@
     \begin{align*}
-        &\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right] \\
-        &\quad = 
+        \mathbb{E}\left[\hat{\tau}\right] &= \underbrace{\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\[3mm]
+        \pause&= 
         \textcolor{green}{\mathbb{E} \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
-        &\quad\quad + 
+        &\quad + \quad 
         \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
-        &\quad\quad - 
-        \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\
-        &\quad \equiv \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
+        &\quad - \quad  
+        \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
+        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
     \end{align*}
@@
     \]
-
-    \begin{table}
-        \caption{Bias from Spillovers}
-        \begin{tabular}{|l|cc|}
-            \hline
-            & + Spillover & - Spillover \\ \hline
-            onto Treated & + Bias & - Bias \\
-            onto Control & - Bias & + Bias \\
-            \hline
-        \end{tabular}
-    \end{table}
 \end{frame}
 
-\begin{frame}{Example of Bias}
+\begin{frame}{Example of Bias: Large Factory Opening}\label{slide:example_bias}
+    \textbf{Control Spillover:}
+
+    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) = 1$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+
     \textbf{Treated Spillover:}
 
-    $Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) = -0.5$ if county $i$ shares a border with a treated county and $0$ otherwise.
+    $Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) = 0.5$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
 
-    \textbf{Control Spillover:}
-
-    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) = 1$ if county $i$ shares a border with a treated county and $0$ otherwise.
-
+    \pause
     Then, the bias term is 
     \begin{align*}
-        &-0.5 * \text{\% of treated counties sharing a border with a treated county} \\
-        &-1 * \text{\% of treated counties sharing a border with a treated county}
-    \end{align*}
-\end{frame}
-
-\begin{frame}{Partial Identification}
-    Researchers can use the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.
-
-    To formalize this, I follow the literature on partial identification for treatment effects
-    \begin{citecolor}
-        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
-    \end{citecolor}
-\end{frame}
-
-\begin{frame}{Partially-identified Set}
-    Following \citet{Rambachan_Roth_2020} and \citet{Manski_Pepper_2018}, researchers can provide bounds to the maximum spillovers.
-
-    Let $\Delta$ denote the interval of potential biases: 
-    \begin{align*}
-        \Delta &\equiv [\underline{\Delta}, \overline{\Delta}] \\
-        &= \left[ \min \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}, \ \max \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \right] 
+        &0.5 * \text{\% of treated counties within 40 miles of another treated county} \\
+        &-1 * \text{\% of treated counties within 40 miles of a treated county}
     \end{align*}
 
-    The partially identified set is formed by \[ 
-        \left[\hat{\tau} - \underline{\Delta} , \ \hat{\tau} + \overline{\Delta} \right]    
-    \]
-
-\end{frame}
-
-\begin{frame}{Bias-adjusted Inference}
-
-    Inference can be done following \citet{Rambachan_Roth_2020} by creating a Fixed-Length Confidence Interval: 
-    \[ 
-        \left[
-            \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}
-        \right]
-    \]
-
-    These standard errors should account for the spatial structure of outcomes following \citet{Conley_1999}.
+    \hyperlink{slide:partial_identification}{\beamerbutton{Partial Identification}}
 \end{frame}
@@
 % ------------------------------------------------------------------------------
-\section{Simulations}
+\section{Estimation with Spillovers}
 % ------------------------------------------------------------------------------
@@
     \begin{itemize}
-        \item Simulated the following Data Generating Process \begin{align*}
-            y_{it} &= -2 + \mu_t + \mu_i + \tau_{\text{direct}} D_{it} + \tau_{\text{spillover, control}} (1-D_{it}) \text{Near}_{it} \\ 
-            &\quad + \tau_{\text{spillover, treated}} D_{it} \text{Near}_{it} + \varepsilon_{it}
+        \item Data Generating Process 
+        \begin{align*}
+            y_{it} &= \mu_t + \mu_i + \textcolor{green}{\tau_{\text{direct}}} D_{it} + \textcolor{purple}{\tau_{\text{spillover, control}}} (1-D_{it}) \text{Within 40mi.}_{it} \\ 
+            &\quad + \textcolor{red}{\tau_{\text{spillover, treated}}} D_{it} \text{Within 40mi.}_{it} + \varepsilon_{it}
         \end{align*}
@@
 
-        \item $\text{Near}_{it}$ is an indicator for having your county centroid be within 40 miles of a treated unit.
+        \item $\text{Within 40mi.}_{it}$ is an indicator for having your county center of population be within 40 miles of a treated unit.
 
-        \item $\tau_{\text{direct}} = 2$, $\tau_{\text{spillover, control}} = 1$ and $\tau_{\text{spillover, treat}} = -0.5$.
+        \item $\textcolor{green}{\tau_{\text{direct}}} = 2$, $\textcolor{purple}{\tau_{\text{spillover, control}}} = 1$ and $\textcolor{red}{\tau_{\text{spillover, treat}}} \in \{0, 0.5\}$.
     \end{itemize}
@@
 
-        \item Estimate the following equation: \[ 
-            y_{it} = \alpha + \mu_t + \mu_i + \tau D_{it} + \epsilon_{it}    
-        \]
+        \item Estimate via TWFE: \begin{equation*}
+            y_{it} = \mu_t + \mu_i + \tau D_{it} + \epsilon_{it}    
+        \end{equation*}
 
@@
 \begin{frame}{Solution: Removing ``contaminated'' controls}
-    A common solution to the problem of spillover is to restimate without neighboring control units and see what happens to the bias.
+    A common solution to the problem of spillover is to restimate on a subsample with neighboring control units removed.
 
-    This simulation assumes the correct ``contaminated'' control units, i.e. only control units with $h_i(\vec{D}) \neq 0$, which is not possible for researchers.
+    This simulation drops only units with $\text{Within 40mi.}_{it} = 1$. The exact exposure mapping is typically not observable for researchers, so this is best case scenario.
 \end{frame}
@@
 
-\begin{frame}{Source of Bias 2: Treated Units}
-    Simulation 2:
+\begin{frame}{Why Removing Controls Doesn't Work Well}
+    \begin{itemize}
+        \item[1.] Lose precision in treatment effect estimate by dropping control units
+        \item[2.] If there are spillovers on treated units, removing controls won't remove both sources of bias. 
+    \end{itemize}
+
+    I repeat the same simulations but with $\textcolor{red}{\tau_{\text{spillover, treat}}} = 0.5$
+
+\end{frame}
+
+\imageframe{../../figures/figure-bias_fix_treat_slides.png}
+
+\begin{frame}{Solution: Parametrize potential outcomes}
+    Another option is to directly control for spillovers by parametrizing the exposure mapping.
+
+    This is not observable to a researcher which raises the question:
+
+    Are there specifications that work well even if the spillovers are misspecified?
+\end{frame}
+
+\begin{frame}{Robustness to Misspecification}
+    Generate data using the same data-generating process as before but with different spillover functions:
+
+    \[ 
+        y_{\it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill,control}} * (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it}
+    \]
+
+    Then, I estimate each data-generating process using (potentially) misspecified $\tilde{h}(\vec{D}, i)$ and report the average estimate bias.
+
+\end{frame}
+
+\begin{frame}{Specifications of $h(\vec{D}, i)$}
 
     \begin{itemize}
-        \item I now add in the bias from spillover of treated units on to other treated units.
+        \item \textit{Within $40/80$mi.}:
+        \begin{itemize}
+            \item Inidicator for nearest treated unit being within $40/80$ miles.
+        \end{itemize}
 
-        \item This source of bias only occurs when treated units are located next to eachother, so the magnitude of bias depends on spatial autocorrelation of $D_{it}$.
+        \item \textit{Within $40/80$mi. (Additive)}: 
+        \begin{itemize}
+            \item Number of treated units being within $40/80$ miles.
+        \end{itemize}
 
-        \item Using a method from geosciences, I generate correlated ``fields'' across the US.
+    \end{itemize}
 
-        \item Then, for the counties in the top 10\% of values (hot spots in the field), I increase the probability of treatment.
-
-        \item The unconditional probability remains fixed at 10\%.
-    \end{itemize}
 \end{frame}
 
-\imageframe{../../figures/figure-krig_slides.png}
+\imageframe{../../figures/figure-spill_within_large.png}
+\imageframe{../../figures/figure-spill_within_large_additive.png}
 
-\imageframe{../../figures/figure-spcorr_high_map_te_spill_all.png}
+\begin{frame}{Specifications of $h(\vec{D}, i)$}
 
-\imageframe{../../figures/figure-spcorr_low_map_te_spill_all}
+    \begin{itemize}
+        \item \textit{Within $40/80$mi.}:
+        \begin{itemize}
+            \item Inidicator for nearest treated unit being within $40/80$ miles.
+        \end{itemize}
 
-\imageframe{../../figures/figure-bias_from_spatial_autocorr_slides.png}
+        \item \textit{Within $40/80$mi. (Additive)}: 
+        \begin{itemize}
+            \item Number of treated units being within $40/80$ miles.
+        \end{itemize}
 
-\imageframe{../../figures/figure-bias_fix_spatial_autocorr_slides.png}
+        \item \textit{Decay}: 
+        \begin{itemize}
+            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
+        \end{itemize}
 
-% ------------------------------------------------------------------------------
-% \section{Estimation with Spillovers}
-% ------------------------------------------------------------------------------
+        \item \textit{Decay (Additive)}: 
+        \begin{itemize}
+            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
+        \end{itemize}
 
-\begin{frame}{Spillovers as estimand of interest}
+    \end{itemize}
+
+\end{frame}
+
+\imageframe{../../figures/figure-spill_decay.png}
+\imageframe{../../figures/figure-spill_decay_additive.png}
+
+\begin{frame}{Specifications of $h(\vec{D}, i)$}
+
+    \begin{itemize}
+        \item \textit{Within $40/80$mi.}:
+        \begin{itemize}
+            \item Inidicator for nearest treated unit being within $40/80$ miles.
+        \end{itemize}
+
+        \item \textit{Within $40/80$mi. (Additive)}: 
+        \begin{itemize}
+            \item Number of treated units being within $40/80$ miles.
+        \end{itemize}
+
+        \item \textit{Decay}: 
+        \begin{itemize}
+            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
+        \end{itemize}
+
+        \item \textit{Decay (Additive)}: 
+        \begin{itemize}
+            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
+        \end{itemize}
+
+        \item \textit{Rings}: 
+        \begin{itemize}
+            \item Set of concentric rings. For each ring, indicator for nearest treated unit being within that distance bin
+        \end{itemize}
+
+        \item \textit{Rings (Additive)}: 
+        \begin{itemize}
+            \item Set of concentric rings. For each ring, number of treated units being within that distance bin
+        \end{itemize}
+    \end{itemize}
+
+\end{frame}
+
+\imageframe{../../figures/figure-spill_ring.png}
+
+\begin{frame}
+
+    \begin{table}[!tb]
+        \caption{Bias from Misspecification of Spillovers}
+        \label{tab:misspecification}
+
+        \begin{adjustbox}{width = 1.1\textwidth, center}
+            \begin{threeparttable}
+                \begin{tabular}{@{} l rrrrrr @{}}
+                    % Head
+                    \toprule
+                    & \multicolumn{6}{c}{Data-Generating Process} \\
+                    \cmidrule{2-7}
+
+                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
+                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
+
+                    % Body
+                    \midrule
+
+                    % \input{../../tables/misspecification_slides.tex}
+                    TWFE (No Spillovers) & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ \\ \midrule
+                    \marktopleft{c1}Within 40mi. & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
+                    Within 80mi. & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c1}
+                    \onslide<2->{
+                        \\ \midrule
+                        Within 40mi. (Additive) & $0.043$ & $0.221$ & $-0.006$ & $0.177$ & $0.174$ & $0.143$ \\ 
+                        Within 80mi. (Additive) & $0.034$ & $0.134$ & $-0.012$ & $-0.009$ & $0.099$ & $-0.010$ \\ \midrule
+                        Decay 80mi. & $-0.159$ & $0.070$ & $-0.174$ & $0.014$ & $-0.009$ & $-0.033$ \\ 
+                        Decay 80mi. (Additive) & $-0.023$ & $0.148$ & $-0.084$ & $0.019$ & $0.088$ & $-0.008$
+                    }
+                    \onslide<3->{
+                        \\ \midrule
+                        \marktopleft{c2}Rings (0-20, 20-30, 30-40) & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
+                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c2}\\ 
+                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $0.036$ & $0.134$ & $-0.008$ & $-0.008$ & $0.100$ & $-0.009$ 
+                    }
+
+                    \\ \bottomrule
+                \end{tabular}
+            \end{threeparttable}
+        \end{adjustbox}
+    \end{table}
+
+\end{frame}
+
+\begin{frame}{Spillovers as Estimand of Interest}
     Until now, we assumed our estimand of interest is $\textcolor{green}{\tau_{\text{direct}}}$.
@@
 
-        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on others treatment? (This is what you should consider if you are a policy maker)
+        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on treatment of neighbors? 
     \end{itemize}
 
-    To estimate the spillover effects, we have to parameterize $h_i(\vec{D})$ function and the potential outcomes function $Y_i(D_i, h_i(\vec{D}))$.
+    To estimate the spillover effects, we have to parameterize $h(\vec{D}, i)$ function and the potential outcomes function $Y_i(D_i, h(\vec{D}, i))$.
 \end{frame}
 
-% @kylebutts @TODO: show parametrization fixes biases.
+\begin{frame}{Estimation of Spillover Effects}
+    To see which specifications can predict spillover effects well, I estimate the spillover effects for each control unit, $\hat{\beta}_{\text{spill, control}} * \tilde{h}(\vec{D}, i)$.
 
-% \begin{frame}{Including Spillovers in Regression}
-%    How well does the modified specification do with misspecified spillovers?
-% \end{frame}
+    Then calculate \[ 
+        1 - \frac{
+                \overbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}^{\text{Mean Square Prediction Error}}
+            }{
+                \underbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}_{\text{Normalization}}
+            }    
+    \]
+
+    This gives the proportion of spillovers explained by $\tilde{h}(\vec{D}, i)$
+
+\end{frame}
+
+\begin{frame}
+    \begin{table}[!tb]
+        \caption{Percent of Spillovers Predicted by Specification}
+        \label{tab:misspecification_mspe}
+
+        \begin{adjustbox}{width = 1.1\textwidth, center}
+            \begin{threeparttable}
+                \begin{tabular}{@{} l rrrrrr @{}}
+                    % Head
+                    \toprule
+                    & \multicolumn{6}{c}{Data-Generating Process} \\
+                    \cmidrule{2-7}
+
+                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
+                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
+
+                    % Body
+                    \midrule
+
+                    % \input{../../tables/misspecification_slides.tex}
+                    TWFE (No Spillovers) & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ \\ \midrule
+                    \marktopleft{c3}Within 40mi. & $99.4\%$ & $25.9\%$ & $85.6\%$ & $38.8\%$ & $59.5\%$ & $56.1\%$ \\ 
+                    Within 80mi. & $39.8\%$ & $96.2\%$ & $34.3\%$ & $71.7\%$ & $85.6\%$ & $68.0\%$ \markbottomright{c3}
+                    \onslide<2->{
+                    \\ \midrule
+                        Within 40mi. (Additive) & $85.3\%$ & $21.2\%$ & $99.5\%$ & $40.6\%$ & $52.0\%$ & $60.7\%$ \\ 
+                        Within 80mi. (Additive) & $45.8\%$ & $61.8\%$ & $47.2\%$ & $98.4\%$ & $71.0\%$ & $93.6\%$ \\ \midrule 
+                        Decay 80mi. & $60.1\%$ & $82.5\%$ & $52.7\%$ & $75.8\%$ & $97.5\%$ & $82.2\%$ \\ 
+                        Decay 80mi. (Additive) & $60.7\%$ & $56.9\%$ & $63.8\%$ & $93.5\%$ & $79.0\%$ & $98.7\%$ 
+                    }
+                    \onslide<3->{
+                        \\ \midrule 
+                        \marktopleft{c4}Rings (0-20, 20-30, 30-40) & $98.4\%$ & $23.7\%$ & $85.9\%$ & $37.5\%$ & $58.9\%$ & $56.2\%$ \\ 
+                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $96.6\%$ & $91.7\%$ & $84.2\%$ & $72.7\%$ & $91.9\%$ & $78.4\%$ \\ 
+                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $83.5\%$ & $57.4\%$ & $97.6\%$ & $95.0\%$ & $73.5\%$ & $94.9\%$\markbottomright{c4} 
+                    }
+
+                    \\ \bottomrule
+                \end{tabular}
+            \end{threeparttable}
+        \end{adjustbox}
+    \end{table}
+
+    \onslide<3->{
+        \textbf{Donuts perform best at estimating spillover effects.}
+
+        \textbf{It is important to get Additive vs. Non-Additive correct.}
+    }
+\end{frame}
 
 % ------------------------------------------------------------------------------
-\section{Application: Tennessee Valley Authority}
+\section{Application in Urban Economics}
 % ------------------------------------------------------------------------------
@@
 \begin{frame}{Tennessee Valley Authority}
-    \citet{Kline_Moretti_2014} look at the long-run impacts of the Tennessee Valley Authority (TVA).
+    \citet{Kline_Moretti_2014a} look at the long-run impacts of the Tennessee Valley Authority (TVA).
 
@@
 \begin{frame}{Identification}
-    \citet{Kline_Moretti_2014} run the county-level difference-in-differences  specification: 
+    \citet{Kline_Moretti_2014a} run the county-level difference-in-differences  specification: 
     \begin{equation}\label{eq:tva_spillover}
@@
     \begin{itemize}
-        \item Agricultural employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley
+        \item Agricultural employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley (negative spillover on control units)
 
-        \item Manufacturing jobs that would have been created in the control units in the absence of treatment might move to the Tennessee Valley
+        \item Manufacturing jobs that would have been created in the control units in the absence of treatment might move to the Tennessee Valley (negative spillover on control units)
 
@@
     \begin{equation}
-        \Delta y_c = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + \Delta \varepsilon_c
+        \Delta y_c = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Ring}(d)\delta_d + X_{i, 1940} \beta + \Delta \varepsilon_c
     \end{equation}
@@
     \begin{itemize}
-        \item $\text{Between}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
+        \item $\text{Ring}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
         \[ d \in \left\{ (0, 50], (50, 100], (100, 150] \right\} \]
@@
                 }
-                \\
 
-                % \input{../../tables/tva_replication_slides.tex}
-                \bottomrule
+                \\ \bottomrule
             \end{tabular}
@@
 
+\begin{frame}{Identification Strategies and Place-Based Policies}
+
+    The literature on federal Enterprise Zones, place-based policy that gives tax breaks to businesses that locate within the boundary, has found conflicting results, suggesting positive or near-zero effects of the program \citep{Neumark_Young_2019}.
+
+    \begin{itemize}
+        \pause
+        \item \citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program.
+They find significant large reduction of poverty.
+
+        \pause
+        \item \citet{Neumark_Kolko_2010} compare census tracts in Empowerment Zones to census tracts within 1,000 feet of the Zone. They find near-zero effects on poverty.
+    \end{itemize}
+
+    \pause
+    My framework can explain both of these results.
+If census tracts just outside the Empowerment Zones also benefit from the policy, then the estimates of \citet{Neumark_Kolko_2010} are attenuated towards zero
+
+\end{frame}
+
 \section{Conclusion}
 
-\begin{frame}{To-do:}
+\begin{frame}{Conclusion}
     \begin{itemize}
-        \item Include Monte-Carlo simulations on misspecification of spillovers
+        \item I decomposed the TWFE estimate into the direct effect and two spillover terms
 
-        \item Extend bias to settings with differential timing of treatment
+        \item I showed that a set of concentric rings allows for estimation of the direct effect of treatment and they are able to model spillovers well
+
+        \item For place-based policies, I show the importance of considering spatial spillovers when estimating treatment effects
+
+        \item More generally, identification strategies that use very close control units in order to minimize differences in unobservables should consider the problems with treatment effect spillovers.
     \end{itemize}
@@
 
-\begin{frame}
-    \begin{center}
-        \Large \textbf{Thank you!}
-    \end{center}
+% ------------------------------------------------------------------------------
+\appendix\section{Appendix}
+% ------------------------------------------------------------------------------
+
+\begin{frame}{Partial Identification}\label{slide:partial_identification}
+    Researchers can use the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.
+
+    To formalize this, I follow the literature on partial identification for treatment effects
+    \begin{citecolor}
+        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
+    \end{citecolor}
+\end{frame}
+
+\begin{frame}{Partially-identified Set}
+    Following \citet{Rambachan_Roth_2020} and \citet{Manski_Pepper_2018}, researchers can provide bounds to the maximum spillovers.
+
+    Let $\Delta$ denote the interval of potential biases: 
+    \begin{align*}
+        \Delta &\equiv [\underline{\Delta}, \overline{\Delta}] \\
+        &= \left[ \min \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}, \ \max \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \right] 
+    \end{align*}
+
+    The partially identified set is formed by \[ 
+        \left[\hat{\tau} - \underline{\Delta} , \ \hat{\tau} + \overline{\Delta} \right]    
+    \]
+
+\end{frame}
+
+\begin{frame}{Bias-adjusted Inference}
+
+    Inference can be done following \citet{Rambachan_Roth_2020} by creating a Fixed-Length Confidence Interval: 
+    \[ 
+        \left[
+            \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}
+        \right]
+    \]
+
+    These standard errors should account for the spatial structure of outcomes following \citet{Conley_1999}.
+
+    \hyperlink{slide:example_bias}{\beamerbutton{Back to Example of Bias}}
 \end{frame}

### 2021-02-22 latex/slides_short/Spillover_slides_short.tex
Update Slides for LEPHD Brown Bag

--- 2021-02-22 latex/slides/Spillover_slides.tex
@@
 \begin{frame}{Spatial Spillovers}
-    Researchers aim to estimate the \textbf{average treatment effect on the treated}: 
+    Researchers aim to estimate the average treatment effect on the treated: 
     \[
@@
 
-    Estimation is complicated by \textbf{Spillover Effects}
-
     \vspace{5mm}
-    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries such as states, counties, etc.
+    Spillover effects are when effect of treatment extend over boundaries such as states, counties, etc.
 
     \begin{itemize}
-        \item e.g. large employer opening/closing in a \textbf{treated} county have positive employment effects on \textit{nearby counties}
+        \item e.g. large employer opening/closing in a county have positive employment effects on nearby counties
     \end{itemize}
@@
 
-\begin{frame}{Outline}
-
-    \begin{itemize}
-        \item[1--] Using a potential outcomes framework, I decompose the difference-in-differences estimator into three parts:
-        \begin{itemize}
-            \item Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units
-        \end{itemize}
-
-        \pause
-        \item[2--] Analyze effectiveness of common ad-hoc adjustments done by researchers
-        \begin{itemize}
-            \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers
-            \item `Rings' are able to estimate spillover effects while still removing all bias
-        \end{itemize}
-
-        \pause
-        \item[3--] Apply framework to Urban Economics
-        \begin{itemize}
-            \item Revisit \citet{Kline_Moretti_2014a} analysis of the Tennessee Valley Authority
-
-            \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}
-        \end{itemize}
-    \end{itemize} 
-\end{frame}
-
 \begin{frame}{Contribution}
@@
     \begin{itemize}
-        \item These papers consider spillovers in network clusters. I focus on spatial setting
+        \item I focus on a spatial setting whereas these papers consider spillovers in network clusters
     \end{itemize}
@@
 
+        \pause
         \item $\vec{D} \in \{0,1\}^N$ is the vector of all units treatments.
@@
 
-\imageframe{../../figures/figure-spill_within.png}
+\imageframe{../../figures/figure-spill_within_large.png}
 
@@
 
-\imageframe{../../figures/figure-spill_within_additive.png}
+\imageframe{../../figures/figure-spill_within_large_additive.png}
 
@@
     \vspace{5mm}
-    In the \textit{complete absence of treatment }(not just the absence of individual $i$'s treatment):
-
-    Changes in outcomes does not depend on treatment status
+    In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
 
@@
 
-\begin{frame}{Example of Bias: Large Factory Opening}\label{slide:example_bias}
-    \textbf{Control Spillover:}
+% ------------------------------------------------------------------------------
+\section{Estimation}
+% ------------------------------------------------------------------------------
 
-    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) = 1$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+\begin{frame}{Problems with "Dropping Bad Controls"}
+    It is common in empirical applications to drop control units near the treated units when estimating the direct effect of treatment.
 
-    \textbf{Treated Spillover:}
+    This is not recommended for two reasons:
 
-    $Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) = 0.5$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+    \begin{itemize}
+        \item[1.] If not all control units that experience spillover effects are removed, then bias remains
 
-    \pause
-    Then, the bias term is 
-    \begin{align*}
-        &0.5 * \text{\% of treated counties within 40 miles of another treated county} \\
-        &-1 * \text{\% of treated counties within 40 miles of a treated county}
-    \end{align*}
+        \item[2.] There is a second source of bias, the spillover effects on treated units, that still remains
+    \end{itemize}
 
-    \hyperlink{slide:partial_identification}{\beamerbutton{Partial Identification}}
 \end{frame}
@@
 
-\begin{frame}{Monte Carlo Simulations}
+\begin{frame}{Spillovers as estimand of interest}
+    Until now, we assumed our estimand of interest is $\textcolor{green}{\tau_{\text{direct}}}$.
+
+    However, the two other spillover effects are of interest as well:
     \begin{itemize}
-        \item Data Generating Process 
-        \begin{align*}
-            y_{it} &= \mu_t + \mu_i + \textcolor{green}{\tau_{\text{direct}}} D_{it} + \textcolor{purple}{\tau_{\text{spillover, control}}} (1-D_{it}) \text{Within 40mi.}_{it} \\ 
-            &\quad + \textcolor{red}{\tau_{\text{spillover, treated}}} D_{it} \text{Within 40mi.}_{it} + \varepsilon_{it}
-        \end{align*}
+        \item $\textcolor{purple}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?
 
-        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly or through a spatial process.
-
-        \item $\text{Within 40mi.}_{it}$ is an indicator for having your county center of population be within 40 miles of a treated unit.
-
-        \item $\textcolor{green}{\tau_{\text{direct}}} = 2$, $\textcolor{purple}{\tau_{\text{spillover, control}}} = 1$ and $\textcolor{red}{\tau_{\text{spillover, treat}}} \in \{0, 0.5\}$.
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{Source of Bias 1: Control Units}
-    Simulation 1:
-
-    \begin{itemize}
-        \item The first simulation changes the probability of treatment, $D_{it}$.
-
-        \item Assume, for now, there is only spillover on the control, i.e. $\tau_{\text{spillover,treat}} = 0$.
-
-        \item Estimate via TWFE: \begin{equation*}
-            y_{it} = \mu_t + \mu_i + \tau D_{it} + \epsilon_{it}    
-        \end{equation*}
-
-        \item The bias of our estimate is \textit{Bias} $= \hat{\tau} - 2$
+        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on others treatment? (This is what you should consider if you are a policy maker)
     \end{itemize}
 
-\end{frame}
-
-\imageframe{../../figures/figure-bias_from_prob_treat_slides.png}
-
-\begin{frame}{Solution: Removing ``contaminated'' controls}
-    A common solution to the problem of spillover is to restimate on a subsample with neighboring control units removed.
-
-    This simulation drops only units with $\text{Within 40mi.}_{it} = 1$. The exact exposure mapping is typically not observable for researchers, so this is best case scenario.
-\end{frame}
-
-\imageframe{../../figures/figure-bias_fix_slides.png}
-
-\begin{frame}{Why Removing Controls Doesn't Work Well}
-    \begin{itemize}
-        \item[1.] Lose precision in treatment effect estimate by dropping control units
-        \item[2.] If there are spillovers on treated units, removing controls won't remove both sources of bias. 
-    \end{itemize}
-
-    I repeat the same simulations but with $\textcolor{red}{\tau_{\text{spillover, treat}}} = 0.5$
-
-\end{frame}
-
-\imageframe{../../figures/figure-bias_fix_treat_slides.png}
-
-\begin{frame}{Solution: Parametrize potential outcomes}
-    Another option is to directly control for spillovers by parametrizing the exposure mapping.
-
-    This is not observable to a researcher which raises the question:
-
-    Are there specifications that work well even if the spillovers are misspecified?
+    To estimate the spillover effects, we have to parameterize $h(\vec{D}, i)$ function and the potential outcomes function $Y_i(D_i, h(\vec{D}, i))$.
 \end{frame}
@@
 
-\begin{frame}{Specifications of $h(\vec{D}, i)$}
-
-    \begin{itemize}
-        \item \textit{Within $40/80$mi.}:
-        \begin{itemize}
-            \item Inidicator for nearest treated unit being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Within $40/80$mi. (Additive)}: 
-        \begin{itemize}
-            \item Number of treated units being within $40/80$ miles.
-        \end{itemize}
-
-    \end{itemize}
+\begin{frame}{Results}
+    \textbf{I find that an indicator for being Within $x$ miles from treated area will remove all bias so long as the indicator contains all the affected units.}
 
@@
 
-\imageframe{../../figures/figure-spill_within_large.png}
-\imageframe{../../figures/figure-spill_within_large_additive.png}
+\begin{frame}{Estimation of Spillover Effects}
+    In a lot of settings, estimating the spillover effects are also an estimand of interest.
 
-\begin{frame}{Specifications of $h(\vec{D}, i)$}
-
-    \begin{itemize}
-        \item \textit{Within $40/80$mi.}:
-        \begin{itemize}
-            \item Inidicator for nearest treated unit being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Within $40/80$mi. (Additive)}: 
-        \begin{itemize}
-            \item Number of treated units being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Decay}: 
-        \begin{itemize}
-            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-        \item \textit{Decay (Additive)}: 
-        \begin{itemize}
-            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-    \end{itemize}
-
-\end{frame}
-
-\imageframe{../../figures/figure-spill_decay.png}
-\imageframe{../../figures/figure-spill_decay_additive.png}
-
-\begin{frame}{Specifications of $h(\vec{D}, i)$}
-
-    \begin{itemize}
-        \item \textit{Within $40/80$mi.}:
-        \begin{itemize}
-            \item Inidicator for nearest treated unit being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Within $40/80$mi. (Additive)}: 
-        \begin{itemize}
-            \item Number of treated units being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Decay}: 
-        \begin{itemize}
-            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-        \item \textit{Decay (Additive)}: 
-        \begin{itemize}
-            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-        \item \textit{Rings}: 
-        \begin{itemize}
-            \item Set of concentric rings. For each ring, indicator for nearest treated unit being within that distance bin
-        \end{itemize}
-
-        \item \textit{Rings (Additive)}: 
-        \begin{itemize}
-            \item Set of concentric rings. For each ring, number of treated units being within that distance bin
-        \end{itemize}
-    \end{itemize}
-
-\end{frame}
-
-\imageframe{../../figures/figure-spill_ring.png}
-
-\begin{frame}
-
-    \begin{table}[!tb]
-        \caption{Bias from Misspecification of Spillovers}
-        \label{tab:misspecification}
-
-        \begin{adjustbox}{width = 1.1\textwidth, center}
-            \begin{threeparttable}
-                \begin{tabular}{@{} l rrrrrr @{}}
-                    % Head
-                    \toprule
-                    & \multicolumn{6}{c}{Data-Generating Process} \\
-                    \cmidrule{2-7}
-
-                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
-                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
-
-                    % Body
-                    \midrule
-
-                    % \input{../../tables/misspecification_slides.tex}
-                    TWFE (No Spillovers) & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ \\ \midrule
-                    \marktopleft{c1}Within 40mi. & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
-                    Within 80mi. & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c1}
-                    \onslide<2->{
-                        \\ \midrule
-                        Within 40mi. (Additive) & $0.043$ & $0.221$ & $-0.006$ & $0.177$ & $0.174$ & $0.143$ \\ 
-                        Within 80mi. (Additive) & $0.034$ & $0.134$ & $-0.012$ & $-0.009$ & $0.099$ & $-0.010$ \\ \midrule
-                        Decay 80mi. & $-0.159$ & $0.070$ & $-0.174$ & $0.014$ & $-0.009$ & $-0.033$ \\ 
-                        Decay 80mi. (Additive) & $-0.023$ & $0.148$ & $-0.084$ & $0.019$ & $0.088$ & $-0.008$
-                    }
-                    \onslide<3->{
-                        \\ \midrule
-                        \marktopleft{c2}Rings (0-20, 20-30, 30-40) & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c2}\\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $0.036$ & $0.134$ & $-0.008$ & $-0.008$ & $0.100$ & $-0.009$ 
-                    }
-
-                    \\ \bottomrule
-                \end{tabular}
-            \end{threeparttable}
-        \end{adjustbox}
-    \end{table}
-
-\end{frame}
-
-\begin{frame}{Spillovers as Estimand of Interest}
-    Until now, we assumed our estimand of interest is $\textcolor{green}{\tau_{\text{direct}}}$.
-
-    However, the two other spillover effects are of interest as well:
-    \begin{itemize}
-        \item $\textcolor{purple}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?
-
-        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on treatment of neighbors? 
-    \end{itemize}
-
-    To estimate the spillover effects, we have to parameterize $h(\vec{D}, i)$ function and the potential outcomes function $Y_i(D_i, h(\vec{D}, i))$.
-\end{frame}
-
-\begin{frame}{Estimation of Spillover Effects}
-    To see which specifications can predict spillover effects well, I estimate the spillover effects for each control unit, $\hat{\beta}_{\text{spill, control}} * \tilde{h}(\vec{D}, i)$.
+    I repeat the same exercise and estimate the spillover effects for each control unit, $\hat{\beta}_{\text{spill, control}} * \tilde{h}(\vec{D}, i)$.
 
@@
 
-\begin{frame}
-    \begin{table}[!tb]
-        \caption{Percent of Spillovers Predicted by Specification}
-        \label{tab:misspecification_mspe}
+\imageframe{../../figures/figure-spill_ring.png}
 
-        \begin{adjustbox}{width = 1.1\textwidth, center}
-            \begin{threeparttable}
-                \begin{tabular}{@{} l rrrrrr @{}}
-                    % Head
-                    \toprule
-                    & \multicolumn{6}{c}{Data-Generating Process} \\
-                    \cmidrule{2-7}
-
-                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
-                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
-
-                    % Body
-                    \midrule
-
-                    % \input{../../tables/misspecification_slides.tex}
-                    TWFE (No Spillovers) & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ \\ \midrule
-                    \marktopleft{c3}Within 40mi. & $99.4\%$ & $25.9\%$ & $85.6\%$ & $38.8\%$ & $59.5\%$ & $56.1\%$ \\ 
-                    Within 80mi. & $39.8\%$ & $96.2\%$ & $34.3\%$ & $71.7\%$ & $85.6\%$ & $68.0\%$ \markbottomright{c3}
-                    \onslide<2->{
-                    \\ \midrule
-                        Within 40mi. (Additive) & $85.3\%$ & $21.2\%$ & $99.5\%$ & $40.6\%$ & $52.0\%$ & $60.7\%$ \\ 
-                        Within 80mi. (Additive) & $45.8\%$ & $61.8\%$ & $47.2\%$ & $98.4\%$ & $71.0\%$ & $93.6\%$ \\ \midrule 
-                        Decay 80mi. & $60.1\%$ & $82.5\%$ & $52.7\%$ & $75.8\%$ & $97.5\%$ & $82.2\%$ \\ 
-                        Decay 80mi. (Additive) & $60.7\%$ & $56.9\%$ & $63.8\%$ & $93.5\%$ & $79.0\%$ & $98.7\%$ 
-                    }
-                    \onslide<3->{
-                        \\ \midrule 
-                        \marktopleft{c4}Rings (0-20, 20-30, 30-40) & $98.4\%$ & $23.7\%$ & $85.9\%$ & $37.5\%$ & $58.9\%$ & $56.2\%$ \\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $96.6\%$ & $91.7\%$ & $84.2\%$ & $72.7\%$ & $91.9\%$ & $78.4\%$ \\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $83.5\%$ & $57.4\%$ & $97.6\%$ & $95.0\%$ & $73.5\%$ & $94.9\%$\markbottomright{c4} 
-                    }
-
-                    \\ \bottomrule
-                \end{tabular}
-            \end{threeparttable}
-        \end{adjustbox}
-    \end{table}
-
-    \onslide<3->{
-        \textbf{Donuts perform best at estimating spillover effects.}
-
-        \textbf{It is important to get Additive vs. Non-Additive correct.}
-    }
-\end{frame}
-
-% ------------------------------------------------------------------------------
-\section{Application in Urban Economics}
-% ------------------------------------------------------------------------------
-
-\begin{frame}{Tennessee Valley Authority}
-    \citet{Kline_Moretti_2014a} look at the long-run impacts of the Tennessee Valley Authority (TVA).
-
-    \begin{itemize}
-        \item The TVA was a large-scale federal investment started in 1934 that focused on improving manufacturing economy.
-
-        \item The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy
-
-        \item Hundreds of dollars spent anually per person
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{Identification}
-    \citet{Kline_Moretti_2014a} run the county-level difference-in-differences  specification: 
-    \begin{equation}\label{eq:tva_spillover}
-        y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \beta + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940})
-    \end{equation}
-
-    \begin{itemize}
-        \item $y$ are outcomes for agricultural employment, manufacturing employment, and median family income.
-        \item $\text{TVA}_c$ is the treatment variable
-        \item $X_{c, 1940}$ allow for different long-term trends based on covariates in 1940. 
-    \end{itemize}
-
-    They trim the sample using a logit regression to predict treatment using $X_{c,1940}$ and then keep control units in the top 75\% of predicted probability.
-\end{frame}
-
-\begin{frame}{Spillovers in the TVA Context}
-    In our context, there is reason to believe spillovers can occur to nearby counties
-
-    \begin{itemize}
-        \item Agricultural employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley (negative spillover on control units)
-
-        \item Manufacturing jobs that would have been created in the control units in the absence of treatment might move to the Tennessee Valley (negative spillover on control units)
-
-        \item Since manufacutring jobs pay higher than agricultural jobs, the above two spillover effects can cause changes in median family income
-    \end{itemize}
-\end{frame}
-
-\begin{frame}{Specification including spillovers}
-    \begin{equation}
-        \Delta y_c = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Ring}(d)\delta_d + X_{i, 1940} \beta + \Delta \varepsilon_c
-    \end{equation}
-
-    \begin{itemize}
-        \item $\text{Ring}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
-        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] \right\} \]
-    \end{itemize}
-\end{frame}
-
-\imageframe{../../figures/figure-tva-sample_slides.pdf}
-
-\begin{frame}
-\begin{table}[ht]
-    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
-    \label{tab:tva}
-    \renewcommand{\arraystretch}{1.2}
-
-    \begin{adjustbox}{width = 1\textwidth, center}
-        \begin{threeparttable}
-            \begin{tabular}{@{} lc@{\extracolsep{20pt}}c@{\extracolsep{4pt}}ccc @{}}
-                % Head
-                \toprule
-
-                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
-                \cmidrule{2-2} \cmidrule{3-6} 
-                & & & TVA between & TVA between & TVA between \\ 
-                \textit{Dependent Var.} & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\
-
-                % Body
-                \midrule
-
-                Agricultural employment     & $-0.0514^{***}$& $-0.0678^{***}$& $-0.0310^{**}$ &    $-0.0112$   & $-0.0252^{***}$\\
-                &   $(0.0087)$   &   $(0.0102)$   &   $(0.0123)$   &   $(0.0094)$   &   $(0.0084)$
-
-                \onslide<2->{
-                    \\
-                    Manufacturing employment    & $0.0560^{***}$ &  $0.0461^{**}$ &    $-0.0104$   &    $-0.0128$   &  $-0.0248^{*}$ \\
-                    &   $(0.0187)$   &   $(0.0210)$   &   $(0.0205)$   &   $(0.0257)$   &   $(0.0147)$
-                }
-                \onslide<3->{
-                    \\
-                    Median family income        & $0.0191^{***}$ &  $0.0196^{**}$ &    $0.0056$    &    $-0.0062$   &    $-0.0011$   \\
-                    &   $(0.0067)$   &   $(0.0077)$   &   $(0.0079)$   &   $(0.0060)$   &   $(0.0032)$ 
-                }
-
-                \\ \bottomrule
-            \end{tabular}
-
-            % Notes 
-            \begin{tablenotes}\footnotesize
-
-                \item $^{*} p< 0.1$; $^{**} p < 0.05$; $^{***} p < 0.01$.
-            \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-
-\end{frame}
-
-\begin{frame}{Identification Strategies and Place-Based Policies}
-
-    The literature on federal Enterprise Zones, place-based policy that gives tax breaks to businesses that locate within the boundary, has found conflicting results, suggesting positive or near-zero effects of the program \citep{Neumark_Young_2019}.
-
-    \begin{itemize}
-        \pause
-        \item \citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program.
-They find significant large reduction of poverty.
-
-        \pause
-        \item \citet{Neumark_Kolko_2010} compare census tracts in Empowerment Zones to census tracts within 1,000 feet of the Zone. They find near-zero effects on poverty.
-    \end{itemize}
-
-    \pause
-    My framework can explain both of these results.
-If census tracts just outside the Empowerment Zones also benefit from the policy, then the estimates of \citet{Neumark_Kolko_2010} are attenuated towards zero
-
+\begin{frame}{Results}
+    \textbf{Rings perform best at estimating spillover effects.}
 \end{frame}
@@
 
-        \item I showed that a set of concentric rings allows for estimation of the direct effect of treatment and they are able to model spillovers well
+        \item I showed that a set of concentric rings removes two spillover terms from treatment effect estimate and models spillovers well
 
         \item For place-based policies, I show the importance of considering spatial spillovers when estimating treatment effects
-
-        \item More generally, identification strategies that use very close control units in order to minimize differences in unobservables should consider the problems with treatment effect spillovers.
     \end{itemize}
@@
 
-% ------------------------------------------------------------------------------
-\appendix\section{Appendix}
-% ------------------------------------------------------------------------------
-
-\begin{frame}{Partial Identification}\label{slide:partial_identification}
-    Researchers can use the above method to create bounds for the biases resulting from spillovers. The choices should follow from the empirical context at hand.
-
-    To formalize this, I follow the literature on partial identification for treatment effects
-    \begin{citecolor}
-        [\citet{Armstrong_Kolesár_2020}, \citet{Rambachan_Roth_2020}, and \citet{Manski_Pepper_2018}]
-    \end{citecolor}
-\end{frame}
-
-\begin{frame}{Partially-identified Set}
-    Following \citet{Rambachan_Roth_2020} and \citet{Manski_Pepper_2018}, researchers can provide bounds to the maximum spillovers.
-
-    Let $\Delta$ denote the interval of potential biases: 
-    \begin{align*}
-        \Delta &\equiv [\underline{\Delta}, \overline{\Delta}] \\
-        &= \left[ \min \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}, \ \max \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \right] 
-    \end{align*}
-
-    The partially identified set is formed by \[ 
-        \left[\hat{\tau} - \underline{\Delta} , \ \hat{\tau} + \overline{\Delta} \right]    
-    \]
-
-\end{frame}
-
-\begin{frame}{Bias-adjusted Inference}
-
-    Inference can be done following \citet{Rambachan_Roth_2020} by creating a Fixed-Length Confidence Interval: 
-    \[ 
-        \left[
-            \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}
-        \right]
-    \]
-
-    These standard errors should account for the spatial structure of outcomes following \citet{Conley_1999}.
-
-    \hyperlink{slide:example_bias}{\beamerbutton{Back to Example of Bias}}
-\end{frame}
-
 \end{document}

### 2021-03-22 latex/paper/Spillover.tex
Update introduction

@@
 I propose estimation strategies that can remove both sources of bias as well as semi-parametrically estimate the spillovers themselves.
-Lastly, I extend this estimation strategy in an event-study framework following \citet{Callaway_Sant’Anna_2020}.
+Lastly, I extend this estimation strategy in an event-study framework following \citet{Callaway_Sant’Anna_2020} to allow for staggered treatment adoption.
 Then, I turn to an empirical application revisiting an analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
@@
 
-Empirical work in economics often considers treatment assigned to groups of units, but the effect of these treatments potentially do not stay within these groups and spillover onto ‘close’ units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+Empirical work in economics often considers settings where treatment is assigned to groups of units, but the effect of these treatments spillover onto ‘close’ units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
 geographic
-distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, treatment is often assigned to geographic boundaries and spillovers occur from people crossing borders to access treatment (imperfect compliance) or from general equilibrium effects influencing neighboring areas.
-Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.\footnote{The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect.
-In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The central result of my paper is that in the presence of spillovers, the difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
+distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, treatment is commonly assigned to geographic boundaries and spillovers occur from people crossing borders to access treatment (i.e.
+imperfect compliance) or from general equilibrium effects influencing neighboring areas.
+Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.
+The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect.\footnote{In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The central theoretical result of my paper is that in the presence of spillovers, the standard difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
 
@@
 For example, consider trying to estimate employment effects of a factory opening in a county.
-Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain which would potentially increase employment \citep{Duranton_Puga_2003}.
+Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain which would potentially increase economic activity \citep{Duranton_Puga_2003}.
 The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
@@
 Difference-in-differences estimation would therefore result in double undercounting.}
+
+% @TODO: Improve examples to better build intuition
 
@@
 Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces.
-The estimated treatment effect will count the `direct' effect of the factory opening as well as the benefit of the agglomeration economies.
+The estimated treatment effect will count the `direct' effect of the factory opening as well as the benefit of the agglomeration economies from nearby factory openings.
 Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.
 
-I then propose an estimation strategy that will remove both sources of bias with very minimal assumptions on the structure of spillovers.
+I then use my framework to evaluate commonly used empirical strategies found in applied work and provide practical recommendations for researchers.
+The most common approach is to remove potentially contaminated control units from the sample in order to remove spillover effects on control units \citep{Berg_Streitz_2019}.
+This approach is not recommended for two reasons.
+First, the removal of too few control units will leave bias and removal of too many control units will lower precision of the treatment effect estimate.
+This results in a bias-variance trade-off that other approaches do not share.
+Second, this method does not remove spillover effects on treated units and will leave this bias term in the difference-in-differences estimate.
+Another common approach is to include either an indicator or a set of rings around treated units.
+This approach will remove all bias from the spillover effects on control units provided that all control units with spillover effects are included in the indicator.
+Similar to the previous approach, spillover effects on also treated units still add bias to estimates of the direct effect.
+
+Therefore, I propose an estimation strategy that will remove both sources of bias with very minimal assumptions on the structure of spillovers.
 To remove \textit{all bias} from the direct effect estimate, a research needs to just include an indicator for being close to a treated unit interacted with treatment status, so long as the indicator captures all units affected by spillovers.
-An indicator removes all bias because in my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units.
-The interacted indicator will estimate this average and remove both bias terms from the treatment effect estimate.
+In my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units.
+An idicator variable interacted with treatment status therefore can estimate these two averages and remove them from the difference-in-differences estimate.
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
@@
 
-Since spillovers themselves are often important causal effects themselves, I next turn to how to estimate spillovers directly.
+Since spillover effects are often important causal effects themselves, I next turn to how to estimate spillovers directly.
 I show with evidence from Monte Carlo simulations, that commonly used semi-parametric estimation strategies capture spillovers well (in a mean square prediction error sense).
 This involves creating a set of distance bins from treated units (e.g.
-being 0-20 miles, 20-40 miles, 40-60 miles from treated unit).
-The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not.
-For non-additive spillovers, I recommend a set of mutually-exclusive indicators for the closest treated unit being in each distance bin.
-For additive spillovers, I recommend using the number of treated units within each spillover bin.
+being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
+% TODO: Reference Butts and Clarke
+} The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not.
+For non-additive spillovers, I recommend a set of mutually-exclusive indicators which measures which distance bin that the closest treated unit falls within for a given observation.
+For additive spillovers, I recommend using the number of treated units within each distance bin for a given observation.\footnote{While the non-additive version of ring indicators will remove all bias from the direct effect of treatment even under misspecification, this is not true of additive rings.
+Therefore, researchers may want to estimate the direct effect of treatment using non-additive rings and then use additive rings to estimate spillover effects.}
+
+I turn to an empirical application in the literature in urban economics on local place-based policies in Section \ref{sec:tva}.
+Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects in non-treated locations.
+In particular, their model implies these effects are declining in distance.
+I contribute by showing that because of these general equilibrium effects, estimation of local effects are often misestimated by not controlling for the spillover effects in their empirical specification.
 
@@
 The construction of large-scale dams lowered the cost of power for industrial firms giving the region an industrial boost \citep{Kitchens_2014}.
-The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citet{Severnini_2014}.
+The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citep{Severnini_2014}.
 I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.
 
-I turn to an empirical application in the literature in urban economics on local place-based policies in section \ref{sec:tva}.
-Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects in non-treated locations.
-I contribute by showing that because of these general equilibrium effects, estimation of local effects are often underestimated by not controlling for the spillover effects in estimation.
+Following this empirical application, I discuss how my framework fits into a larger discussion on identification strategies with place-based policies.
+I revisit conflicting results about United States' federal Empowerment Zones, a program that creates incentives for businesses to locate in high-poverty neighborhoods.
+\citet{Busso_Gregory_Kline_2013} use Census Tracts from qualified but ultimately rejected applications that are typically far away from accepted Zones as a comparison group and find that significant reductions in poverty.
+This empirical strategy is based on the idea that since they qualified for the program they would be on similar trends without being contaminated by spillover effects.
+\citet{Neumark_Kolko_2010}, on the other hand, use census tracts within 1,000 feet of the Zone and find no statistically significant effects.
+This empirical strategy assumes that the borders are drawn somewhat randomly and therefore being just outside is as good as random.
+Although, using close units is potentially problematic as they can experience spillover effects from the Zones.
+My framework can explain the differences in findings if there are positive spillover effects onto census tracts just outside Empowerment Zones.
 
-Last, in section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_Sant’Anna_2020}.
+Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_Sant’Anna_2020}.
+This allows for a very common setting in which treatment turns on for different units in different periods.
 I first show how to adjust their methods to control for spatial spillovers in estimation of treatment effects.
-Second, I show how an extension of their method allows for estimation of spillover effects.
-My paper is the first paper to study estimation of treatment effects in an event-study framework.
+Then, I show how to estimate average spillover effects.
+My paper is the first paper to study estimation of treatment effects in an event-study framework in the presence of spillover effects.
 
@@
 
-More recently, a new strand of literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster by using a potential outcomes framework.
+There is a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster by using a potential outcomes framework.
 \citet{Vazquez-Bare_2019} presents a potential outcomes model that explicitly accounts for ``within-group'' spillovers in experiments which allows for seperate estimation of direct effect and spillover effects by a simple differences-in-means.
@@
 \citet{Sävje_Aronow_Hudgens_2019} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
-My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.These estimates can be combined afterwards to estimate their definition of average treatment effect.
+My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
+These estimates can be combined to estimate their definition of average treatment effect.
 The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.
@@
 Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_Sant’Anna_2020}.
-% @TODO Fix this
 

### 2021-03-22 latex/slides_short/Spillover_slides_short.tex
Update slides for Westerns

@@
 
+    Estimation is complicated by \textbf{Spillover Effects}
+
     \vspace{5mm}
-    Spillover effects are when effect of treatment extend over boundaries such as states, counties, etc.
+    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries (states, counties, etc.)
 
     \begin{itemize}
-        \item e.g. large employer opening/closing in a county have positive employment effects on nearby counties
+        \item E.g. a large employer opening/closing in a \textbf{treated} county have positive employment effects on \textit{nearby counties}
+
+        \item Having nearby counties with factories raises wages and reduces effect of \textbf{treated} counties
     \end{itemize}
@@
 
-% Grey out overlays
-\setbeamercovered{transparent}
+\begin{frame}{Econometric Contribution}
 
-\begin{frame}{Contribution}
-
-    {\footnotesize
-
-    \underline{Difference-in-Differences Estimation with Spillovers}
+    I formalize spillovers into a potential outcomes framework:
 
@@
     \begin{itemize}
-        \item I generalize the work by deriving the bias in terms of potential outcomes and show how to estimate treatment effects by removing spillover effects
+        \vspace{2.5mm}
+        \item I decompose the difference-in-differences estimator into three parts: Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units
+
+        \vspace{2.5mm}
+        \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers
+
+        \vspace{2.5mm}
+        \item `Rings' are able to estimate spillover effects non-parametrically while still removing all bias
     \end{itemize}
 
-    \pause
-    \underline{Potential Outcome Framework for Spillovers}
+\end{frame}
 
-    \begin{citecolor}
-        [\citet{Miguel_Kremer_2004}, \citet{Vazquez-Bare_2019}, \citet{Angelucci_DiMaro_2016}, \citet{Angrist_2014}]        
-    \end{citecolor}
-
-    \begin{itemize}
-        \item I focus on a spatial setting whereas these papers consider spillovers in network clusters
-    \end{itemize}
-
-    \pause
-    \underline{Place-based Policies}
-
-    \begin{citecolor}
-        [\citet{Kline_Moretti_2014b}, \citet{Kline_Moretti_2014a}, \citet{Busso_Gregory_Kline_2013}, and \citet{Neumark_Kolko_2010}]
-    \end{citecolor}
-
-    \begin{itemize}
-        \item I highlight the need to control for general equilibrium effects to properly estimate local effects of policies
-    \end{itemize}
-    }
-\end{frame}
+% Grey out overlays
+\setbeamercovered{transparent}
 
@@
 \begin{frame}{Potential Outcomes Framework}
-    For exposition, I will label units as counties.
-Assume all treatment occurs at the same time (2-periods or pre-post averages).\footnote{I extend this into an event study framework in the paper, but the intuition is the same as in the $2 \times 2$ setting.}
 
-    \begin{itemize}
-        \item $Y_{it}(D_i, \textcolor{blue}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.
+    $Y_{it}(D_i, \textcolor{blue}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.
 
-        \pause
-        \item $\vec{D} \in \{0,1\}^N$ is the vector of all units treatments.
-
-        \pause
-        \item The function $\textcolor{blue}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping' which can be a scalar or a vector.
-
-        \pause
-        \item No exposure is when $\textcolor{blue}{h(\vec{D}, i)} = \vec{0}$.
-    \end{itemize}
+    The function $\textcolor{blue}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping'
 \end{frame}
 
-% Grey out
-% \setbeamercovered{transparent}
-
 \begin{frame}{Examples of $h_i(\vec{D})$}
-
-    Examples of $h_i(\vec{D})$:
-
-    \begin{itemize}
-        \item \textbf{Treatment within $x$ miles:}
+    \textbf{Treatment within $x$ miles:}
 
@@
     \end{itemize}
-
-    \end{itemize}
 \end{frame}
@@
 
-    Examples of $h_i(\vec{D})$:
-
-    \begin{itemize}
-        \item \textbf{Treatment within $x$ miles:}
+    \textbf{Treatment within $x$ miles:}
 
@@
     \vspace{2.5mm}
-        \item \textbf{Number of Treated within $x$ miles:}
+    \textbf{Number of Treated within $x$ miles:}
 
@@
 
-\begin{frame}{Estimand of Interest}
-    Estimand of Interest: \[ 
-        \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
-    \]
-
-    \vspace{10mm}
-    This is the direct effect in the absense of exposure to spillovers.
-\end{frame}
-
-\begin{frame}{Parallel Trends}
-    I assume a modified version of the parallel counterfactual trends assumption: 
-    \begin{align*}
-        &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] \\
-        = \ &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big],
-    \end{align*}
-
-    \vspace{5mm}
-    In the complete absence of treatment (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status
-
-\end{frame}
-
 \begin{frame}{What does Diff-in-Diff identify?}
-    With the parallel trends assumption and random assignment of $D_i$, I decompose the diff-in-diff estimate as follows:
+    With the parallel trends assumption and a random sample, I decompose the difference-in-differences estimate as follows:
 
@@
     \end{align*}
-
-\end{frame}
-
-\begin{frame}{Biased Estimate for $\tau_{\text{direct}}$}
-    \[ 
-        \mathbb{E}[\hat{\tau}_{\text{diff-in-diff}}] - \textcolor{green}{\tau_{\text{direct}}} = \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
-    \]
-\end{frame}
-
-% ------------------------------------------------------------------------------
-\section{Estimation}
-% ------------------------------------------------------------------------------
-
-\begin{frame}{Problems with "Dropping Bad Controls"}
-    It is common in empirical applications to drop control units near the treated units when estimating the direct effect of treatment.
-
-    This is not recommended for two reasons:
-
-    \begin{itemize}
-        \item[1.] If not all control units that experience spillover effects are removed, then bias remains
-
-        \item[2.] There is a second source of bias, the spillover effects on treated units, that still remains
-    \end{itemize}
 
@@
 \begin{frame}{Robustness to Misspecification}
-    Generate data using the same data-generating process as before but with different spillover functions:
+    I find that an indicator for being Within $x$ miles from treated area interacted with treatment status will remove \textbf{all bias} so long as the indicator contains all the affected units.
 
-    \[ 
-        y_{\it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill,control}} * (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it}
-    \]
-
-    Then, I estimate each data-generating process using (potentially) misspecified $\tilde{h}(\vec{D}, i)$ and report the average estimate bias.
-
-\end{frame}
-
-\begin{frame}{Results}
-    \textbf{I find that an indicator for being Within $x$ miles from treated area will remove all bias so long as the indicator contains all the affected units.}
-
+    \begin{itemize}
+        \item Indicator will estimate the average spillover effect on treated and control units and remove these from estimate, $\hat{\tau}$
+    \end{itemize}
 \end{frame}
@@
 
-    I repeat the same exercise and estimate the spillover effects for each control unit, $\hat{\beta}_{\text{spill, control}} * \tilde{h}(\vec{D}, i)$.
-
-    Then calculate \[ 
-        1 - \frac{
-                \overbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}^{\text{Mean Square Prediction Error}}
-            }{
-                \underbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}_{\text{Normalization}}
-            }    
-    \]
-
-    This gives the proportion of spillovers explained by $\tilde{h}(\vec{D}, i)$
-
+    A set of concentring `rings' around treatment perform best for estimating spillover effects
 \end{frame}
@@
 
-\begin{frame}{Results}
-    \textbf{Rings perform best at estimating spillover effects.}
+\begin{frame}{Benefits of Rings}
+
+    \begin{itemize}
+        \item Still remove all bias from the treatment effect estimate
+
+        \item Can trace out how spillovers spread over distance
+
+        \item If spillovers are additive in the number of nearby treated units, then an additive version of rings should be used (but this loses the bias-removal property)
+    \end{itemize}
+
+\end{frame}
+
+\section{Application in Urban Economics}
+
+\begin{frame}{Urban Economics}
+
+    I apply framework to place-based analyses in Urban Economics
+
+    \begin{itemize}
+        \item Revisit \begin{citecolor}\citet{Kline_Moretti_2014a}\end{citecolor} analysis of the Tennessee Valley Authority
+
+        \begin{itemize}
+            \vspace{2.5mm}
+            \item The local effect estimate is contaminated by spillover effects to neighboring counties \begin{citecolor}\citep{Kline_Moretti_2014b}\end{citecolor}
+
+            \vspace{2.5mm}
+            \item Large scale manufacturing investment creates an `urban shadow' \begin{citecolor}\citep{Cuberes_Desmet_Rappaport_2021,Fujita_Krugman_Venables_2001}\end{citecolor}
+        \end{itemize}
+
+        \vspace{2.5mm}
+        \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones
+
+        \begin{itemize}
+            \vspace{2.5mm}
+            \item Identification Strategy of using far-away rejected applicants \begin{citecolor}\citep{Busso_Gregory_Kline_2013} \end{citecolor} vs.
+census tracts within 1000 feet of empowerment zone \begin{citecolor}\citep{Neumark_Kolko_2010}\end{citecolor}
+        \end{itemize}
+    \end{itemize}
+
 \end{frame}

### 2021-03-22 latex/slides/Spillover_slides.tex
Update slides for Environmental Brownbag

@@
 
+\begin{frame}{This Paper}
+    In this paper, I
+
+    \begin{itemize}
+        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments done in the literature
+
+        \item Propose an estimation strategy that improves on current practices by being more robust to spillovers
+
+        \item Apply this framework to improve estimation of the local effect of place-based policies in Urban Economics 
+    \end{itemize}
+
+\end{frame}
+
 \begin{frame}{Bias from Spatial Spillovers}
@@
     \begin{itemize}
-        \item[1--] Using a potential outcomes framework, I decompose the difference-in-differences estimator into three parts:
-        \begin{itemize}
-            \item Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units
-        \end{itemize}
-
-        \pause
-        \item[2--] Analyze effectiveness of common ad-hoc adjustments done by researchers
-        \begin{itemize}
-            \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers
-            \item `Rings' are able to estimate spillover effects while still removing all bias
-        \end{itemize}
-
-        \pause
-        \item[3--] Apply framework to Urban Economics
-        \begin{itemize}
-            \item Revisit \citet{Kline_Moretti_2014a} analysis of the Tennessee Valley Authority
-
-            \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}
-        \end{itemize}
-    \end{itemize} 
-\end{frame}
-
-\begin{frame}{Contribution}
-
-    {\footnotesize
-
-    \underline{Difference-in-Differences Estimation with Spillovers}
+        \item[1--] Formalize spillovers into a potential outcomes framework:
 
@@
         \begin{itemize}
-        \item I generalize the work by deriving the bias in terms of potential outcomes and show how to estimate treatment effects by removing spillover effects
+            \vspace{2.5mm}
+            \item I decompose the difference-in-differences estimator into three parts: Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units
+
+            \vspace{2.5mm}
+            \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers
+
+            \vspace{2.5mm}
+            \item `Rings' are able to estimate spillover effects while still removing all bias
         \end{itemize}
 
-    \pause
-    \underline{Potential Outcome Framework for Spillovers}
+    \end{itemize}
+\end{frame}
 
-    \begin{citecolor}
-        [\citet{Miguel_Kremer_2004}, \citet{Vazquez-Bare_2019}, \citet{Angelucci_DiMaro_2016}, \citet{Angrist_2014}]        
-    \end{citecolor}
+\begin{frame}{Outline}
+    \begin{itemize}
+        \item[2--] Apply framework to Urban Economics
+        \begin{itemize}
+            \item Revisit \begin{citecolor}\citet{Kline_Moretti_2014a}\end{citecolor} analysis of the Tennessee Valley Authority
 
             \begin{itemize}
-        \item These papers consider spillovers in network clusters. I focus on spatial setting
+                \vspace{2.5mm}
+                \item The local effect estimate is contaminated by spillover effects to neighboring counties \begin{citecolor}\citep{Kline_Moretti_2014b}\end{citecolor}
+
+                \vspace{2.5mm}
+                \item Large scale manufacturing investment creates an `urban shadow' \begin{citecolor}\citep{Cuberes_Desmet_Rappaport_2021,Fujita_Krugman_Venables_2001}\end{citecolor}
             \end{itemize}
 
-    \pause
-    \underline{Place-based Policies}
-
-    \begin{citecolor}
-        [\citet{Kline_Moretti_2014b}, \citet{Kline_Moretti_2014a}, \citet{Busso_Gregory_Kline_2013}, and \citet{Neumark_Kolko_2010}]
-    \end{citecolor}
-
-    \begin{itemize}
-        \item I highlight the need to control for general equilibrium effects to properly estimate local effects of policies
+            \vspace{2.5mm}
+            \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \begin{citecolor}\citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}\end{citecolor}
         \end{itemize}
-    }
+    \end{itemize} 
 \end{frame}
@@
 \begin{frame}{Estimand of Interest}
-    Estimand of Interest: \[ 
+    Estimand of Interest: 
+    \[ 
         \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
@@
 
-    \vspace{10mm}
-    This is the direct effect in the absense of exposure to spillovers.
+    \pause
+    \vspace{2.5mm}
+    Spillover Effects:
+
+    \[
+        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]}
+    \]
+
+    \[ 
+        \textcolor{purple}{\tau_{\text{spillover, control}}} = \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
+    \]
 \end{frame}
@@
 
-\begin{frame}{What does Diff-in-Diff identify?}
+\begin{frame}{What does Difference-in-Differences identify?}
     With the parallel trends assumption and random assignment of $D_i$, I decompose the diff-in-diff estimate as follows:
@@
 
-\end{frame}
-
-\begin{frame}{Biased Estimate for $\tau_{\text{direct}}$}
-    \[ 
-        \mathbb{E}[\hat{\tau}_{\text{diff-in-diff}}] - \textcolor{green}{\tau_{\text{direct}}} = \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
-    \]
 \end{frame}
@@
 
+    \onslide<3->{
+        \textbf{Inidicator that captures all affected unit removes all bias}
+    }
 \end{frame}
@@
     \begin{itemize}
-        \item The TVA was a large-scale federal investment started in 1934 that focused on improving manufacturing economy.
+        \item The TVA was a large-scale federal investment started in 1934 that focused on improving manufacturing economy. (Hundreds of dollars spent anually per person)
 
-        \item The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy
+        \item The program focused on large-scale dam construction that brought cheap wholesale electricity to the region
+    \end{itemize}
 
-        \item Hundreds of dollars spent anually per person
-    \end{itemize}
+    Research Question: What are the local effects of TVA on manufacturing and agricultural economies? Do these effects come at the cost of other counties?
 \end{frame}
@@
     \begin{itemize}
-        \item Agricultural employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley (negative spillover on control units)
+        \item \textbf{Agriculture:} 
+        \begin{itemize}
+            \item Employees might be drawn to hire wages for new manufacturing jobs in Tennessee Valley (negative spillover on control units)
+        \end{itemize}
+
+        \item \textbf{Manufacturing:}
+        \begin{itemize}
+            \item Cheap electricity might be available to nearby counties (positive spillover on control units)
 
             \item Manufacturing jobs that would have been created in the control units in the absence of treatment might move to the Tennessee Valley (negative spillover on control units)
+        \end{itemize}
 
+        \item \textbf{Income:} 
+        \begin{itemize}
             \item Since manufacutring jobs pay higher than agricultural jobs, the above two spillover effects can cause changes in median family income
+        \end{itemize}
     \end{itemize}

### 2021-03-22 tva-analysis-replicate.R
Update TVA analysis

@@ -22,8 +22,8 @@ source("tva-analysis-helpers.R")
 source("helper-conley.R")
 
 # Export
-export <- FALSE
-keep_slides <- TRUE
+export <- TRUE
+slides <- FALSE
 
 ## Load Data -------------------------------------------------------------------
 
@@ -32,8 +32,9 @@ df <- read_dta("data/tva/build.dta") %>%
 		fips = sprintf("%05d", fipstat * 1000 + fipcnty)
 	)
  
-counties <- sf::read_sf("data/counties.geojson") %>% 
-	mutate(state = as.numeric(fips) %% 1000) %>% 
+counties <- sf::read_sf("data/2010_county.geojson") %>% 
+	mutate(fips = paste0(STATEFP10, COUNTYFP10)) %>% 
+	select(state = STATEFP10, county = COUNTYFP10, fips) %>% 
 	rmapshaper::ms_simplify(keep = 0.05)
 
 # Create TVA shape
@@ -65,7 +66,7 @@ df_reg <- df %>%
 		tva_0_50 = !tva & dist_to_tva >= 0 & dist_to_tva < 50,
 		tva_50_100 = !tva & dist_to_tva >= 50 & dist_to_tva < 100,
 		tva_100_150 = !tva & dist_to_tva >= 100 & dist_to_tva < 150,
-		tva_150_250 = !tva & dist_to_tva >= 150 & dist_to_tva < 250
+		tva_150_200 = !tva & dist_to_tva >= 150 & dist_to_tva < 200
 	)
 
 
@@ -86,22 +87,21 @@ fips_in_sample <- df_reg %>%
 	drop_na(!!c(controls)) %>% 
 	filter(keep == TRUE) %>% 
 	pull(fips)
-
 rings <- counties %>% 
 	filter(fips %in% fips_in_sample) %>%
 	mutate(
 		spill = case_when(
 			0 < dist_to_tva & dist_to_tva <= 50 ~ "0 to 50 miles",
 			50 < dist_to_tva & dist_to_tva <= 100 ~ "50 to 100 miles",
-			100 < dist_to_tva & dist_to_tva <= 150 ~ "100 to 150 miles"
+			100 < dist_to_tva & dist_to_tva <= 150 ~ "100 to 150 miles",
+			150 < dist_to_tva & dist_to_tva <= 200 ~ "150 to 200 miles",
 		)
 	) %>% 
 	filter(!is.na(spill)) %>% 
 	group_by(spill) %>% 
 	summarize()
 
[…]

### 2021-03-22 tva-analysis-replicate.R
Remove Oaxaca-Blinder (for presentation purposes)

@@ -170,7 +170,6 @@ dep_names <- c(
 
 
 table_tex <- ""
-table_tex_slides <- ""
 
 for(y in dep_names) {
 	outcome_name <- names(dep_names[dep_names == y])
@@ -182,13 +181,6 @@ for(y in dep_names) {
 		drop_na(!!c(controls, y, "tva_0_100")) %>% 
 		filter(keep == 1)
 	
-	
-	# Oaxcac-Blinder Estimate --------------------------------------------------
-	formula_oaxaca <- as.formula(paste0(y, " ~ ", paste(controls, collapse = " + ")))
-	# Remove bordering counties
-	reg_oaxaca <- oaxaca_estimate(temp %>% filter(is.na(border_county)), formula_oaxaca, "tva", cluster = "FIPSTAT1")
-	
-	
 	# Diff-in-Diff with Controls -----------------------------------------------
 	formula_controls <- as.formula(paste0(y, " ~ tva + ", paste(controls, collapse = " + ")))
 	reg_controls <- fixest::feols(formula_controls, data = temp, demeaned = TRUE)
@@ -198,7 +190,7 @@ for(y in dep_names) {
 	coords <- as.matrix(temp[, c("lat", "long")])
 	time <- rep(1, nrow(coords))
 	# 1 mi = 1.60934 km
-	dist_cutoff <- 500 * 1.60934
+	dist_cutoff <- 200 * 1.60934
 	lag_cutoff <- 1
 	
 	# cov_controls <- conley_ses(X, e, coords, dist_cutoff, lag_cutoff, cores = 4)$Spatial
@@ -212,35 +204,20 @@ for(y in dep_names) {
 	coords <- as.matrix(temp[, c("lat", "long")])
 	time <- rep(1, nrow(coords))
 	# 1 mi = 1.60934 km
-	dist_cutoff <- 500 * 1.60934
+	dist_cutoff <- 200 * 1.60934
 	lag_cutoff <- 1
-	
+
 	# cov_spill <- conley_ses(X, e, coords, dist_cutoff, lag_cutoff, cores = 4, time = time, id = time)$Spatial
 	
-	
-	keep_slides <- y %in% c("D_lnagr", "D_lnmanuf", "D_lnmedfaminc")
 	
 	# Create row
 	row    <- ""
 	row_se <- ""
-	row_slides    <- ""
-	row_slides_se <- ""
 	
[…]

### 2021-04-07 latex/slides/Spillover_slides.tex
Update slides for Oral Comps

@@
     \vspace{5mm}
-    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries such as states, counties, etc.
+    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries (states, counties, etc.). Example:
 
     \begin{itemize}
-        \item e.g. large employer opening/closing in a \textbf{treated} county have positive employment effects on \textit{nearby counties}
+        \item A large employer opening/closing in a treated county have positive employment effects on \textbf{control counties}
+
+        \item Having nearby counties with factories raises wages and reduces effect of \textbf{treated counties}
     \end{itemize}
@@
 
+\end{frame}
+
+\begin{frame}{Remove Bias}
+    \only<1>{
+        \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
+    }
+    \only<2>{
+        \[ 
+            y_{it} = \mu_t + \mu_i + \tau D_{it} + \text{Within}_{it} * D_{it} + \text{Within}_{it} * (1-D_{it}) + \varepsilon_{it}
+        \]
+    }
+
+    \only<1>{ 
+        \[ 
+            \mathbb{E}\{\hat{\tau}\} = \tau + \text{\color{purple} Spillover on Control} + \text{\color{red}Spillover on Treated}
+        \]
+    }
+    \only<2>{
+        \[ 
+            \mathbb{E}\{\hat{\tau}\} = \tau,
+        \]
+        so long as $\text{Within}_{it}$ contains all the units with spillovers.
+    }
 \end{frame}
@@
     I assume a modified version of the parallel counterfactual trends assumption:
+
+    \textbf{Assumption:} \textit{Parallel Counterfactual Trends}
     \begin{align*}
@@
 \begin{frame}{What does Difference-in-Differences identify?}
-    With the parallel trends assumption and random assignment of $D_i$, I decompose the diff-in-diff estimate as follows:
+    With the parallel trends assumption and random assignment of $D_i$, I decompose the difference-in-differences estimate as follows:
 
@@
 
-\begin{frame}{Example of Bias: Large Factory Opening}\label{slide:example_bias}
-    \textbf{Control Spillover:}
+\begin{frame}{Removing Bias}
+    \textbf{Assumption:} \textit{Spillovers are Local}
 
-    $Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) = 1$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+    Let $d(i,j)$ be the distance between units $i$ and $j$. There exists a distance $\bar{d}$ such that
 
-    \textbf{Treated Spillover:}
+        (i) For all units $i$,
+        \[ 
+            \min_{j: \ D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
+        \]
 
-    $Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) = 0.5$ if county $i$ is within 40 miles of a treated county and $0$ otherwise.
+        (ii) There are treated and control units such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
+\end{frame}
 
-    \pause
-    Then, the bias term is 
-    \begin{align*}
-        &0.5 * \text{\% of treated counties within 40 miles of another treated county} \\
-        &-1 * \text{\% of treated counties within 40 miles of a treated county}
-    \end{align*}
+\begin{frame}{Removing Bias}
+    With assumption that spillovers are local, define $S_i$ to be an indicator that contains all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).
 
-    \hyperlink{slide:partial_identification}{\beamerbutton{Partial Identification}}
+    Then $\hat{\tau}$ will be a consistent estimate for $\tau$ in this specification: 
+    \[ 
+        y_{it} = \mu_t + \mu_i + \tau D_{it} + \text{Within}_{it} * D_{it} + \text{Within}_{it} * (1-D_{it}) + \varepsilon_{it}
+    \]
+
 \end{frame}
@@
 
-\begin{frame}{Monte Carlo Simulations}
+\begin{frame}{Common Solution: Removing ``contaminated'' controls}
+    A common solution to the problem of spillover is to restimate on a subsample with neighboring control units removed.
+
+    This is not recommended for two reasons:
+
     \begin{itemize}
-        \item Data Generating Process 
-        \begin{align*}
-            y_{it} &= \mu_t + \mu_i + \textcolor{green}{\tau_{\text{direct}}} D_{it} + \textcolor{purple}{\tau_{\text{spillover, control}}} (1-D_{it}) \text{Within 40mi.}_{it} \\ 
-            &\quad + \textcolor{red}{\tau_{\text{spillover, treated}}} D_{it} \text{Within 40mi.}_{it} + \varepsilon_{it}
-        \end{align*}
+        \item Removing control units from the sample decreases precision of the estimates
 
-        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly or through a spatial process.
-
-        \item $\text{Within 40mi.}_{it}$ is an indicator for having your county center of population be within 40 miles of a treated unit.
-
-        \item $\textcolor{green}{\tau_{\text{direct}}} = 2$, $\textcolor{purple}{\tau_{\text{spillover, control}}} = 1$ and $\textcolor{red}{\tau_{\text{spillover, treat}}} \in \{0, 0.5\}$.
+        \item Spillover effects on treated units will still remain in the estimand. 
     \end{itemize}
 \end{frame}
-
-\begin{frame}{Source of Bias 1: Control Units}
-    Simulation 1:
-
-    \begin{itemize}
-        \item The first simulation changes the probability of treatment, $D_{it}$.
-
-        \item Assume, for now, there is only spillover on the control, i.e. $\tau_{\text{spillover,treat}} = 0$.
-
-        \item Estimate via TWFE: \begin{equation*}
-            y_{it} = \mu_t + \mu_i + \tau D_{it} + \epsilon_{it}    
-        \end{equation*}
-
-        \item The bias of our estimate is \textit{Bias} $= \hat{\tau} - 2$
-    \end{itemize}
-
-\end{frame}
-
-\imageframe{../../figures/figure-bias_from_prob_treat_slides.png}
-
-\begin{frame}{Solution: Removing ``contaminated'' controls}
-    A common solution to the problem of spillover is to restimate on a subsample with neighboring control units removed.
-
-    This simulation drops only units with $\text{Within 40mi.}_{it} = 1$. The exact exposure mapping is typically not observable for researchers, so this is best case scenario.
-\end{frame}
-
-\imageframe{../../figures/figure-bias_fix_slides.png}
-
-\begin{frame}{Why Removing Controls Doesn't Work Well}
-    \begin{itemize}
-        \item[1.] Lose precision in treatment effect estimate by dropping control units
-        \item[2.] If there are spillovers on treated units, removing controls won't remove both sources of bias. 
-    \end{itemize}
-
-    I repeat the same simulations but with $\textcolor{red}{\tau_{\text{spillover, treat}}} = 0.5$
-
-\end{frame}
-
-\imageframe{../../figures/figure-bias_fix_treat_slides.png}
 
@@
 
-    This is not observable to a researcher which raises the question:
+    The corret exposure mapping is not observable to a researcher which raises the question:
 
@@
 
+    \begin{itemize}
+        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly.
+    \end{itemize}
+
     Then, I estimate each data-generating process using (potentially) misspecified $\tilde{h}(\vec{D}, i)$ and report the average estimate bias.
-
 \end{frame}
@@
         \begin{itemize}
-            \item Inidicator for nearest treated unit being within $40/80$ miles.
+            \item Indicator for nearest treated unit being within $40/80$ miles.
         \end{itemize}
@@
     \onslide<3->{
-        \textbf{Inidicator that captures all affected unit removes all bias}
+        \textbf{Indicator (or set of indicators) that captures all affected unit removes all bias}
     }
@@
     \begin{itemize}
-        \item $y$ are outcomes for agricultural employment, manufacturing employment, and median family income.
+        \item $y$ are outcomes for agricultural employment and manufacturing employment.
         \item $\text{TVA}_c$ is the treatment variable
@@
         \end{itemize}
-
-        \item \textbf{Income:} 
-        \begin{itemize}
-            \item Since manufacutring jobs pay higher than agricultural jobs, the above two spillover effects can cause changes in median family income
-        \end{itemize}
     \end{itemize}
@@
 \begin{table}[ht]
-    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
+    \caption{Effects of Tennessee Valley Authority on Decadel Growth, 1940-2000}
     \label{tab:tva}
@@
                     &   $(0.0187)$   &   $(0.0210)$   &   $(0.0205)$   &   $(0.0257)$   &   $(0.0147)$
-                }
-                \onslide<3->{
-                    \\
-                    Median family income        & $0.0191^{***}$ &  $0.0196^{**}$ &    $0.0056$    &    $-0.0062$   &    $-0.0011$   \\
-                    &   $(0.0067)$   &   $(0.0077)$   &   $(0.0079)$   &   $(0.0060)$   &   $(0.0032)$ 
                 }

### 2021-04-07 latex/slides_short/Spillover_slides_short.tex
Update slides for Oral Comps

@@
     \vspace{5mm}
-    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries (states, counties, etc.)
+    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries (states, counties, etc.). Example:
 
     \begin{itemize}
-        \item E.g. a large employer opening/closing in a \textbf{treated} county have positive employment effects on \textit{nearby counties}
+        \item A large employer opening/closing in a \textbf{treated} county have positive employment effects on \textit{nearby counties}
 

### 2021-04-23 latex/paper/Spillover.tex
Draft 4/16

@@
 
-\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillover}
-% \subtitle{Subtitle}
+\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers}
 \author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
@@
 
-Empirical work in economics often considers settings where treatment is assigned to groups of units, but the effect of these treatments spillover onto ‘close’ units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
-geographic
-distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, treatment is commonly assigned to geographic boundaries and spillovers occur from people crossing borders to access treatment (i.e.
-imperfect compliance) or from general equilibrium effects influencing neighboring areas.
-Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.
-The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect.\footnote{In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The central theoretical result of my paper is that in the presence of spillovers, the standard difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.
+Empirical work often considers settings where treatment is assigned to groups of units by geographic boundaries, but the effect of these treatments spillover onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} In this setting, there are two types of spillover effects.
+First, there can be spillover effects onto control units.
+For example, individuals in control areas can travel to the treated areas and receive treatment (e.g.
+a hospital opening serves nearby residents) or changes in the economy in a treated area can have feedback loops that affect nearby economies (e.g.
+a new factory opening increases service sector spending).
+Second, there can be spillover effects onto other treated units.
+For example, forces of agglomeration can increase effects as treatment concentration increases (e.g.
+knowledge-sharing between workers), forces of congestion or market competition can decrease the effects of treatment (e.g.
+bidding up of wages cause employment effects of factory openings to be mitigated), and treatment effectiveness may be improved by multiple jurisidictions learning from one another.
 
-The intuition for the two bias terms resulting from spillovers is as follows.
+In this paper, I introduce a potential outcome framework that directly models spillover effects.
+Using this framework, the central theoretical result of my paper is that in the presence of spillovers, the standard difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.\footnote{The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect.
+In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The intuition for why the two forms of spillovers cause bias is as follows.
+
 First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
@@
 In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
+
 For example, consider trying to estimate employment effects of a factory opening in a county.
@@
 
-% @TODO: Improve examples to better build intuition
+% Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.
 
-Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-The spillover onto other treated units is averaged into the treated units' change in outcomes.
+Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.The spillover onto other treated units is averaged into the treated units' change in outcomes.
 Therefore the bias of treatment effect is the same sign as the sign of the spillover.
@@
 
-I then use my framework to evaluate commonly used empirical strategies found in applied work and provide practical recommendations for researchers.
+I then use my potential outcome framework to evaluate commonly used empirical strategies found in applied work and provide practical recommendations for researchers.
 The most common approach is to remove potentially contaminated control units from the sample in order to remove spillover effects on control units \citep{Berg_Streitz_2019}.
 This approach is not recommended for two reasons.
-First, the removal of too few control units will leave bias and removal of too many control units will lower precision of the treatment effect estimate.
+First, the removal of too few control units will leave bias and removal of too many will lower precision of the treatment effect estimate.
 This results in a bias-variance trade-off that other approaches do not share.
@@
 Therefore, I propose an estimation strategy that will remove both sources of bias with very minimal assumptions on the structure of spillovers.
-To remove \textit{all bias} from the direct effect estimate, a research needs to just include an indicator for being close to a treated unit interacted with treatment status, so long as the indicator captures all units affected by spillovers.
+To remove \textit{all bias} from the direct effect estimate, a researcher needs to just include an indicator for being close to a treated unit interacted with treatment status, so long as the indicator captures all units affected by spillovers.
 In my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units.
-An idicator variable interacted with treatment status therefore can estimate these two averages and remove them from the difference-in-differences estimate.
+An indicator variable interacted with treatment status therefore can estimate these two averages and remove them from the difference-in-differences estimate.
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
 The only assumption required is the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed.
-However, including too many units will increase the variance in the estimates for average spillover effects.}
+Including too many units in the indicator will increase the variance in the estimates for average spillover effects as the other control units identify the parallel counterfactual unit.}
 
@@
 This involves creating a set of distance bins from treated units (e.g.
-being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
-% TODO: Reference Butts and Clarke
-} The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not.
-For non-additive spillovers, I recommend a set of mutually-exclusive indicators which measures which distance bin that the closest treated unit falls within for a given observation.
-For additive spillovers, I recommend using the number of treated units within each distance bin for a given observation.\footnote{While the non-additive version of ring indicators will remove all bias from the direct effect of treatment even under misspecification, this is not true of additive rings.
+being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.} The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not.
+For non-additive spillovers, I recommend a set of mutually-exclusive indicators which measures which distance bin that the \textit{closest} treated unit falls within for a given observation.
+For additive spillovers, I recommend using the \textit{number of} treated units within each distance bin for a given observation.\footnote{While the non-additive version of ring indicators will remove all bias from the direct effect of treatment even under misspecification, this is not true of additive rings.
 Therefore, researchers may want to estimate the direct effect of treatment using non-additive rings and then use additive rings to estimate spillover effects.}
 
-I turn to an empirical application in the literature in urban economics on local place-based policies in Section \ref{sec:tva}.
-Using structural urban models, \citet{Kline_Moretti_2014b} show that the `local' or partial equilibrium effects of a place-based policy are offset in part by indirect or general equilibrium effects in non-treated locations.
-In particular, their model implies these effects are declining in distance.
-I contribute by showing that because of these general equilibrium effects, estimation of local effects are often misestimated by not controlling for the spillover effects in their empirical specification.
-
-As an example, I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
+To show the importance of considering spillover effects, I revisit analyses of place-based policies in urban economics in Section \ref{sec:tva}.
+I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
 The Tennessee Valley Authority was a large scale New Deal program that created many new dams for flood-protection and navigation.
@@
 The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citep{Severnini_2014}.
-I show that estimation by difference-in-differences fails to account for these spillovers and for different outcome variable it underestimates and overestimates the local effect, depending on the sign of the spillovers.
+I show that estimation by difference-in-differences fails to account for these spillovers and therefore forms biased estimates of the local effect of the Tennessee Valley Authority.
 
@@
 \citet{Busso_Gregory_Kline_2013} use Census Tracts from qualified but ultimately rejected applications that are typically far away from accepted Zones as a comparison group and find that significant reductions in poverty.
-This empirical strategy is based on the idea that since they qualified for the program they would be on similar trends without being contaminated by spillover effects.
+This empirical strategy is based on the idea that since they also qualified for the program, these comparison units would be on parallel trends without being contaminated by spillover effects from treatment.
 \citet{Neumark_Kolko_2010}, on the other hand, use census tracts within 1,000 feet of the Zone and find no statistically significant effects.
@@
 My paper is the first paper to study estimation of treatment effects in an event-study framework in the presence of spillover effects.
+
+I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.
+They find that the health centers significantly lowered the mortality rate in treated counties.
+I find that in this context, since the mortality declines caused by the health centers was due to primary care, spillover effects are near-zero.
+This result shows the importance of accessability concerns when deciding the location of the health centers.
+
+% ------------------------------------------------------------------------------
+\subsection{Relation to the Literature} 
+% ------------------------------------------------------------------------------
 
@@
 Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
-Section \ref{sec:estimation} presents Monte Carlo simulations to illlustrate the bias result and to evaluate currently used solutions in the literature.
+Section \ref{sec:estimation} focuses on estimation of the direct and spillover effects of treatment.
+I evaluate currently used solutions in the literature and present a set of recommendations to more robust estimation strategies.
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
 Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_Sant’Anna_2020}.
+I apply these methods in evaluating spillover effects of U.S.
+Community Health Centers in Section \ref{sec:chc}.
 
@@
 
-Following the canonical difference-in-difference framework, there is a time $t_0$ where treatment turns on and remains on afterwards.
-This framework is extended to staggered treatment adoption in section \ref{sec:event_study}.
-Potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+Following the canonical difference-in-differences framework, there is a time $t_0$ where treatment turns on and remains on afterwards.\footnote{This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
 The potential outcomes are denoted $Y_{i,t}(D_i, h(\vec{D}, i)$).
@@
 When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$.
-The exposure mapping formalizes the SUTVA violation in that potential outcomes are affected by other unit's treatment assignment as summarized by $h(\vec{D}, i)$.
-To help better understand the exposure mapping function, I give three examples of $h(\vec{D}, i)$ that are commonly used in the literature.
+The exposure mapping formalizes the SUTVA violation by summarizing how outcomes are affected by other unit's treatment assignment.
+To help better understand the exposure mapping function, I give three examples that are commonly used in the literature.
 
 \begin{example}
-    First, $h(\vec{D}, i)$ can be a 0/1 variable that equals one only if there is a treated unit within $\bar{d}$-miles of unit $i$.\footnote{Similarly a dummy for counties that share borders is commonly used.} Let $d(i,j)$ be a geographic distance measure which tells the distance unit $i$ is from unit $j$.
+    First, $h(\vec{D}, i)$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.
 In this case \begin{equation}\label{eq:h_within}
@@
     \end{equation}
-    This exposure mapping is useful when it is assumed that spillovers do not decay over distance until $\bar{d}$ and the number of neighboring units treated do not impact the intensity of spillovers.
+    This exposure mapping is a realistic specification when it is assumed that spillover effects do not decay over distance until $\bar{d}$ and the intensity of spillovers does not depend on the number of neighboring units treated.
 For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
 In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library.
-Access to a neighboring town library is binary in nature, so it does not matter whether you can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
+The benefits of access to a neighboring town library does not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
 \end{example}
@@
 In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies.
-As more nearby counties receive new stores, the agglomeration forces increase \citep{Basker_2005}.
+As more nearby counties receive new stores, the agglomeration forces increase (e.g.
+\citet{Basker_2005}).
 \end{example}
@@
 \begin{example}
-    Last, is the spatial decay function where exposure decreases with distance.
+    Last, $h(\vec{D}, i)$ is a spatial decay function where exposure decreases with distance.
 In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
@@
 This creates problems with inference because it implies potential correlation between all units' error terms.
-For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed of spillover decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using non-linear least squares.
+For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least squares routine.
 In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
+This specification features exponential decay over distance which captures the theoretical insight that research spending in closer locations has a larger effect than further away spending.
 \end{example}
@@
 After chosing an exposure mapping that makes sense in the economic context, a researcher must also specify the functional form of the potential outcomes.
-Typically, the spillover function enters into the regression linearly and potentially the coefficient is allowed to differ by treatment status.
+Typically, the exposure mapping enters into the regression linearly and potentially the coefficient is allowed to differ by treatment status to reflect that spillovers on control and treated units can be different phenomenon.
 
@@
 \]
-
 To emphasize, the average spillover effect onto conrol units averages over each control unit's exposure mapping.
@@
 the average over all control units exposure mapping.
-
 Similarly, we define the average spillover effect onto also treated units as: \[
@@
 \] 
-which measures the effect of being treated in the absence of exposure to spillovers. This effect does not include the general equilibrium effects of multiple treated areas near one-another.
+which measures the effect of being treated in the absence of exposure to spillovers.
 
@@
 \] 
-where the expectation is over individuals and their exposures.
-I prefer the former because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.
-For example, a county deciding whether to implement a policy will want to consider the treatment effect plus the spillover at their current level of exposure.
-The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at different levels.\footnote{Estimation of the direct effect and spillover effect can be combined to estimate the ATE as defined by \citet{Sävje_Aronow_Hudgens_2019}.}
+where the expectation is over individuals and their exposures. The difference between their treatment effect and mine becomes more clear by adding and subtracting terms and rearranging:
+\begin{align*}
+    &Y_{it}(1, h(\vec{D}, i)) - Y_{it}(0, h(\vec{D}, i)) \\
+    &\quad = Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0) + Y_{it}(1, 0) - Y_{it}(0,0) + Y_{it}(0,0) - Y_{it}(0, h(\vec{D}, i)) \\
+    &\quad = \underbrace{Y_{it}(1, 0) - Y_{it}(0,0)}_{\text{Direct Effect}} + \underbrace{Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0)}_{\text{Spillover on Treated}} - \underbrace{(Y_{it}(0, h(\vec{D}, i) - Y_{it}(0,0))}_{\text{Spillover on Control}}
+\end{align*}
+The individual treatment effect \citet{Sävje_Aronow_Hudgens_2019} use is the direct effect of treatment plus the difference between spillover on treated units and spillover on control units.
+
+I prefer my definition of the direct effect because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.
+For example, a county deciding whether to implement a policy will want to consider the treatment effect plus the difference in spillover effects at a particular level of exposure.
+The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at specific exposure intensities.
+Estimates of the direct effect and spillover effect can be combined to estimate the ATE as defined by \citet{Sävje_Aronow_Hudgens_2019}.
 
@@
 In this section, I identify the two sources of bias in difference-in-differences estimation of the direct effect of treatment.
-To estimate the `direct effect of treatment', researchers estimate the canonical two-way fixed effects model,
+Researchers typically estimate the canonical two-way fixed effects model,
 \begin{equation}\label{eq:twfe}    
-    y_{it} = \tau D_{it} + \mu_i + \mu_t + \epsilon_{it}.
+    y_{it} = \tau D_{it} + \mu_i + \mu_t + \epsilon_{it},
 \end{equation}
-
+where $D_{it} = D_i 1(t=1)$.
 The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$ in the presence of spillovers.
@@
 
-\begin{assumption}[Parallel Counterfactual Trends]\label{eq:parallel}
+\begin{assumption}[Parallel Counterfactual Trends]\label{assumption:parallel}
     \[ 
@@
 
-Given that Assumption \ref{eq:parallel} holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias.
+Given that Assumption \ref{assumption:parallel} holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias.
 The proof is given in Appendix \ref{sec:proofs}.
@@
 \begin{proposition}[Decomposition of Difference-in-Differences Estimate]\label{thm:bias}\ \\    
-    If Assumption \ref{eq:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
+    If Assumption \ref{assumption:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
     \begin{align*}
@@
 If they suspect spillovers onto control units, the bias is the opposite sign of the spillover.
-If they suspect spillovers onto treated units, the bias is in the same sign of the spillover.
+If they suspect spillovers onto treated units, the bias is the same sign of the spillover.
 The overall bias is the sum of the two.
@@
 % ------------------------------------------------------------------------------
-\subsection{Bounding the Bias}
+\subsection{Removing Bias}\label{sec:remove_bias}
 % ------------------------------------------------------------------------------
 
-The previous section finds an explicit form of the bias when estimating (\ref{eq:twfe}).
-The explicit form of bias can be used by researchers to provide bounds on the bias in a manner simmilar to \citet{Rambachan_Roth_2020}.
-To provide bounds on the bias, researchers must identify the set $\Delta = [\underline{\Delta}, \overline{\Delta}]$ such that it contains the bias \[
-    \tau_{\text{spill,treated}} - \tau_{\text{spill, control}} \in \Delta
+Under mild conditions, it is possible to control directly in a regression for the two sources of spillover effects.
+The set of indicators that contains all control/treated units respectively will estimate the average spillover effect on control/treated units and remove these sources of bias.
+The assumptions required to do this is that the researcher needs to be able to identify the maximum distance for which units are affected by spillovers and that there be unexposed units remaining.
+
+\begin{assumption}[Spillovers Are Local]\label{assumption:local}
+    There exists a distance $\bar{d}$ such that
+
+    (i) For all units $i$,
+    \[ 
+        \min_{j: \ D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
     \]
 
-Choosing this set requires considerations of the economic context.
-It is guided by choices of parameterization of the exposure mapping and potential outcomes.
-To exemplify this bias, I will illustrate how a researcher would bound the bias in a simple example.
-I will consider the example of the effect of new libraries on school outcomes.
-Following the motivation above, I assume that spillovers occur for any county that is within $\bar{d}$ miles of a treated county, i.e.
-\begin{align}
-    \label{eq:example_exposure}
-    h(\vec{D}, i) \equiv \text{Near}_{it} = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ].
-\end{align}
-This specification is a simple one in that the spillover is not additive in the number of nearby treated counties and does not decay over distance before reaching $\bar{d}$.
-Since treated counties have access to their own library, I will assume that no spillovers on to treated units exist.
-The potential outcome is assumed to be additive in both treatment and in the exposure mapping:
-\begin{align}
-    \label{eq:example_po}
-    \begin{split}
-        y_{it} &= \beta_{\text{direct}} D_{it} + \beta_{\text{spill,control}} (1-D_{it}) \text{Near}_{it} + \mu_t + \mu_i + \varepsilon_{it},
-    \end{split}
-\end{align}
-where $\mu_t$ and $\mu_i$ are unit and time fixed effects respectively. In this case, the spillover on an individual control unit is given by $\tau_{\text{spill,control}}$.
+    (ii) There are treated and control units such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
 
-If a researcher estimates (\ref{eq:twfe}), then the bias will be \[ 
-    - \tau_{\text{spill,control}} = - \beta_{\text{spill,control}} \frac{\sum_{i: D_{it} = 0} \text{Near}_{it}}{N_C},
-\] 
-where $N_C$ are the number of control units respectively.
-Simply put, the bias will be negative one times the proportion of control units that receive spillover effects time the size of the effect on control units.
-Then the bound can be created by bounding $\beta_{\text{spill,control}}$ and the proportion of control units that receive spillovers.
+\end{assumption}
 
-With a chosen $\Delta$, the partially identified set is given by $[\hat{\tau} + \underline{\Delta}, \hat{\tau} + \overline{\Delta}]$.
-Inference on this set can be done using Fixed-Length Confidence Intervals as in \citet{Rambachan_Roth_2020}.
-The confidence interval can be formed using standard normal critical values and spatially adjusted standard errors following \citet{Conley_1999} since we are assuming a specific spatial relationship between outcomes: \[
-    \left[ \hat{\tau} - \underline{\Delta} - z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}, \ \hat{\tau} + \overline{\Delta} + z_{1 - \alpha/2} \text{SE}_{\hat{\tau}}\right].  
-\]
+Part (i) of Assumption (\ref{assumption:local}) requires that spillovers are `local' in that units are no longer exposed to spillovers after the distance $\bar{d}$.
+Part (ii) of Assumption (\ref{assumption:local}) requires that there exists units outside of this distance $\bar{d}$ so that the counterfactual trend can be estimated.
+Let $S_{i}= 1(\min_{j: \ D_j = 1} d(i,j) > \bar{d})$ be an indicator for being within $\bar{d}$ miles of the closest treated unit after treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
+For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
+
+In order to remove both sources of bias, we modify the two-way fixed effects model to include this indicator interacted with treatment status:
+
+\begin{equation}\label{eq:twfe_with_ind}    
+    y_{it} = \tau D_{it} + \tau_{\text{spill,control}} (1-D_{it}) S_{i} + \tau_{\text{spill,treated}} D_{it} S_{i} +  \mu_i + \mu_t + \epsilon_{it}.
+\end{equation}
+
+\begin{proposition}[Unbiased Estimate for Direct Effect]\label{thm:remove_bias}
+    If Assumption \ref{assumption:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe_with_ind}) is
+    \begin{align*}
+        \mathbb{E}[\hat{\tau}] &= \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1, S_{i} = 0 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0 \right] \\ 
+        &= \tau_{\text{direct}} 
+    \end{align*}
+\end{proposition}
+
+The intuition behind this is that the indicator interacted with treatment status serve as unbiased estimates of the \textit{average} spillover effect onto treated and control units and therefore remove these terms from the direct effect estimate, $\hat{\tau}$.
+The proof uses standard Frisch-Waugh-Lovell style logic on a set of indicator variables and the fact that if $S_{it} = 0$ then $h(\vec{D}, i) = \vec{0}$.\footnote{The derivation follows very closely the work of \citet{Clarke_2019}.}
+
+This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
+An indicator for being `near' treatment ineracted with treatment status is enough to have an unbiased estimate for the treatment effect.
+A natural question is why wouldn't researchers make the distance really large?
+The problem with this is that control units with $S_i = 0$ identify the counterfactual trend and treated units with $S_i = 0$ identify the direct effect.
+Therefore leaving few units with $S_i = 0$ will yield more variable estimates.
+On the other hand, having units that experience spillovers with Therefore there is a bias-variance trade-off that should be balanced by researchers.
 
@@
 In this section, I analyze methods that have been used by researchers for estimation of the direct and spillover effects.
-I provide practical guidance on when the methods are effective and in particular propose a method that is most robust.
+In doing so, I provide practical guidance for the estimation of treatment effects with spillovers.
+After evaluating currently used strategies, I propose a method that improves upon commonly used methods.
 
@@
 
-A common approach in the literature is to drop control units neighboring treated units to avoid the problems of spillovers in identification.
-The above proposition would suggest that this can be effective in removing (at least part of) the average spillover effect on control units.
-However, since researchers do not know how far the spillovers spread there is difficulty in this method.
-On the one hand, removal of too few units will keep some control units that are experiencing spillover effects which would leave the treatment effect biased.
-On the other hand, removing too many units will leave few observations and therefore make the estimate have high variance.
-There is therefore a bias-variance trade off inherit to this method that can be readily improved by the method proposed in Section \ref{sec:parameterize}.
+A common approach in the literature is to drop control units adjacent to treated units to avoid the problems of spillovers in identification.
+Proposition \ref{thm:bias} and Assumption \ref{assumption:local} would suggest that this can be effective in removing (at least part of) the average spillover effect on control units.
+However, since researchers do not know how far the spillovers extend there is difficulty in implementing this method effectively.
+On the one hand, removal of too few units will keep some control units that are experiencing spillover effects which would leave the estimated treatment effect biased.
+On the other hand, removing too many units will leave few observations and therefore increase the variance of the estimates.
+There is therefore a bias-variance trade off inherent to this method that can be readily improved by the method proposed in Section \ref{sec:parameterize}.
 
-The second problem with this approach is that removal of control problems will not remove spillovers onto also treated units.
-Therefore if treated units are affected by the treatment status of nearby units, then the average spillover effect on treated untis which would remain as a source of bias.
+In addition to difficulties in implementation, the removal of problematic control observations, will not remove spillover effects onto treated units.
+Therefore if treated units are affected by the treatment status of nearby units, then the spillover effect on treated untis which would remain as a source of bias.
 Appendix \ref{sec:monte_carlo} contains a set of Monte Carlo simulations that highlight the problems more rigorously.
@@
 
-While some researchers try to remove untis that are most likely to experience spillover effects in order to estimate the direct effects, another common approach is to directly parameterize the spillovers themselves.
+While some researchers try to remove units that are most likely to experience spillover effects to estimate the direct effects, another common approach is to directly parameterize the spillovers themselves.
 Parameterization of the potential outcomes allows for unbiased estimates of $\tau_{\text{direct}}$ by controlling for the exposure mapping directly.
 This is recommended for two reasons.
-
-First, controlling for exposure mapping allows for unbiased estimates of the direct effect of treatment if the potential outcomes are correctly specified.
+First, controlling for the spillover effects allows for unbiased estimates of the direct effect of treatment if the potential outcomes are correctly specified.
 However, the functional form of spillovers is not observed by the researcher.
-I show in simulations below that information on the exact functional form is not required for unbiased estimates of the treatment effect.
-Therefore, estimation can occur without dropping units which will improve efficiency.
+I show in Proposition \ref{thm:remove_bias} that information on the exact functional form is not required for unbiased estimates of the treatment effect provided that spillovers are `local' as in Assumption \ref{assumption:local}.
+Therefore, unbiased estimation can occur without a loss in efficiency that comes from dropping units.
 
 Second, the spillover effects themselves are potentially relevant for policy makers.
-For example, if treatment for a given area is positive and there are positive benefits to neighboring regions, the estimated benefits will double-understate the true effect of treatment.
-First, it will not include the neighboring units' benefit in the calculation.
-Second, since the treatment effect will subtract the neighboring units' benefit, the neighboring units' benefit will be \emph{double undercounted}.
-Similarly, a policy maker trying to determine the net benefits for a treated location must consider the direct effect and the spillover effect onto treated units.
+For example, if the policy maker cares about treated areas and neighboring areas, then they should consider if the direct effect comes at a cost to nearby areas or if the benefits are being undercounted by only considering the treated area.
+Similarly, a policy maker trying to determine the net benefits for a treated location must consider the direct effect and the spillover effect received by treated units.
 This is because the size of benefits created by the treatment depend on the number of treated units nearby.
 
-There are a few practical considerations researchers should make when parametrizing the spillovers and the answers to the questions will depend ultimately on the economic context being studied.
+\subsubsection{Considerations when Modeling Spillovers}
+
+There are a few questions researchers must ask when parameterizing spillovers, the answers to which will ultimately depend on the economic context being studied.
 First, researchers should consider whether control units and/or treated units experience effects from the treatment status of other units.
@@
 Second, a researcher must decide how far the spillovers extend and whether the effect decays over distance.
-Things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
+This should again be guided by the economic context of the research question.
+For example, things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
 There are two commonly used techniques to model treatment effect decay.\footnote{If the spillovers is due to crossing borders into the treated area, then a reasonable decision about whether the effect decays is the frequency in which people use the good.
@@
 On the other hand, abortion clinics opening are used infrequently and therefore the effect likely doesn't decay over distance within a certain cutoff.} First, as seen above is to use an exponential decay function with regards to distance.
-The parameter $\alpha$ in Equation (\ref{eq:h_decay}) determines the rate of decline over distance.
+The parameter $\alpha$ in equation (\ref{eq:h_decay}) determines the rate of decline over distance.
 
-The other option is to use a set of `concentric rings' which are a semi-parametric way to estimate spillovers.
-If the spillovers do decay over distance, then the coefficients on the indicators should decrease as they move out.
-On the other hand, they are robust in estimating spillovers that do not decay, whereas exponential decay is not.
-In the simulations below, we will see that the rings are very flexible across forms of spillovers.
-An example of this is shown in the empirical application in Section \ref{sec:tva}.
+The other option is to use a set of `concentric rings' which are a semi-parametric model of spillovers.
+If the spillovers decay over distance, then the coefficients on the indicators should decrease as they move out.
+On the other hand, the concentric rings can allow for spillovers to be constant across distance.
+The exponential decay is less robust since it imposes a strictly monotonic function.
+In the simulations below, I show that rings are very flexible across forms of spillovers.
+An example of using rings is in the empirical application in Section \ref{sec:tva}.
 
-Last, it is important for estimation to know if the spillovers are additive or non-additive in nature.
+Last, it is important for estimation to determine if the spillovers are additive or non-additive in nature.
 If the number of nearby treated units matter, then the exposure mapping should sum over nearby treated units in some way.
@@
 In the context of factory openings, though, agglomeration economies imply that the spillovers are additive in nature.
-The simulations below show that in order to accurately estimate spillovers requires correctly using a additive or non-additive version of the concentric rings.
+Below, I show that in order to accurately estimate spillovers requires correctly using a additive or non-additive version of the concentric rings.
 
-To highlight the importance of these considerations, we turn to simulations where we include potentially incorrectly specified exposure mappings and see their performance in a set of different data generating processes.
-In the general form, I generate data with the same fixed effects and error term as before, but for many different exposure mappings $h(\vec{D}, i)$
+\subsubsection{Monte Carlo Simulations}
+
+To highlight the importance of these considerations, I turn to simulations where we include potentially incorrectly specified exposure mappings and see their performance in a set of different data generating processes.
+In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h(\vec{D}, i)$.
+I generate data for unit $i$ is a US county at time $t \in \{1, \dots, 20\}$ using the following data-generating process:
 \begin{equation}\label{eq:dgp_general}
-    y_{it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it}   
+    y_{it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it},
 \end{equation}
+where $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is $\varepsilon \sim N(0, 2^2)$.
 
-In order to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are qualitatively the same.
-For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
+In order to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
 The goal of this exercise is to see which specifications perform well under broad classes of spillovers.
+For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are the same.
 
-The set of spillover specifications include `Within $x$mi.' which equals 1 if the counties' center of population is within $x$ miles to a treated county's center of population, and `Within $x$mi.
-(Additive)' is the number of treated county's within $x$ miles of the control county.
-`Decay' is given by $\max_j D_j e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$ and `Decay (Additive)' is given by Equation (\ref{eq:h_decay}) with $\alpha = 0.02$.
+The set of spillover specifications included in the data-generating process are `Within $40/80$mi.' which equals 1 if the counties' center of population is within $40/80$ miles to a treated county's center of population.
+`Within $40/80$mi.
+(Additive)' is the number of treated county's within $40/80$ miles of the control county.
+`Decay' is given by $\max_j D_j e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$ and `Decay (Additive)' is given by $\sum_{j \neq i} D_j \exp^{-0.02 d(i,j)}$.
 
-The last set of spillover specifications is commonly used in the literature as a semi-parametric estimator and are referred to as `Donuts` or `Rings'.
+The last set of spillover specifications is commonly used in the literature as a semi-parametric estimator and are referred to as `Rings'.
 These consist of a set of indicators for falling within distance bins from the nearest treated unit (e.g.
 indicators for being between 0-20, 20-40, and 40-60 miles to closest treated unit).
-This approach is worth discussing in more detail because it will turn out to be the most consistent approach.
-These donuts are able to trace out all of the non-additive spillovers so long as the distance bins are numerous enough.
-For example, the donuts indicators add up to all the `Within xmi.' specifications if there are enough rings.
-The donuts can also trace out the decaying spillovers with the coefficients on each indicator decreasing in an exponential way.
-Donuts that go further than the maximum spillover distance will be estimated near zero, so adding too many rings is not a large concern.
-The last specification is an additive version of `Donuts' which is the number of treated units within each distance bin.
+This approach is worth discussing in more detail because it is the most consistent solution.
+These rings are able to trace out all of the non-additive spillovers so long as the distance bins are numerous enough.
+For example, the rings indicators add up to all the `Within xmi.' specifications if there are enough rings.
+The rings can also trace out the decaying spillovers with the coefficients on each indicator decreasing in an exponential way.
+Rings that extend past the maximum spillover distance will be estimated near zero, so they will still estimate the spillovers well.
+However, too many rings could lower precision of the estimates as estimation of the spillover effects relies on control units outside of the rings.
+In summary, the rings should extend far enough to ensure that all units affected by spillovers are contanied but not too far as to leave few units to estimate the counterfactual trend.
+
+The last specification is an additive version of `Rings' which is the number of treated units within each distance bin.
+This maintains a lot of the intuitive advantages of the `Rings' specification but parameterizes the spillovers to be additive in the number of nearby treated units.
+The advantage of this, as seen below, is enhanced performance of estimating spillover effects that are additive in nature.
+However, if the true specification is non-additive, then the additive specification no longer will remove all the bias from the direct effect estimate.
 
@@
             \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each cell corresponds to the mean bias from 1000 simulations of the data generating process specified by the column header and under the specification given by Equation (\ref{eq:dgp_general}) by the row label.
+                \item \textit{Notes.} Each cell corresponds to the mean bias from 1000 simulations of the data generating process specified by the column header and under the specification given by equation (\ref{eq:dgp_general}) by the row label.
             \end{tablenotes}
@@
 For each entry in the table, the column label corresponds to the true exposure mapping used in the data-generating process and the row label corresponds to the exposure mapping, $\tilde{h}(\vec{D}, i)$, used in estimation.
-The corresponding cell gives the mean bias from estimating Equation (\ref{eq:dgp_general}) with the $\tilde{h}(\vec{D}, i)$.
+The corresponding cell gives the mean bias from estimating equation (\ref{eq:dgp_general}) with the $\tilde{h}(\vec{D}, i)$.
+The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed effect estimate and in particular, correctly specifying the data-generating process removes almost all the bias.
 
-The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed effect estimate and in particular, correctly specifying the data-generating process removes almost all the bias.
-The second result is that both the `Donuts' and the `Within' specification do the best amongst all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers.
-This is due to the fact that indicator variables will correctly identify the average spillovers onto control units if they cover all the affected control units.
-If researchers are primarily interested in identifying the direct effect, then either `Donuts' or `Within' specifications with a large cutoff distance are preferred as they remove almost all bias in all settings.
+The second result is that both the `Rings' and the `Within' specification perform best among all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers.
+This is due to the fact that indicator variables will correctly identify the average spillovers onto control units if they cover all the effected control units (see Proposition \ref{thm:remove_bias}).
+If researchers are primarily interested in identifying the direct effect, then either `Rings' or `Within' specifications with a large cutoff distance are preferred as they remove almost all bias in all settings.
 
-However, we will now turn to seeing how these misspecifications are able to capture the spillovers themselves, and we will see that `Donuts' are superior to `Within' indicators in their ability to trace out spillovers, so they should be the default used by researchers unless there is theoretical motivation to use any specific parametrization for exposure mapping.
-For the next table, for each control county, I will predict their spillover value from the point estimates on $\tilde{h}(\vec{D}, i)$.
-Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (to make numbers comparable across data-generating processes), \[
+Now, I turn to analyzing how the specifications perform at estimating the spillover effects themselves.
+For the next table, I will predict their spillover value for each control unit from the point estimates on $\tilde{h}(\vec{D}, i)$.
+Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (for comparison across data-generating processes), \[
     1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}.
-\] This will produce a percentage of spillovers that are explained by the specification, so numbers closer to 1 represent better modelling of the spillovers.
+\] This will produce a percentage of spillovers that are explained by the specification, so numbers closer to $100\%$ represent better modelling of the spillovers.
 
@@
             \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each cell corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects from 1000 simulations of the data generating process specified by the column header and under the specification given by Equation (\ref{eq:dgp_general}) by the row label.
+                \item \textit{Notes.} Each cell corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects from 1000 simulations of the data generating process specified by the column header and under the specification given by equation (\ref{eq:dgp_general}) by the row label.
             \end{tablenotes}
@@
 
-Results are presented in Table \ref{tab:misspecification_mspe}.
+Results of this exercise are presented in Table \ref{tab:misspecification_mspe}.
 For each specification, correctly specifying the spillovers produces the best estimates for spillovers as expected.
-Among misspecified exposure mapping, `Donuts' that are large enough to caputre all the spillovers perform better than all other specifications in all non-additive data-generating processes.
-When the spillovers are additive, the predicted spillovers from the non-additive donut specifications do not as accurately measure these spillovers as they did before.
+Among misspecified exposure mapping, `Rings' that are large enough to caputre all the spillovers perform better than all other specifications in all non-additive data-generating processes.
+On the other hand, when the spillovers are additive, the predicted spillovers from the non-additive ring specifications do not as accurately measure these spillovers as they did before.\footnote{Although the non-additive Rings do estimate between 70\% and 80\% of the spillover effects while maintaining complete removal of bias.} Non-additvie specifciations perform somewhat poorly at estimating spillovers in the additive data-generating processes, `Within (Additive)' and `Decay (Additive)'.
+The `Rings (Additive)' specification sucessfully predicts spillovers in both additive data-generating processes.
 
-For additive data-generating processes, `Within (Additive)' and `Decay (Additive)' don't do a great job at predicting spillovers for the other data-generating process.
-On the other hand, the additive version of donuts sucessfully predicts spillovers in both additive data-generating processes.
-Therefore, the most important aspect of correctly estimating spillovers is to consider whether they are additive in the number of treated units or not.
-Researchers should use a version of donuts either way.
+Therefore there are two practical pieces of guidance from these simulations.
+First, for their ability to remove all bias, `Rings' should be the default used by researchers for estimating the direct effect of treatment.
+Second, the most important aspect of correctly estimating spillovers is to consider whether they are additive in the number of treated units or not.
+Researchers should use a version of Rings either way.
 
@@
 To illustrate the importance of accounting for spatial spillovers in the estimation of treatment effects, I revisit the analysis of the Tennessee Valley Authority (TVA) in \citet{Kline_Moretti_2014}.
-The TVA program was a large-scale federal investment started in 1934 that focused on modernizing the Tennessee Valley economy.
-The program focused on electrification through dams and transportation canals in order to improve the manufacturing economy.
-By the end of WWII, the TVA became the largest single power supplier in the country.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.} With over \$20 Billion (in 2000 dollars) spent and hundreds of dollars transferred per person in the Authority, the impacts are very likely to cross far past the authority's borders.
+The TVA program was a large-scale federal investment started in 1934 that focused on construction of dams and transportation canals in an attempt to modernize the Tennessee Valley's economy.
+By the end of WWII, the TVA became the largest single power supplier in the country and significantly lowered the cost of wholesale energy for factories.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.
+The effects on wholseale electricity are studied in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
 
-\citet{Kline_Moretti_2014} focus on a set of outcome variables, but I will focus on three in the analysis.
-The first two are (the log of) agricultural and manufacturing employment and the last is (the log of) median household income.
-Since the TVA focused on manufacturing employment, the authors predict that employment will grow in manufacturing and shrink in agricultural.
-Since manufacturing jobs pay more on average, the median household income will therefore grow.
+\citet{Kline_Moretti_2014} analysze a range of outcome variables, but I extend their work on (the log of) agricultural and manufacturing employment.
+Since the TVA primarily improved manufacturing industries through large-scale electrification, the authors predict that employment will grow in manufacturing and shrink in agricultural as workers switch to higher-paying manufacturing jobs.
 
-In \citet{Kline_Moretti_2014}, they discuss the nature of spillovers that can occur.
-For agriculture employment, the authors claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
-Hence they predict a negative spillover.
-For manufacturing, the sign is ambiguous.
-There could be positive spillovers if electrification brought cheap power to the neighboring areas.
-Also, agglomeration effects increase manufacturing employment in nearby counties.\footnote{\citet{Duranton_Puga_2003} give theoretical motivations for different sources of agglomeration.
-In this context, agglomerations due to `sourcing' is most likely.
-When the Authority has a large increase in manufacturing, they develop resource supply chains that in turn make inputs cheaper for neighboring counties.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.
-
-The analysis in \citet{Kline_Moretti_2014} begins by comparing long-differences in county-level outcomes from 1940 to 2000 between treated counties in the Authority and control counties outside.
-The primary difference-in-differences specification is
+The analysis in \citet{Kline_Moretti_2014} begins by comparing changes in county-level outcomes from 1940 to either 1960 (short-run effects) or 2000 (long-run effects) between treated counties in the Authority and control counties outside.
+The primary specification is
 \begin{equation}\label{eq:tva}
-    y_{c, t} = \mu_c + \mu_t + \tau \text{TVA}_c \times \text{Post}_t + X_{c, 1940} \times \text{Post}_t \gamma + \epsilon_{c,t},
+    y_{c, t} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \gamma + (\varepsilon_{c, t} - \varepsilon_{c, 1940}),
 \end{equation}
-where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ equals one when $t = 2010$ and equals zero when $t = 1940$, and $y$ is a set of outcome variables.\footnote{Outcome variables are all in logs and include population, average manufacturing wage, agricultural employment, manufacturing employment, value of farm production, median family income, and median housing value.
-The text writes the equivalent first-differences regression: \[
-    y_{c, 2000} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \gamma + (\varepsilon_{c, 2000} - \varepsilon_{c, 1940}). 
-\]} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
+where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ is an indicator for being in the post-period, and $y$ is a set of outcome variables (in logs).\footnote{The two-periods difference-in-differences regression is equivalent to a first-difference regression.
+The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is equivalent to a weighted difference-in-differences estimate.
+The weights are the propensity scores from a linear probability model where the outcome variable is being in the TVA.
+The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted relative to uniform weights.
+However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
 
@@
 
-As described above and estimated below, the program likely induced manufacturing and agricultural employment effects in nearby counties.
-By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect and median family income is theoretically ambiguous.
-The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this and appear to do so in the empirical analysis below.
+In the paper, the authors discuss the nature of spillovers that can occur.
+For agriculture employment, the authors claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
+Hence they predict a negative spillover.
+For manufacturing, the sign is ambiguous.
+There could be positive spillovers if electrification brought cheap power and agglomeration economies to the neighboring areas.\footnote{\citet{Duranton_Puga_2003} give theoretical motivations for different sources of agglomeration.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.\footnote{\citet{Cuberes_Desmet_Rappaport_2021} refer to the positive spillover effects as `urban access' and the negative spillover effecte as `urban shadows'.} My methodology will allow me to empirically test these predictions in the data and remove their bias from the treatment effect estimates.
 
-The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is a weighted difference-in-differences.
-The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted.
-However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.
+By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
+The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this.
+As discussed in Section \ref{sec:remove_bias}, bias in their estimate will likely remain even after dropping contiguous counties.
+The estimation strategy I present keeps the observations near the TVA while controlling for spillover effects in a more rigorous manner.
 
-In order to more likely satisfy the paralell trends assumption, the run a logistic regression to predict being in the TVA based on their set of control variables $X_{c, pre}$ and keep only observations in the top 75\% of predicted probability.
+To improve the likelihood of the paralell trends assumption, the run a logistic regression to predict being in the TVA based on their set of control variables $X_{c, pre}$ and keep only observations in the top 75\% of predicted probability.
 The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
@@
     {\footnotesize \textit{Notes:} The above figure plots all the counties used in the estimation.
-Counties that fall within the distance intervals $\{(0, 50], (50, 100], (100, 150]\}$ measured in miles are colored by their respective bin.}
+Counties that fall within the distance intervals $\{ (0, 50], (50, 100], (100, 150], (150, 200] \}$ measured in miles are colored by their respective bin.}
 \end{figure}
@@
 I extend their analysis to include spatial spillovers in the difference-in-differences specification.
-To parametrize the exposure mapping, I include a set of indicator variables for being in distance bins away from the Authority.
-I do this for two reasons.
-Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
-Figure \ref{fig:tva_sample} displays the three spillover variables by filling in each distance bin in a different color.
-As discussed above, I suspect the spillover effects to change with distance to the Authority, hence I allow the effect to be seperately identified in bins.
+To parametrize the exposure mapping, I include a set of indicator variables for when a county is within a certain distance interval from the Authority.
+Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150], (150, 200]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
+Figure \ref{fig:tva_sample} displays the four spillover variables by filling in each distance bin in a different color.
+The magnitude and potentially the sign of spillovers can change with distance, hence I allow the effect to be seperately identified in bins.
 I keep the number of bins small to improve precision of spillover estimates.
@@
 \begin{equation}\label{eq:tva_spillover}
-    y_{i, 2000} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, 2000} - \varepsilon_{i, 1940})
+    y_{i, t} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, t} - \varepsilon_{i, 1940}),
 \end{equation} 
-The coefficients $\delta_d$ measure the spillover effect onto control units at different distances from the Authority.
-From the above simulations, then $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect so long as spillovers don't occur past 150 miles from the TVA.
+where $t \in \{1960, 2000\}$.
+The coefficients $\delta_d$ estimate the average spillover effect onto control units at different distances from the Authority.
+From the above simulations, $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect so long as spillovers do not occur past 200 miles from the TVA.
 
-The results of the analysis are presented in Table \ref{tab:tva}.
+The results of the long-run analysis from 1940 to 2000 are presented in Panel A Table \ref{tab:tva}.
 The first column lists which dependent variable (measured in logs) was used in the row.
-The following columns contain point estimates for $\tau$ and $\delta_s$ in different specifications and can be interpreted as decadel growth rates in outcomes.
-The column labeled `Kline \& Moretti (2011)' use an Oaxaca-Blinder estimator while the column labeled difference-in-differences uses an ordinary least squares estimator for (\ref{eq:tva}).
-The two columns are very close in magnitude to each other.
-They find a decline in agricultural employment of about $5.6\%$ per decade, an increase in manufacturing employment of about $6.1\%$ per decade, and an increase in median family income of about $2.2\%$ per decade.
+The following columns contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
+The point estimates can be interpreted as decadel growth rates in outcomes.
+The column labeled difference-in-differences uses an ordinary least squares estimator for the specification without spillovers, equation (\ref{eq:tva}).
+This estimate finds a decline in agricultural employment of about $5.1\%$ per decade and an increase in manufacturing employment of about $5.6\%$ per decade.
 
-% \begin{landscape}
-% \thispagestyle{lscaped}
 \begin{table}[!tb]
@@
 
-    \begin{adjustbox}{width = 1.15\textwidth, center}
+    \begin{adjustbox}{width = \textwidth, center}
         \begin{threeparttable}
-            \begin{tabular}{@{} lc@{\extracolsep{20pt}}cc@{\extracolsep{4pt}}ccc @{}}
+            \begin{tabular}{@{} lc@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
                 % Head
@@
 
-                & \multicolumn{1}{c}{\textbf{\citet{Kline_Moretti_2014}}} &
-                \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
-                \cmidrule{2-2} \cmidrule{3-3} \cmidrule{4-7} 
-                & & & & TVA between & TVA between & TVA between \\ 
-                & TVA & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\ 
+                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{5}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
+                \cmidrule{2-2} \cmidrule{3-7}
+                & & & TVA between & TVA between & TVA between & TVA between \\ 
+                & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. & 150-200 mi. \\ 
                 \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\
@@
                 % Body
+                \toprule
+                \multicolumn{7}{l}{\textbf{Panel A:} 1940-2000} \\
                 \midrule
@@
                 \input{../../tables/tva_replication.tex}
+
+                \toprule
+                \multicolumn{7}{l}{\textbf{Panel B:} 1940-1960} \\
+                \midrule
+
+                \input{../../tables/tva_replication_short.tex}
 
@@
 All standard errors are clustered at the state-level.
-The column labeled \citet{Kline_Moretti_2014} replicates the Oaxaca-Blinder estimator found in column (3) of Table III.
-The column labeled `Diff-in-Diff' estimates (\ref{eq:tva}) by OLS.
+The column labeled `Diff-in-Diff' estimates (\ref{eq:tva}) by OLS and is similar to the estimate reported in \citet{Kline_Moretti_2014}.
 The final four columns labeled `Diff-in-Diff with Spillovers' are estimates from (\ref{eq:tva_spillover}).
@@
 \end{table}
-%\end{landscape}
 
-Turning to the last four columns that estimate (\ref{eq:tva_spillover}), column (3) contains a point estimate for $\tau$ and and columns (4)-(6) contain point estimates of the spillover effects $\delta_d$.
-For agricultural employment, our point estimates show there was a decline in agriculture employment in control units near the Authority.
-For control units between 0 and 50 miles, column (4) indicates a decline in agricultural employment of $3.1\%$.
-Between 50 and 100 miles the point estimate is $-1.1\%$ and between 100 and 150 miles, the point estimate is $-2.5\%$.
-This is likely due to the fact that higher paying manufacturing jobs within the Authority drew migrants from nearby counties.
+Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and and columns (3)-(6) contain point estimates of the spillover effects $\delta_d$.
+For agricultural employment, the point estimates show there was a decline in agriculture employment in control units near the Authority.
+For control units between 0 and 50 miles, column (4) indicates a decline in agricultural employment of $3.7\%$ per decade.
+Between 50 and 100 miles the point estimate is $-1.6\%$ per decade, between 100 and 150 miles the point estimate is $-3\%$ per decade, and between 150 and 2000 miles the point estimate is $-1.6\%$ per decade.
+This is likely due to the fact that higher paying manufacturing jobs within the Authority drew farm-worker migrants from nearby counties.
 Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
-The new point estimate indicates a decline of agricultural employment of about $6.8\%$ per decade compared to $5.1\%$ in the standard difference-in-difference specification.
+The new point estimate indicates a decline of agricultural employment of about $7.4\%$ per decade compared to $5.1\%$ in the standard difference-in-difference specification.
 
-For manufacturing, our point estimates for spillovers in column (4)-(6) are not statistically significant, but the signs on all three spillover estimates suggest that neighboring counties had a potentially negative spillover effect.
-Since there is little to no spillovers present, the new point estimate in column (3) of $4.6\%$ is not too far from the standard difference-in-differences estimate of $5.6\%$.
-Similarly, there is not a significant spillover on median family income.
-The point estimate therefore stays the same between the standard and spillover-adjusted difference-in-differences estimate of about $1.9\%$.
+For manufacturing, our point estimates for spillovers are consistently negative, though imprecisely estimated in some columns.
+The spillover estimates suggest that neighboring counties experienced potentially negative spillover effects in the long-run.
+Since there are negative spillover effects present, the new point estimate in column (2) of $3.5\%$ is significantly smaller than the original estimate of $5.6\%$.
+The spillover estimates are evidence that in the long-run, urban shadow forces dominate the benefits of urban access.
+As you move away from the Tennessee Valley, the point estimates become more negative which suggest that the benefits of urban access vanish over distance faster than the costs of urban shadow.
 
-These results show that including spillovers in the estimation of direct treatment effects is potentially important and in the case of agricultural employment can lead to \emph{significant} differences in treatment effect estimates.
+To see how spillover effects from a large-scale place-based policy develop over time, Panel B in Table \ref{tab:tva} presents results for the effects of the Tennessee Valley in the short-run using outcome data in 1960.
+Unlike in the long-run, areas near the Tennessee Valley did not experience significant declines in agricultural employment in the short-run.
+Since our long-run analysis finds significant increases in high paying manufacturing employment in the Tennessee Valley, this result is consistent with long-run migration costs being lower than short-run costs.
+
+For manufacturing, there are potentially positive increases in manufacturing employment within 100 miles of the Tennessee Valley authority and near zero effects between 100 and 200 miles.
+In the short-run, it appears that the effects of urban access and the cheap wholesale electricity dominated the effects of urban shadow.
+The effect of urban shadows can potentially be smaller in the short-run if operating firms are unlikely to relocate.
+Long-run effects can be larger as new firms change their location decision.
+
+These results show that including spillovers in the estimation of direct treatment effects is potentially important and can lead to \emph{significant} differences in treatment effect estimates.
 Analysis of place-based policies that do not account for the fact that treatment effects can spillover beyond the borders of treated areas can potentially be biased.
-The above results suggest this can over or underestimate the size of the effects depending on the sign of the spillovers.
+More, the effects of place-based policies change over time as frictions can create delays in reoptimizing behavior.
+
+% ------------------------------------------------------------------------------
+\subsection{Identification Strategies in Place-Based Analysis}
+% ------------------------------------------------------------------------------
+
+More generally, my framework provides important insights in the analysis of place-based policies.
+There are two ways I contribute.
+First, \citet{Baum-Snow_Ferreira_2015} recognize the problem of spatial spillovers causing problems in identification and point to aggregation of units as a way to alleviate to the problem (e.g.
+aggregation to metropolitan areas).
+However, this approach collapses the three seperate effects which might each be of interest into a singular aggregate effect.
+I have shown that all three effects of place-based policies can be estimated under very general assumptions about the spillovers.
+
+Second, my framework provides insight for different identification strategies often used in the literature.
+For example, consider the analysis of the effects of federal Empowerment Zones.
+The federal Empowerment Zones are specially designated areas in high-unemployment areas.
+The program gives businesses located in the zone tax incentives and the goal of the program is to reduce unemployment and poverty.
+In the literature, there are a set of conflicting results with some papers suggesting that the Empowerment Zones do indeed reduce poverty rates and others finding near-zero effects.\footnote{See Table 1 of \citet{Neumark_Young_2019} for a summary of the various treatment effect estimates in the literature.}
+
+\citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program.
+The rejected tracts are not typically geographically near accepted Empowerment Zones which removes the concern of spatial spillovers affecting control units' change in outcomes.
+They find large significant reductions in poverty rates.
+Meanwhile, \citet{Neumark_Kolko_2010} compare census tracts in Empowerment Zones to census tracts within 1,000 feet of the Zone.
+These control counties are likely the ones that experience the largest spillover effects.
+They find near-zero effects on poverty.
+
+My framework can reconcile both of these results.
+If census tracts just outside the Empowerment Zones also benefit from the policy, then the estimates of \citet{Neumark_Kolko_2010} are attenuated towards zero.
+These two identification strategies of using rejected applicants or using bordering units as the control group are very common in the urban literature \citep{Baum-Snow_Ferreira_2015}.
+My paper suggests that the former is the preferred strategy if spillovers occur onto nearby control units.
+
+In general, identification strategies that rely on geographically close control units as having similar unobservables should be used cautiously.
+If treatment effects spillover the Empowerment Zone borders, then narrowing the sample to controls very close to the border can leave treatment effect estimates biased.
+This insight applies more generally to identification strategies that compare observations just on either side of a border.
 
@@
 The intuition from how spillovers cause biases in estimates of the direct effect of treatment extend into the setting where there is staggered adoption in treatment.
-Two-way fixed effects estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates and therefore the bias terms will be identically weighted of the bias terms from the $2 \times 2$ estimates, assuming the parallel counterfactual trends assumption (\ref{eq:parallel}).\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Callaway_Sant’Anna_2020}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_D’Haultfoeuille_2019}.
-I won't recharacterize the weights in this article and guide interested readers to the source articles themselves.}
+When treatment turns on for different units at different times, two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_D’Haultfoeuille_2019}.
+I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be identically weighted of the bias terms from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
+However, since the weights can be negative, the sign of the spillover effects do not determine the sign of the weighted average of the spillover effects.
+This makes the bias from spillovers much more difficult to sign.
 
-Now, I will propose an estimation strategy that follows \citet{Callaway_Sant’Anna_2020} (C\&S) while incorporating spillovers directly into estimation.
-However, I won't cover all the technical details and point the reader to the main text for these details.
-To begin, C\&S define a `cohort' $g$ as the set of units that recevie treatment starting in period $g$.
+Now, I will propose an estimation strategy that follows \citet{Callaway_Sant’Anna_2020} while incorporating spillovers directly into estimation.
+However, I do not cover all the technical assumptions and point the reader to the main text for these details.
+To begin, Callaway and Sant'Anna define a `cohort' $g$ as the set of units that recevie treatment starting in period $g$.
 Let $G_g$ be an idicator equal to one for all units where treatment starts at period $g$ and $C$ an indicator equal to one if the unit never receives treatment.
-Each cohort will serve as the treated group for a set of $2\times 2$ difference-in-differences.
+Each cohort, $g$, will serve as the treated group for a set of $2\times 2$ difference-in-differences.
 For each period $t$ they define the `group-time average treatment effect', $ATT(g,t) = \mathbb{E}\left[ Y_t(g) - Y_t(0) \ \vert \ G_g = 1 \right]$, where $G_g$ is an indicator for starting treatment in year $g$.
@@
 $$ where the second term in potential outcomes represents an exposure mapping of $h(\vec{D}, i) = 0$.
-Similar to above, we modify the parallel trends assumptions given by CS to hold in the absence of exposure.
+Similar to above, we modify the parallel trends assumptions given by Callaway and Sant'Anna to hold in the absence of exposure.
 
-\begin{assumption}[Parallel Counterfactual Trends on a ``Never-Treated'' Group]\label{eq:parallel_es_never}
+\begin{assumption}[Parallel Counterfactual Trends on a ``Never-Treated'' Group]\label{assumption:parallel_es_never}
     $$
@@
 
-\begin{assumption}[Parallel Counterfactual Trends on ``Not-Yet-Treated'' Groups]\label{eq:parallel_es_notyet}
+\begin{assumption}[Parallel Counterfactual Trends on ``Not-Yet-Treated'' Groups]\label{assumption:parallel_es_notyet}
     $$ 
@@
 
-% ------------------------------------------------------------------------------
-\subsection{Estimating Direct Effects}
-% ------------------------------------------------------------------------------
+The group-time average direct effect is the building block of analysis in the framework proposed by Callaway and Sant'Anna.
+Estimation of the group-time average direct treatment effect, $ATT_{\text{direct}}(g,t)$ depends on which parallel trends assumption a researcher use.
+The difference-in-difference estimate uses period $t$ outcomes as the post-period and some period $g - \delta$ as the pre-period where $\delta$ is the number of periods before initial treatment.\footnote{It is recommended that $g - \delta$ be the closest period before anticipation can occur.
+For example, if no anticipation is present in the setting, then $\delta = 1$ would be the recommended choice.} In the context of spillovers, the canoncial difference-in-differences estimation will have to be adjusted using a parameterized exposure mapping to prevent the bias detailed in the $2 \times 2$ setting.
+As shown in Section \ref{sec:estimation}, this can be done using a large `Within' indicator that is wide enough to capture all of the spillovers.
+If a researcher is using Assumption \ref{assumption:parallel_es_notyet}, then estimation will be done with a subsample containing treated units from group $g$ and all units that are in groups $g' > t$.
+If a researcher is using Assumption \ref{assumption:parallel_es_never}, then estimation will be done using a supsample containing only control units and units in group $g$.
 
-The group-time average direct effect is the building block of analysis in the framework proposed by C\&S.
-Estimation of the group-time average direct treatment effect, $ATT_{\text{direct}}(g,t)$ depends on which parallel trends assumption a researcher use.
-If a researcher is using Assumption \ref{eq:parallel_es_never}, then estimation will be done using a supsample containing only control units and units in group $g$.
-The difference-in-difference estimate uses period $t$ outcomes as the post-period and some period $g - \delta$ as the pre-period where $\delta$ is the number of periods before initial treatment.
-In the context of spillovers, the canoncial difference-in-differences estimation will have to be adjusted using a parameterized exposure mapping to prevent the bias detailed in the $2 \times 2$ setting.
-As shown in Section \ref{sec:estimation}, this can be done using a set of donut indicators that is wide enough to capture all of the spillovers.
-
-If a researcher is using Assumption \ref{eq:parallel_es_notyet}, then estimation will be done with a subsample containing treated units from group $g$ and all units that are in groups $g' > t$.
-Again, estimation of the group-time direct effect will have to include controls for spillovers.
-
-Then, as detailed in C\&S, these ATT can be aggregated using different weights depending on the pararmeter of interest (see Table 1 of \citet{Callaway_Sant’Anna_2020}).
+Then, as detailed in C\&S, the $ATT(g,t)$ can be aggregated using different weights depending on the pararmeter of interest (see Table 1 of \citet{Callaway_Sant’Anna_2020}).
 These aggregations take the form of
@@
 \end{equation*} 
-These weights include the option to make event study estimates, or group-level average treatment effects (across time).
-Estimation and different aggregation of the direct effects can be done using the `did' package produced by CS where the measure of spillovers are included as covariates.
+Different weights produce different estimates for different average effects of interest, e.g.
+event study estimates, or group-level average treatment effects (across time).
+Estimation and different aggregation of the direct effects can be done using the `did' package produced by C\&S where the measure of exposure mapping are included as covariates.
+It is important to note that exposure can change over time as new units are treated, so researchers should make sure to use the correct values for exposure mapping for each year $t$.
 
@@
 
-Estimation of the spillover effects is potentially much more difficult as estimation of continuous variables in the presence of staggered treatment is still a work in progress and past the scope of this article.
-However, for indicator variables, estimation can be done in much the same way as the direct effect.
+Estimation of the spillover effects is potentially much more difficult as estimation of continuous variables in the presence of staggered treatment timing is still a work in progress and past the scope of this article.
+However, for a `Within' indicator, estimation can be done in much the same way as the direct effect but with more caution when constructing the samples for each $2 \times 2$ estimate.
+The `Within' indicator can be thought of as the treatment indicator and the sample would consist of only the control units.
+The advantage of the `Within' indicator is that it will remove all bias from the direct effects estimates if the indicator extends far enough and will give an estimate of the average spillover effect.
+However, as mentioned above, a `Within' indicator does a poor job of estimating (a) the shape of spillover effects over distance and (b) spillover effects that are additive in the number of nearby treated units.
+Estimation of different exposure mappings is a task left for future research.
 
-Since a set of donut indicators captures non-additive spillovers generally, I will focus on estimation of these donut indicators.
-For a given ring indicator, you would define groups by the period that a unit's ring indicator turns on.
-However, treated units can always move to more inner rings as treatment turns on over time, so control units should only enter estimation for the most inner indicator they enter.
+Groups in this case will be defined by the period which `Within' first equals 1 for a given observation and estimation of $ATT(g,t)$ should use all observations where `Within' is equal to zero for period t and before.
+Then, estimation can be done assuming that all control units are on the same counterfactual trends in the absence of spillovers which is satisfied by Assumption \ref{assumption:parallel_es_never}.
+Therefore, estimation and aggregation can be done in much the same way as for the direct effect but on just the subsample of control units.
 
-Then, estimation can be done assuming that all control units are on the same counterfactual trends in the absence of spillovers.
-For a given ring, the `treated' units consist of units that have that ring be the most inner spillovers they experience and the `control' units consist of all control units whose spillover status remains constant between the pre-period, $g - \delta$ and $t$.
-As above, estimation of the group-time average spillover effect should include the other spillover indicators to avoid biases from other spillover effects.
+% ------------------------------------------------------------------------------
+\section{Application on Community Health Centers}\label{sec:chc}
+% ------------------------------------------------------------------------------
 
-Therefore, for each spillover donut, estimation and aggregation can be done in much the same way as for the direct effect.
-However, estimation and aggregation can not be done using the `did' program as subsamples have to be constructed more specifically for each group-time average spillover effect.
+As an application of the above methods, I extend the analysis of \citet{Bailey_Goodman_Bacon_2015}.
+The authors study the creation of federal community health centers between 1965 and 1974 that provided \textit{primary} care to low-income communities.
+They test the hypothesis if access to low/no- cost health care services decreased mortality rates on the treated population.
+To answer this question, the authors use a common event-study framework to compare outcomes in treated counties to all other US counties by estimating the following specification
+\begin{equation}\label{eq:chc_es}
+    Y_{jt} = \theta_j + X_{jt} \beta + \sum_{y = -7}^{-2} \pi_y D_j 1(t - T_j^* = y) + \sum_{y = 0}^{15} \tau_{y} D_j 1(t - T_j^* = y) + \varepsilon_{jt},
+\end{equation}
+where $T_j^*$ is the year the county establishes a community health center, $D_j$ is an indicator for being treated, $\theta_j$ is county fixed effects, and $X_{jt}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed effects, and urban-group fixed effects.
+A full list can be found on page 1080 of \citet{Bailey_Goodman_Bacon_2015}.} The coefficents $\pi_y$ can be interpreted as tests of parallel pre-trends and $\tau_y$ can be interepreted as the treatment effect of a community health center $y$ years after establishment.
+
+\begin{figure}[tb!]
+    \caption{Effects of Establishment of Community Health Centers}
+    \label{fig:chc_es}
+
+        {\centering
+            \includegraphics[width=\textwidth]{../../figures/figure-chc-es_original.pdf}
+        }
+
+    {\footnotesize
+        \textit{Notes:} This figure recreates figure 5 from \citet{Bailey_Goodman_Bacon_2015}. Details on the event study specificaiton and controls can be found in the text.
+    }
+\end{figure}
+
+The result are in Figure \ref{fig:chc_es}.
+Estimates of $\hat{\tau}_y$ show that counties that received health centers had significantly lower mortality rates than the other counties in the US.
+In years following the establishment of the community health centers, the authors find a reduction of between 15-30 deaths per 100,000 residents compared to a baseline adjusted mortality rate of 929 deaths per 100,000 residents.
+
+\begin{figure}[tb!]
+    \caption{Direct and Spillover Effects of Community Health Centers}
+    \label{fig:chc_es_spill}
+
+        {\centering
+            \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
+        }
+
+    {\footnotesize
+        \textit{Notes:} This figure plots event study estimates for the treatment effect and the spillover effect on control units within 25 miles of treatment at different periods relative to establishment year.
+The estimates are generated using the `did' package produced from the paper \citet{Callaway_Sant’Anna_2020}.
+    }
+\end{figure}
+
+There are theoretical reasons to think spillovers may or may not exist in this context.
+On the one hand, individuals outside the county can potentially travel to the community health centers to receive care.
+This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
+On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that these effects are not due to emergency but rather primary care services.
+In this case, it is less likely low-income individuals would travel very far to receive care and hence the spillover effects would be near zero.
+My methodology can provide an answer to this question.
+
+As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
+Then, I follow \citet{Callaway_Sant’Anna_2020} in estimating event-study coefficients.
+The results are presented in Figure \ref{fig:chc_es_spill}.
+The confidence intervals labeled with circles represent point estimates for the average spillover effect on control units within 25 miles.
+No spillover effect is estimated to be significantly different from zero which suggests that the effects of community health centers are very local.
+Since there are near zero spillover effects, the direct effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
+
+The spillover effects results provide evidence that low-income individuals will not travel far to receive primary care.
+Practically, this suggests that community health centers should be targeted to be as accessible as possible for poor individuals as they are unable to travel far to access the services.
 
@@
 In this context, difference-in-differences estimation will identify a combination of the direct effect of treatment and two additional terms resulting from spillovers.
-I have proposed a potential outcomes framework that is used to express each of these spillover terms as a function of potential outcomes and the exposure mapping.
+I have proposed a potential outcomes framework that formalizes spillovers.
 
-Further, I show that parameterizing these spillovers can remove most of the biases even in the presence of some misspecification.
-In particular, I find that specifications with a set of `Donuts' are the best at capturing the spatial structure of spillovers.
+I use this framework to point to limitations in commonly used ad-hoc approaches to controlling for spillovers.
+Then, I propose a new estimation strategy that is robust to more forms of spillovers.
+In particular, I find that specifications with an indicator for being ``close to'' treated units interacted with treatment status will remove all bias in the direct effect estimate so long as all units affected by spillovers are contained in the indicator.
+More, I show that a set of concentric `rings' are the best at capturing the spatial structure of spillovers.
 When estimating spillover effects themselves, I find that it is important to correctly identify is spillovers are additive or non-additive in the number of nearby treated units.
@@
 Since place-based policies change the nature of agglomeration in the local and surrounding area --that is cause spillovers--local effects of these policies can be misestimated without controlling for spillovers.
+I also show the importance of considering spillovers in weighing the pros and cons of various identificatin strategies.
+Identification strategies based on geographic continuity of unobservables can magnify the bias from spillovers as they restrict the compairson group to observations experiencing the largest spillover effects.
 
 Finally, I show how researchers can include spillovers in settings with variation in treatment timing following \citet{Callaway_Sant’Anna_2020}.
+I then use this method to show how considering spillovers in event-study framework provide additional insights for a researcher.
 
@@
 \label{sec:monte_carlo}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 % ------------------------------------------------------------------------------
@@
 \begin{figure}[tb!]
-    \caption{Bias of $\hat{\tau}$ with Spillovers Effects \emph{only} on Control Units}
-    \label{fig:bias_as_treat_prob}
+    \caption{Effectiveness of Removing `Contaminated' Control Units}
+    \label{fig:bias_drop_control}
+
+    \begin{subfigure}[t]{\textwidth}
+        \caption{Spillovers Effects \emph{only} on Control} \label{fig:bias_as_treat_prob}
+
         {\centering
-        \includegraphics[width=\textwidth]{../../figures/figure-bias_fix.png}
+            \includegraphics[width=0.9\textwidth]{../../figures/figure-bias_fix.png}
         }
+    \end{subfigure}
+
+    \begin{subfigure}[t]{\textwidth}
+        \caption{Spillovers Effects on Control and Treated} \label{fig:bias_as_treat_prob_w_treat}
+
+        {\centering
+            \includegraphics[width=0.9\textwidth]{../../figures/figure-bias_fix_treat.png}
+        }
+    \end{subfigure}
+
     {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp1}.
+        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text by equations (\ref{eq:dgp1}) for Panel A and (\ref{eq:dgp2}) for Panel B.
 Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
@@
 
-For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
-\begin{equation}\label{eq:dgp2} 
-    y_{it} = \mu_t + \mu_i + 2 D_{it} + (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
+There is a second problem with the method of removing control units in the presence of spillover effects onto treated units.
+Since removing control units does not control for this second source of spillover effects, the estimates will be biased.
+In the second simulation, I add in spillover effects into the above data-generating process and set $\beta_{\text{spill, treat}} = 0.5$:
+
+\begin{equation}
+    \label{eq:dgp2} 
+    y_{it} = \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill, control}} (1-D_{it}) \text{Near}_{it} + \beta_{\text{spill, treat}} D_{it} \text{Near}_{it} + \varepsilon_{it}   
 \end{equation}
-The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
+
+The results are displayed in Figure \ref{fig:bias_as_treat_prob_w_treat}.
+Again, two-way fixed effect estimation results in a biased estimate as shown by the line with diamond markers.
+The magnitude is smaller than in Panel (a) because the positive spillovers onto treated units cancel out with the positive spillovers onto control units.
+However, removing the control units near the treated units results in a biased estimate due to the average spillover onto also treated units, as seen by the line with circle markets in Panel (b).
+This problem is particularly concerning as a researcher may assume that there is positive spillovers on control units that is negatively biasing their estimate and when removing those units the estimate would increase in magnitude as expected.
+Researchers could therefore potentially assume they have removed all bias from their estimates even though the second form of bias remains.
+
+% For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
+% \begin{equation}\label{eq:dgp2} 
+%     y_{it} = \mu_t + \mu_i + 2 D_{it} + (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
+% \end{equation} 
+% The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
 In empirical applications, it is often the case that treatment assignment is concentrated in specific areas which yields higher proportion of treated units receiving spillover effects.
 
-\begin{figure}[tbh!]
-    \caption{Example of Kriging Field}
-    \label{fig:kriging}
-    \begin{center}
-        \resizebox{0.8\textwidth}{!}{
-            \includegraphics{../../figures/figure-krig.png}
-        } 
-    \end{center}
+% \begin{figure}[tbh!]
+%     \caption{Example of Kriging Field}
+%     \label{fig:kriging}
+%     \begin{center}
+%         \resizebox{0.8\textwidth}{!}{
+%             \includegraphics{../../figures/figure-krig.png}
+%         } 
+%     \end{center}
 
-    {\footnotesize
-        \textit{Notes:} This figure plots an example of a kriging simulation using the `gstat' package in R using an exponential variogram.
+%     {\footnotesize
+%         \textit{Notes:} This figure plots an example of a kriging simulation using the `gstat' package in R using an exponential variogram.
 The outlined counties are in the top ten percent of values for this simulation.
-    }
-\end{figure}
+%     }
+% \end{figure}
 
-\begin{figure}[tbh!]
-    \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
-    \label{fig:bias_spatial_autocorr}
-    {\centering
-        \resizebox{\textwidth}{!}{
-            \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
-        } 
-    }
+% \begin{figure}[tbh!]
+%     \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
+%     \label{fig:bias_spatial_autocorr}
+%     {\centering
+%         \resizebox{\textwidth}{!}{
+%             \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
+%         } 
+%     }
 
-    {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and Equation \ref{eq:dgp2}.
+%     {\footnotesize
+%         \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and equation \ref{eq:dgp2}.
 Treatment probability is assigned according to the method described by the text and (\ref{eq:cond_prob}).
@@
 The line with circle markers removes control units that share a border with a treated county.
-    }
-\end{figure}
+%     }
+% \end{figure}
 
-In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
+% In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
 Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
@@
 \footnote{
-    To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
-    \begin{equation}
-        \label{eq:cond_prob}
-        P(D_i \ \vert \ \text{Zone}_i) = (.05 + \text{Zone Plus} * \text{Zone}_i) \times \underbrace{\frac{.05}{.05 * .9 + (.05 + \text{Zone Plus}) * .1}}_{\text{Normalize } P(D_i) = 0.05}
-    \end{equation}
-    The second term normalizes probabilities so the unconditional probability stays at five percent.
+%     To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
+%     \begin{equation}
+%         \label{eq:cond_prob}
+%         P(D_i \ \vert \ \text{Zone}_i) = (.05 + \text{Zone Plus} * \text{Zone}_i) \times \underbrace{\frac{.05}{.05 * .9 + (.05 + \text{Zone Plus}) * .1}}_{\text{Normalize } P(D_i) = 0.05}
+%     \end{equation}
+%     The second term normalizes probabilities so the unconditional probability stays at five percent.
 In our simulations, Zone Plus ranges from 0 which is the case where $P(D_i \vert \text{Zone}_i) = P(D_i) = 0.05$ to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.01 + 0.41 * \text{Zone}_i$.
-}
+% }
 
-The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
+% The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
 The line with diamond markers is run on the full sample.
@@
 
-The line with circle markers in Figure \ref{fig:bias_spatial_autocorr} repeats the exercise of dropping control units that share a border with treated units.
+% The line with circle markers in Figure \ref{fig:bias_spatial_autocorr} repeats the exercise of dropping control units that share a border with treated units.
 In the case where spillovers occur on treated units, all bias is not removed when dropping control units.

### 2021-04-28 figure-rings_example.R
Generate Example of Rings vs. Within

@@ -1,0 +1,177 @@
+## -----------------------------------------------------------------------------
+## figure-binscatter_example.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## On Binscatter (2020)
+## -----------------------------------------------------------------------------
+
+library(tidyverse)
+library(glue)
+library(binsreg)
+
+logname <- Sys.getenv("LOGNAME")
+cli::cli_alert_success("User: {logname}")
+
+if (logname == "kylebutts") setwd("~/Documents/Projects/Spatial Spillover/")
+rm(logname)
+
+# Load Custom Theme 
+source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
+
+# ggpreview
+ggpreview <- function(..., device = "png", cairo = TRUE) {
+	fname <- tempfile(fileext = paste0(".", device))
+	
+	if (cairo & device == "pdf") {
+		ggplot2::ggsave(filename = fname, device = cairo_pdf, ...)
+	} else if (cairo & device == "png") {
+		ggplot2::ggsave(filename = fname, device = device, type = "cairo", ...)
+	} else {
+		ggplot2::ggsave(filename = fname, device = device, ...)
+	}
+	
+	system2("open", fname)
+	invisible(NULL)
+}
+
+
+# Generate Data ----------------------------------------------------------------
+
+set.seed(100)
+
+df <- tibble(id = 1:500) %>%
+	# Generate Treatment and Distance
+	mutate(
+		treat = runif(n()) > 0.8,
+		treat = as.numeric(treat),
+		control = 1 - treat,
+		dist = runif(n(), 0, 100),
+		dist = dist * (1-treat)
+	) %>% 
+	# Make pre-post
+	expand_grid(t = c(0,1)) %>%
+	# Treatment Effects
+	mutate(
+		te = treat * t * 2,
+		spill1 = 1.5 * t * exp(-0.03 * dist) * (1-treat) * (dist <= 40),
+		eps = rnorm(n(), mean = 0, sd = 0.05),
+		y1 = 2*t + te + spill1 + eps
+	)
+
+
+# Take First Differences
+first_diff <- df %>% 
+	arrange(id, t) %>%
+	group_by(id) %>% 
[…]

### 2021-04-28 helper-conley.R
Fixed Conley SEs on TVA Analysis

@@ -4,13 +4,11 @@
 ## 
 ## This creates R functions for Conley (1999) Spatial-HAC standard errors. 
 ## For panel or cross-sectional data. For cross-sectional just don't include time and id vectors 
-## 
 ## -----------------------------------------------------------------------------
 
 library(Rcpp)
 library(RcppArmadillo)
 
-# setwd("")
 Rcpp::sourceCpp("helper-conley.cpp")
 
 
@@ -23,56 +21,47 @@ Rcpp::sourceCpp("helper-conley.cpp")
 #' @param e - vector of residuals
 #' @param coords - nx2 matrix of lat and long (order doesn't matter)
 #' @param dist_cutoff - Cutoff distance in km for spatial correlation
-#' @param lag_cutoff - Cutoff time in units of your time variable for serial correlation
-#' @param cores - multicore support with parallel::mclapply
-#' @param verbose - if TRUE, prints out a lot of details
-#' @param id - nx1 vector of id variable
-#' @param time - nx1 vector of time variable (can be in any units)
+#' @param lag_cutoff - (optional if panel) Cutoff time in units of your time variable for serial correlation
+#' @param id - (optional if panel) nx1 vector of id variable
+#' @param time - (optional if panel) nx1 vector of time variable (can be in any units)
 #'
 #' @note could be speed up if you put the lapply within C++ code. I calculate the N^2 distances for each time period
-conley_ses <- function(X, e, coords, dist_cutoff, lag_cutoff, cores = 1, verbose = FALSE, id = NULL, time = NULL) {
+conley_ses <- function(X, e, coords, dist_cutoff, lag_cutoff = 0, id = NULL, time = NULL) {
 	
-	# Load multicore
-	if(cores > 1) library(parallel)
+	X <- as.matrix(X)
+	coords <- as.matrix(coords)
+	e <- as.matrix(e)
 	
 	n <- nrow(X)
 	k <- ncol(X)
 	
 	panel <- !(is.null(id) | is.null(time))
 	if(!panel) print("No Panel dimension provided. Using just Spatial adjustment")
+	if(panel) {
+		time = as.matrix(time)
[…]

### 2021-04-28 helper-conley.cpp

@@ -1,5 +1,3 @@
-// https://github.com/darinchristensen/conley-se
-
 #include <iostream>
 #include <math.h>
 #include <RcppArmadillo.h>
@@ -53,24 +51,22 @@ double sh_cpp(double lat1, double long1,
 
 // Cross-sectional spatial clustering ------------------------------------------
 
-//' Cross-sectional XeeX matrix 
-//' Lg because it doesn't store distance matrices
+//' Cross-sectional XeeX matrix spatial clustering
 //' 
-//' @param M - nx2 matrix of lat-long points 
+//' @param coords - nx2 matrix of lat-long points 
 //' @param cutoff - cutoff distance in kilometers
 //' @param X - nxk model matrix from regression
 //' @param e - nx1 vector or residuals
-//' @param n1 - 
 //' @param k - number of covariates
 //' @param kernel - bartlett or any string "" for 0/1 Kernel
-//' @param dist_fn - Haversine or any string "" for other distance function. Use Haversine
+//' @param dist_fn - Haversine or any string "" for distance function used by Solomon Hsiang. Use Haversine.
 //  [[Rcpp::export]]
-arma::mat XeeX_spatial(arma::mat M, double cutoff,
-                    arma::mat X, arma::vec e, int n1, int k,
-                    std::string kernel="bartlett",
-                    std::string dist_fn="Haversine"){
+arma::mat XeeX_spatial(arma::mat coords, double cutoff,
+                       arma::mat X, arma::vec e, int k,
+                       std::string kernel = "bartlett",
+                       std::string dist_fn= "Haversine"){
 	
-	long long int nrow = M.n_rows;
+	long long int nrow = coords.n_rows;
 	
 	// Initialize XeeXh matrix
 	arma::mat XeeXh(k, k, fill::zeros);
@@ -78,23 +74,24 @@ arma::mat XeeX_spatial(arma::mat M, double cutoff,
 	
 	for( long long int i = 0; i < nrow; i++ ){
 		for( long long int j = 0; j < nrow; j++ ){
+			
 			double d;
 			
 			// Distance Function
 			if(dist_fn == "Haversine") {
[…]

### 2021-04-28 tva-analysis-replicate.R

@@ -165,7 +165,6 @@ controls <- c("lnelevmax", "lnelevrang", "lnarea", "lnpop20", "lnpop20sq", "lnpo
 dep_names <- c(
 	"Agricultural employment" = "D_lnagr", 
 	"Manufacturing employment" = "D_lnmanuf"
-	# "Median family income" = "D_lnmedfaminc", 
 )
 
 
@@ -188,12 +187,10 @@ for(y in dep_names) {
 	X <- reg_controls$X_demeaned
 	e <- reg_controls$residuals
 	coords <- as.matrix(temp[, c("lat", "long")])
-	time <- rep(1, nrow(coords))
 	# 1 mi = 1.60934 km
 	dist_cutoff <- 200 * 1.60934
-	lag_cutoff <- 1
 	
-	# cov_controls <- conley_ses(X, e, coords, dist_cutoff, lag_cutoff, cores = 4)$Spatial
+	cov_controls <- conley_ses(X, e, coords, dist_cutoff)$Spatial
 	
 	# Diff-in-Diff with Spillovers ---------------------------------------------
 	formula_controls_spill <- as.formula(paste0(y, " ~ tva + tva_0_50 + tva_50_100 + tva_100_150 + tva_150_200 + ", paste(controls, collapse = " + ")))
@@ -202,12 +199,10 @@ for(y in dep_names) {
 	X <- reg_spill$X_demeaned
 	e <- reg_spill$residuals
 	coords <- as.matrix(temp[, c("lat", "long")])
-	time <- rep(1, nrow(coords))
 	# 1 mi = 1.60934 km
 	dist_cutoff <- 200 * 1.60934
-	lag_cutoff <- 1
 
-	# cov_spill <- conley_ses(X, e, coords, dist_cutoff, lag_cutoff, cores = 4, time = time, id = time)$Spatial
+	cov_spill <- conley_ses(X, e, coords, dist_cutoff)$Spatial
 	
 	
 	# Create row
@@ -221,8 +216,7 @@ for(y in dep_names) {
 	
 	# Diff-in-Diff Controls TVA
 	pt     <- coef(reg_controls)[["tva"]]
-	se     <- sqrt(clubSandwich::vcovCR(reg_controls, temp$FIPSTAT1, "CR1S")[["tva", "tva"]])
[…]

### 2021-04-28 sim-misspecification_of_spillover.R
Added MSE row to misspecification and ran simulations 1000 times

@@ -27,12 +27,13 @@ source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd4
 
 # Export
 export <- TRUE
-slides <- FALSE
+run <- FALSE
 
 # extract_body()
 extract_body <- function(gt) {
 	if(inherits(gt, "gt_tbl")) gt <- as.character(gt::as_latex(gt))
-	stringr::str_match(gt, "(?s)\\\\midrule\\n(.*)\\\\bottomrule")[[2]]
+	gt <- stringr::str_match(gt, "(?s)\\\\midrule\\n(.*)\\\\bottomrule")[[2]]
+	stringr::str_remove(gt, " \\\\\\\\ \n$")
 }
 
 
@@ -46,88 +47,6 @@ source("helper-sim_function_misspecification.R")
 load(file= "data/counties_and_mat.RData")
 
 
-
-## Experimentation
-
-df <- sim_data_misspecification(drop_geometry=FALSE) %>% 
-	st_as_sf()
-
-# Check treatment effects with optional center of population dots
-ggplot(data = df %>% filter(year == 2019)) + 
-	geom_sf(mapping = aes(fill = te_spill_decay, color = as.factor(treat))) + 
-	# geom_sf(mapping = aes(geometry = centroid), color="white", size= 0.25) +
-	scale_color_manual(values = c("black", "red"))
-
-
-
-## Exerimentation
-
-for(i in 1:10) {
-	
-df <- sim_data_misspecification(drop_geometry=FALSE) %>% 
-	st_as_sf()
-	
-y <- "spill_decay"
-x <- "spill_within_large"
-
-# Rings 80
-formula <- as.formula(glue("y_{y} ~ treat_ind + post:spill_0_20 + spill_20_30:post + spill_30_40:post ", 
-						   "+ spill_40_60:post + spill_60_80:post | state_county + year"))
-
-reg <- feols(formula, data= df %>% st_drop_geometry()) 
-
-coef <- reg %>% coefficients()
-b_0_20 <- coef[2]
-b_20_30 <- coef[3]
-b_30_40 <- coef[4]
-b_40_60 <- coef[5]
-b_60_80 <- coef[6]
-
-var <- as.character(glue("te_{y}"))
-
-# Within 80
-formula <- as.formula(glue("y_{y} ~ treat_ind + ({x}:post) | state_county + year"))
-
-reg <- feols(formula, data= df %>% st_drop_geometry()) 
[…]

### 2021-04-28 latex/paper/Spillover.tex
4/28 Working Paper Draft

@@
 
-\addbibresource{references.bib}
+%\addbibresource{references.bib}
+\hypersetup{pdftitle={Difference-in-Differences Estimation with Spatial Spillovers}, pdfauthor={Kyle Butts}}
+
+\usepackage{dcolumn}
+\newcolumntype{d}[1]{D..{#1}}
+\newcommand{\mcc}[1]{\multicolumn{1}{c@{}}{#1}}
+\newcommand{\mcl}[1]{\multicolumn{1}{l@{}}{#1}}
+\newcommand{\mcr}[1]{\multicolumn{1}{r@{}}{#1}}
 
@@
 When researchers ignore the common problem that the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect.
-In this paper, I decompose this bias in two parts.
-First, the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment.
-Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-I propose estimation strategies that can remove both sources of bias as well as semi-parametrically estimate the spillovers themselves.
-Lastly, I extend this estimation strategy in an event-study framework following \citet{Callaway_Sant’Anna_2020} to allow for staggered treatment adoption.
-Then, I turn to an empirical application revisiting an analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
-I highlight the importance of considering general equilibrium spillovers in the analysis of place-based policies when estimating the direct effect on targeted areas.
+In this paper, I decompose this bias in two parts (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
+I propose estimation strategies that can remove both sources of bias as well as semi-parametrically estimate the spillover effects themselves.
+I extend this estimation strategy in an event-study framework following \citet{Callaway_SantAnna_2020} to allow for staggered treatment adoption.
+To highlight the importance of spillover effects, I revisit the analysis of three place-based policies and show the importance of directly controlling for general equilibrium spillovers caused by place-based policies.: the Tennessee Valley Authority \citep{Kline_Moretti_2014}, Federal Empowerment Zones \citep{Neumark_Young_2019}, and Community Health Centers \citep{Bailey_Goodman_Bacon_2015}.
     \end{abstract}
@@
 
-Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_Sant’Anna_2020}.
+Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_SantAnna_2020}.
 This allows for a very common setting in which treatment turns on for different units in different periods.
@@
 There is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
-Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares untis in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects.
+Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects.
 This allows standard difference-in-differences estimation of both the direct effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).
@@
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
-Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_Sant’Anna_2020}.
+Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_SantAnna_2020}.
 I apply these methods in evaluating spillover effects of U.S.
@@
 
-Following the canonical difference-in-differences framework, there is a time $t_0$ where treatment turns on and remains on afterwards.\footnote{This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Potential outcomes for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
-The potential outcomes are denoted $Y_{i,t}(D_i, h(\vec{D}, i)$).
+This section will present a potential outcome framework that formalizes spatial spillovers.
+Following the canonical difference-in-differences framework, there are T periods and treatment turns on for all treated units at some period $t_0$ and remain on afterwards.\footnote{This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Potential outcomes, denoted $Y_{i,t}(D_i, h(\vec{D},i))$, for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
 The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function.
@@
 In this case \begin{equation}\label{eq:h_within}
-        h(\vec{D}, i) = \max_{i \neq j} D_j * 1[ d(i,j) < \bar{d} ] 
+        h(\vec{D}, i) = \max_{i \neq j} D_j * \one[ d(i,j) < \bar{d} ] 
     \end{equation}
@@
     Second, $h(\vec{D}, i)$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
-        h(\vec{D}, i) = \sum_{j} D_j * 1[ d(i,j) < \bar{d} ].
+        h(\vec{D}, i) = \sum_{j} D_j * \one[ d(i,j) < \bar{d} ].
     \end{equation}
-    This exposure mapping is no longer binary, so the intensity of spillovers depend on the number of nearby units treated.
+    This exposure mapping is no longer binary, so the intensity of spillovers is additive in the number of nearby units treated.
 In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies.
-As more nearby counties receive new stores, the agglomeration forces increase (e.g.
+As more nearby counties receive new stores, the force of agglomeration and therefore the spillover effect increases (e.g.
 \citet{Basker_2005}).
@@
 
+% The results of this paper allows estimation and controlling for spillovers without needing to know the functional form of the exposure mapping. 
+% TODO: Finish
+
 % ------------------------------------------------------------------------------
@@
 
-With the potential outcomes defined, I now formalize what is meant by `spatial spillovers'. I define `spillover onto control units' as: \[
-    Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, \vec{0}).
+With the potential outcomes defined, I define `spillover effects' as: \[
+    Y_{i,t}(D_i, h(\vec{D}, i)) - Y_{i,t}(D_i, \vec{0}).
 \] 
-The spillover measures the difference in non-treated potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
-Then, the average spillover effect onto control units averages over potential heterogeneity in the effect size of spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
-    \tau_{\text{spill,control}} \equiv \mathbb{E} \left[ Y_{it}(0, h(\vec{D}, i)) - Y_{it}(0, \vec{0}) \ \vert \ D_i = 0 \right].
+The spillover effect measures the difference in potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
+This effect can differ for either treated or control units as the magnitude or even the nature of spillovers might differ between treated and untreated units.
+Then, the average spillover effect onto control/treated units averages over potential heterogeneity in the effect size of spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
+    \tau_{\text{spill,control}} \equiv \expec{Y_{i,t}(D, h(\vec{D}, i)) - Y_{i,t}(D, \vec{0}) \ \vert \ D_i = D}.
 \]
-To emphasize, the average spillover effect onto conrol units averages over each control unit's exposure mapping.
-For example, assume the potential outcomes is additively linear in $D_i$ and $h(\vec{D}, i)$ and that the coefficient $\beta_{\text{spill,control}}$ measures the effect of $h(\vec{D}, i)$ on outcome $Y$ among control units.
-Then an individual control unit's spillover effect is $\beta_{\text{spill,control}} \ h(\vec{D}, i)$.
-The average spillover effect onto control unit would therefore be $\tau_{\text{spill,control}} = \beta_{\text{spill,control}} * \mathbb{E} \left[ h(\vec{D}, i)\right]$, i.e.
-the average over all control units exposure mapping.
-Similarly, we define the average spillover effect onto also treated units as: \[
-    \tau_{\text{spill,treated}} \equiv \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0) \ \vert \ D_i = 1 \right].
-\]
-
-It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences.
+To emphasize, the average spillover effect onto conrol/treated units averages over each unit's exposure mapping which can be heterogeneous across units.
+For example, spillover effects can decay over distance as in Equation (\ref{eq:h_decay}) and the average spillover effect averages across different exposure intensities.
+
+It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences because there are multiple potential estimands defined in the literature.
 I assume that what the `average treatment effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
-    \tau_{\text{direct}} = \mathbb{E} \left[ Y_{it}(1, \vec{0}) - Y_{it}(0, \vec{0}) \ \vert \ D_i = 1 \right],
+    \tau_{\text{direct}} = \expec{Y_{i,t}(1, \vec{0}) - Y_{i,t}(0, \vec{0}) \ \vert \ D_i = 1},
 \] 
@@
 My definition of the direct effect of treatment differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the average treatment effect as \[ 
-    \mathbb{E} \left[ Y_{it}(1, h(\vec{D}, i)) - Y_{it}(0, h(\vec{D}, i)) \ \vert \ D_i = 1 \right],
+    \expec{Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(0, h(\vec{D}, i)) \ \vert \ D_i = 1},
 \] 
-where the expectation is over individuals and their exposures. The difference between their treatment effect and mine becomes more clear by adding and subtracting terms and rearranging:
+where the expectation is over individuals and over different levels of exposures.
+The difference between their treatment effect and mine becomes more clear by adding and subtracting terms and rearranging:
 \begin{align*}
-    &Y_{it}(1, h(\vec{D}, i)) - Y_{it}(0, h(\vec{D}, i)) \\
-    &\quad = Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0) + Y_{it}(1, 0) - Y_{it}(0,0) + Y_{it}(0,0) - Y_{it}(0, h(\vec{D}, i)) \\
-    &\quad = \underbrace{Y_{it}(1, 0) - Y_{it}(0,0)}_{\text{Direct Effect}} + \underbrace{Y_{it}(1, h(\vec{D}, i)) - Y_{it}(1, 0)}_{\text{Spillover on Treated}} - \underbrace{(Y_{it}(0, h(\vec{D}, i) - Y_{it}(0,0))}_{\text{Spillover on Control}}
+    &Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(0, h(\vec{D}, i)) \\
+    &\quad\quad = Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(1, 0) + Y_{i,t}(1, 0) - Y_{i,t}(0,0) + Y_{i,t}(0,0) - Y_{i,t}(0, h(\vec{D}, i)) \\
+    &\quad\quad = \underbrace{Y_{i,t}(1, 0) - Y_{i,t}(0,0)}_{\text{Direct Effect}} + \underbrace{Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(1, 0)}_{\text{Spillover on Treated}} - \underbrace{(Y_{i,t}(0, h(\vec{D}, i)) - Y_{i,t}(0,0))}_{\text{Spillover on Control}}
 \end{align*}
@@
 I prefer my definition of the direct effect because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.
-For example, a county deciding whether to implement a policy will want to consider the treatment effect plus the difference in spillover effects at a particular level of exposure.
-The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at specific exposure intensities.
-Estimates of the direct effect and spillover effect can be combined to estimate the ATE as defined by \citet{Sävje_Aronow_Hudgens_2019}.
+The alternative estimand averages over exposure intensities and therefore is difficult to be used by a policy maker in a particular location.
+That is, a county deciding whether to implement a policy will want to consider the treatment effect plus the difference in spillover effects at \textit{a particular} exposure intensity.
+The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at specific exposure intensities while my preferred method of identifying the three effects seperately can.
+Estimates of the direct effect and spillover effect can be later combined to estimate the average treatment effect as defined by \citet{Sävje_Aronow_Hudgens_2019}.
 
@@
 \begin{equation}\label{eq:twfe}    
-    y_{it} = \tau D_{it} + \mu_i + \mu_t + \epsilon_{it},
+    y_{i,t} = \tau D_{i,t} + \mu_i + \mu_t + \epsilon_{i,t},
 \end{equation}
-where $D_{it} = D_i 1(t=1)$.
+where $D_{i,t} = D_i \one(t = 1)$.
 The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$ in the presence of spillovers.
@@
     \[ 
-        \mathbb{E}\left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1 \right] = 
-        \mathbb{E}\left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0 \right]
+        \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \ \vert \ D_i = 1 } = 
+        \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \ \vert \ D_i = 0 },
     \]
+    where $\bar{Y}_{i,W}$ is the average outcome in either the post- or pre-periods.
 \end{assumption}
@@
     \begin{align*}
-        \mathbb{E}[\hat{\tau}] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0 \right]}_{\text{Difference-in-Differences}} \\
+        \mathbb{E}[\hat{\tau}] &= \underbrace{\expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 1 } - \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 0 }}_{\text{Difference-in-Differences}} \\
         &= 
-        \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
-        &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
+        \expec{\bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 1} + \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Post}(1, \vec{0}) \mid D_i = 1} \\
+        &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 0} \\
         &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
@@
 The intuition behind the biases are as follows.
-First, the change in outcomes among treated units combines the direct effect and the spillover from nearby treated units.
+First, the change in outcomes among treated units combines the direct effect of treatment with the spillover effects caused by nearby treated units.
 Therefore the first difference adds the average spillover effect onto the treated units, $\tau_{\text{spill,treated}}$.
 Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units.
-Since $\hat{\tau}$ is found by subtracting this second difference, we subtract the average spillover effect onto the control, $\tau_{\text{spill,control}}$.
+Since $\hat{\tau}$ is found by subtracting the change in outcomes among the control units, we subtract the average spillover effect onto the control, $\tau_{\text{spill,control}}$.
 
@@
 % ------------------------------------------------------------------------------
-\subsection{Removing Bias}\label{sec:remove_bias}
-% ------------------------------------------------------------------------------
-
-Under mild conditions, it is possible to control directly in a regression for the two sources of spillover effects.
-The set of indicators that contains all control/treated units respectively will estimate the average spillover effect on control/treated units and remove these sources of bias.
+\section{Estimation of Treatment Effects with Spillovers}
+\label{sec:estimation}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\subsection{Unbiased Estimation of Direct Effect}\label{sec:remove_bias}
+% ------------------------------------------------------------------------------
+
+Under mild conditions, it is possible to control directly in a regression for the two sources of spillover effects and to have unbiased estimates of the direct effect of treatment.
+A pair of indicators that contains all control/treated units respectively will estimate the average spillover effect on control/treated units and remove these sources of bias.
 The assumptions required to do this is that the researcher needs to be able to identify the maximum distance for which units are affected by spillovers and that there be unexposed units remaining.
@@
 
-    (ii) There are treated and control units such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
+    (ii) There are treated and control units, $i$, such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
 
@@
 
-Part (i) of Assumption (\ref{assumption:local}) requires that spillovers are `local' in that units are no longer exposed to spillovers after the distance $\bar{d}$.
-Part (ii) of Assumption (\ref{assumption:local}) requires that there exists units outside of this distance $\bar{d}$ so that the counterfactual trend can be estimated.
-Let $S_{i}= 1(\min_{j: \ D_j = 1} d(i,j) > \bar{d})$ be an indicator for being within $\bar{d}$ miles of the closest treated unit after treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
-For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
+Part (i) of Assumption (\ref{assumption:local}) requires that spillovers are `local' in that units are no longer exposed to spillovers after some maximum distance $\bar{d}$.
+Part (ii) of Assumption (\ref{assumption:local}) requires that there exists control units with no exposure in order to estimate the counterfactual trend and treated units with no exposure in order to estimate the direct effect.
+Let $S_{i}= \one(\min_{j: \ D_j = 1} d(i,j) \leq \bar{d})$ be an indicator for being within $\bar{d}$ miles of the closest treated unit after treatment.
 
@@
 \begin{equation}\label{eq:twfe_with_ind}    
-    y_{it} = \tau D_{it} + \tau_{\text{spill,control}} (1-D_{it}) S_{i} + \tau_{\text{spill,treated}} D_{it} S_{i} +  \mu_i + \mu_t + \epsilon_{it}.
+    y_{i,t} = \tau D_{i,t} + \tau_{\text{spill,control}} (1-D_{i,t}) S_{i} + \tau_{\text{spill,treated}} D_{i,t} S_{i} +  \mu_i + \mu_t + \epsilon_{i,t}.
 \end{equation}
@@
     \begin{align*}
-        \mathbb{E}[\hat{\tau}] &= \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 1, S_{i} = 0 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0 \right] \\ 
+        \expec{\hat{\tau}} &= \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 1, S_{i} = 0 } - \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 0, S_{i} = 0 } \\ 
         &= \tau_{\text{direct}} 
     \end{align*}
+
+    The expectation of the two spillover effect estimates are 
+    \begin{align*}
+        \expec{\hat{\tau}_{\text{spill,conrol}}} = \expec{ \bar{Y}_{i,Post}(0,h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \ \vert \ D_i = 0, S_i = 1}
+    \end{align*}
+    and 
+    \begin{align*}
+        \expec{\hat{\tau}_{\text{spill,treated}}} = \expec{ \bar{Y}_{i,Post}(1,h(\vec{D}, i)) - \bar{Y}_{i,Post}(1, \vec{0}) \ \vert \ D_i = 1, S_i = 1}
+    \end{align*}
 \end{proposition}
@@
 The intuition behind this is that the indicator interacted with treatment status serve as unbiased estimates of the \textit{average} spillover effect onto treated and control units and therefore remove these terms from the direct effect estimate, $\hat{\tau}$.
-The proof uses standard Frisch-Waugh-Lovell style logic on a set of indicator variables and the fact that if $S_{it} = 0$ then $h(\vec{D}, i) = \vec{0}$.\footnote{The derivation follows very closely the work of \citet{Clarke_2019}.}
-
-This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
-An indicator for being `near' treatment ineracted with treatment status is enough to have an unbiased estimate for the treatment effect.
-A natural question is why wouldn't researchers make the distance really large?
+The proof uses standard Frisch-Waugh-Lovell style logic on a set of indicator variables and the fact that if $S_{i} = 0$ then $h(\vec{D}, i) = \vec{0}$.\footnote{The derivation follows closely the work of \citet{Clarke_2019}.} This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
+An indicator for being `near' treatment ineracted with treatment status is enough to have an unbiased estimate for the treatment effect.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
+For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
+
+A natural question is why wouldn't researchers make the distance really large in order to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$?
 The problem with this is that control units with $S_i = 0$ identify the counterfactual trend and treated units with $S_i = 0$ identify the direct effect.
 Therefore leaving few units with $S_i = 0$ will yield more variable estimates.
-On the other hand, having units that experience spillovers with Therefore there is a bias-variance trade-off that should be balanced by researchers.
-
-% ------------------------------------------------------------------------------
-\section{Estimation of Treatment Effects with Spillovers}
-\label{sec:estimation}
-% ------------------------------------------------------------------------------
-
-In this section, I analyze methods that have been used by researchers for estimation of the direct and spillover effects.
-In doing so, I provide practical guidance for the estimation of treatment effects with spillovers.
-After evaluating currently used strategies, I propose a method that improves upon commonly used methods.
-
-% ------------------------------------------------------------------------------
-\subsection{Removing Bias by Dropping Control Units}
-% ------------------------------------------------------------------------------
+On the other hand, having units that experience spillovers not included in the $S_i$ indicator will leave some bias in the estimate.
+Although, since spillover effects typically will grow weaker over distance, the bias may not be particularly large if distant units are mistakenly treated as if they have zero exposure.
+Therefore there is a bias-variance trade-off in extending the extent of $S_i$ that should be balanced by researchers guided by their particular economic context.
 
@@
 On the other hand, removing too many units will leave few observations and therefore increase the variance of the estimates.
-There is therefore a bias-variance trade off inherent to this method that can be readily improved by the method proposed in Section \ref{sec:parameterize}.
-
-In addition to difficulties in implementation, the removal of problematic control observations, will not remove spillover effects onto treated units.
-Therefore if treated units are affected by the treatment status of nearby units, then the spillover effect on treated untis which would remain as a source of bias.
-Appendix \ref{sec:monte_carlo} contains a set of Monte Carlo simulations that highlight the problems more rigorously.
-
-% ------------------------------------------------------------------------------
-\subsection{Parameterization of Spillovers}
-\label{sec:parameterize}
-% ------------------------------------------------------------------------------
-
-While some researchers try to remove units that are most likely to experience spillover effects to estimate the direct effects, another common approach is to directly parameterize the spillovers themselves.
-Parameterization of the potential outcomes allows for unbiased estimates of $\tau_{\text{direct}}$ by controlling for the exposure mapping directly.
-This is recommended for two reasons.
-First, controlling for the spillover effects allows for unbiased estimates of the direct effect of treatment if the potential outcomes are correctly specified.
-However, the functional form of spillovers is not observed by the researcher.
-I show in Proposition \ref{thm:remove_bias} that information on the exact functional form is not required for unbiased estimates of the treatment effect provided that spillovers are `local' as in Assumption \ref{assumption:local}.
-Therefore, unbiased estimation can occur without a loss in efficiency that comes from dropping units.
-
-Second, the spillover effects themselves are potentially relevant for policy makers.
-For example, if the policy maker cares about treated areas and neighboring areas, then they should consider if the direct effect comes at a cost to nearby areas or if the benefits are being undercounted by only considering the treated area.
+There is therefore a bias-variance trade off inherent to this method that can be easily improved by creating an indicator for these units rather than dropping them from the sample.
+In addition to the unnecessary loss of precision induced by this method, the removal of problematic control observations, will not remove spillover effects onto treated units.
+Therefore if treated units are affected by the treatment status of nearby units, then the spillover effect on treated units which would remain as a source of bias.\footnote{Appendix \ref{sec:monte_carlo} contains a set of Monte Carlo simulations that highlight the problems more rigorously.}
+
+The second part of proposition \ref{thm:remove_bias} shows that equation (\ref{eq:twfe_with_ind}) can also be used to estimate average spillover effects.
+The spillover effects themselves are potentially relevant for policy makers.
+For example, if the policy maker cares about treated areas and neighboring areas, then they should consider if the direct effect comes at a cost to nearby areas (negative spillovers) or if the benefits are being undercounted by only considering the treated area (positive spillovers).
 Similarly, a policy maker trying to determine the net benefits for a treated location must consider the direct effect and the spillover effect received by treated units.
-This is because the size of benefits created by the treatment depend on the number of treated units nearby.
-
-\subsubsection{Considerations when Modeling Spillovers}
-
-There are a few questions researchers must ask when parameterizing spillovers, the answers to which will ultimately depend on the economic context being studied.
-First, researchers should consider whether control units and/or treated units experience effects from the treatment status of other units.
-For example, in the context of library construction, treated units likely do not experience spillovers while close control units do.
-In the context of factory openings, both control and treated units likely experience spillovers.
-
-Second, a researcher must decide how far the spillovers extend and whether the effect decays over distance.
-This should again be guided by the economic context of the research question.
-For example, things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
-There are two commonly used techniques to model treatment effect decay.\footnote{If the spillovers is due to crossing borders into the treated area, then a reasonable decision about whether the effect decays is the frequency in which people use the good.
-For example, libraries whose benefit is only experienced from frequent usage would suggest that the effect decays over distance.
-On the other hand, abortion clinics opening are used infrequently and therefore the effect likely doesn't decay over distance within a certain cutoff.} First, as seen above is to use an exponential decay function with regards to distance.
-The parameter $\alpha$ in equation (\ref{eq:h_decay}) determines the rate of decline over distance.
-
-The other option is to use a set of `concentric rings' which are a semi-parametric model of spillovers.
-If the spillovers decay over distance, then the coefficients on the indicators should decrease as they move out.
-On the other hand, the concentric rings can allow for spillovers to be constant across distance.
-The exponential decay is less robust since it imposes a strictly monotonic function.
-In the simulations below, I show that rings are very flexible across forms of spillovers.
-An example of using rings is in the empirical application in Section \ref{sec:tva}.
-
-Last, it is important for estimation to determine if the spillovers are additive or non-additive in nature.
-If the number of nearby treated units matter, then the exposure mapping should sum over nearby treated units in some way.
-For example, in the context of library construction, the number of neighbors with libraries does not change the size of the spillover for it is access to \textit{any} library that matters.
-In the context of factory openings, though, agglomeration economies imply that the spillovers are additive in nature.
-Below, I show that in order to accurately estimate spillovers requires correctly using a additive or non-additive version of the concentric rings.
-
-\subsubsection{Monte Carlo Simulations}
-
-To highlight the importance of these considerations, I turn to simulations where we include potentially incorrectly specified exposure mappings and see their performance in a set of different data generating processes.
-In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h(\vec{D}, i)$.
+This could vary by location if the size of benefits created by the treatment depend on the number of treated units nearby.
+
+However, the estimates are not trivial to interpret as the ``typical'' magnitude of spillover effects.
+This is because $\hat{\tau}_{\text{spill,control}}$ and $\hat{\tau}_{\text{spill,treat}}$ average spillover effects across all units with $S_i = 1$ which could contain units that experience no spillover effects.
+For example, if only units really close to treatment receive spillover effects and $S_i$ contains a lot of units that experience no spillover effects, then $\hat{\tau}_{\text{spill, control}}$ could be estimated near zero even though there are spillover effects.
+
+An improvement on this is to use a set of concentric ring indicators instead of a single large ring indicator to more flexibly estimate the spillover effects (e.g 0-20 miles, 20-40 miles and 40-60 miles from the nearest treated unit).
+Since the set of rings is collinear with a single large ring, the direct effect estimate retains its unbiased properties, while spillover effects can potentially be estimated more accurately.
+A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
+
+% Figure: Example Rings --------------------------------------------------------
+\begin{figure}[tb!]
+    \caption{Rings Improve Estimation of Spillover Effects}
+    \label{fig:example_rings}
+
+    \begin{subfigure}{\textwidth}
+        \caption{Single Ring}
+        \begin{center}
+            \resizebox{0.8\textwidth}{!}{
+                \includegraphics{../../figures/figure-within_example.pdf}
+            }
+        \end{center}
+
+    \end{subfigure}
+    \begin{subfigure}{\textwidth}
+        \caption{Multiple Rings}
+        \begin{center}
+            \resizebox{0.8\textwidth}{!}{
+                \includegraphics{../../figures/figure-rings_example.pdf}
+            } 
+        \end{center}
+    \end{subfigure}
+
+    \noindent{\footnotesize \textit{Notes:} Panel (a) shows the estimate of a single large ring indicator following equation (\ref{eq:twfe_with_ind}).
+Panel (b) shows a set of concentric ring indicators following equation (\ref{eq:twfe_with_ind}) where $S_{i}$ is replaced with a set of ring indicators.}
+\end{figure}
+
+The figure displays observations of $\bar{Y}_{i,Post} - \bar{Y}_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the x-axis and treated units are placed at a zero distance for visualization purposes.
+The example has a counterfactual trend of 2 so any difference from 2 is due to either treatment/spillover effects and the error term.
+Panel (a) uses a single indicator for being between 0 and 60 miles from treatment and the difference between the bar and the estimated counterfactual trend is the estimated spillover effect which in this case is about 0.6.
+This number masks that units within the first 15 miles have a treatment effect of 1 or larger and units between 40 and 60 miles have 0 spillover effects.
+
+Figure (b) on the other hand uses 4 indicators for every 15 mile interval (0-15, 15-30, 30-45, and 45-60 miles).
+This improves on the estimate of a single ring in two ways.
+The multiple rings is able to better capture the way spillover effects evolve over distance.
+Further, the ring that is included past the true maximum distance where spillover effects occur has a point estimate near zero.
+The rings method acts a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to their being units outside of the rings).
+However, precision of estimates would decrease as the number of rings increase and therefore there is a bias-variance trade-off in the number and width of rings.
+\citet{Clarke_2017} proposes a cross-validation technique for optimally choosing the number of rings and their techniques that uses the out-of-sample mean square prediction error as a way to estimate the bias-variance tradeoff.
+Interested readers can see the paper for technical and implementation details.
+
+One disadvantage of using a set of indicator for \textit{the nearest} treated unit is that some spillover effects are additive in the number of nearby treated units.
+In this case, summarizing exposure by the distance to the closest treated unit fails to capture important information on the location of other treated units and the coefficients on the ring indicators might be interpreted incorrectly.
+One potential solution is to count the number of treated units within each ring instead of creating indicators for nearest treated unit.
+This additive version of rings however no longer removes all bias from the direct effect of treatment unless the exposure mapping is correctly specified.
+Therefore, if spillover effects are expected to be additive in nature, seperate estimation of the direct effect and spillover effects would be the preferred method.
+
+% ------------------------------------------------------------------------------
+\subsection{Monte Carlo Simulations}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\subsubsection{Bias Under Misspecification of Spillovers}
+% ------------------------------------------------------------------------------
+
+To illustrate the above discussion, I turn to a set of Monte Carlo simulations.
+The first exercise is to consider a set of different data generating processes and see how well estimates of the direct effect perform when controlling for spillovers using potentially misspecified exposure mappings.
+In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{i,t}$ for many different exposure mappings $h(\vec{D}, i)$.
 I generate data for unit $i$ is a US county at time $t \in \{1, \dots, 20\}$ using the following data-generating process:
 \begin{equation}\label{eq:dgp_general}
-    y_{it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it},
+    y_{i,t} = \mu_t + \mu_i + 2 D_{i,t} + \beta_{\text{spill, control}} (1-D_{i,t}) h(\vec{D}, i) + \varepsilon_{i,t},
 \end{equation}
-where $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is $\varepsilon \sim N(0, 2^2)$.
-
+where $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is IID and distributed as $\varepsilon_{i,t} \sim N(0, 2^2)$.
+
+For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are the same.
 In order to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
-The goal of this exercise is to see which specifications perform well under broad classes of spillovers.
-For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are the same.
 
@@
 These consist of a set of indicators for falling within distance bins from the nearest treated unit (e.g.
-indicators for being between 0-20, 20-40, and 40-60 miles to closest treated unit).
-This approach is worth discussing in more detail because it is the most consistent solution.
-These rings are able to trace out all of the non-additive spillovers so long as the distance bins are numerous enough.
-For example, the rings indicators add up to all the `Within xmi.' specifications if there are enough rings.
-The rings can also trace out the decaying spillovers with the coefficients on each indicator decreasing in an exponential way.
-Rings that extend past the maximum spillover distance will be estimated near zero, so they will still estimate the spillovers well.
-However, too many rings could lower precision of the estimates as estimation of the spillover effects relies on control units outside of the rings.
-In summary, the rings should extend far enough to ensure that all units affected by spillovers are contanied but not too far as to leave few units to estimate the counterfactual trend.
-
+indicators for being between 0-20, 20-40, 40-60, and 60-80 miles to closest treated unit).
 The last specification is an additive version of `Rings' which is the number of treated units within each distance bin.
@@
 
+% Bias Table
 \begin{table}[!tb]
@@
     \label{tab:misspecification}
+    \renewcommand\arraystretch{1}
 
@@
         \begin{threeparttable}
-            \begin{tabular}{@{} l rrrrrr @{}}
+            \begin{tabular}{@{} l *{6}{d{2.4}} @{}}
                 % Head
@@
 
-                & \multicolumn{1}{c}{\textbf{Within 40mi}} & \multicolumn{1}{c}{\textbf{Within 80mi}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay}} & \multicolumn{1}{c}{\textbf{Decay}} \\
-                Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
+                & \mcl{\textbf{Within 40mi}} & \mcl{\textbf{Within 80mi}} & \mcl{\textbf{Within 40mi.}} & \mcl{\textbf{Within 80mi.}} & \mcl{\textbf{Decay}} & \mcl{\textbf{Decay}} \\
+                Specification & & & \mcl{\textbf{(Additive)}} & \mcl{\textbf{(Additive)}} & & \mcl{\textbf{(Additive)}} \\
 
@@
 
-                \bottomrule
+                \\ \bottomrule
             \end{tabular}
@@
             \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each cell corresponds to the mean bias from 1000 simulations of the data generating process specified by the column header and under the specification given by equation (\ref{eq:dgp_general}) by the row label.
+                \item \textit{Notes.} Each cell corresponds to the results from 1000 simulations of the data generating process specified by the column header and estimated by equation (\ref{eq:dgp_general}) with $\tilde{h}(\vec{D},i)$ given by the row label.
+The non-bracketed number represents the mean bias from the simulations and the bracketed number represents the mean square error given by $\sum_{i = 1}^n \frac{(\hat{\tau}_i - \tau_0)^2}{n}$
             \end{tablenotes}
@@
 For each entry in the table, the column label corresponds to the true exposure mapping used in the data-generating process and the row label corresponds to the exposure mapping, $\tilde{h}(\vec{D}, i)$, used in estimation.
-The corresponding cell gives the mean bias from estimating equation (\ref{eq:dgp_general}) with the $\tilde{h}(\vec{D}, i)$.
-The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed effect estimate and in particular, correctly specifying the data-generating process removes almost all the bias.
-
-The second result is that both the `Rings' and the `Within' specification perform best among all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers.
+The corresponding cell gives the mean bias from estimating equation (\ref{eq:dgp_general}) with the $\tilde{h}(\vec{D}, i)$ given by the row.
+The bracketed number below the mean bias is the mean-squared error of the estimate which is given by $\sum_{i=1}^n \frac{(\hat{\tau}_{i,\text{direct}} - \tau_0)^2}{n}$.
+The mean squared error combines the square of the bias term, the variance of the estimator, and the variance of the error term which does not depend on the equation specification.
+This measure gives a good sense of the trade-off with whether decreasing bias comes at the cost of increasing the variance of the estimator.
+
+The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed effect estimate and lower the mean-squared error.
+In particular, correctly specifying the data-generating process removes almost all the bias in the direct effect estimate and greatly lowers the mean-squared error.
+
+The second result is that both the non-additive `Rings' and the `Within' specification perform best among all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers.
 This is due to the fact that indicator variables will correctly identify the average spillovers onto control units if they cover all the effected control units (see Proposition \ref{thm:remove_bias}).
-If researchers are primarily interested in identifying the direct effect, then either `Rings' or `Within' specifications with a large cutoff distance are preferred as they remove almost all bias in all settings.
+They also do so without increasing the variance of the estimator relative to the true specification, as shown by comparing the mean-squared errors.
+However, if the indicator is not wide enough as is the case with Within 40mi.
+for the 80mi.
+data-generating process, bias remains in the estimates.
+Therefore, if researchers are primarily interested in identifying the direct effect, then either `Rings' or `Within' specifications with a large cutoff distance are preferred as they remove almost all bias in all settings.
+
+% ------------------------------------------------------------------------------
+\subsubsection{Spillover Effect Estimation}
+% ------------------------------------------------------------------------------
 
@@
 
+% MSPE Table
 \begin{table}[!tb]
@@
         \begin{threeparttable}
-            \begin{tabular}{@{} l rrrrrr @{}}
+            \begin{tabular}{@{} l *{6}{d{2.2}} @{}}
                 % Head
@@
             \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each cell corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects from 1000 simulations of the data generating process specified by the column header and under the specification given by equation (\ref{eq:dgp_general}) by the row label.
+                \item \textit{Notes.} Each cell corresponds to the results from 1000 simulations of the data generating process specified by the column header and estimated by equation (\ref{eq:dgp_general}) with $\tilde{h}(\vec{D},i)$ given by the row label.
+The number corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects, given by
+                \[ 
+                    1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}.
+                \]
             \end{tablenotes}
@@
 % ------------------------------------------------------------------------------
+\subsection{Guide for Researchers}
+\label{sec:parameterize}
+% ------------------------------------------------------------------------------
+
+The above discussion yields to practical recommendations based on three questions, the answers to which will ultimately depend on the economic context being studied.
+
+\begin{enumerate}
+    \item Researchers should consider whether control units and/or treated units experience effects from the treatment status of other units.
+For example, in the context of library construction, treated units likely do not experience spillovers while close control units do.
+In the context of factory openings which affects nearby labor markets regardless of treatment status, both control and treated units likely experience spillovers.
+
+    \item Researchers must decide how far the spillovers extend and whether the effect decays over distance.
+This should again be guided by the economic context of the research question.
+For example, things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
+
+    Importantly, Proposition \ref{thm:remove_bias} shows that the researcher does not need to specify the exact functional form of spillovers in order to have unbiased estimates of the treatment effect provided that spillovers are `local' as in Assumption \ref{assumption:local}.
+If only the direct effect of treatment is of interest, than a single ring indicator that contains units within the maximum distance will suffice.
+On the other hand, if spillover effects are of interest themselves, then a set of concentric rings is preferred for the reasons given above.
+
+    \item Last, it is important for estimation to determine if the spillovers are additive or non-additive in nature.
+If the number of nearby treated units matter, then the exposure mapping should sum over nearby treated units in some way.
+For example, in the context of library construction, the number of neighbors with libraries does not change the size of the spillover for it is access to \textit{any} library that matters.
+In the context of factory openings, though, agglomeration economies imply that the spillovers are additive in nature.
+As illustrated in the Monte Carlo simulations, in order to accurately estimate spillovers requires correctly using a additive or non-additive version of the concentric rings.
+\end{enumerate}
+
+% ------------------------------------------------------------------------------
 \section{Application in Place-Based Policy Analysis}
@@
 By the end of WWII, the TVA became the largest single power supplier in the country and significantly lowered the cost of wholesale energy for factories.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.
-The effects on wholseale electricity are studied in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
-
-\citet{Kline_Moretti_2014} analysze a range of outcome variables, but I extend their work on (the log of) agricultural and manufacturing employment.
+The effects on wholseale electricity are discussed in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
+\citet{Kline_Moretti_2014} analysze a range of outcome variables, but for succinctness I use only (the log of) agricultural and manufacturing employment.
 Since the TVA primarily improved manufacturing industries through large-scale electrification, the authors predict that employment will grow in manufacturing and shrink in agricultural as workers switch to higher-paying manufacturing jobs.
@@
 The weights are the propensity scores from a linear probability model where the outcome variable is being in the TVA.
-The weights can be seen in Figure III of their text, but generally counties close to the TVA are upweighted relative to uniform weights.
-However, in Table \ref{tab:tva} below, I will show their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.}
+The weights can be seen in Figure III of their text, but generally counties close to the TVA are slightly upweighted relative to uniform weights.
+Their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.} To improve the likelihood of the paralell trends assumption, they run a logistic regression to predict being in the TVA based on their set of control variables $X_{c,1940}$ and keep only observations in the top 75\% of predicted probability.
+The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
 
@@
 For manufacturing, the sign is ambiguous.
-There could be positive spillovers if electrification brought cheap power and agglomeration economies to the neighboring areas.\footnote{\citet{Duranton_Puga_2003} give theoretical motivations for different sources of agglomeration.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.\footnote{\citet{Cuberes_Desmet_Rappaport_2021} refer to the positive spillover effects as `urban access' and the negative spillover effecte as `urban shadows'.} My methodology will allow me to empirically test these predictions in the data and remove their bias from the treatment effect estimates.
+There could be positive spillovers if electrification brought cheap power and agglomeration economies to the neighboring areas.\footnote{\citet{Duranton_Puga_2003} give theoretical motivations for different sources of agglomeration.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.\footnote{\citet{Cuberes_Desmet_Rappaport_2021} refer to the positive spillover effects as `urban access' and the negative spillover effecte as `urban shadows' and find descriptive evidence of these effects changing importance over time.} My methodology will allow me to empirically test these predictions in the data and remove their bias from the treatment effect estimates.
 
@@
 The estimation strategy I present keeps the observations near the TVA while controlling for spillover effects in a more rigorous manner.
-
-To improve the likelihood of the paralell trends assumption, the run a logistic regression to predict being in the TVA based on their set of control variables $X_{c, pre}$ and keep only observations in the top 75\% of predicted probability.
-The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
 
@@
 
-I extend their analysis to include spatial spillovers in the difference-in-differences specification.
+I extend their analysis to control for spatial spillovers in the difference-in-differences specification.
 To parametrize the exposure mapping, I include a set of indicator variables for when a county is within a certain distance interval from the Authority.
@@
 The coefficients $\delta_d$ estimate the average spillover effect onto control units at different distances from the Authority.
-From the above simulations, $\hat{\tau}$ will be an unbiased estimate for what the authors call the `local' effect so long as spillovers do not occur past 200 miles from the TVA.
+From proposition \ref{thm:remove_bias}, $\hat{\tau}$ will be an unbiased estimate for the `local' effect so long as spillovers do not occur past 200 miles from the TVA.
 
@@
 
+% TVA Table
 \begin{table}[!tb]
@@
     \label{tab:tva}
-    \renewcommand{\arraystretch}{1}
+    \renewcommand{\arraystretch}{1.1}
 
@@
         \begin{threeparttable}
-            \begin{tabular}{@{} lc@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
+            \begin{tabular}{@{} l c@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
                 % Head
@@
 
-                \toprule
+                \\ \toprule
                 \multicolumn{7}{l}{\textbf{Panel B:} 1940-1960} \\
@@
 Each cell is the point estimate and the standard error for the variable described in the column title.
-All standard errors are clustered at the state-level.
+All standard errors are Conley standard errors with a correlation cutoff of 200 miles following \citet{Conley_1999}.
 The column labeled `Diff-in-Diff' estimates (\ref{eq:tva}) by OLS and is similar to the estimate reported in \citet{Kline_Moretti_2014}.
@@
 The effect of urban shadows can potentially be smaller in the short-run if operating firms are unlikely to relocate.
-Long-run effects can be larger as new firms change their location decision.
+Long-run effects can be larger as entrant firms change their location decision and operating firms are slowly replaced which is what the long-run spillover effect estimates suggest.
 
@@
 Analysis of place-based policies that do not account for the fact that treatment effects can spillover beyond the borders of treated areas can potentially be biased.
-More, the effects of place-based policies change over time as frictions can create delays in reoptimizing behavior.
+More, the spillover effects caused by place-based policies change over time as frictions can create delays in reoptimizing behavior.
 
@@
 
-More generally, my framework provides important insights in the analysis of place-based policies.
+More generally, my framework provides important insights into identification strategies when analysizing the effects of place-based policies.
 There are two ways I contribute.
 First, \citet{Baum-Snow_Ferreira_2015} recognize the problem of spatial spillovers causing problems in identification and point to aggregation of units as a way to alleviate to the problem (e.g.
-aggregation to metropolitan areas).
+aggregating census tracts to metropolitan areas).
 However, this approach collapses the three seperate effects which might each be of interest into a singular aggregate effect.
 I have shown that all three effects of place-based policies can be estimated under very general assumptions about the spillovers.
+Therefore, the methods propose simple ways to estimate treatment effects with non-aggregated data.
 
 Second, my framework provides insight for different identification strategies often used in the literature.
+Since place-based policies are targeted to specific distressed areas, comparison units are often hard to find.
+Researchers have developed many identification strategies to find comparison units that are similar in terms of unobservables.
+First, researchers use border discontinuities to compare treated units to units just on the otehr side of the border.
+The rationale for this is that unobservables that could be correlated with treatment would evolve continuously across the border and so neighobring units would serve as valid comparisons.
+A different identification strategy compares approved and close but ultimately rejected applicants (e.g.
+\citet{}).
+Since both the treated and comparison groups likely are simliar due to the comparison group was close to being treated, unobservables should be balanced.
+A key difference in these identification strategies is the distance comparison units are from the treated area and therefore the former is more prone to bias due to spillovers than the latter.
+
 For example, consider the analysis of the effects of federal Empowerment Zones.
@@
 If census tracts just outside the Empowerment Zones also benefit from the policy, then the estimates of \citet{Neumark_Kolko_2010} are attenuated towards zero.
-These two identification strategies of using rejected applicants or using bordering units as the control group are very common in the urban literature \citep{Baum-Snow_Ferreira_2015}.
+These two identification strategies of using rejected applicants or using bordering units as the control group are very common in the urban literature more generally \citep{Baum-Snow_Ferreira_2015}.
 My paper suggests that the former is the preferred strategy if spillovers occur onto nearby control units.
-
-In general, identification strategies that rely on geographically close control units as having similar unobservables should be used cautiously.
-If treatment effects spillover the Empowerment Zone borders, then narrowing the sample to controls very close to the border can leave treatment effect estimates biased.
-This insight applies more generally to identification strategies that compare observations just on either side of a border.
+Identification strategies that rely on geographically close control units as having similar unobservables should be used cautiously.
+If treatment effects spillover treatment border, then estimated treatment effects can be biased.
 
@@
 The intuition from how spillovers cause biases in estimates of the direct effect of treatment extend into the setting where there is staggered adoption in treatment.
-When treatment turns on for different units at different times, two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_D’Haultfoeuille_2019}.
-I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be identically weighted of the bias terms from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
-However, since the weights can be negative, the sign of the spillover effects do not determine the sign of the weighted average of the spillover effects.
+When treatment turns on for different units at different times, two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
+I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias terms from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
+However, since weights on some of the $2 \times 2$ estimates can be negative, the sign of the spillover effects do not determine the sign of the weighted average of the spillover effects.
 This makes the bias from spillovers much more difficult to sign.
 
-Now, I will propose an estimation strategy that follows \citet{Callaway_Sant’Anna_2020} while incorporating spillovers directly into estimation.
+In order to estimate treatment effects in the presence of spatial spillovers and staggered treatment timing, I will propose an estimation strategy that follows \citet{Callaway_SantAnna_2020} while incorporating spillovers directly into estimation.
 However, I do not cover all the technical assumptions and point the reader to the main text for these details.
@@
 Each cohort, $g$, will serve as the treated group for a set of $2\times 2$ difference-in-differences.
-For each period $t$ they define the `group-time average treatment effect', $ATT(g,t) = \mathbb{E}\left[ Y_t(g) - Y_t(0) \ \vert \ G_g = 1 \right]$, where $G_g$ is an indicator for starting treatment in year $g$.
+For each period $t$ they define the `group-time average treatment effect', $ATT(g,t) = \expec{Y_t(g) - Y_t(0) \ \vert \ G_g = 1 }$, where $G_g$ is an indicator for starting treatment in year $g$.
 The potential outcome is indexed by $g$ to allow for treatment effects to differ depending on the initial treatment year.
@@
 Therefore in the context of spillovers, our equivalent term is the `group-time average direct effect' which will be defined as $$ 
-    ATT_{\text{direct}}(g,t) = \mathbb{E}\left[ Y_t(g, 0) - Y_t(0, 0) \ \vert \ G_g = 1 \right],
+    ATT_{\text{direct}}(g,t) = \expec{Y_t(g, 0) - Y_t(0, 0) \ \vert \ G_g = 1 },
 $$ where the second term in potential outcomes represents an exposure mapping of $h(\vec{D}, i) = 0$.
@@
     $$
-        \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 \right] = \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ C = 1 \right] 
+        \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 } = \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ C = 1 } 
     $$ 
@@
     $$ 
-        \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 \right] = \mathbb{E}\left[ Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ D_s = 0, G_g = 0 \right]
+        \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 } = \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ D_s = 0, G_g = 0 }
     $$ 
@@
 
-Then, as detailed in C\&S, the $ATT(g,t)$ can be aggregated using different weights depending on the pararmeter of interest (see Table 1 of \citet{Callaway_Sant’Anna_2020}).
+Then, as detailed in C\&S, the $ATT(g,t)$ can be aggregated using different weights depending on the pararmeter of interest (see Table 1 of \citet{Callaway_SantAnna_2020}).
 These aggregations take the form of
@@
 Different weights produce different estimates for different average effects of interest, e.g.
-event study estimates, or group-level average treatment effects (across time).
-Estimation and different aggregation of the direct effects can be done using the `did' package produced by C\&S where the measure of exposure mapping are included as covariates.
+event study estimates, group-level average treatment effects (across time), or an aggergate treatment effect.
+Estimation and different aggregation of the direct effects can be done using the `did' package produced by C\&S where the the `Within' indicator is included as a covariate.
 It is important to note that exposure can change over time as new units are treated, so researchers should make sure to use the correct values for exposure mapping for each year $t$.
@@
 % ------------------------------------------------------------------------------
-\subsection{Estimating Spillover Effects}
-% ------------------------------------------------------------------------------
-
-Estimation of the spillover effects is potentially much more difficult as estimation of continuous variables in the presence of staggered treatment timing is still a work in progress and past the scope of this article.
+\subsection{Estimation of Spillover Effects}
+% ------------------------------------------------------------------------------
+
+Estimation of the spillover effects is potentially much more difficult as estimation of continuous variables or multiple treatment variables in the presence of staggered treatment timing is still a work in progress and past the scope of this article.
 However, for a `Within' indicator, estimation can be done in much the same way as the direct effect but with more caution when constructing the samples for each $2 \times 2$ estimate.
-The `Within' indicator can be thought of as the treatment indicator and the sample would consist of only the control units.
+The `Within' indicator can be thought of as the treatment indicator and the sample would consist of only the never-treated units.
 The advantage of the `Within' indicator is that it will remove all bias from the direct effects estimates if the indicator extends far enough and will give an estimate of the average spillover effect.
@@
         \textit{Notes:} This figure plots event study estimates for the treatment effect and the spillover effect on control units within 25 miles of treatment at different periods relative to establishment year.
-The estimates are generated using the `did' package produced from the paper \citet{Callaway_Sant’Anna_2020}.
+The estimates are generated using the `did' package produced from the paper \citet{Callaway_SantAnna_2020}.
     }
@@
 This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
-On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that these effects are not due to emergency but rather primary care services.
-In this case, it is less likely low-income individuals would travel very far to receive care and hence the spillover effects would be near zero.
-My methodology can provide an answer to this question.
+On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergency but rather primary care services.
+In this case, it is less likely low-income individuals would travel very far to receive primary care and hence the spillover effects is potentially near zero.
+My methodology can provide an answer to the question of how far do individuals travel for low/no -cost primary care.
 
 As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
-Then, I follow \citet{Callaway_Sant’Anna_2020} in estimating event-study coefficients.
+Then, I follow \citet{Callaway_SantAnna_2020} in estimating event-study coefficients.
 The results are presented in Figure \ref{fig:chc_es_spill}.
@@
 
-Finally, I show how researchers can include spillovers in settings with variation in treatment timing following \citet{Callaway_Sant’Anna_2020}.
+Finally, I show how researchers can include spillovers in settings with variation in treatment timing following \citet{Callaway_SantAnna_2020}.
 I then use this method to show how considering spillovers in event-study framework provide additional insights for a researcher.
@@
 % ------------------------------------------------------------------------------
-\newpage \printbibliography%
+\newpage \bibliography{references.bib}
 % ------------------------------------------------------------------------------
@@
 \begin{align*}
-    \mathbb{E}\left[ \hat{\tau} \right] &= \underbrace{\mathbb{E}\left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\
-    &= 
-    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
-    &= 
-    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E}\left[ Y_{i1}(0, h(\vec{D}, i)) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\
-    &= 
-    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 \right] \\ 
-    &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\ 
-    &= 
-    \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1 \right] \\
-    &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right] \\  
-    &= \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= \mathbb{E}\left[ Y_{i1}(1, h(\vec{D}, i)) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0 \right]\\
-    &= 
-    \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right] + \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1 \right] \\
-    &\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0 \right] \\
-    &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
+    \expec{\hat{\tau} } &= \underbrace{\expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \mid D_i = 1 } - \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \mid D_i = 0 }}_{\text{Difference-in-Differences}} \\
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 0 } \\
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } \\
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) + \bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 0 } \\
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } - \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 0} \\ 
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0} \\ 
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } \\
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 1} \\
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0} \\  
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) + \bar{Y}_{i,Pre}(0, \vec{0})\mid D_i = 1 } \\
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0}\\
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 1 } - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0}\\
+    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) + \bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 1 } \\
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0} \\
+    &= \expec{\bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 1} + \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Post}(1, \vec{0}) \mid D_i = 1} \\
+    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 0} \\
+    &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \\
 \end{align*}
@@
 % ------------------------------------------------------------------------------
-\section{Details on Monte Carlo Simulations}
+\section{Details on Dropping Control Unit Approach}
 \label{sec:monte_carlo}
@@
     \label{eq:dgp1} 
-    y_{it} = \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill, control}} (1-D_{it}) \text{Near}_{it} + \varepsilon_{it}   
+    y_{i,t} = \mu_t + \mu_i + \beta_{\text{direct}} D_{i,t} + \beta_{\text{spill, control}} (1-D_{i,t}) \text{Near}_{i,t} + \varepsilon_{i,t}   
 \end{equation}
@@
     \label{eq:dgp2} 
-    y_{it} = \mu_t + \mu_i + \beta_{\text{direct}} D_{it} + \beta_{\text{spill, control}} (1-D_{it}) \text{Near}_{it} + \beta_{\text{spill, treat}} D_{it} \text{Near}_{it} + \varepsilon_{it}   
+    y_{i,t} = \mu_t + \mu_i + \beta_{\text{direct}} D_{i,t} + \beta_{\text{spill, control}} (1-D_{i,t}) \text{Near}_{i,t} + \beta_{\text{spill, treat}} D_{i,t} \text{Near}_{i,t} + \varepsilon_{i,t}   
 \end{equation}
@@
 
-% For the following simulation, I will add in spillovers onto also treated units with $\beta_{\text{spill, treat}} = -0.5$. The DGP is as follows 
-% \begin{equation}\label{eq:dgp2} 
-%     y_{it} = \mu_t + \mu_i + 2 D_{it} + (1-D_{it}) \text{Near}_{it} - 0.5 D_{it} \text{Near}_{it} + \varepsilon_{it}   
-% \end{equation} 
-% The proportion of treated units affected by the spillover depends on the spatial autocorrelation of the treatment assignment.
-In empirical applications, it is often the case that treatment assignment is concentrated in specific areas which yields higher proportion of treated units receiving spillover effects.
-
-% \begin{figure}[tbh!]
-%     \caption{Example of Kriging Field}
-%     \label{fig:kriging}
-%     \begin{center}
-%         \resizebox{0.8\textwidth}{!}{
-%             \includegraphics{../../figures/figure-krig.png}
-%         } 
-%     \end{center}
-
-%     {\footnotesize
-%         \textit{Notes:} This figure plots an example of a kriging simulation using the `gstat' package in R using an exponential variogram.
-The outlined counties are in the top ten percent of values for this simulation.
-%     }
-% \end{figure}
-
-% \begin{figure}[tbh!]
-%     \caption{Bias of $\hat{\tau}$ at Different Levels of Spatial Autocorrelation}
-%     \label{fig:bias_spatial_autocorr}
-%     {\centering
-%         \resizebox{\textwidth}{!}{
-%             \includegraphics{../../figures/figure-bias_fix_spatial_autocorr.png}
-%         } 
-%     }
-
-%     {\footnotesize
-%         \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text and equation \ref{eq:dgp2}.
-Treatment probability is assigned according to the method described by the text and (\ref{eq:cond_prob}).
-Each point corresponds to the average bias for the given Zone Plus and the band is the 95 percent empirical confidence interval over 1000 simulations.
-The line with diamond markers estimates with all control units.
-The line with circle markers removes control units that share a border with a treated county.
-%     }
-% \end{figure}
-
-% In order to model spatial autocorrelation of treatment, I turn to a method from geosciences called `kriging'.
-Kriging generates a Gaussian field for a large grid of points across the entire United States where the spatial autocorrelation of the points is described by a set of parameters.
-One such field is depicted in Figure \ref{fig:kriging}.
-For a given field, I find the counties in the top ten percent of values and give these counties a value of $\text{Zone}_i = 1$.
-Then I assign treatment with a probability that differs based on $\text{Zone}_i$.
-To avoid changes in bias due to a difference in the number of treated units, the unconditional probability is equal to 5 percent in all simulations.
-To increase the spatial autocorrelation of treatment, I increase the probability of treatment for units with $\text{Zone}_i = 1$ and hence lower the probability for units with $\text{Zone}_i = 0$.
-\footnote{
-%     To change the spatial autocorrelation of treatment, I use a variable `Zone Plus' to adjust the relative probability of receiving treatment: 
-%     \begin{equation}
-%         \label{eq:cond_prob}
-%         P(D_i \ \vert \ \text{Zone}_i) = (.05 + \text{Zone Plus} * \text{Zone}_i) \times \underbrace{\frac{.05}{.05 * .9 + (.05 + \text{Zone Plus}) * .1}}_{\text{Normalize } P(D_i) = 0.05}
-%     \end{equation}
-%     The second term normalizes probabilities so the unconditional probability stays at five percent.
-In our simulations, Zone Plus ranges from 0 which is the case where $P(D_i \vert \text{Zone}_i) = P(D_i) = 0.05$ to 2 which has $P(D_i \ \vert \ \text{Zone}_i) = 0.01 + 0.41 * \text{Zone}_i$.
-% }
-
-% The results for the bias of $\hat{\tau}$ are in Figure \ref{fig:bias_spatial_autocorr}.
-The line with diamond markers is run on the full sample.
-As the level of spatial autocorrelation increases, the bias surprisingly decreases.
-The reason for this is that as treatment becomes more concentrated in the `Zones', the number of control units receiving spillovers decreases while the number of treated units receiving spillovers increases.
-In this particular data-generating process, the effect of fewer control units on the bias is larger than the bias from more treated units.
-
-% The line with circle markers in Figure \ref{fig:bias_spatial_autocorr} repeats the exercise of dropping control units that share a border with treated units.
-In the case where spillovers occur on treated units, all bias is not removed when dropping control units.
-That is because we only remove $\tau_{\text{spill,control}}$ but $\tau_{\text{spill,treated}}$ remains.
-To remove the second source of bias, it is necessary to acount directly for spillovers in the estimation strategy.
-
 \end{document}

### 2021-05-03 latex/paper/Spillover.tex
5-3 Draft

@@
 
-\usepackage{dcolumn}
-\newcolumntype{d}[1]{D..{#1}}
-\newcommand{\mcc}[1]{\multicolumn{1}{c@{}}{#1}}
-\newcommand{\mcl}[1]{\multicolumn{1}{l@{}}{#1}}
-\newcommand{\mcr}[1]{\multicolumn{1}{r@{}}{#1}}
-
 \begin{document}
@@
     \begin{abstract}
-        Empirical work often uses treatment variables defined by geographic boundaries.
-When researchers ignore the common problem that the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect.
-In this paper, I decompose this bias in two parts (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-I propose estimation strategies that can remove both sources of bias as well as semi-parametrically estimate the spillover effects themselves.
-I extend this estimation strategy in an event-study framework following \citet{Callaway_SantAnna_2020} to allow for staggered treatment adoption.
-To highlight the importance of spillover effects, I revisit the analysis of three place-based policies and show the importance of directly controlling for general equilibrium spillovers caused by place-based policies.: the Tennessee Valley Authority \citep{Kline_Moretti_2014}, Federal Empowerment Zones \citep{Neumark_Young_2019}, and Community Health Centers \citep{Bailey_Goodman_Bacon_2015}.
+        Empirical work often uses treatment assigned following geographic boundaries.
+When the effects of treatment cross over borders, classical difference-in-differences estimation produces biased estimates for the average treatment effect.
+In this paper, I introduce a potential outcomes framework to model spillover effects and decompose the estimate's bias in two parts: (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
+I propose estimation strategies that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves.
+I extend \citet{Callaway_SantAnna_2020} to allow for event-study estimates that control for spillovers.
+To highlight the importance of spillover effects, I revisit analyses of three place-based interventions.
     \end{abstract}
@@
 
-Empirical work often considers settings where treatment is assigned to groups of units by geographic boundaries, but the effect of these treatments spillover onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
-geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} In this setting, there are two types of spillover effects.
+Empirical work often considers settings where policy is targeted to groups of units by geographic boundaries, but the effect of these treatments spillover onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} Place-based policies, programs that are targeted to specific locations, are known to have general-equilibrium effects that extend far past the area intended to receive treatment \citep{Kline_Moretti_2014b}.
+Spillover effects can occur on to both control and treated units.
 First, there can be spillover effects onto control units.
@@
 I extend this work by focusing on difference-in-differences estimation in non-experimental settings.
-\citet{Sävje_Aronow_Hudgens_2019} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
+\citet{Savje_Aronow_Hudgens_2019} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
 My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
@@
 
-My definition of the direct effect of treatment differs from \citet{Sävje_Aronow_Hudgens_2019} where they define the average treatment effect as \[ 
+My definition of the direct effect of treatment differs from \citet{Savje_Aronow_Hudgens_2019} where they define the average treatment effect as \[ 
     \expec{Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(0, h(\vec{D}, i)) \ \vert \ D_i = 1},
@@
 \end{align*}
-The individual treatment effect \citet{Sävje_Aronow_Hudgens_2019} use is the direct effect of treatment plus the difference between spillover on treated units and spillover on control units.
+The individual treatment effect \citet{Savje_Aronow_Hudgens_2019} use is the direct effect of treatment plus the difference between spillover on treated units and spillover on control units.
 
@@
 That is, a county deciding whether to implement a policy will want to consider the treatment effect plus the difference in spillover effects at \textit{a particular} exposure intensity.
-The estimand proposed by \citet{Sävje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at specific exposure intensities while my preferred method of identifying the three effects seperately can.
-Estimates of the direct effect and spillover effect can be later combined to estimate the average treatment effect as defined by \citet{Sävje_Aronow_Hudgens_2019}.
+The estimand proposed by \citet{Savje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at specific exposure intensities while my preferred method of identifying the three effects seperately can.
+Estimates of the direct effect and spillover effect can be later combined to estimate the average treatment effect as defined by \citet{Savje_Aronow_Hudgens_2019}.
 
@@
 % ------------------------------------------------------------------------------
-\section{Estimation of Treatment Effects with Spillovers}
+\section{Estimating $2\times 2$ Difference-in-Differences with Spillovers}
 \label{sec:estimation}
@@
 
-Under mild conditions, it is possible to control directly in a regression for the two sources of spillover effects and to have unbiased estimates of the direct effect of treatment.
+Under mild conditions, it is possible to control directly in a regression for the two sources of spillover effects and unbiasedly estimate the direct effect of treatment.
 A pair of indicators that contains all control/treated units respectively will estimate the average spillover effect on control/treated units and remove these sources of bias.
@@
 
-The intuition behind this is that the indicator interacted with treatment status serve as unbiased estimates of the \textit{average} spillover effect onto treated and control units and therefore remove these terms from the direct effect estimate, $\hat{\tau}$.
-The proof uses standard Frisch-Waugh-Lovell style logic on a set of indicator variables and the fact that if $S_{i} = 0$ then $h(\vec{D}, i) = \vec{0}$.\footnote{The derivation follows closely the work of \citet{Clarke_2019}.} This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
+The intuition behind this is that the indicator interacted with treatment status serve as unbiased estimates of the \textit{average} spillover effect onto treated and control units and therefore remove these terms from the direct effect estimate, $\hat{\tau}$.\footnote{The proof uses standard Frisch-Waugh-Lovell style logic on a set of indicator variables and the fact that if $S_{i} = 0$ then $h(\vec{D}, i) = \vec{0}$.
+The derivation follows closely the work of \citet{Clarke_2019}.} This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
 An indicator for being `near' treatment ineracted with treatment status is enough to have an unbiased estimate for the treatment effect.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
@@
 For example, if only units really close to treatment receive spillover effects and $S_i$ contains a lot of units that experience no spillover effects, then $\hat{\tau}_{\text{spill, control}}$ could be estimated near zero even though there are spillover effects.
-
-An improvement on this is to use a set of concentric ring indicators instead of a single large ring indicator to more flexibly estimate the spillover effects (e.g 0-20 miles, 20-40 miles and 40-60 miles from the nearest treated unit).
-Since the set of rings is collinear with a single large ring, the direct effect estimate retains its unbiased properties, while spillover effects can potentially be estimated more accurately.
-A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
 
@@
 
+An improvement on this is to use a set of concentric ring indicators instead of a single large ring indicator to more flexibly estimate the spillover effects (e.g 0-20 miles, 20-40 miles and 40-60 miles from the nearest treated unit).
+Since the set of rings is collinear with a single large ring, the direct effect estimate retains its unbiased properties, while spillover effects can potentially be estimated more accurately.
+A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
 The figure displays observations of $\bar{Y}_{i,Post} - \bar{Y}_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the x-axis and treated units are placed at a zero distance for visualization purposes.
@@
 This improves on the estimate of a single ring in two ways.
-The multiple rings is able to better capture the way spillover effects evolve over distance.
-Further, the ring that is included past the true maximum distance where spillover effects occur has a point estimate near zero.
+Multiple rings are better able to capture the evolution of spillover effects over distance.
+Furthermore, the ring that is included past the true maximum distance where spillover effects occur has a point estimate near zero.
 The rings method acts a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to their being units outside of the rings).
@@
 Now, I turn to analyzing how the specifications perform at estimating the spillover effects themselves.
-For the next table, I will predict their spillover value for each control unit from the point estimates on $\tilde{h}(\vec{D}, i)$.
+For the next table, I predict the spillover effect for each control unit from the point estimates on $\tilde{h}(\vec{D}, i)$.
 Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (for comparison across data-generating processes), \[
@@
 % ------------------------------------------------------------------------------
-\subsection{Guide for Researchers}
+\subsection{Guide for Applied Researchers}
 \label{sec:parameterize}
@@
 % ------------------------------------------------------------------------------
-\section{Application in Place-Based Policy Analysis}
+\subsection{Application in Place-Based Policy Analysis}
 \label{sec:tva}
@@
 % ------------------------------------------------------------------------------
-\section{Event Study with Spillovers}
+\section{Estimating Event Study with Spillovers}
 \label{sec:event_study}
@@
 % ------------------------------------------------------------------------------
-\section{Application on Community Health Centers}\label{sec:chc}
+\subsection{Application on Community Health Centers}\label{sec:chc}
 % ------------------------------------------------------------------------------
@@
 
-I use the set of counties in the contiguous United States and the data generating process used is defined by the exposure mapping given in (\ref{eq:example_exposure}) with cutoff distance $\bar{d} = 40$ miles and the data generating process given in (\ref{eq:example_po}).
+I use the set of counties in the contiguous United States and the data generating process used is defined by the exposure mapping given in (\ref{eq:h_within}) with cutoff distance $\bar{d} = 40$ miles and the data generating process given in (\ref{eq:example_po}).
 A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.

### 2021-05-10 latex/paper/Spillover.tex
Add acknowledgements

@@
 
-\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers}
+\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, and participants of the CU Boulder Labor Economics Seminar for helpful comments.}}
 \author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}

### 2021-05-10 chc-analysis.R
Make png of figures

@@ -263,6 +263,8 @@ ggplot(es_pts_spillover_effect) +
 if(slides) ggsave("figures/figure-chc-es_original_slides.pdf", es_plot_original, width = 8, height = 8 * h_w_ratio, dpi = 300)
 if(!slides) ggsave("figures/figure-chc-es_original.pdf", es_plot_original, width = 8, height = 5, dpi = 300)
 
+if(slides) ggsave("figures/figure-chc-es_original_slides.png", es_plot_original, width = 8, height = 8 * h_w_ratio, dpi = 300)
+if(!slides) ggsave("figures/figure-chc-es_original.png", es_plot_original, width = 8, height = 5, dpi = 300)
 
 
 # treatment effect with controls
@@ -281,6 +283,9 @@ if(!slides) ggsave("figures/figure-chc-es_original.pdf", es_plot_original, width
 if(slides) ggsave("figures/figure-chc-es_spillover_control_slides.pdf", es_plot_spillover_control, width = 8, height = 8 * h_w_ratio, dpi = 300)
 if(!slides) ggsave("figures/figure-chc-es_spillover_control.pdf", es_plot_spillover_control, width = 8, height = 5, dpi = 300)
 
+if(slides) ggsave("figures/figure-chc-es_spillover_control_slides.png", es_plot_spillover_control, width = 8, height = 8 * h_w_ratio, dpi = 300)
+if(!slides) ggsave("figures/figure-chc-es_spillover_control.png", es_plot_spillover_control, width = 8, height = 5, dpi = 300)
+
 
 
 # spillover effect
@@ -298,6 +303,9 @@ if(!slides) ggsave("figures/figure-chc-es_spillover_control.pdf", es_plot_spillo
 
 if(slides) ggsave("figures/figure-chc-es_spillover_effect_slides.pdf", es_plot_spillover_effect, width = 8, height = 8 * h_w_ratio, dpi = 300)
 if(!slides) ggsave("figures/figure-chc-es_spillover_effect.pdf", es_plot_spillover_effect, width = 8, height = 5, dpi = 300)
+
+if(slides) ggsave("figures/figure-chc-es_spillover_effect_slides.png", es_plot_spillover_effect, width = 8, height = 8 * h_w_ratio, dpi = 300)
+if(!slides) ggsave("figures/figure-chc-es_spillover_effect.png", es_plot_spillover_effect, width = 8, height = 5, dpi = 300)
 
 
[…]

### 2021-05-10 figure-rings_example.R

@@ -160,11 +160,15 @@ line_within <- tribble(
 				  mapping = aes(x = x, y = y, label = label), size = 4, 
 				  hjust = 0L, vjust = 0L, family = "fira_sans", fontface = 3, inherit.aes = FALSE))
 
-ggpreview(plot, width = 2400/300, height = 2400/300 * 9/16, dpi = 300, device="pdf")
-ggpreview(plot_within, width = 2400/300, height = 2400/300 * 9/16, dpi = 300, device="pdf")
+# ggpreview(plot, width = 2400/300, height = 2400/300 * 9/16, dpi = 300, device="pdf")
+# ggpreview(plot_within, width = 2400/300, height = 2400/300 * 9/16, dpi = 300, device="pdf")
 
 ggsave("figures/figure-rings_example.pdf", plot, width = 2400/300, height = 2400/300 * 9/16, dpi = 300)
 ggsave("figures/figure-within_example.pdf", plot_within, width = 2400/300, height = 2400/300 * 9/16, dpi = 300)
+
+
+ggsave("figures/figure-rings_example.png", plot, width = 2400/300, height = 2400/300 * 9/16, dpi = 300)
+ggsave("figures/figure-within_example.png", plot_within, width = 2400/300, height = 2400/300 * 9/16, dpi = 300)
 
 
 

### 2021-05-10 tva-analysis-replicate.R

@@ -133,6 +133,12 @@ if(export & !slides) ggsave("figures/figure-tva-sample.pdf", spillover_map,
 if(export & slides) ggsave("figures/figure-tva-sample_slides.pdf", spillover_map, 
 						   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
 
+if(export & !slides) ggsave("figures/figure-tva-sample.png", spillover_map, 
+							dpi= 300, width= 2400/300, height= 1350/300, bg= "white")
+
+if(export & slides) ggsave("figures/figure-tva-sample_slides.png", spillover_map, 
+						   dpi= 300, width= 2400/300, height= 2400/300 * h_w_ratio, bg= "#ECECEC")
+
 
 
 

### 2021-10-27 latex/paper/Spillover.tex
Removed too large file

--- 2021-05-03 latex/paper/Spillover.tex
@@
 
-\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers}
-\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
-\date{\footnotesize\today}
+\title{Difference-in-Differences Estimation with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, and participants of the CU Boulder Labor Economics Seminar for helpful comments.}}
+\author{\href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado, Boulder. Email: \href{mailto:kyle.butts@colorado.edu}{kyle.butts@colorado.edu}.}}
+\date{\today}
 
@@
     \maketitle
-
     \begin{abstract}
@@
 To highlight the importance of spillover effects, I revisit analyses of three place-based interventions.
+
+        \par~\par
+        \noindent{\bf Keywords:} causal inference, spatial econometrics, spillover effects
+        \par
+        \noindent{\bf JEL Classification Number:} C01, R15, R58
+        \par 
     \end{abstract}
@@
 A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
-The figure displays observations of $\bar{Y}_{i,Post} - \bar{Y}_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the x-axis and treated units are placed at a zero distance for visualization purposes.
+The figure displays observations of $Y_{i,Post} - Y_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the x-axis and treated units are placed at a zero distance for visualization purposes.
 The example has a counterfactual trend of 2 so any difference from 2 is due to either treatment/spillover effects and the error term.

### 2021-10-27 latex/slides/Spillover_slides.tex
Removed too large file

@@
 \documentclass[aspectratio=169]{beamer}
-% Metropolis Theme ------------------------------------------------------------------------------
-\usetheme{metropolis} % Use metropolis theme
 
@@
 \addbibresource{references.bib}
-
-\usepackage{adjustbox}
-\usepackage{tabularx}
-\usepackage{booktabs}
-\usepackage{threeparttable}
-\usepackage{dcolumn}
-
-% Table Highlighting
-\usepackage[beamer,customcolors]{hf-tikz}
-\usetikzlibrary{calc}
-\usetikzlibrary{fit,shapes.misc}
-
-% To set the hypothesis highlighting boxes red.
-\tikzset{hl/.style={
-    set fill color=red!80!black!40,
-    set border color=red!80!black,
-  },
-}
-\newcommand\marktopleft[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-a) at (0,1.5ex) {};%
-}
-\newcommand\markbottomright[1]{%
-    \tikz[overlay,remember picture] 
-        \node (marker-#1-b) at (0,0) {};%
-    \tikz[red, ultra thick, overlay, remember picture, inner sep=4pt]
-        \node[draw, rectangle, fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
-}
 
@@
     \vspace{5mm}
-    \textbf{Spillover effects} are when effect of treatment extend over the treatment boundaries (states, counties, etc.). Example:
+    \textbf{Spillover effects} occur when the effect of treatment extends over the treatment boundaries (states, counties, etc.). Example: Amazon Shipping Center
 
     \begin{itemize}
-        \item A large employer opening/closing in a treated county have positive employment effects on \textbf{control counties}
+        \item A shipping center opening in county \textit{c} has positive employment effects on \textbf{nearby control counties}
 
-        \item Having nearby counties with factories raises wages and reduces effect of \textbf{treated counties}
+        \item Having nearby counties with shipping centers raises employment and therefore reduces the effect of \textbf{treated counties} through general equilibrium effects
     \end{itemize}
@@
 \begin{frame}{This Paper}
-    In this paper, I
+    In this paper, I...
 
     \begin{itemize}
-        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments done in the literature
+        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments commonly found in the literature
 
@@
                 \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\text{Counterfactual Trend} \ + \ \tau} - 
-                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{purple} Spillover on Control}}}
+                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
             \]
@@
             \[ 
-                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{red} Spillover on Treated}}} -
-                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{purple} Spillover on Control}}}
+                \hat{\tau} = \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right]}_{\substack{\text{Counterfactual Trend} \ + \ \tau \\[2mm] \ + \ \text{\color{kelly} Spillover on Treated}}} -
+                \underbrace{\hat{\mathbb{E}} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\substack{\text{Counterfactual Trend} \\[2mm] \ + \ \text{\color{coral} Spillover on Control}}}
             \]
@@
 
-    Two problems in presence of spillover effects:
+    Two problems occur in the presence of spillover effects:
 
@@
         \onslide<2->{
-            \item {\bf \color{purple} Spillover onto Control Units:}
+            \item {\bf \color{coral} Spillover onto Control Units:}
 
@@
             \vspace{2.5mm}
-            \item {\bf \color{red} Spillover onto other Treated Units:}
+            \item {\bf \color{kelly} Spillover onto other Treated Units:}
 
-            Treated units are also affected by nearby units and therefore combines ``direct'' effects with spillover effects
+            Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
         }
@@
         \[ 
-            y_{it} = \mu_t + \mu_i + \tau D_{it} + \text{Within}_{it} * D_{it} + \text{Within}_{it} * (1-D_{it}) + \varepsilon_{it}
+            y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} +  + \varepsilon_{it}
         \]
@@
         \[ 
-            \mathbb{E}\{\hat{\tau}\} = \tau + \text{\color{purple} Spillover on Control} + \text{\color{red}Spillover on Treated}
+            \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
         \]
@@
         \[ 
-            \mathbb{E}\{\hat{\tau}\} = \tau,
+            \mathbb{E}[\hat{\tau}] = \tau,
         \]
@@
 \end{frame}
+
+\begin{frame}
+    \begin{figure}[tb!]
+        \caption{Single Ring - Removes spillover effects}
+        \begin{center}
+            \resizebox{0.9\textwidth}{!}{
+                \includegraphics{../../figures/figure-within_example.pdf}
+            }
+        \end{center}
+    \end{figure}
+\end{frame}
+
+\begin{frame}
+    \begin{figure}[tb!]
+        \caption{Multiple Rings - Improves estimation of spillover effects}
+        \begin{center}
+            \resizebox{0.9\textwidth}{!}{
+                \includegraphics{../../figures/figure-rings_example.pdf}
+                } 
+            \end{center}
+    \end{figure}
+\end{frame}
+
+% \begin{frame}
+%     \begin{figure}[tb!]
+%         \caption{Community Health Centers}
+%         \begin{center}
+%             \resizebox{0.9\textwidth}{!}{
+%                 \includegraphics{../../figures/figure-chc-es_combined_slides.pdf}
+%                 } 
+%             \end{center}
+%     \end{figure}
+% \end{frame}
 
@@
             \item Discuss how framework can reconcile conflicting findings on effect of federal Empowerment Zones \begin{citecolor}\citep{Busso_Gregory_Kline_2013,Neumark_Kolko_2010}\end{citecolor}
+
+            \vspace{2.5mm}
+            \item Event Study estimates of Community Health Centers find highly localized efffects \begin{citecolor}\citep{Bailey_Goodman_Bacon_2015}\end{citecolor}
         \end{itemize}
@@
     \begin{itemize}
-        \item $Y_{it}(D_i, \textcolor{blue}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.
+        \item $Y_{it}(D_i, \textcolor{alice}{h(\vec{D}, i)})$ is the potential outcome of county $i \in \{ 1, \dots, N \}$ at time $t$ with treatment status $D_i \in \{0, 1\}$.
 
@@
         \pause
-        \item The function $\textcolor{blue}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping' which can be a scalar or a vector.
+        \item The function $\textcolor{alice}{h(\vec{D}, i)}$ maps the entire treatment vector into an `exposure mapping' which can be a scalar or a vector.
 
         \pause
-        \item No exposure is when $\textcolor{blue}{h(\vec{D}, i)} = \vec{0}$.
+        \item No exposure is when $\textcolor{alice}{h(\vec{D}, i)} = \vec{0}$.
     \end{itemize}
@@
 
-        $\textcolor{blue}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.
+        $\textcolor{alice}{h(\vec{D}, i)} = max_j \ 1\left(d(i, j\right) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.
 
@@
 
-            \item Spillovers are non-additive
+            \item Spillovers are non-additive, i.e. spillover effects do not depend on number of nearby treated areas
         \end{itemize}
@@
 
-        $\textcolor{blue}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.
+        $\textcolor{alice}{h(\vec{D}, i)} = max_j \ 1(d(i, j) \leq x)$ where $d(i,j)$ is the distance between counties $i$ and $j$.
 
@@
 
-        $\textcolor{blue}{h(\vec{D}, i)} = \sum_{j = 1}^k 1(d(i, j) \leq x)$.
+        $\textcolor{alice}{h(\vec{D}, i)} = \sum_{j = 1}^k 1(d(i, j) \leq x)$.
 
         \begin{itemize}
-            \item e.g. large factories opening
+            \item e.g. Amazon shipping center
 
@@
 \begin{frame}{Estimand of Interest}
-    Estimand of Interest: 
+    \begin{block}{Estimand of Interest:}
     \[ 
@@
     \]
+    \end{block}
 
@@
     \vspace{2.5mm}
-    Spillover Effects:
-
+    \begin{block}{Spillover Effects:}
     \[
@@
     \[ 
-        \textcolor{purple}{\tau_{\text{spillover, control}}} = \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
+        \textcolor{coral}{\tau_{\text{spillover, control}}} = \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
     \]
+    \end{block}
 \end{frame}
@@
 
-    \textbf{Assumption:} \textit{Parallel Counterfactual Trends}
+    \vspace{2.5mm}
+    \begin{block}{Assumption: {\it Parallel Counterfactual Trends}}
     \begin{align*}
-        &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] \\
-        = \ &\mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{blue}{\vec{0}}) - Y_{i,0}(0, \textcolor{blue}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big],
+        \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 1 \big] = \ \mathbb{E}\big[ \underbrace{Y_{i,1}(0, \textcolor{alice}{\vec{0}}) - Y_{i,0}(0, \textcolor{alice}{\vec{0}})}_{\text{Counterfactual Trend}} \mid D_i = 0 \big]
     \end{align*}
+    \end{block}
 
@@
 
-    Changes in outcomes does not depend on treatment status
+    Changes in outcomes do not depend on treatment status
 
@@
         &\quad - \quad  
-        \textcolor{purple}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
-        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{purple}{\tau_{\text{spillover, control}}}
+        \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
+        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{coral}{\tau_{\text{spillover, control}}}
     \end{align*}
@@
 \begin{frame}{Removing Bias}
-    \textbf{Assumption:} \textit{Spillovers are Local}
+
+    \begin{block}{Assumption: {\it Spillovers are Local}}
 
@@
         \[ 
-            \min_{j: \ D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
+            \min_{j: D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
         \]
@@
         (ii) There are treated and control units such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
+
+    \end{block}
 \end{frame}
@@
 \begin{frame}{Removing Bias}
-    With assumption that spillovers are local, define $S_i$ to be an indicator that contains all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).
+    With assumption that spillovers are local, define $S_it$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).
 
-    Then $\hat{\tau}$ will be a consistent estimate for $\tau$ in this specification: 
+    Estimation of the following equation:
     \[ 
-        y_{it} = \mu_t + \mu_i + \tau D_{it} + \text{Within}_{it} * D_{it} + \text{Within}_{it} * (1-D_{it}) + \varepsilon_{it}
+        y_{it} = \mu_t + \mu_i + \tau D_{it} + \tau_{\text{spill,treat}} S_{it} * D_{it} + \tau_{\text{spill,control}} S_{it} * (1-D_{it}) + \varepsilon_{it}
     \]
+
+    \begin{itemize}
+        \item $\hat{\tau}$ is consistent for $\tau_{\text{direct}}$
+
+        \item $\hat{\tau}_{\text{spill}}$'s are not consistent for average spillover effects (hence the need for rings).
+    \end{itemize}
 
@@
 
-% ------------------------------------------------------------------------------
-\section{Estimation with Spillovers}
-% ------------------------------------------------------------------------------
-
-\begin{frame}{Common Solution: Removing ``contaminated'' controls}
-    A common solution to the problem of spillover is to restimate on a subsample with neighboring control units removed.
+\begin{frame}{Aside -- Removing ``contaminated'' controls}
+    A common solution to the problem of spillover is to re-estimate on a subsample with neighboring control units removed.
 
@@
 
-\begin{frame}{Solution: Parametrize potential outcomes}
-    Another option is to directly control for spillovers by parametrizing the exposure mapping.
-
-    The corret exposure mapping is not observable to a researcher which raises the question:
-
-    Are there specifications that work well even if the spillovers are misspecified?
-\end{frame}
+% ------------------------------------------------------------------------------
+\section{Estimation of Spillovers}
+% ------------------------------------------------------------------------------
 
 \begin{frame}{Robustness to Misspecification}
-    Generate data using the same data-generating process as before but with different spillover functions:
+    Generate data using the following data-generating process with different exposure mappings:
 
@@
         \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly.
+
+        \item Details in the paper, but $\mu_t$ is normally distributed on a linear time trend, $\mu_i$ are normally distributed
     \end{itemize}
@@
     \begin{itemize}
-        \item \textit{Within $40/80$mi.}:
-        \begin{itemize}
-            \item Indicator for nearest treated unit being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Within $40/80$mi. (Additive)}: 
-        \begin{itemize}
-            \item Number of treated units being within $40/80$ miles.
-        \end{itemize}
-
         \item \textit{Decay}: 
@@
     \begin{itemize}
-        \item \textit{Within $40/80$mi.}:
-        \begin{itemize}
-            \item Indicator for nearest treated unit being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Within $40/80$mi. (Additive)}: 
-        \begin{itemize}
-            \item Number of treated units being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Decay}: 
-        \begin{itemize}
-            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-        \item \textit{Decay (Additive)}: 
-        \begin{itemize}
-            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
         \item \textit{Rings}: 
@@
 
-        \begin{adjustbox}{width = 1.1\textwidth, center}
+        \begin{adjustbox}{width = \textwidth, center}
             \begin{threeparttable}
@@
     \onslide<3->{
-        \textbf{Indicator (or set of indicators) that captures all affected unit removes all bias}
+        \textbf{Indicator (or set of rings) that captures \emph{all} affected unit removes all bias}
     }
@@
     \begin{itemize}
-        \item $\textcolor{purple}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?
+        \item $\textcolor{coral}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?
 
@@
 \begin{frame}
+    \begin{figure}[tb!]
+        \caption{Single Ring - Removes spillover effects}
+        \begin{center}
+            \resizebox{0.9\textwidth}{!}{
+                \includegraphics{../../figures/figure-within_example.pdf}
+            }
+        \end{center}
+    \end{figure}
+\end{frame}
+
+\begin{frame}
+    \begin{figure}[tb!]
+        \caption{Multiple Rings - Improves estimation of spillover effects}
+        \begin{center}
+            \resizebox{0.9\textwidth}{!}{
+                \includegraphics{../../figures/figure-rings_example.pdf}
+                } 
+            \end{center}
+    \end{figure}
+\end{frame}
+
+\begin{frame}
     \begin{table}[!tb]
@@
 
-    Research Question: What are the local effects of TVA on manufacturing and agricultural economies? Do these effects come at the cost of other counties?
+    \pause
+    Research Questions:
+    \begin{itemize}
+        \item What are the local effects of TVA on manufacturing and agricultural economies?
+        \item Do these effects come at the cost of other counties?
+    \end{itemize}
 \end{frame}
@@
         \item $\text{Ring}(d)$ is a set of indicators for being in the following distance bins (in miles) from the Tennessee Valley Authority: 
-        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] \right\} \]
+        \[ d \in \left\{ (0, 50], (50, 100], (100, 150] (150, 200]\right\} \]
     \end{itemize}
@@
         \begin{threeparttable}
-            \begin{tabular}{@{} lc@{\extracolsep{20pt}}c@{\extracolsep{4pt}}ccc @{}}
+            \begin{tabular}{@{} l c@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
                 % Head
@@
 
-                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{4}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
-                \cmidrule{2-2} \cmidrule{3-6} 
-                & & & TVA between & TVA between & TVA between \\ 
-                \textit{Dependent Var.} & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. \\
+                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{5}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
+                \cmidrule{2-2} \cmidrule{3-7}
+                & & & TVA between & TVA between & TVA between & TVA between \\ 
+                & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. & 150-200 mi. \\ 
+                \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\
 
@@
 
-                Agricultural employment     & $-0.0514^{***}$& $-0.0678^{***}$& $-0.0310^{**}$ &    $-0.0112$   & $-0.0252^{***}$\\
-                &   $(0.0087)$   &   $(0.0102)$   &   $(0.0123)$   &   $(0.0094)$   &   $(0.0084)$
+                Agricultural employment     & $-0.0514^{***}$ & $-0.0739^{***}$& $-0.0371^{***}$&    $-0.0164$   & $-0.0298^{***}$&  $-0.0157^{*}$ \\
+                &   $(0.0114)$   &   $(0.0142)$   &   $(0.0002)$   &   $(0.0114)$   &   $(0.0096)$   &   $(0.0088)$
 
@@
                     \\
-                    Manufacturing employment    & $0.0560^{***}$ &  $0.0461^{**}$ &    $-0.0104$   &    $-0.0128$   &  $-0.0248^{*}$ \\
-                    &   $(0.0187)$   &   $(0.0210)$   &   $(0.0205)$   &   $(0.0257)$   &   $(0.0147)$
+                    Manufacturing employment    & $0.0560^{***}$ &    $0.0350$    & $-0.0203^{***}$&    $-0.0245$   &  $-0.0331^{*}$ & $-0.0296^{**}$ \\
+                    &   $(0.0161)$   &   $(0.0218)$   &   $(0.0006)$   &   $(0.0282)$   &   $(0.0189)$   &   $(0.0142)$ 
                 }
@@
 
+\end{frame}
+
+\begin{frame}{Identification Strategies and Place-Based Policies}
+
     \begin{itemize}
-        \pause
         \item \citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program.
@@
 
+\end{frame}
+
+\section{Event Study}
+
+\begin{frame}{Gardner (2021) Overview}
+
+    \[ 
+        y_{it} = \mu_i + \mu_t + \tau D_{it} + \varepsilon_{it}
+    \]
+
+    The problem with estimating this by OLS is that the treatment variable becomes residualized $\tilde{D}_{it}$ and this leads to all sorts of problems... (see new diff-in-diff literature)
+
+    \pause
+
+    Gardner (2021) recommends a two-step approach:
+
+    1. Estimate $\mu_i$ and $\mu_t$ using never-treated/not-year-treated observations ($D_{it}$ = 0). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.
+
+    \pause
+    2.
+Then, regress $y_{it} - \hat{\mu}_i - \hat{\mu}_t \equiv \tilde{y}_{it}$ on $\tau D_{it}$ (or event study leads/lags).
+This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).
+\end{frame}
+
+\begin{frame}{Controlling for Spillovers in Staggered Treatment Timing}
+    \[ 
+        y_{it} = \mu_i + \mu_t + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} + \varepsilon_{it}
+    \]
+
+    Adjust two-step approach:
+
+    \pause
+
+    1. Estimate $\mu_i$ and $\mu_t$ using observations that aren't yet treated/affected by spillovers ($D_{it} = 0$ and $Within_{it} = 0$). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.
+
+    2.
+Then, regress $\tilde{y}_{it}$ on $\tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}}$ (or interacted event study leads/lags).
+This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).
+
+\end{frame}
+
+\begin{frame}{Community Health Centers}
+    \begin{citecolor}\citet{Bailey_Goodman_Bacon_2015}\end{citecolor} study the creation of federal community health centers between 1965 and 1974
+
+    \textbf{Research Question:} Do low-/no-cost health services lower the mortality rate of the treated counties? \emph{New Question:} Do these effects spread to neighboring counties?
+\end{frame}
+
+\begin{frame}
+    \begin{figure}[tb!]
+        \caption{Effects of Establishment of Community Health Centers}
+        \begin{center}
+            \resizebox{0.9\textwidth}{!}{
+                \includegraphics[width=\textwidth]{../../figures/figure-chc-es_original.pdf}
+            }
+        \end{center}
+    \end{figure}
+\end{frame}
+
+\begin{frame}
+    \begin{figure}[tb!]
+        \caption{Direct and Spillover Effects of Community Health Centers}
+        \begin{center}
+            \resizebox{0.9\textwidth}{!}{
+                \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
+            }
+        \end{center}
+    \end{figure}
 \end{frame}

### 2021-10-27 chc-analysis.R

@@ -1,63 +1,59 @@
-## -----------------------------------------------------------------------------
-## chc_replicate.R
+## chc-analysis.R --------------------------------------------------------------
 ## Kyle Butts, CU Boulder Economics 
 ## 
 ## Replication of Bailey and Goodman-Bacon (2015) with extension for event study 
-## framework.
-## -----------------------------------------------------------------------------
+## framework including spillover effect controls.
+
 
 library(tidyverse)
 library(sf)
-library(cli)
-library(did)
+library(kfbmisc)
 library(fixest)
+library(did2s)
 
-source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
-
-setwd("~/Documents/Projects/Spatial Spillover/")
-
-slides <- FALSE
+slides <- TRUE
 h_w_ratio <- 9/16
 
+# ---- Data Cleaning -----------------------------------------------------------
 
-# Set-up Data ------------------------------------------------------------------
-
-df <- 
-	haven::read_dta("data/chc/aer_data.dta") %>% 
+df <- haven::read_dta(here::here("data/chc/aer_data.dta")) |> 
 	# Remove LA, New York, Chicago
 	filter(
 		!(stfips==36 & cofips==61) & !(stfips==6  & cofips==37) & !(stfips==17 & cofips==31)
-	) %>%
+	) |>
 	# Create urban dummy
-	group_by(fips) %>% 
+	group_by(fips) |> 
 	mutate(
 		`_urb` = sum(`_60pcturban` * (year == 1960), na.rm = TRUE)
-	) %>% 
-	ungroup() %>%
+	) |> 
+	ungroup() |>
 	# cut every 25% with indicator from 0
 	mutate(
 		Durb = Hmisc::cut2(`_urb`, cuts = c(0, 1, 24.999, 49.999, 74.999, 110))
-	) %>% 
+	) |> 
 	replace_na(list(chc_year_exp = 0))
 
-ctr_pop <- read_sf("data/2010_county_centpop/") %>% 
-	mutate(fips = as.numeric(paste0(STATEFP, COUNTYFP))) %>% 
-	select(fips) %>% 
-	arrange(fips)
[…]

### 2021-10-27 data-prepare_counties.R

@@ -1,22 +1,17 @@
 ## -----------------------------------------------------------------------------
-## 2020-09-01_prepare_counties.R
+## data-prepare_counties.R
 ## Kyle Butts, CU Boulder Economics 
 ## 
-## Downloads counties, simplifies geometries, create distance matrix and contiguous matrix, and saves it. This download will be used by all the other scripts
+## Downloads counties, simplifies geometries, create distance matrix and 
+## contiguous matrix, and saves it.
 ## -----------------------------------------------------------------------------
 
-
-setwd("~/Documents/Projects/Spatial Spillover/")
-
-library("tidyverse")
-library("sf")
-library("stars")
-library("units")
-library("tigris")
-library("gstat")
-library("exactextractr") 
-library("fixest")
-library("doParallel")  
+library(tidyverse)
+library(sf)
+library(stars)
+library(units)
+library(tigris)
+library(here)
 
 
 ## Prepare Spatial Data --------------------------------------------------------
@@ -24,11 +19,8 @@ library("doParallel")
 # Load FIPS codes
 data("fips_codes", package= "tigris")
 
-# Run once
-# sf::read_sf("data/2010_county/US_county_2010.shp") %>% rmapshaper::ms_simplify(keep = 0.02) %>% st_transform(st_crs(2163)) %>% sf::write_sf(., "data/2010_county.geojson")
-
 # Load Counties Shapefile at low resolution
-counties <- sf::read_sf("data/2010_county.geojson") %>% 
+counties <- sf::read_sf(here::here("data/2010_county.geojson")) %>% 
 	sf::st_make_valid() %>% st_buffer(0) %>%
 	select(state_code= STATEFP10, county_code= COUNTYFP10) %>%
 	# Merge with fips_codes to get state and county names
@@ -39,8 +31,8 @@ counties <- sf::read_sf("data/2010_county.geojson") %>%
 	arrange(state_code, county_code)
 
 
-# Load Counties Center of Popula"tion from NHGIS
-counties_centpop <- sf::read_sf("data/2010_county_centpop/US_county_cenpop_2010.shp") %>%
+# Load Counties Center of Populaion from NHGIS
+counties_centpop <- sf::read_sf(here::here("data/2010_centpop/US_county_cenpop_2010.shp")) %>%
 	filter(!STNAME %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) %>%
[…]

### 2021-10-27 figure-example_exposure_mappings.R

@@ -2,35 +2,22 @@
 ## figure-example_exposure_mappings.R
 ## Kyle Butts, CU Boulder Economics 
 ## 
-## Create examples of each exposure mapping
+## Create examples of each exposure mapping using US counties
 ## -----------------------------------------------------------------------------
 
-library("tidyverse")
-library("glue")
-library("sf")
-library("stars")
-library("units")
-library("gstat")
-library("exactextractr")
-library("fixest")
-library("doParallel")
-library("gt")
-library("magrittr")
-
-# Macbook
-setwd("~/Documents/Projects/Spatial Spillover/")
-# Research Computing
-# setwd("/projects/kybu6659/spatial_spillover/")
-
-# Load theme_kyle()
-source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/15196997e5aad41696b03c49be3bfaaca132fdf2/theme_kyle.R")
+library(tidyverse)
+library(here)
+library(glue)
+library(sf)
+library(stars)
+library(fixest)
+library(doParallel)
+library(gt)
+library(kfbmisc)
 
 # Export Options
 slides <- TRUE
 h_w_ratio <- 9/16
-# h_w_ratio <- 3/4
-
-
 
 # sim_data_misspecification()
 source("helper-sim_function_misspecification.R")
@@ -38,18 +25,14 @@ source("helper-sim_function_misspecification.R")
 
 ## Load Spatial Data -----------------------------------------------------------
 # From data_prepare_counties.R
-load(file= "data/counties_and_mat.RData")
+load(file= here::here("data/counties_and_mat.RData"))
 
 us <- counties %>% summarize()
-
 
 set.seed(20210215)
 
 df <- sim_data_misspecification(drop_geometry = FALSE, normalize = TRUE) %>% 
 	st_as_sf()
-
-
-
 
 
 ## Treatment Effect ------------------------------------------------------------
@@ -86,7 +69,7 @@ for(type in types){
 				fill = "Spillover", color = "Treated"
 			) + 
 			scale_fill_gradient(low = "white", high = "grey10", na.value = NA, limits = c(0, 2)) +
-			theme_kyle(slides = TRUE) + 
+			theme_kyle() + 
 			guides(
 				fill = guide_legend(title.position = "top"),
[…]

### 2021-10-27 figure-gen_map_examples_with_bias.R

@@ -1,288 +1,0 @@
-## -----------------------------------------------------------------------------
-## figure-gen_map_examples_with_bias.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## Generate maps of Spatial Spillover, Spatial Autocorrelation of Treatment, etc. and their bias
-## -----------------------------------------------------------------------------
-
-setwd("~/Documents/Projects/Spatial Spillover/")
-
-library("tidyverse")
-library("sf")
-library("stars")
-library("units")
-library("tigris")
-library("gstat")
-library("exactextractr") 
-library("fixest")
-library("doParallel")  
-library("RColorBrewer")
-library("patchwork")
-
-# sim_data(i)
-source("helper-sim_function.R")
-
-# Load theme_kyle()
-source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
-
-# Is for slides or paper?
-slides <- TRUE
-h_w_ratio <- 9/16
-# h_w_ratio <- 3/4
-
-
-## Load Parameters -------------------------------------------------------------
-te <- 2
-te_spill <- 1
-te_spill_treat <- -0.5
-low_zone_plus <- 0.4
-high_zone_plus <- 1.4
-
-
-##------------------------------------------------------------------------------
-##  Prepare Spatial Data                                                    ----
-##------------------------------------------------------------------------------
-
-## Load Spatial Data -----------------------------------------------------------
-# From data_prepare_counties.R
-load(file= "data/counties_and_mat.RData")
-
-us <- counties %>% st_make_valid() %>% st_buffer(0) %>% st_set_precision(1e4) %>% summarize() 
-
-
-##------------------------------------------------------------------------------
-##  Generate Maps with No Spatial Autocorrelation                           ----
-##------------------------------------------------------------------------------
-
-set.seed(70)
-
-treat_prob <- 0.05
-treat_prob_percent <- paste0(round(treat_prob * 100, 1), "%")
-
[…]

### 2021-10-27 figure-rings_example.R

@@ -2,38 +2,13 @@
 ## figure-binscatter_example.R
 ## Kyle Butts, CU Boulder Economics 
 ## 
-## On Binscatter (2020)
+## Single indicator and multiple rings
 ## -----------------------------------------------------------------------------
 
 library(tidyverse)
 library(glue)
 library(binsreg)
-
-logname <- Sys.getenv("LOGNAME")
-cli::cli_alert_success("User: {logname}")
-
-if (logname == "kylebutts") setwd("~/Documents/Projects/Spatial Spillover/")
-rm(logname)
-
-# Load Custom Theme 
-source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
-
-# ggpreview
-ggpreview <- function(..., device = "png", cairo = TRUE) {
-	fname <- tempfile(fileext = paste0(".", device))
-	
-	if (cairo & device == "pdf") {
-		ggplot2::ggsave(filename = fname, device = cairo_pdf, ...)
-	} else if (cairo & device == "png") {
-		ggplot2::ggsave(filename = fname, device = device, type = "cairo", ...)
-	} else {
-		ggplot2::ggsave(filename = fname, device = device, ...)
-	}
-	
-	system2("open", fname)
-	invisible(NULL)
-}
-
+library(kfbmisc)
 
 # Generate Data ----------------------------------------------------------------
 
@@ -129,10 +104,10 @@ line_within <- tribble(
 (plot <- ggplot() + 
 	geom_point(data=first_diff, aes(x=dist, y=d_y1), shape=16, col="lightgrey") + 
 	geom_hline(yintercept = reg[[("(Intercept)")]], linetype = 'longdash') + 
-	geom_point(data=dots, aes(x=x, y=fit), col="#5e81ac", size=2, shape=19) +
-	geom_line(data=line, aes(x=x, y=fit), col="#5e81ac", size=0.5) + 
+	geom_point(data=dots, aes(x=x, y=fit), col="#5e81ac", size=3, shape=19) +
+	geom_line(data=line, aes(x=x, y=fit), col="#5e81ac", size=1.5) + 
 	theme_kyle(base_size = 16) + 
-	labs(x = "Distance from Nearest Treated", y = "Change in Outcome") +
[…]

### 2021-10-27 sim-bias_as_treat_increase.R

@@ -1,452 +1,0 @@
-## -----------------------------------------------------------------------------
-## sim-bias_as_treat_increases.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## This file will run a simulation of the bias arising from Diff-in-diffs in spatial situations where spillover effects occur. The end result is a plot of the magnitude of the bias occurring as the number of treated units, and hence the "corrupted" control units, increase. 
-## -----------------------------------------------------------------------------
-
-
-library("tidyverse")
-library("sf")
-library("stars")
-library("units")
-library("gstat")
-library("exactextractr")
-library("fixest")
-library("doParallel")
-
-# Macbook
-setwd("~/Documents/Projects/Spatial Spillover/")
-# Research Computing
-# setwd("/projects/kybu6659/spatial_spillover/")
-
-# sim_data()
-source("helper-sim_function.R")
-
-# Load theme_kyle()
-source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/15196997e5aad41696b03c49be3bfaaca132fdf2/theme_kyle.R")
-
-# Export
-export <- TRUE
-slides <- FALSE
-h_w_ratio <- 9/16
-# h_w_ratio <- 3/4
-
-
-
-## Load Spatial Data -----------------------------------------------------------
-# From data_prepare_counties.R
-load(file= "data/counties_and_mat.RData")
-
-
-
-## Simulation Function ---------------------------------------------------------
-
-#' Repeats n trials with specific parameters and returns a vector of te_hat
-#'
-#' @param n_trials the number of trials for each simulation
-#' @param treat_prob This is the unconditional probability of treatment
-#' @param treat_spillover_distance The maximum distance in meters away a treated county can be to be considered treated 
-#' @param treat_effect The true simulated treatment effect
[…]

### 2021-10-27 sim-bias_from_spatial_autocorr.R

@@ -1,282 +1,0 @@
-## -----------------------------------------------------------------------------
-## 2020-08-22_bias_from_spatial_autocorr.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## Initial attempt at spatial autocorrelation of treatment variable with spillovers. Conditional on holding the number of units treated, does bias increase with the closeness of treated units. This answer will likely be different if treated units receive spillover effects or not.
-## -----------------------------------------------------------------------------
-
-library("tidyverse")
-library("sf")
-library("stars")
-library("units")
-library("gstat")
-library("exactextractr")
-library("fixest")
-library("doParallel")
-
-# Macbook
-# setwd("~/Documents/Projects/Spatial Spillover/")
-# Research Computing
-setwd("/projects/kybu6659/spatial_spillover/")
-
-# sim_data()
-source("helper-sim_function.R")
-
-# Load theme_kyle()
-source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/15196997e5aad41696b03c49be3bfaaca132fdf2/theme_kyle.R")
-
-# Export
-export <- TRUE
-slides <- TRUE
-h_w_ratio <- 9/16
-# h_w_ratio <- 3/4
-
-
-## Load Spatial Data -----------------------------------------------------------
-# From data-prepare_counties.R
-load(file= "data/counties_and_mat.RData")
-
-
-
-## Simulation Function ---------------------------------------------------------
-
-#' Repeats n trials with specific parameters and returns a vector of te_hat
-#'
-#' @param n_trials the number of trials for each simulation
-#' @param cl the number of cores to run this on
-#' @return a tibble of estimates of treatment effect under different scenarios. This will be used with dplyr::add_row
-treatment_effect_simulation <- function(
-	# Simulation Parameters
-	n_trials = 100, cl = 14,
-	# sim_function parameters
-	treat_prob = 0.1,
[…]

### 2021-10-27 sim-misspecification_of_spillover.R

@@ -2,28 +2,22 @@
 ## sim-misspecification_of_spillover.R
 ## Kyle Butts, CU Boulder Economics 
 ## 
-## This file estimates spillover functions using misspecified spillover variables and compares the biases found.
+## This file performs a set of Monte Carlo simulations that estimate a set of 
+## DGPs using various exposure mappings and estimates them using exposure 
+## mappings and ring(s). The first simulation reports on average bias found in 
+## the treatment effect estimate and the second simulation reports on the 
+## ability to accurately predict spillover effects from fitted values.
 ## -----------------------------------------------------------------------------
 
-library("tidyverse")
-library("glue")
-library("sf")
-library("stars")
-library("units")
-library("gstat")
-library("exactextractr")
-library("fixest")
-library("doParallel")
-library("gt")
-library("magrittr")
-
-# Macbook
-setwd("~/Documents/Projects/Spatial Spillover/")
-# Research Computing
-# setwd("/projects/kybu6659/spatial_spillover/")
-
-# Load theme_kyle()
-source("https://gist.githubusercontent.com/kylebutts/7dc66a01ec7e499faa90b4f1fd46ef9f/raw/15196997e5aad41696b03c49be3bfaaca132fdf2/theme_kyle.R")
+library(tidyverse)
+library(here)
+library(glue)
+library(sf)
+library(stars)
+library(fixest)
+library(doParallel)
+library(gt)
+library(kfbmisc)
 
 # Export
 export <- TRUE
@@ -37,17 +31,20 @@ extract_body <- function(gt) {
 }
 
 
-
 # sim_data_misspecification()
-source("helper-sim_function_misspecification.R")
+source(here::here("helper-sim_function_misspecification.R"))
  
 
-## Load Spatial Data -----------------------------------------------------------
+# ---- Load Spatial Data -------------------------------------------------------
 # From data_prepare_counties.R
-load(file= "data/counties_and_mat.RData")
+load(file= here::here("data/counties_and_mat.RData"))
 
 
-## Simulation: Bias ------------------------------------------------------------
+# ---- Simulation: Bias --------------------------------------------------------
+# Simulates a set of DGPs with different kinds of exposure mappings
+# For each DGP, estimates using many different parametric forms + ring(s) method
[…]

### 2021-10-27 tva-analysis-helpers.R

@@ -1,6 +1,5 @@
 
 # Winsorize helper function ----------------------------------------------------
-
 # https://gist.github.com/maifeng/3e5a1f0dd65bf0fd9c2b8f4ac8f5fab3
 winsorize_x = function(x, cut = 0.01){
 	cut_point_top <- quantile(x, 1 - cut, na.rm = T)

### 2021-10-27 tva-analysis-replicate.R

@@ -1,44 +1,37 @@
-## -----------------------------------------------------------------------------
-## tva-analysis-replicate.R
+## tva-analysis-replicate.R ----------------------------------------------------
 ## Kyle Butts, CU Boulder Economics 
 ## 
-## Replicate Table 3 of Klein and Moretti (2014) 
-## -----------------------------------------------------------------------------
+## Replicate Table 3 of Klein and Moretti (2014) with extension that includes
+## spillover control using rings method
 
 library(tidyverse)
 library(haven)
 library(sf)
 library(Rcpp)
 library(RcppArmadillo)
-
-
-setwd("~/Documents/Projects/Spatial Spillover/")
-
-# Load theme_kyle()
-source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")
+library(kfbmisc)
 
 # Helper functions
-source("tva-analysis-helpers.R")
-source("helper-conley.R")
+source(here::here("tva-analysis-helpers.R"))
+source(here::here("helper-conley.R"))
 
-# Export
-export <- TRUE
-slides <- FALSE
+h_w_ratio <- 9/16
 
-## Load Data -------------------------------------------------------------------
 
-df <- read_dta("data/tva/build.dta") %>% 
+# ---- Load Data ---------------------------------------------------------------
+
+df <- read_dta(here::here("data/tva/build.dta")) %>% 
 	mutate(
 		fips = sprintf("%05d", fipstat * 1000 + fipcnty)
 	)
  
-counties <- sf::read_sf("data/2010_county.geojson") %>% 
+counties <- sf::read_sf(here::here("data/2010_county.geojson")) %>% 
 	mutate(fips = paste0(STATEFP10, COUNTYFP10)) %>% 
 	select(state = STATEFP10, county = COUNTYFP10, fips) %>% 
 	rmapshaper::ms_simplify(keep = 0.05)
 
 # Create TVA shape
-tva_fips <- scan("data/tva/tvacounties.txt", character())
+tva_fips <- scan(here::here("data/tva/tvacounties.txt"), character())
 
 tva <- counties %>% 
 	filter(fips %in% tva_fips) %>% 
@@ -51,7 +44,7 @@ counties$dist_to_tva <- as.vector(units::drop_units(units::set_units(dist_mat, "
[…]

### 2021-10-27 latex/paper/Spillover.tex
Update draft
- More systematically discussed effects of interest
- Identification section on each effect and estimation
- Section on estimation of spillovers more rigorous
- Event Study -> Gardner (2021) to allow spillover estimation
- Reworked introduction

--- 2021-05-03 latex/paper/Spillover.tex
@@
 
-\title{\color{navyblue} Difference-in-Differences Estimation with Spatial Spillovers}
-\author{\normalsize Kyle Butts\\{\footnotesize Univ. of Colorado, Boulder}}
-\date{\footnotesize\today}
+\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, and the WEAI Conference}}
+ %, and the University of Rochester HEEL Lab for helpful comments.}}
+\author{\href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado Boulder, Economics Department (\href{mailto:kyle.butts@colorado.edu}{kyle.butts@colorado.edu})}}
+\date{\today}
 
@@
 
-%\addbibresource{references.bib}
-\hypersetup{pdftitle={Difference-in-Differences Estimation with Spatial Spillovers}, pdfauthor={Kyle Butts}}
+\hypersetup{
+    pdftitle={Difference-in-Differences Estimation with Spatial Spillovers},    pdfauthor={Kyle Butts}
+}
 
@@
     \begin{abstract}
+        {\small
         Empirical work often uses treatment assigned following geographic boundaries.
@@
 In this paper, I introduce a potential outcomes framework to model spillover effects and decompose the estimate's bias in two parts: (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-I propose estimation strategies that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves.
-I extend \citet{Callaway_SantAnna_2020} to allow for event-study estimates that control for spillovers.
+I propose estimation strategies that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves including in settings with staggered treatment timing.
 To highlight the importance of spillover effects, I revisit analyses of three place-based interventions.
+
+        \par~\par\noindent
+        \noindent{\color{asher} JEL Classification Number:} C01, R15, R58
+        \par
+        \noindent{\color{asher} Keywords:} difference-in-differences, spatial econometrics, spillover effects, causal inference, place-based interventions
+        \par\vspace{-2.5mm}
+        }
     \end{abstract}
@@
 
-Empirical work often considers settings where policy is targeted to groups of units by geographic boundaries, but the effect of these treatments spillover onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
-geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} Place-based policies, programs that are targeted to specific locations, are known to have general-equilibrium effects that extend far past the area intended to receive treatment \citep{Kline_Moretti_2014b}.
-Spillover effects can occur on to both control and treated units.
-First, there can be spillover effects onto control units.
-For example, individuals in control areas can travel to the treated areas and receive treatment (e.g.
-a hospital opening serves nearby residents) or changes in the economy in a treated area can have feedback loops that affect nearby economies (e.g.
-a new factory opening increases service sector spending).
-Second, there can be spillover effects onto other treated units.
-For example, forces of agglomeration can increase effects as treatment concentration increases (e.g.
-knowledge-sharing between workers), forces of congestion or market competition can decrease the effects of treatment (e.g.
-bidding up of wages cause employment effects of factory openings to be mitigated), and treatment effectiveness may be improved by multiple jurisidictions learning from one another.
-
-In this paper, I introduce a potential outcome framework that directly models spillover effects.
-Using this framework, the central theoretical result of my paper is that in the presence of spillovers, the standard difference-in-differences estimate identifies the direct effect of treatment (the estimand of interest) plus two additional bias terms resulting from the spillovers.\footnote{The term `direct' effect can refer to either the average treatment effect on the treated or the intent to treat effect.
-In empirical applications, the `direct` effect is sometimes called the `partial equilibrium' effect or the `local' effect.} The intuition for why the two forms of spillovers cause bias is as follows.
-
+Empirical work often considers settings where a policy is targeted to groups of units by geographic boundaries, but the effect of treatment spillovers onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, individuals in control areas can travel to the treated areas and receive treatment (e.g.
+a hospital opening serves nearby residents) or shocks to a labor market can have feedback loops that affect nearby areas (e.g.
+a new factory opening increases service sector spending in the commuting zone).
+For other treated units, forces of agglomeration can increase effect size as treatment concentration increases (e.g.
+knowledge-sharing between firms) or forces of congestion/competition can decrease the effects of treatment (e.g.
+bidding up of wages causes the employment effects of factory openings to be mitigated).
+In this paper, I introduce a potential outcomes framework that directly models spillover effects.
+
+Using this potential outcome framework, I define the different possible treatment/spillover effects of interest and the relative advantage and interpretation of each.
+First, there is the `switching effect' which is the relevant parameter for local policy makers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units''.
+It is difficult to estimate the switching effect without parametric assumptions.
+The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors.
+For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities versus the case where a close neighbor already has constructed one.
+Therefore, switching effects are defined seperately for each level of exposure and estimation of a switching effect requires knowledge of which units experience the same level of exposure.
+While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions.
+This effect is the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatment.
+That is, what are the effects of turning on a unit's treatment if this were the \emph{only} unit to be treated in their area.
+
+Second, there is the `total effect' which is the relevant parameter for national policy makers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
+This treatment effect summarizes what were the effects of going from the world with no treatment to the entire vector of treatment status.
+I further show that this effect comes from two sources: the direct effect and the average spillover effect from other treated units.
+
+The standard difference-in-differences estimate identifies none of these treatment effects in the presence of spillovers.
+The first result of the paper shows that the difference-in-differences esitmand can be decomposed into the direct effect plus two additional bias terms resulting from the spillovers.
+The intuition is as follows.
 First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
@@
 In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
-
-For example, consider trying to estimate employment effects of a factory opening in a county.
-Agglomeration economies suggest that neighboring counties would also benefit from knowledge spillovers and improved access to supply chain which would potentially increase economic activity \citep{Duranton_Puga_2003}.
-The treatment effect estimate is negatively biased because the change in outcome in neighboring counties is higher than it would be absent treatment.
-Researchers would therefore underestimate the positive benefits of treatment.\footnote{If the policy maker had a welfare function that included both treated and neighboring counties, they would fail to count the positive benefits of the control units and they would underestimate the positive benefits on the treated units.
-Difference-in-differences estimation would therefore result in double undercounting.}
-
-% Despite the problem of spillovers being common across many settings, \citet{Berg_Streitz_2019} document that little empirical analysis directly controls for spillovers when estimating the `direct' effect of treatment on the treated units.
-
-Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.The spillover onto other treated units is averaged into the treated units' change in outcomes.
+For example, if nearby control units also benefit from treatment, then researchers would underestimate the positive benefits of treatment.
+Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
+The spillover onto other treated units is averaged into the treated units' change in outcomes.
 Therefore the bias of treatment effect is the same sign as the sign of the spillover.
-Continuing with our example, two factory openings in neighboring counties might cause the benefit of each individual factory to increase due to agglomeration forces.
-The estimated treatment effect will count the `direct' effect of the factory opening as well as the benefit of the agglomeration economies from nearby factory openings.
-Therefore the treatment effect will be positively biased due to the positive spillover onto also treated units.
-
-I then use my potential outcome framework to evaluate commonly used empirical strategies found in applied work and provide practical recommendations for researchers.
-The most common approach is to remove potentially contaminated control units from the sample in order to remove spillover effects on control units \citep{Berg_Streitz_2019}.
-This approach is not recommended for two reasons.
-First, the removal of too few control units will leave bias and removal of too many will lower precision of the treatment effect estimate.
-This results in a bias-variance trade-off that other approaches do not share.
-Second, this method does not remove spillover effects on treated units and will leave this bias term in the difference-in-differences estimate.
-Another common approach is to include either an indicator or a set of rings around treated units.
-This approach will remove all bias from the spillover effects on control units provided that all control units with spillover effects are included in the indicator.
-Similar to the previous approach, spillover effects on also treated units still add bias to estimates of the direct effect.
-
-Therefore, I propose an estimation strategy that will remove both sources of bias with very minimal assumptions on the structure of spillovers.
-To remove \textit{all bias} from the direct effect estimate, a researcher needs to just include an indicator for being close to a treated unit interacted with treatment status, so long as the indicator captures all units affected by spillovers.
+Last, since the total effect is the direct effect plus the average spillover effect on treated units, the difference-in-differences estimand can also be decomposed into the total effect minus the average spillover effect on control units.
+
+This paper then defines conditions under which each treatment effect is nonparametrically identified.
+I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} under certain constraints on the spillover effects.
+The other two treatment effects considered are able to be identfified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units close to treated units.
+This could fail in the case of general equilibrium shocks that cause units far away to be affected by treatment.
+
+Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
 In my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units.
@@
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
-The only assumption required is the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed.
+The only assumption required is selecting the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed.
 Including too many units in the indicator will increase the variance in the estimates for average spillover effects as the other control units identify the parallel counterfactual unit.}
 
-Since spillover effects are often important causal effects themselves, I next turn to how to estimate spillovers directly.
-I show with evidence from Monte Carlo simulations, that commonly used semi-parametric estimation strategies capture spillovers well (in a mean square prediction error sense).
-This involves creating a set of distance bins from treated units (e.g.
-being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.} The key consideration required by a researcher is whether the size of spillover effects are additive in the number of nearby treated units or not.
-For non-additive spillovers, I recommend a set of mutually-exclusive indicators which measures which distance bin that the \textit{closest} treated unit falls within for a given observation.
-For additive spillovers, I recommend using the \textit{number of} treated units within each distance bin for a given observation.\footnote{While the non-additive version of ring indicators will remove all bias from the direct effect of treatment even under misspecification, this is not true of additive rings.
-Therefore, researchers may want to estimate the direct effect of treatment using non-additive rings and then use additive rings to estimate spillover effects.}
+The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers.
+The above method can be improved by creating a set of distance bins from treated units (e.g.
+being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
+In some cases, the bins can be determined in a data driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single large indicator, this estimator still consistently estimates the treatment effect of interest.
+This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.
 
@@
 I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
-The Tennessee Valley Authority was a large scale New Deal program that created many new dams for flood-protection and navigation.
-The construction of large-scale dams lowered the cost of power for industrial firms giving the region an industrial boost \citep{Kitchens_2014}.
+The Tennessee Valley Authority was a large scale New Deal program that lowered the cost of power for industrial firms \citep{Kitchens_2014}.
 The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citep{Severnini_2014}.
@@
 
-Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the event study framework by extending the work of \citet{Callaway_SantAnna_2020}.
+Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}.
 This allows for a very common setting in which treatment turns on for different units in different periods.
-I first show how to adjust their methods to control for spatial spillovers in estimation of treatment effects.
-Then, I show how to estimate average spillover effects.
-My paper is the first paper to study estimation of treatment effects in an event-study framework in the presence of spillover effects.
+Their proposed two-stage estimator first estimates group and time fixed-effects using untreated/not-yet-treated observations.
+Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed effects.
+Then these estimated unit and time fixed-effects are subtracted from the observed outcome \emph{in the full sample}.
+The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects.
 
@@
 I find that in this context, since the mortality declines caused by the health centers was due to primary care, spillover effects are near-zero.
-This result shows the importance of accessability concerns when deciding the location of the health centers.
+This result shows the importance of accessability concerns when targeting programs in low-income areas.
 
@@
 % ------------------------------------------------------------------------------
+
+I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
+I contribute to this literature in two ways.
+My paper is the first to consider identification in terms of general potential outcomes.
+Other papers derive results for specific spillover mappings and if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs.
+Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
+
+This paper relates to a literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work.
+See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.} Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
+
+Partial inference allows interference between but not across groups..
+\citep{Hudgens_Halloran_2008,Vazquez-Bare_2019}.
+This allows for seperate identification of treatment and spillover effect in experimental settings.
+My paper ...
+
+\citet{Savje_Aronow_Hudgens_2021} show what is identified under no assumptions of interference.
+My paper shows under a different set of assumptions what is estimated and how to estimate effects seperately ...
 
@@
 I extend this work by focusing on difference-in-differences estimation in non-experimental settings.
-\citet{Savje_Aronow_Hudgens_2019} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
+\citet{Savje_Aronow_Hudgens_2021} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
 My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
@@
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
-Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Callaway_SantAnna_2020}.
+Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021}.
 I apply these methods in evaluating spillover effects of U.S.
-Community Health Centers in Section \ref{sec:chc}.
+Community Health Centers in Subsection \ref{sec:chc}.
 
@@
 This section will present a potential outcome framework that formalizes spatial spillovers.
-Following the canonical difference-in-differences framework, there are T periods and treatment turns on for all treated units at some period $t_0$ and remain on afterwards.\footnote{This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Potential outcomes, denoted $Y_{i,t}(D_i, h(\vec{D},i))$, for unit $i$ at time $t$ are a function of own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
-The function $h(\vec{D}, i)$ is referred to as an `exposure mapping' and is a non-negative scalar- or vector- valued function.
-The exposure mapping measures the intensity at which unit $i$ is affected by spatial spillovers.
-When unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$.
+Following the canonical difference-in-differences framework, I observe a panel of units for periods $t \in \{0,1\}$ and treatment turns on between periods for some of the units.\footnote{This can be extended to multiple periods by replacing $Y_{i0}$ and $Y_{i1}$ throughout with pre- and post- sample averages of $Y_{it}$.
+This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Let $D_{i}$ be an indicator equal to one if unit $i$ is treated and therefore treatment status is defined as $D_{it} = D_{i} * \one(t = 1)$.
+
+\begin{assumption}[Random Sampling]\label{assumption:random}
+    $\{ Y_{i0}, Y_{i1}, D_{i} \}_{i = 1}^{n}$ are independent and identically distributed sample of panel data.
+\end{assumption}
+
+Assumption (\ref{assumption:random}) allows me to consider observations as coming from a larger population (sometimes called a superpopulation).
+Later, when discussing inference, I will relax this assumption to account for spatial correlation between observations, but identification does not rely on independence.
+As an alternative, inference could come from a design-based perspective following \citet{Athey_Imbens_2021}.
+
+Potential outcomes, denoted $Y_{it}(D_i, h(\vec{D},i))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+The non-negative scalar- or vector-valued function $h(\vec{D}, i)$ is referred to as an `exposure mapping'.
+This setup follows \citet{Vazquez-Bare_2019} who studies identification of spillover effects under an experimental setting.\footnote{Note that throughout, expectations and inference are conditional on the vector of exposure mappings.
+In design-based settings, the distribution of exposure mappings is known so expectations can be taken without conditioning on the vector of exposure mappings.
+See \citet{Savje_Aronow_Hudgens_2021} for discussion estimation and inference when the treatment design is known.}
+
+The exposure mapping measures the intensity at which unit $i$ is affected by spillovers.
+Without restrictions on the exposure mapping, nonparametric identification of treatment effects will be impossible.
+The main assumption for identification, as will be formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$ .
+In the world of no spillovers, that is $h(\vec{D}, i) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.
 The exposure mapping formalizes the SUTVA violation by summarizing how outcomes are affected by other unit's treatment assignment.
-To help better understand the exposure mapping function, I give three examples that are commonly used in the literature.
+
+The identification results of this paper do not require parameterization of the exposure mapping.
+However, to help better understand the exposure mapping, I give three examples that are commonly used in the literature.
 
 \begin{example}
-    First, $h(\vec{D}, i)$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.
+    $h(\vec{D}, i)$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.
 In this case \begin{equation}\label{eq:h_within}
-        h(\vec{D}, i) = \max_{i \neq j} D_j * \one[ d(i,j) < \bar{d} ] 
+        h(\vec{D}, i) = \max_{j \neq i} D_j * \one[ d(i,j) < \bar{d} ] 
     \end{equation}
@@
     Second, $h(\vec{D}, i)$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
-        h(\vec{D}, i) = \sum_{j} D_j * \one[ d(i,j) < \bar{d} ].
+        h(\vec{D}, i) = \sum_{j \neq i} D_j * \one[ d(i,j) < \bar{d} ].
     \end{equation}
     This exposure mapping is no longer binary, so the intensity of spillovers is additive in the number of nearby units treated.
-In the context of large store openings, this exposure mapping captures the additive nature of agglomeration economies.
+In the context of wholesale store openings, this exposure mapping captures the additive nature of agglomeration economies.
 As more nearby counties receive new stores, the force of agglomeration and therefore the spillover effect increases (e.g.
@@
 
-After chosing an exposure mapping that makes sense in the economic context, a researcher must also specify the functional form of the potential outcomes.
-Typically, the exposure mapping enters into the regression linearly and potentially the coefficient is allowed to differ by treatment status to reflect that spillovers on control and treated units can be different phenomenon.
-
-% The results of this paper allows estimation and controlling for spillovers without needing to know the functional form of the exposure mapping. 
-% TODO: Finish
-
-% ------------------------------------------------------------------------------
-\subsection{Spatial Spillovers}
-% ------------------------------------------------------------------------------
-
-With the potential outcomes defined, I define `spillover effects' as: \[
-    Y_{i,t}(D_i, h(\vec{D}, i)) - Y_{i,t}(D_i, \vec{0}).
-\] 
-The spillover effect measures the difference in potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
-This effect can differ for either treated or control units as the magnitude or even the nature of spillovers might differ between treated and untreated units.
-Then, the average spillover effect onto control/treated units averages over potential heterogeneity in the effect size of spillovers and over heterogeneity in exposure intensity $h(\vec{D}, i)$: \[
-    \tau_{\text{spill,control}} \equiv \expec{Y_{i,t}(D, h(\vec{D}, i)) - Y_{i,t}(D, \vec{0}) \ \vert \ D_i = D}.
-\]
-To emphasize, the average spillover effect onto conrol/treated units averages over each unit's exposure mapping which can be heterogeneous across units.
-For example, spillover effects can decay over distance as in Equation (\ref{eq:h_decay}) and the average spillover effect averages across different exposure intensities.
-
-It is important to clarify what I am assuming is the estimand of interest researchers would like to estimate when using difference-in-differences because there are multiple potential estimands defined in the literature.
-I assume that what the `average treatment effect' is trying to measure in this context is what I will call the `direct effect of treatment': \[
-    \tau_{\text{direct}} = \expec{Y_{i,t}(1, \vec{0}) - Y_{i,t}(0, \vec{0}) \ \vert \ D_i = 1},
-\] 
-which measures the effect of being treated in the absence of exposure to spillovers.
-
-My definition of the direct effect of treatment differs from \citet{Savje_Aronow_Hudgens_2019} where they define the average treatment effect as \[ 
-    \expec{Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(0, h(\vec{D}, i)) \ \vert \ D_i = 1},
-\] 
-where the expectation is over individuals and over different levels of exposures.
-The difference between their treatment effect and mine becomes more clear by adding and subtracting terms and rearranging:
-\begin{align*}
-    &Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(0, h(\vec{D}, i)) \\
-    &\quad\quad = Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(1, 0) + Y_{i,t}(1, 0) - Y_{i,t}(0,0) + Y_{i,t}(0,0) - Y_{i,t}(0, h(\vec{D}, i)) \\
-    &\quad\quad = \underbrace{Y_{i,t}(1, 0) - Y_{i,t}(0,0)}_{\text{Direct Effect}} + \underbrace{Y_{i,t}(1, h(\vec{D}, i)) - Y_{i,t}(1, 0)}_{\text{Spillover on Treated}} - \underbrace{(Y_{i,t}(0, h(\vec{D}, i)) - Y_{i,t}(0,0))}_{\text{Spillover on Control}}
-\end{align*}
-The individual treatment effect \citet{Savje_Aronow_Hudgens_2019} use is the direct effect of treatment plus the difference between spillover on treated units and spillover on control units.
-
-I prefer my definition of the direct effect because it allows for seperate identification of the direct effect of treatment and the spillover effects themselves.
-The alternative estimand averages over exposure intensities and therefore is difficult to be used by a policy maker in a particular location.
-That is, a county deciding whether to implement a policy will want to consider the treatment effect plus the difference in spillover effects at \textit{a particular} exposure intensity.
-The estimand proposed by \citet{Savje_Aronow_Hudgens_2019} returns the average of spillovers across levels of exposure and can not be used to predict spillovers at specific exposure intensities while my preferred method of identifying the three effects seperately can.
-Estimates of the direct effect and spillover effect can be later combined to estimate the average treatment effect as defined by \citet{Savje_Aronow_Hudgens_2019}.
-
-% ------------------------------------------------------------------------------
-\subsection{Bias in Difference-in-Differences Estimation}
-% ------------------------------------------------------------------------------
-
-In this section, I identify the two sources of bias in difference-in-differences estimation of the direct effect of treatment.
-Researchers typically estimate the canonical two-way fixed effects model,
-\begin{equation}\label{eq:twfe}    
-    y_{i,t} = \tau D_{i,t} + \mu_i + \mu_t + \epsilon_{i,t},
-\end{equation}
-where $D_{i,t} = D_i \one(t = 1)$.
-The estimator $\hat{\tau}$ is a biased estimate for $\tau_{\text{direct}}$ in the presence of spillovers.
-To show this, I first present the equivalent to the parallel counterfactual trends assumption in the context of the new potential outcome framework.
-
+Often times, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers in a way similar to the above examples.
+Estimation in this case will rely on the functional form assumptions made by researchers.
+This paper will take an alternative approach to identification and estimation which will allow for estimation of treatment effects without requiring direct knowledge of the functional form of the exposure mapping/potential outcomes.
+
+In particular, I will redefine the standard difference-in-differences identifying assumptions in the context of the new potential outcome framework.
+First, I assume that units do not adjust there actions in period $0$ to knowledge of future treatment  and therefore:
+\begin{assumption}[No Anticipation]\label{assumption:no-anticipation}
+    $Y_{i0}(D, h) = Y_{i0}(0,0)$ for all values of $D$ and $h$.
+\end{assumption}
+Second, I formalize the parallel counterfactual trends assumption as follows:
 \begin{assumption}[Parallel Counterfactual Trends]\label{assumption:parallel}
-    \[ 
-        \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \ \vert \ D_i = 1 } = 
-        \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \ \vert \ D_i = 0 },
-    \]
-    where $\bar{Y}_{i,W}$ is the average outcome in either the post- or pre-periods.
+    Counterfactual trends do not depend on $D_i$:
+    \[ 
+        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1 } = 
+        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0 }
+    \]
 \end{assumption}
@@
 
-Given that Assumption \ref{assumption:parallel} holds, the estimate $\hat{\tau}$ from (\ref{eq:twfe}) can be decomposed as the direct effect and the two sources of spillover bias.
-The proof is given in Appendix \ref{sec:proofs}.
-
-\begin{proposition}[Decomposition of Difference-in-Differences Estimate]\label{thm:bias}\ \\    
-    If Assumption \ref{assumption:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe}) is
+% ------------------------------------------------------------------------------
+\subsection{Treatment and Spillover Effects}
+% ------------------------------------------------------------------------------
+
+In setups without spillovers, treatment effects for an individual unit is well defined as $\tau_i \equiv Y_{i1}(1) - Y_{i1}(0)$, i.e.
+the effect of turning on treatment for a unit and the above two assumptions would lead to identification of the average effect by the traditional difference-in-differences estimator.
+In the presence of spillovers, there are multiple treatment effects that can be defined in this setting.
+This subsection will define them and discuss their relative advantages/disadvantages.
+
+The natural analogue to the above treatment effect which I will label the `switching effect' is:
+\[
+    \tau_{i, switch}(h(\vec{D}, i)) \equiv Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i)).
+\] 
+This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant.
+This treatment effect is policy relevant as it summarizes what would happen if a `local' policy makers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).
+It is important to note that the switching effect can depend on the level of exposure.
+For instance, consider the construction of libraries in towns.
+The effect of library construction in a town that is far away from any other library ($h = \vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h(\vec{D},i)$.
+Since the size of the switching effect depends on a units exposure level, we will consider an average switching effect at each value of exposure,
+\[
+    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i))}{D_i = 1, h(\vec{D}, i) = h}.
+\]
+
+% Work by \citet{Savje_Aronow_Hudgens_2021} suggests averaging the switching effect over exposure levels,
+%\[ 
+%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h(\vec{D},i)) \vert D_i = 1}.
+%\] 
+%This estimand averages the switching effect over all treated units and hence average over the distribution of exposure.
+Any given unit $i$ trying to understand the effect of switching on a policy can't use this parameter as it averages over exposures different than theirs.
+More, this parameter can not be identified without further assumptions as the distribution of exposure mappings is not necessarily the same for control units as treated units.\footnote{\citet{Savje_Aronow_Hudgens_2021} discuss conditions on the distribution of exposure mappings that can lead to asymptotic identification of the average switching effect.
+However it relies on design-based assumptions that do not apply here.}
+
+There is a particular switching effect at zero exposure that I call the `direct effect' of treatment, 
+\[
+    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h(\vec{D},i) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
+\] 
+which measures the average effect of being treated \emph{among unexposed treated units}.
+Specifying this particular switching effect will prove useful when discussing identification as it requires fewer assumptions than switching effects at other exposure levels.
+As discussed above, this is not necessarily a policy-relevant parameter for every unit if the switching effect has different magnitudes at different levels of exposure.
+
+The second policy-relevant parameter is the `total effect of treatment': 
+\[
+    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
+\] 
+As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h(\vec{D}, i)$ simultaneously.
+This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$.
+This treatment effect is helpful for `national' policy makers in order to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.
+
+To better understand how the above treatment effects are connected, it will be useful to formalize a unit's `spillover effect' as:
+\[
+    \tau_{i, \text{spill}}(D_i, h(\vec{D},i)) \equiv Y_{i1}(D_i, h(\vec{D}, i)) - Y_{i1}(D_i, \vec{0}).
+\] 
+The spillover effect measures the difference in potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
+This effect can differ for either treated or control units as the magnitude or even the nature of spillovers might differ between treated and untreated units.
+That is $\tau_{i, \text{spill}}(1)$ does not necessarily equal $\tau_{i, \text{spill}}(0)$.
+We can then average over treated/control units to form average spillover effects:
+\[
+    \tau_{\text{spill}}(D) \equiv \expec{Y_{i1}(D, h(\vec{D}, i)) - Y_{i1}(D, \vec{0}) \ \vert \ D_i = D},
+\]
+where the expectation is over individuals and hence over different exposures.
+This will give us the average spillover effect among \emph{all} treated/control units regardless if they receive any spillover effects.
+It is often also of interest to estimate the average spillover effects on subsets of units (e.g.
+all units experiencing non-zero exposure).
+Estimation of spillover effects will be discussed in Section \ref{sec:spill}.
+
+With spillover effects formally defined, the difference between the proposed estimands become more clear by the following algebraic identity:
 \begin{align*}
-        \mathbb{E}[\hat{\tau}] &= \underbrace{\expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 1 } - \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 0 }}_{\text{Difference-in-Differences}} \\
-        &= 
-        \expec{\bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 1} + \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Post}(1, \vec{0}) \mid D_i = 1} \\
-        &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 0} \\
-        &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}}
+    &\overbrace{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i))}^{\text{Switching Effect}} = \\
+    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect}} \ - \ \underbrace{(Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0,0))}_{\text{Spillover on Control}}
+\end{align*}
+
+From this identity, we see that whenever $\tau_{i,spill}(D_i, h(\vec{D}_i))$ does not depend on treatment status $D_i$, then we have that the switching effect is constant and equal to the direct effect.
+In this situation, the simpler identification assumptions behind the direct effect will identify the switching effect at all exposure levels.
+For example, if treatment is a factory opening and the spillover effect on employment is due to increased spending on services, then it could be reasonable to assume the effect does not depend on treatment status and hence the switching effect is constant and equal to the direct effect of changing treatment status.
+
+However, the spillover effects can sometimes differ depending on treatment status.
+Continuing the above example, perhaps control units could experience negative employment shocks from a nearby country opening a factory if workers relocate to the treated areas resulting in a negative spillover effect on control units.
+Other treated units could, for instance, experience positive spillover effects due to agglomeration economies.
+When it is the case that spillover effects depend on treatment status, the switching effect can be thought of as two seperate effects.
+First, the unit is affected by its own treatment status as summarized by the direct effect.
+Second, the unit changes from experiencing spillover effects as a control unit to experiencing spillover effects as a treated unit.
+
+% ------------------------------------------------------------------------------
+\subsection{What Does Difference-in-Differences Estimate?}
+% ------------------------------------------------------------------------------
+
+With treatment effects properly defined, I will first derive what the standard difference-in-differences estimand identifies under parallel trends assumption.
+
+\begin{proposition}[Decomposition of Difference-in-Differences Estimand]\label{thm:bias}\ \\    
+    If assumptions (\ref{assumption:random}), (\ref{assumption:no-anticipation}) and \nameref{assumption:parallel} hold, the population difference-in-differences estimand can be decomposed as follows:
+    \begin{align}
+        &\underbrace{\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0 }}_{\text{Difference-in-Differences}} \label{eq:did}\\ 
+        &\quad\quad= \tau_{\text{direct}} + \tau_{\text{spill}}(1) - \tau_{\text{spill}}(0) \\ 
+        &\quad\quad= \tau_{\text{total}} - \tau_{\text{spill}}(0)
+    \end{align}
+\end{proposition}
+
+The proof is given in Appendix \ref{sec:proofs}, but the intuition behind the additional terms is as follows.
+First, the change in outcomes among treated units combines the direct effect of treatment with the spillover effects caused by nearby treated units.
+Therefore the first difference adds the average spillover effect onto the treated units, $\tau_{\text{spill}}(1)$.
+Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units.
+Since $\hat{\tau}$ is found by subtracting the change in outcomes among the control units, we subtract the average spillover effect onto the control, $\tau_{\text{spill}}(0)$.
+
+Researchers typically estimate the canonical two-way fixed effects model, 
+\begin{equation}\label{eq:twfe}    
+    y_{it} = \tau D_{it} + \mu_i + \lambda_t + \epsilon_{it}.
+\end{equation}
+The estimator $\hat{\tau}$, which is well understood to be the sample analog of (\ref{eq:did}), is therefore a biased estimate for $\tau_{\text{direct}}$ and $\tau_{\text{total}}$ in the presence of spillovers.
+In particular, if a researcher were to estimate a difference-in-differences model and reported $\hat{\tau}$ as an estimate of the total effect, their estimate would be biased in the presence of spillover effects on control units.
+If spillover effects are of the same sign as the total effect, then estimates would be attenuated towards zero.
+On the other hand, if spillovers are the opposite sign, then results would increase in magnitude.
+
+% ------------------------------------------------------------------------------
+\subsection{Identification of Treatment Effects}\label{sec:remove_bias}
+% ------------------------------------------------------------------------------
+
+The following subsection will talk about identification of treatment effects and present corresponding estimators for each effect.
+
+% ------------------------------------------------------------------------------
+\subsubsection{Switching Effect}
+% ------------------------------------------------------------------------------
+
+It is difficult to identify the switching effect in general as identifying the unobserved counterfactual outcome $Y_{i1}(0, h(\vec{D}, i))$ requires knowledge of which control units have same level of exposure.
+The reason for this can be seen by rewriting this in terms of a difference-in-differences style estimand:
+\begin{align*}
+    \tau_{\text{switch}}(\vec{h}) &= \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h(\vec{D}, i) = \vec{h} \right] \\ 
+    &\quad\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h(\vec{D}, i) = \vec{h} \right].
+\end{align*}
+Writing it in this way highlights the two problems in estimating the second term.
+First, this requires knowledge of the unobserved exposure mapping to be correctly specified in order to identify control units with $h(\vec{D}, i) = h$.
+More, this estimand requires a more demanding parallel trends assumption.\footnote{This problem is similar to those highlighted by \citet{Callaway_Goodman-Bacon_SantAnna_2021} for difference-in-differences with continuous treatment.}
+
+\begin{assumption}[Switching Effect Parallel Trends]\label{assumption:parallel-switching}
+    For a given exposure, $\vec{h}$, counterfactual trends do not depend on $D_i$:
+    \[ 
+        \expec{Y_{i1}(0, \vec{h}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1, h(\vec{D}, i) = \vec{h} } = 
+        \expec{Y_{i1}(0, \vec{h}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0, h(\vec{D}, i) = \vec{h} }
+    \]
+\end{assumption}
+
+This assumption is equivalent to \nameref{assumption:parallel}) and an additional assumption that spillover effects being equal between control and treated units that experience exposure $\vec{h}$.
+Under this assumption, the switching effect can be identified.
+
+\begin{proposition}[Identification of the Switching Effect]
+    For a given exposure, $\vec{h}$, if assumption (\ref{assumption:random}), (\ref{assumption:no-anticipation}), and \nameref{assumption:parallel-switching} holds, then
+
+    \begin{align*}
+        \tau_{\text{switch}}(\vec{h}) &= \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h(\vec{D}, i) = \vec{h} \right] \\ 
+        &\quad\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 0, h(\vec{D}, i) = \vec{h} \right].
     \end{align*}
@@
 
-The intuition behind the biases are as follows.
-First, the change in outcomes among treated units combines the direct effect of treatment with the spillover effects caused by nearby treated units.
-Therefore the first difference adds the average spillover effect onto the treated units, $\tau_{\text{spill,treated}}$.
-Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units.
-Since $\hat{\tau}$ is found by subtracting the change in outcomes among the control units, we subtract the average spillover effect onto the control, $\tau_{\text{spill,control}}$.
-
-Readers that are judging estimates in the presence of spillovers can use the following heuristics to sign the bias.
-If they suspect spillovers onto control units, the bias is the opposite sign of the spillover.
-If they suspect spillovers onto treated units, the bias is the same sign of the spillover.
-The overall bias is the sum of the two.
-
-% ------------------------------------------------------------------------------
-\section{Estimating $2\times 2$ Difference-in-Differences with Spillovers}
-\label{sec:estimation}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\subsection{Unbiased Estimation of Direct Effect}\label{sec:remove_bias}
-% ------------------------------------------------------------------------------
-
-Under mild conditions, it is possible to control directly in a regression for the two sources of spillover effects and unbiasedly estimate the direct effect of treatment.
-A pair of indicators that contains all control/treated units respectively will estimate the average spillover effect on control/treated units and remove these sources of bias.
-The assumptions required to do this is that the researcher needs to be able to identify the maximum distance for which units are affected by spillovers and that there be unexposed units remaining.
+The switching effect can be estimated by a difference-in-differences estimator on the subsample of units with exposure $\vec{h}$.
+However, this approach relies on correct specification of the exposure mapping which is a difficult assumption to maintain.
+Researchers may be tempted to introduce the parameterized exposure mapping linearly in order to `compare individuals at the same level $\vec{h}$'.
+However, this assumes additive seperatability between the treatment dummy and the exposure mapping.
+Additive seperatability would imply treatment effects don't depend on exposure level, i.e.
+the switching effect is constant across $\vec{h}$.
+
+\subsubsection{Direct and Total Effects}
+
+To identify the direct and total effects, additional assumptions on the nature of spillover effects is needed.
+In particular, I will formalize the idea that spillovers are `local' in that units are only affected by treatment if they are near treatment.
+For example, if treatment has to be accessed in person, then it is natural that further away places are not affected by treatment.
+However this example may fail under general equilibrium shocks that do not necessarily decay over distance.
 
@@
     (ii) There are treated and control units, $i$, such that $\min_{j: \ D_j = 1} d(i,j) > \bar{d}$.
-
 \end{assumption}
 
-Part (i) of Assumption (\ref{assumption:local}) requires that spillovers are `local' in that units are no longer exposed to spillovers after some maximum distance $\bar{d}$.
-Part (ii) of Assumption (\ref{assumption:local}) requires that there exists control units with no exposure in order to estimate the counterfactual trend and treated units with no exposure in order to estimate the direct effect.
-Let $S_{i}= \one(\min_{j: \ D_j = 1} d(i,j) \leq \bar{d})$ be an indicator for being within $\bar{d}$ miles of the closest treated unit after treatment.
-
-In order to remove both sources of bias, we modify the two-way fixed effects model to include this indicator interacted with treatment status:
-
-\begin{equation}\label{eq:twfe_with_ind}    
-    y_{i,t} = \tau D_{i,t} + \tau_{\text{spill,control}} (1-D_{i,t}) S_{i} + \tau_{\text{spill,treated}} D_{i,t} S_{i} +  \mu_i + \mu_t + \epsilon_{i,t}.
-\end{equation}
-
-\begin{proposition}[Unbiased Estimate for Direct Effect]\label{thm:remove_bias}
-    If Assumption \ref{assumption:parallel} holds, the expectation of the estimate $\hat{\tau}$ from (\ref{eq:twfe_with_ind}) is
-    \begin{align*}
-        \expec{\hat{\tau}} &= \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 1, S_{i} = 0 } - \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \ \vert \ D_i = 0, S_{i} = 0 } \\ 
-        &= \tau_{\text{direct}} 
-    \end{align*}
-
-    The expectation of the two spillover effect estimates are 
-    \begin{align*}
-        \expec{\hat{\tau}_{\text{spill,conrol}}} = \expec{ \bar{Y}_{i,Post}(0,h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \ \vert \ D_i = 0, S_i = 1}
-    \end{align*}
-    and 
-    \begin{align*}
-        \expec{\hat{\tau}_{\text{spill,treated}}} = \expec{ \bar{Y}_{i,Post}(1,h(\vec{D}, i)) - \bar{Y}_{i,Post}(1, \vec{0}) \ \vert \ D_i = 1, S_i = 1}
-    \end{align*}
+Part (i) of assumption (\ref{assumption:local}) requires that spillovers are `local' in that units are no longer exposed to spillovers after some maximum distance $\bar{d}$.
+Part (ii) of Assumption (\ref{assumption:local}) requires that there exists control and treated units with no exposure.
+This assumption is far less strict than the identifying assumption for the switching effect in that we only need to identify units with zero exposure and don't need to parameterize the exposure mapping any further.
+For a given $\bar{d}$ that satisfies Assumption (\ref{assumption:local}), let $S_{i}= \one(\min_{j: \ D_j = 1} d(i,j) \leq \bar{d})$ be an indicator for being within $\bar{d}$ miles of the closest treated unit.
+
+The intuition behind identifying the direct effect seperately from the spillover effects requires that we use control units experiencing no spillover effects to identify the counterfactual trend and use treated units experiencing no spillover effects to identify the direct effect.
+Since we are leveraging subgroups of treated and control units, we need a parallel trends assumption for each subgroup:
+
+\begin{assumption}[Direct/Total Effect Parallel Trends]\label{assumption:parallel-mod}
+    Counterfactual trends do not depend on $D_i$ and $S_i$:
+    \[
+        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i, S_i} = 
+        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0})}
+    \]
+\end{assumption}
+
+It is worth remarking on \nameref{assumption:parallel-mod} in terms of applied work.
+Often times, individuals use only a subsample of observations that are close to treated observations in estimating their difference-in-differences model.
+The idea is that close units are more likely to be on similar counterfactual trends than units that are further away.
+The identification result and it's corresponding estimator are formed by using further away units (i.e.
+units with $S_i = 0$).
+In this case, if parallel trends only hold locally, then focusing on further away units fix the spillover bias but increase bias from non-parallel trends.
+
+Note that for identification of the total effect, you only need that the counterfactual trend among \emph{all} treated units is the same as the counterfactual trend among control units with $S_i = 0$ which is implied by \nameref{assumption:parallel-mod}.
+Identification of the direct effect will be average the individual treatment effects \emph{only} for treated units with $S_i = 0$.
+So identification of the average treatment effect among \emph{all} treated units requires a subtle assumption to ensure treatment effect homogeneity.
+
+\begin{assumption}[Direct Effect Does Not Depend on $S_i$]\label{assumption:homogenous-direct}
+    For $s \in \{0, 1\}$,
+    \[
+        \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, S_i = s} = 
+        \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}
+    \]
+\end{assumption}
+
+With these assumptions, we have the following identification result for the direct and total effects:
+
+\begin{proposition}[Identification of Direct and Total Effects]\label{thm:remove_bias}
+    If assumption (\ref{assumption:random}), (\ref{assumption:no-anticipation}), \nameref{assumption:local}, and \nameref{assumption:parallel-mod}) hold, then (i) 
+    \begin{equation}\label{eq:id_total}
+        \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0} = \tau_{\text{total}}
+    \end{equation}
+    and (ii) 
+    \begin{align}\begin{split}\label{eq:id_direct}
+        &\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1, S_{i} = 0 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0 } \\
+        &\quad\quad= \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, S_i = 0}\\
+        &\quad\quad= \tau_{\text{direct}},
+    \end{split}\end{align}
+    where the last equality holds only under assumption (\ref{assumption:homogenous-direct}).
 \end{proposition}
 
-The intuition behind this is that the indicator interacted with treatment status serve as unbiased estimates of the \textit{average} spillover effect onto treated and control units and therefore remove these terms from the direct effect estimate, $\hat{\tau}$.\footnote{The proof uses standard Frisch-Waugh-Lovell style logic on a set of indicator variables and the fact that if $S_{i} = 0$ then $h(\vec{D}, i) = \vec{0}$.
-The derivation follows closely the work of \citet{Clarke_2019}.} This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
-An indicator for being `near' treatment ineracted with treatment status is enough to have an unbiased estimate for the treatment effect.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
+The proof is given in Appendix \ref{sec:proofs}, but the intuition is simple.
+Conditioning on $S_i = 0$ will use only observations with $h(\vec{D}, i) = 0$ which give rise to identification of the direct and total effect.
+This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
+All that is required to identify the direct or total effects is being able to classify which units are considered `near' treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
 For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
 
-A natural question is why wouldn't researchers make the distance really large in order to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$?
-The problem with this is that control units with $S_i = 0$ identify the counterfactual trend and treated units with $S_i = 0$ identify the direct effect.
-Therefore leaving few units with $S_i = 0$ will yield more variable estimates.
-On the other hand, having units that experience spillovers not included in the $S_i$ indicator will leave some bias in the estimate.
-Although, since spillover effects typically will grow weaker over distance, the bias may not be particularly large if distant units are mistakenly treated as if they have zero exposure.
-Therefore there is a bias-variance trade-off in extending the extent of $S_i$ that should be balanced by researchers guided by their particular economic context.
-
-A common approach in the literature is to drop control units adjacent to treated units to avoid the problems of spillovers in identification.
-Proposition \ref{thm:bias} and Assumption \ref{assumption:local} would suggest that this can be effective in removing (at least part of) the average spillover effect on control units.
-However, since researchers do not know how far the spillovers extend there is difficulty in implementing this method effectively.
-On the one hand, removal of too few units will keep some control units that are experiencing spillover effects which would leave the estimated treatment effect biased.
-On the other hand, removing too many units will leave few observations and therefore increase the variance of the estimates.
-There is therefore a bias-variance trade off inherent to this method that can be easily improved by creating an indicator for these units rather than dropping them from the sample.
-In addition to the unnecessary loss of precision induced by this method, the removal of problematic control observations, will not remove spillover effects onto treated units.
-Therefore if treated units are affected by the treatment status of nearby units, then the spillover effect on treated units which would remain as a source of bias.\footnote{Appendix \ref{sec:monte_carlo} contains a set of Monte Carlo simulations that highlight the problems more rigorously.}
-
-The second part of proposition \ref{thm:remove_bias} shows that equation (\ref{eq:twfe_with_ind}) can also be used to estimate average spillover effects.
-The spillover effects themselves are potentially relevant for policy makers.
-For example, if the policy maker cares about treated areas and neighboring areas, then they should consider if the direct effect comes at a cost to nearby areas (negative spillovers) or if the benefits are being undercounted by only considering the treated area (positive spillovers).
-Similarly, a policy maker trying to determine the net benefits for a treated location must consider the direct effect and the spillover effect received by treated units.
-This could vary by location if the size of benefits created by the treatment depend on the number of treated units nearby.
-
-However, the estimates are not trivial to interpret as the ``typical'' magnitude of spillover effects.
-This is because $\hat{\tau}_{\text{spill,control}}$ and $\hat{\tau}_{\text{spill,treat}}$ average spillover effects across all units with $S_i = 1$ which could contain units that experience no spillover effects.
+In order to estimate the direct effect and the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
+However, it will prove advantageous to modify the two-way fixed effects model to estimate the direct or the total effect because it will also allow estimation of spillover effects as well.
+To estimate the total effect, the modified model is given by:
+\begin{equation}\label{eq:twfe_total}    
+    y_{it} = \tau D_{it} + \gamma_{0} (1-D_{it}) S_{i} + \mu_i + \lambda_t + \epsilon_{it}.
+\end{equation}
+
+To estimate the direct effect, the modified model is given by:
+\begin{equation}\label{eq:twfe_direct}    
+    y_{it} = \tau D_{it} + \gamma_0 (1-D_{it}) S_{i} + \gamma_1 D_{it} S_{i} +  \mu_i + \lambda_t + \epsilon_{it}.
+\end{equation}
+From standard regression analysis the estimates of $\hat{\tau}$ from equations (\ref{eq:twfe_direct}) and (\ref{eq:twfe_total}) are sample analogues of (\ref{eq:id_direct}) and (\ref{eq:id_total}).
+
+Since $\hat{\tau}$ is a linear combination of sample averages, inference can be done using large-n asymptotics.
+However, it is important to account for two sources of correlation in the error structure.
+First, errors should be clustered by unit $i$ to allow for correlation between periods.
+Second, since our model is predicated on the fact that nearby places effect one another, we should account for such spatial correlation by allowing for spatial correlations following \citet{Conley_1999}.
+More recent work by \citet{Ferman_2020} show that for large-n asymptotics to be used, the structure of spatial correlation must be limited in that errors are assumed to be uncorrelated after a certain cutoff distance.
+A natural candidate for this cutoff would be $\bar{d}$ used for the creation of $S_i$.
+
+A natural question is why wouldn't researchers make the distance really large in order to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$ or $\tau_{\text{total}}$?
+Equation (\ref{thm:remove_bias}) should make this problem clear.
+Since these estimates rely on averages among units with $S_i = 0$, as $\bar{d}$ increases, the number of units with $S_i = 0$ decreases which yields more variable estimates.
+On the other hand, having units that experience spillovers not included in the $S_i$ indicator will leave some bias in the estimate.\footnote{Although, spillover effects typically will grow weaker over distance and if distant units are mistakenly treated as if they have zero exposure, bias should be small.} Therefore there is a bias-variance trade-off in extending the extent of $S_i$ that should be balanced by researchers guided by their particular economic context.
+
+% ------------------------------------------------------------------------------
+\section{Estimation of Spillover Effects}\label{sec:spill}
+% ------------------------------------------------------------------------------
+
+The estimates of $\gamma_D$ in the modified TWFE models (\ref{eq:twfe_total}) and (\ref{eq:twfe_direct}) do not estimate the corresponding average spillover effects $\tau_{\text{spill}}(D)$ for $D = 0,1$.
+This is because $\hat{\gamma}_D$ average spillover effects across only units with $S_i = 1$:
+\[ 
+    \expec{\hat{\gamma}_0} = \condexpec{\tau_{i, spill}(0)}{ S_i = 1, D_i = 0}, \text{ and}
+\]
+\[ 
+    \expec{\hat{\gamma}_1} = \condexpec{\tau_{i, spill}(1)}{ S_i = 1, D_i = 1}.
+\]
+These estimates average individual spillover effects for all units with $S_i = 1$.
+Since some units with $S_i = 1$ do not have positive exposure, this is not the average spillover effect for units with non-zero exposure either.
 For example, if only units really close to treatment receive spillover effects and $S_i$ contains a lot of units that experience no spillover effects, then $\hat{\tau}_{\text{spill, control}}$ could be estimated near zero even though there are spillover effects.
+
+It is possible to more accurately estimate spillover effects by using a set of concentric ring indicators (e.g 0-20 miles, 20-40 miles and 40-60 miles from the nearest treated unit) instead of a single large ring indicator to more flexibly estimate the spillover effects.
+For example, for the total effect, equation (\ref{eq:twfe_total}) can be modified as
+\begin{equation}\label{eq:twfe_total_rings}    
+    y_{it} = \tau D_{it} + \sum_{i=1}^n (1-D_{it}) \text{Ring}_{i} + \mu_i + \lambda_t + \epsilon_{it},
+\end{equation}
+where $\text{Ring}_i$ is a given ring.
+Similarly, equation (\ref{eq:twfe_direct}) can be modified to include multiple rings.
+Since the set of rings is collinear with a single large ring, the direct and total effects estimate will continue to be identified.
+The estimates for each ring will represent the average of $\tau_{i,spill}$ for all observations within a given distance ring.
+Having estimates of average spillover effects at different distances allows a researcher to better understand the nature of the spillovers.
+
+A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
+The figure displays observations of $Y_{i,Post} - Y_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the $x$-axis and treated units are placed at a zero distance for visualization purposes.
+The example has a counterfactual trend of 2 so any difference from 2 is due to either treatment/spillover effects and the error term.
 
@@
 \begin{figure}[tb!]
-    \caption{Rings Improve Estimation of Spillover Effects}
+    \caption{Comparison of Single vs. Multiple Rings Estimation of Spillover Effects}
     \label{fig:example_rings}
 
-    \begin{subfigure}{\textwidth}
-        \caption{Single Ring}
-        \begin{center}
-            \resizebox{0.8\textwidth}{!}{
-                \includegraphics{../../figures/figure-within_example.pdf}
-            }
-        \end{center}
-
-    \end{subfigure}
-    \begin{subfigure}{\textwidth}
-        \caption{Multiple Rings}
-        \begin{center}
-            \resizebox{0.8\textwidth}{!}{
-                \includegraphics{../../figures/figure-rings_example.pdf}
-            } 
-        \end{center}
-    \end{subfigure}
-
-    \noindent{\footnotesize \textit{Notes:} Panel (a) shows the estimate of a single large ring indicator following equation (\ref{eq:twfe_with_ind}).
-Panel (b) shows a set of concentric ring indicators following equation (\ref{eq:twfe_with_ind}) where $S_{i}$ is replaced with a set of ring indicators.}
+    \includegraphics[width = \textwidth]{../../figures/figure-rings_v_within.pdf}
+
+    {\footnotesize \textit{Notes:} The figure compares estimates of equation (\ref{eq:twfe_total}) with $S_i$ a ring of $(0, 60]$ miles from the nearest treated unit and of equation (\ref{eq:twfe_total_rings}) with rings for $(0,15], (15,30], (30,45], (45, 60]$ miles for a simulated set of data.}
 \end{figure}
 
-An improvement on this is to use a set of concentric ring indicators instead of a single large ring indicator to more flexibly estimate the spillover effects (e.g 0-20 miles, 20-40 miles and 40-60 miles from the nearest treated unit).
-Since the set of rings is collinear with a single large ring, the direct effect estimate retains its unbiased properties, while spillover effects can potentially be estimated more accurately.
-A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
-The figure displays observations of $\bar{Y}_{i,Post} - \bar{Y}_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the x-axis and treated units are placed at a zero distance for visualization purposes.
-The example has a counterfactual trend of 2 so any difference from 2 is due to either treatment/spillover effects and the error term.
 Panel (a) uses a single indicator for being between 0 and 60 miles from treatment and the difference between the bar and the estimated counterfactual trend is the estimated spillover effect which in this case is about 0.6.
 This number masks that units within the first 15 miles have a treatment effect of 1 or larger and units between 40 and 60 miles have 0 spillover effects.
-
 Figure (b) on the other hand uses 4 indicators for every 15 mile interval (0-15, 15-30, 30-45, and 45-60 miles).
@@
 The rings method acts a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to their being units outside of the rings).
-However, precision of estimates would decrease as the number of rings increase and therefore there is a bias-variance trade-off in the number and width of rings.
-\citet{Clarke_2017} proposes a cross-validation technique for optimally choosing the number of rings and their techniques that uses the out-of-sample mean square prediction error as a way to estimate the bias-variance tradeoff.
-Interested readers can see the paper for technical and implementation details.
+However, precision of estimates would decrease as the number of rings increase and therefore there is a bias-variance trade-off in the number and width of rings.\footnote{\citet{Clarke_2017} proposes a cross-validation technique for optimally choosing the number of rings and their techniques that uses the out-of-sample mean square prediction error as a way to estimate the bias-variance tradeoff.
+\citet{Butts_2021} provides a data-driven method to selecting rings under a more strict version of the parallel trends assumption.}
 
@@
 % ------------------------------------------------------------------------------
-\subsection{Monte Carlo Simulations}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\subsubsection{Bias Under Misspecification of Spillovers}
+\section{Application in Place-Based Policy Analysis}
+\label{sec:tva}
+% ------------------------------------------------------------------------------
+
+To illustrate the importance of accounting for spatial spillovers in the estimation of treatment effects, I revisit the analysis of the Tennessee Valley Authority (TVA) in \citet{Kline_Moretti_2014}.
+The TVA program was a large-scale federal investment started in 1934 that focused on construction of dams and transportation canals in an attempt to modernize the Tennessee Valley's economy.
+By the end of WWII, the TVA became the largest single power supplier in the country and significantly lowered the cost of wholesale energy for factories.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.
+The effects on wholseale electricity are discussed in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
+\citet{Kline_Moretti_2014} analyze a range of outcome variables, but for succinctness I use only (the log of) agricultural and manufacturing employment.
+Since the TVA primarily improved manufacturing industries through large-scale electrification, the authors predict that employment will grow in manufacturing and shrink in agricultural as workers switch to higher-paying manufacturing jobs.
+
+The analysis in \citet{Kline_Moretti_2014} begins by comparing changes in county-level outcomes from 1940 to either 1960 (short-run effects) or 2000 (long-run effects) between treated counties in the Authority and control counties outside.
+The primary specification is
+\begin{equation}\label{eq:tva}
+    y_{c, t} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \gamma + (\varepsilon_{c, t} - \varepsilon_{c, 1940}),
+\end{equation}
+where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ is an indicator for being in the post-period, and $y$ is a set of outcome variables (in logs).\footnote{The two-periods difference-in-differences regression is equivalent to a first-difference regression.
+The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is equivalent to a weighted difference-in-differences estimate.
+Their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.} To improve the likelihood of the paralell trends assumption, they run a logistic regression to predict being in the TVA based on their set of control variables $X_{c,1940}$ and keep only observations in the top 75\% of predicted probability.
+The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
+\citet{Kline_Moretti_2014} estimate (\ref{eq:tva}) to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
+However, their point estimates compare, in part, changes in outcomes in TVA counties with changes in outcomes for neighboring counties that likely were impacted by the large-scale program.
+
+In the paper, the authors discuss the nature of spillovers that can occur.
+For agriculture employment, the authors claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
+Hence they predict a negative spillover.
+For manufacturing, the sign is ambiguous.
+There could be positive spillovers if electrification brought cheap power and agglomeration economies to the neighboring areas.
+However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.
+My methodology will allow me to empirically test these predictions in the data and remove their bias from the treatment effect estimates.
+
+By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
+The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this.
+Therefore, bias in their estimate will likely remain even after dropping contiguous counties.
+The estimation strategy I present keeps the observations near the TVA while controlling for spillover effects in a more rigorous manner.
+
+% Figure: TVA Effective Sample and Spillover Variables
+\begin{figure}[tb!]
+    \caption{TVA Effective Sample and Spillover Variables}
+    \label{fig:tva_sample}
+
+    {\centering
+        \resizebox{\textwidth}{!}{
+            \includegraphics{../../figures/figure-tva-sample.pdf}
+        } 
+    }
+    {\footnotesize \textit{Notes:} The above figure plots all the counties used in the estimation.
+Counties that fall within the distance intervals $\{ (0, 50], (50, 100], (100, 150], (150, 200] \}$ measured in miles are colored by their respective bin.}
+\end{figure}
+
+I extend their analysis to control for spatial spillovers in the difference-in-differences specification.
+To parametrize the exposure mapping, I use a set of rings as described in Section \ref{sec:remove_bias}.
+Specifically,
+the specification with spillovers is given as follows:  
+\begin{equation}\label{eq:tva_spillover}
+    y_{i, t} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, t} - \varepsilon_{i, 1940}),
+\end{equation} 
+where $\text{Dist} = \{(0, 50], (50, 100], (100, 150], (150, 200]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority and $t \in \{1960, 2000\}$.
+Figure \ref{fig:tva_sample} displays the four spillover variables by filling in each distance bin in a different color.
+The coefficients $\delta_d$ estimate the average spillover effect onto control units for each of these distance bins.
+From proposition \ref{thm:remove_bias}, $\hat{\tau}$ will be an unbiased estimate for the `local' effect so long as spillovers do not occur past 200 miles from the TVA.
+
+The results of the long-run analysis from 1940 to 2000 are presented in Panel A Table \ref{tab:tva}.
+The first column lists which dependent variable (measured in logs) was used in the row.
+The following columns contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
+The point estimates can be interpreted as decadel growth rates in outcomes.
+The column labeled difference-in-differences uses an ordinary least squares estimator for the specification without spillovers, equation (\ref{eq:tva}).
+This estimate finds a decline in agricultural employment of about $5.1\%$ per decade and an increase in manufacturing employment of about $5.6\%$ per decade.
+
+% Table: Effects of Tennessee Valley Authority on Decadel Growth
+\begin{table}[!tb]
+    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
+    \label{tab:tva}
+    \renewcommand{\arraystretch}{1.1}
+
+    \begin{adjustbox}{width = \textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} l c@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
+                % Head
+                \toprule
+
+                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{5}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
+                \cmidrule{2-2} \cmidrule{3-7}
+                & & & TVA between & TVA between & TVA between & TVA between \\ 
+                & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. & 150-200 mi. \\ 
+                \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\
+
+                % Body
+                \toprule
+                \multicolumn{7}{l}{\textbf{Panel A:} 1940-2000} \\
+                \midrule
+
+                \input{../../tables/tva_replication.tex}
+
+                \\ \toprule
+                \multicolumn{7}{l}{\textbf{Panel B:} 1940-1960} \\
+                \midrule
+
+                \input{../../tables/tva_replication_short.tex}
+
+                \\ \bottomrule
+            \end{tabular}
+
+            % Notes 
+            \begin{tablenotes}\footnotesize
+                \item \textit{Notes.} Each row corresponds to an outcome variable.
+Each cell is the point estimate and the standard error for the variable described in the column title.
+All standard errors are Conley standard errors with a correlation cutoff of 200 miles following \citet{Conley_1999}.
+The column labeled `Diff-in-Diff' estimates (\ref{eq:tva}) by OLS and is similar to the estimate reported in \citet{Kline_Moretti_2014}.
+The final four columns labeled `Diff-in-Diff with Spillovers' are estimates from (\ref{eq:tva_spillover}).
+
+                \item $^{*} p< 0.1$; $^{**} p < 0.05$; $^{***} p < 0.01$.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
+Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and and columns (3)-(6) contain point estimates of the spillover effects $\delta_d$.
+For agricultural employment, the point estimates show there was a decline in agriculture employment in control units near the Authority.
+For control units between 0 and 50 miles, column (4) indicates a decline in agricultural employment of $3.7\%$ per decade.
+Between 50 and 100 miles the point estimate is $-1.6\%$ per decade, between 100 and 150 miles the point estimate is $-3\%$ per decade, and between 150 and 2000 miles the point estimate is $-1.6\%$ per decade.
+This is likely due to the fact that higher paying manufacturing jobs within the Authority drew farm-worker migrants from nearby counties.
+Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
+The new point estimate indicates a decline of agricultural employment of about $7.4\%$ per decade compared to $5.1\%$ in the standard difference-in-difference specification.
+
+For manufacturing, our point estimates for spillovers are consistently negative, though imprecisely estimated in some columns.
+The spillover estimates suggest that neighboring counties experienced potentially negative spillover effects in the long-run.
+Since there are negative spillover effects present, the new point estimate in column (2) of $3.5\%$ is significantly smaller than the original estimate of $5.6\%$.
+The spillover estimates are evidence that in the long-run, urban shadow forces dominate the benefits of urban access.
+As you move away from the Tennessee Valley, the point estimates become more negative which suggest that the benefits of urban access vanish over distance faster than the costs of urban shadow.
+
+To see how spillover effects from a large-scale place-based policy develop over time, Panel B in Table \ref{tab:tva} presents results for the effects of the Tennessee Valley in the short-run using outcome data in 1960.
+Unlike in the long-run, areas near the Tennessee Valley did not experience significant declines in agricultural employment in the short-run.
+Since our long-run analysis finds significant increases in high paying manufacturing employment in the Tennessee Valley, this result is consistent with long-run migration costs being lower than short-run costs.
+
+For manufacturing, there are potentially positive increases in manufacturing employment within 100 miles of the Tennessee Valley authority and near zero effects between 100 and 200 miles.
+In the short-run, it appears that the effects of urban access and the cheap wholesale electricity dominated the effects of urban shadow.
+The effect of urban shadows can potentially be smaller in the short-run if operating firms are unlikely to relocate.
+Long-run effects can be larger as entrant firms change their location decision and operating firms are slowly replaced which is what the long-run spillover effect estimates suggest.
+
+These results show that including spillovers in the estimation of direct treatment effects is potentially important and can lead to \emph{significant} differences in treatment effect estimates.
+Analysis of place-based policies that do not account for the fact that treatment effects can spillover beyond the borders of treated areas can potentially be biased.
+More, the spillover effects caused by place-based policies change over time as frictions can create delays in reoptimizing behavior.
+
+% ------------------------------------------------------------------------------
+\subsection{Identification Strategies in Place-Based Policy Analysis}
+% ------------------------------------------------------------------------------
+
+More generally, my framework provides important insights into identification strategies when analysizing the effects of place-based policies.
+There are two ways I contribute.
+First, \citet{Baum-Snow_Ferreira_2015} recognize the problem of spatial spillovers causing problems in identification and point to aggregation of units as a way to alleviate to the problem (e.g.
+aggregating census tracts to metropolitan areas).
+However, this approach collapses the three seperate effects which might each be of interest into a singular aggregate effect.
+I have shown that all three effects of place-based policies can be estimated under very general assumptions about the spillovers.
+Therefore, the methods propose simple ways to estimate treatment effects with non-aggregated data.
+
+Second, my framework provides insight for different identification strategies often used in the literature.
+Since place-based policies are targeted to specific distressed areas, comparison units are often hard to find.
+Researchers have developed many identification strategies to find comparison units that are facetimesimilar in terms of unobservables.
+First, researchers use border discontinuities to compare treated units to units just on the otehr side of the border.
+Other times, researchers compare approved applicants to narrowly rejected applicants.
+Both strategies aim to balance unobservables between treated and control units.
+A key difference in these identification strategies is the distance comparison units are from the treated area and therefore the former is more prone to bias due to spillovers than the latter.
+
+For example, consider the analysis of the effects of federal Empowerment Zones.
+The federal Empowerment Zones are specially designated areas in high-unemployment areas.
+The program gives businesses located in the zone tax incentives and the goal of the program is to reduce unemployment and poverty.
+In the literature, there are a set of conflicting results with some papers suggesting that the Empowerment Zones do indeed reduce poverty rates and others finding near-zero effects.\footnote{See Table 1 of \citet{Neumark_Young_2019} for a summary of the various treatment effect estimates in the literature.}
+
+\citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program.
+The rejected tracts are not typically geographically near accepted Empowerment Zones and they find large significant reductions in poverty rates.
+Meanwhile, \citet{Neumark_Kolko_2010} compare census tracts in Empowerment Zones to census tracts within 1,000 feet of the Zone.
+These control counties are likely the ones that experience the largest spillover effects and they find near-zero effects on poverty.
+
+My framework can reconcile both of these results.
+If census tracts just outside the Empowerment Zones also benefit from the policy, then the estimates of \citet{Neumark_Kolko_2010} are attenuated towards zero.
+These two identification strategies of using rejected applicants or using bordering units as the control group are very common in the urban literature more generally \citep{Baum-Snow_Ferreira_2015}.
+My paper suggests that the former is the preferred strategy if spillovers occur onto nearby control units.
+Identification strategies that rely on geographically close control units as having similar unobservables should be used cautiously.
+If treatment effects spillover treatment border, then estimated treatment effects can be biased.
+
+% ------------------------------------------------------------------------------
+\section{Estimating Event Study with Spillovers}
+\label{sec:event_study}
+% ------------------------------------------------------------------------------
+
+The intuition from how spillovers cause biases in estimates of the direct effect of treatment extend into the setting where there is staggered adoption in treatment.
+When treatment turns on for different units at different times, two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
+I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias term(s) from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
+However, since weights on some of the $2 \times 2$ estimates can be negative, the sign of the spillover effects do not determine the sign of the weighted average of the spillover effects.
+This makes the bias from spillovers much more difficult to sign.
+
+In order to estimate treatment effects in the presence of spatial spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} while incorporating spillovers directly into estimation.
+I assume I observe an independent and identically distributed panel for units $i$ and periods $t$.
+The imputation-based method relies on a model-based assumption for untreated/unexposed units to formalize parallel trends:
+\begin{assumption}[Parallel Counterfactual Trends (Staggered)]\label{assumption:parallel_staggered}
+    For all units and all periods, the untreated and unexposed outcome is given by
+    \begin{equation}\label{eq:y0_staggered}
+        Y_{it}(0, \vec{0}) = \mu_i + \lambda_t + \varepsilon_{it},
+    \end{equation}
+    where $\expec{\varepsilon_{it}} = 0$, $\mu_i$ and $\lambda_t$ are non-stochastic unit and time fixed effects.
+\end{assumption}
+This formalizes parallel trend by imposing that there is a common time-trend in the absence of treatment, $\lambda_t$.
+Note that this does not impose any structure on the effects of treatment and exposure $(D_{it}, h(\vec{D},i))$.
+I also assume that units do not have any anticipatory effects before treatment starts:
+\begin{assumption}[No Anticipation (Staggered)]\label{assumption:no-anticipation_staggered}
+    For all observations with $D_{it} = 0$ and $h(\vec{D}, i) = 0$, $Y_{it}(D, \vec{h}) = Y_{it}(0,0)$ for all values of $D$ and $\vec{h}$.
+\end{assumption}
+
+With a model for $Y_{it}(0, \vec{0})$, treatment effects for individual $i$ and time $t$ under treatment status $D_{it}$ and exposure $h(\vec{D}, i)$ are given by $\tau_{it}(D_{it}, h(\vec{D}, i)) = Y_{it}(D_{it}, h(\vec{D}, i)) - Y_{it}(0, \vec{0})$.
+Then, the total effect and the direct effect are formed similar to above:
+\[
+    \tau_{\text{total}} \equiv \expec{ \tau_{it}(1, h(\vec{D}, i)) \ \vert \ D_{it} = 1} \text{ and }
+    \tau_{\text{direct}} \equiv \expec{ \tau_{it}(1, 0) \ \vert \ D_{it} = 1, h(\vec{D},i) = \vec{0}}.
+\]
+However, it is also common in event-study analyses to allow heterogeneity in effects by the number of years that a unit experiences treatment.
+Let $K_{it}$ denote the number of years since treatment turns on (-1 for year prior, 0 for intial year, and so on).
+Then we can define dummy variables $D_{it}^k \equiv D_it \one_{K_{it} = k}$ and estimate average total effects for each relative period:
+\[
+    \tau_{\text{total}}^k \equiv \expec{ \tau_{it}(1, h(\vec{D}, i)) \ \vert \ D_{it}^k = 1},
+\]
+and similarly for the direct effect.
+
+Estimation of $\tau_{it}$ is the difference between the observed $Y_{it}$ and the unobserved outcome $Y_{it}(0, \vec{0})$ which we will estimate using observations with $D_{it} = 0$ and $h(\vec{D}, 0) = \vec{0}$.
+Similar to the previous section, under assumption (\ref{assumption:local}) we define $S_{it}$ to be an indicator equal to one if in period $t$, unit $i$ is within $\bar{d}$ distance from the nearest treated unit.
+Following the procedure laid out in \citet{Gardner_2021}, I propose a modified version of the two-stage difference-in-differences estimator:
+
+\begin{enumerate}
+    \item Estimate $Y_{it} = \mu_i + \lambda_t + u_{it}$ for observations with $D_{it} = 0$ and $S_{it} = 0$ to estimate the common trend $\lambda_t$ and unit fixed effects $\mu_i$.
+For all observations, residualize $\tilde{Y}_{it} \equiv Y_{it} - \hat{\mu}_i - \hat{\lambda}_t$ which is our estimate for $\tau_{it}$.
+
+    \item Regress $\tilde{Y}_{it}$ on treatment and spillover dummy variables (discussed in table (\ref{tab:second_stage})).
+\end{enumerate}
+
+The first stage uses untreated and unexposed outcomes to consistently estimate the model (\ref{eq:y0_staggered}).
+Then, $\tilde{Y}_{it}$ will serve as an estimate for $\tau_{it}$.
+The second stage regression can be used to estimate averages of $\tau_{it}$ for different groups depending on the parameters of interest.
+This is equivalent to regressing the residual $\tilde{Y}_{it}$ on dummy variable(s).
+Table \ref{tab:second_stage} provides examples of treatment effects of interest and corresponding dummy variables to include.
+
+% Table: Bias from Misspecification of Spillovers
+\begin{table}[!tb]
+    \caption{Second Stage Variables}
+    \label{tab:second_stage}
+
+    \centering
+    \begin{threeparttable}
+        \begin{tabular}{@{} *{2}{l} @{}}
+            % Head
+            \toprule
+            \textbf{Estimand} & \textbf{Included Variables} \\
+
+            % Body
+            \midrule
+            Total Effect & $D_{it}$ \\
+            Total Effect (Event Study) & $D_{it}^k$ dummies \\
+            Direct Effect & $D_{it}(1 - S_{it})$ \\
+            Direct Effect (Event Study) & $D_{it}^k(1 - S_{it})$ dummies \\
+            Spillover Effect on Control & $S_{it}(1 - D_{it})$ or $\text{Ring}_{it}(1-D_{it})$ \\
+            Spillover Effect on Control (Event Study) & $S_{it}^k(1 - D_{it})$ or $\text{Ring}_{it}^k(1-D_{it})$ \\
+            \bottomrule
+        \end{tabular}
+    \end{threeparttable}
+
+\end{table}
+
+As discussed in \citet{Gardner_2021}, inference must account for the fact that the regressand in the second stage is estimated in step 1.
+\citet{Gardner_2021} propose reframing the two-stage process as a two-stage GMM estimator and discusses how to perform valid inference in this setting.
+This procedure is implemented in the R/Stata package \texttt{did2s} \citep{did2s}.
+
+% ------------------------------------------------------------------------------
+\subsection{Application on Community Health Centers}\label{sec:chc}
+% ------------------------------------------------------------------------------
+
+As an application of the above methods, I extend the analysis of \citet{Bailey_Goodman_Bacon_2015}.
+The authors study the creation of federal community health centers between 1965 and 1974 that provided \textit{primary} care to low-income communities.
+They test the hypothesis if access to low/no- cost health care services decreased mortality rates on the treated population.
+To answer this question, the authors use a common event-study framework to compare outcomes in treated counties to all other US counties by estimating the following specification
+\begin{equation}\label{eq:chc_es}
+    Y_{it} = \theta_i + X_{it} \beta + \sum_{k = -7}^{-2} \pi_y D_{it}^k + \sum_{k = 0}^{15} \tau_{y} D_{it}^k + \varepsilon_{it},
+\end{equation}
+where $D_i^k$ is the typical `event study' indicator for being treated for $k$ years, $\theta_i$ is county fixed effects, and $X_{it}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed effects, and urban-group fixed effects.
+A full list can be found on page 1080 of \citet{Bailey_Goodman_Bacon_2015}.} The coefficents $\pi_y$ can be interpreted as tests of parallel pre-trends and $\tau_y$ can be interepreted as the treatment effect of a community health center $y$ years after establishment.
+In years following the establishment of the community health centers, the authors find a reduction of between 15-30 deaths per 100,000 residents compared to a baseline adjusted mortality rate of 929 deaths per 100,000 residents.
+
+% Figure: Direct and Spillover Effects of Community Health Centers
+\begin{figure}[tb!]
+    \caption{Direct and Spillover Effects of Community Health Centers}
+    \label{fig:chc_es_spill}
+
+    {\centering
+        \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
+    }
+    {\footnotesize
+        \textit{Notes:} This figure plots event study estimates for the total effect and the spillover effect on control units within 25 miles of treatment at different periods relative to establishment year.
+The estimates are generated using the `did2s' package \citep{did2s}.
+    }
+\end{figure}
+
+There are theoretical reasons to think spillovers may or may not exist in this context.
+On the one hand, individuals outside the county can potentially travel to the community health centers to receive care.
+This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
+On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergency but rather primary care services.
+In this case, it is less likely low-income individuals would travel very far to receive primary care and hence the spillover effects is potentially near zero.
+My methodology can provide an answer to the question of how far do individuals travel for low/no -cost primary care.
+
+As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
+Then, I follow \citet{Callaway_SantAnna_2020} in estimating event-study coefficients.
+The results are presented in Figure \ref{fig:chc_es_spill}.
+The confidence intervals labeled with circles represent point estimates for the average spillover effect on control units within 25 miles.
+No spillover effect is estimated to be significantly different from zero which suggests that the effects of community health centers are very local.
+Since there are near zero spillover effects, the direct effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
+
+The spillover effects results provide evidence that low-income individuals will not travel far to receive primary care.
+Practically, this suggests that community health centers should be targeted to be as accessible as possible for poor individuals as they are unable to travel far to access the services.
+
+% ------------------------------------------------------------------------------
+\section{Discussion}
+\label{sec:conclusion}
+% ------------------------------------------------------------------------------
+
+This paper has considered the common environment where treatment is assigned via administrative boundary while the effects of treatment spread across these borders.
+In this context, difference-in-differences estimation will identify a combination of the direct effect of treatment and two additional terms resulting from spillovers.
+I use a potential outcomes framework that formalizes spillovers to improve upon ad-hoc estimation strategies by proposing a new estimation strategy that is robust to more forms of spillovers.
+In particular, I find that specifications with an indicator for being ``close to'' treated units interacted with treatment status will remove all bias in the direct effect estimate so long as all units affected by spillovers are contained in the indicator.
+More, I show that a set of concentric `rings' are the best at capturing the spatial structure of spillovers.
+When estimating spillover effects themselves, I find that it is important to correctly identify is spillovers are additive or non-additive in the number of nearby treated units.
+
+Then, I show that in settings with spatial spillovers, estimates can change significantly.
+In particular, place-based interventions change the nature of agglomeration in the local and surrounding area--that is cause spillovers--local effects of these policies can be misestimated without controlling for general equilibrium effects.
+I also show the importance of considering spillovers in weighing the pros and cons of various identificatin strategies.
+Identification strategies based on geographic continuity of unobservables can magnify the bias from spillovers as they restrict the compairson group to observations experiencing the largest spillover effects.
+
+% \section*{Acknowledgements}
+
+% I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, and participants of the Western Economics Association Conference and the CU Boulder Labor Economics Seminar for helpful feedback.
+
+% ------------------------------------------------------------------------------
+\setlength{\bibsep}{0.0pt}
+\bibliography{references.bib}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\appendix 
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\section{Proofs}
+\label{sec:proofs}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\subsection{Proof of Theorem \ref{thm:bias}}
+% ------------------------------------------------------------------------------
+
+\begin{align*}
+    &\underbrace{\expec{Y_{i1} - Y_{i0} \mid D_i = 1 } - \expec{Y_{i1} - Y_{i0} \mid D_i = 0 }}_{\text{Difference-in-Differences}} \\
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) \mid D_i = 0 } \\
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } \\
+    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 } \\
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0} \\ 
+    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\ 
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1} \\
+    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\  
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 } \\
+    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 1 } - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
+    &= \expec{Y_{i1}(1, h(\vec{D}, i)) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 } \\
+    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\
+    &= \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1} + \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1} \\
+    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0} \\
+    &\equiv \tau_{\text{direct}} + \tau_{\text{spill}}(1) - \tau_{\text{spill}}(0) = \tau_{\text{total}} - \tau_{\text{spill}}(0) \\
+\end{align*}
+
+% ------------------------------------------------------------------------------
+\subsection{Proof of Theorem \ref{thm:remove_bias}}
+% ------------------------------------------------------------------------------
+
+For part (i):
+
+\begin{align*}
+    &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} \\
+    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1} \\
+    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
+    &\quad\quad\equiv \tau_{\text{total}},
+\end{align*}
+where the first equality comes from the fact that $S_i = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}), and the last by definition of the total effect.
+
+Similarly, for part (ii):
+
+\begin{align*}
+    &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1, S_i = 0} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0, S_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i1}(0, 0) \ \mid \ D_i = 1, S_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
+    &\quad\quad\equiv \tau_{\text{direct}},
+\end{align*}
+where the first equality comes from the fact that $S_i = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}) and 
+the second to last equality follows from assumption (\ref{assumption:homogenous-direct}).
+
+% ------------------------------------------------------------------------------
+\section{Monte Carlo Simulations}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\subsection{Bias Under Misspecification of Spillovers}
 % ------------------------------------------------------------------------------
@@
 The first exercise is to consider a set of different data generating processes and see how well estimates of the direct effect perform when controlling for spillovers using potentially misspecified exposure mappings.
-In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{i,t}$ for many different exposure mappings $h(\vec{D}, i)$.
+In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h(\vec{D}, i)$.
 I generate data for unit $i$ is a US county at time $t \in \{1, \dots, 20\}$ using the following data-generating process:
 \begin{equation}\label{eq:dgp_general}
-    y_{i,t} = \mu_t + \mu_i + 2 D_{i,t} + \beta_{\text{spill, control}} (1-D_{i,t}) h(\vec{D}, i) + \varepsilon_{i,t},
-\end{equation}
-where $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is IID and distributed as $\varepsilon_{i,t} \sim N(0, 2^2)$.
+    y_{it} = \lambda_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it},
+\end{equation}
+where $\lambda_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is IID and distributed as $\varepsilon_{it} \sim N(0, 2^2)$.
 
@@
 
-% Bias Table
+% Table: Bias from Misspecification of Spillovers
 \begin{table}[!tb]
@@
 In particular, correctly specifying the data-generating process removes almost all the bias in the direct effect estimate and greatly lowers the mean-squared error.
-
-The second result is that both the non-additive `Rings' and the `Within' specification perform best among all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers.
-This is due to the fact that indicator variables will correctly identify the average spillovers onto control units if they cover all the effected control units (see Proposition \ref{thm:remove_bias}).
-They also do so without increasing the variance of the estimator relative to the true specification, as shown by comparing the mean-squared errors.
+The second result is that both the non-additive `Rings' and the `Within' specification perform best among all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers (see Proposition \ref{thm:remove_bias}).
+These specifications do so without increasing the variance of the estimator relative to the true specification.
 However, if the indicator is not wide enough as is the case with Within 40mi.
@@
 data-generating process, bias remains in the estimates.
-Therefore, if researchers are primarily interested in identifying the direct effect, then either `Rings' or `Within' specifications with a large cutoff distance are preferred as they remove almost all bias in all settings.
-
-% ------------------------------------------------------------------------------
-\subsubsection{Spillover Effect Estimation}
+Therefore, if researchers are primarily interested in identifying the direct effect, then either `Rings' or `Within' specifications with a large cutoff distance are preferred.
+
+% ------------------------------------------------------------------------------
+\subsection{Spillover Effect Estimation}
 % ------------------------------------------------------------------------------
@@
 For the next table, I predict the spillover effect for each control unit from the point estimates on $\tilde{h}(\vec{D}, i)$.
-Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (for comparison across data-generating processes), \[
+Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (for comparison across data-generating processes),
+\begin{equation}\label{eq:mspe}
     1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}.
-\] This will produce a percentage of spillovers that are explained by the specification, so numbers closer to $100\%$ represent better modelling of the spillovers.
-
-% MSPE Table
+\end{equation} 
+This will produce a percentage of spillovers that are explained by the specification, so numbers closer to $100\%$ represent better modelling of the spillovers.
+
+% Table: Percent of Spillovers Predicted by Specification
 \begin{table}[!tb]
@@
                 \item \textit{Notes.} Each cell corresponds to the results from 1000 simulations of the data generating process specified by the column header and estimated by equation (\ref{eq:dgp_general}) with $\tilde{h}(\vec{D},i)$ given by the row label.
-The number corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects, given by
-                \[ 
-                    1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}.
-                \]
+The number corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects, given by Equation \ref{eq:mspe}.
             \end{tablenotes}
@@
 
-Therefore there are two practical pieces of guidance from these simulations.
-First, for their ability to remove all bias, `Rings' should be the default used by researchers for estimating the direct effect of treatment.
-Second, the most important aspect of correctly estimating spillovers is to consider whether they are additive in the number of treated units or not.
-Researchers should use a version of Rings either way.
-
-% ------------------------------------------------------------------------------
-\subsection{Guide for Applied Researchers}
-\label{sec:parameterize}
-% ------------------------------------------------------------------------------
-
-The above discussion yields to practical recommendations based on three questions, the answers to which will ultimately depend on the economic context being studied.
-
-\begin{enumerate}
-    \item Researchers should consider whether control units and/or treated units experience effects from the treatment status of other units.
-For example, in the context of library construction, treated units likely do not experience spillovers while close control units do.
-In the context of factory openings which affects nearby labor markets regardless of treatment status, both control and treated units likely experience spillovers.
-
-    \item Researchers must decide how far the spillovers extend and whether the effect decays over distance.
-This should again be guided by the economic context of the research question.
-For example, things such as driving distance or access via public transportation can be helpful in deciding which units are `close enough' to experience spillovers.
-
-    Importantly, Proposition \ref{thm:remove_bias} shows that the researcher does not need to specify the exact functional form of spillovers in order to have unbiased estimates of the treatment effect provided that spillovers are `local' as in Assumption \ref{assumption:local}.
-If only the direct effect of treatment is of interest, than a single ring indicator that contains units within the maximum distance will suffice.
-On the other hand, if spillover effects are of interest themselves, then a set of concentric rings is preferred for the reasons given above.
-
-    \item Last, it is important for estimation to determine if the spillovers are additive or non-additive in nature.
-If the number of nearby treated units matter, then the exposure mapping should sum over nearby treated units in some way.
-For example, in the context of library construction, the number of neighbors with libraries does not change the size of the spillover for it is access to \textit{any} library that matters.
-In the context of factory openings, though, agglomeration economies imply that the spillovers are additive in nature.
-As illustrated in the Monte Carlo simulations, in order to accurately estimate spillovers requires correctly using a additive or non-additive version of the concentric rings.
-\end{enumerate}
-
-% ------------------------------------------------------------------------------
-\subsection{Application in Place-Based Policy Analysis}
-\label{sec:tva}
-% ------------------------------------------------------------------------------
-
-To illustrate the importance of accounting for spatial spillovers in the estimation of treatment effects, I revisit the analysis of the Tennessee Valley Authority (TVA) in \citet{Kline_Moretti_2014}.
-The TVA program was a large-scale federal investment started in 1934 that focused on construction of dams and transportation canals in an attempt to modernize the Tennessee Valley's economy.
-By the end of WWII, the TVA became the largest single power supplier in the country and significantly lowered the cost of wholesale energy for factories.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.
-The effects on wholseale electricity are discussed in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
-\citet{Kline_Moretti_2014} analysze a range of outcome variables, but for succinctness I use only (the log of) agricultural and manufacturing employment.
-Since the TVA primarily improved manufacturing industries through large-scale electrification, the authors predict that employment will grow in manufacturing and shrink in agricultural as workers switch to higher-paying manufacturing jobs.
-
-The analysis in \citet{Kline_Moretti_2014} begins by comparing changes in county-level outcomes from 1940 to either 1960 (short-run effects) or 2000 (long-run effects) between treated counties in the Authority and control counties outside.
-The primary specification is
-\begin{equation}\label{eq:tva}
-    y_{c, t} - y_{c, 1940} = \alpha + \text{TVA}_c \tau + X_{c, 1940} \gamma + (\varepsilon_{c, t} - \varepsilon_{c, 1940}),
-\end{equation}
-where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ is an indicator for being in the post-period, and $y$ is a set of outcome variables (in logs).\footnote{The two-periods difference-in-differences regression is equivalent to a first-difference regression.
-The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is equivalent to a weighted difference-in-differences estimate.
-The weights are the propensity scores from a linear probability model where the outcome variable is being in the TVA.
-The weights can be seen in Figure III of their text, but generally counties close to the TVA are slightly upweighted relative to uniform weights.
-Their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.} To improve the likelihood of the paralell trends assumption, they run a logistic regression to predict being in the TVA based on their set of control variables $X_{c,1940}$ and keep only observations in the top 75\% of predicted probability.
-The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
-
-\citet{Kline_Moretti_2014} estimate (\ref{eq:tva}) to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
-However, their point estimates compare, in part, changes in outcomes in TVA counties with changes in outcomes for neighboring counties that likely were impacted by the large-scale program.
-Their identification strategy depends \emph{explicitly} on a parallel counterfactual trends assumption after controlling for covariates and \emph{implicitly} on the SUTVA assumption.
-
-In the paper, the authors discuss the nature of spillovers that can occur.
-For agriculture employment, the authors claim that improved wages in the Authority will draw agriculture workers out of nearby counties.
-Hence they predict a negative spillover.
-For manufacturing, the sign is ambiguous.
-There could be positive spillovers if electrification brought cheap power and agglomeration economies to the neighboring areas.\footnote{\citet{Duranton_Puga_2003} give theoretical motivations for different sources of agglomeration.} However, manufacturing could decline if firms chose to locate in the Authority that would have, in the absence of the program, decided to locate in nearby counties.\footnote{\citet{Cuberes_Desmet_Rappaport_2021} refer to the positive spillover effects as `urban access' and the negative spillover effecte as `urban shadows' and find descriptive evidence of these effects changing importance over time.} My methodology will allow me to empirically test these predictions in the data and remove their bias from the treatment effect estimates.
-
-By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
-The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this.
-As discussed in Section \ref{sec:remove_bias}, bias in their estimate will likely remain even after dropping contiguous counties.
-The estimation strategy I present keeps the observations near the TVA while controlling for spillover effects in a more rigorous manner.
-
-\begin{figure}[tb!]
-    \caption{TVA Effective Sample and Spillover Variables}
-    \label{fig:tva_sample}
-
-    {\centering
-        \resizebox{\textwidth}{!}{
-            \includegraphics{../../figures/figure-tva-sample.pdf}
-        } 
-    }
-
-    {\footnotesize \textit{Notes:} The above figure plots all the counties used in the estimation.
-Counties that fall within the distance intervals $\{ (0, 50], (50, 100], (100, 150], (150, 200] \}$ measured in miles are colored by their respective bin.}
-\end{figure}
-
-I extend their analysis to control for spatial spillovers in the difference-in-differences specification.
-To parametrize the exposure mapping, I include a set of indicator variables for when a county is within a certain distance interval from the Authority.
-Specifically, I use the following intervals $\text{Dist} = \{(0, 50], (50, 100], (100, 150], (150, 200]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority.
-Figure \ref{fig:tva_sample} displays the four spillover variables by filling in each distance bin in a different color.
-The magnitude and potentially the sign of spillovers can change with distance, hence I allow the effect to be seperately identified in bins.
-I keep the number of bins small to improve precision of spillover estimates.
-
-The specification with spillovers is given as follows:  
-\begin{equation}\label{eq:tva_spillover}
-    y_{i, t} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, t} - \varepsilon_{i, 1940}),
-\end{equation} 
-where $t \in \{1960, 2000\}$.
-The coefficients $\delta_d$ estimate the average spillover effect onto control units at different distances from the Authority.
-From proposition \ref{thm:remove_bias}, $\hat{\tau}$ will be an unbiased estimate for the `local' effect so long as spillovers do not occur past 200 miles from the TVA.
-
-The results of the long-run analysis from 1940 to 2000 are presented in Panel A Table \ref{tab:tva}.
-The first column lists which dependent variable (measured in logs) was used in the row.
-The following columns contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
-The point estimates can be interpreted as decadel growth rates in outcomes.
-The column labeled difference-in-differences uses an ordinary least squares estimator for the specification without spillovers, equation (\ref{eq:tva}).
-This estimate finds a decline in agricultural employment of about $5.1\%$ per decade and an increase in manufacturing employment of about $5.6\%$ per decade.
-
-% TVA Table
-\begin{table}[!tb]
-    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
-    \label{tab:tva}
-    \renewcommand{\arraystretch}{1.1}
-
-    \begin{adjustbox}{width = \textwidth, center}
-        \begin{threeparttable}
-            \begin{tabular}{@{} l c@{\extracolsep{20pt}}c@{\extracolsep{4pt}}cccc @{}}
-                % Head
-                \toprule
-
-                & \multicolumn{1}{c}{\textbf{Diff-in-Diff}} & \multicolumn{5}{c}{\textbf{Diff-in-Diff with Spillovers}} \\ 
-                \cmidrule{2-2} \cmidrule{3-7}
-                & & & TVA between & TVA between & TVA between & TVA between \\ 
-                & TVA & TVA & 0-50 mi. & 50-100 mi. & 100-150 mi. & 150-200 mi. \\ 
-                \textit{Dependent Var.} & (1) & (2) & (3) & (4) & (5) & (6) \\
-
-                % Body
-                \toprule
-                \multicolumn{7}{l}{\textbf{Panel A:} 1940-2000} \\
-                \midrule
-
-                \input{../../tables/tva_replication.tex}
-
-                \\ \toprule
-                \multicolumn{7}{l}{\textbf{Panel B:} 1940-1960} \\
-                \midrule
-
-                \input{../../tables/tva_replication_short.tex}
-
-                \\ \bottomrule
-            \end{tabular}
-
-            % Notes 
-            \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each row corresponds to an outcome variable.
-Each cell is the point estimate and the standard error for the variable described in the column title.
-All standard errors are Conley standard errors with a correlation cutoff of 200 miles following \citet{Conley_1999}.
-The column labeled `Diff-in-Diff' estimates (\ref{eq:tva}) by OLS and is similar to the estimate reported in \citet{Kline_Moretti_2014}.
-The final four columns labeled `Diff-in-Diff with Spillovers' are estimates from (\ref{eq:tva_spillover}).
-
-                \item $^{*} p< 0.1$; $^{**} p < 0.05$; $^{***} p < 0.01$.
-            \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-
-Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and and columns (3)-(6) contain point estimates of the spillover effects $\delta_d$.
-For agricultural employment, the point estimates show there was a decline in agriculture employment in control units near the Authority.
-For control units between 0 and 50 miles, column (4) indicates a decline in agricultural employment of $3.7\%$ per decade.
-Between 50 and 100 miles the point estimate is $-1.6\%$ per decade, between 100 and 150 miles the point estimate is $-3\%$ per decade, and between 150 and 2000 miles the point estimate is $-1.6\%$ per decade.
-This is likely due to the fact that higher paying manufacturing jobs within the Authority drew farm-worker migrants from nearby counties.
-Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
-The new point estimate indicates a decline of agricultural employment of about $7.4\%$ per decade compared to $5.1\%$ in the standard difference-in-difference specification.
-
-For manufacturing, our point estimates for spillovers are consistently negative, though imprecisely estimated in some columns.
-The spillover estimates suggest that neighboring counties experienced potentially negative spillover effects in the long-run.
-Since there are negative spillover effects present, the new point estimate in column (2) of $3.5\%$ is significantly smaller than the original estimate of $5.6\%$.
-The spillover estimates are evidence that in the long-run, urban shadow forces dominate the benefits of urban access.
-As you move away from the Tennessee Valley, the point estimates become more negative which suggest that the benefits of urban access vanish over distance faster than the costs of urban shadow.
-
-To see how spillover effects from a large-scale place-based policy develop over time, Panel B in Table \ref{tab:tva} presents results for the effects of the Tennessee Valley in the short-run using outcome data in 1960.
-Unlike in the long-run, areas near the Tennessee Valley did not experience significant declines in agricultural employment in the short-run.
-Since our long-run analysis finds significant increases in high paying manufacturing employment in the Tennessee Valley, this result is consistent with long-run migration costs being lower than short-run costs.
-
-For manufacturing, there are potentially positive increases in manufacturing employment within 100 miles of the Tennessee Valley authority and near zero effects between 100 and 200 miles.
-In the short-run, it appears that the effects of urban access and the cheap wholesale electricity dominated the effects of urban shadow.
-The effect of urban shadows can potentially be smaller in the short-run if operating firms are unlikely to relocate.
-Long-run effects can be larger as entrant firms change their location decision and operating firms are slowly replaced which is what the long-run spillover effect estimates suggest.
-
-These results show that including spillovers in the estimation of direct treatment effects is potentially important and can lead to \emph{significant} differences in treatment effect estimates.
-Analysis of place-based policies that do not account for the fact that treatment effects can spillover beyond the borders of treated areas can potentially be biased.
-More, the spillover effects caused by place-based policies change over time as frictions can create delays in reoptimizing behavior.
-
-% ------------------------------------------------------------------------------
-\subsection{Identification Strategies in Place-Based Analysis}
-% ------------------------------------------------------------------------------
-
-More generally, my framework provides important insights into identification strategies when analysizing the effects of place-based policies.
-There are two ways I contribute.
-First, \citet{Baum-Snow_Ferreira_2015} recognize the problem of spatial spillovers causing problems in identification and point to aggregation of units as a way to alleviate to the problem (e.g.
-aggregating census tracts to metropolitan areas).
-However, this approach collapses the three seperate effects which might each be of interest into a singular aggregate effect.
-I have shown that all three effects of place-based policies can be estimated under very general assumptions about the spillovers.
-Therefore, the methods propose simple ways to estimate treatment effects with non-aggregated data.
-
-Second, my framework provides insight for different identification strategies often used in the literature.
-Since place-based policies are targeted to specific distressed areas, comparison units are often hard to find.
-Researchers have developed many identification strategies to find comparison units that are similar in terms of unobservables.
-First, researchers use border discontinuities to compare treated units to units just on the otehr side of the border.
-The rationale for this is that unobservables that could be correlated with treatment would evolve continuously across the border and so neighobring units would serve as valid comparisons.
-A different identification strategy compares approved and close but ultimately rejected applicants (e.g.
-\citet{}).
-Since both the treated and comparison groups likely are simliar due to the comparison group was close to being treated, unobservables should be balanced.
-A key difference in these identification strategies is the distance comparison units are from the treated area and therefore the former is more prone to bias due to spillovers than the latter.
-
-For example, consider the analysis of the effects of federal Empowerment Zones.
-The federal Empowerment Zones are specially designated areas in high-unemployment areas.
-The program gives businesses located in the zone tax incentives and the goal of the program is to reduce unemployment and poverty.
-In the literature, there are a set of conflicting results with some papers suggesting that the Empowerment Zones do indeed reduce poverty rates and others finding near-zero effects.\footnote{See Table 1 of \citet{Neumark_Young_2019} for a summary of the various treatment effect estimates in the literature.}
-
-\citet{Busso_Gregory_Kline_2013} compare census tracts in Empowerment Zones to census tracts that qualified and were rejected from the program.
-The rejected tracts are not typically geographically near accepted Empowerment Zones which removes the concern of spatial spillovers affecting control units' change in outcomes.
-They find large significant reductions in poverty rates.
-Meanwhile, \citet{Neumark_Kolko_2010} compare census tracts in Empowerment Zones to census tracts within 1,000 feet of the Zone.
-These control counties are likely the ones that experience the largest spillover effects.
-They find near-zero effects on poverty.
-
-My framework can reconcile both of these results.
-If census tracts just outside the Empowerment Zones also benefit from the policy, then the estimates of \citet{Neumark_Kolko_2010} are attenuated towards zero.
-These two identification strategies of using rejected applicants or using bordering units as the control group are very common in the urban literature more generally \citep{Baum-Snow_Ferreira_2015}.
-My paper suggests that the former is the preferred strategy if spillovers occur onto nearby control units.
-Identification strategies that rely on geographically close control units as having similar unobservables should be used cautiously.
-If treatment effects spillover treatment border, then estimated treatment effects can be biased.
-
-% ------------------------------------------------------------------------------
-\section{Estimating Event Study with Spillovers}
-\label{sec:event_study}
-% ------------------------------------------------------------------------------
-
-The intuition from how spillovers cause biases in estimates of the direct effect of treatment extend into the setting where there is staggered adoption in treatment.
-When treatment turns on for different units at different times, two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
-I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias terms from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
-However, since weights on some of the $2 \times 2$ estimates can be negative, the sign of the spillover effects do not determine the sign of the weighted average of the spillover effects.
-This makes the bias from spillovers much more difficult to sign.
-
-In order to estimate treatment effects in the presence of spatial spillovers and staggered treatment timing, I will propose an estimation strategy that follows \citet{Callaway_SantAnna_2020} while incorporating spillovers directly into estimation.
-However, I do not cover all the technical assumptions and point the reader to the main text for these details.
-To begin, Callaway and Sant'Anna define a `cohort' $g$ as the set of units that recevie treatment starting in period $g$.
-Let $G_g$ be an idicator equal to one for all units where treatment starts at period $g$ and $C$ an indicator equal to one if the unit never receives treatment.
-Each cohort, $g$, will serve as the treated group for a set of $2\times 2$ difference-in-differences.
-For each period $t$ they define the `group-time average treatment effect', $ATT(g,t) = \expec{Y_t(g) - Y_t(0) \ \vert \ G_g = 1 }$, where $G_g$ is an indicator for starting treatment in year $g$.
-The potential outcome is indexed by $g$ to allow for treatment effects to differ depending on the initial treatment year.
-
-Therefore in the context of spillovers, our equivalent term is the `group-time average direct effect' which will be defined as $$ 
-    ATT_{\text{direct}}(g,t) = \expec{Y_t(g, 0) - Y_t(0, 0) \ \vert \ G_g = 1 },
-$$ where the second term in potential outcomes represents an exposure mapping of $h(\vec{D}, i) = 0$.
-Similar to above, we modify the parallel trends assumptions given by Callaway and Sant'Anna to hold in the absence of exposure.
-
-\begin{assumption}[Parallel Counterfactual Trends on a ``Never-Treated'' Group]\label{assumption:parallel_es_never}
-    $$
-        \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 } = \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ C = 1 } 
-    $$ 
-\end{assumption}
-
-\begin{assumption}[Parallel Counterfactual Trends on ``Not-Yet-Treated'' Groups]\label{assumption:parallel_es_notyet}
-    $$ 
-        \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ G_g = 1 } = \expec{Y_t(0, 0) - Y_{t-1}(0, 0) \ \vert \ D_s = 0, G_g = 0 }
-    $$ 
-\end{assumption}
-
-The group-time average direct effect is the building block of analysis in the framework proposed by Callaway and Sant'Anna.
-Estimation of the group-time average direct treatment effect, $ATT_{\text{direct}}(g,t)$ depends on which parallel trends assumption a researcher use.
-The difference-in-difference estimate uses period $t$ outcomes as the post-period and some period $g - \delta$ as the pre-period where $\delta$ is the number of periods before initial treatment.\footnote{It is recommended that $g - \delta$ be the closest period before anticipation can occur.
-For example, if no anticipation is present in the setting, then $\delta = 1$ would be the recommended choice.} In the context of spillovers, the canoncial difference-in-differences estimation will have to be adjusted using a parameterized exposure mapping to prevent the bias detailed in the $2 \times 2$ setting.
-As shown in Section \ref{sec:estimation}, this can be done using a large `Within' indicator that is wide enough to capture all of the spillovers.
-If a researcher is using Assumption \ref{assumption:parallel_es_notyet}, then estimation will be done with a subsample containing treated units from group $g$ and all units that are in groups $g' > t$.
-If a researcher is using Assumption \ref{assumption:parallel_es_never}, then estimation will be done using a supsample containing only control units and units in group $g$.
-
-Then, as detailed in C\&S, the $ATT(g,t)$ can be aggregated using different weights depending on the pararmeter of interest (see Table 1 of \citet{Callaway_SantAnna_2020}).
-These aggregations take the form of
-\begin{equation*}
-    \theta = \sum_{g} \sum_{t} w(g,t) ATT_{\text{direct}}(g,t)    
-\end{equation*} 
-Different weights produce different estimates for different average effects of interest, e.g.
-event study estimates, group-level average treatment effects (across time), or an aggergate treatment effect.
-Estimation and different aggregation of the direct effects can be done using the `did' package produced by C\&S where the the `Within' indicator is included as a covariate.
-It is important to note that exposure can change over time as new units are treated, so researchers should make sure to use the correct values for exposure mapping for each year $t$.
-
-% ------------------------------------------------------------------------------
-\subsection{Estimation of Spillover Effects}
-% ------------------------------------------------------------------------------
-
-Estimation of the spillover effects is potentially much more difficult as estimation of continuous variables or multiple treatment variables in the presence of staggered treatment timing is still a work in progress and past the scope of this article.
-However, for a `Within' indicator, estimation can be done in much the same way as the direct effect but with more caution when constructing the samples for each $2 \times 2$ estimate.
-The `Within' indicator can be thought of as the treatment indicator and the sample would consist of only the never-treated units.
-The advantage of the `Within' indicator is that it will remove all bias from the direct effects estimates if the indicator extends far enough and will give an estimate of the average spillover effect.
-However, as mentioned above, a `Within' indicator does a poor job of estimating (a) the shape of spillover effects over distance and (b) spillover effects that are additive in the number of nearby treated units.
-Estimation of different exposure mappings is a task left for future research.
-
-Groups in this case will be defined by the period which `Within' first equals 1 for a given observation and estimation of $ATT(g,t)$ should use all observations where `Within' is equal to zero for period t and before.
-Then, estimation can be done assuming that all control units are on the same counterfactual trends in the absence of spillovers which is satisfied by Assumption \ref{assumption:parallel_es_never}.
-Therefore, estimation and aggregation can be done in much the same way as for the direct effect but on just the subsample of control units.
-
-% ------------------------------------------------------------------------------
-\subsection{Application on Community Health Centers}\label{sec:chc}
-% ------------------------------------------------------------------------------
-
-As an application of the above methods, I extend the analysis of \citet{Bailey_Goodman_Bacon_2015}.
-The authors study the creation of federal community health centers between 1965 and 1974 that provided \textit{primary} care to low-income communities.
-They test the hypothesis if access to low/no- cost health care services decreased mortality rates on the treated population.
-To answer this question, the authors use a common event-study framework to compare outcomes in treated counties to all other US counties by estimating the following specification
-\begin{equation}\label{eq:chc_es}
-    Y_{jt} = \theta_j + X_{jt} \beta + \sum_{y = -7}^{-2} \pi_y D_j 1(t - T_j^* = y) + \sum_{y = 0}^{15} \tau_{y} D_j 1(t - T_j^* = y) + \varepsilon_{jt},
-\end{equation}
-where $T_j^*$ is the year the county establishes a community health center, $D_j$ is an indicator for being treated, $\theta_j$ is county fixed effects, and $X_{jt}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed effects, and urban-group fixed effects.
-A full list can be found on page 1080 of \citet{Bailey_Goodman_Bacon_2015}.} The coefficents $\pi_y$ can be interpreted as tests of parallel pre-trends and $\tau_y$ can be interepreted as the treatment effect of a community health center $y$ years after establishment.
-
-\begin{figure}[tb!]
-    \caption{Effects of Establishment of Community Health Centers}
-    \label{fig:chc_es}
-
-        {\centering
-            \includegraphics[width=\textwidth]{../../figures/figure-chc-es_original.pdf}
-        }
-
-    {\footnotesize
-        \textit{Notes:} This figure recreates figure 5 from \citet{Bailey_Goodman_Bacon_2015}. Details on the event study specificaiton and controls can be found in the text.
-    }
-\end{figure}
-
-The result are in Figure \ref{fig:chc_es}.
-Estimates of $\hat{\tau}_y$ show that counties that received health centers had significantly lower mortality rates than the other counties in the US.
-In years following the establishment of the community health centers, the authors find a reduction of between 15-30 deaths per 100,000 residents compared to a baseline adjusted mortality rate of 929 deaths per 100,000 residents.
-
-\begin{figure}[tb!]
-    \caption{Direct and Spillover Effects of Community Health Centers}
-    \label{fig:chc_es_spill}
-
-        {\centering
-            \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
-        }
-
-    {\footnotesize
-        \textit{Notes:} This figure plots event study estimates for the treatment effect and the spillover effect on control units within 25 miles of treatment at different periods relative to establishment year.
-The estimates are generated using the `did' package produced from the paper \citet{Callaway_SantAnna_2020}.
-    }
-\end{figure}
-
-There are theoretical reasons to think spillovers may or may not exist in this context.
-On the one hand, individuals outside the county can potentially travel to the community health centers to receive care.
-This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
-On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergency but rather primary care services.
-In this case, it is less likely low-income individuals would travel very far to receive primary care and hence the spillover effects is potentially near zero.
-My methodology can provide an answer to the question of how far do individuals travel for low/no -cost primary care.
-
-As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
-Then, I follow \citet{Callaway_SantAnna_2020} in estimating event-study coefficients.
-The results are presented in Figure \ref{fig:chc_es_spill}.
-The confidence intervals labeled with circles represent point estimates for the average spillover effect on control units within 25 miles.
-No spillover effect is estimated to be significantly different from zero which suggests that the effects of community health centers are very local.
-Since there are near zero spillover effects, the direct effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
-
-The spillover effects results provide evidence that low-income individuals will not travel far to receive primary care.
-Practically, this suggests that community health centers should be targeted to be as accessible as possible for poor individuals as they are unable to travel far to access the services.
-
-% ------------------------------------------------------------------------------
-\section{Conclusion}
-\label{sec:conclusion}
-% ------------------------------------------------------------------------------
-
-This paper has considered the common environment where treatment is assigned via administrative boundary while the effects of treatment spread across these borders.
-In this context, difference-in-differences estimation will identify a combination of the direct effect of treatment and two additional terms resulting from spillovers.
-I have proposed a potential outcomes framework that formalizes spillovers.
-
-I use this framework to point to limitations in commonly used ad-hoc approaches to controlling for spillovers.
-Then, I propose a new estimation strategy that is robust to more forms of spillovers.
-In particular, I find that specifications with an indicator for being ``close to'' treated units interacted with treatment status will remove all bias in the direct effect estimate so long as all units affected by spillovers are contained in the indicator.
-More, I show that a set of concentric `rings' are the best at capturing the spatial structure of spillovers.
-When estimating spillover effects themselves, I find that it is important to correctly identify is spillovers are additive or non-additive in the number of nearby treated units.
-
-Then, I show that these approaches can change estimates significantly in the context of estimating the effects of place-based policies.
-Since place-based policies change the nature of agglomeration in the local and surrounding area --that is cause spillovers--local effects of these policies can be misestimated without controlling for spillovers.
-I also show the importance of considering spillovers in weighing the pros and cons of various identificatin strategies.
-Identification strategies based on geographic continuity of unobservables can magnify the bias from spillovers as they restrict the compairson group to observations experiencing the largest spillover effects.
-
-Finally, I show how researchers can include spillovers in settings with variation in treatment timing following \citet{Callaway_SantAnna_2020}.
-I then use this method to show how considering spillovers in event-study framework provide additional insights for a researcher.
-
-% ------------------------------------------------------------------------------
-\newpage \bibliography{references.bib}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\newpage \appendix 
-\renewcommand{\thetable}{\Alph{section}.\arabic{table}}
-\renewcommand{\thefigure}{\Alph{section}.\arabic{figure}}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\section{Proofs}
-\label{sec:proofs}
-% ------------------------------------------------------------------------------
-
-\textbf{Proof of Theorem \ref{thm:bias}}
-\begin{align*}
-    \expec{\hat{\tau} } &= \underbrace{\expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \mid D_i = 1 } - \expec{\bar{Y}_{i,Post} - \bar{Y}_{i,Pre} \mid D_i = 0 }}_{\text{Difference-in-Differences}} \\
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 0 } \\
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } \\
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) + \bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 0 } \\
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } - \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 0} \\ 
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0} \\ 
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0})  \mid D_i = 1 } \\
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, \vec{0}) - \bar{Y}_{i,Pre}(0, \vec{0}) \mid D_i = 1} \\
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0} \\  
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Pre}(0, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) + \bar{Y}_{i,Pre}(0, \vec{0})\mid D_i = 1 } \\
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0}\\
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 1 } - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0}\\
-    &= \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) + \bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 1 } \\
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0})\mid D_i = 0} \\
-    &= \expec{\bar{Y}_{i,Post}(1, \vec{0}) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 1} + \expec{\bar{Y}_{i,Post}(1, h(\vec{D}, i)) - \bar{Y}_{i,Post}(1, \vec{0}) \mid D_i = 1} \\
-    &\quad\quad - \expec{\bar{Y}_{i,Post}(0, h(\vec{D}, i)) - \bar{Y}_{i,Post}(0, \vec{0}) \mid D_i = 0} \\
-    &= \tau_{\text{direct}} + \tau_{\text{spill,treated}} - \tau_{\text{spill,control}} \\
-\end{align*}
-
-% ------------------------------------------------------------------------------
-\section{Details on Dropping Control Unit Approach}
-\label{sec:monte_carlo}
-\setcounter{figure}{0}
-\setcounter{table}{0}
-% ------------------------------------------------------------------------------
-
-I use the set of counties in the contiguous United States and the data generating process used is defined by the exposure mapping given in (\ref{eq:h_within}) with cutoff distance $\bar{d} = 40$ miles and the data generating process given in (\ref{eq:example_po}).
-A unit of observation is a US county and the periods are $t \in \{1, \dots, 20\}$ with treatment turning on after period $t = 10$.
-The unit and time fixed effects are generated by $\mu_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively, and the error term is $\varepsilon \sim N(0, 2^2)$.
-Last, the size of treatment and spillovers are as follows: $\beta_{\text{direct}} = 2$, $\beta_{\text{spill, control}} = 1$ and $\beta_{\text{spill, treat}} = 0$.
-
-This data generating process where spillovers only occur onto control units matches what has been typically assumed in the literature.
-I assign treatment among counties randomly with various unconditional probabilities between 3 percent and 50 percent.
-The data-generating process is therefore
-\begin{equation}
-    \label{eq:dgp1} 
-    y_{i,t} = \mu_t + \mu_i + \beta_{\text{direct}} D_{i,t} + \beta_{\text{spill, control}} (1-D_{i,t}) \text{Near}_{i,t} + \varepsilon_{i,t}   
-\end{equation}
-
-\begin{figure}[tb!]
-    \caption{Effectiveness of Removing `Contaminated' Control Units}
-    \label{fig:bias_drop_control}
-
-    \begin{subfigure}[t]{\textwidth}
-        \caption{Spillovers Effects \emph{only} on Control} \label{fig:bias_as_treat_prob}
-
-        {\centering
-            \includegraphics[width=0.9\textwidth]{../../figures/figure-bias_fix.png}
-        }
-    \end{subfigure}
-
-    \begin{subfigure}[t]{\textwidth}
-        \caption{Spillovers Effects on Control and Treated} \label{fig:bias_as_treat_prob_w_treat}
-
-        {\centering
-            \includegraphics[width=0.9\textwidth]{../../figures/figure-bias_fix_treat.png}
-        }
-    \end{subfigure}
-
-    {\footnotesize
-        \textit{Notes:} This figure plots the bias of $\hat{\tau}$ found from estimating (\ref{eq:twfe}) for data generated as described in the text by equations (\ref{eq:dgp1}) for Panel A and (\ref{eq:dgp2}) for Panel B.
-Each point corresponds to the average bias for the given treatment probability and the band is the 95 percent empirical confidence interval over 1000 simulations.
-The line with diamond markers estimates with all control units.
-The line with circle markers removes control units that share a border with a treated county.
-    }
-\end{figure}
-
-The size of the bias from estimating the two-fixed effects model, (\ref{eq:twfe}), at different treatment probabilities are presented in Figure \ref{fig:bias_as_treat_prob} as the line with diamond markers.
-Each point represents a set of 10,000 simulation and displays the mean bias as well as a 95 percent empirical confidence interval.
-As displayed in the figure, even for a low treatment probability of three percent, the bias is quite large with a 95 percent empirical confidence interval between -0.28 and -0.75.
-As treatment frequency increases, the bias increases as well but at a slower rate due to fewer additional control units receiving spillover units.
-The slow increase in bias is in part due to the assumption that spillovers are not additive in the number of nearby units treated.
-
-A common solution in the literature is to remove control units from the estimated sample that are most likely to be affected by spillovers.
-To do this, I remove contiguous control counties which is a close, but misspecificied, measure of $h(\vec{D}, i)$.
-The results are shown in Figure \ref{fig:bias_as_treat_prob} by the line with circle markers.
-Even though the exposure mapping is misspecified, contiguous counties approximates the true exposure mapping well enough such that the bias stays centered constantly around zero as most control units experiencing spillovers are removed.
-However, if the distance cutoff $\bar{d}$ were larger, more control units would remain in the sample that experience non-zero exposures.
-In this case, the bias would fall between the two lines.
-
-There is a trade-off between the bias and the variance of the estimator when using this methodolgy.
-As the treatment probability increases, the number of control units removed increases as well.
-This naturally yields a more variable estimator as seen in the wider 95 percent empirical confidence intervals in Figure \ref{fig:bias_as_treat_prob}.
-This trade-off can be avoided altogether by parameterizing the spillovers and including them in estimation directly.
-
-There is a second problem with the method of removing control units in the presence of spillover effects onto treated units.
-Since removing control units does not control for this second source of spillover effects, the estimates will be biased.
-In the second simulation, I add in spillover effects into the above data-generating process and set $\beta_{\text{spill, treat}} = 0.5$:
-
-\begin{equation}
-    \label{eq:dgp2} 
-    y_{i,t} = \mu_t + \mu_i + \beta_{\text{direct}} D_{i,t} + \beta_{\text{spill, control}} (1-D_{i,t}) \text{Near}_{i,t} + \beta_{\text{spill, treat}} D_{i,t} \text{Near}_{i,t} + \varepsilon_{i,t}   
-\end{equation}
-
-The results are displayed in Figure \ref{fig:bias_as_treat_prob_w_treat}.
-Again, two-way fixed effect estimation results in a biased estimate as shown by the line with diamond markers.
-The magnitude is smaller than in Panel (a) because the positive spillovers onto treated units cancel out with the positive spillovers onto control units.
-However, removing the control units near the treated units results in a biased estimate due to the average spillover onto also treated units, as seen by the line with circle markets in Panel (b).
-This problem is particularly concerning as a researcher may assume that there is positive spillovers on control units that is negatively biasing their estimate and when removing those units the estimate would increase in magnitude as expected.
-Researchers could therefore potentially assume they have removed all bias from their estimates even though the second form of bias remains.
-
 \end{document}

### 2021-11-04 latex/paper/Spillover.tex
Finished Revising Paper

@@
 Using this potential outcome framework, I define the different possible treatment/spillover effects of interest and the relative advantage and interpretation of each.
-First, there is the `switching effect' which is the relevant parameter for local policy makers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units''.
+First, there is the `switching effect' which is the relevant parameter for local policy makers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
 It is difficult to estimate the switching effect without parametric assumptions.
@@
 This treatment effect summarizes what were the effects of going from the world with no treatment to the entire vector of treatment status.
-I further show that this effect comes from two sources: the direct effect and the average spillover effect from other treated units.
-
-The standard difference-in-differences estimate identifies none of these treatment effects in the presence of spillovers.
-The first result of the paper shows that the difference-in-differences esitmand can be decomposed into the direct effect plus two additional bias terms resulting from the spillovers.
-The intuition is as follows.
-First, untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
+This effect comes from two sources: the direct effect and the average spillover effect from other treated units.
+Unlike the switching effect, the total effect effect is nonparametrically identified under a mild assumption that spillovers are `local' in that spillovers are only experienced within a certain distance from treatment.
+
+This paper shows that the difference-in-differences esitmator is a biased estimate for the total effect because of spillover effects on control units.
+The intuition is that untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
 When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes.
-In this case, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
-For example, if nearby control units also benefit from treatment, then researchers would underestimate the positive benefits of treatment.
-Second, changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
+Hence, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
+For example, if nearby control units also benefit from treatment, then researchers would underestimate the effects on the treated.
+If a researcher is interested in the direct effect, there is an additional source of bias since changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units.
 The spillover onto other treated units is averaged into the treated units' change in outcomes.
-Therefore the bias of treatment effect is the same sign as the sign of the spillover.
-Last, since the total effect is the direct effect plus the average spillover effect on treated units, the difference-in-differences estimand can also be decomposed into the total effect minus the average spillover effect on control units.
+Therefore the bias on the direct effect estimate is the same sign as the sign of the spillover.
 
 This paper then defines conditions under which each treatment effect is nonparametrically identified.
-I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} under certain constraints on the spillover effects.
-The other two treatment effects considered are able to be identfified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units close to treated units.
-This could fail in the case of general equilibrium shocks that cause units far away to be affected by treatment.
+I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
+The other two treatment effects considered are able to be identfified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
+This would hold in the case where individuals can travel to access treatment.
+This could fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g.
+San Francisco being affected by shocks to New York economy).
 
 Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
-In my decomposition of the treatment effect estimate, the bias terms are the \textit{average} spillover effects onto treated and control units.
-An indicator variable interacted with treatment status therefore can estimate these two averages and remove them from the difference-in-differences estimate.
+In my decomposition of the difference-in-differences estimate, the bias term for the total effect is the \textit{average} spillover effects onto control units.
+An indicator variable for control units affected by spillover can remove this bias.
+When estimating the direct effect, a second indicator variable for treated units affected by spillovers is included to remove the second source of bias.
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
-The only assumption required is selecting the maximum distance from treated units spillovers can occur.\footnote{Even if the maximum distance is not large enough, since treatment effects typically decay over distance, most of the bias will still be removed.
-Including too many units in the indicator will increase the variance in the estimates for average spillover effects as the other control units identify the parallel counterfactual unit.}
-
-The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers.
+The only assumption required is selecting the maximum distance from treated units spillovers can occur.\footnote{Since treatment effects typically decay over distance, even if the maximum distance is not large enough, most of the bias will still be removed.
+On the other hand, making the maximum distance too large, will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}
+
+The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of average spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers.
 The above method can be improved by creating a set of distance bins from treated units (e.g.
@@
 
-I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
-I contribute to this literature in two ways.
+I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in two ways.
+\citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
 My paper is the first to consider identification in terms of general potential outcomes.
 Other papers derive results for specific spillover mappings and if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs.
+The literatuere has focused on estimating the total effect, so I contribute by discussing alternative treatment effect estimates and identification results.
 Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
 
-This paper relates to a literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work.
-See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.} Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
-
-Partial inference allows interference between but not across groups..
-\citep{Hudgens_Halloran_2008,Vazquez-Bare_2019}.
-This allows for seperate identification of treatment and spillover effect in experimental settings.
-My paper ...
-
-\citet{Savje_Aronow_Hudgens_2021} show what is identified under no assumptions of interference.
-My paper shows under a different set of assumptions what is estimated and how to estimate effects seperately ...
-
-There is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
+This paper relates to a broad literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work.
+See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.}
+
+There are two main strands of this literature.
+First, there is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
 Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects.
-This allows standard difference-in-differences estimation of both the direct effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).
-
-There is a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster by using a potential outcomes framework.
-\citet{Vazquez-Bare_2019} presents a potential outcomes model that explicitly accounts for ``within-group'' spillovers in experiments which allows for seperate estimation of direct effect and spillover effects by a simple differences-in-means.
-I extend this work by focusing on difference-in-differences estimation in non-experimental settings.
-\citet{Savje_Aronow_Hudgens_2021} consider estimation of treatment effects by difference-in-differences, but they define treatment effects as the combination of direct effects and spillover effects.
-My paper develops a strategy to allow researchers to seperately identify treatment effects and spillovers.
-These estimates can be combined to estimate their definition of average treatment effect.
-The further advantage is that `net' treatment effects can be estimated at different levels of exposure which is more relevant for future policy decisions.
-
-I also contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
-I contribute to this literature in two ways.
-First, my paper derives an explicit form for this bias in terms of general potential outcomes which allows my results to capture many different forms of spillovers.
-For the above papers, if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs if they have one derived explicitly.
-Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
+This allows standard difference-in-differences estimation of both the total effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).
+However, in many settings distinct clusters are not plausible, e.g.
+counties near the border of a state can effect eachother.
+My proposed estimator generalizes this method by using control units are unaffected by treatment without requiring a notion of clusters.
+
+There is a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}, \citet{Vazquez-Bare_2019}, and \citet{Hu_Li_Wager_2021}).
+Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
+I also contribute in this literature by thinking about different definitions of treatment effects and their identification in non-experimental settings.
 
@@
 This section will present a potential outcome framework that formalizes spatial spillovers.
+The goal of this exercise is to formalize treatment effects which are no longer uniquely defined in settings with spillovers.
 Following the canonical difference-in-differences framework, I observe a panel of units for periods $t \in \{0,1\}$ and treatment turns on between periods for some of the units.\footnote{This can be extended to multiple periods by replacing $Y_{i0}$ and $Y_{i1}$ throughout with pre- and post- sample averages of $Y_{it}$.
-This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Let $D_{i}$ be an indicator equal to one if unit $i$ is treated and therefore treatment status is defined as $D_{it} = D_{i} * \one(t = 1)$.
+This framework is extended to staggered treatment adoption in Section \ref{sec:event_study}.} Let $D_{i}$ be an indicator equal to one if unit $i$ is treated and therefore treatment status is defined as $D_{it} = D_{i} * \one_{t = 1}$.
 
@@
 
-Potential outcomes, denoted $Y_{it}(D_i, h(\vec{D},i))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h(\vec{D}, i)$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
-The non-negative scalar- or vector-valued function $h(\vec{D}, i)$ is referred to as an `exposure mapping'.
+Potential outcomes, denoted $Y_{it}(D_i, h_i(\vec{D}))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
+The non-negative scalar- or vector-valued function $h_i(\vec{D})$ is referred to as an `exposure mapping'.
 This setup follows \citet{Vazquez-Bare_2019} who studies identification of spillover effects under an experimental setting.\footnote{Note that throughout, expectations and inference are conditional on the vector of exposure mappings.
@@
 
-The exposure mapping measures the intensity at which unit $i$ is affected by spillovers.
-Without restrictions on the exposure mapping, nonparametric identification of treatment effects will be impossible.
-The main assumption for identification, as will be formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h(\vec{D}, i) = \vec{0}$ .
-In the world of no spillovers, that is $h(\vec{D}, i) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.
-The exposure mapping formalizes the SUTVA violation by summarizing how outcomes are affected by other unit's treatment assignment.
+The exposure mapping formalizes the SUTVA violation by summarizing the intensity at which unit $i$ is affected by spillovers.
+Without any restrictions on the exposure mapping, nonparametric identification of treatment effects will be impossible.
+The main assumption for identification, as will be formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ .
+In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.
 
@@
 \begin{example}
-    $h(\vec{D}, i)$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.
+    $h_i(\vec{D})$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.
 In this case \begin{equation}\label{eq:h_within}
-        h(\vec{D}, i) = \max_{j \neq i} D_j * \one[ d(i,j) < \bar{d} ] 
+        h_i(\vec{D}) = \max_{j \neq i} D_j * \one_{ d(i,j) < \bar{d}}
     \end{equation}
@@
 \begin{example}
-    Second, $h(\vec{D}, i)$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
-        h(\vec{D}, i) = \sum_{j \neq i} D_j * \one[ d(i,j) < \bar{d} ].
+    Second, $h_i(\vec{D})$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
+        h_i(\vec{D}) = \sum_{j \neq i} D_j * \one_{d(i,j) < \bar{d}}.
     \end{equation}
@@
 \begin{example}
-    Last, $h(\vec{D}, i)$ is a spatial decay function where exposure decreases with distance.
+    Last, $h_i(\vec{D})$ is a spatial decay function where exposure decreases with distance.
 In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
 \begin{equation}\label{eq:h_decay}
-        h(\vec{D}, i) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
+        h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
     \end{equation} 
@@
 In setups without spillovers, treatment effects for an individual unit is well defined as $\tau_i \equiv Y_{i1}(1) - Y_{i1}(0)$, i.e.
-the effect of turning on treatment for a unit and the above two assumptions would lead to identification of the average effect by the traditional difference-in-differences estimator.
+the effect of turning on treatment for a unit, and the above two assumptions would lead to identification of the average effect by the traditional difference-in-differences estimator.
 In the presence of spillovers, there are multiple treatment effects that can be defined in this setting.
@@
 \[
-    \tau_{i, switch}(h(\vec{D}, i)) \equiv Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i)).
+    \tau_{i, switch}(h_i(\vec{D})) \equiv Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})).
 \] 
 This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant.
-This treatment effect is policy relevant as it summarizes what would happen if a `local' policy makers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).
-It is important to note that the switching effect can depend on the level of exposure.
+This treatment effect is policy relevant as it summarizes what would happen if a `local' policy makers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).\footnote{This is what \citet{Savje_Aronow_Hudgens_2021} call the `assignment-conditional unit-level treatment effect'.} It is important to note that the switching effect can depend on the level of exposure.
 For instance, consider the construction of libraries in towns.
-The effect of library construction in a town that is far away from any other library ($h = \vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h(\vec{D},i)$.
+The effect of library construction in a town that is far away from any other library (exposure of $\vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h_i(\vec{D})$.
 Since the size of the switching effect depends on a units exposure level, we will consider an average switching effect at each value of exposure,
 \[
-    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i))}{D_i = 1, h(\vec{D}, i) = h}.
+    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}{D_i = 1, h_i(\vec{D}) = h}.
 \]
@@
 %\[ 
-%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h(\vec{D},i)) \vert D_i = 1}.
+%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h_i(\vec{D})) \vert D_i = 1}.
 %\] 
@@
 \[
-    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h(\vec{D},i) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
+    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h_i(\vec{D}) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
 \] 
@@
 \[
-    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
-\] 
-As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h(\vec{D}, i)$ simultaneously.
+    \tau_{\text{total}} \equiv \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}.
+\] 
+As opposed to the switching effect, which keeps exposure constant, the total effect looks at turning on treatment \emph{and} going from zero exposure to $h_i(\vec{D})$ simultaneously.
 This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$.
@@
 \[
-    \tau_{i, \text{spill}}(D_i, h(\vec{D},i)) \equiv Y_{i1}(D_i, h(\vec{D}, i)) - Y_{i1}(D_i, \vec{0}).
-\] 
-The spillover effect measures the difference in potential outcomes between being exposed at intensity $h(\vec{D}, i)$ and not being exposed.
+    \tau_{i, \text{spill}}(D_i, h_i(\vec{D})) \equiv Y_{i1}(D_i, h_i(\vec{D})) - Y_{i1}(D_i, \vec{0}).
+\] 
+The spillover effect measures the difference in potential outcomes between being exposed at intensity $h_i(\vec{D})$ and not being exposed.
 This effect can differ for either treated or control units as the magnitude or even the nature of spillovers might differ between treated and untreated units.
-That is $\tau_{i, \text{spill}}(1)$ does not necessarily equal $\tau_{i, \text{spill}}(0)$.
+That is $\tau_{i, \text{spill}}(1, h_i(\vec{D}))$ does not necessarily equal $\tau_{i, \text{spill}}(0, h_i(\vec{D}))$.
 We can then average over treated/control units to form average spillover effects:
 \[
-    \tau_{\text{spill}}(D) \equiv \expec{Y_{i1}(D, h(\vec{D}, i)) - Y_{i1}(D, \vec{0}) \ \vert \ D_i = D},
+    \tau_{\text{spill}}(D) \equiv \expec{Y_{i1}(D, h_i(\vec{D})) - Y_{i1}(D, \vec{0}) \ \vert \ D_i = D},
 \]
 where the expectation is over individuals and hence over different exposures.
-This will give us the average spillover effect among \emph{all} treated/control units regardless if they receive any spillover effects.
+This will give us the average spillover effect among \emph{all} treated/control units regardless if they experience any spillover effects.
 It is often also of interest to estimate the average spillover effects on subsets of units (e.g.
@@
 \begin{align*}
-    &\overbrace{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, h(\vec{D}, i))}^{\text{Switching Effect}} = \\
-    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect}} \ - \ \underbrace{(Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0,0))}_{\text{Spillover on Control}}
+    &\overbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}^{\text{Switching Effect}} = \\
+    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect}} \ - \ \underbrace{(Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0,0))}_{\text{Spillover on Control}}
 \end{align*}
@@
 In this situation, the simpler identification assumptions behind the direct effect will identify the switching effect at all exposure levels.
-For example, if treatment is a factory opening and the spillover effect on employment is due to increased spending on services, then it could be reasonable to assume the effect does not depend on treatment status and hence the switching effect is constant and equal to the direct effect of changing treatment status.
+For example, if treatment is a factory opening and the spillover effect on employment is due to increased spending on services, then it could be reasonable to assume the effect does not depend on treatment status and hence the switching effect is constant and equal to the direct effect.
 
 However, the spillover effects can sometimes differ depending on treatment status.
-Continuing the above example, perhaps control units could experience negative employment shocks from a nearby country opening a factory if workers relocate to the treated areas resulting in a negative spillover effect on control units.
+Continuing the above example, perhaps control units could experience negative employment shocks from a nearby country opening a factory if workers relocate/commute to the treated areas resulting in a negative spillover effect on control units.
 Other treated units could, for instance, experience positive spillover effects due to agglomeration economies.
 When it is the case that spillover effects depend on treatment status, the switching effect can be thought of as two seperate effects.
-First, the unit is affected by its own treatment status as summarized by the direct effect.
+First, the unit is affected by changing its own treatment status as summarized by the direct effect.
 Second, the unit changes from experiencing spillover effects as a control unit to experiencing spillover effects as a treated unit.
@@
 The estimator $\hat{\tau}$, which is well understood to be the sample analog of (\ref{eq:did}), is therefore a biased estimate for $\tau_{\text{direct}}$ and $\tau_{\text{total}}$ in the presence of spillovers.
-In particular, if a researcher were to estimate a difference-in-differences model and reported $\hat{\tau}$ as an estimate of the total effect, their estimate would be biased in the presence of spillover effects on control units.
+In particular, if a researcher estimates a difference-in-differences model and reports $\hat{\tau}$ as an estimate of the total effect, their estimate would be biased in the presence of spillover effects on control units.
 If spillover effects are of the same sign as the total effect, then estimates would be attenuated towards zero.
@@
 
-It is difficult to identify the switching effect in general as identifying the unobserved counterfactual outcome $Y_{i1}(0, h(\vec{D}, i))$ requires knowledge of which control units have same level of exposure.
+It is difficult to identify the switching effect in general as identifying the unobserved counterfactual outcome $Y_{i1}(0, h_i(\vec{D}))$ requires knowledge of which control units have same level of exposure.
 The reason for this can be seen by rewriting this in terms of a difference-in-differences style estimand:
 \begin{align*}
-    \tau_{\text{switch}}(\vec{h}) &= \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h(\vec{D}, i) = \vec{h} \right] \\ 
-    &\quad\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h(\vec{D}, i) = \vec{h} \right].
+    \tau_{\text{switch}}(\vec{h}) &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = \vec{h} \right] \\ 
+    &\quad\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = \vec{h} \right].
 \end{align*}
 Writing it in this way highlights the two problems in estimating the second term.
-First, this requires knowledge of the unobserved exposure mapping to be correctly specified in order to identify control units with $h(\vec{D}, i) = h$.
+First, this requires knowledge of the unobserved exposure mapping to be correctly specified in order to identify control units with $h_i(\vec{D}) = h$.
 More, this estimand requires a more demanding parallel trends assumption.\footnote{This problem is similar to those highlighted by \citet{Callaway_Goodman-Bacon_SantAnna_2021} for difference-in-differences with continuous treatment.}
@@
     \[ 
-        \expec{Y_{i1}(0, \vec{h}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1, h(\vec{D}, i) = \vec{h} } = 
-        \expec{Y_{i1}(0, \vec{h}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0, h(\vec{D}, i) = \vec{h} }
+        \expec{Y_{i1}(0, \vec{h}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1, h_i(\vec{D}) = \vec{h} } = 
+        \expec{Y_{i1}(0, \vec{h}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0, h_i(\vec{D}) = \vec{h} }
     \]
@@
 
-This assumption is equivalent to \nameref{assumption:parallel}) and an additional assumption that spillover effects being equal between control and treated units that experience exposure $\vec{h}$.
+This assumption requires parallel trends among treated and control units at exposure $\vec{h}$.
+This assumption is implied by \nameref{assumption:parallel} and an additional assumption that spillover effects being equal between control and treated units that experience exposure $\vec{h}$.
 Under this assumption, the switching effect can be identified.
@@
     \begin{align*}
-        \tau_{\text{switch}}(\vec{h}) &= \mathbb{E} \left[ Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h(\vec{D}, i) = \vec{h} \right] \\ 
-        &\quad\quad - \mathbb{E} \left[ Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0,\vec{0}) \mid D_i = 0, h(\vec{D}, i) = \vec{h} \right].
+        \tau_{\text{switch}}(\vec{h}) &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = \vec{h} \right] \\ 
+        &\quad\quad - \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 0, h_i(\vec{D}) = \vec{h} \right].
     \end{align*}
@@
 The switching effect can be estimated by a difference-in-differences estimator on the subsample of units with exposure $\vec{h}$.
-However, this approach relies on correct specification of the exposure mapping which is a difficult assumption to maintain.
-Researchers may be tempted to introduce the parameterized exposure mapping linearly in order to `compare individuals at the same level $\vec{h}$'.
+However, this approach relies on correct specification of the exposure mapping which is a difficult assumption to maintain in practice.
+Researchers may be tempted to introduce the parameterized exposure mapping linearly in order to ``compare individuals at the same level $\vec{h}$''.
 However, this assumes additive seperatability between the treatment dummy and the exposure mapping.
-Additive seperatability would imply treatment effects don't depend on exposure level, i.e.
+Additive seperatability would imply the switching effect does not depend on exposure level, i.e.
 the switching effect is constant across $\vec{h}$.
@@
     \[ 
-        \min_{j: \ D_j = 1} d(i,j) > \bar{d} \implies h(\vec{D}, i) = \vec{0}. 
+        \min_{j: \ D_j = 1} d(i,j) > \bar{d} \implies h_i(\vec{D}) = \vec{0}. 
     \]
@@
 Part (ii) of Assumption (\ref{assumption:local}) requires that there exists control and treated units with no exposure.
-This assumption is far less strict than the identifying assumption for the switching effect in that we only need to identify units with zero exposure and don't need to parameterize the exposure mapping any further.
-For a given $\bar{d}$ that satisfies Assumption (\ref{assumption:local}), let $S_{i}= \one(\min_{j: \ D_j = 1} d(i,j) \leq \bar{d})$ be an indicator for being within $\bar{d}$ miles of the closest treated unit.
+This assumption is far less strict than the identifying assumption for the switching effect in that we only need to identify units with non-zero exposure and don't need to parameterize the exposure mapping any further.
+For a given $\bar{d}$ that satisfies Assumption (\ref{assumption:local}), let $S_{i}$ be an indicator equal to one if $\min_{j: \ D_j = 1} d(i,j) \leq \bar{d}$, i.e.
+unit $i$ is within $\bar{d}$ miles of the closest treated unit.
 
@@
 units with $S_i = 0$).
-In this case, if parallel trends only hold locally, then focusing on further away units fix the spillover bias but increase bias from non-parallel trends.
+In this case, if parallel trends only hold locally, then focusing on further away units can fix the spillover bias but increase bias from non-parallel trends.
 
@@
 The proof is given in Appendix \ref{sec:proofs}, but the intuition is simple.
-Conditioning on $S_i = 0$ will use only observations with $h(\vec{D}, i) = 0$ which give rise to identification of the direct and total effect.
+Conditioning on $S_i = 0$ will use only observations with $h_i(\vec{D}) = 0$ which give rise to identification of the direct and total effect.
 This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
-All that is required to identify the direct or total effects is being able to classify which units are considered `near' treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
+All that is required to identify the direct or total effects is being able to classify which units are considered `close' to treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
 For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
@@
 However, it is important to account for two sources of correlation in the error structure.
-First, errors should be clustered by unit $i$ to allow for correlation between periods.
+First, errors should be clustered by unit $i$ to allow for correlation across time periods.
 Second, since our model is predicated on the fact that nearby places effect one another, we should account for such spatial correlation by allowing for spatial correlations following \citet{Conley_1999}.
@@
 A natural question is why wouldn't researchers make the distance really large in order to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$ or $\tau_{\text{total}}$?
-Equation (\ref{thm:remove_bias}) should make this problem clear.
+Equation (\ref{eq:id_total}) and (\ref{eq:id_direct}) should make this problem clear.
 Since these estimates rely on averages among units with $S_i = 0$, as $\bar{d}$ increases, the number of units with $S_i = 0$ decreases which yields more variable estimates.
 On the other hand, having units that experience spillovers not included in the $S_i$ indicator will leave some bias in the estimate.\footnote{Although, spillover effects typically will grow weaker over distance and if distant units are mistakenly treated as if they have zero exposure, bias should be small.} Therefore there is a bias-variance trade-off in extending the extent of $S_i$ that should be balanced by researchers guided by their particular economic context.
+In seperate work, \citet{Butts_2021} discusses data-driven methods to determine how far $S_i$ should be under a more strict parallel trends assumption.
 
@@
 \]
-These estimates average individual spillover effects for all units with $S_i = 1$.
+These estimates average spillover effects for all units with $S_i = 1$.
 Since some units with $S_i = 1$ do not have positive exposure, this is not the average spillover effect for units with non-zero exposure either.
-For example, if only units really close to treatment receive spillover effects and $S_i$ contains a lot of units that experience no spillover effects, then $\hat{\tau}_{\text{spill, control}}$ could be estimated near zero even though there are spillover effects.
+For example, if only units really close to treatment receive spillover effects and $S_i$ contains a lot of units that experience no spillover effects, then $\hat{\tau}_{\text{spill, control}}$ could be estimated near zero even though some units experience substantial spillover effects.
 
@@
 A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
-The figure displays observations of $Y_{i,Post} - Y_{i,Pre}$ on the y-axis and the distance to the nearest treated unit on the $x$-axis and treated units are placed at a zero distance for visualization purposes.
+The figure displays observations of $Y_{i,1} - Y_{i,0}$ on the y-axis and the distance to the nearest treated unit on the $x$-axis and treated units are placed at a zero distance for visualization purposes.
 The example has a counterfactual trend of 2 so any difference from 2 is due to either treatment/spillover effects and the error term.
@@
 This improves on the estimate of a single ring in two ways.
-Multiple rings are better able to capture the evolution of spillover effects over distance.
-Furthermore, the ring that is included past the true maximum distance where spillover effects occur has a point estimate near zero.
-The rings method acts a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to their being units outside of the rings).
+Multiple rings are better able to capture the decaying nature of spillover effects over distance.
+Furthermore, the ring that is included past the true maximum distance where spillover effects occur (45-60 miles) has a point estimate near zero.
+The rings method acts a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to $\bar{d}$ satisfying assumption (\ref{assumption:local})).
 However, precision of estimates would decrease as the number of rings increase and therefore there is a bias-variance trade-off in the number and width of rings.\footnote{\citet{Clarke_2017} proposes a cross-validation technique for optimally choosing the number of rings and their techniques that uses the out-of-sample mean square prediction error as a way to estimate the bias-variance tradeoff.
@@
 \end{equation}
-where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, $\text{Post}_t$ is an indicator for being in the post-period, and $y$ is a set of outcome variables (in logs).\footnote{The two-periods difference-in-differences regression is equivalent to a first-difference regression.
+where $c$ denotes county, $\text{TVA}_c$ is an indicator variable for being in the Authority, and $y$ is a set of outcome variables (in logs).\footnote{The two-period difference-in-differences regression is equivalent to a first-difference regression.
 The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is equivalent to a weighted difference-in-differences estimate.
@@
 I extend their analysis to control for spatial spillovers in the difference-in-differences specification.
-To parametrize the exposure mapping, I use a set of rings as described in Section \ref{sec:remove_bias}.
+To parametrize the exposure mapping, I use a set of rings as described in Section \ref{sec:spill}.
 Specifically,
@@
 The coefficients $\delta_d$ estimate the average spillover effect onto control units for each of these distance bins.
-From proposition \ref{thm:remove_bias}, $\hat{\tau}$ will be an unbiased estimate for the `local' effect so long as spillovers do not occur past 200 miles from the TVA.
-
-The results of the long-run analysis from 1940 to 2000 are presented in Panel A Table \ref{tab:tva}.
-The first column lists which dependent variable (measured in logs) was used in the row.
-The following columns contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
+From proposition \ref{thm:remove_bias}, $\hat{\tau}$ will be an unbiased estimate for the `total' effect so long as spillovers do not occur past 200 miles from the TVA.
+
+The results of the long-run analysis from 1940 to 2000 are presented in Panel A of Table \ref{tab:tva}.
+Each row contains the results for a different outcome variable (measured in logs).
+Columns (1)-(5) contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
 The point estimates can be interpreted as decadel growth rates in outcomes.
@@
 aggregating census tracts to metropolitan areas).
-However, this approach collapses the three seperate effects which might each be of interest into a singular aggregate effect.
+However, this approach combines the treatment and spillover effects, which might each be of interest, into a singular aggregate effect.
 I have shown that all three effects of place-based policies can be estimated under very general assumptions about the spillovers.
@@
 
-The intuition from how spillovers cause biases in estimates of the direct effect of treatment extend into the setting where there is staggered adoption in treatment.
-When treatment turns on for different units at different times, two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
+Now, I turn to the common setting where treatment turns on at different times for different units, often called staggered adoption.
+The intuition from how spillovers cause biases in estimates of the total/direct effect of treatment extend into the staggered adoption setting.
+In this setting, the literature has shown that two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
 I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias term(s) from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
@@
 
-In order to estimate treatment effects in the presence of spatial spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} while incorporating spillovers directly into estimation.
+In order to estimate treatment and spillover effects in the presence of spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} by incorporating spillovers directly into estimation similar to equations (\ref{eq:id_total}) and (\ref{eq:id_direct}).
 I assume I observe an independent and identically distributed panel for units $i$ and periods $t$.
-The imputation-based method relies on a model-based assumption for untreated/unexposed units to formalize parallel trends:
+The imputation-based method relies on a model-based assumption for untreated and unexposed potential outcomes to formalize parallel trends:
 \begin{assumption}[Parallel Counterfactual Trends (Staggered)]\label{assumption:parallel_staggered}
@@
 This formalizes parallel trend by imposing that there is a common time-trend in the absence of treatment, $\lambda_t$.
-Note that this does not impose any structure on the effects of treatment and exposure $(D_{it}, h(\vec{D},i))$.
+Note that this does not impose any structure on the effects of treatment and exposure $(D_{it}, h_i(\vec{D}))$.
 I also assume that units do not have any anticipatory effects before treatment starts:
 \begin{assumption}[No Anticipation (Staggered)]\label{assumption:no-anticipation_staggered}
-    For all observations with $D_{it} = 0$ and $h(\vec{D}, i) = 0$, $Y_{it}(D, \vec{h}) = Y_{it}(0,0)$ for all values of $D$ and $\vec{h}$.
+    For all observations with $D_{it} = 0$ and $h_i(\vec{D}) = 0$, $Y_{it}(D, \vec{h}) = Y_{it}(0,0)$ for all values of $D$ and $\vec{h}$.
 \end{assumption}
 
-With a model for $Y_{it}(0, \vec{0})$, treatment effects for individual $i$ and time $t$ under treatment status $D_{it}$ and exposure $h(\vec{D}, i)$ are given by $\tau_{it}(D_{it}, h(\vec{D}, i)) = Y_{it}(D_{it}, h(\vec{D}, i)) - Y_{it}(0, \vec{0})$.
+With a model for $Y_{it}(0, \vec{0})$, treatment effects for individual $i$ and time $t$ under treatment status $D_{it}$ and exposure $h_i(\vec{D})$ are given by $\tau_{it}(D_{it}, h_i(\vec{D})) = Y_{it}(D_{it}, h_i(\vec{D})) - Y_{it}(0, \vec{0})$.
 Then, the total effect and the direct effect are formed similar to above:
 \[
-    \tau_{\text{total}} \equiv \expec{ \tau_{it}(1, h(\vec{D}, i)) \ \vert \ D_{it} = 1} \text{ and }
-    \tau_{\text{direct}} \equiv \expec{ \tau_{it}(1, 0) \ \vert \ D_{it} = 1, h(\vec{D},i) = \vec{0}}.
+    \tau_{\text{total}} \equiv \expec{ \tau_{it}(1, h_i(\vec{D})) \ \vert \ D_{it} = 1} \text{ and }
+    \tau_{\text{direct}} \equiv \expec{ \tau_{it}(1, 0) \ \vert \ D_{it} = 1, h_i(\vec{D}) = \vec{0}}.
 \]
@@
 \[
-    \tau_{\text{total}}^k \equiv \expec{ \tau_{it}(1, h(\vec{D}, i)) \ \vert \ D_{it}^k = 1},
+    \tau_{\text{total}}^k \equiv \expec{ \tau_{it}(1, h_i(\vec{D})) \ \vert \ D_{it}^k = 1},
 \]
@@
 
-The first stage uses untreated and unexposed outcomes to consistently estimate the model (\ref{eq:y0_staggered}).
+The first stage uses untreated and unexposed outcomes to estimate (\ref{eq:y0_staggered}).
 Then, $\tilde{Y}_{it}$ will serve as an estimate for $\tau_{it}$.
-The second stage regression can be used to estimate averages of $\tau_{it}$ for different groups depending on the parameters of interest.
+The second stage estimate averages of $\tau_{it}$ for different groups depending on the parameters of interest.
 This is equivalent to regressing the residual $\tilde{Y}_{it}$ on dummy variable(s).
@@
 
-As discussed in \citet{Gardner_2021}, inference must account for the fact that the regressand in the second stage is estimated in step 1.
+As discussed in \citet{Gardner_2021}, inference must account for the fact that the regressand in the second stage is estimated in the first stage.
 \citet{Gardner_2021} propose reframing the two-stage process as a two-stage GMM estimator and discusses how to perform valid inference in this setting.
 This procedure is implemented in the R/Stata package \texttt{did2s} \citep{did2s}.
-
-% ------------------------------------------------------------------------------
-\subsection{Application on Community Health Centers}\label{sec:chc}
-% ------------------------------------------------------------------------------
-
-As an application of the above methods, I extend the analysis of \citet{Bailey_Goodman_Bacon_2015}.
-The authors study the creation of federal community health centers between 1965 and 1974 that provided \textit{primary} care to low-income communities.
-They test the hypothesis if access to low/no- cost health care services decreased mortality rates on the treated population.
-To answer this question, the authors use a common event-study framework to compare outcomes in treated counties to all other US counties by estimating the following specification
-\begin{equation}\label{eq:chc_es}
-    Y_{it} = \theta_i + X_{it} \beta + \sum_{k = -7}^{-2} \pi_y D_{it}^k + \sum_{k = 0}^{15} \tau_{y} D_{it}^k + \varepsilon_{it},
-\end{equation}
-where $D_i^k$ is the typical `event study' indicator for being treated for $k$ years, $\theta_i$ is county fixed effects, and $X_{it}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed effects, and urban-group fixed effects.
-A full list can be found on page 1080 of \citet{Bailey_Goodman_Bacon_2015}.} The coefficents $\pi_y$ can be interpreted as tests of parallel pre-trends and $\tau_y$ can be interepreted as the treatment effect of a community health center $y$ years after establishment.
-In years following the establishment of the community health centers, the authors find a reduction of between 15-30 deaths per 100,000 residents compared to a baseline adjusted mortality rate of 929 deaths per 100,000 residents.
-
-% Figure: Direct and Spillover Effects of Community Health Centers
-\begin{figure}[tb!]
-    \caption{Direct and Spillover Effects of Community Health Centers}
-    \label{fig:chc_es_spill}
-
-    {\centering
-        \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
-    }
-    {\footnotesize
-        \textit{Notes:} This figure plots event study estimates for the total effect and the spillover effect on control units within 25 miles of treatment at different periods relative to establishment year.
-The estimates are generated using the `did2s' package \citep{did2s}.
-    }
-\end{figure}
-
-There are theoretical reasons to think spillovers may or may not exist in this context.
-On the one hand, individuals outside the county can potentially travel to the community health centers to receive care.
-This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
-On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergency but rather primary care services.
-In this case, it is less likely low-income individuals would travel very far to receive primary care and hence the spillover effects is potentially near zero.
-My methodology can provide an answer to the question of how far do individuals travel for low/no -cost primary care.
-
-As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
-Then, I follow \citet{Callaway_SantAnna_2020} in estimating event-study coefficients.
-The results are presented in Figure \ref{fig:chc_es_spill}.
-The confidence intervals labeled with circles represent point estimates for the average spillover effect on control units within 25 miles.
-No spillover effect is estimated to be significantly different from zero which suggests that the effects of community health centers are very local.
-Since there are near zero spillover effects, the direct effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
-
-The spillover effects results provide evidence that low-income individuals will not travel far to receive primary care.
-Practically, this suggests that community health centers should be targeted to be as accessible as possible for poor individuals as they are unable to travel far to access the services.
+In appendiex section (\ref{sec:chc}), I use this two-stage estimator to revisit the analysis of \citet{Bailey_Goodman_Bacon_2015}.
 
@@
 This paper has considered the common environment where treatment is assigned via administrative boundary while the effects of treatment spread across these borders.
-In this context, difference-in-differences estimation will identify a combination of the direct effect of treatment and two additional terms resulting from spillovers.
-I use a potential outcomes framework that formalizes spillovers to improve upon ad-hoc estimation strategies by proposing a new estimation strategy that is robust to more forms of spillovers.
-In particular, I find that specifications with an indicator for being ``close to'' treated units interacted with treatment status will remove all bias in the direct effect estimate so long as all units affected by spillovers are contained in the indicator.
-More, I show that a set of concentric `rings' are the best at capturing the spatial structure of spillovers.
-When estimating spillover effects themselves, I find that it is important to correctly identify is spillovers are additive or non-additive in the number of nearby treated units.
+I model this phenomenon in a potential outcomes framework and show why difference-in-differences estimation does not identify any treatment effect of interest.
+I then improve upon ad-hoc estimation strategies by proposing a new estimation strategy that is robust to more forms of spillovers.
+In particular, I find that specifications with an indicator for being ``close to'' treated units will remove all bias in the treatment effect estimate so long as all units affected by spillovers are contained in the indicator under a modified parallel trends assupmtion.
+More, I show that a set of concentric `rings' are able to remove all the bias and improve estimation of spillover effects.
+A limitation of this research is in deciding how wide and how many rings to include in estimation.
+Concurrent work by \citet{Butts_2021} discusses data-driven ring selection under a more stringent parallel trends assumption that does not readily apply in the context of large geographic units such as counties.
 
@@
 
-% \section*{Acknowledgements}
-
-% I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, and participants of the Western Economics Association Conference and the CU Boulder Labor Economics Seminar for helpful feedback.
-
 % ------------------------------------------------------------------------------
@@
 \appendix 
+\numberwithin{equation}{section}
+\numberwithin{figure}{section}
+\numberwithin{table}{section}
+\renewcommand{\thefigure}{\Alph{section}\arabic{figure}}
+\renewcommand{\thetable}{\Alph{section}\arabic{table}}
 % ------------------------------------------------------------------------------
@@
 % ------------------------------------------------------------------------------
-\subsection{Proof of Theorem \ref{thm:bias}}
+\subsection{Proof of Proposition \ref{thm:bias}}
 % ------------------------------------------------------------------------------
@@
     &\underbrace{\expec{Y_{i1} - Y_{i0} \mid D_i = 1 } - \expec{Y_{i1} - Y_{i0} \mid D_i = 0 }}_{\text{Difference-in-Differences}} \\
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) \mid D_i = 0 } \\
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } \\
-    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 } \\
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0} \\ 
-    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\ 
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1} \\
-    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\  
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 } \\
-    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 1 } - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
-    &= \expec{Y_{i1}(1, h(\vec{D}, i)) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 } \\
-    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\
-    &= \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1} + \expec{Y_{i1}(1, h(\vec{D}, i)) - Y_{i1}(1, \vec{0}) \mid D_i = 1} \\
-    &\quad\quad - \expec{Y_{i1}(0, h(\vec{D}, i)) - Y_{i1}(0, \vec{0}) \mid D_i = 0} \\
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) \mid D_i = 0 } \\
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } \\
+    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) + Y_{i1}(0, \vec{0}) - Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0 } \\
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 0} \\ 
+    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\ 
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0})  \mid D_i = 1 } - \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \mid D_i = 1} \\
+    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\  
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0, \vec{0}) - Y_{i1}(0, \vec{0}) + Y_{i0}(0, \vec{0})\mid D_i = 1 } \\
+    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 } - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 } \\
+    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\
+    &= \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1} + \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1} \\
+    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0} \\
     &\equiv \tau_{\text{direct}} + \tau_{\text{spill}}(1) - \tau_{\text{spill}}(0) = \tau_{\text{total}} - \tau_{\text{spill}}(0) \\
@@
 % ------------------------------------------------------------------------------
-\subsection{Proof of Theorem \ref{thm:remove_bias}}
+\subsection{Proof of Proposition \ref{thm:remove_bias}}
 % ------------------------------------------------------------------------------
@@
     &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} \\
-    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1} \\
-    &\quad\quad= \expec{Y_{i1}(1, h(\vec{D},i)) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
+    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} \\
+    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1} \\
+    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
     &\quad\quad\equiv \tau_{\text{total}},
@@
 % ------------------------------------------------------------------------------
+\section{Application on Community Health Centers}\label{sec:chc}
+% ------------------------------------------------------------------------------
+
+As an application of the above methods, I extend the analysis of \citet{Bailey_Goodman_Bacon_2015}.
+The authors study the creation of federal community health centers between 1965 and 1974 that provided \textit{primary} care to low-income communities.
+They test the hypothesis if access to low/no- cost health care services decreased mortality rates on the treated population.
+To answer this question, the authors use a common event-study framework to compare outcomes in treated counties to all other US counties by estimating the following specification
+\begin{equation}\label{eq:chc_es}
+    Y_{it} = \theta_i + X_{it} \beta + \sum_{k = -7}^{-2} \pi_y D_{it}^k + \sum_{k = 0}^{15} \tau_{y} D_{it}^k + \varepsilon_{it},
+\end{equation}
+where $D_i^k$ is the typical `event study' indicator for being treated for $k$ years, $\theta_i$ is county fixed effects, and $X_{it}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed effects, and urban-group fixed effects.
+A full list can be found on page 1080 of \citet{Bailey_Goodman_Bacon_2015}.} The coefficents $\pi_y$ can be interpreted as tests of parallel pre-trends and $\tau_y$ can be interepreted as the treatment effect of a community health center $y$ years after establishment.
+In years following the establishment of the community health centers, the authors find a reduction of between 15-30 deaths per 100,000 residents compared to a baseline adjusted mortality rate of 929 deaths per 100,000 residents.
+
+% Figure: Direct and Spillover Effects of Community Health Centers
+\begin{figure}[tb!]
+    \caption{Direct and Spillover Effects of Community Health Centers}
+    \label{fig:chc_es_spill}
+
+    {\centering
+        \includegraphics[width=\textwidth]{../../figures/figure-chc-es_combined.pdf}
+    }
+    {\footnotesize
+        \textit{Notes:} This figure plots event study estimates for the total effect and the spillover effect on control units within 25 miles of treatment at different periods relative to establishment year.
+The estimates are generated using the `did2s' package \citep{did2s}.
+    }
+\end{figure}
+
+There are theoretical reasons to think spillovers may or may not exist in this context.
+On the one hand, individuals outside the county can potentially travel to the community health centers to receive care.
+This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
+On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergency but rather primary care services.
+In this case, it is less likely low-income individuals would travel very far to receive primary care and hence the spillover effects is potentially near zero.
+My methodology can provide an answer to the question of how far do individuals travel for low/no -cost primary care.
+
+As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
+Then, I follow \citet{Callaway_SantAnna_2020} in estimating event-study coefficients.
+The results are presented in Figure \ref{fig:chc_es_spill}.
+The confidence intervals labeled with circles represent point estimates for the average spillover effect on control units within 25 miles.
+No spillover effect is estimated to be significantly different from zero which suggests that the effects of community health centers are very local.
+Since there are near zero spillover effects, the direct effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
+
+The spillover effects results provide evidence that low-income individuals will not travel far to receive primary care.
+Practically, this suggests that community health centers should be targeted to be as accessible as possible for poor individuals as they are unable to travel far to access the services.
+
+% ------------------------------------------------------------------------------
 \section{Monte Carlo Simulations}
@@
 To illustrate the above discussion, I turn to a set of Monte Carlo simulations.
-The first exercise is to consider a set of different data generating processes and see how well estimates of the direct effect perform when controlling for spillovers using potentially misspecified exposure mappings.
-In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h(\vec{D}, i)$.
+The first exercise is to consider a set of different data generating processes and see how well estimates of the total effect perform when controlling for spillovers using potentially misspecified exposure mappings.
+In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h_i(\vec{D})$.
 I generate data for unit $i$ is a US county at time $t \in \{1, \dots, 20\}$ using the following data-generating process:
 \begin{equation}\label{eq:dgp_general}
-    y_{it} = \lambda_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it},
+    y_{it} = \lambda_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h_i(\vec{D}) + \varepsilon_{it},
 \end{equation}
 where $\lambda_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is IID and distributed as $\varepsilon_{it} \sim N(0, 2^2)$.
-
 For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are the same.
@@
 The set of spillover specifications included in the data-generating process are `Within $40/80$mi.' which equals 1 if the counties' center of population is within $40/80$ miles to a treated county's center of population.
+This corresponds to different choices of $\bar{D}$ and hence $S_i$ in the text.
 `Within $40/80$mi.
@@
 However, if the true specification is non-additive, then the additive specification no longer will remove all the bias from the direct effect estimate.
+Hence, if the direct effect is of principal concern, then the non-additive rings estimate is preferred.
 
@@
 \begin{equation}\label{eq:mspe}
-    1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}.
+    1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h_i(\vec{D}) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h_i(\vec{D}))^2}.
 \end{equation} 

### 2021-11-04 figure-rings_example.R
Update README

@@ -197,3 +197,7 @@ ggsave(
 	here::here("figures/figure-rings_v_within.pdf"), plot_both, 
 	width = 8, height = 8 * 9/16, dpi = 300
 )
+ggsave(
+	here::here("figures/figure-rings_v_within.png"), plot_both, 
+	width = 8, height = 8 * 9/16, dpi = 300
+)

### 2021-11-04 figure-rings_example.R
Quick Fix

@@ -197,7 +197,3 @@ ggsave(
 	here::here("figures/figure-rings_v_within.pdf"), plot_both, 
 	width = 8, height = 8 * 9/16, dpi = 300
 )
-ggsave(
-	here::here("figures/figure-rings_v_within.png"), plot_both, 
-	width = 8, height = 8 * 9/16, dpi = 300
-)

### 2021-11-04 latex/paper/Spillover.tex
Fixed typos and grammar

@@
 geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, individuals in control areas can travel to the treated areas and receive treatment (e.g.
-a hospital opening serves nearby residents) or shocks to a labor market can have feedback loops that affect nearby areas (e.g.
+a hospital opening serves nearby residents), or shocks to a labor market can have feedback loops that affect nearby areas (e.g.
 a new factory opening increases service sector spending in the commuting zone).
@@
 Using this potential outcome framework, I define the different possible treatment/spillover effects of interest and the relative advantage and interpretation of each.
-First, there is the `switching effect' which is the relevant parameter for local policy makers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
+First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
 It is difficult to estimate the switching effect without parametric assumptions.
@@
 For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities versus the case where a close neighbor already has constructed one.
-Therefore, switching effects are defined seperately for each level of exposure and estimation of a switching effect requires knowledge of which units experience the same level of exposure.
+Switching effects therefore are defined separately for each level of exposure, and estimation of a switching effect requires knowledge of which units experience the same level of exposure.
 While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions.
-This effect is the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatment.
+This effect is the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatments.
 That is, what are the effects of turning on a unit's treatment if this were the \emph{only} unit to be treated in their area.
 
-Second, there is the `total effect' which is the relevant parameter for national policy makers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
+Second, there is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
 This treatment effect summarizes what were the effects of going from the world with no treatment to the entire vector of treatment status.
 This effect comes from two sources: the direct effect and the average spillover effect from other treated units.
-Unlike the switching effect, the total effect effect is nonparametrically identified under a mild assumption that spillovers are `local' in that spillovers are only experienced within a certain distance from treatment.
-
-This paper shows that the difference-in-differences esitmator is a biased estimate for the total effect because of spillover effects on control units.
+Unlike the switching effect, the total effect is nonparametrically identified under a mild assumption that spillovers are `local' in that spillovers are only experienced within a certain distance from treatment.
+
+This paper shows that the difference-in-differences estimator is a biased estimate for the total effect because of spillover effects on control units.
 The intuition is that untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
@@
 I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
-The other two treatment effects considered are able to be identfified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
+The other two treatment effects considered can be identified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
 This would hold in the case where individuals can travel to access treatment.
 This could fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g.
-San Francisco being affected by shocks to New York economy).
+San Francisco being affected by shocks to the New York economy).
 
@@
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
-The only assumption required is selecting the maximum distance from treated units spillovers can occur.\footnote{Since treatment effects typically decay over distance, even if the maximum distance is not large enough, most of the bias will still be removed.
-On the other hand, making the maximum distance too large, will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}
+The only assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, even if the maximum distance is not large enough, most of the bias will still be removed.
+On the other hand, making the maximum distance too large will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}
 
 The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of average spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers.
-The above method can be improved by creating a set of distance bins from treated units (e.g.
-being 0-20 miles, 20-40 miles, 40-60 miles from treated unit) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
-In some cases, the bins can be determined in a data driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single large indicator, this estimator still consistently estimates the treatment effect of interest.
+The above method can be improved by creating a set of distance bins from the treated units (e.g.
+being 0-20 miles, 20-40 miles, 40-60 miles from the treated units) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
+In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single large indicator, this estimator still consistently estimates the treatment effect of interest.
 This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.
@@
 I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
-The Tennessee Valley Authority was a large scale New Deal program that lowered the cost of power for industrial firms \citep{Kitchens_2014}.
-The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastucture and agglomeration economies \citep{Severnini_2014}.
+The Tennessee Valley Authority was a large-scale New Deal program that lowered the cost of power for industrial firms \citep{Kitchens_2014}.
+The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastructure and agglomeration economies \citep{Severnini_2014}.
 I show that estimation by difference-in-differences fails to account for these spillovers and therefore forms biased estimates of the local effect of the Tennessee Valley Authority.
@@
 I revisit conflicting results about United States' federal Empowerment Zones, a program that creates incentives for businesses to locate in high-poverty neighborhoods.
-\citet{Busso_Gregory_Kline_2013} use Census Tracts from qualified but ultimately rejected applications that are typically far away from accepted Zones as a comparison group and find that significant reductions in poverty.
+\citet{Busso_Gregory_Kline_2013} use Census Tracts from qualified but ultimately rejected applications that are typically far away from accepted Zones as a comparison group and find significant reductions in poverty.
 This empirical strategy is based on the idea that since they also qualified for the program, these comparison units would be on parallel trends without being contaminated by spillover effects from treatment.
@@
 Their proposed two-stage estimator first estimates group and time fixed-effects using untreated/not-yet-treated observations.
-Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed effects.
+Since some control/not-yet-treated units can be affected by spillovers, these units must be removed to consistently estimate the group and time fixed-effects.
 Then these estimated unit and time fixed-effects are subtracted from the observed outcome \emph{in the full sample}.
 The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects.
-
-I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.
-They find that the health centers significantly lowered the mortality rate in treated counties.
-I find that in this context, since the mortality declines caused by the health centers was due to primary care, spillover effects are near-zero.
-This result shows the importance of accessability concerns when targeting programs in low-income areas.
+In the online appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.
 
@@
 Other papers derive results for specific spillover mappings and if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs.
-The literatuere has focused on estimating the total effect, so I contribute by discussing alternative treatment effect estimates and identification results.
-Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in event-study framework which allows for the common occurence of staggered treatment adoption.
+The literature has focused on estimating the total effect, so I contribute by discussing alternative treatment effect estimates and identification results.
+Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.
 
@@
 There are two main strands of this literature.
-First, there is a large literature on estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
-Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects.
+First, there is a large literature on the estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
+Examples in the literature include: \citet{Halloran_Struchiner_1995} consider community-vaccine rates in epidemiology; \citet{Miguel_Kremer_2004} consider deworming programs in Kenyan schools; \citet{Sobel_2006} considers interference in the Moving to Opportunity Program; and \citet{Angrist_2014} studies the context of school peer effects.} Estimation compares units in the partially treated clusters with control units in completely untreated clusters which do not receive spillover effects.
 This allows standard difference-in-differences estimation of both the total effect (treatment effect on the treated) and spillover effects (treatment effect on the untreated in the treated clusters).
 However, in many settings distinct clusters are not plausible, e.g.
-counties near the border of a state can effect eachother.
-My proposed estimator generalizes this method by using control units are unaffected by treatment without requiring a notion of clusters.
+counties near the border of a state can affect each other.
+My proposed estimator generalizes this method by using control units that are unaffected by treatment without requiring a notion of clusters.
 
@@
 Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
-I also contribute in this literature by thinking about different definitions of treatment effects and their identification in non-experimental settings.
+I also contribute to this literature by thinking about different definitions of treatment effects and their identification in non-experimental settings.
 
@@
 Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
-Section \ref{sec:estimation} focuses on estimation of the direct and spillover effects of treatment.
+Section \ref{sec:estimation} focuses on the estimation of the direct and spillover effects of treatment.
 I evaluate currently used solutions in the literature and present a set of recommendations to more robust estimation strategies.
@@
 This section will present a potential outcome framework that formalizes spatial spillovers.
-The goal of this exercise is to formalize treatment effects which are no longer uniquely defined in settings with spillovers.
+The goal of this exercise is to formalize treatment effects that are no longer uniquely defined in settings with spillovers.
 Following the canonical difference-in-differences framework, I observe a panel of units for periods $t \in \{0,1\}$ and treatment turns on between periods for some of the units.\footnote{This can be extended to multiple periods by replacing $Y_{i0}$ and $Y_{i1}$ throughout with pre- and post- sample averages of $Y_{it}$.
@@
 \begin{assumption}[Random Sampling]\label{assumption:random}
-    $\{ Y_{i0}, Y_{i1}, D_{i} \}_{i = 1}^{n}$ are independent and identically distributed sample of panel data.
+    $\{ Y_{i0}, Y_{i1}, D_{i} \}_{i = 1}^{n}$ is an independent and identically distributed sample of panel data.
 \end{assumption}
@@
 \begin{example}
-    $h_i(\vec{D})$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure which tells the distance unit $i$ is from unit $j$.
+    $h_i(\vec{D})$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly, a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure that is the distance between unit $i$ and $j$.
 In this case \begin{equation}\label{eq:h_within}
@@
 For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
-In this case the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library.
-The benefits of access to a neighboring town library does not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
+In this case, the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library.
+The benefits of access to a neighboring town library do not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
 \end{example}
@@
     Last, $h_i(\vec{D})$ is a spatial decay function where exposure decreases with distance.
-In this case, spillover intensity is the sum across all treated observations' decay term, i.e.
+In this case, spillover intensity is the sum across all treated observations' decay terms, i.e.
 \begin{equation}\label{eq:h_decay}
@@
     \end{equation} 
-    This exposure mapping allows for the intensity of spillovers to depend on distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units.
-This creates problems with inference because it implies potential correlation between all units' error terms.
-For this reason, this function often is summed over only the $k$-nearest neighbors or over units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least squares routine.
+    This exposure mapping allows for the intensity of spillovers to depend on the distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units.
+This creates problems with inference because it implies a potential correlation between all units' error terms.
+For this reason, this function often is summed over only the $k$-nearest neighbors or units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least-squares routine.
 In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
@@
 
-Often times, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers in a way similar to the above examples.
+Often, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers in a way similar to the above examples.
 Estimation in this case will rely on the functional form assumptions made by researchers.
@@
 In particular, I will redefine the standard difference-in-differences identifying assumptions in the context of the new potential outcome framework.
-First, I assume that units do not adjust there actions in period $0$ to knowledge of future treatment  and therefore:
+First, I assume that units do not adjust their actions in period $0$ from knowledge of future treatment:
 \begin{assumption}[No Anticipation]\label{assumption:no-anticipation}
@@
 
-In setups without spillovers, treatment effects for an individual unit is well defined as $\tau_i \equiv Y_{i1}(1) - Y_{i1}(0)$, i.e.
-the effect of turning on treatment for a unit, and the above two assumptions would lead to identification of the average effect by the traditional difference-in-differences estimator.
-In the presence of spillovers, there are multiple treatment effects that can be defined in this setting.
+In setups without spillovers, the treatment effect for an individual unit is well defined as $\tau_i \equiv Y_{i1}(1) - Y_{i1}(0)$, i.e.
+the effect of turning on treatment for a unit, and the above two assumptions would lead to the identification of the average effect by the traditional difference-in-differences estimator.
+In the presence of spillovers, multiple treatment effects can be defined in this setting.
 This subsection will define them and discuss their relative advantages/disadvantages.
@@
 This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant.
-This treatment effect is policy relevant as it summarizes what would happen if a `local' policy makers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).\footnote{This is what \citet{Savje_Aronow_Hudgens_2021} call the `assignment-conditional unit-level treatment effect'.} It is important to note that the switching effect can depend on the level of exposure.
+This treatment effect is policy-relevant as it summarizes what would happen if a `local' policymakers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).\footnote{This is what \citet{Savje_Aronow_Hudgens_2021} call the `assignment-conditional unit-level treatment effect'.} It is important to note that the switching effect can depend on the level of exposure.
 For instance, consider the construction of libraries in towns.
 The effect of library construction in a town that is far away from any other library (exposure of $\vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h_i(\vec{D})$.
-Since the size of the switching effect depends on a units exposure level, we will consider an average switching effect at each value of exposure,
+Since the size of the switching effect depends on a unit's exposure level, we will consider an average switching effect at each value of exposure,
 \[
@@
 This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$.
-This treatment effect is helpful for `national' policy makers in order to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.
+This treatment effect is helpful for `national' policymakers to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.
 
@@
 Other treated units could, for instance, experience positive spillover effects due to agglomeration economies.
-When it is the case that spillover effects depend on treatment status, the switching effect can be thought of as two seperate effects.
-First, the unit is affected by changing its own treatment status as summarized by the direct effect.
+When it is the case that spillover effects depend on treatment status, the switching effect can be thought of as two separate effects.
+First, the unit is affected by changing its treatment status as summarized by the direct effect.
 Second, the unit changes from experiencing spillover effects as a control unit to experiencing spillover effects as a treated unit.
@@
 
-Researchers typically estimate the canonical two-way fixed effects model, 
+Researchers typically estimate the canonical two-way fixed-effects model, 
 \begin{equation}\label{eq:twfe}    
@@
 \end{equation}
-The estimator $\hat{\tau}$, which is well understood to be the sample analog of (\ref{eq:did}), is therefore a biased estimate for $\tau_{\text{direct}}$ and $\tau_{\text{total}}$ in the presence of spillovers.
+The estimator $\hat{\tau}$, which is well understood to be the sample analog of (\ref{eq:did}), is, therefore, a biased estimate for $\tau_{\text{direct}}$ and $\tau_{\text{total}}$ in the presence of spillovers.
 In particular, if a researcher estimates a difference-in-differences model and reports $\hat{\tau}$ as an estimate of the total effect, their estimate would be biased in the presence of spillover effects on control units.
@@
 
-The following subsection will talk about identification of treatment effects and present corresponding estimators for each effect.
+The following subsection will talk about the identification of treatment effects and present corresponding estimators for each effect.
 
@@
 
-It is difficult to identify the switching effect in general as identifying the unobserved counterfactual outcome $Y_{i1}(0, h_i(\vec{D}))$ requires knowledge of which control units have same level of exposure.
+It is difficult to identify the switching effect in general as identifying the unobserved counterfactual outcome $Y_{i1}(0, h_i(\vec{D}))$ requires knowledge of which control units have the same level of exposure.
 The reason for this can be seen by rewriting this in terms of a difference-in-differences style estimand:
@@
 Writing it in this way highlights the two problems in estimating the second term.
-First, this requires knowledge of the unobserved exposure mapping to be correctly specified in order to identify control units with $h_i(\vec{D}) = h$.
+First, this requires knowledge of the unobserved exposure mapping to be correctly specified to identify control units with $h_i(\vec{D}) = h$.
 More, this estimand requires a more demanding parallel trends assumption.\footnote{This problem is similar to those highlighted by \citet{Callaway_Goodman-Bacon_SantAnna_2021} for difference-in-differences with continuous treatment.}
@@
 This assumption requires parallel trends among treated and control units at exposure $\vec{h}$.
-This assumption is implied by \nameref{assumption:parallel} and an additional assumption that spillover effects being equal between control and treated units that experience exposure $\vec{h}$.
+This assumption is implied by \nameref{assumption:parallel} and an additional assumption that spillover effects are equal between control and treated units that experience exposure $\vec{h}$.
 Under this assumption, the switching effect can be identified.
@@
 However, this approach relies on correct specification of the exposure mapping which is a difficult assumption to maintain in practice.
-Researchers may be tempted to introduce the parameterized exposure mapping linearly in order to ``compare individuals at the same level $\vec{h}$''.
-However, this assumes additive seperatability between the treatment dummy and the exposure mapping.
-Additive seperatability would imply the switching effect does not depend on exposure level, i.e.
+Researchers may be tempted to introduce the parameterized exposure mapping linearly to ``compare individuals at the same level $\vec{h}$''.
+However, this assumes additive separability between the treatment dummy and the exposure mapping.
+Additive separability would imply the switching effect does not depend on exposure level, i.e.
 the switching effect is constant across $\vec{h}$.
@@
 
-To identify the direct and total effects, additional assumptions on the nature of spillover effects is needed.
+To identify the direct and total effects, additional assumptions on the nature of spillover effects are needed.
 In particular, I will formalize the idea that spillovers are `local' in that units are only affected by treatment if they are near treatment.
 For example, if treatment has to be accessed in person, then it is natural that further away places are not affected by treatment.
-However this example may fail under general equilibrium shocks that do not necessarily decay over distance.
+However, this assumption may fail under general equilibrium shocks that do not necessarily decay over distance.
 
@@
 
-The intuition behind identifying the direct effect seperately from the spillover effects requires that we use control units experiencing no spillover effects to identify the counterfactual trend and use treated units experiencing no spillover effects to identify the direct effect.
+The intuition behind identifying the direct effect separately from the spillover effects requires that we use control units experiencing no spillover effects to identify the counterfactual trend and use treated units experiencing no spillover effects to identify the direct effect.
 Since we are leveraging subgroups of treated and control units, we need a parallel trends assumption for each subgroup:
@@
 It is worth remarking on \nameref{assumption:parallel-mod} in terms of applied work.
-Often times, individuals use only a subsample of observations that are close to treated observations in estimating their difference-in-differences model.
+Often, individuals use only a subsample of observations that are close to treated observations in estimating their difference-in-differences model.
 The idea is that close units are more likely to be on similar counterfactual trends than units that are further away.
-The identification result and it's corresponding estimator are formed by using further away units (i.e.
+The identification result and its corresponding estimator are formed by using further away units (i.e.
 units with $S_i = 0$).
@@
 The proof is given in Appendix \ref{sec:proofs}, but the intuition is simple.
-Conditioning on $S_i = 0$ will use only observations with $h_i(\vec{D}) = 0$ which give rise to identification of the direct and total effect.
-This proposition shows that a researcher does not need to know how the spillovers occur over space in order to have an unbiased estimate for treatment effects.
+Conditioning on $S_i = 0$ will use only observations with $h_i(\vec{D}) = 0$ which gives rise to the identification of the direct and total effect.
+This proposition shows that a researcher does not need to know how the spillovers occur over space to have an unbiased estimate for treatment effects.
 All that is required to identify the direct or total effects is being able to classify which units are considered `close' to treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
@@
 
-In order to estimate the direct effect and the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
-However, it will prove advantageous to modify the two-way fixed effects model to estimate the direct or the total effect because it will also allow estimation of spillover effects as well.
+to estimate the direct effect and the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
+However, it will prove advantageous to modify the two-way fixed-effects model to estimate the direct or the total effect because it will allow the estimation of spillover effects as well.
 To estimate the total effect, the modified model is given by:
@@
 However, it is important to account for two sources of correlation in the error structure.
-First, errors should be clustered by unit $i$ to allow for correlation across time periods.
-Second, since our model is predicated on the fact that nearby places effect one another, we should account for such spatial correlation by allowing for spatial correlations following \citet{Conley_1999}.
+First, errors should be clustered by unit $i$ to allow for correlation across periods.
+Second, since our model is predicated on the fact that nearby places affect one another, we should account for such spatial correlation by allowing for spatial correlations following \citet{Conley_1999}.
 More recent work by \citet{Ferman_2020} show that for large-n asymptotics to be used, the structure of spatial correlation must be limited in that errors are assumed to be uncorrelated after a certain cutoff distance.
@@
 
-A natural question is why wouldn't researchers make the distance really large in order to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$ or $\tau_{\text{total}}$?
+A natural question is why wouldn't researchers make the distance large to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$ or $\tau_{\text{total}}$?
 Equation (\ref{eq:id_total}) and (\ref{eq:id_direct}) should make this problem clear.
@@
 On the other hand, having units that experience spillovers not included in the $S_i$ indicator will leave some bias in the estimate.\footnote{Although, spillover effects typically will grow weaker over distance and if distant units are mistakenly treated as if they have zero exposure, bias should be small.} Therefore there is a bias-variance trade-off in extending the extent of $S_i$ that should be balanced by researchers guided by their particular economic context.
-In seperate work, \citet{Butts_2021} discusses data-driven methods to determine how far $S_i$ should be under a more strict parallel trends assumption.
+In separate work, \citet{Butts_2021} discusses data-driven methods to determine how far $S_i$ should be under a more strict parallel trends assumption.
 
@@
 
-It is possible to more accurately estimate spillover effects by using a set of concentric ring indicators (e.g 0-20 miles, 20-40 miles and 40-60 miles from the nearest treated unit) instead of a single large ring indicator to more flexibly estimate the spillover effects.
+It is possible to more accurately estimate spillover effects by using a set of concentric ring indicators (e.g 0-20 miles, 20-40 miles, and 40-60 miles from the nearest treated unit) instead of a single large ring indicator to more flexibly estimate the spillover effects.
 For example, for the total effect, equation (\ref{eq:twfe_total}) can be modified as
@@
 
-A simple example of how rings improves estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
-The figure displays observations of $Y_{i,1} - Y_{i,0}$ on the y-axis and the distance to the nearest treated unit on the $x$-axis and treated units are placed at a zero distance for visualization purposes.
+A simple example of how rings improve the estimation of spillover effects can be seen in Figure \ref{fig:example_rings}.
+The figure displays observations of $Y_{i,1} - Y_{i,0}$ on the y-axis and the distance to the nearest treated unit on the $x$-axis.
+Treated units are placed at a zero distance for visualization purposes.
 The example has a counterfactual trend of 2 so any difference from 2 is due to either treatment/spillover effects and the error term.
@@
 This number masks that units within the first 15 miles have a treatment effect of 1 or larger and units between 40 and 60 miles have 0 spillover effects.
-Figure (b) on the other hand uses 4 indicators for every 15 mile interval (0-15, 15-30, 30-45, and 45-60 miles).
-This improves on the estimate of a single ring in two ways.
+Figure (b) on the other hand uses 4 indicators for every 15-mile interval (0-15, 15-30, 30-45, and 45-60 miles).
+This improves the estimate of a single ring in two ways.
 Multiple rings are better able to capture the decaying nature of spillover effects over distance.
 Furthermore, the ring that is included past the true maximum distance where spillover effects occur (45-60 miles) has a point estimate near zero.
-The rings method acts a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to $\bar{d}$ satisfying assumption (\ref{assumption:local})).
-However, precision of estimates would decrease as the number of rings increase and therefore there is a bias-variance trade-off in the number and width of rings.\footnote{\citet{Clarke_2017} proposes a cross-validation technique for optimally choosing the number of rings and their techniques that uses the out-of-sample mean square prediction error as a way to estimate the bias-variance tradeoff.
+The rings method is a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to $\bar{d}$ satisfying assumption (\ref{assumption:local})).
+However, the precision of estimates would decrease as the number of rings increases and therefore there is a bias-variance trade-off in the number and width of rings.\footnote{\citet{Clarke_2017} proposes a cross-validation technique for optimally choosing the number of rings and their techniques that uses the out-of-sample mean square prediction error as a way to estimate the bias-variance tradeoff.
 \citet{Butts_2021} provides a data-driven method to selecting rings under a more strict version of the parallel trends assumption.}
 
-One disadvantage of using a set of indicator for \textit{the nearest} treated unit is that some spillover effects are additive in the number of nearby treated units.
+One disadvantage of using a set of indicators for \textit{the nearest} treated unit is that some spillover effects are additive in the number of nearby treated units.
 In this case, summarizing exposure by the distance to the closest treated unit fails to capture important information on the location of other treated units and the coefficients on the ring indicators might be interpreted incorrectly.
-One potential solution is to count the number of treated units within each ring instead of creating indicators for nearest treated unit.
+One potential solution is to count the number of treated units within each ring instead of creating indicators for the nearest treated unit.
 This additive version of rings however no longer removes all bias from the direct effect of treatment unless the exposure mapping is correctly specified.
-Therefore, if spillover effects are expected to be additive in nature, seperate estimation of the direct effect and spillover effects would be the preferred method.
+Therefore, if spillover effects are expected to be additive in nature, separate estimation of the direct effect and spillover effects would be the preferred method.
 
@@
 To illustrate the importance of accounting for spatial spillovers in the estimation of treatment effects, I revisit the analysis of the Tennessee Valley Authority (TVA) in \citet{Kline_Moretti_2014}.
-The TVA program was a large-scale federal investment started in 1934 that focused on construction of dams and transportation canals in an attempt to modernize the Tennessee Valley's economy.
+The TVA program was a large-scale federal investment started in 1934 that focused on the construction of dams and transportation canals in an attempt to modernize the Tennessee Valley's economy.
 By the end of WWII, the TVA became the largest single power supplier in the country and significantly lowered the cost of wholesale energy for factories.\footnote{More details on the program are found in \citet{Kline_Moretti_2014}.
-The effects on wholseale electricity are discussed in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
-\citet{Kline_Moretti_2014} analyze a range of outcome variables, but for succinctness I use only (the log of) agricultural and manufacturing employment.
+The effects on wholeseale electricity are discussed in \citet{Kitchens_2014}.} With over \$20 Billion (in 2000 dollars) spent which is hundreds of dollars transferred per person in the Authority, the impacts are very likely to extend past the authority's borders.
+\citet{Kline_Moretti_2014} analyze a range of outcome variables, but for succinctness, I use only (the log of) agricultural and manufacturing employment.
 Since the TVA primarily improved manufacturing industries through large-scale electrification, the authors predict that employment will grow in manufacturing and shrink in agricultural as workers switch to higher-paying manufacturing jobs.
 
-The analysis in \citet{Kline_Moretti_2014} begins by comparing changes in county-level outcomes from 1940 to either 1960 (short-run effects) or 2000 (long-run effects) between treated counties in the Authority and control counties outside.
+The analysis in \citet{Kline_Moretti_2014} begins by comparing changes in county-level outcomes from 1940 to either 1960 (short run effects) or 2000 (long run effects) between treated counties in the Authority and control counties outside.
 The primary specification is
@@
 The authors use an Oaxaca-Blinder estimator on the first differences and the results of \citet{Kline_2011} show that this estimator is equivalent to a weighted difference-in-differences estimate.
-Their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.} To improve the likelihood of the paralell trends assumption, they run a logistic regression to predict being in the TVA based on their set of control variables $X_{c,1940}$ and keep only observations in the top 75\% of predicted probability.
+Their estimator does not differ much from the standard difference-in-differences results since the weights are not that different from uniform weights.} Pre-treatment control variables, $X_{c,1940}$, are interacted with $\text{Post}_t$ to allow for places to be on different long-term trends.\footnote{See footnote 8 in \citet{Kline_Moretti_2014} for a full listing of control variables.} To improve the likelihood of the parallel trends assumption, they run a logistic regression to predict being in the TVA based on their set of control variables $X_{c,1940}$ and keep only observations in the top 75\% of predicted probability.
 The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
@@
 
-By comparing counties inside the Authroity to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
-The authors do recognize the problem of these comparisons and remove counties that share borders with the authority's, but due to the scale of the program, the spillovers are likely to extend further than this.
+By comparing counties inside the Authority to counties on the other side of the border, the authors likely underestimate the negative effect on agricultural employment while the bias in the manufacturing effect is theoretically ambiguous.
+The authors do recognize the problem of these comparisons and remove counties that share borders with the authority, but due to the scale of the program, the spillovers are likely to extend further than this.
 Therefore, bias in their estimate will likely remain even after dropping contiguous counties.
@@
 
-The results of the long-run analysis from 1940 to 2000 are presented in Panel A of Table \ref{tab:tva}.
+The results of the long run analysis from 1940 to 2000 are presented in Panel A of Table \ref{tab:tva}.
 Each row contains the results for a different outcome variable (measured in logs).
 Columns (1)-(5) contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
-The point estimates can be interpreted as decadel growth rates in outcomes.
+The point estimates can be interpreted as decadal growth rates in outcomes.
 The column labeled difference-in-differences uses an ordinary least squares estimator for the specification without spillovers, equation (\ref{eq:tva}).
@@
 
-% Table: Effects of Tennessee Valley Authority on Decadel Growth
+% Table: Effects of Tennessee Valley Authority on Decadal Growth
 \begin{table}[!tb]
-    \caption{Effects of Tennessee Valley Authority on Decadel Growth}
+    \caption{Effects of Tennessee Valley Authority on Decadal Growth}
     \label{tab:tva}
@@
 
-Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and and columns (3)-(6) contain point estimates of the spillover effects $\delta_d$.
+Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and columns (3)-(6) contain point estimates of the spillover effects $\delta_d$.
 For agricultural employment, the point estimates show there was a decline in agriculture employment in control units near the Authority.
@@
 Between 50 and 100 miles the point estimate is $-1.6\%$ per decade, between 100 and 150 miles the point estimate is $-3\%$ per decade, and between 150 and 2000 miles the point estimate is $-1.6\%$ per decade.
-This is likely due to the fact that higher paying manufacturing jobs within the Authority drew farm-worker migrants from nearby counties.
-Because the spillovers onto the control counties is negative, the original difference-in-differences estimator was positively biased.
+This is likely because higher-paying manufacturing jobs within the Authority drew farm-worker migrants from nearby counties.
+Because the spillovers onto the control counties are negative, the original difference-in-differences estimator was positively biased.
 The new point estimate indicates a decline of agricultural employment of about $7.4\%$ per decade compared to $5.1\%$ in the standard difference-in-difference specification.
@@
 For manufacturing, our point estimates for spillovers are consistently negative, though imprecisely estimated in some columns.
-The spillover estimates suggest that neighboring counties experienced potentially negative spillover effects in the long-run.
+The spillover estimates suggest that neighboring counties experienced potentially negative spillover effects in the long run.
 Since there are negative spillover effects present, the new point estimate in column (2) of $3.5\%$ is significantly smaller than the original estimate of $5.6\%$.
-The spillover estimates are evidence that in the long-run, urban shadow forces dominate the benefits of urban access.
-As you move away from the Tennessee Valley, the point estimates become more negative which suggest that the benefits of urban access vanish over distance faster than the costs of urban shadow.
-
-To see how spillover effects from a large-scale place-based policy develop over time, Panel B in Table \ref{tab:tva} presents results for the effects of the Tennessee Valley in the short-run using outcome data in 1960.
-Unlike in the long-run, areas near the Tennessee Valley did not experience significant declines in agricultural employment in the short-run.
-Since our long-run analysis finds significant increases in high paying manufacturing employment in the Tennessee Valley, this result is consistent with long-run migration costs being lower than short-run costs.
-
-For manufacturing, there are potentially positive increases in manufacturing employment within 100 miles of the Tennessee Valley authority and near zero effects between 100 and 200 miles.
-In the short-run, it appears that the effects of urban access and the cheap wholesale electricity dominated the effects of urban shadow.
-The effect of urban shadows can potentially be smaller in the short-run if operating firms are unlikely to relocate.
-Long-run effects can be larger as entrant firms change their location decision and operating firms are slowly replaced which is what the long-run spillover effect estimates suggest.
+The spillover estimates are evidence that in the long run, urban shadow forces dominate the benefits of urban access.
+As you move away from the Tennessee Valley, the point estimates become more negative which suggests that the benefits of urban access vanish over distance faster than the costs of urban shadow.
+
+To see how spillover effects from a large-scale place-based policy develop over time, Panel B in Table \ref{tab:tva} presents results for the effects of the Tennessee Valley in the short run using outcome data in 1960.
+Unlike in the long run, areas near the Tennessee Valley did not experience significant declines in agricultural employment in the short run.
+Since our long run analysis finds significant increases in high-paying manufacturing employment in the Tennessee Valley, this result is consistent with long run migration costs being lower than short run costs.
+
+For manufacturing, there are potentially positive increases in manufacturing employment within 100 miles of the Tennessee Valley Authority and near-zero effects between 100 and 200 miles.
+In the short run, it appears that the effects of urban access and the cheap wholesale electricity dominated the effects of urban shadow.
+The effect of urban shadows can potentially be smaller in the short run if operating firms are unlikely to relocate.
+long run effects can be larger as entrant firms change their location decision and operating firms are slowly replaced which is what the long run spillover effect estimates suggest.
 
 These results show that including spillovers in the estimation of direct treatment effects is potentially important and can lead to \emph{significant} differences in treatment effect estimates.
-Analysis of place-based policies that do not account for the fact that treatment effects can spillover beyond the borders of treated areas can potentially be biased.
+Analysis of place-based policies that do not account for the fact that treatment effects can spill beyond the borders of treated areas can potentially be biased.
 More, the spillover effects caused by place-based policies change over time as frictions can create delays in reoptimizing behavior.
@@
 
-More generally, my framework provides important insights into identification strategies when analysizing the effects of place-based policies.
+More generally, my framework provides important insights into identification strategies when analyzing the effects of place-based policies.
 There are two ways I contribute.
-First, \citet{Baum-Snow_Ferreira_2015} recognize the problem of spatial spillovers causing problems in identification and point to aggregation of units as a way to alleviate to the problem (e.g.
+First, \citet{Baum-Snow_Ferreira_2015} recognize the problem of spatial spillovers causing problems in identification and point to aggregation of units as a way to alleviate the problem (e.g.
 aggregating census tracts to metropolitan areas).
@@
 
-Second, my framework provides insight for different identification strategies often used in the literature.
+Second, my framework provides insight into different identification strategies often used in the literature.
 Since place-based policies are targeted to specific distressed areas, comparison units are often hard to find.
-Researchers have developed many identification strategies to find comparison units that are facetimesimilar in terms of unobservables.
-First, researchers use border discontinuities to compare treated units to units just on the otehr side of the border.
+Researchers have developed many identification strategies to find comparison units that are similar in terms of unobservables.
+First, researchers use border discontinuities to compare treated units to units just on the other side of the border.
 Other times, researchers compare approved applicants to narrowly rejected applicants.
@@
 Identification strategies that rely on geographically close control units as having similar unobservables should be used cautiously.
-If treatment effects spillover treatment border, then estimated treatment effects can be biased.
+If treatment affects units on the other side of a border, then estimated treatment effects can be biased.
 
@@
 Now, I turn to the common setting where treatment turns on at different times for different units, often called staggered adoption.
-The intuition from how spillovers cause biases in estimates of the total/direct effect of treatment extend into the staggered adoption setting.
-In this setting, the literature has shown that two-way fixed effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
+The intuition from how spillovers cause biases in estimates of the total/direct effect of treatment extends into the staggered adoption setting.
+In this setting, the literature has shown that two-way fixed-effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
 I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias term(s) from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
-However, since weights on some of the $2 \times 2$ estimates can be negative, the sign of the spillover effects do not determine the sign of the weighted average of the spillover effects.
+However, since weights on some of the $2 \times 2$ estimates can be negative, the sign of the spillover effects does not determine the sign of the weighted average of the spillover effects.
 This makes the bias from spillovers much more difficult to sign.
 
-In order to estimate treatment and spillover effects in the presence of spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} by incorporating spillovers directly into estimation similar to equations (\ref{eq:id_total}) and (\ref{eq:id_direct}).
+To estimate treatment and spillover effects in the presence of spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} by incorporating spillovers directly into estimation similar to equations (\ref{eq:id_total}) and (\ref{eq:id_direct}).
 I assume I observe an independent and identically distributed panel for units $i$ and periods $t$.
@@
     \end{equation}
-    where $\expec{\varepsilon_{it}} = 0$, $\mu_i$ and $\lambda_t$ are non-stochastic unit and time fixed effects.
+    where $\expec{\varepsilon_{it}} = 0$, $\mu_i$ and $\lambda_t$ are non-stochastic unit and time fixed-effects.
 \end{assumption}
@@
 However, it is also common in event-study analyses to allow heterogeneity in effects by the number of years that a unit experiences treatment.
-Let $K_{it}$ denote the number of years since treatment turns on (-1 for year prior, 0 for intial year, and so on).
+Let $K_{it}$ denote the number of years since treatment turns on (-1 for the year prior, 0 for the initial year, and so on).
 Then we can define dummy variables $D_{it}^k \equiv D_it \one_{K_{it} = k}$ and estimate average total effects for each relative period:
@@
 \begin{enumerate}
-    \item Estimate $Y_{it} = \mu_i + \lambda_t + u_{it}$ for observations with $D_{it} = 0$ and $S_{it} = 0$ to estimate the common trend $\lambda_t$ and unit fixed effects $\mu_i$.
+    \item Estimate $Y_{it} = \mu_i + \lambda_t + u_{it}$ for observations with $D_{it} = 0$ and $S_{it} = 0$ to estimate the common trend $\lambda_t$ and unit fixed-effects $\mu_i$.
 For all observations, residualize $\tilde{Y}_{it} \equiv Y_{it} - \hat{\mu}_i - \hat{\lambda}_t$ which is our estimate for $\tau_{it}$.
@@
 Then, $\tilde{Y}_{it}$ will serve as an estimate for $\tau_{it}$.
-The second stage estimate averages of $\tau_{it}$ for different groups depending on the parameters of interest.
+The second stage estimates averages of $\tau_{it}$ for different groups depending on the parameters of interest.
 This is equivalent to regressing the residual $\tilde{Y}_{it}$ on dummy variable(s).
@@
 This procedure is implemented in the R/Stata package \texttt{did2s} \citep{did2s}.
-In appendiex section (\ref{sec:chc}), I use this two-stage estimator to revisit the analysis of \citet{Bailey_Goodman_Bacon_2015}.
+In appendix section (\ref{sec:chc}), I use this two-stage estimator to revisit the analysis of \citet{Bailey_Goodman_Bacon_2015}.
 
@@
 I then improve upon ad-hoc estimation strategies by proposing a new estimation strategy that is robust to more forms of spillovers.
-In particular, I find that specifications with an indicator for being ``close to'' treated units will remove all bias in the treatment effect estimate so long as all units affected by spillovers are contained in the indicator under a modified parallel trends assupmtion.
-More, I show that a set of concentric `rings' are able to remove all the bias and improve estimation of spillover effects.
+In particular, I find that specifications with an indicator for being ``close to'' treated units will remove all bias in the treatment effect estimate so long as all units affected by spillovers are contained in the indicator under a modified parallel trends assumption.
+More, I show that a set of concentric `rings' can remove all the bias and improve the estimation of spillover effects.
 A limitation of this research is in deciding how wide and how many rings to include in estimation.
@@
 In particular, place-based interventions change the nature of agglomeration in the local and surrounding area--that is cause spillovers--local effects of these policies can be misestimated without controlling for general equilibrium effects.
-I also show the importance of considering spillovers in weighing the pros and cons of various identificatin strategies.
-Identification strategies based on geographic continuity of unobservables can magnify the bias from spillovers as they restrict the compairson group to observations experiencing the largest spillover effects.
+I also show the importance of considering spillovers in weighing the pros and cons of various identification strategies.
+Identification strategies based on geographic continuity of unobservables can magnify the bias from spillovers as they restrict the comparison group to observations experiencing the largest spillover effects.
 
@@
 The authors study the creation of federal community health centers between 1965 and 1974 that provided \textit{primary} care to low-income communities.
-They test the hypothesis if access to low/no- cost health care services decreased mortality rates on the treated population.
+They test the hypothesis if access to low-/no-cost health care services decreased mortality rates on the treated population.
 To answer this question, the authors use a common event-study framework to compare outcomes in treated counties to all other US counties by estimating the following specification
@@
 \end{equation}
-where $D_i^k$ is the typical `event study' indicator for being treated for $k$ years, $\theta_i$ is county fixed effects, and $X_{it}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed effects, and urban-group fixed effects.
+where $D_i^k$ is the typical `event study' indicator for being treated for $k$ years, $\theta_i$ is county fixed-effects, and $X_{it}$ contains a set of controls.\footnote{Controls include 1960 county characteristic trends, state-year fixed-effects, and urban-group fixed-effects.
 A full list can be found on page 1080 of \citet{Bailey_Goodman_Bacon_2015}.} The coefficents $\pi_y$ can be interpreted as tests of parallel pre-trends and $\tau_y$ can be interepreted as the treatment effect of a community health center $y$ years after establishment.
@@
 This would create a negative spillover effect on mortality rates in nearby counties which would bias their estimates towards zero.
-On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergency but rather primary care services.
-In this case, it is less likely low-income individuals would travel very far to receive primary care and hence the spillover effects is potentially near zero.
-My methodology can provide an answer to the question of how far do individuals travel for low/no -cost primary care.
-
-As in the method detailed above, I use the subsample of counties that do not receive a community health center and use an indicator for being within 25 miles of a treated county as the treatment variable.
-Then, I follow \citet{Callaway_SantAnna_2020} in estimating event-study coefficients.
+On the other hand, \citet{Bailey_Goodman_Bacon_2015} document evidence that their estimated effects are not due to emergencies but rather primary care services.
+In this case, it is less likely low-income individuals would travel very far to receive primary care, and hence the spillover effects are potentially near zero.
+My methodology can provide an answer to the question of how far do individuals travel for low-/no-cost primary care.
+
+As in the method detailed above, I use an indicator for being within 25 miles of a treated county as the spillover variable.
 The results are presented in Figure \ref{fig:chc_es_spill}.
@@
 The first exercise is to consider a set of different data generating processes and see how well estimates of the total effect perform when controlling for spillovers using potentially misspecified exposure mappings.
-In the general form, I generate data with unit and time fixed effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h_i(\vec{D})$.
+In the general form, I generate data with unit and time fixed-effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h_i(\vec{D})$.
 I generate data for unit $i$ is a US county at time $t \in \{1, \dots, 20\}$ using the following data-generating process:
@@
 For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are the same.
-In order to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
-
-The set of spillover specifications included in the data-generating process are `Within $40/80$mi.' which equals 1 if the counties' center of population is within $40/80$ miles to a treated county's center of population.
+to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
+
+The set of spillover specifications included in the data-generating process are `Within $40/80$mi.' which equals 1 if the counties' center of population is within $40/80$ miles to a treated counties center of population.
 This corresponds to different choices of $\bar{D}$ and hence $S_i$ in the text.
@@
 
-The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed effect estimate and lower the mean-squared error.
+The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed-effect estimates and lower the mean-squared error.
 In particular, correctly specifying the data-generating process removes almost all the bias in the direct effect estimate and greatly lowers the mean-squared error.
@@
 
-Now, I turn to analyzing how the specifications perform at estimating the spillover effects themselves.
+Now, I turn to analyze how the specifications perform at estimating the spillover effects themselves.
 For the next table, I predict the spillover effect for each control unit from the point estimates on $\tilde{h}(\vec{D}, i)$.
@@
 \end{equation} 
-This will produce a percentage of spillovers that are explained by the specification, so numbers closer to $100\%$ represent better modelling of the spillovers.
+This will produce a percentage of spillovers that are explained by the specification, so numbers closer to $100\%$ represent better modeling of the spillovers.
 
@@
 For each specification, correctly specifying the spillovers produces the best estimates for spillovers as expected.
-Among misspecified exposure mapping, `Rings' that are large enough to caputre all the spillovers perform better than all other specifications in all non-additive data-generating processes.
-On the other hand, when the spillovers are additive, the predicted spillovers from the non-additive ring specifications do not as accurately measure these spillovers as they did before.\footnote{Although the non-additive Rings do estimate between 70\% and 80\% of the spillover effects while maintaining complete removal of bias.} Non-additvie specifciations perform somewhat poorly at estimating spillovers in the additive data-generating processes, `Within (Additive)' and `Decay (Additive)'.
-The `Rings (Additive)' specification sucessfully predicts spillovers in both additive data-generating processes.
+Among misspecified exposure mapping, a `Rings' specification that is large enough to capture all the spillovers perform better than all other specifications in all non-additive data-generating processes.
+On the other hand, when the spillovers are additive, the predicted spillovers from the non-additive ring specifications do not as accurately measure these spillovers as they did before.\footnote{Although the non-additive Rings do estimate between 70\% and 80\% of the spillover effects while maintaining complete removal of bias.} Non-additive specifcations perform somewhat poorly at estimating spillovers in the additive data-generating processes, `Within (Additive)' and `Decay (Additive)'.
+The `Rings (Additive)' specification successfully predicts spillovers in both additive data-generating processes.
 

### 2021-11-04 latex/paper/Spillover.tex
Add Alex's feedback

@@
 
-Empirical work often considers settings where a policy is targeted to groups of units by geographic boundaries, but the effect of treatment spillovers onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+Empirical work in economics often considers settings where a policy is targeted to groups of units by geographic boundaries, but the effect of treatment spillovers onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
 geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, individuals in control areas can travel to the treated areas and receive treatment (e.g.
-a hospital opening serves nearby residents), or shocks to a labor market can have feedback loops that affect nearby areas (e.g.
+a hospital opening serves nearby residents), or shocks to a labor market can affect nearby areas (e.g.
 a new factory opening increases service sector spending in the commuting zone).
@@
 bidding up of wages causes the employment effects of factory openings to be mitigated).
+
 In this paper, I introduce a potential outcomes framework that directly models spillover effects.
-
-Using this potential outcome framework, I define the different possible treatment/spillover effects of interest and the relative advantage and interpretation of each.
+While other papers have derived identification results using specific parameterizations, my paper is the first to model spillovers in a general form.
+Using this potential outcome framework, I define different possible treatment/spillover effects of interest and the relative advantage and interpretation of each.
 First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
@@
 The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors.
-For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities versus the case where a close neighbor already has constructed one.
-Switching effects therefore are defined separately for each level of exposure, and estimation of a switching effect requires knowledge of which units experience the same level of exposure.
+For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities.
+Switching effects therefore are defined separately for each level of exposure.
+Estimation of a switching effect requires knowledge of which units experience the same level of exposure.
 While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions.
@@
 Second, there is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
-This treatment effect summarizes what were the effects of going from the world with no treatment to the entire vector of treatment status.
+This treatment effect summarizes the effects of going from the world with no treatment to the entire treatment regime.
 This effect comes from two sources: the direct effect and the average spillover effect from other treated units.
-Unlike the switching effect, the total effect is nonparametrically identified under a mild assumption that spillovers are `local' in that spillovers are only experienced within a certain distance from treatment.
-
-This paper shows that the difference-in-differences estimator is a biased estimate for the total effect because of spillover effects on control units.
-The intuition is that untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
-When estimating by difference-in-differences, the spillover onto the `close' control units is averaged into the untreated units' change in outcomes.
+Unlike the switching effect, the total effect is nonparametrically identified under a mild assumption that spillovers are `local'.
+The `local' assumption requires that spillovers are only experienced within a certain distance from treatment.
+
+This paper then defines conditions under which each treatment effect is nonparametrically identified.
+I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences which requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
+The direct and total effects considered can be identified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature.
+The local assumption holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
+This would hold in the case where individuals can travel to access treatment.
+However, this would fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g.
+San Francisco being affected by shocks to the New York economy).
+
+Next, I assess the commonly used difference-in-differences estimate.
+This paper shows that the difference-in-differences estimator is a biased estimate for the total effect and direct effect.
+Both the total effect and the direct effect are biased from spillovers on control units.
+This bias arises because untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
+Difference-in-differences estimates average the spillover onto the `close' control units into the untreated units' change in outcomes.
 Hence, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
-For example, if nearby control units also benefit from treatment, then researchers would underestimate the effects on the treated.
-If a researcher is interested in the direct effect, there is an additional source of bias since changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units.
-The spillover onto other treated units is averaged into the treated units' change in outcomes.
+For example, if nearby control units also benefit from treatment, then researchers would underestimate the treatment effect of the treated.
+The direct effect is also biased because changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units.
+In difference-in-differences, the spillover onto other treated units is averaged into the treated units' change in outcomes.
 Therefore the bias on the direct effect estimate is the same sign as the sign of the spillover.
 
-This paper then defines conditions under which each treatment effect is nonparametrically identified.
-I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences of treatment which requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
-The other two treatment effects considered can be identified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature which holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
-This would hold in the case where individuals can travel to access treatment.
-This could fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g.
-San Francisco being affected by shocks to the New York economy).
-
-Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
-In my decomposition of the difference-in-differences estimate, the bias term for the total effect is the \textit{average} spillover effects onto control units.
-An indicator variable for control units affected by spillover can remove this bias.
-When estimating the direct effect, a second indicator variable for treated units affected by spillovers is included to remove the second source of bias.
+Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers in the two-way fixed-effects model will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
+The bias term in the difference-in-differences estimate for the total effect is the \textit{average} spillover effects onto control units.
+An indicator variable that contains \emph{all} control units affected by spillover can therefore remove this bias.
+When estimating the direct effect, a second indicator variable containing \emph{all} treated units affected by spillovers can remove the second source of bias.
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
-The only assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, even if the maximum distance is not large enough, most of the bias will still be removed.
+The only assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, this is not a strong assumption.
+Even if the maximum distance is not large enough, most of the bias will still be removed.
 On the other hand, making the maximum distance too large will increase the variance in the estimates as there are fewer remaining control units to identify the parallel counterfactual unit.}
 
-The modified difference-in-differences framework with an added spillover indicator provides a theoretically poor estimate of average spillover effects as it averages over all units with the indicator equal to 1 which can include units that are unaffected by spillovers.
+The modified difference-in-differences framework with an added spillover indicator provides a poor estimate of spillover effects.
+The estimate averages spillover effects over all units with the indicator equal to 1 which can include units that are unaffected by spillovers.
+Therefore the estimate will be attenuated to zero.
 The above method can be improved by creating a set of distance bins from the treated units (e.g.
 being 0-20 miles, 20-40 miles, 40-60 miles from the treated units) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
-In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single large indicator, this estimator still consistently estimates the treatment effect of interest.
+In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single indicator covering the bins, this estimator consistently estimates the treatment effect of interest.
 This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.
 
-To show the importance of considering spillover effects, I revisit analyses of place-based policies in urban economics in Section \ref{sec:tva}.
+To show the importance of considering spillover effects and the utility of my estimators, I revisit analyses of place-based policies in urban economics in Section \ref{sec:tva}.
 I revisit the analysis of the Tennessee Valley Authority by \citet{Kline_Moretti_2014}.
@@
 The scale of federal investment in the region was large and the pro-manufacturing benefits likely spread further than the Authority's boundary due to the electrification infrastructure and agglomeration economies \citep{Severnini_2014}.
-I show that estimation by difference-in-differences fails to account for these spillovers and therefore forms biased estimates of the local effect of the Tennessee Valley Authority.
+I show that estimation by difference-in-differences fails to account for these spillovers and therefore the authors obtain biased estimates of the total effect of the Tennessee Valley Authority.
 
@@
 I revisit conflicting results about United States' federal Empowerment Zones, a program that creates incentives for businesses to locate in high-poverty neighborhoods.
+States apply for Empowerment Zone status for ares that meet a list of requirements but due to limited funding, not all proposed areas were accepted.
 \citet{Busso_Gregory_Kline_2013} use Census Tracts from qualified but ultimately rejected applications that are typically far away from accepted Zones as a comparison group and find significant reductions in poverty.
@@
 \citet{Neumark_Kolko_2010}, on the other hand, use census tracts within 1,000 feet of the Zone and find no statistically significant effects.
-This empirical strategy assumes that the borders are drawn somewhat randomly and therefore being just outside is as good as random.
+This empirical strategy assumes that the borders are drawn somewhat randomly and therefore units being just outside will have parallel counterfactual trends.
 Although, using close units is potentially problematic as they can experience spillover effects from the Zones.
@@
 This paper relates to a broad literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work.
-See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.}
-
-There are two main strands of this literature.
+See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.} There are two main strands of this literature.
 First, there is a large literature on the estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
@@
 
-There is a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}, \citet{Vazquez-Bare_2019}, and \citet{Hu_Li_Wager_2021}).
+There is also a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}, \citet{Vazquez-Bare_2019}, and \citet{Hu_Li_Wager_2021}).
 Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
-I also contribute to this literature by thinking about different definitions of treatment effects and their identification in non-experimental settings.
+I contribute to this literature by thinking about identification of different treatment effects in non-experimental settings.
 
 The rest of the paper is structured as follows.
-Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, and shows the resulting bias from estimating a classical difference-in-differences model.
-Section \ref{sec:estimation} focuses on the estimation of the direct and spillover effects of treatment.
-I evaluate currently used solutions in the literature and present a set of recommendations to more robust estimation strategies.
+Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, discusses identification of effects, and shows the resulting bias from estimating a classical difference-in-differences model.
+Section \ref{sec:estimation} focuses on the estimation of the direct effect, the total effect, and spillover effects.
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
-Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021}.
-I apply these methods in evaluating spillover effects of U.S.
-Community Health Centers in Subsection \ref{sec:chc}.
+Last, Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021}.
 
@@
 
-to estimate the direct effect and the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
+% ------------------------------------------------------------------------------
+\section{Estimation of Effects}\label{sec:estimation}
+% ------------------------------------------------------------------------------
+
+% ------------------------------------------------------------------------------
+\subsection{Estimation of Direct and Total Effects}
+% ------------------------------------------------------------------------------
+
+To estimate the direct effect and the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
 However, it will prove advantageous to modify the two-way fixed-effects model to estimate the direct or the total effect because it will allow the estimation of spillover effects as well.
@@
 % ------------------------------------------------------------------------------
-\section{Estimation of Spillover Effects}\label{sec:spill}
+\subsection{Estimation of Spillover Effects}\label{sec:spill}
 % ------------------------------------------------------------------------------

### 2022-01-18 latex/paper/Spillover.tex
Add Opportunity Zone

@@
 a hospital opening serves nearby residents), or shocks to a labor market can affect nearby areas (e.g.
-a new factory opening increases service sector spending in the commuting zone).
+a new factory opening increases service sector spending in the entire commuting zone).
 For other treated units, forces of agglomeration can increase effect size as treatment concentration increases (e.g.
@@
 
-In this paper, I introduce a potential outcomes framework that directly models spillover effects.
-While other papers have derived identification results using specific parameterizations, my paper is the first to model spillovers in a general form.
-Using this potential outcome framework, I define different possible treatment/spillover effects of interest and the relative advantage and interpretation of each.
+In this paper, I introduce a potential outcomes framework that directly models spillover effects and use this model to derive identification results in difference-in-differences settings.
+Using this potential outcome framework, I define different possible treatment effects of interest and the relative advantage and interpretation of each.
 First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
@@
 For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities.
-Switching effects therefore are defined separately for each level of exposure.
-Estimation of a switching effect requires knowledge of which units experience the same level of exposure.
+Switching effects therefore are defined separately for each level of exposure and estimation of the effect at a particular level requires knowledge of which units experience the same level of exposure.
+I show that identification therefore requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
+
 While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions.
-This effect is the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatments.
+I call this effect the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatments.
 That is, what are the effects of turning on a unit's treatment if this were the \emph{only} unit to be treated in their area.
-
-Second, there is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
+The second effect of interest is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
 This treatment effect summarizes the effects of going from the world with no treatment to the entire treatment regime.
-This effect comes from two sources: the direct effect and the average spillover effect from other treated units.
-Unlike the switching effect, the total effect is nonparametrically identified under a mild assumption that spillovers are `local'.
-The `local' assumption requires that spillovers are only experienced within a certain distance from treatment.
-
-This paper then defines conditions under which each treatment effect is nonparametrically identified.
-I find that the switching effect is identified only with knowledge of the amount of `exposure' that a unit experiences which requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
-The direct and total effects considered can be identified nonparametrically under mild assumptions about spillovers, namely that they are ``local'' in nature.
-The local assumption holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
-This would hold in the case where individuals can travel to access treatment.
+This effect comes from two sources: the direct effect and the average spillover effect from other units' treatment.
+
+This paper then defines conditions under which the direct and total effects is nonparametrically identified by a modified difference-in-differences type estimand under a mild assumption that spillovers are `local' in nature.
+The local spillovers assumption holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
+This would hold in the case where individuals can travel to access treatment and therefore spillovers are limited by travel costs.
 However, this would fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g.
@@
 Next, I assess the commonly used difference-in-differences estimate.
-This paper shows that the difference-in-differences estimator is a biased estimate for the total effect and direct effect.
-Both the total effect and the direct effect are biased from spillovers on control units.
+This paper shows that the difference-in-differences estimator is a biased estimate for the direct and the total effect.
 This bias arises because untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
@@
 For example, if nearby control units also benefit from treatment, then researchers would underestimate the treatment effect of the treated.
-The direct effect is also biased because changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units.
+The direct effect also has a second source of bias because changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units.
 In difference-in-differences, the spillover onto other treated units is averaged into the treated units' change in outcomes.
@@
 An indicator variable that contains \emph{all} control units affected by spillover can therefore remove this bias.
+However, adding this indicator changes the underlying control group to the control units not included in the indicator variable and hence a researcher must justify why this subsample will form a valid control group for the parallel trends assumption.
 When estimating the direct effect, a second indicator variable containing \emph{all} treated units affected by spillovers can remove the second source of bias.
@@
 My framework can explain the differences in findings if there are positive spillover effects onto census tracts just outside Empowerment Zones.
+In an appendix section, I show an example of the importance in considering spillovers when chosing identification strategy by analyzing the effects of the 2017 Opportunity Zone place-based policy.
 
@@
 % ------------------------------------------------------------------------------
-\subsection{Identification Strategies in Place-Based Policy Analysis}
+\subsection{Identification Strategies in Place-Based Policy Analysis}\label{sec:pbp}
 % ------------------------------------------------------------------------------
@@
 If treatment affects units on the other side of a border, then estimated treatment effects can be biased.
+In Appendix \ref{sec:oz}, I revisit analysis by \citet{Chen_Glaeser_Wessel_2021} on the 2017 Opportunity Zone program who find differing results between the `nearby' and `eligibe, but not selected' methodologies and show that my framework is able to reconcile their differences in estimates.
 
@@
 Let $K_{it}$ denote the number of years since treatment turns on (-1 for the year prior, 0 for the initial year, and so on).
-Then we can define dummy variables $D_{it}^k \equiv D_it \one_{K_{it} = k}$ and estimate average total effects for each relative period:
+Then we can define dummy variables $D_{it}^k \equiv D_{it} \one_{K_{it} = k}$ and estimate average total effects for each relative period:
 \[
@@
 This procedure is implemented in the R/Stata package \texttt{did2s} \citep{did2s}.
+
 In appendix section (\ref{sec:chc}), I use this two-stage estimator to revisit the analysis of \citet{Bailey_Goodman_Bacon_2015}.
+In particular, I find that the effects of community health centers stay within the county and therefore the originally estimated effects are robust.
 
@@
 For part (i):
-
 \begin{align*}
@@
 Similarly, for part (ii):
-
 \begin{align*}
@@
 % ------------------------------------------------------------------------------
+\section{Application on Opportunity Zones}\label{sec:oz}
+% ------------------------------------------------------------------------------
+
+In this section, I revist the analysis of \citet{Chen_Glaeser_Wessel_2021} on the 2017 Opportunity Zone program which created tax incentives for captial investment in targeted Census Tracts.
+To measure the affects of the opportunity zone program on housing prices, the authors collect a panel of census tracts with a measure of housing prices from the Federal Housing Finance Agency (FHFA) from 2014-2019.\footnote{The index tries to create a consistent price index that captures for changes in the composition of homes that are sold over time.} They produce estimates using two different identification strategies.
+
+First, they compare census tracts that were selected as Opportunity Zones to eligible, but ultimately not selected, census tracts.
+As discussed in Section \ref{sec:pbp}, this estimation strategy relies on the assumption that since these census tracts are similar in nature to the treated census tracts (both meeting the program's criteria), it is likely that home prices would continue on similar trajectories in the absence of the program.
+The authors run a standard two-way fixed effect specification on the subsample of eligible census tracts:
+\begin{equation}\label{eq:oz-eligible}
+    Y_{it} = \mu_i + \mu_t + \tau D_{it} + \varepsilon_{it},
+\end{equation}
+where $Y_{it}$ is the annual change in the home price index, $\mu_i$ are tract fixed-effects, $\mu_t$ are time fixed effects, and $D_{it}$ is an indicator for treatment.
+
+The second identification strategy relies on comparing selected census tracts to geographically neighboring census tracts.
+As discussed in Section \ref{sec:pbp}, this estimation strategy relies on the assumption that proximity of census tracts would face similar economic shocks and hence home prices would likely evolve in parallel.
+For each treated census tract, they find the nearest non-treated census tract to form a pair, $(i, \tilde{i}) \equiv \nu$.
+They then estimate the following equation:
+\begin{equation}\label{eq:oz-neighbor}
+    Y_{it} - Y_{\tilde{i}t}  = \mu_\nu + \tau D_{it} + u_{it},
+\end{equation}
+where $Y_{it}$ is the annual change in the home price index, $\mu_\nu$ are pair fixed-effects and $D_{it}$ is an indicator for treatment.
+
+In both cases, the authors provide evidence of parallel `pre-trends' as evidence supporting the respective underlying assumptions.
+The results of both estimation strategies are shown in Table \ref{tab:oz}.
+Column (1) and (2) show the results of estimating Equation (\ref{eq:oz-eligible}) and (\ref{eq:oz-neighbor}) respectively.
+The `not-selected' estimate finds a marginally significant effect of an increase in home prices of about 0.3\% annually while the `neighboring' estimate finds a strongly significant effect twice as large of about 0.65\%.\footnote{The authors use this estimate to rule out effects larger than $\approx 0.65 + 2 * 0.25 = 1.15\%$.
+As shown before, these estimates are biased upwards and hence the upper bound of effect size can be lowered to about $\approx 0.65\%$.}
+
+% Table: Effects of Opportunity Zones on Annual Home Price Growth
+\begin{table}[!tb]
+    \caption{Effects of Opportunity Zones on Annual Home Price Growth}
+    \label{tab:oz}
+    \renewcommand{\arraystretch}{1.1}
+
+    \begin{adjustbox}{width = 0.8\textwidth, center}
+        \begin{threeparttable}
+            \begin{tabular}{@{} l ccc @{}}
+                % Head
+                \toprule
+
+                & \multicolumn{1}{c}{\textbf{Not-Selected}} & \multicolumn{1}{c}{\textbf{Neighboring}} & \multicolumn{1}{c}{\textbf{Not-Selected and Neighboring}} \\ 
+                \textit{Dependent Var.} & (1) & (2) & (3) \\
+
+                % Body
+                \midrule
+
+                \input{../../tables/OZ_replication.tex}
+
+                \bottomrule
+            \end{tabular}
+
+            % Notes 
+            \begin{tablenotes}\footnotesize
+                \item \textit{Notes.} This table contains estimation 
+                \item $^{*} p< 0.1$; $^{**} p < 0.05$; $^{***} p < 0.01$.
+            \end{tablenotes}
+        \end{threeparttable}
+    \end{adjustbox}
+\end{table}
+
+What is driving the differences in these estimates?
+As I proposed in section \ref{sec:pbp}, the differences could be due to the fact that neighboring units could be experiencing effects from the Opportunity Zones.
+To test this, I use the estimation strategy proposed in section \ref{sec:estimation} to modify equation \ref{eq:oz-eligible}.
+For the subsample of eligible census tracts, I run the following specification:
+\begin{equation}\label{eq:oz-spill}
+    Y_{it} = \mu_i + \mu_t + \tau D_{it} + \gamma_{1} \text{Within 1/2mi.} +  \gamma_{2} \text{Within 1mi.} + \varepsilon_{it},
+\end{equation}
+where $\text{Within}$ are indicators for being within 1/2mi.
+and being between 1/2 and 1mi.
+from an Opportunity Zone.
+This estimation strategy uses non-neighboring census tracts as the effective control group and estimates effects for census tracts within or close to Opportunity Zones.
+The results are estimated in Table \ref{tab:oz} in Column (3).
+These estimated treatment effect decreased in this specification to 0.17\% and reveals that census tracts just outside of the Opportunity Zone experience negative and significant declines in home prices of about 1\%.
+This result explains why the estimated effect using the `neighbor' speficiation is twice as large as the `eligible' specification.
+
+The results of this section highlight the importance of considering spillovers when using "neighbor" style identification strategies, especially in settings where the unit of observation is small and spillover effects are quite likely.
+
+% ------------------------------------------------------------------------------
 \section{Application on Community Health Centers}\label{sec:chc}

### 2022-01-18 OZ-analaysis-replicate.R

@@ -1,0 +1,134 @@
+library(tidyverse)
+library(arrow)
+library(here)
+library(fixest)
+library(broom)
+
+# ---- Load Data ---------------------------------------------------------------
+
+zillow_data <- read_feather(here("data/tracts_data.feather"))
+zillow_data <- zillow_data |> filter(year != 2020)
+zillow_data$tract <- factor(zillow_data$tract)
+zillow_data$treat_x_post <- zillow_data$treatment * zillow_data$post
+
+# ------------------------------------------------------------------------------
+# Difference-in-Differences
+# ------------------------------------------------------------------------------
+
+# ---- Helper Function ---------------------------------------------------------
+
+fit_did_fixest <- function(data, fmla, pretest_fmla, pretest_cols) {
+  model_pretest <- fixest::feols(
+    fml = pretest_fmla,
+    data = data, cluster = ~state_abbr
+  )
+
+  pretest <- wald(model_pretest, keep = pretest_cols)
+
+  model <- fixest::feols(
+    fml = fmla, 
+    data = data, cluster = ~state_abbr
+  )
+
+	return(list(
+    model_pretest = model_pretest,
+    lh_pretest = pretest,
+    model = model
+  ))
+}
+
+# ---- No Covariates -----------------------------------------------------------
+
+zillow_model <- fit_did_fixest(
+  data = zillow_data, 
+  fmla = annual_change ~ treatment_and_post | year + tract,
+  pretest_fmla = annual_change ~  i(treatment, i.year, ref = F, ref2 = 2017) | year + tract,
+  pretest_cols = c("treatmentTRUE:year2014", "treatmentTRUE:year2015", "treatmentTRUE:year2016")
+)
+zillow_model
+
+
+model_results <- tidy(zillow_model$model)
+tau <- zillow_model$model$estimate 
+se <- zillow_model$model$std.error
+tstat <- zillow_model$model$statistics
+pval <- zillow_model$model$p.value
+
+
+# ---- Sparse Covariates -------------------------------------------------------
+
+zillow_model_cov_sp <- fit_did_fixest(
+  data = zillow_data,
+  fmla = annual_change ~ 1 + treatment * post + i(year, log_median_household_income, ref = 2017) + i(year, pct_white, ref = 2017) | year + tract, 
[…]

### 2022-01-18 OZ-analysis-spillovers.R

@@ -1,0 +1,108 @@
+## analysis_spillovers.R -------------------------------------------------------
+## Kyle Butts, CU Boulder Economics 
+## 
+## Opportunity Zone analysis where I run Selected vs. Eligible but Not Selected and have spillovers on adjacent census tracts. See if differences in effect is due to identification strategy.
+
+
+# Tidyverse
+library(tidyverse)
+# Spatial
+library(sf)
+library(units)
+# read_feather
+library(arrow)
+# here() for relative file
+library(here)
+# Estimation
+library(fixest)
+library(broom)
+
+# ---- Find distance to nearest treated ----------------------------------------
+
+geos <- read_sf(here("data/OZ/tracts/all_tracts_with_status.shp"))
+
+geos <- geos |>
+    st_point_on_surface() |>
+    mutate(
+        status = ifelse(is.na(status), "Ineligible", status),
+        intptlat = as.numeric(intptlat),
+        intptlon = as.numeric(intptlon),
+    )
+
+# # Code is inefficient because of memory concerns
+selected <- geos[geos$status == "Selected", ]
+geos$distance_to_nearest <- kfbmisc::st_nearest_distance_rcpp(geos, selected)[,2]
+
+geos <- geos |> 
+    st_as_sf() |> 
+    st_drop_geometry() |>
+    mutate(tract = as.character(geoid)) |> 
+    select(tract, status, distance_to_nearest)
+
+# ---- Combine geos with tract data --------------------------------------------
+
+tracts <- read_feather(here("data/OZ/tracts_data.feather")) 
+
+tracts <- filter(tracts, year != 2020)
+
+tracts <- left_join(tracts, geos, by = "tract")
+
+
+# ------------------------------------------------------------------------------
+# Regression Analysis
+# ------------------------------------------------------------------------------
+
+
+# ---- Selected vs. Eligible ---------------------------------------------------
+
+(eligible <- feols(
[…]

### 2023-02-26 latex/paper/Spillover.tex
Previous draft

@@
 
-\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, and the WEAI Conference}}
- %, and the University of Rochester HEEL Lab for helpful comments.}}
+\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Brantly Callaway, Pedro Sant'Anna, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, the Urban Economics Association Conference, the WEAI Conference, and the University of Rochester HEEL Lab for helpful comments.}}
 \author{\href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado Boulder, Economics Department (\href{mailto:kyle.butts@colorado.edu}{kyle.butts@colorado.edu})}}
@@
         \par~\par\noindent
-        \noindent{\color{asher} JEL Classification Number:} C01, R15, R58
+        \noindent{\color{asher} JEL Classification Number:} C01, C21, C23, R15, R58
         \par
@@
 
-Empirical work in economics often considers settings where a policy is targeted to groups of units by geographic boundaries, but the effect of treatment spillovers onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
+Empirical work in economics often considers settings where a policy is targeted to groups of units defined by geographic boundaries, but the effect of treatment spills over onto `nearby' units.\footnote{The framework of this paper applies to any setting with a well-defined measures of distance, e.g.
 geographic distance, economic distance such as supply chains, node distance in a graph, or social relationships in schools or cities.} For example, individuals in control areas can travel to the treated areas and receive treatment (e.g.
@@
 a new factory opening increases service sector spending in the entire commuting zone).
-For other treated units, forces of agglomeration can increase effect size as treatment concentration increases (e.g.
+For other treated units, the treatment effect can depend on other units' treatment status.
+Forces of agglomeration can increase effect size as treatment concentration increases (e.g.
 knowledge-sharing between firms) or forces of congestion/competition can decrease the effects of treatment (e.g.
@@
 In this paper, I introduce a potential outcomes framework that directly models spillover effects and use this model to derive identification results in difference-in-differences settings.
-Using this potential outcome framework, I define different possible treatment effects of interest and the relative advantage and interpretation of each.
+Using this potential outcome framework, I define different possible treatment effects of interest, discuss their interpretation, and show which effects are non-parametrically identified.
+
 First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
-It is difficult to estimate the switching effect without parametric assumptions.
+It is difficult to estimate the switching effect without parametric assumptions on spillovers.
 The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors.
 For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities.
-Switching effects therefore are defined separately for each level of exposure and estimation of the effect at a particular level requires knowledge of which units experience the same level of exposure.
-I show that identification therefore requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the spillover effects.
-
-While the switching effect is not identified nonparametrically in general, there is one effect that is identified under mild assumptions.
-I call this effect the `direct effect' of treatment which represents the switching effect for units with zero exposure to other treatments.
-That is, what are the effects of turning on a unit's treatment if this were the \emph{only} unit to be treated in their area.
+Switching effects therefore are defined separately for each level of exposure and estimation of the effect at a particular level requires knowledge of which control units experience the same level of exposure.
+I show that identification therefore requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the homogeneity of spillover effects.
+While the switching effect is not identified nonparametrically in general, the switching effect for units with zero exposure is identified under mild assumptions.
+I call this effect the `direct effect' which measures the effects of turning on a unit's treatment if they were the \emph{only} unit to be treated in their general area.
+
 The second effect of interest is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
-This treatment effect summarizes the effects of going from the world with no treatment to the entire treatment regime.
-This effect comes from two sources: the direct effect and the average spillover effect from other units' treatment.
-
-This paper then defines conditions under which the direct and total effects is nonparametrically identified by a modified difference-in-differences type estimand under a mild assumption that spillovers are `local' in nature.
+This treatment effect summarizes the post-hoc effects of going from the world with no treatment to the observed treatment vector.
+This effect comes from two sources: the direct effect on each treated unit and the average spillover effect on to treated units from other treated units.
+
+This paper then defines conditions under which the direct and total effects are nonparametrically identified by a modified difference-in-differences type estimand under a mild assumption that spillovers are `local' in nature.
 The local spillovers assumption holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
@@
 
-Under the assumption that spillovers are local, I show a common adjustment of including an indicator for being affected by spillovers in the two-way fixed-effects model will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
+Under the assumption that spillovers are local, I formalize the identification argument used in a common adjustment of including an indicator for being affected by spillovers (or removing them from the sample) in the two-way fixed-effects model.
+I show, under mild assumptions, that this method will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
 The bias term in the difference-in-differences estimate for the total effect is the \textit{average} spillover effects onto control units.
@@
 When estimating the direct effect, a second indicator variable containing \emph{all} treated units affected by spillovers can remove the second source of bias.
+Similar to the control group indicator, this modifies the treatment group over which the average treatment group is taken (those with indicator equal to zero).
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
-The only assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, this is not a strong assumption.
+The primary assumption required is selecting the maximum distance from treated units that spillovers can occur.\footnote{Since treatment effects typically decay over distance, this is not a strong assumption.
 Even if the maximum distance is not large enough, most of the bias will still be removed.
@@
 I show that estimation by difference-in-differences fails to account for these spillovers and therefore the authors obtain biased estimates of the total effect of the Tennessee Valley Authority.
+For agriculture employment, I find that the long-run spillovers cause the original estimates to be about 40 percent too small for agriculture employment and 40 percent too large for manufacturing employment.
+% (-0.0739 - -0.0514) / (-0.0514) = 43.7\% increase
+% (0.0350 - 0.0560) / (0.0560) = 37.5\% decrease
 
@@
 I revisit conflicting results about United States' federal Empowerment Zones, a program that creates incentives for businesses to locate in high-poverty neighborhoods.
-States apply for Empowerment Zone status for ares that meet a list of requirements but due to limited funding, not all proposed areas were accepted.
+States apply for Empowerment Zone status for areas that meet a list of requirements but due to limited funding, not all proposed areas were accepted.
 \citet{Busso_Gregory_Kline_2013} use Census Tracts from qualified but ultimately rejected applications that are typically far away from accepted Zones as a comparison group and find significant reductions in poverty.
@@
 This empirical strategy assumes that the borders are drawn somewhat randomly and therefore units being just outside will have parallel counterfactual trends.
-Although, using close units is potentially problematic as they can experience spillover effects from the Zones.
+Although, the trade-off is that using close units is potentially problematic as they can experience spillover effects from the Zones.
 My framework can explain the differences in findings if there are positive spillover effects onto census tracts just outside Empowerment Zones.
-In an appendix section, I show an example of the importance in considering spillovers when chosing identification strategy by analyzing the effects of the 2017 Opportunity Zone place-based policy.
+In appendix \ref{sec:oz}, I show an example of the importance in considering spillovers when chosing identification strategy by analyzing the effects of the 2017 Opportunity Zone place-based policy.
 
@@
 
-I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in two ways.
-\citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
+I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in three ways \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
 My paper is the first to consider identification in terms of general potential outcomes.
-Other papers derive results for specific spillover mappings and if I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs.
-The literature has focused on estimating the total effect, so I contribute by discussing alternative treatment effect estimates and identification results.
-Second, my paper also advances the literature by considering estimation of direct effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.
+Other papers derive results for specific spillover mappings.
+If I assume the particular functional forms for potential outcomes, I arrive at the same bias equation as theirs.
+The literature has focused on estimating the total effect, so I further contribute by discussing alternative treatment effect estimates and identification results.
+Last, my paper also advances the literature by considering estimation of direct effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.
 
@@
 Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
-I contribute to this literature by thinking about identification of different treatment effects in non-experimental settings.
+I contribute to this literature by formalizing identification results of different treatment effects in non-experimental settings.
 
@@
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
-Last, Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021}.
+Last, Section \ref{sec:event_study} discusses briefly how to incorporate spillovers into event-study estimation following the insights from \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021}.
 
@@
 
-This section will present a potential outcome framework that formalizes spatial spillovers.
-The goal of this exercise is to formalize treatment effects that are no longer uniquely defined in settings with spillovers.
+This section presents a potential outcome framework that formalizes spatial spillovers.
+The goal of this exercise is to define possible treatment effects of interest since they are no longer uniquely defined in settings with spillovers.
 Following the canonical difference-in-differences framework, I observe a panel of units for periods $t \in \{0,1\}$ and treatment turns on between periods for some of the units.\footnote{This can be extended to multiple periods by replacing $Y_{i0}$ and $Y_{i1}$ throughout with pre- and post- sample averages of $Y_{it}$.
@@
 
-The exposure mapping formalizes the SUTVA violation by summarizing the intensity at which unit $i$ is affected by spillovers.
-Without any restrictions on the exposure mapping, nonparametric identification of treatment effects will be impossible.
-The main assumption for identification, as will be formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ .
+The exposure mapping formalizes violations to the stable-unit treatment value assumption (SUTVA) by summarizing the intensity at which unit $i$ is affected by spillovers.
+Without any restrictions on the exposure mapping, nonparametric identification of treatment effects is impossible.
+The main assumption for identification, as is formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ .
 In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.
@@
 \[
-    \tau_{i, switch}(h_i(\vec{D})) \equiv Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})).
-\] 
-This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant.
-This treatment effect is policy-relevant as it summarizes what would happen if a `local' policymakers decide to enact the policy for unit $i$ (implicity keeping $h$ constant).\footnote{This is what \citet{Savje_Aronow_Hudgens_2021} call the `assignment-conditional unit-level treatment effect'.} It is important to note that the switching effect can depend on the level of exposure.
+    \tau_{i, switch}(\vec{h}) \equiv Y_{i1}(1, \vec{h}) - Y_{i1}(0, \vec{h}).
+\] 
+This is the effect of changing only unit $i$'s treatment status while keeping their exposure to spillovers constant at some value $\vec{h}$.
+This treatment effect is policy-relevant as it summarizes what would happen if a `local' policymakers decide to enact the policy for unit $i$ (implicity keeping $\vec{h}$ constant).\footnote{This is what \citet{Savje_Aronow_Hudgens_2021} call the `assignment-conditional unit-level treatment effect'.} It is important to note that the switching effect can depend on the level of exposure.
 For instance, consider the construction of libraries in towns.
-The effect of library construction in a town that is far away from any other library (exposure of $\vec{0}$) can be different than a town that is very close to a neighboring town's library (large exposure), hence the dependence of $\tau_{i, switch}$ on $h_i(\vec{D})$.
+The effect of library construction in a town that is far away from any other library (exposure of $\vec{0}$) can be different than a town that is very close to a neighboring town's library (large $\vec{h}$), hence the dependence of $\tau_{i, switch}$ on $\vec{h}$.
 Since the size of the switching effect depends on a unit's exposure level, we will consider an average switching effect at each value of exposure,
 \[
-    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}{D_i = 1, h_i(\vec{D}) = h}.
+    \tau_{\text{switch}}(\vec{h}) \equiv \condexpec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}{D_i = 1, h_i(\vec{D}) = \vec{h}}.
 \]
@@
         \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}
-    \]
+    \]d
 \end{assumption}
@@
 \begin{proposition}[Identification of Direct and Total Effects]\label{thm:remove_bias}
-    If assumption (\ref{assumption:random}), (\ref{assumption:no-anticipation}), \nameref{assumption:local}, and \nameref{assumption:parallel-mod}) hold, then (i) 
+    If assumption (\ref{assumption:random}), (\ref{assumption:no-anticipation}),
+
+    \noindent\nameref{assumption:local}, and \nameref{assumption:parallel-mod} hold, then (i) 
     \begin{equation}\label{eq:id_total}
@@
     \end{split}\end{align}
-    where the last equality holds only under assumption (\ref{assumption:homogenous-direct}).
+    where the last equality holds only under assumption \nameref{assumption:homogenous-direct}.
 \end{proposition}
@@
 
-In this section, I revist the analysis of \citet{Chen_Glaeser_Wessel_2021} on the 2017 Opportunity Zone program which created tax incentives for captial investment in targeted Census Tracts.
-To measure the affects of the opportunity zone program on housing prices, the authors collect a panel of census tracts with a measure of housing prices from the Federal Housing Finance Agency (FHFA) from 2014-2019.\footnote{The index tries to create a consistent price index that captures for changes in the composition of homes that are sold over time.} They produce estimates using two different identification strategies.
+In this section, I revist the analysis of \citet{Chen_Glaeser_Wessel_2021} on the 2017 Opportunity Zone program which created tax incentives for captial investment in targeted Census Tracts.\footnote{Concurrent work by \citet{Arefeva_2021} also estimates spillover to nearby opportunity zones using a different datset and finds positive spillover effects on nearby census tracts as well.} To measure the affects of the opportunity zone program on housing prices, the authors collect a panel of census tracts with a measure of housing prices from the Federal Housing Finance Agency (FHFA) from 2014-2019.\footnote{The index tries to create a consistent price index that captures for changes in the composition of homes that are sold over time.} They produce estimates using two different identification strategies.
 

### 2023-02-26 latex/slides/Spillover_slides.tex
Slides draft from 2021

@@
-\documentclass[aspectratio=169]{beamer}
+\documentclass[aspectratio=169,t]{beamer}
 
@@
 
-    Estimation is complicated by \textbf{Spillover Effects}
+    Estimation is complicated by \textbf{Spillover Effects}, when the effect of treatment extends over the treatment boundaries (states, counties, etc.).
 
-    \vspace{5mm}
-    \textbf{Spillover effects} occur when the effect of treatment extends over the treatment boundaries (states, counties, etc.). Example: Amazon Shipping Center
+    Example: Amazon Shipping Center on employment
 
@@
 
-        \item Having nearby counties with shipping centers raises employment and therefore reduces the effect of \textbf{treated counties} through general equilibrium effects
+        \item Having nearby counties with shipping centers raises wages and therefore reduces the employment effect on \textbf{treated counties}
     \end{itemize}
@@
     \begin{itemize}
-        \item Present a potential outcomes framework to formalize spillover effects and evaluate ad-hoc adjustments commonly found in the literature
+        \item Present a potential outcomes framework to formalize treatment and spillover effects and discuss potential estimands of interest
 
-        \item Propose an estimation strategy that improves on current practices by being more robust to spillovers
+        \item Discuss estimation of effects that are \emph{robust} to spillovers
 
@@
         \onslide<2->{
-            \item {\bf \color{coral} Spillover onto Control Units:}
-
-            Nearby ``control'' units fail to estimate counterfactual trends because they are affected by treatment
+            \item {\bf \color{coral} Spillover onto Control Units:} Nearby ``control'' units fail to estimate counterfactual trends
         }
@@
             \vspace{2.5mm}
-            \item {\bf \color{kelly} Spillover onto other Treated Units:}
-
-            Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
+            \item {\bf \color{kelly} Spillover onto other Treated Units:} Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
         }
@@
 
-\begin{frame}{Remove Bias}
-    \only<1>{
-        \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
-    }
-    \only<2>{
-        \[ 
-            y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} +  + \varepsilon_{it}
-        \]
-    }
+% \begin{frame}{Remove Bias}
+%     \only<1>{
+%         \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
+%     }
+%     \only<2>{
+%         \[ 
+%             y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}} +  + \varepsilon_{it}
+%         \]
+%     }
 
-    \only<1>{ 
-        \[ 
-            \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
-        \]
-    }
-    \only<2>{
-        \[ 
-            \mathbb{E}[\hat{\tau}] = \tau,
-        \]
-        so long as $\text{Within}_{it}$ contains all the units with spillovers.
-    }
-\end{frame}
+%     \only<1>{ 
+%         \[ 
+%             \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
+%         \]
+%     }
+%     \only<2>{
+%         \[ 
+%             \mathbb{E}[\hat{\tau}] = \tau,
+%         \]
+%         so long as $S_{it}$ contains all the units with spillovers.
+%     }
+% \end{frame}
 
-\begin{frame}
-    \begin{figure}[tb!]
-        \caption{Single Ring - Removes spillover effects}
-        \begin{center}
-            \resizebox{0.9\textwidth}{!}{
-                \includegraphics{../../figures/figure-within_example.pdf}
-            }
-        \end{center}
-    \end{figure}
-\end{frame}
+% \begin{frame}
+%     \begin{figure}[tb!]
+%         \caption{Single Ring - Removes spillover effects}
+%         \begin{center}
+%             \resizebox{0.9\textwidth}{!}{
+%                 \includegraphics{../../figures/figure-within_example.pdf}
+%             }
+%         \end{center}
+%     \end{figure}
+% \end{frame}
 
-\begin{frame}
-    \begin{figure}[tb!]
-        \caption{Multiple Rings - Improves estimation of spillover effects}
-        \begin{center}
-            \resizebox{0.9\textwidth}{!}{
-                \includegraphics{../../figures/figure-rings_example.pdf}
-                } 
-            \end{center}
-    \end{figure}
-\end{frame}
+% \begin{frame}
+%     \begin{figure}[tb!]
+%         \caption{Multiple Rings - Improves estimation of spillover effects}
+%         \begin{center}
+%             \resizebox{0.9\textwidth}{!}{
+%                 \includegraphics{../../figures/figure-rings_example.pdf}
+%                 } 
+%             \end{center}
+%     \end{figure}
+% \end{frame}
 
@@
             \vspace{2.5mm}
-            \item Show that an indicator for being close to treated units remove \textit{all bias} so long as the indicator contains all units affected by spillovers
-
-            \vspace{2.5mm}
-            \item `Rings' are able to estimate spillover effects while still removing all bias
+            \item Discuss estimands of interest and classify which are identifiable and which are not
         \end{itemize}
@@
 
-\imageframe{../../figures/figure-spill_within.png}
-
 \begin{frame}{Examples of $h_i(\vec{D})$}
@@
 
-\imageframe{../../figures/figure-spill_within_additive.png}
+\begin{frame}{Estimands}{Treatment Effect without Spillovers}
+    \[
+        \tau \equiv \mathbb{E} \left[ Y_i(1) - Y_i(0) \mid D_i = 1\right]
+    \]
+    \vspace{5mm}
 
-\begin{frame}{Estimand of Interest}
-    \begin{block}{Estimand of Interest:}
+    \begin{itemize}
+        \item The average effect of switching on unit $i$'s treatment
+    \end{itemize}
+
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Switching Effect}
     \[
-        \textcolor{green}{\tau_{\text{direct}}} \equiv \textcolor{green}{\mathbb{E}\left[ Y_{i,1}(1, 0) - Y_{i,1}(0, 0) \mid D_i = 1\right]}
+        \textcolor{maroon}{\tau_{\text{switch}}(h)} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})) \mid D_i = 1, h_i(\vec{D}) = h \right]
     \]
-    \end{block}
+
+    \vspace{5mm}
+
+    \begin{itemize}
+        \item Keep everyone's treatment constant and toggle unit $i$'s treatment effect. Average across all units with exposure $h$.
+
+        \item This is policy relevant: what will happen if my county turns on treatment.
+        \pause
+
+        \item This requires knowledge of $h_i(\vec{D})$ in order to find control units to estimate $Y_{i1}(0, h_i(\vec{D}))$.
+    \end{itemize}
+
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Switching Effect}
+    \begin{align*}
+        \textcolor{maroon}{\tau_{\text{switch}}(h)} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]\\ 
+        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]} 
+    \end{align*}
+
+    \vspace{5mm}
+    Identification requires two things:
+    \begin{enumerate}
+        \item Knowledge of $h_i(\vec{D})$ in order to estimate the second term with control units.
+
+        \item Spillover effect homogeneity (so second term would be the same for treated units).
+    \end{enumerate}
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Total Effect}
+    \[
+        \textcolor{navy}{\tau_{\text{total}}} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right]
+    \]
+
+    \vspace{5mm}
+    \begin{itemize}
+        \item Toggle entire vector of treatment effects. Average across all treated units.
+
+        \item This is helpful for post-hoc policy analysis: what was the average effect on treated units of implementing $\vec{D}$.
+    \end{itemize}
+
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Total Effect}
+    \begin{align*}
+        \textcolor{navy}{\tau_{\text{total}}} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1\right]\\ 
+        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0,\vec{0}) \mid D_i = 1 \right]} 
+    \end{align*}
+
+    \vspace{5mm}
+    Identification much simpler:
+    \begin{itemize}
+        \item Need to identify control units without spillover effects
+    \end{itemize}
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Direct Effect}
+    \[
+        \textcolor{kelly}{\tau_{\text{direct}}} \equiv \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1 \right]
+    \]
+
+    \vspace{5mm}
+    \begin{itemize}
+        \item Toggle treatment effect for individuals with no exposure.
+
+        \item This is the switching effect with $h = 0$.
 
         \pause
-    \vspace{2.5mm}
-    \begin{block}{Spillover Effects:}
+        \item Identified under mild assumptions.
+    \end{itemize}
+
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Direct Effect}
+    \begin{align*}
+        \textcolor{kelly}{\tau_{\text{direct}}} &= \mathbb{E} \left[ Y_{i1}(1, \vec{0}) - Y_{i0}(0,\vec{0}) \mid D_i = 1 \right]\\ 
+        &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, \vec{0}) - Y_{i0}(0,\vec{0}) \mid D_i = 1 \right]} 
+    \end{align*}
+
+    \vspace{5mm}
+    Identification much simpler:
+    \begin{itemize}
+        \item Need to identify treated/control units without spillover effects
+    \end{itemize}
+    \vspace{60mm}
+\end{frame}
+
+\begin{frame}{Estimands}{Spillover Effects}
     \[
-        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]}
+        \textcolor{red}{\tau_{\text{spillover, treated}}} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]
     \]
@@
     \[ 
-        \textcolor{coral}{\tau_{\text{spillover, control}}} = \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]}
+        \textcolor{coral}{\tau_{\text{spillover, control}}} \equiv \mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]
     \]
-    \end{block}
+    \vspace{5mm}
+    \vspace{60mm}
 \end{frame}
 
-\begin{frame}{Parallel Trends}
+\begin{frame}{What does Difference-in-Differences identify?}{Parallel Trends}
     I assume a modified version of the parallel counterfactual trends assumption:
@@
     \begin{block}{Assumption: {\it Parallel Counterfactual Trends}}
+        \vspace{-5mm}
         \begin{align*}
@@
 
-    \vspace{5mm}
-    In the \textit{complete absence of treatment }(not just the absence of individual $i$'s treatment):
+    In the \emph{complete absence of treatment} (not just the absence of individual $i$'s treatment):
 
@@
 
-\begin{frame}{What does Difference-in-Differences identify?}
-    With the parallel trends assumption and random assignment of $D_i$, I decompose the difference-in-differences estimate as follows:
+\begin{frame}{What does Difference-in-Differences identify?}{Decomposition}
+    With the parallel trends assumption, I decompose the difference-in-differences estimate as follows:
 
@@
         \mathbb{E}\left[\hat{\tau}\right] &= \underbrace{\mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 1 \right] - \mathbb{E} \left[ Y_{i1} - Y_{i0} \mid D_i = 0 \right]}_{\text{Difference-in-Differences}} \\[3mm]
-        \pause&= 
-        \textcolor{green}{\mathbb{E} \left[ Y_{i1}(1, 0) - Y_{i1}(0, 0) \mid D_i = 1 \right]} \\
-        &\quad + \quad 
-        \textcolor{red}{\mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0) \mid D_i = 1 \right]} \\ 
-        &\quad - \quad  
-        \textcolor{coral}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, 0) \mid D_i = 0 \right]} \\[3mm]
-        &= \textcolor{green}{\tau_{\text{direct}}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{coral}{\tau_{\text{spillover, control}}}
+        \pause&= \tau_{\text{direct}} + \textcolor{red}{\tau_{\text{spillover, treated}}} - \textcolor{coral}{\tau_{\text{spillover, control}}} \\[3mm]
+        \pause&= \tau_{\text{total}} - \textcolor{coral}{\tau_{\text{spillover, control}}} 
     \end{align*}
@@
 
-\begin{frame}{Removing Bias}
-
+\begin{frame}{Identification of Direct/Total Effects}
     \begin{block}{Assumption: {\it Spillovers are Local}}
@@
 
-\begin{frame}{Removing Bias}
-    With assumption that spillovers are local, define $S_it$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).
+\begin{frame}{Identification of Total Effect}
+    With assumption that spillovers are local, define $S_{it}$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).
 
+    \vspace{5mm}
+    Estimation of the following equation:
+    \[ 
+        y_{it} = \mu_t + \mu_i + \tau D_{it} + \tau_{\text{spill,control}} S_{it} * (1-D_{it}) + \varepsilon_{it}
+    \]
+
+    \begin{itemize}
+        \item $\hat{\tau}$ is consistent for $\tau_{\text{total}}$
+
+        \item $\hat{\tau}_{\text{spill, control}}$ is not consistent for average spillover effects. 
+    \end{itemize}
+\end{frame}
+
+\begin{frame}{Identification of Direct Effect}
+    With assumption that spillovers are local, define $S_{it}$ to be an indicator equal to one in the post period for all units with $h(\vec{D}, i) \neq \vec{0}$ (and potentially some units with $= \vec{0}$).
+
+    \vspace{5mm}
     Estimation of the following equation:
@@
 
-        \item $\hat{\tau}_{\text{spill}}$'s are not consistent for average spillover effects (hence the need for rings).
+        \item $\hat{\tau}_{\text{spill}}$'s are not consistent for average spillover effects.
     \end{itemize}
 
-\end{frame}
-
-\begin{frame}{Aside -- Removing ``contaminated'' controls}
-    A common solution to the problem of spillover is to re-estimate on a subsample with neighboring control units removed.
-
-    This is not recommended for two reasons:
-
-    \begin{itemize}
-        \item Removing control units from the sample decreases precision of the estimates
-
-        \item Spillover effects on treated units will still remain in the estimand. 
-    \end{itemize}
-\end{frame}
-
-% ------------------------------------------------------------------------------
-\section{Estimation of Spillovers}
-% ------------------------------------------------------------------------------
-
-\begin{frame}{Robustness to Misspecification}
-    Generate data using the following data-generating process with different exposure mappings:
-
-    \[ 
-        y_{\it} = \mu_t + \mu_i + 2 D_{it} + \beta_{\text{spill,control}} * (1-D_{it}) h(\vec{D}, i) + \varepsilon_{it}
-    \]
-
-    \begin{itemize}
-        \item Observation $i$ is a U.S. county, year $t \in \{2000, \dots, 2019\}$, treatment $D_{it}$ turns on in 2010 and is assigned randomly.
-
-        \item Details in the paper, but $\mu_t$ is normally distributed on a linear time trend, $\mu_i$ are normally distributed
-    \end{itemize}
-
-    Then, I estimate each data-generating process using (potentially) misspecified $\tilde{h}(\vec{D}, i)$ and report the average estimate bias.
-\end{frame}
-
-\begin{frame}{Specifications of $h(\vec{D}, i)$}
-
-    \begin{itemize}
-        \item \textit{Within $40/80$mi.}:
-        \begin{itemize}
-            \item Indicator for nearest treated unit being within $40/80$ miles.
-        \end{itemize}
-
-        \item \textit{Within $40/80$mi. (Additive)}: 
-        \begin{itemize}
-            \item Number of treated units being within $40/80$ miles.
-        \end{itemize}
-
-    \end{itemize}
-
-\end{frame}
-
-\imageframe{../../figures/figure-spill_within_large.png}
-\imageframe{../../figures/figure-spill_within_large_additive.png}
-
-\begin{frame}{Specifications of $h(\vec{D}, i)$}
-
-    \begin{itemize}
-        \item \textit{Decay}: 
-        \begin{itemize}
-            \item $\max_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-        \item \textit{Decay (Additive)}: 
-        \begin{itemize}
-            \item $\sum_j D_j * e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$
-        \end{itemize}
-
-    \end{itemize}
-
-\end{frame}
-
-\imageframe{../../figures/figure-spill_decay.png}
-\imageframe{../../figures/figure-spill_decay_additive.png}
-
-\begin{frame}{Specifications of $h(\vec{D}, i)$}
-
-    \begin{itemize}
-        \item \textit{Rings}: 
-        \begin{itemize}
-            \item Set of concentric rings. For each ring, indicator for nearest treated unit being within that distance bin
-        \end{itemize}
-
-        \item \textit{Rings (Additive)}: 
-        \begin{itemize}
-            \item Set of concentric rings. For each ring, number of treated units being within that distance bin
-        \end{itemize}
-    \end{itemize}
-
-\end{frame}
-
-\imageframe{../../figures/figure-spill_ring.png}
-
-\begin{frame}
-
-    \begin{table}[!tb]
-        \caption{Bias from Misspecification of Spillovers}
-        \label{tab:misspecification}
-
-        \begin{adjustbox}{width = \textwidth, center}
-            \begin{threeparttable}
-                \begin{tabular}{@{} l rrrrrr @{}}
-                    % Head
-                    \toprule
-                    & \multicolumn{6}{c}{Data-Generating Process} \\
-                    \cmidrule{2-7}
-
-                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
-                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
-
-                    % Body
-                    \midrule
-
-                    % \input{../../tables/misspecification_slides.tex}
-                    TWFE (No Spillovers) & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ & $0.258$ \\ \midrule
-                    \marktopleft{c1}Within 40mi. & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
-                    Within 80mi. & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c1}
-                    \onslide<2->{
-                        \\ \midrule
-                        Within 40mi. (Additive) & $0.043$ & $0.221$ & $-0.006$ & $0.177$ & $0.174$ & $0.143$ \\ 
-                        Within 80mi. (Additive) & $0.034$ & $0.134$ & $-0.012$ & $-0.009$ & $0.099$ & $-0.010$ \\ \midrule
-                        Decay 80mi. & $-0.159$ & $0.070$ & $-0.174$ & $0.014$ & $-0.009$ & $-0.033$ \\ 
-                        Decay 80mi. (Additive) & $-0.023$ & $0.148$ & $-0.084$ & $0.019$ & $0.088$ & $-0.008$
-                    }
-                    \onslide<3->{
-                        \\ \midrule
-                        \marktopleft{c2}Rings (0-20, 20-30, 30-40) & $-0.005$ & $0.213$ & $-0.005$ & $0.176$ & $0.159$ & $0.143$ \\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ & $-0.009$ \markbottomright{c2}\\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $0.036$ & $0.134$ & $-0.008$ & $-0.008$ & $0.100$ & $-0.009$ 
-                    }
-
-                    \\ \bottomrule
-                \end{tabular}
-            \end{threeparttable}
-        \end{adjustbox}
-    \end{table}
-
-    \onslide<3->{
-        \textbf{Indicator (or set of rings) that captures \emph{all} affected unit removes all bias}
-    }
-\end{frame}
-
-\begin{frame}{Spillovers as Estimand of Interest}
-    Until now, we assumed our estimand of interest is $\textcolor{green}{\tau_{\text{direct}}}$.
-
-    However, the two other spillover effects are of interest as well:
-    \begin{itemize}
-        \item $\textcolor{coral}{\tau_{\text{spillover, control}}}$: Do the benefits of a treated county come at a cost to neighbor counties?
-
-        \item $\textcolor{red}{\tau_{\text{spillover, treated}}}$: Does the estimated effect change based on treatment of neighbors? 
-    \end{itemize}
-
-    To estimate the spillover effects, we have to parameterize $h(\vec{D}, i)$ function and the potential outcomes function $Y_i(D_i, h(\vec{D}, i))$.
-\end{frame}
-
-\begin{frame}{Estimation of Spillover Effects}
-    To see which specifications can predict spillover effects well, I estimate the spillover effects for each control unit, $\hat{\beta}_{\text{spill, control}} * \tilde{h}(\vec{D}, i)$.
-
-    Then calculate \[ 
-        1 - \frac{
-                \overbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}^{\text{Mean Square Prediction Error}}
-            }{
-                \underbrace{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h(\vec{D}, i))^2}_{\text{Normalization}}
-            }    
-    \]
-
-    This gives the proportion of spillovers explained by $\tilde{h}(\vec{D}, i)$
-
-\end{frame}
-
-\begin{frame}
-    \begin{figure}[tb!]
-        \caption{Single Ring - Removes spillover effects}
-        \begin{center}
-            \resizebox{0.9\textwidth}{!}{
-                \includegraphics{../../figures/figure-within_example.pdf}
-            }
-        \end{center}
-    \end{figure}
-\end{frame}
-
-\begin{frame}
-    \begin{figure}[tb!]
-        \caption{Multiple Rings - Improves estimation of spillover effects}
-        \begin{center}
-            \resizebox{0.9\textwidth}{!}{
-                \includegraphics{../../figures/figure-rings_example.pdf}
-                } 
-            \end{center}
-    \end{figure}
-\end{frame}
-
-\begin{frame}
-    \begin{table}[!tb]
-        \caption{Percent of Spillovers Predicted by Specification}
-        \label{tab:misspecification_mspe}
-
-        \begin{adjustbox}{width = \textwidth, center}
-            \begin{threeparttable}
-                \begin{tabular}{@{} l rrrrrr @{}}
-                    % Head
-                    \toprule
-                    & \multicolumn{6}{c}{Data-Generating Process} \\
-                    \cmidrule{2-7}
-
-                    & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Within 40mi.}} & \multicolumn{1}{c}{\textbf{Within 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} & \multicolumn{1}{c}{\textbf{Decay 80mi.}} \\
-                    Specification & & & \multicolumn{1}{c}{\textbf{(Additive)}} & \multicolumn{1}{c}{\textbf{(Additive)}} & & \multicolumn{1}{c}{\textbf{(Additive)}} \\
-
-                    % Body
-                    \midrule
-
-                    % \input{../../tables/misspecification_slides.tex}
-                    TWFE (No Spillovers) & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ & $0.0\%$ \\ \midrule
-                    \marktopleft{c3}Within 40mi. & $99.4\%$ & $25.9\%$ & $85.6\%$ & $38.8\%$ & $59.5\%$ & $56.1\%$ \\ 
-                    Within 80mi. & $39.8\%$ & $96.2\%$ & $34.3\%$ & $71.7\%$ & $85.6\%$ & $68.0\%$ \markbottomright{c3}
-                    \onslide<2->{
-                    \\ \midrule
-                        Within 40mi. (Additive) & $85.3\%$ & $21.2\%$ & $99.5\%$ & $40.6\%$ & $52.0\%$ & $60.7\%$ \\ 
-                        Within 80mi. (Additive) & $45.8\%$ & $61.8\%$ & $47.2\%$ & $98.4\%$ & $71.0\%$ & $93.6\%$ \\ \midrule 
-                        Decay 80mi. & $60.1\%$ & $82.5\%$ & $52.7\%$ & $75.8\%$ & $97.5\%$ & $82.2\%$ \\ 
-                        Decay 80mi. (Additive) & $60.7\%$ & $56.9\%$ & $63.8\%$ & $93.5\%$ & $79.0\%$ & $98.7\%$ 
-                    }
-                    \onslide<3->{
-                        \\ \midrule 
-                        \marktopleft{c4}Rings (0-20, 20-30, 30-40) & $98.4\%$ & $23.7\%$ & $85.9\%$ & $37.5\%$ & $58.9\%$ & $56.2\%$ \\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) & $96.6\%$ & $91.7\%$ & $84.2\%$ & $72.7\%$ & $91.9\%$ & $78.4\%$ \\ 
-                        Rings (0-20, 20-30, 30-40, 40-60, 60-80) (Additive) & $83.5\%$ & $57.4\%$ & $97.6\%$ & $95.0\%$ & $73.5\%$ & $94.9\%$\markbottomright{c4} 
-                    }
-
-                    \\ \bottomrule
-                \end{tabular}
-            \end{threeparttable}
-        \end{adjustbox}
-    \end{table}
-
-    \onslide<3->{
-        \textbf{Donuts perform best at estimating spillover effects.}
-
-        \textbf{It is important to get Additive vs. Non-Additive correct.}
-    }
 \end{frame}
@@
     \begin{itemize}
-        \item What are the local effects of TVA on manufacturing and agricultural economies?
+        \item What is the total effect of TVA investments on manufacturing and agricultural employment?
         \item Do these effects come at the cost of other counties?
@@
     \[ 
-        y_{it} = \mu_i + \mu_t + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}} + \varepsilon_{it}
+        y_{it} = \mu_i + \mu_t + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}} + \varepsilon_{it}
     \]
@@
 
-    1. Estimate $\mu_i$ and $\mu_t$ using observations that aren't yet treated/affected by spillovers ($D_{it} = 0$ and $Within_{it} = 0$). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.
+    1. Estimate $\mu_i$ and $\mu_t$ using observations that are not yet treated/affected by spillovers ($D_{it} = 0$ and $S_{it} = 0$). Then subtract off $\hat{\mu}_i$ and $\hat{\mu}_t$.
 
     2.
-Then, regress $\tilde{y}_{it}$ on $\tau D_{it} + {\color{coral} \tau_{\text{spill,control}} \text{Within}_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} \text{Within}_{it} * D_{it}}$ (or interacted event study leads/lags).
+Then, regress $\tilde{y}_{it}$ on $\tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}}$ (or interacted event study leads/lags).
 This estimate is unbiased because $D_{it}$ is non-residualized (standard errors require adjusting).
@@
 \begin{frame}{Community Health Centers}
-    \begin{citecolor}\citet{Bailey_Goodman_Bacon_2015}\end{citecolor} study the creation of federal community health centers between 1965 and 1974
+    \begin{citecolor}\citet{Bailey_Goodman_Bacon_2015}\end{citecolor} study the creation of federal community health centers between 1965 and 1974.
 
-    \textbf{Research Question:} Do low-/no-cost health services lower the mortality rate of the treated counties? \emph{New Question:} Do these effects spread to neighboring counties?
+    \vspace{5mm}
+    Research Question:
+
+    \begin{itemize}
+        \item Do low-/no-cost health services lower the mortality rate of the treated counties? 
+        \item \emph{New Question:} Do these effects spread to neighboring counties?
+    \end{itemize}
 \end{frame}

### 2023-02-27 latex/paper/Spillover.tex
Rework paper to make it more concise and fix some proofs

@@
 
-\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Brantly Callaway, Pedro Sant'Anna, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, the Urban Economics Association Conference, the WEAI Conference, and the University of Rochester HEEL Lab for helpful comments.}}
+\title{Difference-in-Differences with Spatial Spillovers\thanks{I am grateful to Taylor Jaworski, Adam McCloskey, Brantly Callaway, Pedro H.C.
+Sant'Anna, Damian Clarke, Daniel Kaffine, Tania Barham, Alexander Bentz, James Flynn, Brach Champion, Hannah Denker, the CU Boulder Labor Economics Seminar, the Urban Economics Association Conference, the WEAI Conference, and the University of Rochester HEEL Lab for helpful comments.}}
 \author{\href{https://kylebutts.com/}{Kyle Butts}\thanks{University of Colorado Boulder, Economics Department (\href{mailto:kyle.butts@colorado.edu}{kyle.butts@colorado.edu})}}
@@
 }
+
+% Conditionally display thoughts
+% https://tex.stackexchange.com/questions/33576/conditional-typesetting-build
+\usepackage{etoolbox}
+
+\newtoggle{INCLUDECOMMENTS}
+\toggletrue{INCLUDECOMMENTS}
+% \togglefalse{INCLUDECOMMENTS}
+
+\newcommand{\nick}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Nick:} #1}}{}}
+\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}
 
@@
 In this paper, I introduce a potential outcomes framework to model spillover effects and decompose the estimate's bias in two parts: (1) the control group no longer identifies the counterfactual trend because their outcomes are affected by treatment and (2) changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of ``close'' units.
-I propose estimation strategies that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves including in settings with staggered treatment timing.
+I propose conditions for non-parametric identification that can remove both sources of bias and semi-parametrically estimate the spillover effects themselves including in settings with staggered treatment timing.
 To highlight the importance of spillover effects, I revisit analyses of three place-based interventions.
@@
 a new factory opening increases service sector spending in the entire commuting zone).
-For other treated units, the treatment effect can depend on other units' treatment status.
-Forces of agglomeration can increase effect size as treatment concentration increases (e.g.
-knowledge-sharing between firms) or forces of congestion/competition can decrease the effects of treatment (e.g.
-bidding up of wages causes the employment effects of factory openings to be mitigated).
-
-In this paper, I introduce a potential outcomes framework that directly models spillover effects and use this model to derive identification results in difference-in-differences settings.
-Using this potential outcome framework, I define different possible treatment effects of interest, discuss their interpretation, and show which effects are non-parametrically identified.
-
-First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
-It is difficult to estimate the switching effect without parametric assumptions on spillovers.
-The reason for this is that the magnitude of the switching effect potentially depends on the treatment status of a unit's neighbors.
-For example, the construction of low-cost medical facilities will have larger treatment effects when neighboring areas do not have facilities.
-Switching effects therefore are defined separately for each level of exposure and estimation of the effect at a particular level requires knowledge of which control units experience the same level of exposure.
-I show that identification therefore requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the homogeneity of spillover effects.
-While the switching effect is not identified nonparametrically in general, the switching effect for units with zero exposure is identified under mild assumptions.
-I call this effect the `direct effect' which measures the effects of turning on a unit's treatment if they were the \emph{only} unit to be treated in their general area.
-
+In some cases, the treatment effect may depend on the treatment status of other units.
+The concentration of treatment can increase its impact through knowledge-sharing between firms, while congestion or competition may decrease its effects, such as when wage bids mitigate employment effects of factory openings.
+
+Estimation of treatment effects in these settings typically proceed in two ways.
+One approach involves using a structural model to account for general equilibrium effects.
+For example, trade models generate a market access term that effectively controls for such effects \citep{Donaldson_Hornbeck_2016} or the common Manski linear-in-means model controls for the average characteristics of a unit's peers \citep{manski1993identification,goldsmith2013social}.
+Another strategy involves excluding units located close to the treatment area (or including a dummy variable) to avoid any spillover biases on the effects, which is preferred by researchers who wish to remain agnostic to structural assumptions.
+This paper adopts the latter non-parametric approach and formalizes the identification assumptions required to interpret the estimates causally.
+
+To do so, this paper introduces a potential outcomes framework following \citet{vazquez2022identification} and extends the framework to difference-in-differences settings.
+Since potential outcomes are now characterized by a unit's treatment status as well as the treatment status of other units, there are many potential treatment effects that can be formualted.
+I study two relevant treatment effects.
 The second effect of interest is the `total effect' which is the relevant parameter for national policymakers who want to answer ``What is the average effect of implementing the entire treatment regime?''.
 This treatment effect summarizes the post-hoc effects of going from the world with no treatment to the observed treatment vector.
-This effect comes from two sources: the direct effect on each treated unit and the average spillover effect on to treated units from other treated units.
-
-This paper then defines conditions under which the direct and total effects are nonparametrically identified by a modified difference-in-differences type estimand under a mild assumption that spillovers are `local' in nature.
-The local spillovers assumption holds in the case where spillover effects are only experienced by units within a certain distance of treated units.
+First, there is the `switching effect' which is the relevant parameter for local policymakers who want to answer ``What is the effect of switching my treatment status, holding fixed all other units' treatment?''.
+
+After defining these effects, I discuss non-parametric identification results extending standard parallel-trends assumptions to settings with spillovers.
+First, I demonstrate that the `total effect' can be identified under assumptions that spillovers are ``local'' and only affect nearby units, while parallel trends exist between treated and non-affected ``far-away'' units.
 This would hold in the case where individuals can travel to access treatment and therefore spillovers are limited by travel costs.
-However, this would fail in the case of large general equilibrium shocks that cause units far away to be affected by treatment (e.g.
-San Francisco being affected by shocks to the New York economy).
-
-Next, I assess the commonly used difference-in-differences estimate.
-This paper shows that the difference-in-differences estimator is a biased estimate for the direct and the total effect.
-This bias arises because untreated units that are `close' to treated units experience effects of treatment and therefore these `control' units fail to identify the counterfactual trend.
-Difference-in-differences estimates average the spillover onto the `close' control units into the untreated units' change in outcomes.
-Hence, the spillover is subtracted from the estimated treatment effect and biases the estimate in the opposite sign of the spillover effect.
-For example, if nearby control units also benefit from treatment, then researchers would underestimate the treatment effect of the treated.
-The direct effect also has a second source of bias because changes in treated units' outcomes reflect the effect of their own treatment status and the effect from the treatment status of `close' units.
-In difference-in-differences, the spillover onto other treated units is averaged into the treated units' change in outcomes.
-Therefore the bias on the direct effect estimate is the same sign as the sign of the spillover.
-
-Under the assumption that spillovers are local, I formalize the identification argument used in a common adjustment of including an indicator for being affected by spillovers (or removing them from the sample) in the two-way fixed-effects model.
+However, this assumption may not hold in the case of large general equilibrium shocks that affect units far away from the treatment area, such as when New York's economy impacts San Francisco.
+
+Estimating the switching effect without parametric assumptions on spillovers is challenging since the effect's magnitude often depends on the treatment status of neighboring units.
+For instance, the construction of low-cost medical facilities will have more substantial treatment effects when neighboring areas lack such facilities.
+As a result, switching effects must be defined separately for each level of exposure, and estimating the effect at a specific level necessitates knowledge of which control units share the same level of exposure.
+I demonstrate that identification requires \emph{either} parametrization of spillovers \emph{or} certain constraints on the homogeneity of spillover effects.
+
+Subsequently, the commonly used difference-in-differences estimator is evaluated.
+The study demonstrates that this estimator produces biased estimates for both the total effects.
+This bias arises from the fact that untreated units that are "close" to treated units experience treatment effects, thereby failing to identify the counterfactual trend.
+The difference-in-differences estimate averages the spillover onto the "close" control units into the untreated units' change in outcomes.
+As a result, the spillover is subtracted from the estimated treatment effect, introducing bias in the opposite sign of the spillover effect.
+
+Then, I formalize the identification strategy commonly used to adjust for spillovers by including an indicator variable for units affected by spillovers (or removing them from the sample) in the two-way fixed-effects model.
 I show, under mild assumptions, that this method will remove \emph{all bias} from the treatment effect estimate so long as the indicator captures all units affected by spillovers.
-The bias term in the difference-in-differences estimate for the total effect is the \textit{average} spillover effects onto control units.
-An indicator variable that contains \emph{all} control units affected by spillover can therefore remove this bias.
 However, adding this indicator changes the underlying control group to the control units not included in the indicator variable and hence a researcher must justify why this subsample will form a valid control group for the parallel trends assumption.
-When estimating the direct effect, a second indicator variable containing \emph{all} treated units affected by spillovers can remove the second source of bias.
-Similar to the control group indicator, this modifies the treatment group over which the average treatment group is taken (those with indicator equal to zero).
 Importantly, my method does not require researchers to make any assumptions about how spillover effects propagate across space.
@@
 The above method can be improved by creating a set of distance bins from the treated units (e.g.
-being 0-20 miles, 20-40 miles, 40-60 miles from the treated units) and interacting them with a treatment indicator.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
-In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.} Since a set of `rings' is collinear with a single indicator covering the bins, this estimator consistently estimates the treatment effect of interest.
+being 0-20 miles, 20-40 miles, 40-60 miles from the treated units) and interacting them with a treatment indicator.
+Since a set of `rings' is collinear with a single indicator covering the bins, this estimator consistently estimates the treatment effect of interest.
 This estimator has the added benefit that each indicator will estimate the average spillover effect on treated/control units within that distance range which provides a more complete picture of which units are affected by treatment and at what magnitude.
+However, interpreting these estimates causally requires that each ring satisfies a parallel trends assumption with the `far-away' control units.\footnote{The choice of the distance bins depends on the economic context and in particular the source of the spillovers.
+In some cases, the bins can be determined in a data-driven way \citep{Butts_2021}.}
 
@@
 
-Last, in Section \ref{sec:event_study}, I extend estimation of the direct effect and spillover effects of treatment into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}.
+Last, in Section \ref{sec:event_study}, I extend estimation of treatment and spillover effects into the TWFE/event-study framework by extending the work of \citet{Gardner_2021}.
 This allows for a very common setting in which treatment turns on for different units in different periods.
@@
 I contribute to the literature that focuses on estimation of treatment effects with spatial spillovers using the difference-in-differences framework in three ways \citep{Clarke_2017,Berg_Streitz_2019,Verbitsky-Savitz_Raudenbush_2012,Delgado_Florax_2015}.
-My paper is the first to consider identification in terms of general potential outcomes.
+My paper is the first to consider non-parametric identification in terms of general potential outcomes.
 Other papers derive results for specific spillover mappings.
@@
 The literature has focused on estimating the total effect, so I further contribute by discussing alternative treatment effect estimates and identification results.
-Last, my paper also advances the literature by considering estimation of direct effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.
+Last, my paper also advances the literature by considering estimation of treatment effects and spillover effects in the event-study framework which allows for the common occurrence of staggered treatment adoption.
 
 This paper relates to a broad literature on spillover effect estimation in randomized experiments.\footnote{See \citet{Sobel_2006} and \citet{Hudgens_Halloran_2008} for early work.
-See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{Vazquez-Bare_2019} and references therein for recent work on this.} There are two main strands of this literature.
+See \citet{Hu_Li_Wager_2021}, \citet{Savje_Aronow_Hudgens_2021}, and \citet{vazquez2022identification} and references therein for recent work on this.} There are two main strands of this literature.
 First, there is a large literature on the estimation of treatment effects in the presence of spillovers using a `partial identification' framework where units are in distinct treatment clusters and outcomes depend on the treatment status within the observation's cluster only.\footnote{ \citet{Angelucci_DiMaro_2016} provides an overview of estimation of treatment effects in the presence of ``within-group'' spillovers.
@@
 
-There is also a nascent literature exploring estimation of direct and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}, \citet{Vazquez-Bare_2019}, and \citet{Hu_Li_Wager_2021}).
-Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, including a modified parallel-trends assumption, for identification in non-experimental settings.
+There is also a nascent literature exploring estimation of treatment and spillover effects which does not require a completely untreated cluster in experimental settings (\citet{Savje_Aronow_Hudgens_2021}; \citet{vazquez2022identification}; \citet{Hu_Li_Wager_2021}; \citet{yu2022estimating}).
+Those papers' identification results rely on \emph{design-based} assumptions around the treatment-assignment mechanism, while this paper relies on \emph{model-based} assumptions, based on a modified parallel-trends assumption, for identification in non-experimental settings.
 I contribute to this literature by formalizing identification results of different treatment effects in non-experimental settings.
@@
 Section \ref{sec:po_framework} presents the potential outcomes framework, defines the estimand of interest, discusses identification of effects, and shows the resulting bias from estimating a classical difference-in-differences model.
-Section \ref{sec:estimation} focuses on the estimation of the direct effect, the total effect, and spillover effects.
+Section \ref{sec:estimation} focuses on the estimation of the total effect and spillover effects.
 Section \ref{sec:tva} presents an application for evaluating the Tennessee Valley Authority program.
@@
 
-\begin{assumption}[Random Sampling]\label{assumption:random}
-    $\{ Y_{i0}, Y_{i1}, D_{i} \}_{i = 1}^{n}$ is an independent and identically distributed sample of panel data.
-\end{assumption}
-
-Assumption (\ref{assumption:random}) allows me to consider observations as coming from a larger population (sometimes called a superpopulation).
-Later, when discussing inference, I will relax this assumption to account for spatial correlation between observations, but identification does not rely on independence.
-As an alternative, inference could come from a design-based perspective following \citet{Athey_Imbens_2021}.
-
 Potential outcomes, denoted $Y_{it}(D_i, h_i(\vec{D}))$, are a function of unit $i$'s own treatment-status $D_i$ and, departing from the standard potential outcomes framework, of a function of the entire vector of treatment assignments $h_i(\vec{D})$ where $\vec{D} \in \{0,1 \}^n$ denotes the $n$-dimensional vector of all unit treatments.
 The non-negative scalar- or vector-valued function $h_i(\vec{D})$ is referred to as an `exposure mapping'.
-This setup follows \citet{Vazquez-Bare_2019} who studies identification of spillover effects under an experimental setting.\footnote{Note that throughout, expectations and inference are conditional on the vector of exposure mappings.
+This setup follows \citet{vazquez2022identification} who studies identification of spillover effects under an experimental setting.
+Assumption (\ref{assumption:random}) allows me to consider observations as coming from a larger population (sometimes called a superpopulation).\footnote{Note that throughout, expectations and inference are conditional on the treatment vector (and hence exposure mappings) as in \citet{Borusyak_Jaravel_Spiess_2021}.
 In design-based settings, the distribution of exposure mappings is known so expectations can be taken without conditioning on the vector of exposure mappings.
 See \citet{Savje_Aronow_Hudgens_2021} for discussion estimation and inference when the treatment design is known.}
+
+\begin{assumption}[Random Sampling]\label{assumption:random}
+  $\{ Y_{i0}, Y_{i1} \}_{i = 1}^{n}$ is an independent and identically distributed sample of panel data.
+\end{assumption}
 
@@
 The main assumption for identification, as is formalized in section \ref{sec:remove_bias}, is that when unit $i$ is sufficiently `far' away, it has no exposure to spatial spillovers and $h_i(\vec{D}) = \vec{0}$ .
-In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.
-
-The identification results of this paper do not require parameterization of the exposure mapping.
-However, to help better understand the exposure mapping, I give three examples that are commonly used in the literature.
-
-\begin{example}
-    $h_i(\vec{D})$ can be an indicator variable that equals one only if there is a treated unit within $\bar{d}$ miles of unit $i$.\footnote{Similarly, a dummy for counties that share contiguous borders is commonly used.} Let $d(i,j)$ be a distance measure that is the distance between unit $i$ and $j$.
-In this case \begin{equation}\label{eq:h_within}
-        h_i(\vec{D}) = \max_{j \neq i} D_j * \one_{ d(i,j) < \bar{d}}
-    \end{equation}
-    This exposure mapping is a realistic specification when it is assumed that spillover effects do not decay over distance until $\bar{d}$ and the intensity of spillovers does not depend on the number of neighboring units treated.
-For example, this exposure mapping likely applies in the context of new library creation \citep{Berkes_Nencka_2020}.
-In this case, the distance $\bar{d}$ would be the maximum distance people would travel to a nearby library.
-The benefits of access to a neighboring town library do not depend on whether people can access 1 or more nearby libraries, so the binary exposure mapping is a good approximation to spillovers in this context.
-\end{example}
-
-\begin{example}
-    Second, $h_i(\vec{D})$ can be a function that equals the number of units treated within distance $\bar{d}$, i.e. \begin{equation}\label{eq:h_within_additive}
-        h_i(\vec{D}) = \sum_{j \neq i} D_j * \one_{d(i,j) < \bar{d}}.
-    \end{equation}
-    This exposure mapping is no longer binary, so the intensity of spillovers is additive in the number of nearby units treated.
-In the context of wholesale store openings, this exposure mapping captures the additive nature of agglomeration economies.
-As more nearby counties receive new stores, the force of agglomeration and therefore the spillover effect increases (e.g.
-\citet{Basker_2005}).
-\end{example}
-
-\begin{example}
-    Last, $h_i(\vec{D})$ is a spatial decay function where exposure decreases with distance.
-In this case, spillover intensity is the sum across all treated observations' decay terms, i.e.
-\begin{equation}\label{eq:h_decay}
-        h_i(\vec{D}) = \sum_{j \neq i} D_j e^{-\alpha d(i,j)}.
-    \end{equation} 
-    This exposure mapping allows for the intensity of spillovers to depend on the distance to treatment and also is additive in the number of nearby units treated.\footnote{However, this specification assumes that all units are affected by all other units.
-This creates problems with inference because it implies a potential correlation between all units' error terms.
-For this reason, this function often is summed over only the $k$-nearest neighbors or units within $\bar{d}$ miles.} The speed that spillover effects decay over distance depends on the parameter $\alpha$ that can be calibrated by the researcher or estimated using a non-linear least-squares routine.
-In the literature on R\&D investment, for example, \citet{Keller_2002} uses a modified version of this exposure mapping where $D_j$ is country $j$'s R\&D expenditure.
-This specification features exponential decay over distance which captures the theoretical insight that research spending in closer locations has a larger effect than further away spending.
-\end{example}
-
-Often, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers in a way similar to the above examples.
-Estimation in this case will rely on the functional form assumptions made by researchers.
+In the world of no spillovers, that is $h_i(\vec{D}) = \vec{0}$ for all individuals, potential outcomes would return to only depending on own-treatment status.\footnote{For example, $h_i(\vec{D})$ could be an indicator for being within a certain distance of a treated unit.
+Additionally, exposure could be defined as a spatial decay function where exposure is declining in the distance of treated units.}
+
+Often, researchers will try to parameterize potential outcomes by reasoning through the nature of the spillovers and subsequent estimation will rely on the functional form assumptions made by researchers.
 This paper will take an alternative approach to identification and estimation which will allow for estimation of treatment effects without requiring direct knowledge of the functional form of the exposure mapping/potential outcomes.
@@
 \end{assumption}
-This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 would not depend on treatment status.
+This assumption states that in the absence of treatment and with zero exposure (not just the absence of individual $i$'s treatment), the change in potential outcomes from period 0 to 1 do not depend on treatment status.
 This generalizes to the classic parallel counterfactual trends when SUTVA is satisfied because then every unit has zero exposure.
@@
 
-% Work by \citet{Savje_Aronow_Hudgens_2021} suggests averaging the switching effect over exposure levels,
-%\[ 
-%    \tau_{\text{avg,switch}} \equiv \expec{\tau_{i, switch}(h_i(\vec{D})) \vert D_i = 1}.
-%\] 
-%This estimand averages the switching effect over all treated units and hence average over the distribution of exposure.
-Any given unit $i$ trying to understand the effect of switching on a policy can't use this parameter as it averages over exposures different than theirs.
-More, this parameter can not be identified without further assumptions as the distribution of exposure mappings is not necessarily the same for control units as treated units.\footnote{\citet{Savje_Aronow_Hudgens_2021} discuss conditions on the distribution of exposure mappings that can lead to asymptotic identification of the average switching effect.
-However it relies on design-based assumptions that do not apply here.}
-
-There is a particular switching effect at zero exposure that I call the `direct effect' of treatment, 
-\[
-    \tau_{\text{direct}} \equiv \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, h_i(\vec{D}) = \vec{0}} = \tau_{\text{switch}}(\vec{0}),
-\] 
-which measures the average effect of being treated \emph{among unexposed treated units}.
-Specifying this particular switching effect will prove useful when discussing identification as it requires fewer assumptions than switching effects at other exposure levels.
-As discussed above, this is not necessarily a policy-relevant parameter for every unit if the switching effect has different magnitudes at different levels of exposure.
-
-The second policy-relevant parameter is the `total effect of treatment': 
+The second policy-relevant parameter is the `total effect of treatment on the treated': 
 \[
@@
 This can be thought of as going from the world with a \emph{complete} absence of treatment, $\vec{0}$ to the current treatment vector $\vec{D}$.
-This treatment effect is helpful for `national' policymakers to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.
+This treatment effect is helpful for `national' policymakers to evaluate what \emph{were} the effects of the entire vector of \emph{enacted policies}.\footnote{\citet{yu2022estimating} label the `total effect' to be $\expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0})}$ where the average is over all units including control units.
+Identification of this effect relies on assumptions about experimental-design so this paper does not pursuit identification of this effect.}
 
@@
     &\overbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D}))}^{\text{Switching Effect}} = \\
-    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect}} \ - \ \underbrace{(Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0,0))}_{\text{Spillover on Control}}
+    &\quad\quad \underbrace{\underbrace{Y_{i1}(1, 0) - Y_{i1}(0,0)}_{\text{Direct Effect}} \ + \ \underbrace{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, 0)}_{\text{Spillover on Treated}}}_{\text{Total Effect on Treated}} \ - \ \underbrace{(Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0,0))}_{\text{Spillover on Control}}
 \end{align*}
 
-From this identity, we see that whenever $\tau_{i,spill}(D_i, h(\vec{D}_i))$ does not depend on treatment status $D_i$, then we have that the switching effect is constant and equal to the direct effect.
-In this situation, the simpler identification assumptions behind the direct effect will identify the switching effect at all exposure levels.
-For example, if treatment is a factory opening and the spillover effect on employment is due to increased spending on services, then it could be reasonable to assume the effect does not depend on treatment status and hence the switching effect is constant and equal to the direct effect.
-
-However, the spillover effects can sometimes differ depending on treatment status.
-Continuing the above example, perhaps control units could experience negative employment shocks from a nearby country opening a factory if workers relocate/commute to the treated areas resulting in a negative spillover effect on control units.
-Other treated units could, for instance, experience positive spillover effects due to agglomeration economies.
-When it is the case that spillover effects depend on treatment status, the switching effect can be thought of as two separate effects.
-First, the unit is affected by changing its treatment status as summarized by the direct effect.
+From this identify, we see that the switching effect can be decomposed into two parts.
+First, the unit is affected by changing its treatment status as summarized by the `direct effect'.
 Second, the unit changes from experiencing spillover effects as a control unit to experiencing spillover effects as a treated unit.
+Additionally, the above work shows that the switching effect is closely related to the total effect.
+The primary difference is that the total effect is concerned with post-hoc analysis so that the reference potential outcome is $Y_{i1}(0,0)$.
+On the other hand, the switching effect has a reference of $Y_{i1}(0, h_i(\vec{D}))$ so that when entering treatment, the spillover on control units is lost.
 
@@
     \begin{align}
-        &\underbrace{\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0 }}_{\text{Difference-in-Differences}} \label{eq:did}\\ 
-        &\quad\quad= \tau_{\text{direct}} + \tau_{\text{spill}}(1) - \tau_{\text{spill}}(0) \\ 
+        &\underbrace{\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0 }}_{\text{Difference-in-Differences}} \label{eq:did} \\ 
         &\quad\quad= \tau_{\text{total}} - \tau_{\text{spill}}(0)
@@
 
-The proof is given in Appendix \ref{sec:proofs}, but the intuition behind the additional terms is as follows.
-First, the change in outcomes among treated units combines the direct effect of treatment with the spillover effects caused by nearby treated units.
-Therefore the first difference adds the average spillover effect onto the treated units, $\tau_{\text{spill}}(1)$.
-Second, the change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units.
+The proof is given in Appendix \ref{sec:proofs}, but the intuition is as follows.
+The change in outcomes among control units combines the parallel counterfactual trend with the average spillover effect onto control units.
 Since $\hat{\tau}$ is found by subtracting the change in outcomes among the control units, we subtract the average spillover effect onto the control, $\tau_{\text{spill}}(0)$.
@@
 \end{equation}
-The estimator $\hat{\tau}$, which is well understood to be the sample analog of (\ref{eq:did}), is, therefore, a biased estimate for $\tau_{\text{direct}}$ and $\tau_{\text{total}}$ in the presence of spillovers.
+The estimator $\hat{\tau}$, which is well understood to be the sample analog of (\ref{eq:did}), is, therefore, a biased estimate for $\tau_{\text{total}}$ in the presence of spillovers.
 In particular, if a researcher estimates a difference-in-differences model and reports $\hat{\tau}$ as an estimate of the total effect, their estimate would be biased in the presence of spillover effects on control units.
@@
 Writing it in this way highlights the two problems in estimating the second term.
-First, this requires knowledge of the unobserved exposure mapping to be correctly specified to identify control units with $h_i(\vec{D}) = h$.
+First, this requires knowledge of the unobserved exposure mapping to be correctly specified to identify control units with $h_i(\vec{D}) = \vec{h}$.
 More, this estimand requires a more demanding parallel trends assumption.\footnote{This problem is similar to those highlighted by \citet{Callaway_Goodman-Bacon_SantAnna_2021} for difference-in-differences with continuous treatment.}
@@
 This assumption requires parallel trends among treated and control units at exposure $\vec{h}$.
-This assumption is implied by \nameref{assumption:parallel} and an additional assumption that spillover effects are equal between control and treated units that experience exposure $\vec{h}$.
-Under this assumption, the switching effect can be identified.
+Under this assumption, the switching effect can be identified by a difference-in-differences estimand calculated using only units with an exposure of $\vec{h}$.
 
@@
 
-\subsubsection{Direct and Total Effects}
-
-To identify the direct and total effects, additional assumptions on the nature of spillover effects are needed.
+\subsubsection{Total Effect}
+
+To identify the total effect, additional assumptions on the nature of spillover effects are needed.
 In particular, I will formalize the idea that spillovers are `local' in that units are only affected by treatment if they are near treatment.
@@
 unit $i$ is within $\bar{d}$ miles of the closest treated unit.
-
-The intuition behind identifying the direct effect separately from the spillover effects requires that we use control units experiencing no spillover effects to identify the counterfactual trend and use treated units experiencing no spillover effects to identify the direct effect.
-Since we are leveraging subgroups of treated and control units, we need a parallel trends assumption for each subgroup:
-
-\begin{assumption}[Direct/Total Effect Parallel Trends]\label{assumption:parallel-mod}
+Similar to above, let $S_{it} = S_i * \one{t = 1}$ be the treatment indicator.
+
+The intuition behind identifying the total effect requires that we use control units experiencing no spillover effects to identify the counterfactual trend.
+Since we are leveraging subgroups of control units, we need a parallel trends assumption for each subgroup:
+
+\begin{assumption}[Total Effect Parallel Trends]\label{assumption:parallel-mod}
     Counterfactual trends do not depend on $D_i$ and $S_i$:
     \[
-        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i, S_i} = 
-        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0})}
+        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1}= 
+        \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0, S_i = 0}
     \]
@@
 units with $S_i = 0$).
-In this case, if parallel trends only hold locally, then focusing on further away units can fix the spillover bias but increase bias from non-parallel trends.
-
-Note that for identification of the total effect, you only need that the counterfactual trend among \emph{all} treated units is the same as the counterfactual trend among control units with $S_i = 0$ which is implied by \nameref{assumption:parallel-mod}.
-Identification of the direct effect will be average the individual treatment effects \emph{only} for treated units with $S_i = 0$.
-So identification of the average treatment effect among \emph{all} treated units requires a subtle assumption to ensure treatment effect homogeneity.
-
-\begin{assumption}[Direct Effect Does Not Depend on $S_i$]\label{assumption:homogenous-direct}
-    For $s \in \{0, 1\}$,
-    \[
-        \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, S_i = s} = 
-        \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1}
-    \]d
-\end{assumption}
-
-With these assumptions, we have the following identification result for the direct and total effects:
-
-\begin{proposition}[Identification of Direct and Total Effects]\label{thm:remove_bias}
+In this case, if parallel trends only hold locally, then focusing on further away units can fix the spillover bias but worsten bias from non-parallel trends.
+With this assumption, we have the following identification result for the total effects:
+
+\begin{proposition}[Identification of Total Effects]\label{thm:remove_bias}
     If assumption (\ref{assumption:random}), (\ref{assumption:no-anticipation}),
@@
     \begin{equation}\label{eq:id_total}
-        \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0} = \tau_{\text{total}}
-    \end{equation}
-    and (ii) 
-    \begin{align}\begin{split}\label{eq:id_direct}
-        &\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1, S_{i} = 0 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0 } \\
-        &\quad\quad= \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \ \vert \ D_i = 1, S_i = 0}\\
-        &\quad\quad= \tau_{\text{direct}},
-    \end{split}\end{align}
-    where the last equality holds only under assumption \nameref{assumption:homogenous-direct}.
+        \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0} = \tau_{\text{total}}.
+    \end{equation}
 \end{proposition}
@@
 The proof is given in Appendix \ref{sec:proofs}, but the intuition is simple.
-Conditioning on $S_i = 0$ will use only observations with $h_i(\vec{D}) = 0$ which gives rise to the identification of the direct and total effect.
+Conditioning on $S_i = 0$ will use only observations with $h_i(\vec{D}) = 0$ which gives rise to the identification of the total effect.
 This proposition shows that a researcher does not need to know how the spillovers occur over space to have an unbiased estimate for treatment effects.
-All that is required to identify the direct or total effects is being able to classify which units are considered `close' to treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
+All that is required to identify the total effect is being able to classify which units are considered `close' to treatment.\footnote{In contexts with different measures of `distance', note that this result only requires an indicator that captures all affected units.
 For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
@@
 % ------------------------------------------------------------------------------
-\subsection{Estimation of Direct and Total Effects}
-% ------------------------------------------------------------------------------
-
-To estimate the direct effect and the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
-However, it will prove advantageous to modify the two-way fixed-effects model to estimate the direct or the total effect because it will allow the estimation of spillover effects as well.
-To estimate the total effect, the modified model is given by:
-\begin{equation}\label{eq:twfe_total}    
-    y_{it} = \tau D_{it} + \gamma_{0} (1-D_{it}) S_{i} + \mu_i + \lambda_t + \epsilon_{it}.
-\end{equation}
-
-To estimate the direct effect, the modified model is given by:
-\begin{equation}\label{eq:twfe_direct}    
-    y_{it} = \tau D_{it} + \gamma_0 (1-D_{it}) S_{i} + \gamma_1 D_{it} S_{i} +  \mu_i + \lambda_t + \epsilon_{it}.
-\end{equation}
-From standard regression analysis the estimates of $\hat{\tau}$ from equations (\ref{eq:twfe_direct}) and (\ref{eq:twfe_total}) are sample analogues of (\ref{eq:id_direct}) and (\ref{eq:id_total}).
+\subsection{Estimation of Total Effect}
+% ------------------------------------------------------------------------------
+
+To estimate the total effect, we could replace the terms in proposition \ref{thm:remove_bias} with their sample analogs.
+However, it will prove advantageous to modify the two-way fixed-effects model to estimate treatment effects because we will extend it to estimate spillover effects in the following subsection.
+To estimate the total effect, one can run the regression specification (\ref{eq:twfe}) on the subsample of units with $D_i = 1$ or $S_i = 0$.
+From standard regression analysis the estimates of $\hat{\tau}$ are sample analogues of (\ref{eq:id_total}).
 
@@
 First, errors should be clustered by unit $i$ to allow for correlation across periods.
-Second, since our model is predicated on the fact that nearby places affect one another, we should account for such spatial correlation by allowing for spatial correlations following \citet{Conley_1999}.
+Second, since assumption \ref{assumption:local} is predicated on the fact that nearby places affect one another, we should account for such spatial correlation by allowing for spatial correlations following \citet{Conley_1999}.
 More recent work by \citet{Ferman_2020} show that for large-n asymptotics to be used, the structure of spatial correlation must be limited in that errors are assumed to be uncorrelated after a certain cutoff distance.
@@
 
-A natural question is why wouldn't researchers make the distance large to guarantee they have an unbiased estimate of $\tau_{\text{direct}}$ or $\tau_{\text{total}}$?
-Equation (\ref{eq:id_total}) and (\ref{eq:id_direct}) should make this problem clear.
+A natural question is why wouldn't researchers make the distance large to guarantee they have an unbiased estimate of $\tau_{\text{total}}$?
+Equation (\ref{eq:id_total}) should make this problem clear.
 Since these estimates rely on averages among units with $S_i = 0$, as $\bar{d}$ increases, the number of units with $S_i = 0$ decreases which yields more variable estimates.
 On the other hand, having units that experience spillovers not included in the $S_i$ indicator will leave some bias in the estimate.\footnote{Although, spillover effects typically will grow weaker over distance and if distant units are mistakenly treated as if they have zero exposure, bias should be small.} Therefore there is a bias-variance trade-off in extending the extent of $S_i$ that should be balanced by researchers guided by their particular economic context.
+Additionally, each value of $\bar{d}$ corresponds to a different effective control group and hence a different parallel trends assumption.
 In separate work, \citet{Butts_2021} discusses data-driven methods to determine how far $S_i$ should be under a more strict parallel trends assumption.
@@
 
-The estimates of $\gamma_D$ in the modified TWFE models (\ref{eq:twfe_total}) and (\ref{eq:twfe_direct}) do not estimate the corresponding average spillover effects $\tau_{\text{spill}}(D)$ for $D = 0,1$.
-This is because $\hat{\gamma}_D$ average spillover effects across only units with $S_i = 1$:
-\[ 
-    \expec{\hat{\gamma}_0} = \condexpec{\tau_{i, spill}(0)}{ S_i = 1, D_i = 0}, \text{ and}
-\]
-\[ 
-    \expec{\hat{\gamma}_1} = \condexpec{\tau_{i, spill}(1)}{ S_i = 1, D_i = 1}.
-\]
-These estimates average spillover effects for all units with $S_i = 1$.
+This subsection turns to estimating averages of spillover effects themselves. To do so, we must extend the \nameref{assumption:parallel-mod} to allow include control units with $S_i = 1$. 
+\begin{assumption}[Spillover Effect Parallel Trends]\label{assumption:parallel-spill}
+  For $s = 0, 1$, we have: 
+  \[
+      \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 1} = 
+      \expec{Y_{i1}(0, \vec{0}) - Y_{i0}(0, \vec{0}) \ \vert \ D_i = 0, S_i = s}
+  \]
+\end{assumption}
+
+In this case, both treatment effects and spillover effects can be estimated with the following regression specification using the full sample:
+\begin{equation}\label{eq:twfe_spill}
+  Y_{it} = \tau D_{it} + \gamma_0 (1 - D_{it}) S_i + \mu_i + \lambda_t + \epsilon_{it}.
+\end{equation}
+Our total effect estimate, $\hat{\tau}$, from (\ref{eq:twfe_spill}) is consistent under \nameref{assumption:parallel-spill}.
+The spillover effect estimate $\hat{\gamma}_0$ in (\ref{eq:twfe_spill}) does not estimate the corresponding average spillover effects $\tau_{\text{spill}}(0)$.
+This is because $\hat{\gamma}_0$ average spillover effects across only untreated units with $S_i = 1$:
+\[ 
+    \expec{\hat{\gamma}_0} = \condexpec{\tau_{i, spill}(0)}{ S_i = 1, D_i = 0}.
+\]
 Since some units with $S_i = 1$ do not have positive exposure, this is not the average spillover effect for units with non-zero exposure either.
@@
 It is possible to more accurately estimate spillover effects by using a set of concentric ring indicators (e.g 0-20 miles, 20-40 miles, and 40-60 miles from the nearest treated unit) instead of a single large ring indicator to more flexibly estimate the spillover effects.
-For example, for the total effect, equation (\ref{eq:twfe_total}) can be modified as
-\begin{equation}\label{eq:twfe_total_rings}    
-    y_{it} = \tau D_{it} + \sum_{i=1}^n (1-D_{it}) \text{Ring}_{i} + \mu_i + \lambda_t + \epsilon_{it},
-\end{equation}
-where $\text{Ring}_i$ is a given ring.
-Similarly, equation (\ref{eq:twfe_direct}) can be modified to include multiple rings.
-Since the set of rings is collinear with a single large ring, the direct and total effects estimate will continue to be identified.
-The estimates for each ring will represent the average of $\tau_{i,spill}$ for all observations within a given distance ring.
+Equation (\ref{eq:twfe_spill}) can be modified as
+\begin{equation}\label{eq:twfe_rings}    
+    y_{it} = \tau D_{it} + \sum_{j=1}^n (1-D_{it}) \text{Ring}_{ij} + \mu_i + \lambda_t + \epsilon_{it},
+\end{equation}
+where $\text{Ring}_{ij}$ is an indicator for unit $i$ being in ring $j$.
+However, this estimator relies on a yet more stringent parallel trends assumption that the untreated units in each ring are on the same trend as the untreated units with $S_i = 0$.\footnote{\citet{Butts_2021} takes this to the logical extreme where more and more rings are added.
+The parallel trends assumption becomes that untreated units are on the same trend at every distance from treatment.} Since the set of rings is collinear with a single large ring, the total effects estimate will continue to be identified.
+Each ring will estimate the average of $\tau_{i,spill}(0)$ for all observations within a given distance ring.
 Having estimates of average spillover effects at different distances allows a researcher to better understand the nature of the spillovers.
@@
 
-    {\footnotesize \textit{Notes:} The figure compares estimates of equation (\ref{eq:twfe_total}) with $S_i$ a ring of $(0, 60]$ miles from the nearest treated unit and of equation (\ref{eq:twfe_total_rings}) with rings for $(0,15], (15,30], (30,45], (45, 60]$ miles for a simulated set of data.}
+    {\footnotesize \textit{Notes:} The figure compares estimates of equation (\ref{eq:twfe_rings}) with $S_i$ a ring of $(0, 60]$ miles from the nearest treated unit and of equation (\ref{eq:twfe_rings}) with rings for $(0,15], (15,30], (30,45], (45, 60]$ miles for a simulated set of data.}
 \end{figure}
 
-Panel (a) uses a single indicator for being between 0 and 60 miles from treatment and the difference between the bar and the estimated counterfactual trend is the estimated spillover effect which in this case is about 0.6.
+The `One Ring' estimation method uses a single indicator for being between 0 and 60 miles from treatment.
+The difference between the bar and the estimated counterfactual trend is the estimated spillover effect which in this case is about 0.6.
 This number masks that units within the first 15 miles have a treatment effect of 1 or larger and units between 40 and 60 miles have 0 spillover effects.
-Figure (b) on the other hand uses 4 indicators for every 15-mile interval (0-15, 15-30, 30-45, and 45-60 miles).
+The `Multiple Rings' estimation method uses 4 indicators for every 15-mile interval (0-15, 15-30, 30-45, and 45-60 miles).
 This improves the estimate of a single ring in two ways.
@@
 Furthermore, the ring that is included past the true maximum distance where spillover effects occur (45-60 miles) has a point estimate near zero.
+Note that this example works well because counterfactual trends are assumed to be constant across distance.
+If this weren't true, adding rings would require stronger and stronger parallel trends assumptions.
+
 The rings method is a semi-parametric estimator in the sense that as the number of rings increase and their width shrinks, the estimates would trace out the spillover effect function (subject to $\bar{d}$ satisfying assumption (\ref{assumption:local})).
@@
 One potential solution is to count the number of treated units within each ring instead of creating indicators for the nearest treated unit.
-This additive version of rings however no longer removes all bias from the direct effect of treatment unless the exposure mapping is correctly specified.
-Therefore, if spillover effects are expected to be additive in nature, separate estimation of the direct effect and spillover effects would be the preferred method.
+This additive version of rings however no longer removes all bias from the treatment effect estimate unless the exposure mapping is correctly specified.
+Therefore, if spillover effects are expected to be additive in nature, separate estimation of the total effect and spillover effects would be the preferred method.
 
@@
 The counties used in the sample are presented in Figure \ref{fig:tva_sample}.
-\citet{Kline_Moretti_2014} estimate (\ref{eq:tva}) to identify the `local effect' of the TVA -- what I am calling the `direct effect'.
+\citet{Kline_Moretti_2014} estimate (\ref{eq:tva}) to identify the `local effect' of the TVA -- what I am calling the `total effect on the treated'.
 However, their point estimates compare, in part, changes in outcomes in TVA counties with changes in outcomes for neighboring counties that likely were impacted by the large-scale program.
@@
 \begin{equation}\label{eq:tva_spillover}
-    y_{i, t} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{d \in \text{Dist}} \text{Between}(d)\delta_d + X_{i, 1940} \beta + (\varepsilon_{i, t} - \varepsilon_{i, 1940}),
-\end{equation} 
-where $\text{Dist} = \{(0, 50], (50, 100], (100, 150], (150, 200]\}$ measured in miles and define $\text{Between}(d)$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority and $t \in \{1960, 2000\}$.
+    y_{i, t} - y_{i, 1940} = \alpha + \text{TVA}_i \tau + \sum_{j \in \text{Dist}} \text{Ring}_{ij} \delta_j + X_{i, 1940} \beta + (\varepsilon_{i, t} - \varepsilon_{i, 1940}),
+\end{equation} 
+where $\text{Dist} = \{(0, 50], (50, 100], (100, 150], (150, 200]\}$ measured in miles and define $\text{Ring}_{ij}$ as an indicator for being within the interval $d \in \text{Dist}$ away from the Authority and $t \in \{1960, 2000\}$.
 Figure \ref{fig:tva_sample} displays the four spillover variables by filling in each distance bin in a different color.
-The coefficients $\delta_d$ estimate the average spillover effect onto control units for each of these distance bins.
+The coefficients $\delta_j$ estimate the average spillover effect onto control units for each of these distance bins.
 From proposition \ref{thm:remove_bias}, $\hat{\tau}$ will be an unbiased estimate for the `total' effect so long as spillovers do not occur past 200 miles from the TVA.
@@
 Each row contains the results for a different outcome variable (measured in logs).
-Columns (1)-(5) contain point estimates for $\tau$ and $\delta_d$'s in different specifications.
+Columns (1)-(5) contain point estimates for $\tau$ and $\delta_j$'s in different specifications.
 The point estimates can be interpreted as decadal growth rates in outcomes.
@@
 
-Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and columns (3)-(6) contain point estimates of the spillover effects $\delta_d$.
+Turning to the specification that includes spillovers, equation (\ref{eq:tva_spillover}), column (2) contains a point estimate for $\tau$ and columns (3)-(6) contain point estimates of the spillover effects $\delta_j$.
 For agricultural employment, the point estimates show there was a decline in agriculture employment in control units near the Authority.
@@
 
-These results show that including spillovers in the estimation of direct treatment effects is potentially important and can lead to \emph{significant} differences in treatment effect estimates.
+These results show that including spillovers in the estimation of treatment effects is potentially important and can lead to \emph{significant} differences in treatment effect estimates.
 Analysis of place-based policies that do not account for the fact that treatment effects can spill beyond the borders of treated areas can potentially be biased.
@@
 % ------------------------------------------------------------------------------
-\section{Estimating Event Study with Spillovers}
+\section{Estimating Event Study Specifications with Spillovers}
 \label{sec:event_study}
@@
 Now, I turn to the common setting where treatment turns on at different times for different units, often called staggered adoption.
-The intuition from how spillovers cause biases in estimates of the total/direct effect of treatment extends into the staggered adoption setting.
+The intuition from how spillovers cause biases in estimates of the total effect of treatment on the treated extends into the staggered adoption setting.
 In this setting, the literature has shown that two-way fixed-effect estimates can be viewed as a weighted sum of $2 \times 2$ difference-in-differences estimates.\footnote{Various forms for these weights are described in \citet{Goodman-Bacon_2018}, \citet{Sun_Abraham_2020}, and \citet{deChaisemartin_DHaultfoeuille_2019}.
-I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias term(s) from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds.
+I do not recharacterize the weights in this article and guide interested readers to the source articles themselves.} Therefore the bias terms will be an identically weighted sum of the bias term(s) from the $2 \times 2$ estimates, assuming that the parallel counterfactual trends assumption (\ref{assumption:parallel}) holds for all groups.
 However, since weights on some of the $2 \times 2$ estimates can be negative, the sign of the spillover effects does not determine the sign of the weighted average of the spillover effects.
@@
 
-To estimate treatment and spillover effects in the presence of spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} by incorporating spillovers directly into estimation similar to equations (\ref{eq:id_total}) and (\ref{eq:id_direct}).
-I assume I observe an independent and identically distributed panel for units $i$ and periods $t$.
+To estimate treatment and spillover effects in the presence of spillovers and staggered treatment timing, I will propose an estimation strategy that follows the `imputation-based' approach proposed in concurrent work by \citet{Gardner_2021} and \citet{Borusyak_Jaravel_Spiess_2021} by incorporating spillovers directly into estimation.\footnote{Our identification results in section \ref{sec:po_framework} lend themselves to similar identification results as in \citet{Callaway_SantAnna_2020}.
+One advantage of this is that covariates are flexibly included to allow for parallel-trends to hold conditionally on a set of covariates.} I assume a sample of independent and identically distributed panel for units $i$ and periods $t$ again taking the distribution of treatment and exposure treated as fixed.
 The imputation-based method relies on a model-based assumption for untreated and unexposed potential outcomes to formalize parallel trends:
@@
     \end{equation}
-    where $\expec{\varepsilon_{it}} = 0$, $\mu_i$ and $\lambda_t$ are non-stochastic unit and time fixed-effects.
+    where $\expec{\varepsilon_{it}} = 0$.
 \end{assumption}
 This formalizes parallel trend by imposing that there is a common time-trend in the absence of treatment, $\lambda_t$.
-Note that this does not impose any structure on the effects of treatment and exposure $(D_{it}, h_i(\vec{D}))$.
+This is a particularly strong form of parallel trends in that it imposes units at every distance from treatment are on the same parallel trend $\lambda_t$ (see the discussion in section 2 of \citet{Borusyak_Jaravel_Spiess_2021}).
+Alternative parallel trends assumptions similar to assumption \ref{assumption:parallel-spill} can be used that assume parallel trends for all treatment timing-groups (units that start experiencing treatment in the same period) and spillover timing-groups (units that start having $S_{it} = 1$ in the same period) be equal to the never-affected control group.
+
+Note that assumption \ref{assumption:parallel_staggered} does not impose any structure on the effects of treatment and exposure $(D_{it}, h_i(\vec{D}_t))$ where now the exposure mapping is a function of the current period's treatment vector $\vec{D}_t \equiv \{D_{1t}, \dots, D_{nt} \}$.
 I also assume that units do not have any anticipatory effects before treatment starts:
 \begin{assumption}[No Anticipation (Staggered)]\label{assumption:no-anticipation_staggered}
-    For all observations with $D_{it} = 0$ and $h_i(\vec{D}) = 0$, $Y_{it}(D, \vec{h}) = Y_{it}(0,0)$ for all values of $D$ and $\vec{h}$.
+    For all observations with $D_{it} = 0$ and $h_i(\vec{D}_t) = 0$, $Y_{it}(D, \vec{h}) = Y_{it}(0,0)$ for all values of $D$ and $\vec{h}$.
 \end{assumption}
@@
 With a model for $Y_{it}(0, \vec{0})$, treatment effects for individual $i$ and time $t$ under treatment status $D_{it}$ and exposure $h_i(\vec{D})$ are given by $\tau_{it}(D_{it}, h_i(\vec{D})) = Y_{it}(D_{it}, h_i(\vec{D})) - Y_{it}(0, \vec{0})$.
-Then, the total effect and the direct effect are formed similar to above:
-\[
-    \tau_{\text{total}} \equiv \expec{ \tau_{it}(1, h_i(\vec{D})) \ \vert \ D_{it} = 1} \text{ and }
-    \tau_{\text{direct}} \equiv \expec{ \tau_{it}(1, 0) \ \vert \ D_{it} = 1, h_i(\vec{D}) = \vec{0}}.
+Then, the total effect is formed similar to above:
+\[
+    \tau_{\text{total}} \equiv \expec{ \tau_{it}(1, h_i(\vec{D}_t)) \ \vert \ D_{it} = 1}
 \]
@@
 Let $K_{it}$ denote the number of years since treatment turns on (-1 for the year prior, 0 for the initial year, and so on).
-Then we can define dummy variables $D_{it}^k \equiv D_{it} \one_{K_{it} = k}$ and estimate average total effects for each relative period:
-\[
-    \tau_{\text{total}}^k \equiv \expec{ \tau_{it}(1, h_i(\vec{D})) \ \vert \ D_{it}^k = 1},
-\]
-and similarly for the direct effect.
-
-Estimation of $\tau_{it}$ is the difference between the observed $Y_{it}$ and the unobserved outcome $Y_{it}(0, \vec{0})$ which we will estimate using observations with $D_{it} = 0$ and $h(\vec{D}, 0) = \vec{0}$.
+Then we can define dummy variables $D_{it}^k \equiv D_{i} \one_{K_{it} = k}$ and estimate average total effects for each relative period:
+\[
+    \tau_{\text{total}}^k \equiv \expec{ \tau_{it}(1, h_i(\vec{D})) \ \vert \ D_{it}^k = 1}.
+\]
+
+Our identification argument follows from noting that under \nameref{assumption:parallel_staggered},
+$$
+  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ \Omega} = \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ \Omega},
+$$
+where $\Omega$ is a set of observations $(i, t)$.
+Estimation of $\tau_{it}$ is the difference between the observed $Y_{it}$ and the unobserved outcome $Y_{it}(0, \vec{0})$.
 Similar to the previous section, under assumption (\ref{assumption:local}) we define $S_{it}$ to be an indicator equal to one if in period $t$, unit $i$ is within $\bar{d}$ distance from the nearest treated unit.
+
 Following the procedure laid out in \citet{Gardner_2021}, I propose a modified version of the two-stage difference-in-differences estimator: 
-
 \begin{enumerate}
@@
 The first stage uses untreated and unexposed outcomes to estimate (\ref{eq:y0_staggered}).
-Then, $\tilde{Y}_{it}$ will serve as an estimate for $\tau_{it}$.
-The second stage estimates averages of $\tau_{it}$ for different groups depending on the parameters of interest.
-This is equivalent to regressing the residual $\tilde{Y}_{it}$ on dummy variable(s).
-Table \ref{tab:second_stage} provides examples of treatment effects of interest and corresponding dummy variables to include.
+Then, averaging $\tilde{Y}_{it}$ in the second state will be unbiased and consistent for corresponding averages of $\tau_{it}$ under \nameref{assumption:parallel_staggered}.
+Table \ref{tab:second_stage} provides examples of treatment effects of interest and corresponding dummy variables to include.\footnote{Recent work by \citet{goldsmith2022contamination} suggests that multiple mutually exclusive treatment variables can create contamination bias.
+This is not a concern in this setting because the above imputation strategy avoids residualizing the treatment variables.}
 
@@
             Total Effect (Event Study) & $D_{it}^k$ dummies \\
-            Direct Effect & $D_{it}(1 - S_{it})$ \\
-            Direct Effect (Event Study) & $D_{it}^k(1 - S_{it})$ dummies \\
             Spillover Effect on Control & $S_{it}(1 - D_{it})$ or $\text{Ring}_{it}(1-D_{it})$ \\
@@
     \end{threeparttable}
-
 \end{table}
@@
 I model this phenomenon in a potential outcomes framework and show why difference-in-differences estimation does not identify any treatment effect of interest.
-I then improve upon ad-hoc estimation strategies by proposing a new estimation strategy that is robust to more forms of spillovers.
+I then improve upon ad-hoc estimation strategies by begining with identification of well-defined treatment effects and then proposing estimation strategies that are robust to more forms of spillovers.
 In particular, I find that specifications with an indicator for being ``close to'' treated units will remove all bias in the treatment effect estimate so long as all units affected by spillovers are contained in the indicator under a modified parallel trends assumption.
@@
     &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
-    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 } - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0}\\
-    &= \expec{Y_{i1}(1, h_i(\vec{D})) + Y_{i1}(1, \vec{0}) - Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0})\mid D_i = 1 } \\
-    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\
-    &= \expec{Y_{i1}(1, \vec{0}) - Y_{i1}(0, \vec{0}) \mid D_i = 1} + \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(1, \vec{0}) \mid D_i = 1} \\
-    &\quad\quad - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 0} \\
-    &\equiv \tau_{\text{direct}} + \tau_{\text{spill}}(1) - \tau_{\text{spill}}(0) = \tau_{\text{total}} - \tau_{\text{spill}}(0) \\
+    &= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, \vec{0}) \mid D_i = 1 } - \expec{Y_{i1}(0, h_i(\vec{D})) - Y_{i1}(0, \vec{0})\mid D_i = 0} \\
+    &\equiv \tau_{\text{total}} - \tau_{\text{spill}}(0), 
 \end{align*}
+where the fourth equality follows from our parallel trends assumption \ref{assumption:parallel} and the final equality follows from the definitions.
 
@@
 
-For part (i):
 \begin{align*}
@@
 \end{align*}
-where the first equality comes from the fact that $S_i = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}), and the last by definition of the total effect.
-
-Similarly, for part (ii):
-\begin{align*}
-    &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1, S_i = 0} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i0}(0,0) - Y_{i1}(0, 0) + Y_{i0}(0,0) \ \mid \ D_i = 1, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i1}(0, 0) \ \mid \ D_i = 1, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, 0) - Y_{i1}(0, 0) \ \mid \ D_i = 1} \\
-    &\quad\quad\equiv \tau_{\text{direct}},
-\end{align*}
-where the first equality comes from the fact that $S_i = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}) and 
-the second to last equality follows from assumption (\ref{assumption:homogenous-direct}).
+where the first equality comes from the fact that $S_i = 0$ implies $h_i(\vec{D}) = 0$, the second equality from parallel trends assumption (\ref{assumption:parallel-mod}), and the last by definition of the total effect.
+
+% ------------------------------------------------------------------------------
+\subsection{Identification of Imputation Estimator}
+% ------------------------------------------------------------------------------
+
+This section will give identification arguments for the total effect and spillover effects. First, note under \nameref{assumption:parallel_staggered}, we have 
+\begin{align}
+  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 1} 
+  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) + \varepsilon_{it} \ | \ D_{it} = 1} \\
+  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 1} \\
+  &= \tau_{total}.
+\end{align}
+In the first stage, we estimate $\mu_i$ and $\lambda_t$ using observations with $D_{it}$ and $S_{it} = 0$.
+Unbiasedness/consistency follows from \nameref{assumption:local} and \nameref{assumption:no-anticipation_staggered} and the arguments of the appendix of \citet{Gardner_2021}.
+
+A similar argument follows for spillover effects. Again, assuming \nameref{assumption:parallel_staggered}, we have 
+\begin{align}
+  \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 0, S_{it} = 1} 
+  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) + \varepsilon_{it} \ | \ D_{it} = 0, S_{it} = 0} \\
+  &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 0, S_{it} = 1}.
+\end{align}
 
@@
 
-% Figure: Direct and Spillover Effects of Community Health Centers
+% Figure: Total and Spillover Effects of Community Health Centers
 \begin{figure}[tb!]
-    \caption{Direct and Spillover Effects of Community Health Centers}
+    \caption{Total and Spillover Effects of Community Health Centers}
     \label{fig:chc_es_spill}
@@
 No spillover effect is estimated to be significantly different from zero which suggests that the effects of community health centers are very local.
-Since there are near zero spillover effects, the direct effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
+Since there are near zero spillover effects, the total effect estimates marked in Figure \ref{fig:chc_es_spill} as diamonds maintain the same shape as the author's original estimates with estimates between 15-30 fewer deaths per 100,000 persons.
 
@@
 
-% ------------------------------------------------------------------------------
-\section{Monte Carlo Simulations}
-% ------------------------------------------------------------------------------
-
-% ------------------------------------------------------------------------------
-\subsection{Bias Under Misspecification of Spillovers}
-% ------------------------------------------------------------------------------
-
-To illustrate the above discussion, I turn to a set of Monte Carlo simulations.
-The first exercise is to consider a set of different data generating processes and see how well estimates of the total effect perform when controlling for spillovers using potentially misspecified exposure mappings.
-In the general form, I generate data with unit and time fixed-effects and an error term that is uncorrelated with $D_{it}$ for many different exposure mappings $h_i(\vec{D})$.
-I generate data for unit $i$ is a US county at time $t \in \{1, \dots, 20\}$ using the following data-generating process:
-\begin{equation}\label{eq:dgp_general}
-    y_{it} = \lambda_t + \mu_i + 2 D_{it} + \beta_{\text{spill, control}} (1-D_{it}) h_i(\vec{D}) + \varepsilon_{it},
-\end{equation}
-where $\lambda_t \sim N(0.2t, 0.1^2)$ and $\mu_i \sim N(6, 2^2)$ respectively and the error term is IID and distributed as $\varepsilon_{it} \sim N(0, 2^2)$.
-For simplicity, I also remove spillovers onto treated units, but the results of which specifications perform best in the simulation are the same.
-to keep the magnitude of bias constant across specifications, I normalize the average spillover magnitude to be equal across specifications.\footnote{This results in a constant bias for TWFE estimates across data-generating processes.} For each true data-generating process, I estimate (\ref{eq:dgp_general}) with the correct spillover and misspecified alternatives $\tilde{h}(\vec{D}, i)$.
-
-The set of spillover specifications included in the data-generating process are `Within $40/80$mi.' which equals 1 if the counties' center of population is within $40/80$ miles to a treated counties center of population.
-This corresponds to different choices of $\bar{D}$ and hence $S_i$ in the text.
-`Within $40/80$mi.
-(Additive)' is the number of treated county's within $40/80$ miles of the control county.
-`Decay' is given by $\max_j D_j e^{-0.02 d(i,j)} * 1(d(i,j) < 80)$ and `Decay (Additive)' is given by $\sum_{j \neq i} D_j \exp^{-0.02 d(i,j)}$.
-
-The last set of spillover specifications is commonly used in the literature as a semi-parametric estimator and are referred to as `Rings'.
-These consist of a set of indicators for falling within distance bins from the nearest treated unit (e.g.
-indicators for being between 0-20, 20-40, 40-60, and 60-80 miles to closest treated unit).
-The last specification is an additive version of `Rings' which is the number of treated units within each distance bin.
-This maintains a lot of the intuitive advantages of the `Rings' specification but parameterizes the spillovers to be additive in the number of nearby treated units.
-The advantage of this, as seen below, is enhanced performance of estimating spillover effects that are additive in nature.
-However, if the true specification is non-additive, then the additive specification no longer will remove all the bias from the direct effect estimate.
-Hence, if the direct effect is of principal concern, then the non-additive rings estimate is preferred.
-
-% Table: Bias from Misspecification of Spillovers
-\begin{table}[!tb]
-    \caption{Bias from Misspecification of Spillovers}
-    \label{tab:misspecification}
-    \renewcommand\arraystretch{1}
-
-    \begin{adjustbox}{width = 1.1\textwidth, center}
-        \begin{threeparttable}
-            \begin{tabular}{@{} l *{6}{d{2.4}} @{}}
-                % Head
-                \toprule
-                & \multicolumn{6}{c}{Data-Generating Process} \\
-                \cmidrule{2-7}
-
-                & \mcl{\textbf{Within 40mi}} & \mcl{\textbf{Within 80mi}} & \mcl{\textbf{Within 40mi.}} & \mcl{\textbf{Within 80mi.}} & \mcl{\textbf{Decay}} & \mcl{\textbf{Decay}} \\
-                Specification & & & \mcl{\textbf{(Additive)}} & \mcl{\textbf{(Additive)}} & & \mcl{\textbf{(Additive)}} \\
-
-                % Body
-                \midrule
-
-                \input{../../tables/misspecification.tex}
-
-                \\ \bottomrule
-            \end{tabular}
-
-            % Notes 
-            \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each cell corresponds to the results from 1000 simulations of the data generating process specified by the column header and estimated by equation (\ref{eq:dgp_general}) with $\tilde{h}(\vec{D},i)$ given by the row label.
-The non-bracketed number represents the mean bias from the simulations and the bracketed number represents the mean square error given by $\sum_{i = 1}^n \frac{(\hat{\tau}_i - \tau_0)^2}{n}$
-            \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-
-The results of the simulations are produced in Table \ref{tab:misspecification}.
-For each entry in the table, the column label corresponds to the true exposure mapping used in the data-generating process and the row label corresponds to the exposure mapping, $\tilde{h}(\vec{D}, i)$, used in estimation.
-The corresponding cell gives the mean bias from estimating equation (\ref{eq:dgp_general}) with the $\tilde{h}(\vec{D}, i)$ given by the row.
-The bracketed number below the mean bias is the mean-squared error of the estimate which is given by $\sum_{i=1}^n \frac{(\hat{\tau}_{i,\text{direct}} - \tau_0)^2}{n}$.
-The mean squared error combines the square of the bias term, the variance of the estimator, and the variance of the error term which does not depend on the equation specification.
-This measure gives a good sense of the trade-off with whether decreasing bias comes at the cost of increasing the variance of the estimator.
-
-The first thing to note is that all specifications remove a large portion of the bias relative to traditional two-way fixed-effect estimates and lower the mean-squared error.
-In particular, correctly specifying the data-generating process removes almost all the bias in the direct effect estimate and greatly lowers the mean-squared error.
-The second result is that both the non-additive `Rings' and the `Within' specification perform best among all the misspecified spillovers in terms of removing bias, so long as they are wide enough to capture all the spillovers (see Proposition \ref{thm:remove_bias}).
-These specifications do so without increasing the variance of the estimator relative to the true specification.
-However, if the indicator is not wide enough as is the case with Within 40mi.
-for the 80mi.
-data-generating process, bias remains in the estimates.
-Therefore, if researchers are primarily interested in identifying the direct effect, then either `Rings' or `Within' specifications with a large cutoff distance are preferred.
-
-% ------------------------------------------------------------------------------
-\subsection{Spillover Effect Estimation}
-% ------------------------------------------------------------------------------
-
-Now, I turn to analyze how the specifications perform at estimating the spillover effects themselves.
-For the next table, I predict the spillover effect for each control unit from the point estimates on $\tilde{h}(\vec{D}, i)$.
-Then as a measure for how well spillovers are estimated, I will calculate one minus the mean squared prediction error normalized by the sum of squared spillovers (for comparison across data-generating processes),
-\begin{equation}\label{eq:mspe}
-    1 - \frac{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h_i(\vec{D}) - \hat{\beta}_{\text{spill, control}} \tilde{h}(\vec{D}, i))^2}{\sum_{i: D_i = 0} (\beta_{\text{spill, control}} h_i(\vec{D}))^2}.
-\end{equation} 
-This will produce a percentage of spillovers that are explained by the specification, so numbers closer to $100\%$ represent better modeling of the spillovers.
-
-% Table: Percent of Spillovers Predicted by Specification
-\begin{table}[!tb]
-    \caption{Percent of Spillovers Predicted by Specification}
-    \label{tab:misspecification_mspe}
-
-    \begin{adjustbox}{width = 1.1\textwidth, center}
-        \begin{threeparttable}
-            \begin{tabular}{@{} l *{6}{d{2.2}} @{}}
-                % Head
-                \toprule
-                & \multicolumn{6}{c}{Data-Generating Process} \\
-                \cmidrule{2-7}
-
-                & \mcl{\textbf{Within 40mi}} & \mcl{\textbf{Within 80mi}} & \mcl{\textbf{Within 40mi.}} & \mcl{\textbf{Within 80mi.}} & \mcl{\textbf{Decay}} & \mcl{\textbf{Decay}} \\
-                Specification & & & \mcl{\textbf{(Additive)}} & \mcl{\textbf{(Additive)}} & & \mcl{\textbf{(Additive)}} \\
-
-                % Body
-                \midrule
-
-                \input{../../tables/misspecification_mspe_percent.tex}
-
-                \\ \bottomrule
-            \end{tabular}
-
-            % Notes 
-            \begin{tablenotes}\footnotesize
-                \item \textit{Notes.} Each cell corresponds to the results from 1000 simulations of the data generating process specified by the column header and estimated by equation (\ref{eq:dgp_general}) with $\tilde{h}(\vec{D},i)$ given by the row label.
-The number corresponds to the mean square prediction error of the spillover effect for each control unit normalized by the total variance of spillover effects, given by Equation \ref{eq:mspe}.
-            \end{tablenotes}
-        \end{threeparttable}
-    \end{adjustbox}
-\end{table}
-
-Results of this exercise are presented in Table \ref{tab:misspecification_mspe}.
-For each specification, correctly specifying the spillovers produces the best estimates for spillovers as expected.
-Among misspecified exposure mapping, a `Rings' specification that is large enough to capture all the spillovers perform better than all other specifications in all non-additive data-generating processes.
-On the other hand, when the spillovers are additive, the predicted spillovers from the non-additive ring specifications do not as accurately measure these spillovers as they did before.\footnote{Although the non-additive Rings do estimate between 70\% and 80\% of the spillover effects while maintaining complete removal of bias.} Non-additive specifcations perform somewhat poorly at estimating spillovers in the additive data-generating processes, `Within (Additive)' and `Decay (Additive)'.
-The `Rings (Additive)' specification successfully predicts spillovers in both additive data-generating processes.
-
 \end{document}

### 2023-02-27 latex/paper/Spillover.tex
Remove "online" appendix reference

@@
 The resulting residuals are then regressed on the treatment and spillover variables to estimate treatment and spillover effects.
-In the online appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.
+In the appendix, I demonstrate the method by revisiting the analysis by \citet{Bailey_Goodman_Bacon_2015} of Community Health Centers which provided low-cost primary care to impoverished areas.
 

### 2023-06-10 latex/paper/Spillover.tex
New draft

@@
 For example, thinking about spillovers between industries, this requires the researcher to correctly identify which industries are affected by spillovers and which are not.}
+
+\begin{remark}
+  To highlight the importance of the modified parallel trends, we will compare the two estimands under the original \nameref{assumption:parallel}.
+The standard difference-in-differences estimate is biased from spillovers on nearby control units:
+  $$
+    \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1 } - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0 } = \tau_{\text{total}} - \tau_{\text{spill}}(0).
+  $$
+  On the other hand, using the $S_i = 0$ control group is biased by (potentially) non-parallel trends:
+  \begin{align*}
+    &\expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \vert \ D_i = 0, S_{i} = 0} \\
+    &\quad\quad= \tau_{\text{total}} + (\expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0, S_i = 0}) 
+  \end{align*}
+  In this sense, there is a practical trade-off between two different sources of bias: spillover bias and the forming of potentially worse counterfactual conrol group.
+\end{remark}
 
@@
     &\expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 1} - \expec{Y_{i1} - Y_{i0} \ \mid \ D_i = 0, S_i = 0} \\
-    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0} \\
+    &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 0, S_i = 0} \\
     &\quad\quad= \expec{Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,0) \ \mid \ D_i = 1} - \expec{Y_{i1}(0, 0) - Y_{i0}(0,0) \ \mid \ D_i = 1} \\
@@
 This section will give identification arguments for the total effect and spillover effects. First, note under \nameref{assumption:parallel_staggered}, we have 
-\begin{align}
+\begin{align*}
   \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 1} 
@@
   &= \tau_{total}.
-\end{align}
+\end{align*}
 In the first stage, we estimate $\mu_i$ and $\lambda_t$ using observations with $D_{it}$ and $S_{it} = 0$.
@@
 A similar argument follows for spillover effects. Again, assuming \nameref{assumption:parallel_staggered}, we have 
-\begin{align}
+\begin{align*}
   \expec{Y_{it}(D_{it}, h_i(\vec{D}_t)) - \mu_i - \lambda_t \ | \ D_{it} = 0, S_{it} = 1} 
@@
   &= \expec{\tau_{it}(D_{it}, h_i(\vec{D}_t)) \ | \ D_{it} = 0, S_{it} = 1}.
-\end{align}
+\end{align*}
 

### 2023-06-10 figure-rings_example.R

@@ -1,6 +1,6 @@
 ## figure-binscatter_example.R -------------------------------------------------
-## Kyle Butts, CU Boulder Economics 
-## 
+## Kyle Butts, CU Boulder Economics
+##
 ## Single indicator vs. multiple rings
 
 library(tidyverse)
@@ -13,187 +13,390 @@ library(kfbmisc)
 set.seed(100)
 
 df <- tibble(id = 1:500) %>%
-	# Generate Treatment and Distance
-	mutate(
-		treat = runif(n()) > 0.8,
-		treat = as.numeric(treat),
-		control = 1 - treat,
-		dist = runif(n(), 0, 100),
-		dist = dist * (1-treat)
-	) %>% 
-	# Make pre-post
-	expand_grid(t = c(0,1)) %>%
-	# Treatment Effects
-	mutate(
-		te = treat * t * 2,
-		spill1 = 1.5 * t * exp(-0.03 * dist) * (1-treat) * (dist <= 40),
-		eps = rnorm(n(), mean = 0, sd = 0.05),
-		y1 = 2*t + te + spill1 + eps
-	)
+  # Generate Treatment and Distance
+  mutate(
+    treat = runif(n()) > 0.8,
+    treat = as.numeric(treat),
+    control = 1 - treat,
+    dist = runif(n(), 0, 90),
+    dist = dist * (1 - treat)
+  ) %>%
+  # Make pre-post
+  expand_grid(t = c(0, 1)) %>%
+  # Treatment Effects
+  mutate(
+    te = treat * t * 2,
+    spill1 = 1.5 * t * exp(-0.03 * dist) * (1 - treat) * (dist <= 40),
+    eps = rnorm(n(), mean = 0, sd = 0.05),
+    y1 = 2 * t + te + spill1 + eps
+  )
 
 
 # Take First Differences
-first_diff <- df %>% 
-	arrange(id, t) %>%
-	group_by(id) %>% 
-	mutate(
-		d_y1 = y1 - lag(y1)
-	) %>% 
-	filter(t == 1)
+first_diff <- df %>%
+  arrange(id, t) %>%
+  group_by(id) %>%
+  mutate(
+    d_y1 = y1 - lag(y1)
+  ) %>%
+  filter(t == 1)
 
-ggplot() + 
-	geom_point(data=first_diff, aes(x=dist, y=d_y1), shape=16, col="lightgrey")
+ggplot() +
+  geom_point(data = first_diff, aes(x = dist, y = d_y1), shape = 16, col = "lightgrey")
 
[…]

### 2023-06-10 latex/slides/Spillover_slides.tex
Updated Slides

@@
 
-        \item Discuss estimation of effects that are \emph{robust} to spillovers
+        \item Discuss estimation of effects in the presence of spillovers
 
@@
 
-    \onslide<1->{
   The canonical difference-in-differences estimate is: 
@@
   }
-    }
 
-    Two problems occur in the presence of spillover effects:
+  \only<1>{Use the control units to estimate what the treated units' trends would have been without treatment}
+  \only<2-3>{
+    \noindent Two problems occur in the presence of spillover effects:
+    \begin{itemize}
+        \item {\bf \color{coral} Spillover onto Control Units:} Nearby ``control'' units fail to estimate counterfactual trends
 
-    \begin{itemize}
-        \onslide<2->{
-            \item {\bf \color{coral} Spillover onto Control Units:} Nearby ``control'' units fail to estimate counterfactual trends
-        }
-
-        \onslide<3->{
-            \vspace{2.5mm}
+        \only<3>{
             \item {\bf \color{kelly} Spillover onto other Treated Units:} Treated units are also affected by nearby units and therefore combine ``direct'' effects with spillover effects
@@
     \end{itemize}
-
+  }
 \end{frame}
-
-% \begin{frame}{Remove Bias}
-%     \only<1>{
-%         \[ y_{it} = \mu_t + \mu_i + \tau D_{it} + \varepsilon_{it} \]
-%     }
-%     \only<2>{
-%         \[ 
-%             y_{it} = \mu_t + \mu_i + \tau D_{it} + {\color{coral} \tau_{\text{spill,control}} S_{it} * (1-D_{it}) } + {\color{kelly} \tau_{\text{spill,treat}} S_{it} * D_{it}} +  + \varepsilon_{it}
-%         \]
-%     }
-
-%     \only<1>{ 
-%         \[ 
-%             \mathbb{E}[\hat{\tau}] = \tau + \text{\color{coral} Spillover on Control} + \text{\color{kelly}Spillover on Treated}
-%         \]
-%     }
-%     \only<2>{
-%         \[ 
-%             \mathbb{E}[\hat{\tau}] = \tau,
-%         \]
-%         so long as $S_{it}$ contains all the units with spillovers.
-%     }
-% \end{frame}
-
-% \begin{frame}
-%     \begin{figure}[tb!]
-%         \caption{Single Ring - Removes spillover effects}
-%         \begin{center}
-%             \resizebox{0.9\textwidth}{!}{
-%                 \includegraphics{../../figures/figure-within_example.pdf}
-%             }
-%         \end{center}
-%     \end{figure}
-% \end{frame}
-
-% \begin{frame}
-%     \begin{figure}[tb!]
-%         \caption{Multiple Rings - Improves estimation of spillover effects}
-%         \begin{center}
-%             \resizebox{0.9\textwidth}{!}{
-%                 \includegraphics{../../figures/figure-rings_example.pdf}
-%                 } 
-%             \end{center}
-%     \end{figure}
-% \end{frame}
-
-% \begin{frame}
-%     \begin{figure}[tb!]
-%         \caption{Community Health Centers}
-%         \begin{center}
-%             \resizebox{0.9\textwidth}{!}{
-%                 \includegraphics{../../figures/figure-chc-es_combined_slides.pdf}
-%                 } 
-%             \end{center}
-%     \end{figure}
-% \end{frame}
 
@@
             \vspace{2.5mm}
-            \item I decompose the difference-in-differences estimator into three parts: Direct Effect of Treatment, Spillover onto Treated Units, Spillover onto Control Units
+            \item I focus on non-parametric identification conditions
 
             \vspace{2.5mm}
-            \item Discuss estimands of interest and classify which are identifiable and which are not
+            \item Discuss estimands of interest and classify identification for each
         \end{itemize}
@@
     \[
-        \textcolor{maroon}{\tau_{\text{switch}}(h)} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})) \mid D_i = 1, h_i(\vec{D}) = h \right]
+        \textcolor{purple}{\tau_{\text{switch}}(h)} \equiv \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i1}(0, h_i(\vec{D})) \mid D_i = 1, h_i(\vec{D}) = h \right]
     \]
@@
     \begin{align*}
-        \textcolor{maroon}{\tau_{\text{switch}}(h)} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]\\ 
+        \textcolor{purple}{\tau_{\text{switch}}(h)} &= \mathbb{E} \left[ Y_{i1}(1, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]\\ 
         &\quad\quad - \textcolor{asher}{\mathbb{E} \left[ Y_{i1}(0, h_i(\vec{D})) - Y_{i0}(0,\vec{0}) \mid D_i = 1, h_i(\vec{D}) = h \right]} 

### 2024-02-02 OZ-analaysis-replicate.R
Clean code to reproducible logbook

@@ -1,134 +1,0 @@
-library(tidyverse)
-library(arrow)
-library(here)
-library(fixest)
-library(broom)
-
-# ---- Load Data ---------------------------------------------------------------
-
-zillow_data <- read_feather(here("data/tracts_data.feather"))
-zillow_data <- zillow_data |> filter(year != 2020)
-zillow_data$tract <- factor(zillow_data$tract)
-zillow_data$treat_x_post <- zillow_data$treatment * zillow_data$post
-
-# ------------------------------------------------------------------------------
-# Difference-in-Differences
-# ------------------------------------------------------------------------------
-
-# ---- Helper Function ---------------------------------------------------------
-
-fit_did_fixest <- function(data, fmla, pretest_fmla, pretest_cols) {
-  model_pretest <- fixest::feols(
-    fml = pretest_fmla,
-    data = data, cluster = ~state_abbr
-  )
-
-  pretest <- wald(model_pretest, keep = pretest_cols)
-
-  model <- fixest::feols(
-    fml = fmla, 
-    data = data, cluster = ~state_abbr
-  )
-
-	return(list(
-    model_pretest = model_pretest,
-    lh_pretest = pretest,
-    model = model
-  ))
-}
-
-# ---- No Covariates -----------------------------------------------------------
-
-zillow_model <- fit_did_fixest(
-  data = zillow_data, 
-  fmla = annual_change ~ treatment_and_post | year + tract,
-  pretest_fmla = annual_change ~  i(treatment, i.year, ref = F, ref2 = 2017) | year + tract,
-  pretest_cols = c("treatmentTRUE:year2014", "treatmentTRUE:year2015", "treatmentTRUE:year2016")
-)
-zillow_model
-
-
-model_results <- tidy(zillow_model$model)
-tau <- zillow_model$model$estimate 
-se <- zillow_model$model$std.error
-tstat <- zillow_model$model$statistics
-pval <- zillow_model$model$p.value
-
-
-# ---- Sparse Covariates -------------------------------------------------------
-
-zillow_model_cov_sp <- fit_did_fixest(
-  data = zillow_data,
-  fmla = annual_change ~ 1 + treatment * post + i(year, log_median_household_income, ref = 2017) + i(year, pct_white, ref = 2017) | year + tract, 
[…]

### 2024-02-02 OZ-analysis-spillovers.R

@@ -1,108 +1,0 @@
-## analysis_spillovers.R -------------------------------------------------------
-## Kyle Butts, CU Boulder Economics 
-## 
-## Opportunity Zone analysis where I run Selected vs. Eligible but Not Selected and have spillovers on adjacent census tracts. See if differences in effect is due to identification strategy.
-
-
-# Tidyverse
-library(tidyverse)
-# Spatial
-library(sf)
-library(units)
-# read_feather
-library(arrow)
-# here() for relative file
-library(here)
-# Estimation
-library(fixest)
-library(broom)
-
-# ---- Find distance to nearest treated ----------------------------------------
-
-geos <- read_sf(here("data/OZ/tracts/all_tracts_with_status.shp"))
-
-geos <- geos |>
-    st_point_on_surface() |>
-    mutate(
-        status = ifelse(is.na(status), "Ineligible", status),
-        intptlat = as.numeric(intptlat),
-        intptlon = as.numeric(intptlon),
-    )
-
-# # Code is inefficient because of memory concerns
-selected <- geos[geos$status == "Selected", ]
-geos$distance_to_nearest <- kfbmisc::st_nearest_distance_rcpp(geos, selected)[,2]
-
-geos <- geos |> 
-    st_as_sf() |> 
-    st_drop_geometry() |>
-    mutate(tract = as.character(geoid)) |> 
-    select(tract, status, distance_to_nearest)
-
-# ---- Combine geos with tract data --------------------------------------------
-
-tracts <- read_feather(here("data/OZ/tracts_data.feather")) 
-
-tracts <- filter(tracts, year != 2020)
-
-tracts <- left_join(tracts, geos, by = "tract")
-
-
-# ------------------------------------------------------------------------------
-# Regression Analysis
-# ------------------------------------------------------------------------------
-
-
-# ---- Selected vs. Eligible ---------------------------------------------------
-
-(eligible <- feols(
[…]

### 2024-02-02 chc-analysis.R

@@ -1,253 +1,0 @@
-## chc-analysis.R --------------------------------------------------------------
-## Kyle Butts, CU Boulder Economics 
-## 
-## Replication of Bailey and Goodman-Bacon (2015) with extension for event study 
-## framework including spillover effect controls.
-
-
-library(tidyverse)
-library(sf)
-library(kfbmisc)
-library(fixest)
-library(did2s)
-
-slides <- TRUE
-h_w_ratio <- 9/16
-
-# ---- Data Cleaning -----------------------------------------------------------
-
-df <- haven::read_dta(here::here("data/chc/aer_data.dta")) |> 
-	# Remove LA, New York, Chicago
-	filter(
-		!(stfips==36 & cofips==61) & !(stfips==6  & cofips==37) & !(stfips==17 & cofips==31)
-	) |>
-	# Create urban dummy
-	group_by(fips) |> 
-	mutate(
-		`_urb` = sum(`_60pcturban` * (year == 1960), na.rm = TRUE)
-	) |> 
-	ungroup() |>
-	# cut every 25% with indicator from 0
-	mutate(
-		Durb = Hmisc::cut2(`_urb`, cuts = c(0, 1, 24.999, 49.999, 74.999, 110))
-	) |> 
-	replace_na(list(chc_year_exp = 0))
-
-ctr_pop <- read_sf(here::here("data/2010_centpop/")) |> 
-	mutate(fips = as.numeric(paste0(STATEFP, COUNTYFP))) |> 
-	select(fips) |> 
-	arrange(fips) |> 
-	st_transform(st_crs(2163))
-
-df <- df |> filter(fips != 12025) |> left_join(ctr_pop, by = "fips") |> st_as_sf()
-
-
-# ---- Create Spillover variables ----------------------------------------------
-
-## helper function: for each year, calculate within
-within_x_treat <- function(dist, year, chc_year_exp, geometry) {
-	y <- min(year)
-	
-	# Last term is because Bailey and Goodman-Bacon define it for chc's before 1974
-	treated <- (chc_year_exp <= y) & (chc_year_exp > 0) & (chc_year_exp <= 1974)
-	
-	
-	dist_mat <- st_distance(geometry, geometry) |>
-		units::set_units("mi") |> units::drop_units()
-	
[…]

### 2024-02-02 code/CHC/analysis.R

@@ -1,0 +1,271 @@
+#' ---
+#' title: 'Bailey and Goodman-Bacon (2015)'
+#' ---
+#' Replication of Bailey and Goodman-Bacon (2015) with extension for event study framework including spillover effect controls.
+
+# %%
+#| message: false
+#| warning: false
+library(tidyverse, warn.conflicts = FALSE)
+library(sf)
+library(kfbmisc)
+library(fixest)
+library(did2s, quietly = TRUE)
+
+slides <- TRUE
+h_w_ratio <- 9 / 16
+
+# Data Cleaning ----------------------------------------------------------------
+# %%
+df <- haven::read_dta(here::here("data/chc/aer_data.dta")) |>
+  # Remove LA, New York, Chicago
+  filter(
+    !(stfips == 36 & cofips == 61) &
+      !(stfips == 6 & cofips == 37) &
+      !(stfips == 17 & cofips == 31)
+  ) |>
+  # Create urban dummy
+  group_by(fips) |>
+  mutate(
+    `_urb` = sum(`_60pcturban` * (year == 1960), na.rm = TRUE)
+  ) |>
+  ungroup() |>
+  # cut every 25% with indicator from 0
+  mutate(
+    Durb = Hmisc::cut2(`_urb`, cuts = c(0, 1, 24.999, 49.999, 74.999, 110))
+  ) |>
+  replace_na(list(chc_year_exp = 0))
+
+ctr_pop <- read_sf(here::here("data/2010_centpop/")) |>
+  mutate(fips = as.numeric(paste0(STATEFP, COUNTYFP))) |>
+  select(fips) |>
+  arrange(fips) |>
+  st_transform(st_crs(2163))
+
+df <- df |>
+  filter(fips != 12025) |>
+  left_join(ctr_pop, by = "fips") |>
+  st_as_sf()
+
+
+# Create Spillover variables ---------------------------------------------------
+# %%
+## helper function: for each year, calculate within
+within_x_treat <- function(dist, year, chc_year_exp, geometry) {
+  y <- min(year)
+
+  # Last term is because Bailey and Goodman-Bacon define it for chc's before 1974
+  treated <- (chc_year_exp <= y) & (chc_year_exp > 0) & (chc_year_exp <= 1974)
+
+
+  dist_mat <- st_distance(geometry, geometry) |>
+    units::set_units("mi") |>
+    units::drop_units()
+
[…]

### 2024-02-02 code/OZ/replication.R

@@ -1,0 +1,127 @@
+#' ---
+#' title: "Replication of Chen, Glaeser, and Wessel (2023)"
+#' ---
+# %%
+#| message: false
+#| warning: false
+library(tidyverse, warn.conflicts = FALSE)
+library(arrow)
+library(here)
+library(fixest)
+library(broom)
+
+# Load Data --------------------------------------------------------------------
+
+zillow_data <- read_feather(here("data/OZ/tracts_data.feather"))
+zillow_data <- zillow_data |> filter(year != 2020)
+zillow_data$tract <- factor(zillow_data$tract)
+zillow_data$treat_x_post <- zillow_data$treatment * zillow_data$post
+
+
+# Classic Difference-in-Differences --------------------------------------------
+# %%
+fit_did_fixest <- function(data, fmla, pretest_fmla, pretest_cols) {
+  model_pretest <- fixest::feols(
+    fml = pretest_fmla,
+    data = data, cluster = ~state_abbr
+  )
+
+  pretest <- wald(model_pretest, keep = pretest_cols)
+
+  model <- fixest::feols(
+    fml = fmla,
+    data = data, cluster = ~state_abbr
+  )
+
+  return(list(
+    model_pretest = model_pretest,
+    lh_pretest = pretest,
+    model = model
+  ))
+}
+
+#' ### No Covariates
+# %%
+zillow_model <- fit_did_fixest(
+  data = zillow_data,
+  fmla = annual_change ~ treatment_and_post | year + tract,
+  pretest_fmla = annual_change ~ 
+    i(treatment, i.year, ref = FALSE, ref2 = 2017) | 
+    year + tract,
+  pretest_cols = c("treatment::TRUE:year::2014", "treatment::TRUE:year::2015", "treatment::TRUE:year::2016")
+)
+zillow_model
+
+model_results <- tidy(zillow_model$model)
+tau <- zillow_model$model$estimate
+se <- zillow_model$model$std.error
+tstat <- zillow_model$model$statistics
+pval <- zillow_model$model$p.value
+
+#' ### Sparse covariates
+# %%
+zillow_model_cov_sp <- fit_did_fixest(
+  data = zillow_data,
+  fmla = annual_change ~ 1 + treatment * post + i(year, log_median_household_income, ref = 2017) + i(year, pct_white, ref = 2017) | year + tract,
[…]

### 2024-02-02 code/OZ/spillovers.R

@@ -1,0 +1,122 @@
+#' ---
+#' title: "Adding spillovers to Opportunity Zone analysis"
+#' ---
+#' Opportunity Zone analysis where I run Selected vs. Eligible but Not Selected and have spillovers on adjacent census tracts. See if differences in effect is due to identification strategy.
+
+# %%
+#| message: false
+#| warning: false
+library(tidyverse, warn.conflicts = FALSE)
+library(sf)
+library(units)
+library(arrow)
+library(here)
+library(fixest)
+library(broom)
+
+#' Find distance to nearest treated:
+# %%
+geos <- read_sf(here("data/OZ/tracts/all_tracts_with_status.shp"))
+geos <- geos |>
+    st_point_on_surface() |>
+    mutate(
+        status = ifelse(is.na(status), "Ineligible", status),
+        intptlat = as.numeric(intptlat),
+        intptlon = as.numeric(intptlon),
+    )
+
+#' Code is inefficient because of memory concerns
+# %%
+selected <- geos[geos$status == "Selected", ]
+geos$distance_to_nearest <- kfbmisc::st_nearest_distance_rcpp(geos, selected)[, 2]
+
+geos <- geos |>
+    st_as_sf() |>
+    st_drop_geometry() |>
+    mutate(tract = as.character(geoid)) |>
+    select(tract, status, distance_to_nearest)
+
+#' Loading the data and merging with spatial data
+# %% 
+tracts <- read_feather(here("data/OZ/tracts_data.feather")) |> 
+    filter(year != 2020) |> 
+    left_join(geos, by = "tract")
+
+
+
+# Regression Analysis ----------------------------------------------------------
+## Selected vs. Eligible -------------------------------------------------------
+# %% 
+(eligible <- feols(
+    annual_change ~ treatment_and_post + 
+        i(year, log_median_household_income, ref = 2017) + 
+        i(year, total_housing, ref = 2017) + 
+        i(year, pct_white, ref = 2017) + 
+        i(year, pct_higher_ed, ref = 2017) + 
+        i(year, pct_rent, ref = 2017) + 
+        i(year, pct_native_hc_covered, ref = 2017) + 
+        i(year, pct_poverty, ref = 2017) + 
+        i(year, pct_supplemental_income, ref = 2017) + 
+        i(year, pct_employed, ref = 2017) | 
+        year + tract,
[…]

### 2024-02-02 code/TVA/analysis.R

@@ -1,0 +1,366 @@
+#' ---
+#' title: "Kline and Moretti (2014)"
+#' ---
+#' Replicate Table 3 of Kline and Moretti (2014) with extension that includes
+#' spillover control using rings method
+
+# %%
+#| message: false
+#| warning: false
+library(tidyverse, warn.conflicts = FALSE)
+library(fixest)
+library(haven)
+library(sf)
+library(Rcpp)
+library(RcppArmadillo)
+library(kfbmisc)
+
+# Helper functions
+source(here::here("code/TVA/helpers.R"))
+source(here::here("code/TVA/helper-conley.R"))
+h_w_ratio <- 9 / 16
+
+# %%
+df <- read_dta(here::here("data/tva/build.dta")) |>
+  mutate(
+    fips = sprintf("%05d", fipstat * 1000 + fipcnty)
+  )
+
+counties <- sf::read_sf(here::here("data/2010_county.geojson")) |>
+  mutate(fips = paste0(STATEFP10, COUNTYFP10)) |>
+  select(state = STATEFP10, county = COUNTYFP10, fips) |>
+  rmapshaper::ms_simplify(keep = 0.05)
+
+# Create TVA shape
+tva_fips <- scan(here::here("data/tva/tvacounties.txt"), character())
+
+tva <- counties |>
+  filter(fips %in% tva_fips) |>
+  summarize()
+
+dist_mat <- st_distance(counties |> st_point_on_surface(), tva)
+counties$dist_to_tva <- as.vector(units::drop_units(units::set_units(dist_mat, "mi")))
+
+setFixest_fml(
+  ..controls = ~ lnelevmax + lnelevrang + lnarea + lnpop20 + lnpop20sq + lnpop30 + lnpop30sq + popdifsq + agrshr20 + agrshr20sq + agrshr30 + agrshr30sq + manufshr20 + manufshr30 + lnwage20 + lnwage30 + lntwage30 + lnemp20 + lnemp30 + urbshare20 + urbshare30 + lnfaval20 + lnfaval30 + lnmedhsval30 + lnmedrnt30 + white20 + white20sq + white30 + white30sq + pctil20 + pctil30 + urate30 + fbshr20 + fbshr30 + PRADIO30 + nowage20dum + nowage30dum + notwage30dum
+)
+
[…]

### 2024-02-02 code/TVA/helper-conley.R

@@ -1,0 +1,108 @@
+## -----------------------------------------------------------------------------
+## helper-conley.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## This creates R functions for Conley (1999) Spatial-HAC standard errors. 
+## For panel or cross-sectional data. For cross-sectional just don't include time and id vectors 
+## -----------------------------------------------------------------------------
+
+library(Rcpp)
+library(RcppArmadillo)
+
+Rcpp::sourceCpp(here::here("code/TVA/helper-conley.cpp"))
+
+
+#' Conley Spatial-HAC Variance-Covariance Matrix
+#' 
+#' Formula from: Conley (1999) and Robust Inference with Multi-way Clustering
+#' Original code from: https://github.com/darinchristensen/conley-se
+#' 
+#' @param X - nxk matrix of covariates (don't include lat and long if not in regression; if using fixed effects, they should not be included and X should be centered. See the `demeaned` option in `fixest::feols` if you want centered Xs)
+#' @param e - vector of residuals
+#' @param coords - nx2 matrix of lat and long (order doesn't matter)
+#' @param dist_cutoff - Cutoff distance in km for spatial correlation
+#' @param lag_cutoff - (optional if panel) Cutoff time in units of your time variable for serial correlation
+#' @param id - (optional if panel) nx1 vector of id variable
+#' @param time - (optional if panel) nx1 vector of time variable (can be in any units)
+#'
+#' @note could be speed up if you put the lapply within C++ code. I calculate the N^2 distances for each time period
+conley_ses <- function(X, e, coords, dist_cutoff, lag_cutoff = 0, id = NULL, time = NULL) {
+	
+	X <- as.matrix(X)
+	coords <- as.matrix(coords)
+	e <- as.matrix(e)
+	
+	n <- nrow(X)
+	k <- ncol(X)
+	
+	panel <- !(is.null(id) | is.null(time))
+	if(!panel) print("No Panel dimension provided. Using just Spatial adjustment")
+	if(panel) {
+		time = as.matrix(time)
+		id = as.matrix(id)
+	}
+	
[…]

### 2024-02-02 code/main.R

@@ -1,0 +1,26 @@
+#' # Main script to run the complete project
+#' 
+#' `render_file` will run the R file and log the results of the script 
+#' in the `logbook`. The logbook can be viewed with 
+#' `quarto preview logbook` from the terminal.
+library(here)
+source(here("logbook/render_file.R"))
+
+# Examples ---------------------------------------------------------------------
+0 && render_file(here("code/rings-example/rings_example.R"))
+
+# TVA --------------------------------------------------------------------------
+1 && render_file(here("code/TVA/analysis.R"))
+
+# CHC --------------------------------------------------------------------------
+1 && render_file(here("code/chc/analysis.R"))
+
+# Opportunity Zones ------------------------------------------------------------
+0 && render_file(here("code/OZ/replication.R"))
+0 && render_file(here("code/OZ/spillovers.R"))
+
+# Simulations ------------------------------------------------------------------
+0 && render_file(here("code/simulations/misspecified_exposure_mapping.R"))
+
+
+

### 2024-02-02 code/rings-example/rings_example.R

@@ -1,0 +1,414 @@
+#' ---
+#' title: "Example single indicator vs. multiple rings"
+#' ---
+
+# %%
+#| message: false
+#| warning: false
+library(tidyverse, warn.conflicts = FALSE)
+library(glue)
+library(here)
+library(binsreg)
+library(kfbmisc)
+
+# Counterfactual Trends Everywhere ---------------------------------------------
+#' First we will generate a setting where parallel trends is constant across distance from nearest treated (e.g. small neighborhood around treatment where treatment location is random). This makes rings very effective. 
+ 
+# %%
+set.seed(100)
+df <- tibble(id = 1:500) |>
+  # Generate Treatment and Distance
+  mutate(
+    treat = runif(n()) > 0.8,
+    treat = as.numeric(treat),
+    control = 1 - treat,
+    dist = runif(n(), 0, 90),
+    dist = dist * (1 - treat)
+  ) |>
+  # Make pre-post
+  expand_grid(t = c(0, 1)) |>
+  # Treatment Effects
+  mutate(
+    te = treat * t * 2,
+    spill1 = 1.5 * t * exp(-0.03 * dist) * (1 - treat) * (dist <= 40),
+    eps = rnorm(n(), mean = 0, sd = 0.05),
+    y1 = 2 * t + te + spill1 + eps
+  )
+
+# %%
+first_diff <- df |>
+  arrange(id, t) |>
+  group_by(id) |>
+  mutate(
+    d_y1 = y1 - lag(y1)
+  ) |>
+  filter(t == 1)
+
+ggplot() +
+  geom_point(
+    data = first_diff, aes(x = dist, y = d_y1), 
+    shape = 16, col = "lightgrey"
+  ) +
+  labs(
+    x = "Distance to nearest treated", 
+    y = "Change in y"
+  ) +
+  kfbmisc::theme_kyle(base_size = 12)
+
+## Ad-Hoc Approach -------------------------------------------------------------
+
+# %%
+# Bins for 0-15, 15-30, 30-45
+first_diff <- first_diff |>
+  mutate(
+    within_0_60  = dist > 0 & dist <= 60,
+    within_0_15  = dist > 0 & dist <= 15,
+    within_15_30 = dist > 15 & dist <= 30,
[…]

### 2024-02-02 code/simulations/helper-sim_function.R

@@ -1,0 +1,180 @@
+## -----------------------------------------------------------------------------
+## helper-sim_function.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## This file is going to create a function that will be used for monte carlo simulations. There will be many options to the function that can be used to test things. 
+## -----------------------------------------------------------------------------
+
+## Sim Function ----------------------------------------------------------------
+
+#' Returns a dataframe generated with the given parameters to be used for diff-in-diff estimation
+#'
+#' @param treat_prob This is the unconditional probability of treatment
+#' @param treat_spillover_distance The maximum distance in miles away a treated county can be to be considered treated 
+#' @param treat_effect The true simulated treatment effect
+#' @param treat_effect_spill The true simulated spillover effect. This effect is non-additive
+#' @param treat_effect_spill_treat The true simulated spillover effect onto treated units.
+#' @param spill_type Either "within", "contig", or "decay". Represents how spillover indicator is created
+#' @param spatial_autocorr Should there be spatial autocorrelation of treament
+#' @param zone_plus Value >= 0 and tells you how much to favor counties with values in the top 10% of the generated field
+#' @param remove_spill Should control units with spillover effects be removed
+#' 
+#' @return a tibble of estimates of treatment effect under different scenarios. This will be used with dplyr::add_row
+#'
+sim_data <- function(
+	treat_prob = 0.1,
+	treat_spillover_distance = 40,
+	treat_effect = 2,
+	treat_effect_spill = 1,
+	treat_effect_spill_treat = 0.5,
+	spill_type = "contig",
+	spatial_autocorr = FALSE,
+	zone_plus = 0.4,
+	drop_geometry = TRUE
+){
+	## Create Treatment and Spillover Variables --------------------------------
+	
+	# Logical matrix, =1 if within the maxmium distance for spillover
+	within <- (dist_mi > 0 & dist_mi <= treat_spillover_distance)
+
+	# Spatial Decay
[…]

### 2024-02-02 code/simulations/helper-sim_function_misspecification.R

@@ -1,0 +1,144 @@
+#' This file is going to create a function that will be used for monte carlo simulations. There will be many options to the function that can be used to test things.
+#' 
+
+#' Generate treatment and spillover effects
+#' 
+#' @param treat_prob This is the unconditional probability of treatment
+#' @param treat_effect The true simulated treatment effect
+#' @param treat_effect_spill The true simulated spillover onto control units
+#' @param normalize Should the treatment effects be normalized across specifications
+#' 
+#' @return counties modified with treatment/spillover vars
+gen_treat_and_spill <- function(
+	counties, 
+	treat_prob = 0.05,
+	treat_effect = 2,
+	treat_effect_spill = 1,
+	normalize = TRUE
+) {
+
+	counties$treat = runif(nrow(counties)) <= treat_prob
+	counties$control = !counties$treat
+	counties$treat_effect = treat_effect
+
+	# Closest
+	counties$closest_treat = apply(dist_mi[, counties$treat], 1, min)
+
+	# create treatment and spillover variables
+  counties <- counties |>
+    mutate(
+      # Within
+      spill_within = control & (closest_treat <= 40),
+      # Within Large
+      spill_within_large = control & (closest_treat <= 80),
+      # Within 100
+      spill_within_100 = control & (closest_treat <= 100),
+      # Within Additive
+      spill_within_additive = 
+				control * rowSums(within[, treat]),
+      # Within Large Additive
+      spill_within_large_additive = 
+				control * rowSums(within_large[, treat]),
+      # Decay Additive w/ Cutoff Length
+      spill_decay_additive = 
+				control * rowSums(spatial_decay[, treat]),
+      # Decay (Closest) w/ Cutoff Length
+			# Following https://fmwww.bc.edu/repec/bocode/s/spgen.pdf
+      spill_decay = 
+				exp(-0.02 * closest_treat) * (closest_treat <= 80),
+      # Spillover Rings
+      spill_0_20 = control & between(closest_treat, 0, 20),
+      spill_20_30 = control & between(closest_treat, 20, 30),
+      spill_30_40 = control & between(closest_treat, 30, 40),
+      spill_40_60 = control & between(closest_treat, 40, 60),
+      spill_60_80 = control & between(closest_treat, 60, 80),
+      spill_80_100 = control & between(closest_treat, 80, 100),
[…]

### 2024-02-02 code/simulations/misspecified_exposure_mapping.R

@@ -1,0 +1,410 @@
+#' ---
+#' title: "Misspecification of Exposure Mapping"
+#' ---
+#' This file performs a set of Monte Carlo simulations that estimate a set of
+#' DGPs using various exposure mappings and estimates them using exposure
+#' mappings and ring(s). The first simulation reports on average bias found in
+#' the treatment effect estimate and the second simulation reports on the
+#' ability to accurately predict spillover effects from fitted values.
+
+# %%
+#| message: false
+#| warning: false
+library(tidyverse, warn.conflicts = FALSE)
+library(data.table)
+library(here)
+library(glue)
+library(sf)
+library(stars)
+library(fixest)
+library(doParallel)
+library(gt)
+library(kfbmisc)
+library(Matrix)
+
+# flags
+EXPORT <- FALSE
+RUN <- TRUE
+
+# %%
+# extract_body()
+extract_body <- function(gt) {
+  if (inherits(gt, "gt_tbl")) gt <- as.character(gt::as_latex(gt))
+	gt = stringr::str_split_1(gt, "\\n")
+	
+	idx = c(
+		which(str_detect(gt, "\\\\midrule")) + 1,
+		which(str_detect(gt, "\\\\bottomrule")) - 1
+	)
+	gt = paste0(gt[idx[1]:idx[2]], collapse = "\n")
+  stringr::str_remove(gt, " \\\\\\\\ \n$")
+}
+
+# sim_data_misspecification()
+source(here::here("code/simulations/helper-sim_function_misspecification.R"))
+
+# Helper function estimate
+estimate_treatment_effect <- function(df, formula, treat_var) {
+  coef(feols(formula, data = df, warn = FALSE, notes = FALSE))[[treat_var]]
+}
+
+
+#' From data_prepare_counties.R
+# %%
+# counties, dist_mi
+load(file = here::here("data/counties_and_mat.RData"))
+
+counties = counties |> st_drop_geometry() |> as.data.table()
+
+# Logical matrix, =1 if within the maxmium distance for spillover
+within <- (dist_mi > 0 & dist_mi <= 40)
+within_large <- (dist_mi > 0 & dist_mi <= 80)
+within_100 <- (dist_mi > 0 & dist_mi <= 100)
+within_0_20 <- (dist_mi > 0 & dist_mi <= 20)
+within_20_30 <- (dist_mi > 20 & dist_mi <= 30)
+within_30_40 <- (dist_mi > 30 & dist_mi <= 40)
[…]

### 2024-02-02 code/simulations/prepare_county_data.R

@@ -1,0 +1,57 @@
+## -----------------------------------------------------------------------------
+## data-prepare_counties.R
+## Kyle Butts, CU Boulder Economics 
+## 
+## Downloads counties, simplifies geometries, create distance matrix and 
+## contiguous matrix, and saves it.
+## -----------------------------------------------------------------------------
+
+library(tidyverse, warn.conflicts = FALSE)
+library(sf)
+library(stars)
+library(units)
+library(tigris)
+library(here)
+
+
+## Prepare Spatial Data --------------------------------------------------------
+
+# Load FIPS codes
+data("fips_codes", package= "tigris")
+
+# Load Counties Shapefile at low resolution
+counties <- sf::read_sf(here::here("data/2010_county.geojson")) |> 
+	sf::st_make_valid() |> st_buffer(0) |>
+	select(state_code= STATEFP10, county_code= COUNTYFP10) |>
+	# Merge with fips_codes to get state and county names
+	left_join(., fips_codes, by= c("state_code", "county_code")) |>
+	# Remove non-continental states
+	filter(!state_name %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) |>
+	mutate(state_county = paste(state_code, county_code, sep="-")) |> 
+	arrange(state_code, county_code)
+
+
+# Load Counties Center of Populaion from NHGIS
+counties_centpop <- sf::read_sf(here::here("data/2010_centpop/US_county_cenpop_2010.shp")) |>
+	filter(!STNAME %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) |>
+	select(state_code= STATEFP, county_code= COUNTYFP) |>
+	arrange(state_code, county_code) |> 
+	# Project to a prettier US project EPSG:2163
+	st_transform(st_crs(2163))
+
+## Create Distance Matrix ------------------------------------------------------
+counties$centroid <- counties_centpop$geometry
+
+# st_crs(counties) will show you that units are in meters
+dist <- st_distance(st_geometry(counties_centpop))
+
+dist_mi <- dist |>
+	units::set_units(., "mi") |> 
+	units::drop_units()
+
+contiguous <- st_touches(counties, counties, sparse= FALSE)
+
+
+## Save Results ----------------------------------------------------------------
+
+save(counties, dist_mi, contiguous, file = here::here("data/counties_and_mat.RData"))

### 2024-02-02 data-prepare_counties.R

@@ -1,57 +1,0 @@
-## -----------------------------------------------------------------------------
-## data-prepare_counties.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## Downloads counties, simplifies geometries, create distance matrix and 
-## contiguous matrix, and saves it.
-## -----------------------------------------------------------------------------
-
-library(tidyverse)
-library(sf)
-library(stars)
-library(units)
-library(tigris)
-library(here)
-
-
-## Prepare Spatial Data --------------------------------------------------------
-
-# Load FIPS codes
-data("fips_codes", package= "tigris")
-
-# Load Counties Shapefile at low resolution
-counties <- sf::read_sf(here::here("data/2010_county.geojson")) %>% 
-	sf::st_make_valid() %>% st_buffer(0) %>%
-	select(state_code= STATEFP10, county_code= COUNTYFP10) %>%
-	# Merge with fips_codes to get state and county names
-	left_join(., fips_codes, by= c("state_code", "county_code")) %>%
-	# Remove non-continental states
-	filter(!state_name %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) %>%
-	mutate(state_county = paste(state_code, county_code, sep="-")) %>% 
-	arrange(state_code, county_code)
-
-
-# Load Counties Center of Populaion from NHGIS
-counties_centpop <- sf::read_sf(here::here("data/2010_centpop/US_county_cenpop_2010.shp")) %>%
-	filter(!STNAME %in% c("Alaska", "Hawaii", "Puerto Rico", "U.S. Virgin Islands", "American Samoa", "Northern Mariana Islands", "Guam")) %>%
-	select(state_code= STATEFP, county_code= COUNTYFP) %>%
-	arrange(state_code, county_code) %>% 
-	# Project to a prettier US project EPSG:2163
-	st_transform(st_crs(2163))
-
-## Create Distance Matrix ------------------------------------------------------
-counties$centroid <- counties_centpop$geometry
-
-# st_crs(counties) will show you that units are in meters
-dist <- st_distance(st_geometry(counties_centpop))
-
-dist_mi <- dist %>%
-	units::set_units(., "mi") %>% 
-	units::drop_units()
-
-contiguous <- st_touches(counties, counties, sparse= FALSE)
-
-
-## Save Results ----------------------------------------------------------------
-
-save(counties, dist_mi, contiguous, file = here::here("data/counties_and_mat.RData"))

### 2024-02-02 figure-example_exposure_mappings.R

@@ -1,139 +1,0 @@
-## -----------------------------------------------------------------------------
-## figure-example_exposure_mappings.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## Create examples of each exposure mapping using US counties
-## -----------------------------------------------------------------------------
-
-library(tidyverse)
-library(here)
-library(glue)
-library(sf)
-library(stars)
-library(fixest)
-library(doParallel)
-library(gt)
-library(kfbmisc)
-
-# Export Options
-slides <- TRUE
-h_w_ratio <- 9/16
-
-# sim_data_misspecification()
-source("helper-sim_function_misspecification.R")
-
-
-## Load Spatial Data -----------------------------------------------------------
-# From data_prepare_counties.R
-load(file= here::here("data/counties_and_mat.RData"))
-
-us <- counties %>% summarize()
-
-set.seed(20210215)
-
-df <- sim_data_misspecification(drop_geometry = FALSE, normalize = TRUE) %>% 
-	st_as_sf()
-
-
-## Treatment Effect ------------------------------------------------------------
-
-types <- c(
-	"Within 40mi." = "spill_within", 
-	"Within 80mi." = "spill_within_large", 
-	"Within 40mi. (Additive)" = "spill_within_additive", 
-	"Within 80mi. (Additive)" = "spill_within_large_additive", 
-	"Decay" = "spill_decay", 
-	"Decay (Additive)" = "spill_decay_additive"
-)
-
-
-
-for(type in types){
-	title <- names(types)[types == type]
-	cli::cli_rule(glue("{title}: {type}"))
-
-	temp <- df %>% 
-		filter(year == 2019) %>% 
-		mutate(!!rlang::sym(glue("te_{type}")) := if_else(treat == 1, NA_real_, !!rlang::sym(glue("te_{type}"))))
-	
-
-	
-	(
-		plot <- ggplot(data = temp) + 
-			geom_sf(mapping = aes(fill = !!rlang::sym(glue("te_{type}")), color = as.factor(treat)), size= 0.2) + 
-			geom_sf(data = us, color = "black", fill = NA) + 
-			scale_color_manual(values = c("white", "black"), labels = c("Not Treated", "Treated")) +
-			coord_sf(datum = NA) +
-			labs(
-				title = title,
[…]

### 2024-02-02 figure-rings_example.R

@@ -1,402 +1,0 @@
-## figure-binscatter_example.R -------------------------------------------------
-## Kyle Butts, CU Boulder Economics
-##
-## Single indicator vs. multiple rings
-
-library(tidyverse)
-library(glue)
-library(binsreg)
-library(kfbmisc)
-
-# Generate Data ----------------------------------------------------------------
-
-set.seed(100)
-
-df <- tibble(id = 1:500) %>%
-  # Generate Treatment and Distance
-  mutate(
-    treat = runif(n()) > 0.8,
-    treat = as.numeric(treat),
-    control = 1 - treat,
-    dist = runif(n(), 0, 90),
-    dist = dist * (1 - treat)
-  ) %>%
-  # Make pre-post
-  expand_grid(t = c(0, 1)) %>%
-  # Treatment Effects
-  mutate(
-    te = treat * t * 2,
-    spill1 = 1.5 * t * exp(-0.03 * dist) * (1 - treat) * (dist <= 40),
-    eps = rnorm(n(), mean = 0, sd = 0.05),
-    y1 = 2 * t + te + spill1 + eps
-  )
-
-
-# Take First Differences
-first_diff <- df %>%
-  arrange(id, t) %>%
-  group_by(id) %>%
-  mutate(
-    d_y1 = y1 - lag(y1)
-  ) %>%
-  filter(t == 1)
-
-ggplot() +
-  geom_point(data = first_diff, aes(x = dist, y = d_y1), shape = 16, col = "lightgrey")
-
-# Ad-Hoc Approach --------------------------------------------------------------
-
-# Bins for 0-15, 15-30, 30-45
-first_diff <- first_diff %>%
-  mutate(
-    within_0_60  = dist > 0 & dist <= 60,
-    within_0_15  = dist > 0 & dist <= 15,
-    within_15_30 = dist > 15 & dist <= 30,
-    within_30_45 = dist > 30 & dist <= 45,
-    within_45_60 = dist > 45 & dist <= 60
-  )
-
-reg <- fixest::feols(d_y1 ~ treat + within_0_15 + within_15_30 + within_30_45 + within_45_60, data = first_diff) %>% coef()
-
-dots <- tribble(
-  ~x, ~fit,
-  0, reg[["treat"]] + reg[["(Intercept)"]],
-  7.5, reg[["within_0_15TRUE"]] + reg[["(Intercept)"]],
[…]

### 2024-02-02 helper-conley.R

@@ -1,108 +1,0 @@
-## -----------------------------------------------------------------------------
-## helper-conley.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## This creates R functions for Conley (1999) Spatial-HAC standard errors. 
-## For panel or cross-sectional data. For cross-sectional just don't include time and id vectors 
-## -----------------------------------------------------------------------------
-
-library(Rcpp)
-library(RcppArmadillo)
-
-Rcpp::sourceCpp("helper-conley.cpp")
-
-
-#' Conley Spatial-HAC Variance-Covariance Matrix
-#' 
-#' Formula from: Conley (1999) and Robust Inference with Multi-way Clustering
-#' Original code from: https://github.com/darinchristensen/conley-se
-#' 
-#' @param X - nxk matrix of covariates (don't include lat and long if not in regression; if using fixed effects, they should not be included and X should be centered. See the `demeaned` option in `fixest::feols` if you want centered Xs)
-#' @param e - vector of residuals
-#' @param coords - nx2 matrix of lat and long (order doesn't matter)
-#' @param dist_cutoff - Cutoff distance in km for spatial correlation
-#' @param lag_cutoff - (optional if panel) Cutoff time in units of your time variable for serial correlation
-#' @param id - (optional if panel) nx1 vector of id variable
-#' @param time - (optional if panel) nx1 vector of time variable (can be in any units)
-#'
-#' @note could be speed up if you put the lapply within C++ code. I calculate the N^2 distances for each time period
-conley_ses <- function(X, e, coords, dist_cutoff, lag_cutoff = 0, id = NULL, time = NULL) {
-	
-	X <- as.matrix(X)
-	coords <- as.matrix(coords)
-	e <- as.matrix(e)
-	
-	n <- nrow(X)
-	k <- ncol(X)
-	
-	panel <- !(is.null(id) | is.null(time))
-	if(!panel) print("No Panel dimension provided. Using just Spatial adjustment")
-	if(panel) {
-		time = as.matrix(time)
-		id = as.matrix(id)
-	}
-	
-	# Spatial Correlation ------------------------------------------------------
-	
[…]

### 2024-02-02 helper-sim_function.R

@@ -1,180 +1,0 @@
-## -----------------------------------------------------------------------------
-## helper-sim_function.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## This file is going to create a function that will be used for monte carlo simulations. There will be many options to the function that can be used to test things. 
-## -----------------------------------------------------------------------------
-
-## Sim Function ----------------------------------------------------------------
-
-#' Returns a dataframe generated with the given parameters to be used for diff-in-diff estimation
-#'
-#' @param treat_prob This is the unconditional probability of treatment
-#' @param treat_spillover_distance The maximum distance in miles away a treated county can be to be considered treated 
-#' @param treat_effect The true simulated treatment effect
-#' @param treat_effect_spill The true simulated spillover effect. This effect is non-additive
-#' @param treat_effect_spill_treat The true simulated spillover effect onto treated units.
-#' @param spill_type Either "within", "contig", or "decay". Represents how spillover indicator is created
-#' @param spatial_autocorr Should there be spatial autocorrelation of treament
-#' @param zone_plus Value >= 0 and tells you how much to favor counties with values in the top 10% of the generated field
-#' @param remove_spill Should control units with spillover effects be removed
-#' 
-#' @return a tibble of estimates of treatment effect under different scenarios. This will be used with dplyr::add_row
-#'
-sim_data <- function(
-	treat_prob = 0.1,
-	treat_spillover_distance = 40,
-	treat_effect = 2,
-	treat_effect_spill = 1,
-	treat_effect_spill_treat = 0.5,
-	spill_type = "contig",
-	spatial_autocorr = FALSE,
-	zone_plus = 0.4,
-	drop_geometry = TRUE
-){
-	## Create Treatment and Spillover Variables --------------------------------
-	
-	# Logical matrix, =1 if within the maxmium distance for spillover
-	within <- (dist_mi > 0 & dist_mi <= treat_spillover_distance)
-
-	# Spatial Decay
[…]

### 2024-02-02 helper-sim_function_misspecification.R

@@ -1,211 +1,0 @@
-## -----------------------------------------------------------------------------
-## helper-sim_function_misspecification.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## This file is going to create a function that will be used for monte carlo simulations. There will be many options to the function that can be used to test things. 
-## -----------------------------------------------------------------------------
-
-## Sim Function ----------------------------------------------------------------
-
-#' Returns a dataframe generated with the given parameters to be used for diff-in-diff estimation
-#'
-#' @param treat_prob This is the unconditional probability of treatment
-#' @param treat_spillover_distance The maximum distance in miles away a treated county can be to be considered treated 
-#' @param treat_effect The true simulated treatment effect
-#' @param treat_effect_spill The true simulated spillover effect.
-#' @param treat_effect_spill_treat The true simulated spillover effect onto treated units.
-#' @param spill_type Either "within", "contig", or "decay". Represents how spillover indicator is created
-#' @param spatial_autocorr Should there be spatial autocorrelation of treament
-#' @param zone_plus Value >= 0 and tells you how much to favor counties with values in the top 10% of the generated field
-#' @param remove_spill Should control units with spillover effects be removed
-#' @param normalize Should the treatment effects be normalized across specifications
-#' 
-#' @return a tibble of estimates of treatment effect under different scenarios. This will be used with dplyr::add_row
-#'
-sim_data_misspecification <- function(
-	treat_prob = 0.05,
-	treat_spillover_distance = 40,
-	treat_spillover_distance_large = 80,
-	treat_effect = 2,
-	treat_effect_spill = 1,
-	treat_effect_spill_treat = 0.5,
-	spill_type = "contig",
-	spatial_autocorr = FALSE,
-	zone_plus = 0.4,
-	drop_geometry = TRUE,
-	normalize = TRUE
-){
-	## Create Treatment and Spillover Variables --------------------------------
-	
[…]

### 2024-02-02 logbook/copy_readme.R

@@ -1,0 +1,11 @@
+readme_file <- here::here("README.md")
+out_file <- here::here("logbook", "index.md")
+
+if (fs::file_exists(readme_file)) {
+  fs::file_copy(readme_file, out_file, overwrite = TRUE)
+} else {
+  cat(
+    "# TODO: Create a README.md file in the project directory",
+    file = here::here("logbook", "index.md")
+  )
+}

### 2024-02-02 logbook/render_file.R

@@ -1,0 +1,303 @@
+# REPRO_ORDER <- list()
+# repro_init <- function() { 
+#   REPRO_ORDER <<- list()
+# }
+# repro_section <- function(str) {
+#   if (!exists(str, where = REPRO_ORDER)) {
+#     REPRO_ORDER[str] = c()
+#   }
+# }
+
+#' Code layout:
+#' 1. Functions `preprocess_R/py/jl_file` that will do small changes before
+#' rendering. Mainly converting # Header ---- to #' ## Header.
+#' This will save the file as a `index.R/py/jl`
+#'
+#' 2. Function that takes `index.R/py/jl`, runs `quarto render` to produce
+#' `index.html.md`, using `keep-md` true. This is the intermediate step
+#' before producing a html file that has run the code, but not converted.
+#' This will be moved to the logbook as `index.md`. Additionally, a
+#' `readme.md` will be made from rendering to `gfm`.
+#' This function is also in charge of cleanup.
+#
+
+#' Take file and create a default title
+#' @param file A file name
+#' @examples 
+#'  file_to_title("render_file.R")
+#' @return String of title
+file_to_title <- function(file) {
+  default_title <- fs::path_ext_remove(fs::path_file(file))
+  default_title <- gsub("_", " ", default_title)
+  default_title <- gsub("-", " ", default_title)
+  # title case
+  default_title <- gsub(
+    "(^|\\s)([a-z])",
+    "\\1\\U\\2",
+    default_title,
+    perl = TRUE
+  )
+  return(default_title)
+}
+preprocess_R_file <- function(file, index_file_name) {
+  txt <- xfun::read_utf8(here::here(file))
+
+  # Add default yaml frontmatter, if needed
+  # Look for `#' ---` at the start of the file
+  # matches https://github.com/quarto-dev/quarto-cli/blob/770c47fbfeefe404fa43799116922bdb7c47a3c1/src/execute/rmd.ts#L395
+  has_yaml <- grepl("^\\s*#'\\s*---", txt[1])
+  if (!has_yaml) {
+    txt <- c(
+      "#' ---",
+      paste0("#' title: '", file_to_title(file), "'"),
+      "#' ---",
+      txt
+    )
+  }
+
+  # Convert code headers
+  # `# Header ----` -> `#' ## Header`
+  regex_header <- "^(#{1,}) (.*?)-{4,}"
+  txt <- gsub(
+    regex_header,
+    "#' \\1# \\2",
+    txt
+  )
+
+  # Save as index file
[…]

### 2024-02-02 sim-misspecification_of_spillover.R

@@ -1,355 +1,0 @@
-## -----------------------------------------------------------------------------
-## sim-misspecification_of_spillover.R
-## Kyle Butts, CU Boulder Economics 
-## 
-## This file performs a set of Monte Carlo simulations that estimate a set of 
-## DGPs using various exposure mappings and estimates them using exposure 
-## mappings and ring(s). The first simulation reports on average bias found in 
-## the treatment effect estimate and the second simulation reports on the 
-## ability to accurately predict spillover effects from fitted values.
-## -----------------------------------------------------------------------------
-
-library(tidyverse)
-library(here)
-library(glue)
-library(sf)
-library(stars)
-library(fixest)
-library(doParallel)
-library(gt)
-library(kfbmisc)
-
-# Export
-export <- TRUE
-run <- FALSE
-
-# extract_body()
-extract_body <- function(gt) {
-	if(inherits(gt, "gt_tbl")) gt <- as.character(gt::as_latex(gt))
-	gt <- stringr::str_match(gt, "(?s)\\\\midrule\\n(.*)\\\\bottomrule")[[2]]
-	stringr::str_remove(gt, " \\\\\\\\ \n$")
-}
-
-
-# sim_data_misspecification()
-source(here::here("helper-sim_function_misspecification.R"))
- 
-
-# ---- Load Spatial Data -------------------------------------------------------
-# From data_prepare_counties.R
-load(file= here::here("data/counties_and_mat.RData"))
-
-
-# ---- Simulation: Bias --------------------------------------------------------
-# Simulates a set of DGPs with different kinds of exposure mappings
-# For each DGP, estimates using many different parametric forms + ring(s) method
-# Report on the bias of the treatment effect estimate
-
-# Helper function estimate
-estimate_treatment_effect <- function(df, formula, treat_var){
-	feols(formula, data= df) %>%
-		coefficients() %>% .[[treat_var]]
-}
-
-
-n_trials <- 1000
-doParallel::registerDoParallel(10)
-
-dgp_types <- c(
[…]

### 2024-02-02 tva-analysis-replicate.R

@@ -1,385 +1,0 @@
-## tva-analysis-replicate.R ----------------------------------------------------
-## Kyle Butts, CU Boulder Economics 
-## 
-## Replicate Table 3 of Klein and Moretti (2014) with extension that includes
-## spillover control using rings method
-
-library(tidyverse)
-library(haven)
-library(sf)
-library(Rcpp)
-library(RcppArmadillo)
-library(kfbmisc)
-
-# Helper functions
-source(here::here("tva-analysis-helpers.R"))
-source(here::here("helper-conley.R"))
-
-h_w_ratio <- 9/16
-
-
-# ---- Load Data ---------------------------------------------------------------
-
-df <- read_dta(here::here("data/tva/build.dta")) %>% 
-	mutate(
-		fips = sprintf("%05d", fipstat * 1000 + fipcnty)
-	)
- 
-counties <- sf::read_sf(here::here("data/2010_county.geojson")) %>% 
-	mutate(fips = paste0(STATEFP10, COUNTYFP10)) %>% 
-	select(state = STATEFP10, county = COUNTYFP10, fips) %>% 
-	rmapshaper::ms_simplify(keep = 0.05)
-
-# Create TVA shape
-tva_fips <- scan(here::here("data/tva/tvacounties.txt"), character())
-
-tva <- counties %>% 
-	filter(fips %in% tva_fips) %>% 
-	summarize()
-	
-dist_mat <- st_distance(counties %>% st_point_on_surface(), tva) 
-counties$dist_to_tva <- as.vector(units::drop_units(units::set_units(dist_mat, "mi")))
-
-
[…]
